### 2020-02-22 system-model.tex
:heavy_plus_sign: Problem formulation: received signal (in progress)

\documentclass{IEEEtran}

\input{info.tex}
\input{packages.tex}

\begin{document}

    \begin{section} {System Model}
        Consider a IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation. The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a time-division duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the user-AP and user-IRS-AP links. A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are adapted to the CSI to maximize the rate-energy tradeoff \cite{Clerckx2018b}. Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}. Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.

        \begin{subsection} {Transmitted Signal}

            \begin{subsubsection} {Modulated Information Waveform}
                Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+n \Delta f$ ($n = 1,\dots,N$). The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e. $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$). Denote $w_{I,n,m} = s_{I,n,m} e^{j\phi_{I,n,m}}$ as the information weight on the $n$-th subcarrier of the $m$-th ($m = 1,\dots,M$) transmit antenna with magnitude $s_{I,n,m}$ and phase $\phi_{I,n,m}$, the corresponding modulated symbol can be expressed as $x_{I,n,m} = \tilde{s}_{I,n,m} e^{j\tilde{\phi}_{I,n,m}}$, with $\tilde{s}_{I,n,m} = s_{I,n,m} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n,m} = \phi_{I,n,m} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e. $x_{I,n,m} \sim \mathcal{CN}(0,s_{I,n,m}^2)$). Therefore, the transmit information waveform on the antenna $m$ at time $t$ writes as
                \begin{equation} \label{eq:x_{I,m}(t)}
                    \begin{split}
                        x_{I,m}(t)
                        &= \sum_{n=1}^{N} \tilde{s}_{I,n,m}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{I,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{I,n,m} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

            \begin{subsubsection} {Unmodulated Power Waveform}
                As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy. It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ on subband $n$ is a constant (i.e. $\tilde{x}_{P,n} = 1$). Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e. $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband. The transmit power waveform on the antenna $m$ at time $t$ is given by
                \begin{equation} \label{eq:x{P,m}(t)}
                    \begin{split}
                        x_{P,m}(t)
                        &= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right) \\
                        &= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\} \\
                        &= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

            \begin{subsubsection} {Superposed Waveform}
                At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ gives
                \begin{equation} \label{eq:x_{n,m}(t)}
                    \begin{split}
                        x_{n,m}(t)
                        &= x_{I,n,m}(t)+x_{P,n,m}(t) \\
                        &= w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}
                    \end{split}
                \end{equation}
                The transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
                \begin{equation} \label{eq:x_m(t)}
                    \begin{split}
                        x_m(t)
                        &= x_{I,m}(t)+x_{P,m}(t) \\
                        &= \Re \left\{ \sum_{n=1}^{N} (w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}) e^{j2 \pi f_n t} \right\}
                    \end{split}
                \end{equation}
            \end{subsubsection}

        \end{subsection}

        \begin{subsection} {Composite Channel Model}
            Consider a single-IRS scenario in a multipath environment. The frequency response of the AP-user (i.e. direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k} = \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$. Similarly, the AP-IRS channel between antenna $m$ and element $u$ at subband $n$ writes as $g_{n,m,u} = \sum_{l_u=1}^{L_u} \alpha_{l_u} e^{j\left( -2 \pi f_n \tau_{l_u}+\varsigma_{l_u,n,m,u} \right)}$, and the IRS-user (i.e. reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k} = \sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$. Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_u,l_{R,k} \neq l_u',l_{R,k}'} \lvert \left( \tau_{l_u}+\tau_{l_{R,k}} \right)-\left( \tau_{l_u'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_u}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_u}-\tau_{l_R}) = x_{n,m}(t)$.

            Stack the entries and denote the baseband equivalent channel from the AP to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, from the AP to the IRS as $\boldsymbol{G} \in \mathbb{C}^{U \times MN}$, and from the IRS to user $k$ as $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$. Element $u$ of the IRS receives a superposed waveform transmitted by $M$ antennas after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$ where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift. Note each passive reflector need to absorb a small portion ($1 - \beta_u$) of the signal and combine them to support information decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat IRS, we then construct the IRS reflecting coefficient matrix $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$ by stacking $R_0$ over $N$ subbands. The IRS-aided extra link from the AP to user $k$ can be modeled as a concatenation of the AP-IRS channel, the IRS reflection, and the IRS-user $k$ channel. Both the direct link and the IRS-aided link contributes to the overall channel of user $k$, which writes as
            \begin{equation} \label{eq:h_k}
                \boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{G} \right)
            \end{equation}
        \end{subsection}

        \begin{subsection} {Received Signal}
            In the signal received by the single antenna of user $k$, the component from transmit antenna $m$ through both direct and reflective links can be expressed as

            \begin{equation} \label{eq:y_{m,k}(t)}
                \begin{split}
                    y_{m,k}(t)
                    &= y_{I,m,k}(t)+y_{P,m,k}(t) \\
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} \alpha_{l_u} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_u}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_u})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{R,k},n,m,u}\right)} \right\} \\
                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t)g_{n,m,u}(t)) x_{n,m}(t) e^{j2 \pi f_n t} \right\}
                \end{split}
            \end{equation}

            It captures the contribution of information and power waveform.
        \end{subsection}
    \end{section}

    \bibliographystyle{IEEEtran}
    \bibliography{library.bib}
\end{document}

### 2020-03-02 system-model.tex
:pencil: Modify notations

@@
     \begin{section} {System Model}
-        Consider a IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation.
+        Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation.
 The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
@@
 The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the user-AP and user-IRS-AP links.
-A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are adapted to the CSI to maximize the rate-energy tradeoff \cite{Clerckx2018b}.
+A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}.
 Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}.
@@
             \begin{subsubsection} {Modulated Information Waveform}
-                Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+n \Delta f$ ($n = 1,\dots,N$).
+                Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$).
 The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d.
@@
                 As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy.
-It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ on subband $n$ is a constant (i.e.
+It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e.
 $\tilde{x}_{P,n} = 1$).
@@
             \begin{subsubsection} {Superposed Waveform}
-                At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ gives
+                At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ writes as
                 \begin{equation} \label{eq:x_{n,m}(t)}
@@
 direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k} = \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$.
-Similarly, the AP-IRS channel between antenna $m$ and element $u$ at subband $n$ writes as $g_{n,m,u} = \sum_{l_u=1}^{L_u} \alpha_{l_u} e^{j\left( -2 \pi f_n \tau_{l_u}+\varsigma_{l_u,n,m,u} \right)}$, and the IRS-user (i.e.
+Similarly, the AP-IRS (i.e.
+incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u} = \sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
 reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k} = \sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$.
-Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_u,l_{R,k} \neq l_u',l_{R,k}'} \lvert \left( \tau_{l_u}+\tau_{l_{R,k}} \right)-\left( \tau_{l_u'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_u}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_u}-\tau_{l_R}) = x_{n,m}(t)$.
+Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.
 
-            Stack the entries and denote the baseband equivalent channel from the AP to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, from the AP to the IRS as $\boldsymbol{G} \in \mathbb{C}^{U \times MN}$, and from the IRS to user $k$ as $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$.
+            Stack the entries and denote the baseband equivalent channel from the AP to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, from the AP to the IRS as $\boldsymbol{h}_I \in \mathbb{C}^{U \times MN}$, and from the IRS to user $k$ as $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$.
 Element $u$ of the IRS receives a superposed waveform transmitted by $M$ antennas after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$ where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift.
-Note each passive reflector need to absorb a small portion ($1 - \beta_u$) of the signal and combine them to support information decoding and impedance matching.
+Note each passive reflector need to absorb a small portion ($1 - \beta_u$) of the signal, then combine and harvest it to support information decoding and impedance matching.
 Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$.
-With the assumption of frequency-flat IRS, we then construct the IRS reflecting coefficient matrix $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$ by stacking $R_0$ over $N$ subbands.
-The IRS-aided extra link from the AP to user $k$ can be modeled as a concatenation of the AP-IRS channel, the IRS reflection, and the IRS-user $k$ channel.
-Both the direct link and the IRS-aided link contributes to the overall channel of user $k$, which writes as
+With the assumption of frequency-flat IRS, the IRS reflecting coefficient matrix $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$ is obtained by stacking $R_0$ over $N$ subbands.
+The IRS-aided extra link from the AP to user $k$ can be modeled as a concatenation of the AP-IRS channel, the IRS reflection, and the IRS-user channel.
+Both the direct link and the IRS-aided link contributes to the overall channel of user $k$ and the composite channel for user $k$ writes as
             \begin{equation} \label{eq:h_k}
-                \boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{G} \right)
+                \boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{h}_I} \right)
             \end{equation}
@@
         \begin{subsection} {Received Signal}
-            In the signal received by the single antenna of user $k$, the component from transmit antenna $m$ through both direct and reflective links can be expressed as
-
+            In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links.
+It can be expressed as
             \begin{equation} \label{eq:y_{m,k}(t)}
@@
                     y_{m,k}(t)
-                    &= y_{I,m,k}(t)+y_{P,m,k}(t) \\
                     &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} \alpha_{l_u} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_u}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_u})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{R,k},n,m,u}\right)} \right\} \\
-                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t)g_{n,m,u}(t)) x_{n,m}(t) e^{j2 \pi f_n t} \right\}
+                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
+                    &\approx \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t)) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
+                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) \beta_u e^{j\theta_u} h_{I,n,m,u}(t)) \left( w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m} \right) e^{j2{\pi} {f_n}{t}} \right\}
                 \end{split}
@@
 
-            It captures the contribution of information and power waveform.
         \end{subsection}

### 2020-03-03 system-model.tex
:pencil: Received signal

@@
                 \end{equation}
+                On top of this, the information waveform vector is spread over $M$ antennas
+                \begin{equation} \label{eq:x_I(t)}
+                    \boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
+                \end{equation}
+                where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T$.
             \end{subsubsection}
@@
                 \end{equation}
+                The corresponding power waveform vector is stacked across $M$ transmit antennas as
+                \begin{equation} \label{eq:x_P(t)}
+                    \boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
+                \end{equation}
+                where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T$.
             \end{subsubsection}
@@
                 \end{equation}
+                Hence, the composite transmit signal vector is
+                \begin{equation} \label{x(t)}
+                    \begin{split}
+                        \boldsymbol{x}(t)
+                        &=\boldsymbol{x}_I(t)+\boldsymbol{x}_P(t) \\
+                        &=\Re \left\{ \sum_{n=1}^{N} (\boldsymbol{w}_{I,n}\tilde{x}_n(t)+\boldsymbol{w}_{P,n}) e^{j2{\pi}{f_n}t} \right\}
+                    \end{split}
+                \end{equation}
             \end{subsubsection}
@@
 The frequency response of the AP-user (i.e.
-direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k} = \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$.
+direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k}=A_{D,n,m,k}e^{j\bar{\psi}_{D,n,m,k}}=\sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$.
 Similarly, the AP-IRS (i.e.
-incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u} = \sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
-reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k} = \sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$.
+incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
+reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$.
 Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.
@@
                     &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
-                    &\approx \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t)) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
-                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} (h_{D,n,m,k}(t)+h_{R,n,u,k}(t) \beta_u e^{j\theta_u} h_{I,n,m,u}(t)) \left( w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m} \right) e^{j2{\pi} {f_n}{t}} \right\}
+                    &\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
+                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
+                    &= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
+                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
+                    &\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
+                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
                 \end{split}
             \end{equation}
-
+            Therefore, the RF signal input to the antenna at user $k$ is
+            \begin{equation} \label{eq:y_{k}(t)}
+                y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
+            \end{equation}
         \end{subsection}

### 2020-04-04 system-model.tex
:pencil: Composite channel

@@
 The signals reflected by IRS for two and more times are assumed negligible and thus not considered.
-The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the user-AP and user-IRS-AP links.
+The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links.
 A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}.
-Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}.
+Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}.
 Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.
@@
 	\begin{subsection} {Composite Channel Model}
-            Consider a single-IRS scenario in a multipath environment.
+		% Consider a single-IRS scenario in a multipath environment.
 The frequency response of the AP-user (i.e.
@@
 reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$.
-Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.
+Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.;
 
-            Stack the entries and denote the baseband equivalent channel from the AP to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, from the AP to the IRS as $\boldsymbol{h}_I \in \mathbb{C}^{U \times MN}$, and from the IRS to user $k$ as $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$.
-Element $u$ of the IRS receives a superposed waveform transmitted by $M$ antennas after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$ where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift.
-Note each passive reflector need to absorb a small portion ($1 - \beta_u$) of the signal, then combine and harvest it to support information decoding and impedance matching.
+		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively.
+At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$.
+Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
+Element $u$ of the IRS receives a superposed waveform after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
+Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching.
 Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$.
-With the assumption of frequency-flat IRS, the IRS reflecting coefficient matrix $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$ is obtained by stacking $R_0$ over $N$ subbands.
-The IRS-aided extra link from the AP to user $k$ can be modeled as a concatenation of the AP-IRS channel, the IRS reflection, and the IRS-user channel.
-Both the direct link and the IRS-aided link contributes to the overall channel of user $k$ and the composite channel for user $k$ writes as
+With the assumption of frequency-flat reflection, the IRS matrix is obtained by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$.
+The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel.
+Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
 		\begin{equation} \label{eq:h_k}
-                \boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{h}_I} \right)
+			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
 		\end{equation}
+		On top of this, we select the $n$-th of every $N$ entries and combine them to form the subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, with $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
 	\end{subsection}
@@
 	\begin{subsection} {Received Signal}
-            In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links.
-It can be expressed as
+		In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links as
 		\begin{equation} \label{eq:y_{m,k}(t)}
-                \begin{split}
-                    y_{m,k}(t)
-                    &= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
-                    &\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
-                    &= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
-                    &\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
-                \end{split}
+			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}}\right\}
 		\end{equation}
-            Therefore, the RF signal input to the antenna at user $k$ is
-            \begin{equation} \label{eq:y_{k}(t)}
-                y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
-            \end{equation}
+		Therefore, the RF input signal to the antenna of user $k$ writes as
+		% \begin{equation}
+
+		% \end{equation}
+		% \begin{equation} \label{eq:y_{m,k}(t)}
+		% 	\begin{split}
+		% 		y_{m,k}(t)
+		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\} \\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\} \\
+		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\} \\
+		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\} \\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\} \\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
+		% 	\end{split}
+		% \end{equation}
+		% Therefore, the RF signal input to the antenna at user $k$ is
+		% \begin{equation} \label{eq:y_{k}(t)}
+		% 	y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
+		% \end{equation}
 	\end{subsection}

### 2020-04-05 system-model.tex
:pencil: Receiver architectures

@@
 \begin{section} {System Model}
-	Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves channel state information (CSI) and harvests energy for its own operation.
+	Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
 The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
 It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
-Due to the passive characteristics of IRS, we consider a time-division duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity.
+Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity.
 Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system.
 The signals reflected by IRS for two and more times are assumed negligible and thus not considered.
-The channel is assumed to be unchanged within each transmission frame and the quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links.
+A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame.
 A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}.
-Note that although frequency selective surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive while passive FSS is not reconfigurable with fixed physical characteristics \cite{Kim2006,Xu2014,Anwar2018}.
+Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}.
+In contrast, passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}.
 Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.
+Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
+In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots with duration ratio $(1 - \alpha)$ and $\alpha$ respectively.
+Hence, the achievable rate-energy region can be obtained through a direct time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$.
+The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design, since they are optimized individually in data and energy slots.
+In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1 - \rho)$ and $\rho$.
+Note that $\rho$ is coupled with waveform and IRS design.
+Therefore, the rate-energy region is disclosed by placing different rate constraints and optimizing waveform, PS ratio and reflectors accordingly.
+Perfect synchronization is assumed among the three parties in both operations.
 
@@
 			\end{equation}
-			where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T$.
+			where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
@@
 			\end{equation}
-			where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T$.
+			where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
@@
 Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
-Element $u$ of the IRS receives a superposed waveform after the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
+Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
 Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching.
 Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$.
-With the assumption of frequency-flat reflection, the IRS matrix is obtained by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$.
+With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$.
 The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel.
@@
 		\end{equation}
-		On top of this, we select the $n$-th of every $N$ entries and combine them to form the subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, with $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
+		On top of this, we select the $n$-th of every $N$ entries and combine them to form a subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
 	\end{subsection}
@@
 		\begin{equation}	\label{eq:y_{m,k}(t)}
-			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}}\right\}
+			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}\right\}
 		\end{equation}
 		Therefore, the RF input signal to the antenna of user $k$ writes as
-		% \begin{equation}
-
-		% \end{equation}
+		\begin{equation}	\label{eq:y_k(t)}
+			\begin{split}
+				y_k(t)
+				&=\Re\left\{\sum_{m=1}^M{y_{m,k}(t)}\right\}	\\
+				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
+				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
+			\end{split}
+		\end{equation}
 		% \begin{equation}	\label{eq:y_{m,k}(t)}
@@
 	\end{subsection}
+
+	\begin{subsection}	{Information Decoder}
+		In the
+	\end{subsection}
 \end{section}

### 2020-04-06 system-model.tex
:pencil: Fix subchannels

@@
 Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
+We also define the channel between antenna $m$ and all IRS elements as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,U,n,m}]^T$, as represented by the columns of $\boldsymbol{H}_{I,n}$.
 Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
@@
 		\end{equation}
-		On top of this, we select the $n$-th of every $N$ entries and combine them to form a subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
+		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
+		\begin{equation}	\label{eq:h_{k,n}}
+			\begin{split}
+				\boldsymbol{h}_{k,n}
+				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}	\\
+				&=[h_{k,n,1},\dots,h_{k,n,M}]
+			\end{split}
+		\end{equation}
+		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{h}_{I,n,m}$.
 	\end{subsection}
@@
 	\begin{subsection}	{Information Decoder}
-		In the
+		One major benefit of using proposed waveform is that as a translation, the deterministic power term $\boldsymbol{x}_P(t)$ bears no information and creates no interference to the modulated information term $\boldsymbol{x}_I(t)$.
+Therefore, the achievable rate of user $k$ is expressed as
+		\begin{equation}	\label{eq:I_k}
+			\begin{split}
+				I_k(\boldsymbol{w}_I,\boldsymbol{R},\rho)
+				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
+				&=?
+			\end{split}
+		\end{equation}
+
 	\end{subsection}
+
 \end{section}

### 2020-04-06 system-model.tex
:pencil2: Energy harvester

--- 2020-04-05 system-model.tex
@@
 Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e.
-$x_{P,n,m}(t) = w_{P,n,m}$) in the baseband.
+$x_{P,n,m}(t) = w_{P,n,m}$) in the baseband (BB).
 The transmit power waveform on the antenna $m$ at time $t$ is given by
@@
 At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$.
-Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
-Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
+Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
+We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,U,n,m}]^T$ to represent the channel between antenna $m$ and IRS.
+Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
 Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching.
-Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$.
-With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$.
+Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_U e^{j \theta_U}) \in \mathbb{C}^{U \times U}$.
+With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{UN \times U}$.
 The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel.
@@
 		\begin{equation}	\label{eq:h_k}
-			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
+			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{\Theta} \boldsymbol{\boldsymbol{H}_I} \right)
 		\end{equation}
-		On top of this, we select the $n$-th of every $N$ entries and combine them to form a subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
+		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
+		\begin{equation}	\label{eq:h_{k,n}}
+			\begin{split}
+				\boldsymbol{h}_{k,n}
+				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{H}_{I,n}	\\
+				&=[h_{k,n,1},\dots,h_{k,n,M}]
+			\end{split}
+		\end{equation}
+		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n,m}$.
 	\end{subsection}
@@
 				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
-				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
+				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
+				&=y_{I,k}(t)+y_{P,k}(t)
 			\end{split}
@@
 	\begin{subsection}	{Information Decoder}
-		In the
+		One major benefit of using proposed waveform is that as a translation, the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
+Therefore, the achievable rate of user $k$ is expressed as
+		\begin{equation}	\label{eq:I_k}
+			\begin{split}
+				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
+				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
+				&=?
+			\end{split}
+		\end{equation}
+		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$.
+A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
+	\end{subsection}
+
+	\begin{subsection}	{Energy Harvester}
+		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner.
+Consider the nonlinear diode model based on the Taylor expansion of small signal model that highlights the dependency between the harvester output DC current and the received waveform \cite{Clerckx2018b,Clerckx2016a}
+		\begin{equation}	\label{eq:i_k}
+			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}
+		\end{equation}
+		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
+With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
+\cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic function truncated to the $n_0$ order
+		\begin{equation}	\label{eq:z_{DC,k}}
+			\begin{split}
+				z_{DC,k}
+				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}	\\
+				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_P(t)^i\right\}}	\\
+				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_I(t)^i\right\}\right\}}
+			\end{split}
+		\end{equation}
+		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+
 	\end{subsection}

### 2020-04-06 system-model.tex
:pencil2: Change notation

@@
 	Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
-The $M$-antenna transmitter delivers information and power simultaneously, through the $U$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
+The $M$-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
 It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
@@
 Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}.
-In contrast, passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}.
-Therefore, we assume a frequency-flat IRS with same reflection coefficients for all subbands.
+Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with same reflection coefficients for all subbands.
 Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
@@
 In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1 - \rho)$ and $\rho$.
-Note that $\rho$ is coupled with waveform and IRS design.
-Therefore, the rate-energy region is disclosed by placing different rate constraints and optimizing waveform, PS ratio and reflectors accordingly.
-Perfect synchronization is assumed among the three parties in both operations.
+As $\rho$ is coupled with waveform and IRS design, we investigate the rate-energy region by placing different rate constraints and optimizing waveform, PS ratio and reflectors accordingly.
+Perfect synchronization is assumed among the three parties in both scenario.
 
@@
 			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy.
-It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant on subband $n$ (i.e.
+It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant (i.e.
 $\tilde{x}_{P,n} = 1$).
-Therefore, on the $n$-th subcarrier of the $m$-th transmit antenna, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e.
+Therefore,, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e.
 $x_{P,n,m}(t) = w_{P,n,m}$) in the baseband (BB).
@@
 			\end{equation}
-			The corresponding power waveform vector is stacked across $M$ transmit antennas as
+			Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
 			\begin{equation}	\label{eq:x_P(t)}
@@
 			\end{equation}
-			The transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
+			Hence, the transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
 			\begin{equation}	\label{eq:x_m(t)}
@@
 			\end{equation}
-			Hence, the composite transmit signal vector is
+			Therefore, the composite transmit signal vector is
 			\begin{equation}	\label{x(t)}
@@
 Similarly, the AP-IRS (i.e.
-incident) channel between antenna $m$ and element $u$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
-reflective) channel between element $u$ and user $k$ is $h_{R,n,u,k}=A_{R,n,u,k}e^{j\bar{\psi}_{R,n,u,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,u,k} \right)}$.
+incident) channel between antenna $m$ and element $l$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
+reflective) channel between element $l$ and user $k$ is $h_{R,n,l,k}=A_{R,n,l,k}e^{j\bar{\psi}_{R,n,l,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,l,k} \right)}$.
 Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.;
 
-		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively.
-At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$.
-Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$.
-We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,U,n,m}]^T$ to represent the channel between antenna $m$ and IRS.
-Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
-Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching.
-Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_U e^{j \theta_U}) \in \mathbb{C}^{U \times U}$.
-With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{UN \times U}$.
+		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times LN}$ respectively.
+At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $L$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times L}$.
+Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $L$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,L,n}^T]^T \in \mathbb{C}^{L \times M}$, with $\boldsymbol{h}_{I,l,n}=[h_{I,l,n,1},\dots,h_{I,l,n,M}] \in \mathbb{C}^{1 \times M}$.
+We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,L,n,m}]^T \in \mathbb{C}^{L \times 1}$ to represent the channel between antenna $m$ and the IRS.
+Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_l e^{j \theta_l}$, where $\beta_l \in [0,1]$ and $\theta_l \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
+Each passive reflector harvests a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
+Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
+With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{LN \times L}$.
 The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel.
@@
 				y_k(t)
+				&=y_{I,k}(t)+y_{P,k}(t)	\\
 				&=\Re\left\{\sum_{m=1}^M{y_{m,k}(t)}\right\}	\\
 				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
-				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
-				&=y_{I,k}(t)+y_{P,k}(t)
+				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
 			\end{split}
@@
 		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,u,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\}	\\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,l,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\}	\\
 		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,u,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,l,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
 		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}	\\
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,l,k}}{\beta_l}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,l,k}+\theta_l+\bar{\psi}_{I,n,m,u} \right)} \right\}	\\
 		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,u,k}}{\beta_u}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,u,k}+\theta_u+\bar{\psi}_{I,n,m,u} \right)} \right\}
+		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,l,k}}{\beta_l}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,l,k}+\theta_l+\bar{\psi}_{I,n,m,u} \right)} \right\}
 		% 	\end{split}
@@
 	\begin{subsection}	{Information Decoder}
-		One major benefit of using proposed waveform is that as a translation, the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
+		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
 Therefore, the achievable rate of user $k$ is expressed as
@@
 		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner.
-Consider the nonlinear diode model based on the Taylor expansion of small signal model that highlights the dependency between the harvester output DC current and the received waveform \cite{Clerckx2018b,Clerckx2016a}
+Consider the nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
 		\begin{equation}	\label{eq:i_k}
-			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}
+			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
 		\end{equation}
@@
 With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
-\cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic function truncated to the $n_0$ order
+\cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
 		\begin{equation}	\label{eq:z_{DC,k}}
@@
 				z_{DC,k}
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y(t)^i\right\}}	\\
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_P(t)^i\right\}}	\\
-				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_I(t)^i\right\}\right\}}
+				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}	\\
+				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_{P,k}(t)^i\right\}}	\\
+				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)^i\right\}\right\}}
 			\end{split}

### 2020-04-07 system-model.tex
:pencil: SISO

@@
 \begin{section} {System Model}
-	Consider an IRS-aided multiuser MISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
-The $M$-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
+	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
+The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
 It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
@@
 $\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$).
-Denote $w_{I,n,m} = s_{I,n,m} e^{j\phi_{I,n,m}}$ as the information weight on the $n$-th subcarrier of the $m$-th ($m = 1,\dots,M$) transmit antenna with magnitude $s_{I,n,m}$ and phase $\phi_{I,n,m}$, the corresponding modulated symbol can be expressed as $x_{I,n,m} = \tilde{s}_{I,n,m} e^{j\tilde{\phi}_{I,n,m}}$, with $\tilde{s}_{I,n,m} = s_{I,n,m} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n,m} = \phi_{I,n,m} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e.
-$x_{I,n,m} \sim \mathcal{CN}(0,s_{I,n,m}^2)$).
-Therefore, the transmit information waveform on the antenna $m$ at time $t$ writes as
-			\begin{equation}	\label{eq:x_{I,m}(t)}
+Denote $w_{I,n} = s_{I,n} e^{j\phi_{I,n}}$ as the information weight on the $n$-th subcarrier with magnitude $s_{I,n}$ and phase $\phi_{I,n}$, the corresponding modulated symbol can be expressed as $x_{I,n} = \tilde{s}_{I,n} e^{j\tilde{\phi}_{I,n}}$, with $\tilde{s}_{I,n} = s_{I,n} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n} = \phi_{I,n} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e.
+$x_{I,n} \sim \mathcal{CN}(0,s_{I,n}^2)$).
+Therefore, the transmit information waveform at time $t$ writes as
+			\begin{equation}	\label{eq:x_{I}(t)}
 				\begin{split}
-					x_{I,m}(t)
-					&= \sum_{n=1}^{N} \tilde{s}_{I,n,m}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n,m}(t) \right)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} x_{I,n,m}(t) e^{j2 \pi f_n t} \right\}	\\
-					&= \Re \left\{ \sum_{n=1}^{N} w_{I,n,m} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
+					x_{I}(t)
+					&= \sum_{n=1}^{N} \tilde{s}_{I,n}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n}(t) \right)	\\
+					&= \Re \left\{ \sum_{n=1}^{N} x_{I,n}(t) e^{j2 \pi f_n t} \right\}	\\
+					&= \Re \left\{ \sum_{n=1}^{N} w_{I,n} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
 				\end{split}
 			\end{equation}
-			On top of this, the information waveform vector is spread over $M$ antennas
-			\begin{equation}	\label{eq:x_I(t)}
-				\boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
-			\end{equation}
-			where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
+			% On top of this, the information waveform vector is spread over $M$ antennas
+			% \begin{equation}	\label{eq:x_I(t)}
+			% 	\boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
+			% \end{equation}
+			% where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
@@
 $\tilde{x}_{P,n} = 1$).
-Therefore,, the power weight $w_{P,n,m} = s_{P,n,m} e^{j\phi_{P,n,m}}$ represents the complex-valued sinewave (i.e.
-$x_{P,n,m}(t) = w_{P,n,m}$) in the baseband (BB).
-The transmit power waveform on the antenna $m$ at time $t$ is given by
-			\begin{equation}	\label{eq:x{P,m}(t)}
+Therefore, the power weight $w_{P,n} = s_{P,n} e^{j\phi_{P,n}}$ represents the complex-valued sinewave (i.e.
+$x_{P,n}(t) = w_{P,n}$) in the baseband (BB).
+The transmit power waveform at time $t$ is given by
+			\begin{equation}	\label{eq:x{P}(t)}
 				\begin{split}
-					x_{P,m}(t)
-					&= \sum_{n=1}^{N} s_{P,n,m}(t) \cos \left( 2 \pi f_n t + \phi_{P,n,m}(t) \right)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n,m}(t) e^{j2 \pi f_n t} \right\}	\\
-					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n,m} e^{j2 \pi f_n t} \right\}
+					x_{P}(t)
+					&= \sum_{n=1}^{N} s_{P,n}(t) \cos \left( 2 \pi f_n t + \phi_{P,n}(t) \right)	\\
+					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n}(t) e^{j2 \pi f_n t} \right\}	\\
+					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n} e^{j2 \pi f_n t} \right\}
 				\end{split}
 			\end{equation}
-			Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
-			\begin{equation}	\label{eq:x_P(t)}
-				\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
-			\end{equation}
-			where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
+			% Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
+			% \begin{equation}	\label{eq:x_P(t)}
+			% 	\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
+			% \end{equation}
+			% where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
@@
 		\begin{subsubsection} {Superposed Waveform}
-			At time $t$, a superposition of the information and power waveform on antenna $m$ over subband $n$ writes as
-			\begin{equation}	\label{eq:x_{n,m}(t)}
+			At time $t$, a superposition of the information and power waveform at subband $n$ writes as
+			\begin{equation}	\label{eq:x_{n}(t)}
 				\begin{split}
-					x_{n,m}(t)
-					&= x_{I,n,m}(t)+x_{P,n,m}(t)	\\
-					&= w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}
+					x_{n}(t)
+					&= x_{I,n}(t)+x_{P,n}(t)	\\
+					&= w_{I,n} \tilde{x}_{I,n}(t)+w_{P,n}
 				\end{split}
 			\end{equation}
-			Hence, the transmitted signal on antenna $m$ at time $t$ is a summation over all subbands
-			\begin{equation}	\label{eq:x_m(t)}
+			Hence, the transmitted signal is summed over all subbands
+			\begin{equation}	\label{eq:x(t)}
 				\begin{split}
-					x_m(t)
-					&= x_{I,m}(t)+x_{P,m}(t)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} (w_{I,n,m} \tilde{x}_{I,n}(t)+w_{P,n,m}) e^{j2 \pi f_n t} \right\}
+					x(t)
+					&= x_{I}(t)+x_{P}(t)	\\
+					&= \Re \left\{ \sum_{n=1}^{N} (w_{I,n} \tilde{x}_{I,n}(t)+w_{P,n}) e^{j2 \pi f_n t} \right\}
 				\end{split}
 			\end{equation}
-			Therefore, the composite transmit signal vector is
-			\begin{equation}	\label{x(t)}
-				\begin{split}
-					\boldsymbol{x}(t)
-					&=\boldsymbol{x}_I(t)+\boldsymbol{x}_P(t)	\\
-					&=\Re \left\{ \sum_{n=1}^{N} (\boldsymbol{w}_{I,n}\tilde{x}_n(t)+\boldsymbol{w}_{P,n}) e^{j2{\pi}{f_n}t} \right\}
-				\end{split}
-			\end{equation}
+			% Therefore, the composite transmit signal vector is
+			% \begin{equation}	\label{x(t)}
+			% 	\begin{split}
+			% 		\boldsymbol{x}(t)
+			% 		&=\boldsymbol{x}_I(t)+\boldsymbol{x}_P(t)	\\
+			% 		&=\Re \left\{ \sum_{n=1}^{N} (\boldsymbol{w}_{I,n}\tilde{x}_n(t)+\boldsymbol{w}_{P,n}) e^{j2{\pi}{f_n}t} \right\}
+			% 	\end{split}
+			% \end{equation}
 		\end{subsubsection}
@@
 		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times LN}$ respectively.
-At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $L$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times L}$.
+At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $L$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,L}] \in \mathbb{C}^{1 \times L}$.
 Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $L$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,L,n}^T]^T \in \mathbb{C}^{L \times M}$, with $\boldsymbol{h}_{I,l,n}=[h_{I,l,n,1},\dots,h_{I,l,n,M}] \in \mathbb{C}^{1 \times M}$.
@@
 	\begin{subsection}	{Received Signal}
-		In the signal received by user $k$, the component from transmit antenna $m$ captures the contribution of information and power waveforms through both direct and reflective links as
-		\begin{equation}	\label{eq:y_{m,k}(t)}
-			y_{m,k}(t)=\Re\left\{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}\right\}
-		\end{equation}
-		Therefore, the RF input signal to the antenna of user $k$ writes as
-		\begin{equation}	\label{eq:y_k(t)}
+		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
+		\begin{equation}	\label{eq:y_{k}(t)}
 			\begin{split}
-				y_k(t)
-				&=y_{I,k}(t)+y_{P,k}(t)	\\
-				&=\Re\left\{\sum_{m=1}^M{y_{m,k}(t)}\right\}	\\
+				y_{k}(t)
+				&=\sum_{m=1}^M{y_{k,m}(t)}	\\
 				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
-				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
+				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
+				&=y_{I,k}(t)+y_{P,k}(t)
 			\end{split}
 		\end{equation}
-		% \begin{equation}	\label{eq:y_{m,k}(t)}
-		% 	\begin{split}
-		% 		y_{m,k}(t)
-		% 		&= \Re \left\{ \sum_{n=1}^{N} \sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} x_{n,m}(t-\tau_{l_{D,k}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{D,k}})+\varsigma_{l_{D,k},n,m,k}\right) } \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{l_{R,k}=1}^{L_{R,k}} \sum_{u=1}^{U} \alpha_{l_{R,k}} r_u \alpha_{l_{I,u}} x_{n,m}(t-\tau_{l_{R,k}}-\tau_{l_{I,u}}) e^{j \left( -2 \pi f_n (t-\tau_{l_{R,k}}-\tau_{l_{I,u}})+\varsigma_{l_{R,k},n,l,k}+\varsigma_{l_{I,u},n,m,u}\right)} \right\}	\\
-		% 		&\approx \Re \left\{ \sum_{n=1}^{N} h_{D,n,m,k}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} h_{R,n,l,k}(t) r_u h_{I,n,m,u}(t) x_{n,m}(t) e^{j2 \pi f_n t} \right\}	\\
-		% 		&= \Re \left\{ \sum_{n=1}^{N} {s_{P,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {s_{P,n,m}}{A_{R,n,l,k}}{\beta_l}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\phi_{P,n,m}+\bar{\psi}_{R,n,l,k}+\theta_l+\bar{\psi}_{I,n,m,u} \right)} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} {\tilde{s}_{I,n,m}}{A_{D,n,m,k}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{D,n,m,k} \right)} \right\}	\\
-		% 		&\quad+ \Re \left\{ \sum_{n=1}^{N} \sum_{u=1}^{U} {\tilde{s}_{I,n,m}}{A_{R,n,l,k}}{\beta_l}{A_{I,n,m,u}} e^{j\left( 2{\pi}{f_n}{t}+\tilde{\phi}_{I,n,m}+\bar{\psi}_{R,n,l,k}+\theta_l+\bar{\psi}_{I,n,m,u} \right)} \right\}
-		% 	\end{split}
-		% \end{equation}
-		% Therefore, the RF signal input to the antenna at user $k$ is
-		% \begin{equation}	\label{eq:y_{k}(t)}
-		% 	y_{k}(t) = \sum_{m=1}^{M} y_{m,k}(t)
-		% \end{equation}
 	\end{subsection}

### 2020-04-08 system-model.tex
:pencil: Construct frequency-selective IRS

@@
 
-		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times LN}$ respectively.
-At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $L$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,L}] \in \mathbb{C}^{1 \times L}$.
-Similarly, the $n$-th incident channel matrix from $M$ transmit antennas to $L$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,L,n}^T]^T \in \mathbb{C}^{L \times M}$, with $\boldsymbol{h}_{I,l,n}=[h_{I,l,n,1},\dots,h_{I,l,n,M}] \in \mathbb{C}^{1 \times M}$.
-We also define the columns of $\boldsymbol{H}_{I,n}$ as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,L,n,m}]^T \in \mathbb{C}^{L \times 1}$ to represent the channel between antenna $m$ and the IRS.
-Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $\beta_l e^{j \theta_l}$, where $\beta_l \in [0,1]$ and $\theta_l \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively.
-Each passive reflector harvests a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{LN \times L}$.
-The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel.
-Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
-		\begin{equation}	\label{eq:h_k}
-			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{\Theta} \boldsymbol{\boldsymbol{H}_I} \right)
+		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
+At subband $n$, the frequency response of direct and reflective links are $\boldsymbol{h}_{D,n}=[h_{D,n,1},\dots,h_{D,n,K}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{h}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$, with $\boldsymbol{h}_{R,n,l}=[h_{R,n,l,1},\dots,h_{R,n,l,k}]^T \in \mathbb{C}^{K \times 1}$.
+'Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
+Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
+Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
+Construct a diagonal subband-wise IRS matrix by collecting all reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
+With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$.
+The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel.
+Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
+		\begin{equation}	\label{eq:H}
+			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
 		\end{equation}
-		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
-		\begin{equation}	\label{eq:h_{k,n}}
-			\begin{split}
-				\boldsymbol{h}_{k,n}
-				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{H}_{I,n}	\\
-				&=[h_{k,n,1},\dots,h_{k,n,M}]
-			\end{split}
+		Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
+		\begin{equation}	\label{eq:h_n}
+			\boldsymbol{h}_n=\boldsymbol{h}_D+\boldsymbol{H}_{R}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
 		\end{equation}
-		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n,m}$.
+		It is interesting to notice that the reflective channel across all $N$ subbands influences the overall frequency response at subband $n$.
 	\end{subsection}

### 2020-04-08 system-model.tex
:pencil: Fix frequency-selective IRS

@@
 		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
-At subband $n$, the frequency response of direct and reflective links are $\boldsymbol{h}_{D,n}=[h_{D,n,1},\dots,h_{D,n,K}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{h}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$, with $\boldsymbol{h}_{R,n,l}=[h_{R,n,l,1},\dots,h_{R,n,l,k}]^T \in \mathbb{C}^{K \times 1}$.
-'Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
+Specifically, the frequency response of direct and reflective links at subband $n$ are $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$.
+Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
+We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
+Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.
 		Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
 Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-Construct a diagonal subband-wise IRS matrix by collecting all reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$.
+We construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
+With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands as $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$.
 The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel.
@@
 		\end{equation}
-		Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
+		whose $(k,n)$-th entry
+		\begin{equation}	\label{eq:h_{k,n}}
+			h_{k,n}=h_{D,n,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
+		\end{equation}
+		represents the overall channel gain of user $k$ at subband $n$. Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
 		\begin{equation}	\label{eq:h_n}
-			\boldsymbol{h}_n=\boldsymbol{h}_D+\boldsymbol{H}_{R}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R}\boldsymbol{\Theta}\boldsymbol{h}_{I,n}
 		\end{equation}
-		It is interesting to notice that the reflective channel across all $N$ subbands influences the overall frequency response at subband $n$.
+		It is interesting to notice that the total frequency response at subband $n$ depends on the reflective channel across all $N$ subbands such that the frequency selectivity only comes from the direct and incident links.
+From another perspective, the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times N}$ for user $k$ writes as
+		\begin{equation}	\label{eq:h_k}
+			\boldsymbol{h}_k=\boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k}\boldsymbol{\Theta}\boldsymbol{H}_I
+		\end{equation}
+		Therefore, we have $\boldsymbol{H}=[\boldsymbol{h}_1,\dots,\boldsymbol{h}_N]=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_K^T]^T$.
 	\end{subsection}
@@
 				y_{k}(t)
-				&=\sum_{m=1}^M{y_{k,m}(t)}	\\
-				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
-				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
-				&=y_{I,k}(t)+y_{P,k}(t)
+				&=y_{I,k}(t)+y_{P,k}(t)	\\
+				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
+				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
 			\end{split}

### 2020-04-09 system-model.tex
:pencil: Energy harvester

@@
 $x_{I,n} \sim \mathcal{CN}(0,s_{I,n}^2)$).
+Collect $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$.
 Therefore, the transmit information waveform at time $t$ writes as
@@
 $x_{P,n}(t) = w_{P,n}$) in the baseband (BB).
+Collect $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$.
 The transmit power waveform at time $t$ is given by
@@
 		\end{equation}
-		It is interesting to notice that the total frequency response at subband $n$ depends on the reflective channel across all $N$ subbands such that the frequency selectivity only comes from the direct and incident links.
+		It is interesting to notice that the frequency response at subband $n$ depends on the reflective channel across all $N$ subbands such that the frequency selectivity only comes from the direct and incident links.
 From another perspective, the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times N}$ for user $k$ writes as
@@
 		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
-		\begin{equation}	\label{eq:y_{k}(t)}
+		\begin{equation}	\label{eq:y_k(t)}
 			\begin{split}
-				y_{k}(t)
+				y_k(t)
 				&=y_{I,k}(t)+y_{P,k}(t)	\\
@@
 		\end{equation}
+
+		% \begin{equation}	\label{eq:y_k**2(t)}
+		% 	\begin{split}
+		% 		\mathcal{A}\left\{y_{P,k}^2(t)=\frac{1}{2}\right\}
+		% 		&=\Re\left\{\sum_{n_1,n_2}\right\}
+		% 	\end{split}
+		% \end{equation}
 	\end{subsection}
@@
 				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
-				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
-				&=?
+				% &=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
+				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}{\sigma_n^2}\right)}
 			\end{split}
@@
 	\begin{subsection}	{Energy Harvester}
-		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner.
-Consider the nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
+		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners.
+Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
 		\begin{equation}	\label{eq:i_k}
-			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
 		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
-With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
+Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$.
+Therefore, we first extract the DC component based on $h_{k,n}$, $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ by $\mathcal{A}\left\{.\right\}$ and then consider the expectation over $\tilde{x}_n$ by $\mathcal{E}\left\{.\right\}$.
+With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components.
 \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
-		\begin{equation}	\label{eq:z_{DC,k}}
+		\begin{equation}	\label{eq:z_k}
+			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+		\end{equation}
+		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy delivery.
+Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}	\\
+		\begin{strip}
+			\begin{equation}	\label{eq:z_k_truncated}
 				\begin{split}
-				z_{DC,k}
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}	\\
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_{P,k}(t)^i\right\}}	\\
-				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)^i\right\}\right\}}
+					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
+					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}	\\
+					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}	\\
+					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
 				\end{split}
 			\end{equation}
-		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+		\end{strip}
+		whose terms are expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4}}	\\
+		\begin{strip}
+			\begin{align}
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\} & =\frac{1}{2}\sum_n{(w_{I,n}h_{k,n})(w_{I,n}h_{k,n})^*}	\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                  \\
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\} & =\frac{3}{4}\sum_{{n_1},{n_2}}{(w_{I,{n_1}}h_{k,{n_1}})(w_{I,{n_2}}h_{k,{n_2}})(w_{I,{n_1}}h_{k,{n_1}})^*(w_{I,{n_2}}h_{k,{n_2}})^*}	\label{eq:E{A{y_{I,k}**4}}}                                                                    \\
+				\mathcal{A}\left\{y_{P,k}^2(t)\right\}                           & =\frac{1}{2}\sum_n{(w_{P,n}h_{k,n})(w_{P,n}h_{k,n})^*}	\label{eq:A{y_{P,k}**2}}                                                                                                                                                     \\
+				\mathcal{A}\left\{y_{P,k}^4(t)\right\}                           & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{n_1}}h_{k,{n_1}})(w_{P,{n_2}}h_{k,{n_2}})(w_{P,{n_3}}h_{k,{n_3}})^*(w_{P,{n_4}}h_{k,{n_4}})^*}	\label{eq:A{y_{P,k}**4}}
+			\end{align}
+		\end{strip}
+		Note that $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^4\right\}=2$.
+The latter provides a modulation gain to the nonlinear terms in the output DC current.
 

### 2020-04-10 system-model.tex
:pencil: Fix composite channel model

--- 2020-04-08 system-model.tex
@@
 
-		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
-At subband $n$, the frequency response of direct and reflective links are $\boldsymbol{h}_{D,n}=[h_{D,n,1},\dots,h_{D,n,K}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{h}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$, with $\boldsymbol{h}_{R,n,l}=[h_{R,n,l,1},\dots,h_{R,n,l,k}]^T \in \mathbb{C}^{K \times 1}$.
-'Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
-Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
+		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
+At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
+Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
+To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$.
+Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
 Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-Construct a diagonal subband-wise IRS matrix by collecting all reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$.
+On top of this, the IRS matrix of each subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
+Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$.
 The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel.
-Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
+Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
+
+		% We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
+Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.
+
+		% [\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$.
+		% , which is further divided into horizontal submatrices $\boldsymbol{\Theta}_n \in \mathbb{C}^{NL \times L}$ such that $\boldsymbol{\Theta}=[\boldsymbol{\Theta}_1,\dots,\boldsymbol{\Theta}_N]$.
+		% , which is then divided into $N$ vertical submatrices $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times N}$ such that $\boldsymbol{H}_{I}=[\boldsymbol{H}_{I,1}^T,\dots,\boldsymbol{H}_{I,N}^T]^T$.
+		% whose $n$-th column denotes the zero-padded incident subchannel $\boldsymbol{h}_{I,n}=[\boldsymbol{0}_{1 \times (n-1)L}^T, \boldsymbol{h}_{I,n}'^T,\boldsymbol{0}_{1 \times (N-n)L}^T]^T \in \mathbb{C}^{NL \times 1}$.
+
 		\begin{equation}	\label{eq:H}
@@
 		\end{equation}
-		Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
+		whose $(k,n)$-th entry
+		\begin{equation}	\label{eq:h_{k,n}}
+			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+		\end{equation}
+		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
 		\begin{equation}	\label{eq:h_n}
-			\boldsymbol{h}_n=\boldsymbol{h}_D+\boldsymbol{H}_{R}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
 		\end{equation}
-		It is interesting to notice that the reflective channel across all $N$ subbands influences the overall frequency response at subband $n$.
 	\end{subsection}
@@
 		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
-		\begin{equation}	\label{eq:y_{k}(t)}
+		\begin{equation}	\label{eq:y_k(t)}
 			\begin{split}
-				y_{k}(t)
-				&=\sum_{m=1}^M{y_{k,m}(t)}	\\
-				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
-				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
-				&=y_{I,k}(t)+y_{P,k}(t)
+				y_k(t)
+				&=y_{I,k}(t)+y_{P,k}(t)	\\
+				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
+				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
 			\end{split}
 		\end{equation}
+
+		% \begin{equation}	\label{eq:y_k**2(t)}
+		% 	\begin{split}
+		% 		\mathcal{A}\left\{y_{P,k}^2(t)=\frac{1}{2}\right\}
+		% 		&=\Re\left\{\sum_{n_1,n_2}\right\}
+		% 	\end{split}
+		% \end{equation}
 	\end{subsection}
@@
 	\begin{subsection}	{Energy Harvester}
-		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner.
-Consider the nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
+		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners.
+Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
 		\begin{equation}	\label{eq:i_k}
-			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
 		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
-With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
+Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$.
+Therefore, we first extract the DC component based on $h_{k,n}$, $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ by $\mathcal{A}\left\{.\right\}$ and then consider the expectation over $\tilde{x}_n$ by $\mathcal{E}\left\{.\right\}$.
+With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components.
 \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
-		\begin{equation}	\label{eq:z_{DC,k}}
+		\begin{equation}	\label{eq:z_k}
+			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+		\end{equation}
+		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy delivery.
+Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}, whose terms are further expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
+		\begin{figure*}[b]
+			\hrule
+			\begin{equation}	\label{eq:z_k_truncated}
 				\begin{split}
-				z_{DC,k}
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}	\\
-				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_{P,k}(t)^i\right\}}	\\
-				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)^i\right\}\right\}}
+					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
+					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}	\\
+					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}	\\
+					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
 				\end{split}
 			\end{equation}
-		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+		\end{figure*}
+		\begin{figure*}[b]
+			\hrule
+
+			\begin{align}
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
+				 & =\frac{1}{2}\sum_n{(w_{I,n}h_{k,n})(w_{I,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                                                                                               \\
+				 & =\frac{1}{2}\sum_n{\left[w_{I,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
+				 & =\frac{3}{4}\sum_{{n_1},{n_2}}{(w_{I,{n_1}}h_{k,{n_1}})(w_{I,{n_2}}h_{k,{n_2}})(w_{I,{n_1}}h_{k,{n_1}})^*(w_{I,{n_2}}h_{k,{n_2}})^*}                                                                                                                                                                                            \\
+				 & =\frac{3}{4}\sum_{{n_1},{n_2}}\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber                                                                       \\
+				 & \quad\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]^*\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]^*                                                                                                     \\
+				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
+				 & =\frac{1}{2}\sum_n{(w_{P,n}h_{k,n})(w_{P,n}h_{k,n})^*}                                                                                                                                                                                                                                                                          \\
+				 & =\frac{1}{2}\sum_n{\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
+				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
+				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{n_1}}h_{k,{n_1}})(w_{P,{n_2}}h_{k,{n_2}})(w_{P,{n_3}}h_{k,{n_3}})^*(w_{P,{n_4}}h_{k,{n_4}})^*}                                                                                                                      \\
+				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
+				 & \quad\left[w_{P,{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
+			\end{align}
+		\end{figure*}
+		Note that $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^4\right\}=2$.
+The latter provides a modulation gain to the nonlinear terms in the output DC current.
 

### 2020-04-11 system-model.tex
:pencil: Fix user rate

@@
 
-\begin{section} {System Model}
+\begin{section}{System Model}
 	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
@@
 Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
-In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots with duration ratio $(1 - \alpha)$ and $\alpha$ respectively.
+In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots with duration ratio $(1-\alpha)$ and $\alpha$ respectively.
 Hence, the achievable rate-energy region can be obtained through a direct time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$.
 The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design, since they are optimized individually in data and energy slots.
-In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1 - \rho)$ and $\rho$.
+In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$.
 As $\rho$ is coupled with waveform and IRS design, we investigate the rate-energy region by placing different rate constraints and optimizing waveform, PS ratio and reflectors accordingly.
@@
 
-	\begin{subsection}	{Transmitted Signal}
-
+	\begin{subsection}{Transmitted Signal}
 		\begin{subsubsection} {Modulated Information Waveform}
-			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n = f_0+(n-1) \Delta f$ ($n = 1,\dots,N$).
-The information symbol $\tilde{x}_{I,n}$ on subband $n$ is a capacity-achieving i.i.d.
-Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance (i.e.
-$\tilde{x}_{I,n} \sim \mathcal{CN}(0,1)$).
-Denote $w_{I,n} = s_{I,n} e^{j\phi_{I,n}}$ as the information weight on the $n$-th subcarrier with magnitude $s_{I,n}$ and phase $\phi_{I,n}$, the corresponding modulated symbol can be expressed as $x_{I,n} = \tilde{s}_{I,n} e^{j\tilde{\phi}_{I,n}}$, with $\tilde{s}_{I,n} = s_{I,n} \lvert\tilde{x}_{I,n}\rvert$ and $\tilde{\phi}_{I,n} = \phi_{I,n} + \angle{\tilde{x}_n}$, which also follows zero-mean CSCG distribution with variance equal to the subcarrier power (i.e.
-$x_{I,n} \sim \mathcal{CN}(0,s_{I,n}^2)$).
-Collect $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$.
-Therefore, the transmit information waveform at time $t$ writes as
-			\begin{equation}	\label{eq:x_{I}(t)}
+			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n=f_0+(n-1){\Delta}{f}$ ($n=1,\dots,N$).
+The information symbol $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$ of user $k$ over subband $n$ is a capacity-achieving i.i.d.
+Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance.
+Therefore, the baseband (BB) transmit information signal at subband $n$ can be expressed as
+			\begin{equation}\label{eq:x_{I,n}(t)}
+				x_{I,n}(t)=\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}
+			\end{equation}
+			where $w_{I,k,n}$ is the corresponding information weight.
+Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+On top of this, the RF transmit information waveform at time $t$ writes as
+			\begin{equation}\label{eq:x_I(t)}
 				\begin{split}
-					x_{I}(t)
-					&= \sum_{n=1}^{N} \tilde{s}_{I,n}(t) \cos \left( 2 \pi f_n t + \tilde{\phi}_{I,n}(t) \right)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} x_{I,n}(t) e^{j2 \pi f_n t} \right\}	\\
-					&= \Re \left\{ \sum_{n=1}^{N} w_{I,n} \tilde{x}_{I,n}(t) e^{j2 \pi f_n t} \right\}
+					x_I(t)
+					&=\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\\
+					&=\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}
+					% &=\Re\left\{\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}\\
+					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}
 				\end{split}
 			\end{equation}
-			% On top of this, the information waveform vector is spread over $M$ antennas
-			% \begin{equation}	\label{eq:x_I(t)}
-			% 	\boldsymbol{x}_I(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{I,n}\tilde{x}_n(t) e^{j2{\pi}{f_n}t} \right\}
-			% \end{equation}
-			% where $\boldsymbol{w}_{I,n}=[w_{I,n,1},\dots,w_{I,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
 
-		\begin{subsubsection} {Unmodulated Power Waveform}
+		\begin{subsubsection}{Unmodulated Power Waveform}
 			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy.
-It has no randomness over time and the equivalent input power symbol $\tilde{x}_{P,n}$ is a constant (i.e.
-$\tilde{x}_{P,n} = 1$).
-Therefore, the power weight $w_{P,n} = s_{P,n} e^{j\phi_{P,n}}$ represents the complex-valued sinewave (i.e.
-$x_{P,n}(t) = w_{P,n}$) in the baseband (BB).
-Collect $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$.
-The transmit power waveform at time $t$ is given by
-			\begin{equation}	\label{eq:x{P}(t)}
+It has no randomness over time such that the baseband transmit power signal at subband $n$ is
+			\begin{equation}\label{eq:x_{P,n}}
+				x_{P,n}=\sum_{k=1}^K{w_{P,k,n}}
+			\end{equation}
+			where $w_{P,k,n}$ is the corresponding power weight.
+Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+Then, the transmit power signal at time $t$ is given by
+			\begin{equation}\label{eq:x_P(t)}
 				\begin{split}
-					x_{P}(t)
-					&= \sum_{n=1}^{N} s_{P,n}(t) \cos \left( 2 \pi f_n t + \phi_{P,n}(t) \right)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} x_{P,n}(t) e^{j2 \pi f_n t} \right\}	\\
-					&= \Re \left\{ \sum_{n=1}^{N} w_{P,n} e^{j2 \pi f_n t} \right\}
+					x_P(t)
+					&=\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\\
+					&=\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}
+					% &=\Re\left\{\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\right\}\\
+					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}\right\}
 				\end{split}
 			\end{equation}
-			% Similarly, the corresponding power waveform vector is stacked across $M$ transmit antennas as
-			% \begin{equation}	\label{eq:x_P(t)}
-			% 	\boldsymbol{x}_P(t) = \Re \left\{ \sum_{n=1}^{N} \boldsymbol{w}_{P,n} e^{j2{\pi}{f_n}t} \right\}
-			% \end{equation}
-			% where $\boldsymbol{w}_{P,n}=[w_{P,n,1},\dots,w_{P,n,M}]^T \in \mathbb{C}^{M \times 1}$.
 		\end{subsubsection}
 
-		\begin{subsubsection} {Superposed Waveform}
+		\begin{subsubsection}{Superposed Waveform}
 			At time $t$, a superposition of the information and power waveform at subband $n$ writes as
-			\begin{equation}	\label{eq:x_{n}(t)}
-				\begin{split}
-					x_{n}(t)
-					&= x_{I,n}(t)+x_{P,n}(t)	\\
-					&= w_{I,n} \tilde{x}_{I,n}(t)+w_{P,n}
-				\end{split}
+			\begin{equation}\label{eq:x_n(t)}
+				x_n(t)=\sum_{k=1}^K{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
 			\end{equation}
-			Hence, the transmitted signal is summed over all subbands
-			\begin{equation}	\label{eq:x(t)}
-				\begin{split}
-					x(t)
-					&= x_{I}(t)+x_{P}(t)	\\
-					&= \Re \left\{ \sum_{n=1}^{N} (w_{I,n} \tilde{x}_{I,n}(t)+w_{P,n}) e^{j2 \pi f_n t} \right\}
-				\end{split}
+			Hence, the transmitted RF signal is
+			\begin{equation}\label{eq:x(t)}
+				x(t)=\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
+				% x(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}\right\}
 			\end{equation}
-			% Therefore, the composite transmit signal vector is
-			% \begin{equation}	\label{x(t)}
-			% 	\begin{split}
-			% 		\boldsymbol{x}(t)
-			% 		&=\boldsymbol{x}_I(t)+\boldsymbol{x}_P(t)	\\
-			% 		&=\Re \left\{ \sum_{n=1}^{N} (\boldsymbol{w}_{I,n}\tilde{x}_n(t)+\boldsymbol{w}_{P,n}) e^{j2{\pi}{f_n}t} \right\}
-			% 	\end{split}
-			% \end{equation}
 		\end{subsubsection}
-
 	\end{subsection}
 
-	\begin{subsection}	{Composite Channel Model}
-		% Consider a single-IRS scenario in a multipath environment.
-The frequency response of the AP-user (i.e.
-direct) channel between antenna $m$ and user $k$ at subband $n$ is $h_{D,n,m,k}=A_{D,n,m,k}e^{j\bar{\psi}_{D,n,m,k}}=\sum_{l_{D,k}=1}^{L_{D,k}} \alpha_{l_{D,k}} e^{j\left( -2 \pi f_n \tau_{l_{D,k}}+\varsigma_{l_{D,k},n,m,k} \right)}$, where $L_{D,k}$ is the number of paths in the direct link of user $k$, $\alpha_{l_{D,k}}$ and $\tau_{l_{D,k}}$ are the delay and amplitude gain of the $l_{D,k}$-th path, $\varsigma_{l_{D,k},n,m,k}$ is the phase shift of the $l_{D,k}$-path between transmit antenna $m$ and the receive antenna of user $k$ at subband $n$.
-Similarly, the AP-IRS (i.e.
-incident) channel between antenna $m$ and element $l$ at subband $n$ writes as $h_{I,n,m,u}=A_{I,n,m,u}e^{j\bar{\psi}_{I,n,m,u}}=\sum_{l_{I,u}=1}^{L_{I,u}} \alpha_{l_{I,u}} e^{j\left( -2 \pi f_n \tau_{l_{I,u}}+\varsigma_{l_{I,u},n,m,u} \right)}$, and the IRS-user (i.e.
-reflective) channel between element $l$ and user $k$ is $h_{R,n,l,k}=A_{R,n,l,k}e^{j\bar{\psi}_{R,n,l,k}}=\sum_{l_{R,k}=1}^{L_{R,k}} \alpha_{l_{R,k}} e^{j\left( -2 \pi f_n \tau_{l_{R,k}}+\varsigma_{l_{R,k},n,l,k} \right)}$.
-Assume that $\max_{l_{D,k} \neq l_{D,k}'} \lvert \tau_{l_{D,k}}-\tau_{l_{D,k}'} \rvert \ll 1/B_s$ and $\max_{l_{I,u},l_{R,k} \neq l_{I,u}',l_{R,k}'} \lvert \left( \tau_{l_{I,u}}+\tau_{l_{R,k}} \right)-\left( \tau_{l_{I,u}'}+\tau_{l_{R,k}'} \right) \rvert \ll 1/B_s$ such that $\tilde{x}_n(t)$ and $x_{n,m}(t)$ are narrowband signals, namely $\tilde{x}_n(t-\tau_{l_D}) = \tilde{x}_n(t-\tau_{l_{I}}-\tau_{l_R}) = \tilde{x}_n(t)$ and $x_{n,m}(t-\tau_{l_D}) = x_{n,m}(t-\tau_{l_{I}}-\tau_{l_R}) = x_{n,m}(t)$.;
-
+	\begin{subsection}{Composite Channel Model}
 		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
@@
 Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-On top of this, the IRS matrix of each subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
+On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
 Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$.
@@
 Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
-
-		% We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
-Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.
-
-		% [\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$.
-		% , which is further divided into horizontal submatrices $\boldsymbol{\Theta}_n \in \mathbb{C}^{NL \times L}$ such that $\boldsymbol{\Theta}=[\boldsymbol{\Theta}_1,\dots,\boldsymbol{\Theta}_N]$.
-		% , which is then divided into $N$ vertical submatrices $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times N}$ such that $\boldsymbol{H}_{I}=[\boldsymbol{H}_{I,1}^T,\dots,\boldsymbol{H}_{I,N}^T]^T$.
-		% whose $n$-th column denotes the zero-padded incident subchannel $\boldsymbol{h}_{I,n}=[\boldsymbol{0}_{1 \times (n-1)L}^T, \boldsymbol{h}_{I,n}'^T,\boldsymbol{0}_{1 \times (N-n)L}^T]^T \in \mathbb{C}^{NL \times 1}$.
-
-		\begin{equation}	\label{eq:H}
+		\begin{equation}\label{eq:H}
 			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
@@
 		whose $(k,n)$-th entry
-		\begin{equation}	\label{eq:h_{k,n}}
+		\begin{equation}\label{eq:h_{k,n}}
 			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
@@
 		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
-		\begin{equation}	\label{eq:h_n}
+		\begin{equation}\label{eq:h_n}
 			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
@@
 
-	\begin{subsection}	{Received Signal}
+	\begin{subsection}{Received Signal}
 		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
-		\begin{equation}	\label{eq:y_k(t)}
-			\begin{split}
-				y_k(t)
-				&=y_{I,k}(t)+y_{P,k}(t)	\\
-				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
-				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
-			\end{split}
+		\begin{equation}\label{eq:y_k(t)}
+			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n})h_{k,n}{e^{j2{\pi}{f_n}{t}}}
+		\end{equation}
+		with the information and power components equal
+		\begin{equation}\label{eq:y_{I,k}(t)}
+			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{I,j,n}\tilde{x}_{I,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
+		\end{equation}
+		\begin{equation}\label{eq:y_{P,k}(t)}
+			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{P,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
 		\end{equation}
 
-		% \begin{equation}	\label{eq:y_k**2(t)}
-		% 	\begin{split}
-		% 		\mathcal{A}\left\{y_{P,k}^2(t)=\frac{1}{2}\right\}
-		% 		&=\Re\left\{\sum_{n_1,n_2}\right\}
-		% 	\end{split}
-		% \end{equation}
 	\end{subsection}
 
-	\begin{subsection}	{Information Decoder}
+	\begin{subsection}{Information Decoder}
 		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
-Therefore, the achievable rate of user $k$ is expressed as
-		\begin{equation}	\label{eq:I_k}
-			\begin{split}
-				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
-				% &=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
-				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}{\sigma_n^2}\right)}
-			\end{split}
+Besides, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
+		\begin{equation}\label{eq:gamma_{k,n}}
+			\gamma_{k,n}=\frac{(1-\rho)(w_{I,k,n}h_{k,n})(w_{I,k,n}h_{k,n})^*}{\sum_{j=1,j{\ne}k}^N{(1-\rho)(w_{I,j,n}h_{I,k,n})(w_{I,j,n}h_{I,k,n})^*+\sigma_n^2}}
 		\end{equation}
 		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$.
-A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
+Therefore, the achievable rate of user $k$ is expressed as
+		\begin{equation}\label{eq:R_k}
+			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta},\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
+		\end{equation}
+		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
+Hence, the weighted sum rate is
+		\begin{equation}\label{eq:R}
+			R=\sum_{k=1}^K{u_kR_k}
+		\end{equation}
+		where $u_k$ is the weight of user $k$.
 	\end{subsection}
 
-	\begin{subsection}	{Energy Harvester}
+	\begin{subsection}{Energy Harvester}
 		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners.
 Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
-		\begin{equation}	\label{eq:i_k}
-			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
+		\begin{equation}\label{eq:i_k}
+			i_k\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
-		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
+		where $k_i'$ depends on $i_k$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
 Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$.
@@
 With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components.
-\cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
-		\begin{equation}	\label{eq:z_k}
+\cite{Clerckx2016a} also demonstrated that to maximize $i_k$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
+		\begin{equation}\label{eq:z_k}
 			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
@@
 			\hrule
-			\begin{equation}	\label{eq:z_k_truncated}
+			\begin{equation}\label{eq:z_k_truncated}
 				\begin{split}
 					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
-					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}	\\
-					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}	\\
+					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}\\
+					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}\\
 					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
@@
 			\hrule
-
 			\begin{align}
@@
 The latter provides a modulation gain to the nonlinear terms in the output DC current.
+	\end{subsection}
+\end{section}
 
+\begin{section}{Problem Formulation}
+	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate specific waveform and IRS optimization problems.
+	\begin{subsection}{Weighted Sum Rate-Energy Region}
+		We define the achievable WSR-E region as
+		\begin{equation}
+			C_{R-I}(P) \triangleq \left\{(R,I):\right\}
+		\end{equation}
 	\end{subsection}

### 2020-04-12 system-model.tex
:pencil: Fix transmit and receive signals

@@
 			where $w_{I,k,n}$ is the corresponding information weight.
-Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
 On top of this, the RF transmit information waveform at time $t$ writes as
+			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
 			\begin{equation}\label{eq:x_I(t)}
@@
 			where $w_{P,k,n}$ is the corresponding power weight.
-Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
 Then, the transmit power signal at time $t$ is given by
@@
 		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
-Besides, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
+Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
 		\begin{equation}\label{eq:gamma_{k,n}}
-			\gamma_{k,n}=\frac{(1-\rho)(w_{I,k,n}h_{k,n})(w_{I,k,n}h_{k,n})^*}{\sum_{j=1,j{\ne}k}^N{(1-\rho)(w_{I,j,n}h_{I,k,n})(w_{I,j,n}h_{I,k,n})^*+\sigma_n^2}}
+			\gamma_{k,n}=\frac{(1-\rho)(w_{I,k,n}h_{k,n})(w_{I,k,n}h_{k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(w_{I,j,n}h_{I,k,n})(w_{I,j,n}h_{I,k,n})^*+\sigma_n^2}}
 		\end{equation}
@@
 		\end{equation}
-		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
-Hence, the weighted sum rate is
+		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
+Therefore, the weighted sum rate is
 		\begin{equation}\label{eq:R}
@@
 	\begin{subsection}{Energy Harvester}
-		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners.
-Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
+		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ have different influence on the output DC current.
+Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency of the harvester output DC current on the received waveform as
 		\begin{equation}\label{eq:i_k}
-			i_k\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
+			i_k\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
-		where $k_i'$ depends on $i_k$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna.
-Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$.
-Therefore, we first extract the DC component based on $h_{k,n}$, $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ by $\mathcal{A}\left\{.\right\}$ and then consider the expectation over $\tilde{x}_n$ by $\mathcal{E}\left\{.\right\}$.
-With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components.
+		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
+Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $w_{I,k,n}$, $w_{P,k,n}$ are thus optimized such that the randomness comes from the input distribution $\tilde{x}_{k,n}$.
+Therefore, we first extract the DC component based on $h_{k,n}$, $w_{I,k,n}$, $w_{P,k,n}$ by $\mathcal{A}\left\{.\right\}$ and then take the expectation over $\tilde{x}_{k,n}$ by $\mathcal{E}\left\{.\right\}$.
+With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ and the related terms has zero contribution to DC components.
 \cite{Clerckx2016a} also demonstrated that to maximize $i_k$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
 		\begin{equation}\label{eq:z_k}
-			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
 		\end{equation}
-		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
-We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy delivery.
+		where $k_i=i_s/i!(nv_t)^i$.
+We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer.
 Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}, whose terms are further expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				 & =\frac{1}{2}\sum_n{(w_{I,n}h_{k,n})(w_{I,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                                                                                               \\
-				 & =\frac{1}{2}\sum_n{\left[w_{I,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{I,j_1,n}h_{k,n})(w_{I,j_2,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                                                                                                           \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				 & =\frac{3}{4}\sum_{{n_1},{n_2}}{(w_{I,{n_1}}h_{k,{n_1}})(w_{I,{n_2}}h_{k,{n_2}})(w_{I,{n_1}}h_{k,{n_1}})^*(w_{I,{n_2}}h_{k,{n_2}})^*}                                                                                                                                                                                            \\
-				 & =\frac{3}{4}\sum_{{n_1},{n_2}}\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber                                                                       \\
-				 & \quad\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]^*\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]^*                                                                                                     \\
+				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{I,{j_1},{n_1}}h_{k,{n_1}})(w_{I,{j_2},{n_2}}h_{k,{n_2}})(w_{I,{j_3},{n_3}}h_{k,{n_3}})^*(w_{I,{j_4},{n_4}}h_{k,{n_4}})^*}                                                                                                          \\
+				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
+				 & \quad\left[w_{I,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{I,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*                                                                                                                           \\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				 & =\frac{1}{2}\sum_n{(w_{P,n}h_{k,n})(w_{P,n}h_{k,n})^*}                                                                                                                                                                                                                                                                          \\
-				 & =\frac{1}{2}\sum_n{\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{P,j_1,n}h_{k,n})(w_{P,j_2,n}h_{k,n})^*}                                                                                                                                                                                                                                                                                      \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{n_1}}h_{k,{n_1}})(w_{P,{n_2}}h_{k,{n_2}})(w_{P,{n_3}}h_{k,{n_3}})^*(w_{P,{n_4}}h_{k,{n_4}})^*}                                                                                                                      \\
-				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
-				 & \quad\left[w_{P,{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
+				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{j_1},{n_1}}h_{k,{n_1}})(w_{P,{j_2},{n_2}}h_{k,{n_2}})(w_{P,{j_3},{n_3}}h_{k,{n_3}})^*(w_{P,{j_4},{n_4}}h_{k,{n_4}})^*}                                                                                                          \\
+				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
+				 & \quad\left[w_{P,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
 			\end{align}
 		\end{figure*}
-		Note that $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^4\right\}=2$.
-The latter provides a modulation gain to the nonlinear terms in the output DC current.
+		Since $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, modulation provides a power gain to the nonlinear terms in the output DC current.
 	\end{subsection}
@@
 \begin{section}{Problem Formulation}
-	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate specific waveform and IRS optimization problems.
+	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
 	\begin{subsection}{Weighted Sum Rate-Energy Region}

### 2020-04-13 system-model.tex
:pencil: Expand target function

@@
 			where $w_{I,k,n}$ is the corresponding information weight.
-Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
+Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
 On top of this, the RF transmit information waveform at time $t$ writes as
@@
 			where $w_{P,k,n}$ is the corresponding power weight.
-Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
+Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
 Then, the transmit power signal at time $t$ is given by
@@
 		\end{equation}
-		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
+		represents the overall channel gain of user $k$ at subband $n$.
+We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.
+On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
 		\begin{equation}\label{eq:h_n}
@@
 		\end{equation}
-		with the information and power components equal
+		with the information and power components of
 		\begin{equation}\label{eq:y_{I,k}(t)}
@@
 		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
-Therefore, the weighted sum rate is
-		\begin{equation}\label{eq:R}
-			R=\sum_{k=1}^K{u_kR_k}
-		\end{equation}
-		where $u_k$ is the weight of user $k$.
 	\end{subsection}
@@
 		\begin{equation}\label{eq:z_k}
-			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
+			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
 		\end{equation}
@@
 We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer.
-Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}, whose terms are further expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
-		\begin{figure*}[b]
-			\hrule
-			\begin{equation}\label{eq:z_k_truncated}
-				\begin{split}
-					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
-					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}\\
-					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}\\
-					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				\end{split}
-			\end{equation}
-		\end{figure*}
+Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
+Since $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, modulation provides a power gain to the nonlinear terms in the output DC current.
 		\begin{figure*}[b]
@@
 				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{I,j_1,n}h_{k,n})(w_{I,j_2,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                                                                                         \\
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
+				 & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                                              \\
+				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
 				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{I,{j_1},{n_1}}h_{k,{n_1}})(w_{I,{j_2},{n_2}}h_{k,{n_2}})(w_{I,{j_3},{n_3}}h_{k,{n_3}})^*(w_{I,{j_4},{n_4}}h_{k,{n_4}})^*}                                                                                        \\
-				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
-				 & \quad\left[w_{I,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{I,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*                                                                                                                           \\
+				 & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})}                         \\
+				%  & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
+				%  & \quad\left[w_{I,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{I,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*                                                                                                                           \\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
 				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{P,j_1,n}h_{k,n})(w_{P,j_2,n}h_{k,n})^*}                                                                                                                                                                                                                                                                    \\
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
+				 & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                                             \\
+				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
 				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{j_1},{n_1}}h_{k,{n_1}})(w_{P,{j_2},{n_2}}h_{k,{n_2}})(w_{P,{j_3},{n_3}}h_{k,{n_3}})^*(w_{P,{j_4},{n_4}}h_{k,{n_4}})^*}                                                                                        \\
-				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
-				 & \quad\left[w_{P,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
+				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\label{eq:A{y_{P,k}**4'}}
+				%  & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
+				%  & \quad\left[w_{P,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
 			\end{align}
 		\end{figure*}
-		Since $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, modulation provides a power gain to the nonlinear terms in the output DC current.
+		Therefore, \ref{eq:z_k} reduces to \ref{eq:z_k_standard}.
+		\begin{figure*}[b]
+			\hrule
+			\begin{equation}\label{eq:z_k_standard}
+				\begin{split}
+					% z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)
+					z_k
+					&={k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})
+				\end{split}
+			\end{equation}
+		\end{figure*}
+
 	\end{subsection}
@@
 		\begin{equation}
-			C_{R-I}(P) \triangleq \left\{(R,I):\right\}
+			C_{R-I}(P) \triangleq \left\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K{u_{P,k}i_k,?}\right\}
 		\end{equation}
+		where $u_{I,k},u_{P,k}$ denote the information and power priority of user $k$.
 	\end{subsection}

### 2020-04-14 system-model.tex
:pencil: Simplify target function

@@
 		\end{equation}
-		represents the overall channel gain of user $k$ at subband $n$.
-We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.
-On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
+		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
+		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
 		\begin{equation}\label{eq:h_n}
@@
 Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
-Since $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, modulation provides a power gain to the nonlinear terms in the output DC current.
+It is noteworthy that modulation provides a power gain to the nonlinear terms in the output DC current as $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$.
 		\begin{figure*}[b]
@@
 				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{I,j_1,n}h_{k,n})(w_{I,j_2,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\
-				 & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                                              \\
+				%  & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                      \\
+				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                         \\
 				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
@@
 				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{I,{j_1},{n_1}}h_{k,{n_1}})(w_{I,{j_2},{n_2}}h_{k,{n_2}})(w_{I,{j_3},{n_3}}h_{k,{n_3}})^*(w_{I,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\
-				 & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})}                         \\
+				%  & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})} \\
+				 & =\frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})} \\
 				%  & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
@@
 				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{P,j_1,n}h_{k,n})(w_{P,j_2,n}h_{k,n})^*}                                                                                                                                                                                                   \\
-				 & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                                             \\
+				%  & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                     \\
+				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                         \\
 				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
@@
 				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{j_1},{n_1}}h_{k,{n_1}})(w_{P,{j_2},{n_2}}h_{k,{n_2}})(w_{P,{j_3},{n_3}}h_{k,{n_3}})^*(w_{P,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\
-				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\label{eq:A{y_{P,k}**4'}}
+				%  & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}  \\
+				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}
+				\label{eq:A{y_{P,k}**4'}}
 				%  & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
@@
 					&={k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})
+					% &=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
+					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
+					% &\quad+\frac{3}{2}{k_4'}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})\\
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
 				\end{split}

### 2020-04-18 system-model.tex
:pencil: WSR-E region
:pencil: Fix notation
:pencil: Fix power constraints

@@
 			where $w_{I,k,n}$ is the corresponding information weight.
-Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
-On top of this, the RF transmit information waveform at time $t$ writes as
+Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+On top of this, the overall frequency weight is denoted as $w_{I,n}=\sum_k{w_{I,k,n}}$ and collected into $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$.
+The RF transmit information waveform at time $t$ writes as
+			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
 			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
@@
 			where $w_{P,k,n}$ is the corresponding power weight.
-Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
-Then, the transmit power signal at time $t$ is given by
+Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$.
+Similarly, the overall frequency weight is denoted as $w_{P,n}=\sum_k{w_{P,k,n}}$ and collected into $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$.
+The transmit power signal at time $t$ is given by
+			% Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
 			\begin{equation}\label{eq:x_P(t)}
@@
 		\begin{equation}\label{eq:y_k(t)}
-			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n})h_{k,n}{e^{j2{\pi}{f_n}{t}}}
+			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}}(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n}){e^{j2{\pi}{f_n}{t}}}
 		\end{equation}
@@
 		\begin{equation}\label{eq:y_{I,k}(t)}
-			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{I,j,n}\tilde{x}_{I,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
+			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{I,j,n}\tilde{x}_{I,j,n}}{e^{j2{\pi}{f_n}{t}}}
 		\end{equation}
 		\begin{equation}\label{eq:y_{P,k}(t)}
-			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{w_{P,j,n}}h_{k,n}{e^{j2{\pi}{f_n}{t}}}
+			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{P,j,n}}{e^{j2{\pi}{f_n}{t}}}
 		\end{equation}
@@
 		\begin{equation}\label{eq:gamma_{k,n}}
-			\gamma_{k,n}=\frac{(1-\rho)(w_{I,k,n}h_{k,n})(w_{I,k,n}h_{k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(w_{I,j,n}h_{I,k,n})(w_{I,j,n}h_{I,k,n})^*+\sigma_n^2}}
+			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
 		\end{equation}
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{I,j_1,n}h_{k,n})(w_{I,j_2,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\
 				%  & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                      \\
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{I,{j_1},{n_1}}h_{k,{n_1}})(w_{I,{j_2},{n_2}}h_{k,{n_2}})(w_{I,{j_3},{n_3}}h_{k,{n_3}})^*(w_{I,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\
+				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}                       \\
 				%  & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})} \\
@@
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(w_{P,j_1,n}h_{k,n})(w_{P,j_2,n}h_{k,n})^*}                                                                                                                                                                                                   \\
+				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}                                                                                                                                                                                                   \\
 				%  & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                     \\
@@
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{j_1},{n_1}}h_{k,{n_1}})(w_{P,{j_2},{n_2}}h_{k,{n_2}})(w_{P,{j_3},{n_3}}h_{k,{n_3}})^*(w_{P,{j_4},{n_4}}h_{k,{n_4}})^*}                       \\
+				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}                       \\
 				%  & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}  \\
@@
 		\begin{equation}
-			C_{R-I}(P) \triangleq \left\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K{u_{P,k}i_k,?}\right\}
+			\begin{split}
+				C_{R-I}(P)
+				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
+				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
+				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
+			\end{split}
 		\end{equation}
-		where $u_{I,k},u_{P,k}$ denote the information and power priority of user $k$.
+		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
 	\end{subsection}

### 2020-04-18 system-model.tex
:pencil: Phase problem

@@
 	\end{subsection}
+
+	\begin{subsection}{Single-user optimization}
+		In this section, we first characterize the rate-energy region in the single-user setup.
+Define $w_{I,n}=s_{I,n}e^{j{\phi}_n}$ and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phase are matched to frequency response as
+		\begin{equation}\label{eq:phi_n}
+			\phi_{I,n}^\star=\phi_{P,n}^\star=-\angle{h_n}
+		\end{equation}
+		\ref{eq:phi_n} maximizes rate and energy simultaneously and depends on the IRS design.
+	\end{subsection}
 \end{section}

### 2020-04-19 system-model.tex
:pencil: Single-user design

--- 2020-04-18 system-model.tex
@@
 Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
-To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$.
+To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$.
 Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
 Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
-Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$.
+On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
+Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$.
 The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel.
@@
 		\begin{equation}\label{eq:R_k}
-			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta},\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
+			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta}_0,\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
 		\end{equation}
-		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
+		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the determaxistic power component or constructing a translated codebook.
 	\end{subsection}
@@
 		\begin{equation}\label{eq:z_k}
-			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
+			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta}_0,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
 		\end{equation}
@@
 					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
 				\end{split}
@@
 	\end{subsection}
+
+	\begin{subsection}{Single-User Optimization}
+		In this section, we first characterize the rate-energy region in the single-user setup.
+Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$.
+Consider the rate maximization problem subject to transmit power and output DC current constraints
+		\begin{maxi}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
+			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho)\ge{\bar{z}}}
+			\addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
+		\end{maxi}
+		Although the problem is non-convex, the target function can be reformed using the triangle inequality
+		\begin{equation}
+			\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
+		\end{equation}
+		where the equality holds if and only if the direct and IRS-aided links align with each other.
+In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$.
+Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
+
+		\begin{equation}
+			\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
+		\end{equation}
+		Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
+		\begin{equation}\label{eq:phi_n}
+			\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
+		\end{equation}
+		Therefore, \ref{op:1} is transformed to
+		\begin{maxi}
+			% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+			\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
+		\end{maxi}
+		with $z$ reduced to \ref{eq:z_gp}.
+
+		\begin{figure*}[b]
+			\hrule
+			\begin{equation}\label{eq:z_gp}
+				\begin{split}
+					z
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
+				\end{split}
+			\end{equation}
+		\end{figure*}
+	\end{subsection}
 \end{section}

### 2020-04-20 system-model.tex
:pencil: Formulate GP problem using AM-GM inequality

@@
 Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
-
 		\begin{equation}
@@
 		\end{maxi}
-		with $z$ reduced to \ref{eq:z_gp}.
-
 		\begin{figure*}[b]
@@
 		\end{figure*}
+		with $z$ given by \ref{eq:z_gp}. It can be transformed to an equivalent problem by introducing an auxiliary variable $t_0$
+		\begin{mini}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:3}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+			\addConstraint{\frac{t_0}{\prod_{n}{\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)}}\le{1}}
+			\addConstraint{\frac{\bar{z}}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\le{1}}
+		\end{mini}
+		\ref{op:3} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
+The basic idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{{m_P}=1}^{M_P}{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:3} is equivalent to
+		% $1+\bar{\rho}{A_n^2}{s_{I,n}^2}/\sigma_n^2=\sum_{{m_{I,n}}=1}^{M_{I,n}}{g_{I,m_{I,n}}(\boldsymbol{s}_I,\bar{\rho})}$
+		\begin{mini}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:4}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+			\addConstraint{{t_0}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
+			\addConstraint{\bar{z}\prod_{m_P}{\left(\frac{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m_P}}\right)^{-\gamma_{P,m_P}}}\le{1}}
+			\addConstraint{\rho+\bar{\rho}\le{1}}
+		\end{mini}
+		where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m_P} \ge 0,\forall m_P=1,\dots,M_P$ and $\sum_{{m_P}=1}^{M_P}{\gamma_{m_P}}=1$.
+As suggested in \cite{Clerckx2018b}, the tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require iterative update.
+At iteration $i$, we choose
+		\begin{align}
+			\gamma_{I,n,1}^{(i)} & =\frac{1}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},                                                                         &  & n=1,\dots,N,    \\
+			\gamma_{I,n,2}^{(i)} & =\frac{\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},           &  & n=1,\dots,N,    \\
+			\gamma_{P,m_P}^{(i)} & =\frac{g_{P,m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}, &  & m_P=1,\dots,M_P
+		\end{align}
+		and then solve problem \ref{op:4}.
 	\end{subsection}

### 2020-04-22 system-model.tex
:pencil: Phase problem

@@
 		\end{maxi}
-		Although the problem is non-convex, the target function can be reformed using the triangle inequality
-		\begin{equation}
-			\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
-		\end{equation}
-		where the equality holds if and only if the direct and IRS-aided links align with each other.
+		Since the objective function is non-convex with $\Theta_0$ and $\boldsymbol{w}_I$ coupled, \ref{op:1} is a non-convex problem.
+To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the information weight at the transmitter and the phase shifts at the IRS iteratively until convergence.
+It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
+		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
+
+		% Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\Phi=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$.
+On top of this, \ref{eq:h_{k,n}} can be expressed as
+		% \begin{equation}
+		% 	\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{v}^H{\Phi}
+		% \end{equation}
+
+		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
+		% \begin{equation}
+		% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
+		% \end{equation}
+		% where the equality holds if and only if the direct and IRS-aided links align with each other.
 In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$.
 Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
-		\begin{equation}
-			\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
-		\end{equation}
-		Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
-		\begin{equation}\label{eq:phi_n}
-			\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
-		\end{equation}
+		% \begin{equation}
+		% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
+		% \end{equation}
+		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
+		% \begin{equation}\label{eq:phi_n}
+		% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
+		% \end{equation}
 		Therefore, \ref{op:1} is transformed to

### 2020-04-22 system-model.tex
:pencil: Vectorize phase shift matrix

@@
 	\begin{subsection}{Single-User Optimization}
-		In this section, we first characterize the rate-energy region in the single-user setup.
-Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$.
-Consider the rate maximization problem subject to transmit power and output DC current constraints
+		In this section, we first characterize the rate-energy region in the single-user setup. Define $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$
+		, $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$, and $\boldsymbol{\Phi}_n=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$.
+On top of this, the composite channel \ref{eq:h_{k,n}} can be expressed as $h_n=h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n}$.
+The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
 		\begin{maxi}
-			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
+			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
 			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho)\ge{\bar{z}}}
-			\addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
+			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
+			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
+			% \addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
 		\end{maxi}
-		Since the objective function is non-convex with $\Theta_0$ and $\boldsymbol{w}_I$ coupled, \ref{op:1} is a non-convex problem.
-To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the information weight at the transmitter and the phase shifts at the IRS iteratively until convergence.
-It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
+		\ref{op:1} is nontrivial due to the non-convex objective function, unit-modulus constraint, and coupled variables.
+To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.
+
+		The phase optimization problem can be formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
+		\begin{maxi}
+			{\boldsymbol{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2\lvert{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}}{}{}
+		\end{maxi}
+
+		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
 		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.

### 2020-04-23 system-model.tex
:pencil: Formulate phase problem

@@
 		\end{maxi}
-		\ref{op:1} is nontrivial due to the non-convex objective function, unit-modulus constraint, and coupled variables.
+		\ref{op:1} is intricate due to the non-convex objective function, unit-modulus constraints, and coupled variables.
 To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.
 
-		The phase optimization problem can be formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
+		The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
 		\begin{maxi}
-			{\boldsymbol{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2\lvert{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}}{}{}
+			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
+			% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
+			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
 		\end{maxi}
-
+		Note that $\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2=\lvert{h}_{D,n}\rvert^2+h_{D,n}\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}^*}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$.
+Introduce an auxiliary variable $t$ with unit modulus and rewrite \ref{op:temp} as
+		\begin{maxi}
+			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
+			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
+		\end{maxi}
+		where
+		\begin{equation}
+			\boldsymbol{R}=
+			\begin{bmatrix}
+				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h}_{D,n}^* \\
+				h_{D,n}\boldsymbol{\Phi}_n               & 0
+			\end{bmatrix},
+			\quad \bar{\boldsymbol{v}}=
+			\begin{bmatrix}
+				\boldsymbol{v} \\
+				t
+			\end{bmatrix}
+		\end{equation}
+		However, problem \ref{op:temp1} is still non-convex.
+We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
+		A semidefinite programming (SDP) problem is then formulated by applying SDR to drop the rank-one constraint as
+		\begin{maxi}
+			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V}))}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+			\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
+			\addConstraint{\boldsymbol{V}\succeq{0}}
+		\end{maxi}
+		which can be solved by softwares as CVX \cite{Grant2013}.
 		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
 		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
-
-		% Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\Phi=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$.
-On top of this, \ref{eq:h_{k,n}} can be expressed as
-		% \begin{equation}
-		% 	\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{v}^H{\Phi}
-		% \end{equation}
-
 		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
@@
 		% \end{equation}
-		Therefore, \ref{op:1} is transformed to
+
+		Once a feasible phase shift set is obtained, the original problem \ref{op:1} can be reduced to
 		\begin{maxi}

### 2020-04-23 system-model.tex
:pencil: Fix channel model

@@
 	\begin{subsection}{Composite Channel Model}
-		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively.
-At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
-Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$.
+		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R^H \in \mathbb{C}^{K \times NL}$ respectively.
+At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^H \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}^H=[\boldsymbol{h}_{R,1,n},\dots,\boldsymbol{h}_{R,K,n}]^H \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}^H=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
+Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^H \in \mathbb{C}^{L \times 1}$.
 To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$.
@@
 		\begin{equation}\label{eq:H}
-			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
+			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R^H\boldsymbol{\Theta}\boldsymbol{H}_I
 		\end{equation}
@@
 		\begin{equation}\label{eq:h_{k,n}}
-			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
 		\end{equation}
@@
 		\begin{equation}\label{eq:h_n}
-			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+		\end{equation}
+		Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Phi}_n^H=\boldsymbol{H}_{R,n}^H\mathrm{diag}\left\{\boldsymbol{h}_{I,n}\right\} \in \mathbb{C}^{K \times L}$.
+Therefore, \ref{eq:h_n} rewrites as
+		\begin{equation}
+			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}
 		\end{equation}
@@
 	\begin{subsection}{Single-User Optimization}
-		In this section, we first characterize the rate-energy region in the single-user setup. Define $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$
-		, $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$, and $\boldsymbol{\Phi}_n=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$.
-On top of this, the composite channel \ref{eq:h_{k,n}} can be expressed as $h_n=h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n}$.
+		In this section, we first characterize the rate-energy region in the single-user setup.
+Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$.
 The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
@@
 			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
-			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
 			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
@@
 		\begin{maxi}
-			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
+			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
 			% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
@@
 		\end{maxi}
-		Note that $\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2=\lvert{h}_{D,n}\rvert^2+h_{D,n}\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}^*}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$.
-Introduce an auxiliary variable $t$ with unit modulus and rewrite \ref{op:temp} as
+		Since $\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$, we introduce an auxiliary variable $t$ with unit modulus and transform \ref{op:temp} to
 		\begin{maxi}
-			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
+			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
 			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
@@
 			\begin{bmatrix}
-				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h}_{D,n}^* \\
-				h_{D,n}\boldsymbol{\Phi}_n               & 0
+				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & h_{D,n}^*{\boldsymbol{\Phi}_n^H} \\
+				\boldsymbol{\Phi}_n{h_{D,n}}             & h_{D,n}^*{h_{D,n}}
 			\end{bmatrix},
@@
 We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
-		A semidefinite programming (SDP) problem is then formulated by applying SDR to drop the rank-one constraint as
+		A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint
 		\begin{maxi}
-			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V}))}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
 			\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
@@
 		\end{maxi}
-		which can be solved by softwares as CVX \cite{Grant2013}.
+		which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
 		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
@@
 
-		Once a feasible phase shift set is obtained, the original problem \ref{op:1} can be reduced to
+		Once a feasible phase shift set is obtained, the original problem \ref{op:1} is reduced to
 		\begin{maxi}

### 2020-04-25 system-model.tex
:pencil: Fix dimension of auxiliary matrix

@@
 			\begin{bmatrix}
-				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & h_{D,n}^*{\boldsymbol{\Phi}_n^H} \\
-				\boldsymbol{\Phi}_n{h_{D,n}}             & h_{D,n}^*{h_{D,n}}
+				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h_{D,n}} \\
+				h_{D,n}^*{\boldsymbol{\Phi}_n^H}         & h_{D,n}^*{h_{D,n}}
 			\end{bmatrix},
@@
 		However, problem \ref{op:temp1} is still non-convex.
-We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
+We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
 		A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint

### 2020-04-26 system-model.tex
:pencil: Joint optimization (in progress)

--- 2020-04-23 system-model.tex
@@
 		\end{figure*}
-		Therefore, \ref{eq:z_k} reduces to \ref{eq:z_k_standard}.
+		Therefore, \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.
 		\begin{figure*}[b]
 			\hrule
-			\begin{equation}\label{eq:z_k_standard}
+			\begin{equation}\label{eq:z_k_truncated}
 				\begin{split}
@@
 		\end{figure*}
-
 	\end{subsection}
@@
 		\end{maxi}
-		\ref{op:1} is intricate due to the non-convex objective function, unit-modulus constraints, and coupled variables.
-To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.
-
-		The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
+		Problem \ref{op:1} is intricate due to the non-convex rate function, unit-modulus constraint, and non-convex DC current requirement with coupled variables.
+		% To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.
+		% The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
+		% \begin{maxi}
+		% 	{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
+		% 	% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
+		% 	\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
+		% \end{maxi}
+		Since $\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$, we introduce an auxiliary variable $t$ with unit modulus and transform \ref{op:1} to
 		\begin{maxi}
-			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
-			% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
-			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
-		\end{maxi}
-		Since $\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$, we introduce an auxiliary variable $t$ with unit modulus and transform \ref{op:temp} to
-		\begin{maxi}
-			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\bar{\boldsymbol{v}},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
+			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
 			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
@@
 		However, problem \ref{op:temp1} is still non-convex.
-We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
-		A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint
+We further define a rank-one positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ such that $\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
+Hence, \ref{op:temp1} is transformed to
 		\begin{maxi}
-			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
+			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
 			\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
 			\addConstraint{\boldsymbol{V}\succeq{0}}
+			\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
 		\end{maxi}
+		To tackle the non-convex current constraint, we introduce channel matrices $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$, whose $(n_1,n_2)$ entry equals
+		\begin{equation}
+			\begin{split}
+				{h_{n_1}^*}{h_{n_2}}
+				&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
+				&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
+				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*
+			\end{split}
+		\end{equation}
+		where
+		\begin{equation}
+			\boldsymbol{R}_{n_1,n_2}=
+			\begin{bmatrix}
+				\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
+				h_{D,n_2}^*{\boldsymbol{\Phi}_{n_1}^T}             & h_{D,n_2}^*{h_{D,n_1}^*}
+			\end{bmatrix}
+		\end{equation}
+		On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries.
+It holds that $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
+		\begin{figure*}[b]
+			\hrule
+			\begin{equation}\label{eq:z_k_su}
+				\begin{split}
+					z
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}{\boldsymbol{w}_I\boldsymbol{M}_0}
+				\end{split}
+			\end{equation}
+		\end{figure*}
+
+		% A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint
+
 		which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
@@
 		% \end{equation}
-		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
+		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
 		% \begin{equation}\label{eq:phi_n}

### 2020-04-27 system-model.tex
:pencil: Reformulate current constraint

@@
 		\end{maxi}
-		To tackle the non-convex current constraint, we introduce channel matrices $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$, whose $(n_1,n_2)$ entry equals
+		% To tackle the non-convex current constraint, we expand and rewrite the coupled channel terms in \ref{eq:z_k_truncated} as
+		% \begin{equation}
+		% 	\begin{split}
+		% 		{h_{n_3}^*}{h_{n_1}}
+		% 		&=(h_{D,n_3}^*+\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*)(h_{D,n_1}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*})\\
+		% 		&={h_{D,n_1}}{h_{D,n_3}^*}+{h_{D,n_1}}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}h_{D,n_3}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*\\
+		% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_3,n_1}\bar{\boldsymbol{v}}^*\\
+		% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)
+		% 	\end{split}
+		% \end{equation}
+		% where
+		% \begin{equation}
+		% 	\boldsymbol{R}_{n_3,n_1}=
+		% 	\begin{bmatrix}
+		% 		\boldsymbol{\Phi}_{n_1}^*\boldsymbol{\Phi}_{n_3}^T & \boldsymbol{\Phi}_{n_1}^*{h_{D,n_3}^*} \\
+		% 		h_{D,n_1}{\boldsymbol{\Phi}_{n_3}^T}               & h_{D,n_1}{h_{D,n_3}^*}
+		% 	\end{bmatrix}
+		% \end{equation}
+		% Similarly, we have ${h_{n_4}^*}{h_{n_2}}=\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)$ and ${h_n^*}{h_n}=\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)$.
+Thus, \ref{eq:z_k_truncated} is equivalent to
+		% \begin{figure*}[b]
+		% 	\hrule
+		% 	\begin{equation}\label{eq:z_k_su_temp}
+		% 		\begin{split}
+		% 			z
+		% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}\\
+		% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{w}_{P,n_2})\right)\\
+		% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)^2(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}
+		% 		\end{split}
+		% 	\end{equation}
+		% \end{figure*}
+
+		To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
 		\begin{equation}
@@
 				&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
-				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*
+				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
+				&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
 			\end{split}
@@
 				\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
-				h_{D,n_2}^*{\boldsymbol{\Phi}_{n_1}^T}             & h_{D,n_2}^*{h_{D,n_1}^*}
+				h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
 			\end{bmatrix}
@@
 		On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries.
-It holds that $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
+It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
+Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_su}.
 		\begin{figure*}[b]
@@
 					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}{\boldsymbol{w}_I\boldsymbol{M}_0}
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
+					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}\left(2\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H\right)\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
 				\end{split}

### 2020-05-01 system-model.tex
:art: Improve format
:pencil: Alternating optimization

@@
 
+		% ? AO: optimize phase shifts with given weights
+		Define waveform matrices $\boldsymbol{M}_I=\boldsymbol{w}_I^*\boldsymbol{w}_I^T$ and $\boldsymbol{M}_P=\boldsymbol{w}_P^*\boldsymbol{w}_P^T$.
+Also, let $\boldsymbol{M}_{I/P, n}$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries.
+It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$ \cite{Huang2017}.
+Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_phase}.
+		\begin{figure*}[b]
+			\hrule
+			\begin{equation}\label{eq:z_k_phase}
+				\begin{split}
+					z
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
+					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
+				\end{split}
+			\end{equation}
+		\end{figure*}
+
+		% ? AO: optimize weights with given phase shifts
 		To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
@@
 It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
-Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_su}.
+Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
 		\begin{figure*}[b]
 			\hrule
-			\begin{equation}\label{eq:z_k_su}
+			\begin{equation}\label{eq:z_k_waveform}
 				\begin{split}
@@
 					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}\left(2\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H\right)\\
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
 					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
@@
 		\end{figure*}
+		We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
+		% and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
+		\begin{equation}\label{eq:z_k_su_compact}
+			\begin{split}
+				z
+				&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
+				&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
+				&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
+			\end{split}
+		\end{equation}
 
@@
 
-		which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
+		% which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
 		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.

### 2020-05-06 system-model.tex
:pencil: Frequency-selective IRS

@@
 		Problem \ref{op:1} is intricate due to the non-convex rate function, unit-modulus constraint, and non-convex DC current requirement with coupled variables.
+
+		\begin{subsubsection}{Frequency-Selective IRS}
+			In frequency-selective IRS, each element is expected to provide adjustable subband-dependent reflection coefficients such that the total degree of freedom of IRS is $NL$.
+Therefore, $\boldsymbol{v}_n$ replaces $\boldsymbol{v}$ in \ref{op:1}.
+Note that $\lvert{(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{\Phi}_n^H\boldsymbol{v}_nw_{I,n}}\rvert$ where the equality holds if and only if the direct and IRS-aided links align with each other, namely
+			\begin{equation}
+				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{\boldsymbol{\Phi}}
+			\end{equation}
+		\end{subsubsection}
+
 		% To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.

### 2020-05-06 system-model.tex
:art: Improve structure

@@
 		\begin{subsubsection}{Frequency-Selective IRS}
-			In frequency-selective IRS, each element is expected to provide adjustable subband-dependent reflection coefficients such that the total degree of freedom of IRS is $NL$.
+			In frequency-selective IRS, each element is expected to provide adjustable subband-dependent reflection coefficients such that the total degree of freedom (DoF) of IRS is $NL$.
 Therefore, $\boldsymbol{v}_n$ replaces $\boldsymbol{v}$ in \ref{op:1}.
-Note that $\lvert{(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{\Phi}_n^H\boldsymbol{v}_nw_{I,n}}\rvert$ where the equality holds if and only if the direct and IRS-aided links align with each other, namely
+Note that $\lvert{(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{\Phi}_n^H\boldsymbol{v}_nw_{I,n}}\rvert$ where the equality holds if and only if the direct and IRS-aided links are aligned by
 			\begin{equation}
-				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{\boldsymbol{\Phi}}
+				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
 			\end{equation}
+			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario.
+On top of this, it can be observed from \ref{eq:gamma_{k,n}}, \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal phase of information and power waveforms are matched to composite frequency response as
+			\begin{equation}\label{eq:phi_n}
+				\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
+			\end{equation}
+			With all the phases determined, the original problem \ref{op:1} is reduced to
+			\begin{maxi}
+				% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+				\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
+			\end{maxi}
+			\begin{figure*}[b]
+				\hrule
+				\begin{equation}\label{eq:z_gp}
+					\begin{split}
+						z
+						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
+						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
+					\end{split}
+				\end{equation}
+			\end{figure*}
+			with $z$ given by \ref{eq:z_gp}. It can be transformed to an equivalent problem by introducing an auxiliary variable $t_0$
+			\begin{mini}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:3}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+				\addConstraint{\frac{t_0}{\prod_{n}{\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)}}\le{1}}
+				\addConstraint{\frac{\bar{z}}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\le{1}}
+			\end{mini}
+			\ref{op:3} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
+The basic idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{{m_P}=1}^{M_P}{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:3} is equivalent to
+			% $1+\bar{\rho}{A_n^2}{s_{I,n}^2}/\sigma_n^2=\sum_{{m_{I,n}}=1}^{M_{I,n}}{g_{I,m_{I,n}}(\boldsymbol{s}_I,\bar{\rho})}$
+			\begin{mini}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:4}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+				\addConstraint{{t_0}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
+				\addConstraint{\bar{z}\prod_{m_P}{\left(\frac{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m_P}}\right)^{-\gamma_{P,m_P}}}\le{1}}
+				\addConstraint{\rho+\bar{\rho}\le{1}}
+			\end{mini}
+			where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m_P} \ge 0,\forall m_P=1,\dots,M_P$ and $\sum_{{m_P}=1}^{M_P}{\gamma_{m_P}}=1$.
+As suggested in \cite{Clerckx2018b}, the tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require iterative update.
+At iteration $i$, we choose
+			\begin{align}
+				\gamma_{I,n,1}^{(i)} & =\frac{1}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},                                                                         &  & n=1,\dots,N,    \\
+				\gamma_{I,n,2}^{(i)} & =\frac{\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},           &  & n=1,\dots,N,    \\
+				\gamma_{P,m_P}^{(i)} & =\frac{g_{P,m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}, &  & m_P=1,\dots,M_P
+			\end{align}
+			and then solve problem \ref{op:4}.
 		\end{subsubsection}
 
-		% To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.
-		% The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
-		% \begin{maxi}
-		% 	{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
-		% 	% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
-		% 	\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
-		% \end{maxi}
-		Since $\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$, we introduce an auxiliary variable $t$ with unit modulus and transform \ref{op:1} to
-		\begin{maxi}
-			{\boldsymbol{w}_I,\boldsymbol{w}_P,\bar{\boldsymbol{v}},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
-			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
-			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
-		\end{maxi}
-		where
+		\begin{subsubsection}{Frequency-Flat IRS}
+			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
+			\begin{equation}
+				\begin{split}
+					\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2
+					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
+					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})
+				\end{split}
+			\end{equation}
+			where $t$ is an auxiliary variable with unit modulus and
 			\begin{equation}
@@
 				\end{bmatrix},
-			\quad \bar{\boldsymbol{v}}=
+				\quad \bar{\boldsymbol{v}}=\
 				\begin{bmatrix}
@@
 					t
-			\end{bmatrix}
+				\end{bmatrix},
+				\quad \bar{\boldsymbol{V}}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H
 			\end{equation}
-		However, problem \ref{op:temp1} is still non-convex.
-We further define a rank-one positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ such that $\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
-Hence, \ref{op:temp1} is transformed to
+			Hence, \ref{op:1} is transformed to
 			\begin{maxi}
@@
 				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
+				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho)\ge{\bar{z}}}
 				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
@@
 			\end{maxi}
+			To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.
+
+			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
+			\begin{maxi}
+				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
+				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
+				\addConstraint{\boldsymbol{V}\succeq{0}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
+			\end{maxi}
+
 			% To tackle the non-convex current constraint, we expand and rewrite the coupled channel terms in \ref{eq:z_k_truncated} as
@@
 			% \end{figure*}
+		\end{subsubsection}
 
@@
 
-		Once a feasible phase shift set is obtained, the original problem \ref{op:1} is reduced to
-		\begin{maxi}
-			% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
-			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
-			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-			\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
-		\end{maxi}
-		\begin{figure*}[b]
-			\hrule
-			\begin{equation}\label{eq:z_gp}
-				\begin{split}
-					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
-				\end{split}
-			\end{equation}
-		\end{figure*}
-		with $z$ given by \ref{eq:z_gp}. It can be transformed to an equivalent problem by introducing an auxiliary variable $t_0$
-		\begin{mini}
-			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:3}}{}
-			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-			\addConstraint{\frac{t_0}{\prod_{n}{\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)}}\le{1}}
-			\addConstraint{\frac{\bar{z}}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\le{1}}
-		\end{mini}
-		\ref{op:3} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
-The basic idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
-Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{{m_P}=1}^{M_P}{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:3} is equivalent to
-		% $1+\bar{\rho}{A_n^2}{s_{I,n}^2}/\sigma_n^2=\sum_{{m_{I,n}}=1}^{M_{I,n}}{g_{I,m_{I,n}}(\boldsymbol{s}_I,\bar{\rho})}$
-		\begin{mini}
-			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:4}}{}
-			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-			\addConstraint{{t_0}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
-			\addConstraint{\bar{z}\prod_{m_P}{\left(\frac{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m_P}}\right)^{-\gamma_{P,m_P}}}\le{1}}
-			\addConstraint{\rho+\bar{\rho}\le{1}}
-		\end{mini}
-		where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m_P} \ge 0,\forall m_P=1,\dots,M_P$ and $\sum_{{m_P}=1}^{M_P}{\gamma_{m_P}}=1$.
-As suggested in \cite{Clerckx2018b}, the tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require iterative update.
-At iteration $i$, we choose
-		\begin{align}
-			\gamma_{I,n,1}^{(i)} & =\frac{1}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},                                                                         &  & n=1,\dots,N,    \\
-			\gamma_{I,n,2}^{(i)} & =\frac{\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},           &  & n=1,\dots,N,    \\
-			\gamma_{P,m_P}^{(i)} & =\frac{g_{P,m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}, &  & m_P=1,\dots,M_P
-		\end{align}
-		and then solve problem \ref{op:4}.
 	\end{subsection}

### 2020-05-06 system-model.tex
:construction: Frequency-selective IRS

@@
 					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
-					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})
+					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})
 				\end{split}
@@
 			\begin{equation}
-				\boldsymbol{R}=
+				\boldsymbol{R}_n=
 				\begin{bmatrix}
@@
 			\begin{maxi}
-				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
 				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
@@
 
+			% ? AO: optimize phase shifts with given waveform
 			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
 			\begin{maxi}
-				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
 				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
@@
 			\end{maxi}
+			To tackle the non-convex current constraint, we define waveform matrices $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$.
+On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries.
+Therefore, the current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
+			\begin{figure*}[b]
+				\hrule
+				\begin{equation}\label{eq:z_k_irs}
+					\begin{split}
+						z
+						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
+						% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+						% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
+						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
+					\end{split}
+				\end{equation}
+			\end{figure*}
+			Introduce auxiliary variables $t_{I/P,n}=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}=\mathrm{Tr}()$ and we have $t_{I/P,n}t_{I/P,n}^*=t_{I/P,-n}t_{I/P,-n}^*$ by noticing $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
+Further define $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{N-1}$.
+
+			% * It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$.
 
@@
 		\end{subsubsection}
-
-		% ? AO: optimize phase shifts with given weights
-		Define waveform matrices $\boldsymbol{M}_I=\boldsymbol{w}_I^*\boldsymbol{w}_I^T$ and $\boldsymbol{M}_P=\boldsymbol{w}_P^*\boldsymbol{w}_P^T$.
-Also, let $\boldsymbol{M}_{I/P, n}$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries.
-It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$ \cite{Huang2017}.
-Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_phase}.
-		\begin{figure*}[b]
-			\hrule
-			\begin{equation}\label{eq:z_k_phase}
-				\begin{split}
-					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
-					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
-				\end{split}
-			\end{equation}
-		\end{figure*}
 

### 2020-05-07 system-model.tex
:construction: Composite SDR problem

@@
 On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries.
-Therefore, the current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
+Therefore, the current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs} with $\boldsymbol{h}=\boldsymbol{h}_D+\boldsymbol{\Phi}^H\boldsymbol{v} \in \mathbb{C}^{N \times 1}$ and $\boldsymbol{\Phi}^H=[\boldsymbol{\Phi}_1,\dots,\boldsymbol{\Phi}_N]^H \in \mathbb{C}^{N \times L}$.
 			\begin{figure*}[b]
@@
 			\end{figure*}
-			Introduce auxiliary variables $t_{I/P,n}=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}=\mathrm{Tr}()$ and we have $t_{I/P,n}t_{I/P,n}^*=t_{I/P,-n}t_{I/P,-n}^*$ by noticing $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
+			Introduce auxiliary variables $t_{I/P,n}=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{M}_{I/P,n})=\mathrm{Tr}(\boldsymbol{H}\boldsymbol{M}_{I/P,n})$
+
+			and we have $t_{I/P,n}t_{I/P,n}^*=t_{I/P,-n}t_{I/P,-n}^*$ by noticing $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
 Further define $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{N-1}$.

### 2020-05-19 system-model.tex
:pencil: Reform outer product
:sparkles: Alternating optimization

--- 2020-05-06 system-model.tex
@@
 			\begin{maxi}
-				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
+				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp4}}{}
 				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
@@
 			\end{maxi}
-			To tackle the non-convex current constraint, we define waveform matrices $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$.
-On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries.
-Therefore, the current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
+			To tackle the non-convex current constraint, we collect the channel matrices into $\boldsymbol{\Phi}^H=[\boldsymbol{\Phi}_1,\dots,\boldsymbol{\Phi}_N]^H \in \mathbb{C}^{N \times L}$ and $\boldsymbol{h}=\boldsymbol{h}_D+\boldsymbol{\Phi}^H\boldsymbol{v} \in \mathbb{C}^{N \times 1}$.
+The fixed waveform matrices are defined as $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$.
+On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and null the remaining entries.
+Due to the positive definiteness of $\boldsymbol{M}_{I/P}$, we have $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
+Hence, the output current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
 			\begin{figure*}[b]
@@
 						% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
+						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^*+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^*}\\
 						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
@@
 			\end{figure*}
-			Introduce auxiliary variables $t_{I/P,n}=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}=\mathrm{Tr}()$ and we have $t_{I/P,n}t_{I/P,n}^*=t_{I/P,-n}t_{I/P,-n}^*$ by noticing $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
-Further define $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{N-1}$.
+			We further simplify it by introducing auxiliary variables
+			\begin{equation}\label{eq:t}
+				\begin{split}
+					t_{I/P,n}
+					&=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}\\
+					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{M}_{I/P,n})\\
+					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{V}\boldsymbol{R}\boldsymbol{M}_{I/P,n})\\
+					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H\boldsymbol{V})\\
+					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{V})
+				\end{split}
+			\end{equation}
+			where $\boldsymbol{R}^H=[\boldsymbol{\Phi}^H,\boldsymbol{h}_D] \in \mathbb{C}^{N \times (L+1)}$ and $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+Therefore, \ref{eq:z_k_irs} rewrites as
+			\begin{equation}\label{eq:z_k_irs_t}
+				\begin{split}
+					z
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
+				\end{split}
+			\end{equation}
+
+			% It holds that $t_{I/P,n}^*t_{I/P,n}=t_{I/P,-n}^*t_{I/P,-n}$ since $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
+On top of this, denote $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{(N-1) \times 1}$ and rewrite \ref{eq:z_k_irs} as
+			% \begin{equation}\label{eq:z_k_irs_t}
+			% 	\begin{split}
+			% 		z
+			% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
+			% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(2t_{I,0}^*t_{I,0}+t_{P,0}^*t_{P,0}+4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P)\\
+			% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
+			% 	\end{split}
+			% \end{equation}
+			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_k_irs_t}.
+Based on the variables optimized at iteration $k - 1$, the local approximations at iteration $k$ are \cite{Adali2010}
+			\begin{equation}
+				\begin{split}
+					t_{I/P,n}^{(k)} (t_{I/P,n}^{(k)})^*
+					& \approx 2 \Re\left\{t_{I/P,n}^{(k)} (t_{I/P,n}^{(k-1)})^*\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^* \\
+					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right)\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right) + \mathrm{Tr}(t_{I/P,n}^{(k-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{V}^{(k)})\\
+					& \quad- t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*
+				\end{split}
+			\end{equation}
+			and
+			\begin{equation}
+				\begin{split}
+					t_{I,0}^{(k)} t_{P,0}^{(k)}
+					& \approx t_{I,0}^{(k)} t_{P,0}^{(k-1)} + t_{I,0}^{(k-1)} t_{P,0}^{(k)} - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}\\
+					& = \mathrm{Tr}(t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0}\boldsymbol{V}^{(k)}) + \mathrm{Tr}(t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0}\boldsymbol{V}^{(k)}) - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}
+				\end{split}
+			\end{equation}
+			The second approximation holds since $t_{I/P,0}$ are real. Therefore, we have
+			\begin{equation}\label{eq:z_irs_approx}
+				\begin{split}
+					\tilde{z}(\boldsymbol{V}^{(k)})
+					& = \mathrm{Tr}(\boldsymbol{A}^{(k)}\boldsymbol{V}^{(k)}) \\
+					& - \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(k-1)} (t_{I,n}^{(k-1)})^* + t_{P,n}^{(k-1)} (t_{P,n}^{(k-1)})^* \\
+					& - \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}
+				\end{split}
+			\end{equation}
+			where the Hermitian matrix $\boldsymbol{A}^{(k)}$ is
+			\begin{equation}\label{eq:A_k}
+				\begin{split}
+					\boldsymbol{A}^{(k)}
+					& = \frac{k_2 \rho R_{\text{ant}}}{2}(\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
+					& \quad+ \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8}\sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(k-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(k-1)}\boldsymbol{C}_{I,n}^H\right)\\
+					& \quad \quad + \left((t_{P,n}^{(k-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(k-1)}\boldsymbol{C}_{P,n}^H\right)\\
+					& \quad+ \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} (t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0})
+				\end{split}
+			\end{equation}
+			Plug \ref{eq:z_irs_approx} into problem \ref{op:temp4} and solve it by iterative interior-point method.
+Denote the optimal IRS matrix as $\boldsymbol{V}^{\star}$.
+If $\mathrm{rank}(\boldsymbol{V}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{v}}^\star$ is attained by eigenvalue decomposition (EVD).
+Otherwise, a best feasible candidate $\bar{\boldsymbol{v}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}.
+First, we perform EVD on $\boldsymbol{V}^{\star}$ as $\boldsymbol{V}^{\star}=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}\boldsymbol{U}_{\boldsymbol{V}^{\star}}^H$.
+Then, we generate $R$ random CSCG vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{v}}_r=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$.
+Next, the optimal solution $\bar{\boldsymbol{v}}^\star$ is approximated by the one achieving maximum objective value of \ref{op:temp4}.
+Finally, we can retrieve the phase shift as $\theta_l=\arg(v_l^\star/v_{L+1}^\star)$.
+The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{alg:irs}.
+
+			\begin{algorithm}
+				\caption{IRS Optimization}
+				\label{alg:irs}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
+					\State \textbf{Initialize} $k=0$, $\boldsymbol{V}^{(0)}$, $t_{I/P,n}^{(0)} \ \forall n$
+					\Repeat
+					\State $k = k + 1$
+					\State Update SDR matrix $\boldsymbol{A}^{(k)}$ by \ref{eq:A_k}
+					\State Obtain IRS matrix $\boldsymbol{V}^{(k)}$ by solving problem \ref{op:temp4}
+					\State Update auxiliary $t_{I/P,n}^{(k)} \forall n$ by \ref{eq:t} for SCA
+					% \Until $\lVert \boldsymbol{V}^{(k)} - \boldsymbol{V}^{(k - 1)} \rVert_F / \lVert \boldsymbol{V}^{(k)} \rVert_F \le \epsilon$
+					\Until $R^{(k)}-R^{(k-1)} \le \epsilon$
+					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall r$
+					\State Perform EVD $\boldsymbol{V}^{\star}=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}\boldsymbol{U}_{\boldsymbol{V}^{\star}}^H$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{v}}_r=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r \forall r$ and corresponding matrices $\boldsymbol{V}_r=\bar{\boldsymbol{v}}_r\bar{\boldsymbol{v}}_r^H  \ \forall r$
+					\State Select the best solution $\boldsymbol{V}_r^\star$ for problem \ref{op:temp4} and corresponding $\boldsymbol{v}_r^\star$
+					\State Compute IRS phase shift by $\theta_l=\arg(v_l^\star/v_{L+1}^\star) \ \forall l$
+					\State \textbf{Output} $\theta_l, l = 1 , \dots L$
+				\end{algorithmic}
+			\end{algorithm}
+
+			The waveform optimization subproblem is formed as follows. For a given $\boldsymbol{V}$, problem \ref{op:temp3} reduces to
+			\begin{maxi}
+				{\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp5}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
+				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)\ge{\bar{z}}}
+			\end{maxi}
+			Similarly, define $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T$ and let $\boldsymbol{M}_n$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and null the remaining entries.
+Since $\boldsymbol{M} \succ 0$, we have $\boldsymbol{M}_{-n}=\boldsymbol{M}_n^H$.
+Hence, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
+			\begin{figure*}[b]
+				\hrule
+				\begin{equation}\label{eq:z_k_waveform}
+					\begin{split}
+						z
+						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
+						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)^*+(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)^*}\\
+						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_{0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_{0}\boldsymbol{w}_P)}
+					\end{split}
+				\end{equation}
+			\end{figure*}
+			Introduce auxiliary variables
+			\begin{equation}\label{eq:t'}
+				\begin{split}
+					t'_{I/P,n}
+					& = \boldsymbol{w}_{I/P}^H\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\\
+					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H)\\
+					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{W}_{I/P})
+				\end{split}
+			\end{equation}
+			where $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$. Therefore, \ref{eq:z_k_waveform} rewrites as
+			\begin{equation}\label{eq:z_k_waveform_t}
+				\begin{split}
+					z
+					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t'_{I,0}+t'_{P,0})\\
+					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
+					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t'_{I,0}t'_{P,0}
+				\end{split}
+			\end{equation}
+			At iteration $k$, the second-order terms are approximated by first-order Taylor series as
+			\begin{equation}
+				\begin{split}
+					t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime \ (k)})^*
+					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime (k-1)})^*\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^* \\
+					& = 2 \Re \left\{\mathrm{Tr}((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(k)})\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(k)}\right) + \mathrm{Tr}(t_{I/P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\boldsymbol{W}_{I/P}^{(k)})\\
+					& \quad- t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*
+				\end{split}
+			\end{equation}
+			and
+			\begin{equation}
+				\begin{split}
+					t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime \ (k)}
+					& \approx t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime (k-1)} + t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime \ (k)} - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}\\
+					& = \mathrm{Tr}\left(t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{I,0}^{(k)}\right) + \mathrm{Tr}(t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{P,0}^{(k)}) - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+				\end{split}
+			\end{equation}
+			Therefore, we have
+			\begin{equation}\label{eq:z_waveform_approx}
+				\begin{split}
+					\tilde{z}(\boldsymbol{W}_I^{(k)},\boldsymbol{W}_P^{(k)},\rho^{(k-1)})
+					& = \mathrm{Tr}(\boldsymbol{A}_I^{(k)}\boldsymbol{W}_I^{(k)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(k)}\boldsymbol{W}_P^{(k)}) \\
+					& - \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (k-1)} (t_{I,n}^{\prime (k-1)})^* + t_{P,n}^{\prime (k-1)} (t_{P,n}^{\prime (k-1)})^* \\
+					& - \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+				\end{split}
+			\end{equation}
+			where the Hermitian matrices $\boldsymbol{A}_I^{(k)}$ and $\boldsymbol{A}_P^{(k)}$ are
+			\begin{equation}\label{eq:A_I,k}
+				\begin{split}
+					\boldsymbol{A}_I^{(k)}
+					& = \frac{k_2 \rho^{(k-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
+					& + \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\right) \\
+					& + \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+				\end{split}
+			\end{equation}
+			\begin{equation}\label{eq:A_P,k}
+				\begin{split}
+					\boldsymbol{A}_P^{(k)}
+					& = \frac{k_2 \rho^{(k-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
+					& + \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H \\
+					& + \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+				\end{split}
+			\end{equation}
+			Plug \ref{eq:z_waveform_approx} into problem \ref{op:temp5} and solve it by iterative interior-point method.
+Given the optimal waveform matrices $\boldsymbol{W}_I$ and $\boldsymbol{W}_P$, the best rank-1 solution $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ can be obtained through randomization method.
+Details are omitted here.
+The algorithm for the waveform optimization subproblem is summarized in Algorithm ~.
+
+			\begin{algorithm}
+				\caption{Waveform Optimization}
+				\label{alg:waveform}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\boldsymbol{V}$
+					\State \textbf{Initialize} $k=0$, $\boldsymbol{w}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\Repeat
+					\State $k = k + 1$
+					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(k)}$ by \ref{eq:A_I,k} and \ref{eq:A_P,k}
+					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(k)}$ and $\rho^{(k)}$ by solving problem \ref{op:temp5}
+					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
+					% \Until $\lVert \boldsymbol{W}_I^{(k)} - \boldsymbol{W}_I^{(k - 1)} \rVert_F / \lVert \boldsymbol{W}_I^{(k)} \rVert_F \le \epsilon$
+					\Until $R^{(k)}-R^{(k-1)} \le \epsilon$
+					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall r$
+					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
+					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r \ \forall r$ and corresponding matrices $\boldsymbol{W}_{I/P,r}=\boldsymbol{w}_{I/P,r}\boldsymbol{w}_{I/P,r}^H  \ \forall r$
+					\State Select the best solution pair $\boldsymbol{W}_{I,r}^\star, \boldsymbol{W}_{P,r}^\star$ for problem \ref{op:temp5} and corresponding $\boldsymbol{w}_{I,r}^\star, \boldsymbol{w}_{P,r}^\star$
+					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
+				\end{algorithmic}
+			\end{algorithm}
 
@@
 
-		% ? AO: optimize weights with given phase shifts
-		To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
-		\begin{equation}
-			\begin{split}
-				{h_{n_1}^*}{h_{n_2}}
-				&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
-				&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
-				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
-				&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
-			\end{split}
-		\end{equation}
-		where
-		\begin{equation}
-			\boldsymbol{R}_{n_1,n_2}=
-			\begin{bmatrix}
-				\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
-				h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
-			\end{bmatrix}
-		\end{equation}
-		On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries.
+		% % ? AO: optimize weights with given phase shifts
+		% To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
+		% \begin{equation}
+		% 	\begin{split}
+		% 		{h_{n_1}^*}{h_{n_2}}
+		% 		&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
+		% 		&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
+		% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
+		% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
+		% 	\end{split}
+		% \end{equation}
+		% where
+		% \begin{equation}
+		% 	\boldsymbol{R}_{n_1,n_2}=
+		% 	\begin{bmatrix}
+		% 		\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
+		% 		h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
+		% 	\end{bmatrix}
+		% \end{equation}
+		% On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries.
 It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
 Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
-		\begin{figure*}[b]
-			\hrule
-			\begin{equation}\label{eq:z_k_waveform}
-				\begin{split}
-					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
-					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
-				\end{split}
-			\end{equation}
-		\end{figure*}
-		We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
-		% and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
-		\begin{equation}\label{eq:z_k_su_compact}
-			\begin{split}
-				z
-				&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
-				&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
-				&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
-			\end{split}
-		\end{equation}
+		% \begin{figure*}[b]
+		% 	\hrule
+		% 	\begin{equation}\label{eq:z_k_waveform}
+		% 		\begin{split}
+		% 			z
+		% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
+		% 			% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+		% 			% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
+		% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
+		% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
+		% 		\end{split}
+		% 	\end{equation}
+		% \end{figure*}
+		% We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
+		% % and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
+		% \begin{equation}\label{eq:z_k_su_compact}
+		% 	\begin{split}
+		% 		z
+		% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
+		% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
+		% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
+		% 	\end{split}
+		% \end{equation}
 

### 2020-05-23 system-model.tex
:construction: Transmit signal

@@
 Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system.
+A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame.
 The signals reflected by IRS for two and more times are assumed negligible and thus not considered.
-A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame.
-A superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, are designed adaptively to maximize the rate-energy tradeoff \cite{Clerckx2018b}.
 Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}.
-Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with same reflection coefficients for all subbands.
+Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands.
+Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff.
 Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
-In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots with duration ratio $(1-\alpha)$ and $\alpha$ respectively.
-Hence, the achievable rate-energy region can be obtained through a direct time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$.
-The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design, since they are optimized individually in data and energy slots.
-In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$.
-As $\rho$ is coupled with waveform and IRS design, we investigate the rate-energy region by placing different rate constraints and optimizing waveform, PS ratio and reflectors accordingly.
-Perfect synchronization is assumed among the three parties in both scenario.
+In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\alpha)$ and $\alpha$ respectively.
+Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$.
+The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots.
+In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design.
+Perfect synchronization is assumed among the three parties in both scenarios.
 
 	\begin{subsection}{Transmitted Signal}
+		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
 		\begin{subsubsection} {Modulated Information Waveform}
-			Assume the carrier are evenly spaced with equal bandwidth $B_s$ such that the frequency of the $n$-th subband is $f_n=f_0+(n-1){\Delta}{f}$ ($n=1,\dots,N$).
-The information symbol $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$ of user $k$ over subband $n$ is a capacity-achieving i.i.d.
-Circular Symmetric Complex Gaussian (CSCG) variable with zero mean and unit variance.
-Therefore, the baseband (BB) transmit information signal at subband $n$ can be expressed as
-			\begin{equation}\label{eq:x_{I,n}(t)}
-				x_{I,n}(t)=\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}
+			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ over subband $n$, which follows a capacity-achieving i.i.d.
+Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$.
+The transmit information signal at time $t$ is
+			\begin{equation}\label{eq:x_I}
+				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
 			\end{equation}
-			where $w_{I,k,n}$ is the corresponding information weight.
-Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
-On top of this, the overall frequency weight is denoted as $w_{I,n}=\sum_k{w_{I,k,n}}$ and collected into $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N \times 1}$.
-The RF transmit information waveform at time $t$ writes as
-			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}]=[\boldsymbol{w}_{I,1}^T,\dots,\boldsymbol{w}_{I,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}] \in \mathbb{C}^{1 \times N}$.
-			% Let $\boldsymbol{W}_I=[\boldsymbol{w}_{I,1},\dots,\boldsymbol{w}_{I,N}] \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{I,n}=[w_{I,1,n},\dots,w_{I,K,n}]^T \in \mathbb{C}^{K \times 1}$.
-			\begin{equation}\label{eq:x_I(t)}
-				\begin{split}
-					x_I(t)
-					&=\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\\
-					&=\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}
-					% &=\Re\left\{\sum_{n=1}^N{x_{I,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}\\
-					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,k,n}\tilde{x}_{I,k,n}(t){e^{j2{\pi}{f_n}{t}}}}\right\}
-				\end{split}
-			\end{equation}
+			where $w_{I,n}=s_{I,n}e^{j\phi_{I,n}}$ collects the magnitude and phase of the information signal at frequency $n$.
+We further define the information waveform vector $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N{\times}1}$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Unmodulated Power Waveform}
-			As suggested in \cite{Clerckx2018b,Clerckx2016a}, we use deterministic multisine waveform to boost the harvested energy.
-It has no randomness over time such that the baseband transmit power signal at subband $n$ is
-			\begin{equation}\label{eq:x_{P,n}}
-				x_{P,n}=\sum_{k=1}^K{w_{P,k,n}}
+			With no randomness over time, the transmit power signal is
+			\begin{equation}\label{eq:x_P}
+				x_{P}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
 			\end{equation}
-			where $w_{P,k,n}$ is the corresponding power weight.
-Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]^T \in \mathbb{C}^{N \times K}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$.
-Similarly, the overall frequency weight is denoted as $w_{P,n}=\sum_k{w_{P,k,n}}$ and collected into $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N \times 1}$.
-The transmit power signal at time $t$ is given by
-			% Let $\boldsymbol{W}_P=[\boldsymbol{w}_{P,1},\dots,\boldsymbol{w}_{P,N}]=[\boldsymbol{w}_{P,1}^T,\dots,\boldsymbol{w}_{P,K}^T]^T \in \mathbb{C}^{K \times N}$ with $\boldsymbol{w}_{P,n}=[w_{P,1,n},\dots,w_{P,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{w}_{P,k}=[w_{P,k,1},\dots,w_{P,k,N}] \in \mathbb{C}^{1 \times N}$.
-			\begin{equation}\label{eq:x_P(t)}
-				\begin{split}
-					x_P(t)
-					&=\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\\
-					&=\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}
-					% &=\Re\left\{\sum_{n=1}^N{x_{P,n}{e^{j2{\pi}{f_n}{t}}}}\right\}\\
-					% &=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}{e^{j2{\pi}{f_n}{t}}}}\right\}
-				\end{split}
-			\end{equation}
+			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}$ includes the magnitude and phase of the $n$-th tone.
+Also, define the power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Superposed Waveform}
-			At time $t$, a superposition of the information and power waveform at subband $n$ writes as
+			The transmit signal at time $t$ over subband $n$ is
 			\begin{equation}\label{eq:x_n(t)}
@@
 		\end{equation}
-		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the determaxistic power component or constructing a translated codebook.
+		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
 	\end{subsection}

### 2020-05-23 system-model.tex
:construction: Transmit and receive signal

@@
 
-	\begin{subsection}{Transmitted Signal}
+	\begin{subsection}{Transmit Signal}
 		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
@@
 			\end{equation}
-			where $w_{I,n}=s_{I,n}e^{j\phi_{I,n}}$ collects the magnitude and phase of the information signal at frequency $n$.
-We further define the information waveform vector $\boldsymbol{w}_I=[w_{I,1},\dots,w_{I,N}]^T \in \mathbb{C}^{N{\times}1}$.
+			where $w_{I,k,n}=s_{I,k,n}e^{j\phi_{I,k,n}}$ collects the magnitude and phase of the information signal of user $k$ at frequency $n$.
+We further define the information waveform vector $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}]^T \in \mathbb{C}^{N{\times}1}$.
 		\end{subsubsection}
@@
 			\begin{equation}\label{eq:x_P}
-				x_{P}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
+				x_{P}=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}}{e^{j2{\pi}{f_n}{t}}}\right\}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
 			\end{equation}
-			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}$ includes the magnitude and phase of the $n$-th tone.
-Also, define the power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
+			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}=\sum_{k=1}^K{w_{P,k,n}}$ combines the magnitude and phase on the $n$-th power tone over all users.
+Also, collect $w_{P,n}$ into power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Superposed Waveform}
-			The transmit signal at time $t$ over subband $n$ is
-			\begin{equation}\label{eq:x_n(t)}
-				x_n(t)=\sum_{k=1}^K{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
+		Therefore, the superposed transmit signal at time $t$ over subband $n$ is
+		\begin{equation}\label{eq:x}
+			x(t)=\Re\left\{\sum_{n=1}^N\left(\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{equation}
-			Hence, the transmitted RF signal is
-			\begin{equation}\label{eq:x(t)}
-				x(t)=\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}
-				% x(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{(w_{I,k,n}\tilde{x}_{I,k,n}(t)+w_{P,k,n}){e^{j2{\pi}{f_n}{t}}}}\right\}
-			\end{equation}
-		\end{subsubsection}
+
 	\end{subsection}
@@
 
-	\begin{subsection}{Received Signal}
+	\begin{subsection}{Receive Signal}
 		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
-		\begin{equation}\label{eq:y_k(t)}
-			y_k(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}}(w_{I,j,n}\tilde{x}_{I,j,n}+w_{P,j,n}){e^{j2{\pi}{f_n}{t}}}
+		\begin{equation}\label{eq:y_k}
+			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left(\sum_{j=1}^K{w_{I,j,n}\tilde{x}_{I,j,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{equation}
-		with the information and power components of
-		\begin{equation}\label{eq:y_{I,k}(t)}
-			y_{I,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{I,j,n}\tilde{x}_{I,j,n}}{e^{j2{\pi}{f_n}{t}}}
-		\end{equation}
-		\begin{equation}\label{eq:y_{P,k}(t)}
-			y_{P,k}(t)=\sum_{j=1}^K\sum_{n=1}^N{h_{k,n}w_{P,j,n}}{e^{j2{\pi}{f_n}{t}}}
-		\end{equation}
-
 	\end{subsection}

### 2020-05-24 system-model.tex
:art: Reconstruct channel model

@@
 The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
+Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$.
+Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
 It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
@@
 	\begin{subsection}{Transmit Signal}
-		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
 		\begin{subsubsection} {Modulated Information Waveform}
-			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ over subband $n$, which follows a capacity-achieving i.i.d.
+			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ ($k=1,\dots,K$) over subband $n$, which follows a capacity-achieving i.i.d.
 Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$.
@@
 	\begin{subsection}{Composite Channel Model}
-		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R^H \in \mathbb{C}^{K \times NL}$ respectively.
-At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^H \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}^H=[\boldsymbol{h}_{R,1,n},\dots,\boldsymbol{h}_{R,K,n}]^H \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}^H=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$.
-Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^H \in \mathbb{C}^{L \times 1}$.
-To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$.
-Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$.
-Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching.
-On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
-Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$.
-The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel.
-Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
-		\begin{equation}\label{eq:H}
-			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R^H\boldsymbol{\Theta}\boldsymbol{H}_I
+		Denote the frequency response of the AP-user $k$ direct link as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}]^T \in \mathbb{C}^{N \times 1}$.
+Let $[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}] \in \mathbb{C}^{L \times N}$ be the frequency response of AP-IRS incident channel, where $\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$ corresponds to the $n$-th incident channel.
+Similarly, let $[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}]^H \in \mathbb{C}^{N \times L}$ be the frequency response of IRS-user $k$ reflective channel, where $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$ corresponds to the $n$-th reflective channel.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the received signal by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\beta_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+On top of this, the IRS matrix is constructed by collecting the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
+The IRS-aided link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user $k$ channel, which for user $k$ over subband $n$ is
+		\begin{equation}\label{eq:h_{E,k,n}}
+			h_{E,k,n} = \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{h}_{I,n} = \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
 		\end{equation}
-		whose $(k,n)$-th entry
-		\begin{equation}\label{eq:h_{k,n}}
-			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
+		where $\boldsymbol{v}_{k,n}^H \triangleq \boldsymbol{h}_{R,k,n}^H \mathrm{diag}(\boldsymbol{h}_{I,n}) \in \mathbb{C}^{1 \times L}$ and $\boldsymbol{\phi}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}] \in \mathbb{C}^{L \times 1}$.
+Both direct and extra link contributes to the corresponding composite channel as
+		\begin{equation}
+			h_{k,n} = h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
 		\end{equation}
-		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
-		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
-		\begin{equation}\label{eq:h_n}
-			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
-		\end{equation}
-		Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Phi}_n^H=\boldsymbol{H}_{R,n}^H\mathrm{diag}\left\{\boldsymbol{h}_{I,n}\right\} \in \mathbb{C}^{K \times L}$.
-Therefore, \ref{eq:h_n} rewrites as
-		\begin{equation}
-			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}
+		Let $\boldsymbol{V}_k^H=[\boldsymbol{v}_{k,1},\dots,\boldsymbol{v}_{k,N}]^H \in \mathbb{C}^{N \times L}$, the extra link for user $k$ is $\boldsymbol{h}_{E,k}=[h_{E,k,1},\dots,h_{E,k,N}]^T=\boldsymbol{V}_k^H \boldsymbol{\phi} \in \mathbb{C}^{N \times 1}$.
+Therefore, the composite channel of user $k$ is
+		\begin{equation}\label{eq:h_k}
+			\boldsymbol{h}_k = \boldsymbol{h}_{D,k} + \boldsymbol{V}_k^H \boldsymbol{\phi}
 		\end{equation}

### 2020-05-25 system-model.tex
:art: Fix achievable rate

@@
 		\end{equation}
+		which can be divided into
+		\begin{align}\label{eq:y_{I/P,k}}
+			y_{I,k}(t) & = \Re\left\{\sum_{j=1}^K\sum_{n=1}^N{h_{{k,n}}}{w_{I,j,n}\tilde{x}_{I,j,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
+			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}w_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
+		\end{align}
 	\end{subsection}
@@
 	\begin{subsection}{Information Decoder}
-		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$.
-Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
-		\begin{equation}\label{eq:gamma_{k,n}}
-			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
+		% ? OFDM interference
+		One major benefit of the superposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
+		\begin{equation}\label{eq:R_k}
+			R_k(\{\boldsymbol{w}_{I,k}\},\boldsymbol{\phi},\rho)=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,k,n} \rvert^2}{\sigma_n^2}\right)}
 		\end{equation}
-		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$.
-Therefore, the achievable rate of user $k$ is expressed as
-		\begin{equation}\label{eq:R_k}
-			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta}_0,\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
-		\end{equation}
-		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
+		where $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion on tone $n$.
+Rate \ref{eq:R_k} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
 	\end{subsection}
@@
 	\begin{subsection}{Energy Harvester}
-		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ have different influence on the output DC current.
-Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency of the harvester output DC current on the received waveform as
+		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights the dependency of harvester output DC current on the received waveform of user $k$ as
 		\begin{equation}\label{eq:i_k}
-			i_k\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
+			i_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
 		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
-Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $w_{I,k,n}$, $w_{P,k,n}$ are thus optimized such that the randomness comes from the input distribution $\tilde{x}_{k,n}$.
-Therefore, we first extract the DC component based on $h_{k,n}$, $w_{I,k,n}$, $w_{P,k,n}$ by $\mathcal{A}\left\{.\right\}$ and then take the expectation over $\tilde{x}_{k,n}$ by $\mathcal{E}\left\{.\right\}$.
-With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ and the related terms has zero contribution to DC components.
-\cite{Clerckx2016a} also demonstrated that to maximize $i_k$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
+For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,k,n}$.
+
+		With the assumption of evenly spaced frequencies, we have $\mathcal{E}\left\{y_k(t)^i\right\}=0 \ \forall i \ \mathrm{odd}$ such that the related terms has no contribution to DC components.
+For simplicity, we truncate the infinite series to the $n_0$-th order.
+Maximizing a truncated \ref{eq:i_k} is equivalent to maximizing a monotonic function \cite{Clerckx2016a}
 		\begin{equation}\label{eq:z_k}
-			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta}_0,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
+			z_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
 		\end{equation}
 		where $k_i=i_s/i!(nv_t)^i$.
-We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer.
-Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
-It is noteworthy that modulation provides a power gain to the nonlinear terms in the output DC current as $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$.
+We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy harvest.
+Nonzero terms are given in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end}.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain in the nonlinear terms of the output DC current.
+On top of this, the current expression \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.
 		\begin{figure*}[b]
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\
-				%  & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                      \\
-				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                         \\
-				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
+				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:z_k_terms_begin}\\
+				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}                       \\
-				%  & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})} \\
-				 & =\frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})} \\
-				%  & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
-				%  & \quad\left[w_{I,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{I,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*                                                                                                                           \\
+				& = \frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}\\
+				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})}\\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}                                                                                                                                                                                                   \\
-				%  & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                     \\
-				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                         \\
-				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\
+				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}\\
+				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}                       \\
-				%  & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}  \\
-				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}
-				\label{eq:A{y_{P,k}**4'}}
-				%  & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
-				%  & \quad\left[w_{P,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
+				& = \frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}\\
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}\label{eq:z_k_terms_end}
 			\end{align}
 		\end{figure*}
-		Therefore, \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.
 		\begin{figure*}[b]
@@
 				\begin{split}
-					% z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)
 					z_k
-					&={k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
-					% &=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
-					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
-					% &\quad+\frac{3}{2}{k_4'}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})\\
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
+					& = {k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
+					& = \frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
+					& \quad+ \frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
+					& \quad+ \frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
 				\end{split}

### 2020-05-25 system-model.tex
:construction: Information waveform

@@
 		\end{equation}
-		where $\boldsymbol{v}_{k,n}^H \triangleq \boldsymbol{h}_{R,k,n}^H \mathrm{diag}(\boldsymbol{h}_{I,n}) \in \mathbb{C}^{1 \times L}$ and $\boldsymbol{\phi}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}] \in \mathbb{C}^{L \times 1}$.
+		where $\boldsymbol{v}_{k,n}^H=\boldsymbol{h}_{R,k,n}^H \mathrm{diag}(\boldsymbol{h}_{I,n}) \in \mathbb{C}^{1 \times L}$ and $\boldsymbol{\phi}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}] \in \mathbb{C}^{L \times 1}$.
 Both direct and extra link contributes to the corresponding composite channel as
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:z_k_terms_begin}\\
-				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}\\
+				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*} = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}\label{eq:z_k_terms_begin}\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
@@
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}\\
-				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}\\
+				& = \frac{1}{2}\sum_n{(h_{k,n}w_{P,n})(h_{k,n}w_{P,n})^*}\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				& = \frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}\\
-				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}\label{eq:z_k_terms_end}
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{n_1}})(h_{k,{n_2}}w_{P,{n_2}})(h_{k,{n_3}}w_{P,{n_3}})^*(h_{k,{n_4}}w_{P,{n_4}})^*}\label{eq:z_k_terms_end}
 			\end{align}

### 2020-05-25 system-model.tex
:construction: Output DC current

@@
 Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
+Suppose each subband is allocated to one user per time slot.
 It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
@@
 Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
-In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\alpha)$ and $\alpha$ respectively.
-Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$.
-The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots.
+In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\lambda)$ and $\lambda$ respectively.
+Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\lambda=1$ and wireless information transfer (WIT) with $\lambda=0$.
+The adjustment of $\lambda$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots.
 In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design.
@@
 	\begin{subsection}{Transmit Signal}
-		\begin{subsubsection} {Modulated Information Waveform}
-			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ ($k=1,\dots,K$) over subband $n$, which follows a capacity-achieving i.i.d.
-Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$.
-The transmit information signal at time $t$ is
-			\begin{equation}\label{eq:x_I}
-				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
+		Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which belongs to one user at time $t$ and follows a capacity-achieving i.i.d.
+Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
+Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0 \ \forall k' \ne k$.
+Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$.
+The superposed transmit signal at time $t$ is
+		\begin{equation}\label{eq:x}
+			x(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{equation}
-			where $w_{I,k,n}=s_{I,k,n}e^{j\phi_{I,k,n}}$ collects the magnitude and phase of the information signal of user $k$ at frequency $n$.
-We further define the information waveform vector $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}]^T \in \mathbb{C}^{N{\times}1}$.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Unmodulated Power Waveform}
-			With no randomness over time, the transmit power signal is
-			\begin{equation}\label{eq:x_P}
-				x_{P}=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{P,k,n}}{e^{j2{\pi}{f_n}{t}}}\right\}=\Re\left\{\sum_{n=1}^N{w_{P,n}}{e^{j2{\pi}{f_n}{t}}}\right\}
-			\end{equation}
-			where $w_{P,n}=s_{P,n}e^{j\phi_{P,n}}=\sum_{k=1}^K{w_{P,k,n}}$ combines the magnitude and phase on the $n$-th power tone over all users.
-Also, collect $w_{P,n}$ into power waveform vector $\boldsymbol{w}_P=[w_{P,1},\dots,w_{P,N}]^T \in \mathbb{C}^{N{\times}1}$.
-		\end{subsubsection}
-
-		Therefore, the superposed transmit signal at time $t$ over subband $n$ is
-		\begin{equation}\label{eq:x}
-			x(t)=\Re\left\{\sum_{n=1}^N\left(\sum_{k=1}^K{w_{I,k,n}\tilde{x}_{I,k,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
-		\end{equation}
-
+		where $w_{I/P,n}=s_{I/P,n}e^{j\psi_{I/P,n}}$ collects the magnitude and phase of the information and power signal at frequency $n$.
+We further define the waveform vectors $\boldsymbol{w}_{I/P}=[w_{I/P,1},\dots,w_{I/P,N}]^T \in \mathbb{C}^{N{\times}1}$.
 	\end{subsection}
@@
 		\begin{equation}
-			h_{k,n} = h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
+			h_{k,n} = A_{k,n} e^{j\bar{\psi}_{k,n}}= h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
 		\end{equation}
+		where $A_{k,n}$ and $\bar{\psi}_{k,n}$ are the amplitude and phase of the composite channel of user $k$ at subband $n$.
 Let $\boldsymbol{V}_k^H=[\boldsymbol{v}_{k,1},\dots,\boldsymbol{v}_{k,N}]^H \in \mathbb{C}^{N \times L}$, the extra link for user $k$ is $\boldsymbol{h}_{E,k}=[h_{E,k,1},\dots,h_{E,k,N}]^T=\boldsymbol{V}_k^H \boldsymbol{\phi} \in \mathbb{C}^{N \times 1}$.
@@
 	\begin{subsection}{Receive Signal}
-		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
+		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and IRS-aided links as
 		\begin{equation}\label{eq:y_k}
-			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left(\sum_{j=1}^K{w_{I,j,n}\tilde{x}_{I,j,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{equation}
@@
 		\begin{align}\label{eq:y_{I/P,k}}
-			y_{I,k}(t) & = \Re\left\{\sum_{j=1}^K\sum_{n=1}^N{h_{{k,n}}}{w_{I,j,n}\tilde{x}_{I,j,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
+			y_{I,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}{w_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
 			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}w_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
@@
 		% ? OFDM interference
-		One major benefit of the superposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
+		A major benefit of the superposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
 		\begin{equation}\label{eq:R_k}
-			R_k(\{\boldsymbol{w}_{I,k}\},\boldsymbol{\phi},\rho)=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,k,n} \rvert^2}{\sigma_n^2}\right)}
+			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,n} \rvert^2}{\sigma_n^2}\right)}
 		\end{equation}
@@
 		\begin{equation}\label{eq:i_k}
-			i_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
+			i_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
 		\end{equation}
@@
 		\begin{equation}\label{eq:z_k}
-			z_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
+			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
 		\end{equation}
 		where $k_i=i_s/i!(nv_t)^i$.
-We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy harvest.
-Nonzero terms are given in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end}.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain in the nonlinear terms of the output DC current.
-On top of this, the current expression \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.
+We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on waveform design.
+Nonzero terms in \ref{eq:z_k} are given in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end}.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+On top of this, the current expression \ref{eq:z_k} reduces to \ref{eq:z_k_expand}.
 		\begin{figure*}[b]
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*} = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}\label{eq:z_k_terms_begin}\\
+				& = \frac{1}{2}\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\label{eq:z_k_terms_begin}\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				& = \frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}\\
-				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})}\\
+				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{n_1}})(h_{k,{n_2}}w_{I,{n_2}})(h_{k,{n_3}}w_{I,{n_3}})^*(h_{k,{n_4}}w_{I,{n_4}})^*}\\
+				& = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^*\\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
 				& = \frac{1}{2}\sum_n{(h_{k,n}w_{P,n})(h_{k,n}w_{P,n})^*}\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{n_1}})(h_{k,{n_2}}w_{P,{n_2}})(h_{k,{n_3}}w_{P,{n_3}})^*(h_{k,{n_4}}w_{P,{n_4}})^*}\label{eq:z_k_terms_end}
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{n_1}})(h_{k,{n_2}}w_{P,{n_2}})(h_{k,{n_3}}w_{P,{n_3}})^*(h_{k,{n_4}}w_{P,{n_4}})^*}\\
+				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^*\label{eq:z_k_terms_end}
 			\end{align}
@@
 			\hrule
-			\begin{equation}\label{eq:z_k_truncated}
-				\begin{split}
-					z_k
-					& = {k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
-					& = \frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
-					& \quad+ \frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
-					& \quad+ \frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
-				\end{split}
-			\end{equation}
+			\begin{align}
+				z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
+				& = \beta_2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
+				& = \frac{1}{2}\beta_2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\\
+				& = \frac{1}{2}\beta_2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)
+			\end{align}
 		\end{figure*}

### 2020-05-26 system-model.tex
:triangular_flag_on_post: Algorithm on FS-IRS

@@
 \input{packages.tex}
+\input{commands.tex}
 
@@
 		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
-For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,k,n}$.
+For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,n}$.
 
@@
 We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on waveform design.
-Nonzero terms in \ref{eq:z_k} are given in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end}.
 Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-On top of this, the current expression \ref{eq:z_k} reduces to \ref{eq:z_k_expand}.
+
+		For simplicity, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ as waveform matrices and channel matrix of user $k$.
+Let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{W}_{I/P}$, $\boldsymbol{H}_k$ and null the remaining entries, respectively.
+Denote $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.	On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
 		\begin{figure*}[b]
@@
 				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{n_1}})(h_{k,{n_2}}w_{P,{n_2}})(h_{k,{n_3}}w_{P,{n_3}})^*(h_{k,{n_4}}w_{P,{n_4}})^*}\\
-				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^*\label{eq:z_k_terms_end}
+				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^*\label{eq:z_k_terms_end}
 			\end{align}
@@
 				z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
-				& = \beta_2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
-				& = \frac{1}{2}\beta_2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\\
-				& = \frac{1}{2}\beta_2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)
+				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_k_channel}\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_k_waveform}
 			\end{align}
@@
 	\begin{subsection}{Weighted Sum Rate-Energy Region}
-		We define the achievable WSR-E region as
+		Define the achievable WSR-E region as
 		\begin{equation}
@@
 				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
-				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
-				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
+				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
 			\end{split}
 		\end{equation}
-		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
+		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
 	\end{subsection}
@@
 	\begin{subsection}{Single-User Optimization}
-		In this section, we first characterize the rate-energy region in the single-user setup.
-Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$.
-The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
-		\begin{maxi}
-			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
-			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
+		Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$.
+We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
+		\begin{maxi!}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
 			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
-			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
-			% \addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
-		\end{maxi}
-		Problem \ref{op:1} is intricate due to the non-convex rate function, unit-modulus constraint, and non-convex DC current requirement with coupled variables.
+			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
+			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
+		\end{maxi!}
+		Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables.
+In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS respectively.
 
 		\begin{subsubsection}{Frequency-Selective IRS}
-			In frequency-selective IRS, each element is expected to provide adjustable subband-dependent reflection coefficients such that the total degree of freedom (DoF) of IRS is $NL$.
-Therefore, $\boldsymbol{v}_n$ replaces $\boldsymbol{v}$ in \ref{op:1}.
-Note that $\lvert{(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{\Phi}_n^H\boldsymbol{v}_nw_{I,n}}\rvert$ where the equality holds if and only if the direct and IRS-aided links are aligned by
-			\begin{equation}
+			Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients.
+Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total degree of freedom (DoF) of $NL$.
+Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned.
+Therefore, we choose the phase shift of element $l$ at subband $n$ as
+			\begin{equation}\label{eq:theta}
 				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
 			\end{equation}
-			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario.
-On top of this, it can be observed from \ref{eq:gamma_{k,n}}, \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal phase of information and power waveforms are matched to composite frequency response as
-			\begin{equation}\label{eq:phi_n}
-				\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
+			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, and the phase of the composite channel equals that of the direct channel.
+Moreover, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
+			\begin{equation}\label{eq:psi}
+				\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=\bar{\psi}_{n}
 			\end{equation}
-			With all the phases determined, the original problem \ref{op:1} is reduced to
-			\begin{maxi}
-				% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
+			By such a phase selection, we have
+			\begin{equation}
+				\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert = \lvert h_{D,n} \rvert \lvert w_{I,n} \rvert + \vert \boldsymbol{v}_n^H\boldsymbol{\phi}_n \rvert \lvert w_{I,n} \rvert
+			\end{equation}
+			Therefore, the original problem \ref{op:su} is reduced to an waveform magnitude optimization problem
+			\begin{maxi!}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:su_gp}}{}
 				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
-			\end{maxi}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \ge \bar{R}}
+			\end{maxi!}
 			\begin{figure*}[b]
@@
 					\begin{split}
-						z
-						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
-						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
+						z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
+						&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
+						&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
+						&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
 					\end{split}
@@
 			\end{figure*}
-			with $z$ given by \ref{eq:z_gp}. It can be transformed to an equivalent problem by introducing an auxiliary variable $t_0$
+			with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t'$ and transform problem \ref{op:su_gp} into
+			\begin{mini!}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t'}{\frac{1}{t'}}{\label{op:su_gp_1}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
+				\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
+				\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \le 1}
+			\end{mini!}
+			Problem \ref{op:su_gp_1} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
+The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
 			\begin{mini}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:3}}{}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:su_gp_2}}{}
 				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{\frac{t_0}{\prod_{n}{\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)}}\le{1}}
-				\addConstraint{\frac{\bar{z}}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\le{1}}
+				\addConstraint{{t'}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
+				\addConstraint{2^{\bar{R}}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
+				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{mini}
-			\ref{op:3} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
-The basic idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
-Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{{m_P}=1}^{M_P}{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:3} is equivalent to
-			% $1+\bar{\rho}{A_n^2}{s_{I,n}^2}/\sigma_n^2=\sum_{{m_{I,n}}=1}^{M_{I,n}}{g_{I,m_{I,n}}(\boldsymbol{s}_I,\bar{\rho})}$
-			\begin{mini}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:4}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{{t_0}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
-				\addConstraint{\bar{z}\prod_{m_P}{\left(\frac{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m_P}}\right)^{-\gamma_{P,m_P}}}\le{1}}
-				\addConstraint{\rho+\bar{\rho}\le{1}}
-			\end{mini}
-			where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m_P} \ge 0,\forall m_P=1,\dots,M_P$ and $\sum_{{m_P}=1}^{M_P}{\gamma_{m_P}}=1$.
-As suggested in \cite{Clerckx2018b}, the tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require iterative update.
-At iteration $i$, we choose
+			where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m} \ge 0 \ \forall m$, and $\sum_{m=1}^{M}{\gamma_m}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require successive update.
+At iteration $i$, we choose \cite{Clerckx2018b}
 			\begin{align}
-				\gamma_{I,n,1}^{(i)} & =\frac{1}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},                                                                         &  & n=1,\dots,N,    \\
-				\gamma_{I,n,2}^{(i)} & =\frac{\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},           &  & n=1,\dots,N,    \\
-				\gamma_{P,m_P}^{(i)} & =\frac{g_{P,m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}, &  & m_P=1,\dots,M_P
+				\gamma_{I,n,1}^{(i)} & = \left. 1 \middle/ \left(1+\frac{\bar{\rho}^{(i-1)}{A_n^2}(s_{I,n}^{(i-1)})^2}{\sigma_n^2}\right) \right.\label{eq:gamma_I_1}\\
+				\gamma_{I,n,2}^{(i)} & = 1 - \gamma_{I,n,1}^{(i)}\label{eq:gamma_I_2}\\
+				\gamma_{P,m}^{(i)} & =\frac{g_{P,m}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
 			\end{align}
-			and then solve problem \ref{op:4}.
+			and then solve problem \ref{op:su_gp_2}. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
+			\begin{algorithm}
+				\caption{FS-IRS: Waveform Amplitude Optimization}
+				\label{al:fs_waveform}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $P, \bar{R}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
+					\Repeat
+					\State $i \leftarrow i + 1$
+					\State Update GM exponents $\{\gamma_{I,n}^{(i)},\gamma_{P}^{(i)}\}$ by \ref{eq:gamma_I_1} -- \ref{eq:gamma_P}
+					\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and splitting ratio $\rho^{(i)}, \bar{\rho}^{(i)}$ by solving problem \ref{op:su_gp_2}
+					\State Compute output DC current $z^{(i)}$ by \ref{eq:z_gp}
+					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State \textbf{Output} $\boldsymbol{s}_{I/P}^{\star}, \rho^{\star}, z^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
 		\end{subsubsection}

### 2020-05-27 system-model.tex
:construction: Phase shift optimization

@@
 Let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{W}_{I/P}$, $\boldsymbol{H}_k$ and null the remaining entries, respectively.
-Denote $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.	On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
+Due to the positive definiteness of $\boldsymbol{W}_{I/P}$ and $\boldsymbol{H}_k$, we have $\boldsymbol{W}_{I/P,-n}=\boldsymbol{W}_{I/P,n}^H$ and $\boldsymbol{H}_{k,-n}=\boldsymbol{H}_{k,n}^H$.
+Let $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.
+On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
 		\begin{figure*}[b]
@@
 	\end{subsection}
-\end{section}
 
-\begin{section}{Problem Formulation}
-	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
 	\begin{subsection}{Weighted Sum Rate-Energy Region}
-		Define the achievable WSR-E region as
+		Define the achievable weighted sum rate-energy (WSR-E) region as
 		\begin{equation}
@@
 	\end{subsection}
+\end{section}
 
-	\begin{subsection}{Single-User Optimization}
+\begin{section}{Single-User Optimization}
 	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$.
@@
 	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables.
-In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS respectively.
+In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
 
-		\begin{subsubsection}{Frequency-Selective IRS}
+	\begin{subsection}{Frequency-Selective IRS}
 		Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients.
@@
 		\end{algorithm}
-		\end{subsubsection}
+	\end{subsection}
 
-		\begin{subsubsection}{Frequency-Flat IRS}
+	\begin{subsection}{Frequency-Flat IRS}
 		In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
@@
 			\begin{split}
-					\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2
-					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
-					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})
+				\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
+				&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
+				&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
 			\end{split}
@@
 			\begin{bmatrix}
-					\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h_{D,n}} \\
-					h_{D,n}^*{\boldsymbol{\Phi}_n^H}         & h_{D,n}^*{h_{D,n}}
+				\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
+				h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
 			\end{bmatrix},
-				\quad \bar{\boldsymbol{v}}=\
+			\quad \bar{\boldsymbol{\phi}}=\
 			\begin{bmatrix}
-					\boldsymbol{v} \\
+				\boldsymbol{\phi} \\
 				t
 			\end{bmatrix},
-				\quad \bar{\boldsymbol{V}}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H
+			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
 		\end{equation}
-			Hence, \ref{op:1} is transformed to
-			\begin{maxi}
-				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho)\ge{\bar{z}}}
-				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
-				\addConstraint{\boldsymbol{V}\succeq{0}}
-				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
-			\end{maxi}
+		with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$.
+On top of this, the outer product of composite channel rewrites as
+		\begin{equation}
+			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}
+		\end{equation}
+		where $\boldsymbol{R}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
+Hence, the output current \ref{eq:z_k_channel} can be reformulated as $z(\boldsymbol{\Phi})$ (details given in section \ref{se:fs_irs}).
 To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.
 
-			% ? AO: optimize phase shifts with given waveform
-			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
-			\begin{maxi}
-				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp4}}{}
-				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
-				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
-				\addConstraint{\boldsymbol{V}\succeq{0}}
-				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
-			\end{maxi}
-			To tackle the non-convex current constraint, we collect the channel matrices into $\boldsymbol{\Phi}^H=[\boldsymbol{\Phi}_1,\dots,\boldsymbol{\Phi}_N]^H \in \mathbb{C}^{N \times L}$ and $\boldsymbol{h}=\boldsymbol{h}_D+\boldsymbol{\Phi}^H\boldsymbol{v} \in \mathbb{C}^{N \times 1}$.
-The fixed waveform matrices are defined as $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$.
-On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and null the remaining entries.
-Due to the positive definiteness of $\boldsymbol{M}_{I/P}$, we have $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
-Hence, the output current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
-			\begin{figure*}[b]
-				\hrule
-				\begin{equation}\label{eq:z_k_irs}
-					\begin{split}
-						z
-						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
-						% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-						% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^*+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^*}\\
-						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
-					\end{split}
-				\end{equation}
-			\end{figure*}
-			We further simplify it by introducing auxiliary variables
+		\begin{subsubsection}{Phase shift optimization}\label{se:fs_irs}
+			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:su} reduces to
+			\begin{maxi!}
+				{\boldsymbol{\boldsymbol{\Phi}}}{z(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
+				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
+			\end{maxi!}
+			Introduce auxiliary variables
 			\begin{equation}\label{eq:t}
@@
 					t_{I/P,n}
-					&=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}\\
-					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{M}_{I/P,n})\\
-					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{V}\boldsymbol{R}\boldsymbol{M}_{I/P,n})\\
-					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H\boldsymbol{V})\\
-					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{V})
+					&=\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*\boldsymbol{h}\\
+					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)\\
+					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*)\\
+					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H\boldsymbol{\Phi})\\
+					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
 				\end{split}
 			\end{equation}
-			where $\boldsymbol{R}^H=[\boldsymbol{\Phi}^H,\boldsymbol{h}_D] \in \mathbb{C}^{N \times (L+1)}$ and $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{M}_{I/P,n}\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, \ref{eq:z_k_irs} rewrites as
-			\begin{equation}\label{eq:z_k_irs_t}
+			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
+			\begin{equation}\label{eq:z_irs}
 				\begin{split}
-					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
+					z(\boldsymbol{\Phi})
+					&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
+					&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
+					&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
 				\end{split}
 			\end{equation}
-
-			% It holds that $t_{I/P,n}^*t_{I/P,n}=t_{I/P,-n}^*t_{I/P,-n}$ since $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$.
-On top of this, denote $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{(N-1) \times 1}$ and rewrite \ref{eq:z_k_irs} as
-			% \begin{equation}\label{eq:z_k_irs_t}
-			% 	\begin{split}
-			% 		z
-			% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
-			% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(2t_{I,0}^*t_{I,0}+t_{P,0}^*t_{P,0}+4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P)\\
-			% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
-			% 	\end{split}
-			% \end{equation}
-			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_k_irs_t}.
-Based on the variables optimized at iteration $k - 1$, the local approximations at iteration $k$ are \cite{Adali2010}
+			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_irs}.
+Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
 			\begin{equation}
 				\begin{split}
-					t_{I/P,n}^{(k)} (t_{I/P,n}^{(k)})^*
-					& \approx 2 \Re\left\{t_{I/P,n}^{(k)} (t_{I/P,n}^{(k-1)})^*\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right)\right\} - t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{(k-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{V}^{(k)}\right) + \mathrm{Tr}(t_{I/P,n}^{(k-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{V}^{(k)})\\
-					& \quad- t_{I/P,n}^{(k-1)} (t_{I/P,n}^{(k-1)})^*
+					t_{I/P,n}^{(i)} (t_{I/P,n}^{(i)})^*
+					& \approx 2 \Re\left\{t_{I/P,n}^{(i)} (t_{I/P,n}^{(i-1)})^*\right\} - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^* \\
+					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\\
+					& \quad - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\\
+					& \quad + \mathrm{Tr}(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)})\\
+					& \quad- t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*
 				\end{split}
@@
 				\begin{split}
-					t_{I,0}^{(k)} t_{P,0}^{(k)}
-					& \approx t_{I,0}^{(k)} t_{P,0}^{(k-1)} + t_{I,0}^{(k-1)} t_{P,0}^{(k)} - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}\\
-					& = \mathrm{Tr}(t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0}\boldsymbol{V}^{(k)}) + \mathrm{Tr}(t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0}\boldsymbol{V}^{(k)}) - t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}
+					t_{I,0}^{(i)} t_{P,0}^{(i)}
+					& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\\
+					& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\\
+					& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
 				\end{split}
 			\end{equation}
-			The second approximation holds since $t_{I/P,0}$ are real. Therefore, we have
+			Therefore, the approximated current function at iteration $i$ is
 			\begin{equation}\label{eq:z_irs_approx}
 				\begin{split}
-					\tilde{z}(\boldsymbol{V}^{(k)})
-					& = \mathrm{Tr}(\boldsymbol{A}^{(k)}\boldsymbol{V}^{(k)}) \\
-					& - \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(k-1)} (t_{I,n}^{(k-1)})^* + t_{P,n}^{(k-1)} (t_{P,n}^{(k-1)})^* \\
-					& - \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{(k-1)} t_{P,0}^{(k-1)}
+					\tilde{z}(\boldsymbol{\Phi}^{(i)})
+					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)}) \\
+					& - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
+					& - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
 				\end{split}
 			\end{equation}
-			where the Hermitian matrix $\boldsymbol{A}^{(k)}$ is
-			\begin{equation}\label{eq:A_k}
+			where the corresponding Hermitian matrix $\boldsymbol{A}^{(i)}$ is
+			\begin{equation}\label{eq:A}
 				\begin{split}
-					\boldsymbol{A}^{(k)}
-					& = \frac{k_2 \rho R_{\text{ant}}}{2}(\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
-					& \quad+ \frac{3 k_4 \rho^2 R_{\text{ant}}^2}{8}\sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(k-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(k-1)}\boldsymbol{C}_{I,n}^H\right)\\
-					& \quad \quad + \left((t_{P,n}^{(k-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(k-1)}\boldsymbol{C}_{P,n}^H\right)\\
-					& \quad+ \frac{3{k_4}{\rho^2}{R_{\text{ant}}^2}}{2} (t_{P,0}^{(k-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(k-1)}\boldsymbol{C}_{P,0})
+					\boldsymbol{A}^{(i)}
+					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
+					& \quad+ \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(i-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(i-1)}\boldsymbol{C}_{I,n}^H\right)\\
+					& \quad \quad + \left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\right)\\
+					& \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})
 				\end{split}
 			\end{equation}
-			Plug \ref{eq:z_irs_approx} into problem \ref{op:temp4} and solve it by iterative interior-point method.
-Denote the optimal IRS matrix as $\boldsymbol{V}^{\star}$.
-If $\mathrm{rank}(\boldsymbol{V}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{v}}^\star$ is attained by eigenvalue decomposition (EVD).
-Otherwise, a best feasible candidate $\bar{\boldsymbol{v}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}.
-First, we perform EVD on $\boldsymbol{V}^{\star}$ as $\boldsymbol{V}^{\star}=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}\boldsymbol{U}_{\boldsymbol{V}^{\star}}^H$.
-Then, we generate $R$ random CSCG vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{v}}_r=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$.
-Next, the optimal solution $\bar{\boldsymbol{v}}^\star$ is approximated by the one achieving maximum objective value of \ref{op:temp4}.
-Finally, we can retrieve the phase shift as $\theta_l=\arg(v_l^\star/v_{L+1}^\star)$.
-The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{alg:irs}.
-
+			We then plug \ref{eq:z_irs_approx} into problem \ref{op:su_irs}, relax the rank constraint \ref{co:irs_rank}, and obtain the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ by interior-point method.
+If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD).
+Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}.
+First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
+Then, generate $R$ CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$.
+Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}.
+Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star)$.
+The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
 			\begin{algorithm}
-				\caption{IRS Optimization}
-				\label{alg:irs}
+				\caption{FF-IRS: Phase Shift Optimization}
+				\label{al:ff_irs}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
-					\State \textbf{Initialize} $k=0$, $\boldsymbol{V}^{(0)}$, $t_{I/P,n}^{(0)} \ \forall n$
+					\State \textbf{Input} $\bar{R},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
+					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
 					\Repeat
-					\State $k = k + 1$
-					\State Update SDR matrix $\boldsymbol{A}^{(k)}$ by \ref{eq:A_k}
-					\State Obtain IRS matrix $\boldsymbol{V}^{(k)}$ by solving problem \ref{op:temp4}
-					\State Update auxiliary $t_{I/P,n}^{(k)} \forall n$ by \ref{eq:t} for SCA
-					% \Until $\lVert \boldsymbol{V}^{(k)} - \boldsymbol{V}^{(k - 1)} \rVert_F / \lVert \boldsymbol{V}^{(k)} \rVert_F \le \epsilon$
-					\Until $R^{(k)}-R^{(k-1)} \le \epsilon$
+					\State $i \leftarrow i + 1$
+					\State Update SDR matrix $\boldsymbol{A}^{(i)}$ by \ref{eq:A}
+					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
+					\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
+					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
+					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
 					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall r$
-					\State Perform EVD $\boldsymbol{V}^{\star}=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}\boldsymbol{U}_{\boldsymbol{V}^{\star}}^H$
-					\State Construct candidate IRS vectors $\bar{\boldsymbol{v}}_r=\boldsymbol{U}_{\boldsymbol{V}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{V}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r \forall r$ and corresponding matrices $\boldsymbol{V}_r=\bar{\boldsymbol{v}}_r\bar{\boldsymbol{v}}_r^H  \ \forall r$
-					\State Select the best solution $\boldsymbol{V}_r^\star$ for problem \ref{op:temp4} and corresponding $\boldsymbol{v}_r^\star$
-					\State Compute IRS phase shift by $\theta_l=\arg(v_l^\star/v_{L+1}^\star) \ \forall l$
-					\State \textbf{Output} $\theta_l, l = 1 , \dots L$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$ and corresponding matrices $\boldsymbol{\Phi}_r=\bar{\boldsymbol{\phi}}_r\bar{\boldsymbol{\phi}}_r^H  \ \forall r$
+					\State Select the best solution $\boldsymbol{\Phi}^\star$ for problem \ref{op:su_irs} and corresponding $\boldsymbol{\phi}^\star$
+					\State Compute IRS phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+					\State \textbf{Output} $\theta_l, \ l=1,\dots,L$
 				\end{algorithmic}
 			\end{algorithm}
+		\end{subsubsection}
 
-			The waveform optimization subproblem is formed as follows. For a given $\boldsymbol{V}$, problem \ref{op:temp3} reduces to
+		\begin{subsubsection}{Waveform optimization}
+			The waveform optimization subproblem is formed as follows. Once $\boldsymbol{\Phi}$ is obtained, problem \ref{op:su} is reduced to
 			\begin{maxi}
-				{\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp5}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)\ge{\bar{z}}}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){W}_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\frac{1}{2}(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P))\le{P}}
+				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
+				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
 			\end{maxi}
@@
 					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime (k-1)})^*\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(k)})\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(k)}\right) + \mathrm{Tr}(t_{I/P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\boldsymbol{W}_{I/P}^{(k)})\\
+					& = 2 \Re \left\{\mathrm{Tr}((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)})\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)}\right) + \mathrm{Tr}(t_{I/P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\boldsymbol{W}_{I/P}^{(i)})\\
 					& \quad- t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*
@@
 					& \approx t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime (k-1)} + t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime \ (k)} - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}\\
-					& = \mathrm{Tr}\left(t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{I,0}^{(k)}\right) + \mathrm{Tr}(t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{P,0}^{(k)}) - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+					& = \mathrm{Tr}\left(t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{I,0}^{(i)}\right) + \mathrm{Tr}(t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{P,0}^{(i)}) - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
 				\end{split}
@@
 				\begin{split}
-					\tilde{z}(\boldsymbol{W}_I^{(k)},\boldsymbol{W}_P^{(k)},\rho^{(k-1)})
-					& = \mathrm{Tr}(\boldsymbol{A}_I^{(k)}\boldsymbol{W}_I^{(k)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(k)}\boldsymbol{W}_P^{(k)}) \\
-					& - \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (k-1)} (t_{I,n}^{\prime (k-1)})^* + t_{P,n}^{\prime (k-1)} (t_{P,n}^{\prime (k-1)})^* \\
-					& - \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i-1)})
+					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)}) \\
+					& - \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (k-1)} (t_{I,n}^{\prime (k-1)})^* + t_{P,n}^{\prime (k-1)} (t_{P,n}^{\prime (k-1)})^* \\
+					& - \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
 				\end{split}
 			\end{equation}
-			where the Hermitian matrices $\boldsymbol{A}_I^{(k)}$ and $\boldsymbol{A}_P^{(k)}$ are
+			where the Hermitian matrices $\boldsymbol{A}_I^{(i)}$ and $\boldsymbol{A}_P^{(i)}$ are
 			\begin{equation}\label{eq:A_I,k}
 				\begin{split}
-					\boldsymbol{A}_I^{(k)}
-					& = \frac{k_2 \rho^{(k-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\right) \\
-					& + \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+					\boldsymbol{A}_I^{(i)}
+					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
+					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\right) \\
+					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}
 				\end{split}
@@
 				\begin{split}
-					\boldsymbol{A}_P^{(k)}
-					& = \frac{k_2 \rho^{(k-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(k-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H \\
-					& + \frac{3{k_4}{(\rho^{(k-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+					\boldsymbol{A}_P^{(i)}
+					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
+					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H \\
+					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}
 				\end{split}
@@
 					\State $k = k + 1$
-					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(k)}$ by \ref{eq:A_I,k} and \ref{eq:A_P,k}
-					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(k)}$ and $\rho^{(k)}$ by solving problem \ref{op:temp5}
+					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I,k} and \ref{eq:A_P,k}
+					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:temp5}
 					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
-					% \Until $\lVert \boldsymbol{W}_I^{(k)} - \boldsymbol{W}_I^{(k - 1)} \rVert_F / \lVert \boldsymbol{W}_I^{(k)} \rVert_F \le \epsilon$
-					\Until $R^{(k)}-R^{(k-1)} \le \epsilon$
+					% \Until $\lVert \boldsymbol{W}_I^{(i)} - \boldsymbol{W}_I^{(k - 1)} \rVert_F / \lVert \boldsymbol{W}_I^{(i)} \rVert_F \le \epsilon$
+					\Until $R^{(i)}-R^{(i-1)} \le \epsilon$
 					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall r$
@@
 			\end{algorithm}
+		\end{subsubsection}
 
@@
 		% \end{figure*}
-		\end{subsubsection}
+	\end{subsection}
 
@@
 
-	\end{subsection}
 \end{section}

### 2020-05-27 system-model.tex
:construction: Waveform optimization

@@
 		\end{figure*}
-		with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t'$ and transform problem \ref{op:su_gp} into
+		with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into
 		\begin{mini!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t'}{\frac{1}{t'}}{\label{op:su_gp_1}}{}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
 				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
-				\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
+				\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \le 1}
@@
 		\begin{mini}
-			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:su_gp_2}}{}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_2}}{}
 			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-			\addConstraint{{t'}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
+			\addConstraint{{t''}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
 			\addConstraint{2^{\bar{R}}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
@@
 		\begin{equation}
-			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}
+			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
 		\end{equation}
-		where $\boldsymbol{R}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
-Hence, the output current \ref{eq:z_k_channel} can be reformulated as $z(\boldsymbol{\Phi})$ (details given in section \ref{se:fs_irs}).
+		where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
 To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.
@@
 		\begin{subsubsection}{Phase shift optimization}\label{se:fs_irs}
-			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:su} reduces to
-			\begin{maxi!}
-				{\boldsymbol{\boldsymbol{\Phi}}}{z(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
-				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
-				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
-			\end{maxi!}
-			Introduce auxiliary variables
+			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
 			\begin{equation}\label{eq:t}
@@
 					&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)\\
-					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*)\\
-					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H\boldsymbol{\Phi})\\
+					&=\mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*)\\
+					&=\mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H\boldsymbol{\Phi})\\
 					&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
@@
 			\end{equation}
-			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
+			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
 			\begin{equation}\label{eq:z_irs}
@@
 					& = \mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\\
-					& \quad + \mathrm{Tr}(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)})\\
+					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)}\right)\\
 					& \quad- t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*
@@
 					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)}) \\
-					& - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
-					& - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
+					& \quad - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
+					& \quad - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
 				\end{split}
@@
 			\end{equation}
-			We then plug \ref{eq:z_irs_approx} into problem \ref{op:su_irs}, relax the rank constraint \ref{co:irs_rank}, and obtain the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ by interior-point method.
+			Hence, problem \ref{op:su} is transformed to
+			\begin{maxi!}
+				{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
+				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
+			\end{maxi!}
+			We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method.
 If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD).
@@
 First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
-Then, generate $R$ CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$.
+Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$.
 Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}.
-Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star)$.
+Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
 The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
@@
 					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
-					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall r$
-					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$ and corresponding matrices $\boldsymbol{\Phi}_r=\bar{\boldsymbol{\phi}}_r\bar{\boldsymbol{\phi}}_r^H  \ \forall r$
+					\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
 					\State Select the best solution $\boldsymbol{\Phi}^\star$ for problem \ref{op:su_irs} and corresponding $\boldsymbol{\phi}^\star$
@@
 		\begin{subsubsection}{Waveform optimization}
-			The waveform optimization subproblem is formed as follows. Once $\boldsymbol{\Phi}$ is obtained, problem \ref{op:su} is reduced to
-			\begin{maxi}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){W}_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
-				\addConstraint{\frac{1}{2}(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P))\le{P}}
-				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
-				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
-			\end{maxi}
-			Similarly, define $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T$ and let $\boldsymbol{M}_n$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and null the remaining entries.
-Since $\boldsymbol{M} \succ 0$, we have $\boldsymbol{M}_{-n}=\boldsymbol{M}_n^H$.
-Hence, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
-			\begin{figure*}[b]
-				\hrule
-				\begin{equation}\label{eq:z_k_waveform}
+			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ is obtained, introduce auxiliary variables
+			\begin{equation}\label{eq:t'}
+				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
+			\end{equation}
+			Therefore, \ref{eq:z_k_waveform} rewrites as
+			\begin{equation}\label{eq:z_waveform}
 				\begin{split}
-						z
-						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
-						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)^*+(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)^*}\\
-						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_{0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_{0}\boldsymbol{w}_P)}
+					z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)
+					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
+					&\quad+\frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
+					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
 				\end{split}
 			\end{equation}
-			\end{figure*}
-			Introduce auxiliary variables
-			\begin{equation}\label{eq:t'}
-				\begin{split}
-					t'_{I/P,n}
-					& = \boldsymbol{w}_{I/P}^H\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\\
-					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H)\\
-					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{W}_{I/P})
-				\end{split}
-			\end{equation}
-			where $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$. Therefore, \ref{eq:z_k_waveform} rewrites as
-			\begin{equation}\label{eq:z_k_waveform_t}
-				\begin{split}
-					z
-					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t'_{I,0}+t'_{P,0})\\
-					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
-					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t'_{I,0}t'_{P,0}
-				\end{split}
-			\end{equation}
-			At iteration $k$, the second-order terms are approximated by first-order Taylor series as
+			At iteration $i$, the second-order terms are approximated by first-order Taylor series as
 			\begin{equation}
 				\begin{split}
-					t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime \ (k)})^*
-					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime (k-1)})^*\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)})\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)}\right) + \mathrm{Tr}(t_{I/P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\boldsymbol{W}_{I/P}^{(i)})\\
-					& \quad- t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*
+					t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime \ (i)})^*
+					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime (i-1)})^*\right\} - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^* \\
+					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
+					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
+					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
+					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*
 				\end{split}
@@
 				\begin{split}
-					t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime \ (k)}
-					& \approx t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime (k-1)} + t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime \ (k)} - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}\\
-					& = \mathrm{Tr}\left(t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{I,0}^{(i)}\right) + \mathrm{Tr}(t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{P,0}^{(i)}) - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+					t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime \ (i)}
+					& \approx t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime \ (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\\
+					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\
+					& \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
 				\end{split}
 			\end{equation}
-			Therefore, we have
+			Therefore, the approximated current function at iteration $i$ is
 			\begin{equation}\label{eq:z_waveform_approx}
 				\begin{split}
-					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i-1)})
-					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)}) \\
-					& - \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (k-1)} (t_{I,n}^{\prime (k-1)})^* + t_{P,n}^{\prime (k-1)} (t_{P,n}^{\prime (k-1)})^* \\
-					& - \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}
+					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
+					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\\
+					& - \frac{3}{8} \beta_4 (\rho^{(i)})^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^* \\
+					& - \frac{3}{2} \beta_4 (\rho^{(i)})^2 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
 				\end{split}
@@
 			where the Hermitian matrices $\boldsymbol{A}_I^{(i)}$ and $\boldsymbol{A}_P^{(i)}$ are
-			\begin{equation}\label{eq:A_I,k}
+			\begin{equation}\label{eq:A_I}
 				\begin{split}
@@
 					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\right) \\
-					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H\right) \\
+					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (i-1)}\boldsymbol{M}_{0}
 				\end{split}
 			\end{equation}
-			\begin{equation}\label{eq:A_P,k}
+			\begin{equation}\label{eq:A_P}
 				\begin{split}
@@
 					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H \\
-					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}
+					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H \\
+					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (i-1)}\boldsymbol{M}_{0}
 				\end{split}

### 2020-05-27 system-model.tex
:triangular_flag_on_post: Algorithm on FF-IRS

@@
 				& = \frac{1}{2}\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\label{eq:z_k_terms_begin}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
@@
 				& = \frac{1}{2}\sum_n{(h_{k,n}w_{P,n})(h_{k,n}w_{P,n})^*}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $P, \bar{R}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}
-				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
+				\State \textbf{Input} $P, \bar{R}, \theta_l \ \forall l$
+				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}
 				\Repeat
@@
 					\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
-					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
-					\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
+					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
 					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
@@
 			\begin{equation}\label{eq:t'}
-				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
+				t_{I/P,n}' = \rho \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\rho \boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
 			\end{equation}
@@
 					z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)
-					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
-					&\quad+\frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
-					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
+					&=\frac{1}{2} \beta_2 (t'_{I,0}+t'_{P,0})\\
+					&\quad+\frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
+					&\quad+\frac{3}{2} \beta_4 t'_{I,0}t'_{P,0}
 				\end{split}
@@
 					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime (i-1)})^*\right\} - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
+					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
 					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
-					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
+					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
+					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
 					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*
@@
 					& \approx t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime \ (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\\
-					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\
+					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\
 					& \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
@@
 					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
-					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\\
-					& - \frac{3}{8} \beta_4 (\rho^{(i)})^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^* \\
-					& - \frac{3}{2} \beta_4 (\rho^{(i)})^2 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
+					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right)\\
+					& \quad - \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
+					& \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
 				\end{split}
@@
 			where the Hermitian matrices $\boldsymbol{A}_I^{(i)}$ and $\boldsymbol{A}_P^{(i)}$ are
-			\begin{equation}\label{eq:A_I}
-				\begin{split}
+			\begin{align}
 				\boldsymbol{A}_I^{(i)}
-					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H\right) \\
-					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (i-1)}\boldsymbol{M}_{0}
-				\end{split}
-			\end{equation}
-			\begin{equation}\label{eq:A_P}
-				\begin{split}
+				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
+				& \quad + \frac{3}{4} \beta_4 \sum_{n=-N+1}^{N-1} (t_{I,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{I,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
+				& \quad + \frac{3}{2} \beta_4 t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_I}\\
 				\boldsymbol{A}_P^{(i)}
-					& = \frac{k_2 \rho^{(i-1)} R_{\text{ant}}}{2}\boldsymbol{M}_0 \\
-					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H \\
-					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (i-1)}\boldsymbol{M}_{0}
-				\end{split}
-			\end{equation}
-			Plug \ref{eq:z_waveform_approx} into problem \ref{op:temp5} and solve it by iterative interior-point method.
-Given the optimal waveform matrices $\boldsymbol{W}_I$ and $\boldsymbol{W}_P$, the best rank-1 solution $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ can be obtained through randomization method.
-Details are omitted here.
-The algorithm for the waveform optimization subproblem is summarized in Algorithm ~.
+				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
+				& \quad + \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
+				& \quad + \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_P}
+			\end{align}
+			Hence, problem \ref{op:su} is transformed to
+			\begin{maxi!}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
+				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
+			\end{maxi!}
+			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
+$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can be approximated via randomization method as in section \ref{se:fs_irs}.
+The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
 
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\boldsymbol{V}$
-					\State \textbf{Initialize} $k=0$, $\boldsymbol{w}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
 					\Repeat
-					\State $k = k + 1$
-					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I,k} and \ref{eq:A_P,k}
-					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:temp5}
+					\State $i \leftarrow i + 1$
+					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
+					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
 					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
-					% \Until $\lVert \boldsymbol{W}_I^{(i)} - \boldsymbol{W}_I^{(k - 1)} \rVert_F / \lVert \boldsymbol{W}_I^{(i)} \rVert_F \le \epsilon$
-					\Until $R^{(i)}-R^{(i-1)} \le \epsilon$
-					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall r$
+					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
-					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r \ \forall r$ and corresponding matrices $\boldsymbol{W}_{I/P,r}=\boldsymbol{w}_{I/P,r}\boldsymbol{w}_{I/P,r}^H  \ \forall r$
-					\State Select the best solution pair $\boldsymbol{W}_{I,r}^\star, \boldsymbol{W}_{P,r}^\star$ for problem \ref{op:temp5} and corresponding $\boldsymbol{w}_{I,r}^\star, \boldsymbol{w}_{P,r}^\star$
+					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall q$
+					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
+					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ for problem \ref{op:su_waveform} and corresponding $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$
 					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
@@
 		\end{subsubsection}
-
-		% * It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$.
-
-		% To tackle the non-convex current constraint, we expand and rewrite the coupled channel terms in \ref{eq:z_k_truncated} as
-		% \begin{equation}
-		% 	\begin{split}
-		% 		{h_{n_3}^*}{h_{n_1}}
-		% 		&=(h_{D,n_3}^*+\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*)(h_{D,n_1}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*})\\
-		% 		&={h_{D,n_1}}{h_{D,n_3}^*}+{h_{D,n_1}}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}h_{D,n_3}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_1}^*}\boldsymbol{\Phi}_{n_3}^T\boldsymbol{v}^*\\
-		% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_3,n_1}\bar{\boldsymbol{v}}^*\\
-		% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)
-		% 	\end{split}
-		% \end{equation}
-		% where
-		% \begin{equation}
-		% 	\boldsymbol{R}_{n_3,n_1}=
-		% 	\begin{bmatrix}
-		% 		\boldsymbol{\Phi}_{n_1}^*\boldsymbol{\Phi}_{n_3}^T & \boldsymbol{\Phi}_{n_1}^*{h_{D,n_3}^*} \\
-		% 		h_{D,n_1}{\boldsymbol{\Phi}_{n_3}^T}               & h_{D,n_1}{h_{D,n_3}^*}
-		% 	\end{bmatrix}
-		% \end{equation}
-		% Similarly, we have ${h_{n_4}^*}{h_{n_2}}=\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)$ and ${h_n^*}{h_n}=\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)$.
-Thus, \ref{eq:z_k_truncated} is equivalent to
-		% \begin{figure*}[b]
-		% 	\hrule
-		% 	\begin{equation}\label{eq:z_k_su_temp}
-		% 		\begin{split}
-		% 			z
-		% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}\\
-		% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\mathrm{Tr}(\boldsymbol{R}_{n_3,n_1}\boldsymbol{V}^*)\mathrm{Tr}(\boldsymbol{R}_{n_4,n_2}\boldsymbol{V}^*)\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{w}_{P,n_2})\right)\\
-		% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{\mathrm{Tr}(\boldsymbol{R}_{n,n}\boldsymbol{V}^*)^2(\boldsymbol{w}_{I,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{w}_{P,n})}
-		% 		\end{split}
-		% 	\end{equation}
-		% \end{figure*}
 	\end{subsection}
-
-	% % ? AO: optimize weights with given phase shifts
-	% To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
-	% \begin{equation}
-	% 	\begin{split}
-	% 		{h_{n_1}^*}{h_{n_2}}
-	% 		&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
-	% 		&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
-	% 		&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
-	% 		&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
-	% 	\end{split}
-	% \end{equation}
-	% where
-	% \begin{equation}
-	% 	\boldsymbol{R}_{n_1,n_2}=
-	% 	\begin{bmatrix}
-	% 		\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
-	% 		h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
-	% 	\end{bmatrix}
-	% \end{equation}
-	% On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries.
-It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}.
-Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
-	% \begin{figure*}[b]
-	% 	\hrule
-	% 	\begin{equation}\label{eq:z_k_waveform}
-	% 		\begin{split}
-	% 			z
-	% 			&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
-	% 			% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-	% 			% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
-	% 			&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
-	% 			&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
-	% 		\end{split}
-	% 	\end{equation}
-	% \end{figure*}
-	% We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
-	% % and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
-	% \begin{equation}\label{eq:z_k_su_compact}
-	% 	\begin{split}
-	% 		z
-	% 		&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
-	% 		&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
-	% 		&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
-	% 	\end{split}
-	% \end{equation}
-
-	% A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint
-
-	% which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
-	% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
-	% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
-	% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
-	% \begin{equation}
-	% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
-	% \end{equation}
-	% where the equality holds if and only if the direct and IRS-aided links align with each other.
-In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$.
-Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
-	% \begin{equation}
-	% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
-	% \end{equation}
-	% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
-	% \begin{equation}\label{eq:phi_n}
-	% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
-	% \end{equation}
-
 \end{section}

### 2020-05-30 system-model.tex
:construction: Fix current expression

@@
 				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\nonumber\\
 				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_k_channel}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\label{eq:z_k_channel}\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\nonumber\\
 				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_k_waveform}
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\label{eq:z_k_waveform}
 			\end{align}
@@
 First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
-Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$.
+Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$.
 Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}.
@@
 					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
-					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
 					\State Select the best solution $\boldsymbol{\Phi}^\star$ for problem \ref{op:su_irs} and corresponding $\boldsymbol{\phi}^\star$
@@
 			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
-$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can be approximated via randomization method as in section \ref{se:fs_irs}.
+$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\omega}, \omega \in [0,2\pi]$.
 The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
@@
 					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
-					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{N}) \ \forall q$
+					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
 					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$

### 2020-05-31 system-model.tex
:construction: Fix iteration index
:ambulance: Fix contribution from information waveform

@@
 \input{packages.tex}
-\input{commands.tex}
 
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{n_1}})(h_{k,{n_2}}w_{I,{n_2}})(h_{k,{n_3}}w_{I,{n_3}})^*(h_{k,{n_4}}w_{I,{n_4}})^*}\\
-				& = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^*\\
+				& = \frac{3}{4}\left(\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\right)^2\\
+				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2\\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
@@
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^*\right)\nonumber\\
 				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\label{eq:z_k_channel}\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
 				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\label{eq:z_k_waveform}
@@
 					&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
-					&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\
+					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\\
 					&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
@@
 Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
-			\begin{equation}
-				\begin{split}
-					t_{I/P,n}^{(i)} (t_{I/P,n}^{(i)})^*
-					& \approx 2 \Re\left\{t_{I/P,n}^{(i)} (t_{I/P,n}^{(i-1)})^*\right\} - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\\
-					& \quad - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\\
-					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)}\right)\\
-					& \quad- t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*
-				\end{split}
-			\end{equation}
-			and
-			\begin{equation}
-				\begin{split}
+			\begin{align}
+				(t_{I,0}^{(i)})^2
+				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\nonumber\\
+				& = 2 \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_1}\\
+				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
+				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
+				& = 2 \Re \left\{\mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\nonumber\\
+				& \quad - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
+				& = \mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
+				& \quad + \mathrm{Tr}\left(t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
+				& \quad- t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\label{eq:t_approx_2}\\
 				t_{I,0}^{(i)} t_{P,0}^{(i)}
-					& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\\
-					& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\\
-					& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
-				\end{split}
-			\end{equation}
+				& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\nonumber\\
+				& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\nonumber\\
+				& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\label{eq:t_approx_3}
+			\end{align}
+			Note that \ref{eq:t_approx_1} and \ref{eq:t_approx_2} provide lower bounds to convex terms $t_{I,0}^2$ and $t_{P,n} t_{P,n}^*$, but \ref{eq:t_approx_3} is only an approximation to $t_{I,0} t_{P,0}$ which is non-convex.
 Therefore, the approximated current function at iteration $i$ is
@@
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)}) \\
-					& \quad - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
+					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)})\\
+					& \quad - \frac{3}{8} \beta_4 \rho^2 \left(2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \right)\\
 					& \quad - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
@@
 					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
-					& \quad+ \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(i-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(i-1)}\boldsymbol{C}_{I,n}^H\right)\\
-					& \quad \quad + \left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\right)\\
+					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,n}^{(i-1)} \boldsymbol{C}_0\\
+					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)\\
 					& \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})
@@
 					&=\frac{1}{2} \beta_2 (t'_{I,0}+t'_{P,0})\\
-					&\quad+\frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
+					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
 					&\quad+\frac{3}{2} \beta_4 t'_{I,0}t'_{P,0}
@@
 			At iteration $i$, the second-order terms are approximated by first-order Taylor series as
-			\begin{equation}
-				\begin{split}
-					t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime \ (i)})^*
-					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime (i-1)})^*\right\} - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^* \\
-					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
-					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*\\
-					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
-					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
-					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*
-				\end{split}
-			\end{equation}
-			and
-			\begin{equation}
-				\begin{split}
-					t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime \ (i)}
-					& \approx t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime \ (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\\
-					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\
+			\begin{align}
+				(t_{I,0}^{\prime (i)})^2
+				& \ge 2 \mathrm{Tr}\left(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right) - (t_{I,0}^{\prime (i-1)})^2\\
+				t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
+				& \ge \mathrm{Tr}\left((t_{P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
+				& \quad + \mathrm{Tr}\left(t_{P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
+				& \quad - t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
+				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
+				& \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
+				& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P}^{(i)})\nonumber\\
 				& \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
-				\end{split}
-			\end{equation}
+			\end{align}
 			Therefore, the approximated current function at iteration $i$ is
@@
 					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right)\\
-					& \quad - \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
+					& \quad - \frac{3}{8} \beta_4 \Biggl(2 (t_{I,0}^{\prime (i-1)})^2\\
+					& \quad \quad + \sum_{n=-N+1}^{N-1} t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\Biggl)\\
 					& \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
@@
 				\boldsymbol{A}_I^{(i)}
-				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
-				& \quad + \frac{3}{4} \beta_4 \sum_{n=-N+1}^{N-1} (t_{I,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{I,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
-				& \quad + \frac{3}{2} \beta_4 t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_I}\\
+				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{2} \beta_4 (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})\boldsymbol{H}_{0}^*\label{eq:A_I}\\
 				\boldsymbol{A}_P^{(i)}
@@
 				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
+				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
 				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
@@
 					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
-					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
+					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
 					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$

### 2020-06-03 system-model.tex
:pencil: Fix typo
:sparkles: Separate waveform and split ratio

@@
 					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
-					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,n}^{(i-1)} \boldsymbol{C}_0\\
+					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,0}^{(i-1)} \boldsymbol{C}_{I,0}\\
 					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)\\
@@
 					&=\frac{1}{2} \beta_2 (t'_{I,0}+t'_{P,0})\\
-					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
+					&\quad+\frac{3}{8} \beta_4 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
 					&\quad+\frac{3}{2} \beta_4 t'_{I,0}t'_{P,0}
@@
 				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint_1}}
 				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
@@
 			\end{maxi!}
+			Note that objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} involve bilinear terms $\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})$ and $(1-\rho)W_{I,n,n}$, which can be lower bounded by partial Taylor expansion as in \ref{eq:bilinear_begin} -- \ref{eq:bilinear_end}.
+			\begin{figure*}[b]
+				\hrule
+				\begin{align}
+					\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})
+					& = \frac{1}{4}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\label{eq:bilinear_begin}\\
+					& \ge \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)\nonumber\\
+					& \quad \quad - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\\
+					\bar{\rho}^{(i)}W_{I,n,n}^{(i)}
+					& = \frac{1}{4}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\\
+					& \ge \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:bilinear_end}
+				\end{align}
+				\begin{align}
+					z'(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
+					& = \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)^2\nonumber\\
+					& \quad + \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\label{eq:z'}\\
+					g(\bar{\rho}^{(i)},W_{I,n,n}^{(i)})
+					& = \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:g}
+				\end{align}
+			\end{figure*}
+			Therefore, problem \ref{op:su_waveform} is transformed to
+			\begin{maxi!}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform_final}}{}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\bar{\rho},W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
+				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
+				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
+				\addConstraint{\rho + \bar{\rho} \le 1}
+			\end{maxi!}
+			where $\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)$ and $g(\bar{\rho},W_{I,n,n})$ are given in \ref{eq:z'} and \ref{eq:g}, respectively.
 We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.

### 2020-06-06 system-model.tex
:pencil: Reconstruct lower bounds

@@
 				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\nonumber\\
-				& = 2 \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_1}\\
+				& = 2 \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_begin}\\
 				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
 				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
-				& = 2 \Re \left\{\mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\nonumber\\
-				& \quad - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
-				& = \mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
-				& \quad + \mathrm{Tr}\left(t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
-				& \quad- t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\label{eq:t_approx_2}\\
+				& = 2 \Re \left\{\mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
+				& = \mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right) + \mathrm{Tr}\left(t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
+				& \quad- t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
 				t_{I,0}^{(i)} t_{P,0}^{(i)}
-				& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\nonumber\\
-				& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\nonumber\\
-				& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\label{eq:t_approx_3}
+				& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
+				& \ge \frac{1}{2}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})(t_{I,0}^{(i)} + t_{P,0}^{(i)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_approx_end}
+				% & \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\nonumber\\
+				% & = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\nonumber\\
+				% & \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\label{eq:t_approx_3}
 			\end{align}
-			Note that \ref{eq:t_approx_1} and \ref{eq:t_approx_2} provide lower bounds to convex terms $t_{I,0}^2$ and $t_{P,n} t_{P,n}^*$, but \ref{eq:t_approx_3} is only an approximation to $t_{I,0} t_{P,0}$ which is non-convex.
-Therefore, the approximated current function at iteration $i$ is
+			\ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is
 			\begin{equation}\label{eq:z_irs_approx}
@@
 					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)})\\
+					& \quad + \frac{1}{2}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})(t_{I,0}^{(i)} + t_{P,0}^{(i)}) - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\\
 					& \quad - \frac{3}{8} \beta_4 \rho^2 \left(2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \right)\\
-					& \quad - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}
+					& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2
 				\end{split}
@@
 					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,0}^{(i-1)} \boldsymbol{C}_{I,0}\\
-					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)\\
-					& \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})
+					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)
+					% & \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})
 				\end{split}
@@
 			\begin{equation}\label{eq:t'}
-				t_{I/P,n}' = \rho \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\rho \boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
+				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
 			\end{equation}
@@
 					z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)
-					&=\frac{1}{2} \beta_2 (t'_{I,0}+t'_{P,0})\\
-					&\quad+\frac{3}{8} \beta_4 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
-					&\quad+\frac{3}{2} \beta_4 t'_{I,0}t'_{P,0}
+					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
+					&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
+					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
 				\end{split}
 			\end{equation}
-			At iteration $i$, the second-order terms are approximated by first-order Taylor series as
+			Similar to \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end}, the second-order terms at iteration $i$ are approximated as
 			\begin{align}
+				(\rho^{(i)})^2
+				& \ge 2\rho^{(i-1)}\rho^{(i)} - (\rho^{(i-1)})^2 \triangleq A\\
 				(t_{I,0}^{\prime (i)})^2
-				& \ge 2 \mathrm{Tr}\left(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right) - (t_{I,0}^{\prime (i-1)})^2\\
+				& \ge 2 \mathrm{Tr}\left(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right) - (t_{I,0}^{\prime (i-1)})^2\\
 				t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
-				& \ge \mathrm{Tr}\left((t_{P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
-				& \quad + \mathrm{Tr}\left(t_{P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
-				& \quad - t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
-				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
-				& \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
-				& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P}^{(i)})\nonumber\\
-				& \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
+				& \ge \mathrm{Tr}\left((t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right) + \mathrm{Tr}\left(t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
+				& \quad - t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*
+				% t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
+				% & \ge \frac{1}{2} (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})(t_{I,0}^{\prime (i)} + t_{P,0}^{\prime (i)})\nonumber\\
+				% & \quad - \frac{1}{4}(t_{I,0}^{\prime (i-1)}+t_{P,0}^{\prime (i-1)})^2 - \frac{1}{4}(t_{I,0}^{\prime (i)} - t_{P,0}^{\prime (i)})^2
+				% & \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
+				% & = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P}^{(i)})\nonumber\\
+				% & \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
 			\end{align}
+			Also, define $t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)} \ge B$.
 			Therefore, the approximated current function at iteration $i$ is

### 2020-06-06 system-model.tex
:pencil: Reconstruct current expression

@@
 					&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
-					&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
+					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})(A_n s_{I,n})^*\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
 					&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
@@
 					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-					\State Select the best solution $\boldsymbol{\Phi}^\star$ for problem \ref{op:su_irs} and corresponding $\boldsymbol{\phi}^\star$
-					\State Compute IRS phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+					\State Select best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
+					\State Compute phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
 					\State \textbf{Output} $\theta_l, \ l=1,\dots,L$
@@
 			\end{equation}
-			Similar to \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end}, the second-order terms at iteration $i$ are approximated as
+			Similar to \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end}, the coupled terms at iteration $i$ are approximated as
 			\begin{align}
+				(\rho^{(i)} t_{I,0}^{\prime (i)})^2
+				& \ge 2 \mathrm{Tr}\left(\rho^{(i-1)}t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right)\nonumber\\
+				& \quad - (\rho^{(i-1)}t_{I,0}^{\prime (i-1)})^2\\
+				(\rho^{(i)})^2 t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
+				& \ge \mathrm{Tr}\left(\rho^{(i-1)}(t_{P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
+				& \quad + \mathrm{Tr}\left(\rho^{(i-1)}t_{P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
+				& \quad - (\rho^{(i-1)})^2 t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
 				(\rho^{(i)})^2
-				& \ge 2\rho^{(i-1)}\rho^{(i)} - (\rho^{(i-1)})^2 \triangleq A\\
-				(t_{I,0}^{\prime (i)})^2
-				& \ge 2 \mathrm{Tr}\left(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right) - (t_{I,0}^{\prime (i-1)})^2\\
-				t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
-				& \ge \mathrm{Tr}\left((t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right) + \mathrm{Tr}\left(t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
-				& \quad - t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*
-				% t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
-				% & \ge \frac{1}{2} (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})(t_{I,0}^{\prime (i)} + t_{P,0}^{\prime (i)})\nonumber\\
-				% & \quad - \frac{1}{4}(t_{I,0}^{\prime (i-1)}+t_{P,0}^{\prime (i-1)})^2 - \frac{1}{4}(t_{I,0}^{\prime (i)} - t_{P,0}^{\prime (i)})^2
+				& \ge 2\rho^{(i-1)}\rho^{(i)} - (\rho^{(i-1)})^2\nonumber\\
+				& \triangleq a^{(i)}\\
+				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
+				& \ge \frac{1}{2} (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})(t_{I,0}^{\prime (i)} + t_{P,0}^{\prime (i)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{I,0}^{\prime (i-1)}+t_{P,0}^{\prime (i-1)})^2 - \frac{1}{4}(t_{I,0}^{\prime (i)} - t_{P,0}^{\prime (i)})^2\nonumber\\
+				& \triangleq b^{(i)}
 				% & \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
@@
 			\end{align}
-			Also, define $t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)} \ge B$.
 			Therefore, the approximated current function at iteration $i$ is
@@
 				\begin{split}
-					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
-					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right)\\
-					& \quad - \frac{3}{8} \beta_4 \Biggl(2 (t_{I,0}^{\prime (i-1)})^2\\
-					& \quad \quad + \sum_{n=-N+1}^{N-1} t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\Biggl)\\
-					& \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
+					% \tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
+					\tilde{z}^{(i)}
+					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right) + a^{(i)} b^{(i)}\\
+					& \quad - \frac{3}{8} \beta_4 (\rho^{(i-1')})^2 \left(2 (t_{I,0}^{\prime (i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\right)
+					% & \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
 				\end{split}
@@
 				\boldsymbol{A}_I^{(i)}
-				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{2} \beta_4 (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})\boldsymbol{H}_{0}^*\label{eq:A_I}\\
+				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{2} \beta_4 \rho^{(i-1)} t_{I,0}^{\prime (i-1)} \boldsymbol{H}_{0}^*\label{eq:A_I}\\
 				\boldsymbol{A}_P^{(i)}
-				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^*\nonumber\\
-				& \quad + \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
-				& \quad + \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_P}
+				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{8} \beta_4 \rho^{(i-1)} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\label{eq:A_P}
+				% & \quad + \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_P}
 			\end{align}
+			\begin{figure*}[b]
+				\hrule
+				\begin{align}
+					\tilde{z}'^{(i)}
+					& = \frac{1}{2}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right)\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right) - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)^2\nonumber\\
+					& \quad + \frac{1}{2}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right) - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\nonumber\\
+					& \quad + \frac{1}{2}(a^{(i-1)} + b^{(i-1)})(a^{(i)} + b^{(i)}) - \frac{1}{4}(a^{(i-1)} + b^{(i-1)})^2 - \frac{1}{4}(a^{(i)} - b^{(i)})^2\label{eq:z_waveform_lb}\\
+					g^{(i)}
+					& = \frac{1}{2}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)\left((1-\rho^{(i)}) + W_{I,n,n}^{(i)}\right) - \frac{1}{4}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left((1-\rho^{(i)}) - W_{I,n,n}^{(i)}\right)^2\label{eq:r_power_lb}
+				\end{align}
+			\end{figure*}
+			% A lower bound of \label{eq:z_waveform_approx} is further provided in \ref{eq:z_waveform_lb}. Hence, problem \ref{op:su} is transformed to
 			Hence, problem \ref{op:su} is transformed to
 			\begin{maxi!}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform_1}}{\label{eq:su_waveform_target}}
 				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint_1}}
@@
 			\end{maxi!}
-			Note that objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} involve bilinear terms $\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})$ and $(1-\rho)W_{I,n,n}$, which can be lower bounded by partial Taylor expansion as in \ref{eq:bilinear_begin} -- \ref{eq:bilinear_end}.
-			\begin{figure*}[b]
-				\hrule
-				\begin{align}
-					\rho^{(i)}\mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})
-					& = \frac{1}{4}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\label{eq:bilinear_begin}\\
-					& \ge \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)\nonumber\\
-					& \quad \quad - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i-1)}\boldsymbol{W}_{I/P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I/P}^{(i)}\boldsymbol{W}_{I/P}^{(i)})\right)^2\\
-					\bar{\rho}^{(i)}W_{I,n,n}^{(i)}
-					& = \frac{1}{4}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\\
-					& \ge \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:bilinear_end}
-				\end{align}
-				\begin{align}
-					z'(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
-					& = \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)^2\nonumber\\
-					& \quad + \frac{1}{2}\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right) - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\label{eq:z'}\\
-					g(\bar{\rho}^{(i)},W_{I,n,n}^{(i)})
-					& = \frac{1}{2}\left(\bar{\rho}^{(i)} + W_{I,n,n}^{(i)}\right)\left(\bar{\rho}^{(i-1)} + W_{I,n,n}^{(i-1)}\right) - \frac{1}{4}\left(\bar{\rho}^{(i)} - W_{I,n,n}^{(i)}\right)^2\label{eq:g}
-				\end{align}
-			\end{figure*}
-			Therefore, problem \ref{op:su_waveform} is transformed to
+			Note that \ref{op:su_waveform_1} involves bilinear terms $\rho\mathrm{Tr}(\boldsymbol{A}_{I/P}\boldsymbol{W}_{I/P})$ and $(1-\rho)W_{I,n,n}$.
+We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$.
+Therefore, problem \ref{op:su_waveform_1} is equivalent to
 			\begin{maxi!}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform_final}}{}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\bar{\rho},W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
 				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
@@
 				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
-				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{maxi!}
-			where $\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)$ and $g(\bar{\rho},W_{I,n,n})$ are given in \ref{eq:z'} and \ref{eq:g}, respectively.
 			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
@@
 					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
-					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ for problem \ref{op:su_waveform} and corresponding $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$
+					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ and $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$ for problem \ref{op:su_waveform}
 					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$

### 2020-06-07 system-model.tex
:pencil: WIT initialization

@@
 		\begin{equation}\label{eq:psi}
-			\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=\bar{\psi}_{n}
+			\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}
 		\end{equation}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
-					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
+					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},\sigma_n \ \forall n$
+					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
 					\Repeat
@@
 					\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
-					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
 					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
-					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
 					\State Select best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
@@
 				& \ge 2\rho^{(i-1)}\rho^{(i)} - (\rho^{(i-1)})^2\nonumber\\
-				& \triangleq a^{(i)}\\
+				& \triangleq a^{(i)}\label{eq:a}\\
 				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
@@
 				& \quad - \frac{1}{4}(t_{I,0}^{\prime (i-1)}+t_{P,0}^{\prime (i-1)})^2 - \frac{1}{4}(t_{I,0}^{\prime (i)} - t_{P,0}^{\prime (i)})^2\nonumber\\
-				& \triangleq b^{(i)}
+				& \triangleq b^{(i)}\label{eq:b}
 				% & \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
@@
 					& \quad + \frac{1}{2}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right) - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\nonumber\\
-					& \quad + \frac{1}{2}(a^{(i-1)} + b^{(i-1)})(a^{(i)} + b^{(i)}) - \frac{1}{4}(a^{(i-1)} + b^{(i-1)})^2 - \frac{1}{4}(a^{(i)} - b^{(i)})^2\label{eq:z_waveform_lb}\\
-					g^{(i)}
+					& \quad + \frac{1}{2}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})(\bar{a}^{(i)} + \bar{b}^{(i)}) - \frac{1}{4}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})^2 - \frac{1}{4}(\bar{a}^{(i)} - \bar{b}^{(i)})^2\label{eq:z_waveform_lb}\\
+					g_n^{(i)}
 					& = \frac{1}{2}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)\left((1-\rho^{(i)}) + W_{I,n,n}^{(i)}\right) - \frac{1}{4}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left((1-\rho^{(i)}) - W_{I,n,n}^{(i)}\right)^2\label{eq:r_power_lb}
@@
 			Note that \ref{op:su_waveform_1} involves bilinear terms $\rho\mathrm{Tr}(\boldsymbol{A}_{I/P}\boldsymbol{W}_{I/P})$ and $(1-\rho)W_{I,n,n}$.
-We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$.
+We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g_n(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$.
 Therefore, problem \ref{op:su_waveform_1} is equivalent to
 			\begin{maxi!}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho,\bar{a},\bar{b}}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g_n(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
 				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
@@
 				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
+				\addConstraint{a \ge \bar{a}}
+				\addConstraint{b \ge \bar{b}}
 			\end{maxi!}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
-					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\State \textbf{Input} $\bar{R},P,Q,\boldsymbol{R}_n,\sigma_n \ \forall n$
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $a^{(0)}$, $b^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
 					\Repeat
@@
 					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
-					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
+					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
 					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
-					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
+					\State Update auxiliary $a^{(i)},b^{(i)}$ by \ref{eq:a} and \ref{eq:b}
+					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
 					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
-					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
+					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
 					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ and $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$ for problem \ref{op:su_waveform}
@@
 		\end{subsubsection}
+
+		\begin{subsection}{WIT initialization}
+			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points.
+Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
+			\begin{maxi!}
+				{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
+				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
+				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
+			\end{maxi!}
+			Problem \ref{op:su_irs_wit} can be solved after SDR.
+Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$.
+After constructing composite channel by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n=\lvert w_{I,n} \rvert^2$ and waveform phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
+Therefore, the optimal information waveform at subband $n$ is
+			\begin{equation}\label{eq:w_wit}
+				w_{I,n}=\sqrt{p_n}e^{j \psi_{I,n}^\star}
+			\end{equation}
+			We update IRS and information waveform iteratively by \ref{op:su_irs_wit} and \ref{eq:w_wit} until convergence. The WIT algorithm is summarized in \ref{alg:wit}.
+			\begin{algorithm}
+				\caption{WIT Initialization}
+				\label{alg:wit}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\Repeat
+					\State $i \leftarrow i + 1$
+					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
+					\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
+					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
+					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
+					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
+					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_k}
+					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
+					\State Obtain optimal waveform phase $\psi_{I,n}^{(i)} \ \forall n$ by \ref{eq:psi}
+					\State Update information waveform $\boldsymbol{w}_I^{(i)}$ by \ref{eq:w_wit}
+					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
+					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \boldsymbol{\phi}^\star$
+				\end{algorithmic}
+			\end{algorithm}
+		\end{subsection}
 	\end{subsection}

### 2020-06-13 system-model.tex
:pencil: SWIPT review

@@
 \begin{document}
+
+\begin{section}{Introduction}
+	With the significant advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
+Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and restricts the scale of networks.
+Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range.
+Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the radio-frequency (RF) band.
+It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner.
+The trend of reduction in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
+
+	The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the rate-energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
+Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switch between energy harvesting (EH) and Information Decoding (ID) modes and Power Splitting (PS) that splits the received signal into individual components.
+On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup.
+Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the weighted sum-power subjective to SINR constraints \cite{Xu2014}.
+Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
+However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level.
+The authors also suggested a practical parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
+From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform outperforms single tone in both operation range and RF-to-DC efficiency, which is more suitable for WPT.
+In \cite{Clerckx2016a}, a tractable diode nonlinear model was derived based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current.
+Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
+The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region.
+In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT alternating between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that boosts the energy while encoding the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
+Assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes such that WPT is only activated at the points with large offset.
+Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the energy constraint, while the information symbols are symmetrically distributed around the origin.
+It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity.
+SWIPT was also applied in the network design of Non-Orthogonal Multiple Access (NOMA) and Rate-Splitting Multiple Access (RSMA).
+\cite{Liu2016} proposed a cooperative SWIPT NOMA protocol with three user selection schemes to enable the strong user assists the EH of the weak user.
+In \cite{Mao2019}, SWIPT was formulated as a Weighted-Sum Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
+
+	Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency.
+A practical IRS consists of multiple individual elements that adjust the incident signal in terms of amplitude and phase through passive beamforming \cite{Wu2019e}.
+Different from relay and backscatter communication, it assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
+IRS also contributes to a squared gain of the number of reflectors on the received signal power, which can be interpreted as a Maximum Ratio Combining (MRC) overlapped to a Maximum Ratio Transmission (MRT).
+\end{section}
 

### 2020-06-13 system-model.tex
:pencil: IRS review

--- 2020-06-07 system-model.tex
@@
 \begin{document}
+
+\begin{section}{Introduction}
+	With the advance of communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
+Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks.
+Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range.
+Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the radio-frequency (RF) band.
+It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner.
+The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
+
+	The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the rate-energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
+Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes and Power Splitting (PS) that splits the received signal into individual components.
+On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup.
+Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the weighted sum-power subjective to SINR constraints \cite{Xu2014}.
+Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
+However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level.
+The authors also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
+From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform outperforms single tone in both operation range and RF-to-DC efficiency, which is more suitable for WPT.
+\cite{Clerckx2016a} derived a tractable diode nonlinear model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current.
+Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
+The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region.
+In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
+By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes such that WPT is only activated at the points with large offset.
+Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin.
+It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity.
+SWIPT was also explored in the network design.
+\cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes to enable the strong user assists the EH of the weak user.
+In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted-Sum Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
+
+	Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency.
+A practical IRS consists of multiple individual elements which can adjust the amplitude and phase of the incident signal through passive beamforming.
+Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
+It also contributes to a quadratic increase of received signal power with the number of reflectors, which can be interpreted as a Maximum Ratio Combining (MRC) receiver overlapped to a Maximum Ratio Transmission (MRT) transmitter.
+
+	Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and multi-path fading.
+At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to solve indoor signal blockage problem.
+Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR).
+The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}.
+In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was performed through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially evaluates the cascaded channel of each IRS element with the others switched off.
+Based on the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
+Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems.
+A practical transmission protocol was proposed in \cite{Yang2019}, where the authors exploited spatial correlation to reduce estimation overhead and optimization complexity by assuming adjacent elements share a common reflection coefficient.
+On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}.
+\cite{Yang2020} proposed a dynamic passive beamforming strategy that adapts IRS over time slots to create time-varying channels within coherence time and exploits the diversity by updating resource allocation and IRS configuration alternatively.
+
+	Most existing IRS SWIPT papers focus on narrow-band transmission and linear harvester model.
+
+\end{section}
 

### 2020-06-14 system-model.tex
:pencil: SWIPT-IRS review

@@
 
-	Most existing IRS SWIPT papers focus on narrow-band transmission and linear harvester model.
+	The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the Weighted-Sum Power (WSP) subject to Signal-to-Interference-plus-Noise Ratio (SINR) constraints.
+The fairness issue was then considered in \cite{Tang2019}, which assumed perfect energy interference cancellation and maximized the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques.
+\cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that one energy stream is enough for all ERs.
+In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms.
+However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
 

### 2020-06-15 system-model.tex
:art: Update review

@@
 \begin{section}{Introduction}
-	With the advance of communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
+	With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
 Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks.
@@
 On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup.
-Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the weighted sum-power subjective to SINR constraints \cite{Xu2014}.
+Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
 Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
@@
 The authors also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
-From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform outperforms single tone in both operation range and RF-to-DC efficiency, which is more suitable for WPT.
-\cite{Clerckx2016a} derived a tractable diode nonlinear model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current.
+From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
+\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current under rate constraints.
 Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
@@
 In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
-By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes such that WPT is only activated at the points with large offset.
+By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes to ensure WPT is only activated at the points with large offset.
 Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin.
@@
 SWIPT was also explored in the network design.
-\cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes to enable the strong user assists the EH of the weak user.
-In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted-Sum Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
+\cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user.
+In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
 
 	Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency.
-A practical IRS consists of multiple individual elements which can adjust the amplitude and phase of the incident signal through passive beamforming.
+In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
 Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
@@
 In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was performed through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially evaluates the cascaded channel of each IRS element with the others switched off.
-Based on the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
+Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
 Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems.
@@
 \cite{Yang2020} proposed a dynamic passive beamforming strategy that adapts IRS over time slots to create time-varying channels within coherence time and exploits the diversity by updating resource allocation and IRS configuration alternatively.
+Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
 
 	The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the Weighted-Sum Power (WSP) subject to Signal-to-Interference-plus-Noise Ratio (SINR) constraints.
+Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
 The fairness issue was then considered in \cite{Tang2019}, which assumed perfect energy interference cancellation and maximized the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that one energy stream is enough for all ERs.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs.
 In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms.
 However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
-
 \end{section}

### 2020-06-19 system-model.tex
:pencil: Waveform optimization

@@
 Both direct and extra link contributes to the corresponding composite channel as
-		\begin{equation}
+		\begin{equation}\label{eq:h_{k,n}}
 			h_{k,n} = A_{k,n} e^{j\bar{\psi}_{k,n}}= h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
@@
 	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables.
-In the next section, we propose two waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
+In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
 
@@
 		\begin{algorithm}
-			\caption{FS-IRS: Waveform Amplitude Optimization}
+			\caption{FS-IRS: Waveform and Splitting Ratio}
 			\label{al:fs_waveform}
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $P, \bar{R}, \theta_l \ \forall l$
-				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}, \boldsymbol{h}$ by \ref{eq:h_k}, \ref{eq:theta}
+				\State \textbf{Input} $P, \bar{R}, A_n \ \forall n$ by \ref{eq:h_{k,n}}
+				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
 				\Repeat
@@
 				\State Update GM exponents $\{\gamma_{I,n}^{(i)},\gamma_{P}^{(i)}\}$ by \ref{eq:gamma_I_1} -- \ref{eq:gamma_P}
-				\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and splitting ratio $\rho^{(i)}, \bar{\rho}^{(i)}$ by solving problem \ref{op:su_gp_2}
+				\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_gp_2}
 				\State Compute output DC current $z^{(i)}$ by \ref{eq:z_gp}
-				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
 				\State \textbf{Output} $\boldsymbol{s}_{I/P}^{\star}, \rho^{\star}, z^{\star}$
@@
 		where $t$ is an auxiliary variable with unit modulus and
-		\begin{equation}
+		\begin{equation}\label{eq:R_n,phi}
 			\boldsymbol{R}_n=
@@
 		where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
-To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.
+To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio with the others being fixed.
 
-		\begin{subsubsection}{Phase shift optimization}\label{se:fs_irs}
+		\begin{subsubsection}{IRS Phase Shift Optimization}\label{se:fs_irs}
 			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
@@
 			\end{equation}
-			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
+			where we define
+			\begin{equation}\label{eq:C_{I/P,n}}
+				\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
+			\end{equation}
+			Therefore, \ref{eq:z_k_channel} rewrites as
 			\begin{equation}\label{eq:z_irs}
@@
 				(t_{I,0}^{(i)})^2
-				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\nonumber\\
-				& = 2 \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_begin}\\
+				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_begin}\\
 				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
-				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
-				& = 2 \Re \left\{\mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
-				& = \mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right) + \mathrm{Tr}\left(t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
-				& \quad- t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
+				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
 				t_{I,0}^{(i)} t_{P,0}^{(i)}
 				& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})(t_{I,0}^{(i)} + t_{P,0}^{(i)})\nonumber\\
+				& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
 				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_approx_end}
-				% & \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\nonumber\\
-				% & = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\nonumber\\
-				% & \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\label{eq:t_approx_3}
 			\end{align}
-			\ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is
+			\ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
+			\begin{figure*}[b]
+				\hrule
 				\begin{equation}\label{eq:z_irs_approx}
@@
 						\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)})\\
-					& \quad + \frac{1}{2}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})(t_{I,0}^{(i)} + t_{P,0}^{(i)}) - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\\
-					& \quad - \frac{3}{8} \beta_4 \rho^2 \left(2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \right)\\
-					& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2
+						& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\\
+						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\\
+						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)
 					\end{split}
 				\end{equation}
-			where the corresponding Hermitian matrix $\boldsymbol{A}^{(i)}$ is
-			\begin{equation}\label{eq:A}
-				\begin{split}
-					\boldsymbol{A}^{(i)}
-					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{I,0}+\boldsymbol{C}_{P,0})\\
-					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,0}^{(i-1)} \boldsymbol{C}_{I,0}\\
-					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)
-					% & \quad+ \frac{3}{2} \beta_4 \rho^2 (t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0} + t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0})
-				\end{split}
-			\end{equation}
+			\end{figure*}
 			Hence, problem \ref{op:su} is transformed to
@@
 Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
+The algorithm for the phase shift optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
 			\begin{algorithm}
-				\caption{FF-IRS: Phase Shift Optimization}
+				\caption{FF-IRS: IRS Phase Shift}
 				\label{al:ff_irs}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},\sigma_n \ \forall n$
+					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
 					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
@@
 					\State $i \leftarrow i + 1$
-					\State Update SDR matrix $\boldsymbol{A}^{(i)}$ by \ref{eq:A}
 					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
 					\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
@@
 					\State Compute phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-					\State \textbf{Output} $\theta_l, \ l=1,\dots,L$
+					\State \textbf{Output} $\theta_l \ \forall l$
 				\end{algorithmic}
@@
 
-		\begin{subsubsection}{Waveform optimization}
-			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ is obtained, introduce auxiliary variables
+		\begin{subsubsection}{Transmit Waveform Optimization}
+			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ and $\rho$ are obtained, introduce auxiliary variables
 			\begin{equation}\label{eq:t'}
@@
 				\begin{split}
-					z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)
+					z(\boldsymbol{W}_I,\boldsymbol{W}_P)
 					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
@@
 			\end{equation}
-			Similar to \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end}, the coupled terms at iteration $i$ are approximated as
-			\begin{align}
-				(\rho^{(i)} t_{I,0}^{\prime (i)})^2
-				& \ge 2 \mathrm{Tr}\left(\rho^{(i-1)}t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right)\nonumber\\
-				& \quad - (\rho^{(i-1)}t_{I,0}^{\prime (i-1)})^2\\
-				(\rho^{(i)})^2 t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
-				& \ge \mathrm{Tr}\left(\rho^{(i-1)}(t_{P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
-				& \quad + \mathrm{Tr}\left(\rho^{(i-1)}t_{P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
-				& \quad - (\rho^{(i-1)})^2 t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
-				(\rho^{(i)})^2
-				& \ge 2\rho^{(i-1)}\rho^{(i)} - (\rho^{(i-1)})^2\nonumber\\
-				& \triangleq a^{(i)}\label{eq:a}\\
-				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
-				& \ge \frac{1}{2} (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})(t_{I,0}^{\prime (i)} + t_{P,0}^{\prime (i)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{I,0}^{\prime (i-1)}+t_{P,0}^{\prime (i-1)})^2 - \frac{1}{4}(t_{I,0}^{\prime (i)} - t_{P,0}^{\prime (i)})^2\nonumber\\
-				& \triangleq b^{(i)}\label{eq:b}
-				% & \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
-				% & = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P}^{(i)})\nonumber\\
-				% & \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
-			\end{align}
-			Therefore, the approximated current function at iteration $i$ is
-			\begin{equation}\label{eq:z_waveform_approx}
-				\begin{split}
-					% \tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
-					\tilde{z}^{(i)}
-					& = \rho^{(i)}\left(\mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\right) + a^{(i)} b^{(i)}\\
-					& \quad - \frac{3}{8} \beta_4 (\rho^{(i-1')})^2 \left(2 (t_{I,0}^{\prime (i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\right)
-					% & \quad - \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}
-				\end{split}
-			\end{equation}
-			where the Hermitian matrices $\boldsymbol{A}_I^{(i)}$ and $\boldsymbol{A}_P^{(i)}$ are
-			\begin{align}
-				\boldsymbol{A}_I^{(i)}
-				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{2} \beta_4 \rho^{(i-1)} t_{I,0}^{\prime (i-1)} \boldsymbol{H}_{0}^*\label{eq:A_I}\\
-				\boldsymbol{A}_P^{(i)}
-				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{8} \beta_4 \rho^{(i-1)} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\label{eq:A_P}
-				% & \quad + \frac{3}{2} \beta_4 t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_P}
-			\end{align}
-			\begin{figure*}[b]
-				\hrule
-				\begin{align}
-					\tilde{z}'^{(i)}
-					& = \frac{1}{2}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right)\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right) - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{I}^{(i-1)}\boldsymbol{W}_{I}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{I}^{(i)}\boldsymbol{W}_{I}^{(i)})\right)^2\nonumber\\
-					& \quad + \frac{1}{2}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)\left(\rho^{(i)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right) - \frac{1}{4}\left(\rho^{(i-1)} + \mathrm{Tr}(\boldsymbol{A}_{P}^{(i-1)}\boldsymbol{W}_{P}^{(i-1)})\right)^2 - \frac{1}{4}\left(\rho^{(i)} - \mathrm{Tr}(\boldsymbol{A}_{P}^{(i)}\boldsymbol{W}_{P}^{(i)})\right)^2\nonumber\\
-					& \quad + \frac{1}{2}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})(\bar{a}^{(i)} + \bar{b}^{(i)}) - \frac{1}{4}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})^2 - \frac{1}{4}(\bar{a}^{(i)} - \bar{b}^{(i)})^2\label{eq:z_waveform_lb}\\
-					g_n^{(i)}
-					& = \frac{1}{2}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)\left((1-\rho^{(i)}) + W_{I,n,n}^{(i)}\right) - \frac{1}{4}\left((1-\rho^{(i-1)}) + W_{I,n,n}^{(i-1)}\right)^2 - \frac{1}{4}\left((1-\rho^{(i)}) - W_{I,n,n}^{(i)}\right)^2\label{eq:r_power_lb}
-				\end{align}
-			\end{figure*}
-			% A lower bound of \label{eq:z_waveform_approx} is further provided in \ref{eq:z_waveform_lb}. Hence, problem \ref{op:su} is transformed to
-			Hence, problem \ref{op:su} is transformed to
+			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.	Hence, problem \ref{op:su} is transformed to
 			\begin{maxi!}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform_1}}{\label{eq:su_waveform_target}}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint_1}}
+				{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
 				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
@@
 			\end{maxi!}
-			Note that \ref{op:su_waveform_1} involves bilinear terms $\rho\mathrm{Tr}(\boldsymbol{A}_{I/P}\boldsymbol{W}_{I/P})$ and $(1-\rho)W_{I,n,n}$.
-We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g_n(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$.
-Therefore, problem \ref{op:su_waveform_1} is equivalent to
-			\begin{maxi!}
-				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho,\bar{a},\bar{b}}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g_n(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
-				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
-				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
-				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
-				\addConstraint{a \ge \bar{a}}
-				\addConstraint{b \ge \bar{b}}
-			\end{maxi!}
 			We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
-$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\omega}, \omega \in [0,2\pi]$.
-The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
-
+$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$.
+The algorithm is summarized in Algorithm \ref{al:ff_waveform}.
 			\begin{algorithm}
-				\caption{Waveform Optimization}
-				\label{alg:waveform}
+				\caption{FF-IRS: Transmit Waveform Optimization}
+				\label{al:ff_waveform}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},P,Q,\boldsymbol{R}_n,\sigma_n \ \forall n$
-					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $a^{(0)}$, $b^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\State \textbf{Input} $\bar{R},P,Q,\sigma_n,\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
 					\Repeat
 					\State $i \leftarrow i + 1$
-					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
-					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
+					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
 					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
-					\State Update auxiliary $a^{(i)},b^{(i)}$ by \ref{eq:a} and \ref{eq:b}
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
 					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
@@
 					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
-					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ and $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$ for problem \ref{op:su_waveform}
-					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
+					\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
+					\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
 				\end{algorithmic}
@@
 			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points.
-Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
+Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ and power splitting ratio $\rho = 0$ as
 			\begin{maxi!}
@@
 Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$.
-After constructing composite channel by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n=\lvert w_{I,n} \rvert^2$ and waveform phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
+After constructing composite channel $\boldsymbol{h}$ by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and beamforming phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
 Therefore, the optimal information waveform at subband $n$ is
 			\begin{equation}\label{eq:w_wit}
-				w_{I,n}=\sqrt{p_n}e^{j \psi_{I,n}^\star}
+				w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
 			\end{equation}
-			We update IRS and information waveform iteratively by \ref{op:su_irs_wit} and \ref{eq:w_wit} until convergence. The WIT algorithm is summarized in \ref{alg:wit}.
+			We update IRS phase shift by \ref{op:su_irs_wit} and information waveform by \ref{eq:w_wit} until convergence. The WIT initialization algorithm is summarized in \ref{al:ff_wit}.
 			\begin{algorithm}
-				\caption{WIT Initialization}
-				\label{alg:wit}
+				\caption{FF-IRS: WIT Initialization}
+				\label{al:ff_wit}
 				\begin{algorithmic}[1]
 					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
-					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$
 					\Repeat
@@
 					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
-					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_k}
+					\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
 					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
-					\State Obtain optimal waveform phase $\psi_{I,n}^{(i)} \ \forall n$ by \ref{eq:psi}
-					\State Update information waveform $\boldsymbol{w}_I^{(i)}$ by \ref{eq:w_wit}
-					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
-					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \boldsymbol{\phi}^\star$
+					\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
+					\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_wit}
+					\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
+					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{\phi}^\star$
 				\end{algorithmic}

### 2020-06-19 system-model.tex
:pencil: Splitting ratio optimization

@@
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
+			\addConstraint{0 \le \rho \le 1}
 		\end{maxi!}
@@
 				(t_{I,0}^{(i)})^2
-				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_begin}\\
+				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\
 				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
@@
 				& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_approx_end}
+				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}
 			\end{align}
-			\ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
+			\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
 			\begin{figure*}[b]
@@
 			\end{equation}
-			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_approx_begin} -- \ref{eq:t_approx_end} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.	Hence, problem \ref{op:su} is transformed to
+			Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.
+Hence, problem \ref{op:su} is transformed to
 			\begin{maxi!}
@@
 
-		\begin{subsection}{WIT initialization}
+		\begin{subsubsection}{Receive Splitting Ratio Optimization}
+			We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
+In this case, the output DC current is also expressed by \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ defined in \ref{eq:t'}.
+Therefore, problem \ref{op:su} is transformed to
+			\begin{maxi!}
+				{\rho}{z(\rho)}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
+				\addConstraint{0 \le \rho \le 1}
+			\end{maxi!}
+			It can be observed that $z(\rho)$ is a monotonically increasing function of $\rho$ such that the maximum value of \ref{eq:su_ratio_target} is achieved when equality in \ref{eq:su_ratio_constraint} holds, namely
+			\begin{equation}\label{eq:rho}
+				\prod_n \left(1 + \frac{(1 - \rho^\star)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right) = 2^{\bar{R}}
+			\end{equation}
+			The optimal power splitting ratio can be obtained from \ref{eq:rho} in closed form.
+		\end{subsubsection}
+
+		\begin{subsubsection}{WIT Initialization}
 			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points.
@@
 			\end{algorithm}
-		\end{subsection}
+		\end{subsubsection}
 	\end{subsection}

### 2020-06-20 system-model.tex
:art: Add cover
:pencil: Splitting ratio optimization

@@
 \begin{document}
+
+% \input{cover.tex}
 
@@
 In this case, the output DC current is also expressed by \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ defined in \ref{eq:t'}.
-Therefore, problem \ref{op:su} is transformed to
+Since $z(\rho)$ is a monotonically increasing function of $\rho \in [0, 1]$, we replace convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
 			\begin{maxi!}
-				{\rho}{z(\rho)}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
+				{\rho}{\rho}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
 				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
@@
 			\end{maxi!}
-			It can be observed that $z(\rho)$ is a monotonically increasing function of $\rho$ such that the maximum value of \ref{eq:su_ratio_target} is achieved when equality in \ref{eq:su_ratio_constraint} holds, namely
-			\begin{equation}\label{eq:rho}
-				\prod_n \left(1 + \frac{(1 - \rho^\star)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right) = 2^{\bar{R}}
-			\end{equation}
-			The optimal power splitting ratio can be obtained from \ref{eq:rho} in closed form.
+			The optimal power splitting ratio $\rho^\star$ can be obtained from problem \ref{op:su_ratio}.
 		\end{subsubsection}

### 2020-06-27 system-model.tex
:pencil: Update algorithm input
:pencil: Alternating optimization

@@
 	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables.
-In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
+To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio iteratively.
+	% In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
 
-	\begin{subsection}{Frequency-Selective IRS}
+	\begin{subsection}{IRS Phase Shift}
+		\begin{subsubsection}{Frequency-Selective IRS}\label{se:fs_irs}
 			Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients.
@@
 			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, and the phase of the composite channel equals that of the direct channel.
-Moreover, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
-		\begin{equation}\label{eq:psi}
-			\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}
-		\end{equation}
-		By such a phase selection, we have
-		\begin{equation}
-			\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert = \lvert h_{D,n} \rvert \lvert w_{I,n} \rvert + \vert \boldsymbol{v}_n^H\boldsymbol{\phi}_n \rvert \lvert w_{I,n} \rvert
-		\end{equation}
-		Therefore, the original problem \ref{op:su} is reduced to an waveform magnitude optimization problem
-		\begin{maxi!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:su_gp}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \ge \bar{R}}
-			\end{maxi!}
-		\begin{figure*}[b]
-			\hrule
-			\begin{equation}\label{eq:z_gp}
-				\begin{split}
-					z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
-					&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
-					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})(A_n s_{I,n})^*\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
-					&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
-				\end{split}
-			\end{equation}
-		\end{figure*}
-		with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into
-		\begin{mini!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
-				\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \le 1}
-			\end{mini!}
-		Problem \ref{op:su_gp_1} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP).
-The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
-Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
-		\begin{mini}
-			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_2}}{}
-			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-			\addConstraint{{t''}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
-			\addConstraint{2^{\bar{R}}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
-			\addConstraint{\rho + \bar{\rho} \le 1}
-		\end{mini}
-		where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m} \ge 0 \ \forall m$, and $\sum_{m=1}^{M}{\gamma_m}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require successive update.
-At iteration $i$, we choose \cite{Clerckx2018b}
-		\begin{align}
-			\gamma_{I,n,1}^{(i)} & = \left. 1 \middle/ \left(1+\frac{\bar{\rho}^{(i-1)}{A_n^2}(s_{I,n}^{(i-1)})^2}{\sigma_n^2}\right) \right.\label{eq:gamma_I_1}\\
-			\gamma_{I,n,2}^{(i)} & = 1 - \gamma_{I,n,1}^{(i)}\label{eq:gamma_I_2}\\
-			\gamma_{P,m}^{(i)} & =\frac{g_{P,m}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
-		\end{align}
-		and then solve problem \ref{op:su_gp_2}. The algorithm is summarized in Algorithm \ref{al:fs_waveform}.
-		\begin{algorithm}
-			\caption{FS-IRS: Waveform and Splitting Ratio}
-			\label{al:fs_waveform}
-			\begin{algorithmic}[1]
-				\State \textbf{Input} $P, \bar{R}, A_n \ \forall n$ by \ref{eq:h_{k,n}}
-				\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
-				\Repeat
-				\State $i \leftarrow i + 1$
-				\State Update GM exponents $\{\gamma_{I,n}^{(i)},\gamma_{P}^{(i)}\}$ by \ref{eq:gamma_I_1} -- \ref{eq:gamma_P}
-				\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_gp_2}
-				\State Compute output DC current $z^{(i)}$ by \ref{eq:z_gp}
-				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-				\State \textbf{Output} $\boldsymbol{s}_{I/P}^{\star}, \rho^{\star}, z^{\star}$
-			\end{algorithmic}
-		\end{algorithm}
-	\end{subsection}
+		\end{subsubsection}
 
-	\begin{subsection}{Frequency-Flat IRS}
+		\begin{subsubsection}{Frequency-Flat IRS}
 			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
@@
 On top of this, the outer product of composite channel rewrites as
-		\begin{equation}
+			\begin{equation}\label{eq:M}
 				\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
@@
 			where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
-To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio with the others being fixed.
 
-		\begin{subsubsection}{IRS Phase Shift Optimization}\label{se:fs_irs}
 			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
@@
 			\begin{algorithm}
-				\caption{FF-IRS: IRS Phase Shift}
+				\caption{FF-IRS: Phase Shift}
 				\label{al:ff_irs}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
-					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
+					\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
+					\State Construct $\boldsymbol{M},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
 					\Repeat
-					\State $i \leftarrow i + 1$
+					\State $i \gets i + 1$
 					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
@@
 					\State Select best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
-					\State Compute phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-					\State \textbf{Output} $\theta_l \ \forall l$
+					\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+					\State \textbf{Output} $\theta_l^\star \ \forall l$
+				\end{algorithmic}
+			\end{algorithm}
+		\end{subsubsection}
+	\end{subsection}
+
+	\begin{subsection}{Waveform and Splitting Ratio}
+		\begin{subsubsection}{Geometric Programming}
+			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
+			\begin{equation}\label{eq:psi}
+				\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}
+			\end{equation}
+			By such a phase selection, we have
+			\begin{equation}
+				\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert = \lvert h_{D,n} \rvert \lvert w_{I,n} \rvert + \vert \boldsymbol{v}_n^H\boldsymbol{\phi}_n \rvert \lvert w_{I,n} \rvert
+			\end{equation}
+			Also, denote the waveform amplitude at subband $n$ as
+			\begin{equation}\label{eq:s}
+				s_{I/P,n} = \lvert w_{I/P,n} \rvert e^{j\psi_{I/P,n}}
+			\end{equation}
+			which is further collected into $\boldsymbol{s}_{I/P} \in \mathbb{C}^{N \times 1}$. Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem
+			\begin{maxi!}
+					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:su_gp}}{}
+					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \ge \bar{R}}
+				\end{maxi!}
+			\begin{figure*}[b]
+				\hrule
+				\begin{equation}\label{eq:z_gp}
+					\begin{split}
+						z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
+						&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
+						&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})(A_n s_{I,n})^*\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
+						&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
+					\end{split}
+				\end{equation}
+			\end{figure*}
+			with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into
+			\begin{mini!}
+					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
+					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
+					\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
+					\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \le 1}
+				\end{mini!}
+			Problem \ref{op:su_gp_1} is a reversed GP which can be transformed to standard GP.
+The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
+			\begin{mini}
+				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_2}}{}
+				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
+				\addConstraint{{t''}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
+				\addConstraint{2^{\bar{R}}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
+				\addConstraint{\rho + \bar{\rho} \le 1}
+			\end{mini}
+			where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m} \ge 0 \ \forall m$, and $\sum_{m=1}^{M}{\gamma_m}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require successive update.
+At iteration $i$, we choose \cite{Clerckx2018b}
+			\begin{align}
+				\gamma_{I,n,1}^{(i)} & = \left. 1 \middle/ \left(1+\frac{\bar{\rho}^{(i-1)}{A_n^2}(s_{I,n}^{(i-1)})^2}{\sigma_n^2}\right) \right.\label{eq:gamma_I_1}\\
+				\gamma_{I,n,2}^{(i)} & = 1 - \gamma_{I,n,1}^{(i)}\label{eq:gamma_I_2}\\
+				\gamma_{P,m}^{(i)} & =\frac{g_{P,m}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
+			\end{align}
+			and then solve problem \ref{op:su_gp_2}. The GP algorithm is summarized in Algorithm \ref{al:waveform_split_ratio_gp}.
+			\begin{algorithm}
+				\caption{GP: Waveform and Splitting Ratio}
+				\label{al:waveform_split_ratio_gp}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\bar{R},\epsilon,\sigma_n \ \forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
+					\State Retrieve channel amplitude response $A_n \ \forall n$ by \ref{eq:h_{k,n}}
+					\Repeat
+					\State $i \gets i + 1$
+					\State Update GM exponents $\{\gamma_{I,n}^{(i)},\gamma_{P}^{(i)}\}$ by \ref{eq:gamma_I_1} -- \ref{eq:gamma_P}
+					\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_gp_2}
+					\State Compute output DC current $z^{(i)}$ by \ref{eq:z_gp}
+					\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+					\State Recover waveform $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:psi} and \ref{eq:s}
+					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
 				\end{algorithmic}
@@
 
-		\begin{subsubsection}{Transmit Waveform Optimization}
-			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ and $\rho$ are obtained, introduce auxiliary variables
+		\begin{subsubsection}{Semi-Definite Relaxation}
+			In this case, waveform and splitting ratio are updated iteratively until convergence.
+			\begin{paragraph}{Transmit Waveform}
+				Consider the waveform optimization subproblem. Once $\boldsymbol{\phi}$ and $\rho$ are obtained, introduce auxiliary variables
 				\begin{equation}\label{eq:t'}
@@
 $\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$.
-The algorithm is summarized in Algorithm \ref{al:ff_waveform}.
+The algorithm is summarized in Algorithm \ref{al:waveform_sdr}.
 				\begin{algorithm}
-				\caption{FF-IRS: Transmit Waveform Optimization}
-				\label{al:ff_waveform}
+					\caption{SDR: Transmit Waveform}
+					\label{al:waveform_sdr}
 					\begin{algorithmic}[1]
-					\State \textbf{Input} $\bar{R},P,Q,\sigma_n,\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
-					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$ by \ref{eq:R_n,phi}
+						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$ by \ref{eq:t'}
+						\State Construct $\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
 						\Repeat
-					\State $i \leftarrow i + 1$
+						\State $i \gets i + 1$
 						\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
@@
 				\end{algorithm}
-		\end{subsubsection}
+			\end{paragraph}
 
-		\begin{subsubsection}{Receive Splitting Ratio Optimization}
+			\begin{paragraph}{Receive Splitting Ratio Optimization}
 				We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
-In this case, the output DC current is also expressed by \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ defined in \ref{eq:t'}.
+In this case, the output DC current is also expressed in \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
 Since $z(\rho)$ is a monotonically increasing function of $\rho \in [0, 1]$, we replace convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
@@
 				\end{maxi!}
-			The optimal power splitting ratio $\rho^\star$ can be obtained from problem \ref{op:su_ratio}.
+				The optimal power splitting ratio $\rho^\star$ can be obtained by solving problem \ref{op:su_ratio}.
+			\end{paragraph}
 		\end{subsubsection}
+	\end{subsection}
 
+	\begin{subsection}{R-E Region Characterization}
 		\begin{subsubsection}{WIT Initialization}
-			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points.
-Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ and power splitting ratio $\rho = 0$ as
+			To characterize the R-E region, we initialize the algorithm to WIT mode ($\rho = 0$) and reduce the rate constraint gradually to obtain the boundary points.
+			\begin{paragraph}{FS-IRS}
+				As discussed in Section \ref{se:fs_irs}, the optimal FS-IRS and composite channel are obtained in closed form.
+We use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and information waveform phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
+Hence, the optimal information waveform at subband $n$ is
+				\begin{equation}\label{eq:w_{I,n}}
+					w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
+				\end{equation}
+			\end{paragraph}
+			\begin{paragraph}{FF-IRS}
+				Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
 				\begin{maxi!}
@@
 				\end{maxi!}
-			Problem \ref{op:su_irs_wit} can be solved after SDR.
-Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$.
-After constructing composite channel $\boldsymbol{h}$ by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and beamforming phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
-Therefore, the optimal information waveform at subband $n$ is
-			\begin{equation}\label{eq:w_wit}
-				w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
-			\end{equation}
-			We update IRS phase shift by \ref{op:su_irs_wit} and information waveform by \ref{eq:w_wit} until convergence. The WIT initialization algorithm is summarized in \ref{al:ff_wit}.
+				Problem \ref{op:su_irs_wit} can be solved after SDR, and a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method.
+$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$.
+We then construct composite channel $\boldsymbol{h}$ by \ref{eq:h_k} and obtain the optimal information waveform from \ref{eq:w_{I,n}}.
+FF-IRS and information waveform are updated iteratively until convergence.
+The WIT algorithm for FF-IRS is summarized in Algorithm \ref{al:ff_wit}.
 				\begin{algorithm}
@@
 					\begin{algorithmic}[1]
-					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
-					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$
+						\State \textbf{Input} $\boldsymbol{h}_D, \boldsymbol{h}_I, \boldsymbol{h}_R, P, Q, \epsilon, \sigma_n$
+						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_I^{(0)}$
+						\State Construct $\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
 						\Repeat
-					\State $i \leftarrow i + 1$
+						\State $i \gets i + 1$
 						\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
@@
 						\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
-					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
+						\State Obtain optimal power allocation $(p_n^{(i)})^\star \ \forall n$ by water-filling algorithm
 						\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
-					\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_wit}
+						\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_{I,n}}
 						\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
-					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{\phi}^\star$
+						\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+						\State \textbf{Output} $\boldsymbol{w}_I^\star,\theta_l^\star \ \forall l$
 					\end{algorithmic}
 				\end{algorithm}
+			\end{paragraph}
+		\end{subsubsection}
+
+		\begin{subsubsection}{R-E Sample}
+			Denote $S$ as the number of samples in the R-E boundary.
+			\begin{paragraph}{FS-IRS}
+				Since the optimal composite channel is fixed, we optimize the splitting ratio and waveform alternatively with the other being fixed. The procedure is included in Algorithm \ref{al:fs_ao}.
+				\begin{algorithm}
+					\caption{FS-IRS: AO Algorithm}
+					\label{al:fs_ao}
+					\begin{algorithmic}[1]
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}, P, Q, S, \epsilon, \sigma_n \ \forall n$
+						\State \textbf{Initialize} $\rho_0^{\star} = 0$, $\boldsymbol{w}_{0,I}^{\star}$ by \ref{eq:w_{I,n}} and $\boldsymbol{w}_{0,P}^{\star} = \boldsymbol{0}$
+						\For{$s \gets 1, S$}
+						\State $i \gets 0$\label{st:inner_begin}
+						\State Initialize splitting ratio and waveform by previous solution $\rho_s^{(0)} = \rho_{s-1}^{\star}, \boldsymbol{w}_{s,I/P}^{(0)}=\boldsymbol{w}_{s-1,I/P}^{\star}$
+						\Repeat
+						\State $i \gets i + 1$
+						\State Update splitting ratio $\rho_s^{(i)}$ by solving problem \ref{op:su_ratio}
+						\State Update waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by Algorithm \ref{al:waveform_sdr}
+						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$\label{st:inner_end}
+						\State \textbf{Return} ($R_s^\star, z_s^\star$)
+						\EndFor
+					\end{algorithmic}
+				\end{algorithm}
+			\end{paragraph}
+
+			\begin{paragraph}{FF-IRS}
+				We propose a two-layer AO algorithm to obtain the R-E region for FF-IRS-assisted SWIPT, where the inner loop updates the splitting ratio and waveform while the outer loop updates the IRS phase shifts, until convergence is achieved.
+The algorithm is summarized in Algorithm \ref{al:ff_ao}.
+				\begin{algorithm}
+					\caption{FF-IRS: AO Algorithm}
+					\label{al:ff_ao}
+					\begin{algorithmic}[1]
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D, \boldsymbol{h}_I, \boldsymbol{h}_R, P, Q, S, \epsilon, \sigma_n \ \forall n$
+						\State \textbf{Initialize} $\rho_0^{\star} = 0$, $\boldsymbol{\phi}_0^{\star}, \boldsymbol{w}_{0,I}^{\star}$ by Algorithm \ref{al:ff_wit} and $\boldsymbol{w}_{0,P}^{\star} = \boldsymbol{0}$
+						\For{$s \gets 1, S$}
+						\State $i \gets 0$
+						\State Initialize IRS, splitting ratio and waveform by previous solution $\boldsymbol{\phi}_s^{(0)} = \boldsymbol{\phi}_{s-1}^{\star}, \rho_s^{(0)} = \rho_{s-1}^{\star}, \boldsymbol{w}_{s,I/P}^{(0)}=\boldsymbol{w}_{s-1,I/P}^{\star}$
+						\State Initialize composite channel $\boldsymbol{h}_s^{(0)}$ by \ref{eq:h_k}
+						\State \textit{Inner loop}: Update splitting ratio $\rho_s^{(0)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(0)}$ by SDR (Algorithm \algref{al:fs_ao}{st:inner_begin} -- \algref{al:fs_ao}{st:inner_end}) or GP (Algorithm \ref{al:waveform_split_ratio_gp})
+						\Repeat
+						\State $i \gets i + 1$
+						\State Update IRS phase shift $\boldsymbol{\phi}_s^{(i)}$ by Algorithm \ref{al:ff_irs}
+						\State Update composite channel $\boldsymbol{h}_s^{(i)}$ by \ref{eq:h_k}
+						\State \textit{Inner loop}: Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by SDR (Algorithm \algref{al:fs_ao}{st:inner_begin} -- \algref{al:fs_ao}{st:inner_end}) or GP (Algorithm \ref{al:waveform_split_ratio_gp})
+						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$
+						\State \textbf{Return} ($R_s^\star, z_s^\star$)
+						\EndFor
+					\end{algorithmic}
+				\end{algorithm}
+			\end{paragraph}
 		\end{subsubsection}

### 2020-06-29 main.tex
:pencil: Abstract

--- 2020-06-27 system-model.tex
@@
 
+\begin{abstract}
+	Simultaneous Wireless Information and Power Transfer (SWIPT) is limited by the low power level of the receive Radio-Frequency (RF) signal.
+To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain by adjusting reflecting elements, which compensates the propagation loss and boosts the energy efficiency with low power consumption.
+This paper investigates an IRS-aided multiuser Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where the single-antenna Access Point (AP) transmits information and energy simultaneously to multiple single-antenna users under the assist of IRS.
+We aim to maximize the weighted sum Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the phase shifts at the IRS, and the power splitting ratio at all users.
+The problem is transformed to a current maximization problem subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
+Simulation results demonstrated significant R-E region enlargement over benchmark schemes when IRS is properly configured.
+\end{abstract}
+
 \begin{section}{Introduction}
+	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
 		With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
@@
 Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range.
-Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the radio-frequency (RF) band.
+Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
 It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner.
@@
 
-	The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the rate-energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
-Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes and Power Splitting (PS) that splits the received signal into individual components.
-On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup.
+		The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
+Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
+On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup.
 Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
 Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
-However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level.
-The authors also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
+However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
 From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
@@
 In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
-By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes to ensure WPT is only activated at the points with large offset.
+By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adapted conventional modulation schemes to ensure WPT is only activated at the points with large offset.
 Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin.
@@
 In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
+	\end{subsection}
 
+	\begin{subsection}{Intelligent Reflecting Surface}
 		Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency.
@@
 Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
-It also contributes to a quadratic increase of received signal power with the number of reflectors, which can be interpreted as a Maximum Ratio Combining (MRC) receiver overlapped to a Maximum Ratio Transmission (MRT) transmitter.
+Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, which can be interpreted as a Maximum Ratio Combining (MRC) superposed to a Maximum Ratio Transmission (MRT).
 
 		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and multi-path fading.
-At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to solve indoor signal blockage problem.
+At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage.
 Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR).
 The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}.
-In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was performed through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially evaluates the cascaded channel of each IRS element with the others switched off.
+In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off.
 Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
 Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems.
-A practical transmission protocol was proposed in \cite{Yang2019}, where the authors exploited spatial correlation to reduce estimation overhead and optimization complexity by assuming adjacent elements share a common reflection coefficient.
+\cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient.
 On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}.
-\cite{Yang2020} proposed a dynamic passive beamforming strategy that adapts IRS over time slots to create time-varying channels within coherence time and exploits the diversity by updating resource allocation and IRS configuration alternatively.
+By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB).
 Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
+	\end{subsection}
 
+	\begin{subsection}{IRS-aided SWIPT}
 		The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
-The fairness issue was then considered in \cite{Tang2019}, which assumed perfect energy interference cancellation and maximized the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques.
+Assuming linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
+The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques based on perfect energy interference cancellation.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients.
@@
 However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
+	\end{subsection}
+
+	\begin{subsection}{Research Proposal}
+		In this paper, we consider an IRS-aided multiuser Single-Input Single-Output (SISO) OFDM SWIPT system based on practical nonlinear harvester model.
+	\end{subsection}
 \end{section}
@@
 \begin{section}{System Model}
-	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation.
+	Consider an IRS-aided multiuser SISO OFDM SWIPT system where the IRS assists the information and energy transmission of all users.
 The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.

### 2020-06-30 main.tex
:pencil: System model

@@
 \begin{abstract}
-	Simultaneous Wireless Information and Power Transfer (SWIPT) is limited by the low power level of the receive Radio-Frequency (RF) signal.
-To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain by adjusting reflecting elements, which compensates the propagation loss and boosts the energy efficiency with low power consumption.
+	Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the low power level of the receive Radio-Frequency (RF) signal.
+To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain to compensate the propagation loss and boost the energy efficiency with a low power consumption.
 This paper investigates an IRS-aided multiuser Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where the single-antenna Access Point (AP) transmits information and energy simultaneously to multiple single-antenna users under the assist of IRS.
-We aim to maximize the weighted sum Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the phase shifts at the IRS, and the power splitting ratio at all users.
-The problem is transformed to a current maximization problem subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
-Simulation results demonstrated significant R-E region enlargement over benchmark schemes when IRS is properly configured.
+We aim to maximize the weighted sum Rate-Energy (R-E) region via jointly optimizing the phase shifts at the IRS, the transmit waveform at the AP, and the power splitting ratio for all users.
+The problem is equivalent to a current maximization problems subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
+Numerical results demonstrated that dedicated power signal is beneficial to multicarrier SWIPT, while IRS brings significant R-E region enlargement over benchmark schemes when properly configured.
 \end{abstract}
@@
 On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup.
-Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
+Information and power beamforming was then considered in multiuser Multi-Input Single-Output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
 Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
-However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
+However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
 From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
@@
 
-		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and multi-path fading.
+		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and fading.
 At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage.
@@
 The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}.
-In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off.
+In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off.
 Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
-Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems.
+Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency-Division Multiplexing (OFDM) systems.
 \cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient.
@@
 Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
+
+		To the best of authors' knowledge, most existing papers assume a Frequency-Flat (FF) IRS where all elements reflect the signal of different frequency equally.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS since active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics \cite{Anwar2018}.
 	\end{subsection}
@@
 		The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Assuming linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
-The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques based on perfect energy interference cancellation.
+Based on linear harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
+The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power on the assumption of perfect energy interference cancellation.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated and a single energy stream can satisfy the energy constraints of all ERs.
 In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms.
@@
 
-	\begin{subsection}{Research Proposal}
-		In this paper, we consider an IRS-aided multiuser Single-Input Single-Output (SISO) OFDM SWIPT system based on practical nonlinear harvester model.
+	\begin{subsection}{Objective and Methodology}
+		In this paper, we study an IRS-aided multiuser Single-Input Single-Output (SISO) system where the IRS assists the information and energy transmission of all users.
+A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g.
+OFDM) to boost the energy transfer efficiency with no interference.
+The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
+Different from previous research, this paper investigates the fundamental impact of harvester nonlinearity on waveform and IRS design.
+We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints.
+To reduce the design complexity, we	propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) technique.
+It was observed that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively.
+Also, FF-IRS produces a significant channel amplification and R-E enhancement especially when developed near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
 	\end{subsection}
@@
 \begin{section}{System Model}
-	Consider an IRS-aided multiuser SISO OFDM SWIPT system where the IRS assists the information and energy transmission of all users.
-The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
-Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$.
+	Consider an IRS-aided multiuser SISO OFDM SWIPT system where the transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
+We assume a total bandwidth $B$ with evenly-spaced carriers around center frequency $f_c$.
 Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
-Suppose each subband is allocated to one user per time slot.
-It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}.
-Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity.
-Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system.
-A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame.
-The signals reflected by IRS for two and more times are assumed negligible and thus not considered.
-Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}.
-Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands.
-Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff.
-Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester.
-In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\lambda)$ and $\lambda$ respectively.
-Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\lambda=1$ and wireless information transfer (WIT) with $\lambda=0$.
-The adjustment of $\lambda$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots.
-In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design.
-Perfect synchronization is assumed among the three parties in both scenarios.
-
+Each subband is allocated to one user per time slot.
+Perfect Channel State Information (CSI) with negligible training overhead is considered to explore the analytical upper-bound of the proposed design.
+A quasi-static block fading channel model is considered for all links and we focus on one particular block where the channels are approximately unchanged.
+We characterize and compare the R-E region achieved by TS and PS receivers.
+Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
+In comparison, PS splits the received signal into data and energy streams for ID and EH purposes, and the splitting ratio $\rho$ is coupled with waveform and IRS design.
+Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
 	\begin{subsection}{Transmit Signal}
@@
 		\end{equation}
-		where $w_{I/P,n}=s_{I/P,n}e^{j\psi_{I/P,n}}$ collects the magnitude and phase of the information and power signal at frequency $n$.
+		where $w_{I/P,n}=s_{I/P,n}e^{j\psi_{I/P,n}}$ collects the magnitude and phase of the information and power signal at subband $n$.
 We further define the waveform vectors $\boldsymbol{w}_{I/P}=[w_{I/P,1},\dots,w_{I/P,N}]^T \in \mathbb{C}^{N{\times}1}$.
@@
 On top of this, the IRS matrix is constructed by collecting the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
-The IRS-aided link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user $k$ channel, which for user $k$ over subband $n$ is
+The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel, which for user $k$ over subband $n$ is
 		\begin{equation}\label{eq:h_{E,k,n}}
@@
 	\begin{subsection}{Information Decoder}
-		% ? OFDM interference
-		A major benefit of the superposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
+		A major benefit of the proposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
 		\begin{equation}\label{eq:R_k}
@@
 
-		With the assumption of evenly spaced frequencies, we have $\mathcal{E}\left\{y_k(t)^i\right\}=0 \ \forall i \ \mathrm{odd}$ such that the related terms has no contribution to DC components.
+		With the assumption of evenly spaced frequencies, we have $\mathcal{E}\left\{y_k(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
 For simplicity, we truncate the infinite series to the $n_0$-th order.
-Maximizing a truncated \ref{eq:i_k} is equivalent to maximizing a monotonic function \cite{Clerckx2016a}
+As proved in \cite{Clerckx2016a}, maximizing a truncated \ref{eq:i_k} is equivalent to maximizing a monotonic function
 		\begin{equation}\label{eq:z_k}
@@
 				& = \frac{1}{2}\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\label{eq:z_k_terms_begin}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
 				& = \frac{3}{4}\left(\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\right)^2\\
-				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2\\
+				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2\\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
 				& = \frac{1}{2}\sum_n{(h_{k,n}w_{P,n})(h_{k,n}w_{P,n})^*}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P\\
+				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
@@
 				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^*\right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}^*\boldsymbol{h}_k)\label{eq:z_k_channel}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_P)\label{eq:z_k_waveform}
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^*\right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_k_channel}\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_k_waveform}
 			\end{align}
@@
 	\begin{subsection}{Weighted Sum Rate-Energy Region}
-		Define the achievable weighted sum rate-energy (WSR-E) region as
+		Define the achievable weighted sum R-E region as
 		\begin{equation}
@@
 				C_{R-I}(P)
-				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
+				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
 				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
@@
 	\begin{maxi!}
-			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{}
+			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
 			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}
+			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraing}
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
@@
 		\end{maxi!}
-	Problem \ref{op:su} is intricate due to the non-convex objective function with coupled variables.
-To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the IRS phase shift, transmit waveform, and receive power splitting ratio iteratively.
-	% In the next section, we propose waveform and phase shift design algorithms for frequency-flat and frequency-selective IRS, respectively.
+	Problem \ref{op:su} is intricate due to the non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraing} with coupled variables.
+To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.
 
@@
 		\begin{subsubsection}{Frequency-Selective IRS}\label{se:fs_irs}
-			Each element in frequency-selective IRS is expected to provide subband-dependent reflection coefficients.
-Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total degree of freedom (DoF) of $NL$.
+			In the ideal case, each element in FS-IRS is expected to provide subband-dependent reflection coefficients.
+Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total Degree of Freedom (DoF) of $NL$.
 Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned.
-Therefore, we choose the phase shift of element $l$ at subband $n$ as
+Therefore, we simply select the phase shift of element $l$ at subband $n$ as
 			\begin{equation}\label{eq:theta}
@@
 			\end{equation}
-			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, and the phase of the composite channel equals that of the direct channel.
+			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, which ensures the direct, extra and composite channels have the same phase.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Frequency-Flat IRS}
-			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
+			In contrast, FF-IRS reflects all subbands equally with a DoF of $L$. We observe that
 			\begin{equation}
@@
 			with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$.
-On top of this, the outer product of composite channel rewrites as
+Therefore, the outer product of composite channel rewrites as
 			\begin{equation}\label{eq:M}
@@
 			where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
-
-			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
+On top of this, we formulate the FF-IRS phase shift optimization subproblem as follows.
+With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
 			\begin{equation}\label{eq:t}
@@
 			\begin{equation}\label{eq:C_{I/P,n}}
-				\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
+				\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H
 			\end{equation}
-			Therefore, \ref{eq:z_k_channel} rewrites as
+			and $\boldsymbol{C}_{I/P,n} \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
 			\begin{equation}\label{eq:z_irs}
@@
 			\end{align}
-			\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to corresponding terms such that the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
+			\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to the corresponding terms in \ref{eq:z_irs}, and the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
 			\begin{figure*}[b]
@@
 Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}.
-First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
+We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
 Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$.
-Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}.
+Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one maximizes the objective function \ref{eq:su_irs_target}.
 Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$ by \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$
 					\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
@@
 					\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
-					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
+					\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
 					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-					\State Select best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
+					\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
 					\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
@@
 		\begin{subsubsection}{Geometric Programming}
-			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} that the optimal phases of information and power waveform are both match to the composite channel as
+			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform} that the optimal phases of information and power waveform are both match to the composite channel as
 			\begin{equation}\label{eq:psi}
@@
 			\begin{equation}\label{eq:s}
-				s_{I/P,n} = \lvert w_{I/P,n} \rvert e^{j\psi_{I/P,n}}
+				s_{I/P,n} = \lvert w_{I/P,n} \rvert
 			\end{equation}
@@
 						&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
-						&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})(A_n s_{I,n})^*\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
+						&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})^2\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
 						&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
@@
 				\end{mini!}
-			Problem \ref{op:su_gp_1} is a reversed GP which can be transformed to standard GP.
-The idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+			Problem \ref{op:su_gp_1} can be transformed to standard GP by first decomposing the information and power posynomials as sum of monomials, then deriving their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
 Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
@@
 				We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
-$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}, \ q=1,\dots,Q$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi}$, $\xi \sim \mathcal{U}[0,2\pi)$.
+$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi_{q,n}}, \ \xi_{q,n} \sim \mathcal{U}[0,2\pi) \ \forall q, n$.
 The algorithm is summarized in Algorithm \ref{al:waveform_sdr}.
@@
 					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$ by \ref{eq:R_n,phi}
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$
 						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$ by \ref{eq:t'}
@@
 						\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
-						\State Select best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
+						\State Select the best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
 						\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
@@
 
-			\begin{paragraph}{Receive Splitting Ratio Optimization}
+			\begin{paragraph}{Receive Splitting Ratio}
 				We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
 In this case, the output DC current is also expressed in \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
-Since $z(\rho)$ is a monotonically increasing function of $\rho \in [0, 1]$, we replace convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
+Since $z(\rho)$ is a monotonically increasing function over $\rho \in [0, 1]$, we replace the convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
 				\begin{maxi!}
@@
 				The optimal power splitting ratio $\rho^\star$ can be obtained by solving problem \ref{op:su_ratio}.
+			\end{paragraph}
+
+			\begin{paragraph}{Alternating Optimization: Inner Loop}
+				As summarized in Algorithm \ref{al:inner_loop}, the inner loop updates the waveform and splitting ratio iteratively until convergence.
+				\begin{algorithm}
+					\caption{Inner Loop: Waveform and Splitting Ratio}
+					\label{al:inner_loop}
+					\begin{algorithmic}[1]
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$
+						\State \textbf{Initialize} $\boldsymbol{w}_{I/P}^{(0)}$
+						\State $i \gets 0$
+						\Repeat
+						\State $i \gets i + 1$
+						\State Update splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_ratio}
+						\State Update waveform $\boldsymbol{w}_{I/P}^{(i)}$ by Algorithm \ref{al:waveform_sdr}
+						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+						\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
+					\end{algorithmic}
+				\end{algorithm}
 			\end{paragraph}
@@
 				As discussed in Section \ref{se:fs_irs}, the optimal FS-IRS and composite channel are obtained in closed form.
-We use water-filling algorithm and matched filter to obtain optimal power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and information waveform phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively.
+We use water-filling algorithm to obtain the best power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and combine with the waveform phase selection in \ref{eq:psi}.
 Hence, the optimal information waveform at subband $n$ is
@@
 						\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
-						\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
+						\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
 						\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-						\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
+						\State Select the best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
 						\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
@@
 		\begin{subsubsection}{R-E Sample}
-			Denote $S$ as the number of samples in the R-E boundary.
+			Denote $S$ as the number of samples in the R-E boundary. Starting from WIT mode, we initialize each following sample with the solution of the previous sample.
 			\begin{paragraph}{FS-IRS}
-				Since the optimal composite channel is fixed, we optimize the splitting ratio and waveform alternatively with the other being fixed. The procedure is included in Algorithm \ref{al:fs_ao}.
+				Since the optimal composite channel is fixed, we only optimize the splitting ratio and waveform by either GP or inner loop method. The procedure is included in Algorithm \ref{al:fs_ao}.
 				\begin{algorithm}
@@
 						\State $i \gets i + 1$
-						\State Update splitting ratio $\rho_s^{(i)}$ by solving problem \ref{op:su_ratio}
-						\State Update waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by Algorithm \ref{al:waveform_sdr}
-						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$\label{st:inner_end}
+						\State Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
+						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$
 						\State \textbf{Return} ($R_s^\star, z_s^\star$)
@@
 			\begin{paragraph}{FF-IRS}
-				We propose a two-layer AO algorithm to obtain the R-E region for FF-IRS-assisted SWIPT, where the inner loop updates the splitting ratio and waveform while the outer loop updates the IRS phase shifts, until convergence is achieved.
+				For SWIPT assisted by FF-IRS, we propose a two-layer AO algorithm to maximize the R-E region where the outer loop updates the phase shifts and the inner loop updates the splitting ratio and waveform until convergence.
 The algorithm is summarized in Algorithm \ref{al:ff_ao}.
@@
 						\State Initialize composite channel $\boldsymbol{h}_s^{(0)}$ by \ref{eq:h_k}
-						\State \textit{Inner loop}: Update splitting ratio $\rho_s^{(0)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(0)}$ by SDR (Algorithm \algref{al:fs_ao}{st:inner_begin} -- \algref{al:fs_ao}{st:inner_end}) or GP (Algorithm \ref{al:waveform_split_ratio_gp})
+						\State Update splitting ratio $\rho_s^{(0)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
 						\Repeat
@@
 						\State Update composite channel $\boldsymbol{h}_s^{(i)}$ by \ref{eq:h_k}
-						\State \textit{Inner loop}: Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by SDR (Algorithm \algref{al:fs_ao}{st:inner_begin} -- \algref{al:fs_ao}{st:inner_end}) or GP (Algorithm \ref{al:waveform_split_ratio_gp})
+						\State Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
 						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$

### 2020-07-01 slides.tex
:pencil: WPT basics

\documentclass[9pt]{beamer}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cuted}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{siunitx}

\usetheme{Warsaw}

\AtBeginSection[]
{
    \begin{frame}
        \frametitle{Table of Contents}
        \tableofcontents[currentsection]
    \end{frame}
}

\title[Waveform and Passive Beamforming Design for IRS-Aided SWIPT]{Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer}
\author{Yang Zhao}
\institute{Department of Electrical and Electronic Engineering\\ Imperial College London}
\date{Early Stage Assessment, \today}

\begin{document}

\frame{\titlepage}

\begin{section}{Introduction and Review}
	\begin{subsection}{From WPT to SWIPT}
		\begin{frame}{What is WPT?}
			\textbf{Wireless Power Transfer} (WPT) varies electromagnetic fields to deliver power.
			\begin{table}
				\scriptsize
				\caption{WPT Technologies}
				\begin{tabular}{|l|l|l|l|l|l|}
					\hline
					Categories                  & Technology                 & Devices           & Power                        & Frequency          & Range           \\ \hline
					\multirow{3}{*}{Near-field} & Magnetic resonant coupling & Resonators        & Up to 10 \si{\W}             & kHz -- MHz         & m               \\ \cline{2-6}
												& Inductive coupling         & Wire coils        & Up to 10 \si{\W}             & Hz -- MHz          & mm -- cm        \\ \cline{2-6}
												& Capacitive coupling        & Metal plates      & Up to 1 \si{\W}              & kHz -- MHz         & mm              \\ \hline
					\multirow{2}{*}{Far-field}  & \alert{RF waves}           & \alert{Rectennas} & \alert{\si{\uW} -- \si{\mW}} & \alert{MHz -- GHz} & \alert{m -- km} \\ \cline{2-6}
												& Light waves                & Lasers            & \si{\uW} -- \si{\mW}         & THz                & km              \\ \hline
				\end{tabular}
			\end{table}
		\end{frame}

		\begin{frame}{WPT by RF waves}
			\textbf{Energy flow}: DC $\to$ RF $\to$ RF $\to$ DC
			\begin{figure}
				\centering
				\includegraphics[width=\textwidth]{assets/wpt.eps}
			\end{figure}
			\textbf{Pros}:
			\begin{itemize}
				\item long range (up to hundreds of \si{\m}) with NLoS support
				\item compact receiver (few \si{\cm}), easy integration
				\item suitable for mobile devices
			\end{itemize}
			\textbf{Cons}:
			\begin{itemize}
				\item low power level (\si{\uW} -- \si{\mW})
				\item low energy harvesting efficiency (40\% at 100 \si{\uW}, 20\% at 10 \si{\uW})
			\end{itemize}
		\end{frame}
	\end{subsection}
\end{section}
\end{document}

### 2020-07-02 main.tex
:pencil: Revise squared gain

@@
 Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
-Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, which can be interpreted as a Maximum Ratio Combining (MRC) superposed to a Maximum Ratio Transmission (MRT).
+Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, since more reflectors boost the power collected by IRS and increase the array gain in its equal gain transmission.
 
-		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and fading.
+		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
 At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage.

### 2020-07-02 slides.tex
:pencil: SWIPT and IRS

@@
 \usepackage{multirow}
+\usepackage{subcaption}
+
 \usepackage{siunitx}
+\DeclareSIUnit{\belmilliwatt}{Bm}
+\DeclareSIUnit{\dBm}{\deci\belmilliwatt}
+
+\usepackage{blindtext}
+\newcommand\blfootnote[1]{%
+\begingroup
+\renewcommand\thefootnote{}\footnote{#1}%
+\addtocounter{footnote}{-1}%
+\endgroup
+}
 
@@
 
-\AtBeginSection[]
+\AtBeginSection
 {
@@
 \begin{section}{Introduction and Review}
-	\begin{subsection}{From WPT to SWIPT}
+	\begin{subsection}{WPT}
 		\begin{frame}{What is WPT?}
 			\textbf{Wireless Power Transfer} (WPT) varies electromagnetic fields to deliver power.
+			\vspace{1em}
 			\begin{table}
@@
 			\end{table}
+			\vspace{1em}
+			\textbf{Characteristics}:
+			\begin{itemize}
+				\item no wires and batteries
+				\item everlasting, controllable, reliable, sustainable
+			\end{itemize}
 		\end{frame}
@@
 			\end{itemize}
+			\blfootnote{Figure from \cite{Clerckx2018a}}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{SWIPT}
+		\begin{frame}{Why RF waves?}
+			RF waves enables:
+			\begin{itemize}
+				\item Wireless communication (WIT)
+				\item WPT
+			\end{itemize}
+			\vspace{1em}
+			\textbf{Simultaneous Wireless Information and Power Transfer} (SWIPT): downlink WIT and WPT at the same time. Receivers can be either separated or \alert{co-located}.
+			\vspace{1em}
+			\begin{figure}
+				\centering
+				\begin{subfigure}{0.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/wipt_receiver_separated.eps}
+					\caption{Separated}
+				\end{subfigure}%
+				\begin{subfigure}{0.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/wipt_receiver_colocated.eps}
+					\caption{Co-located}
+				\end{subfigure}
+				\caption{SWIPT receivers}
+			\end{figure}
+			\blfootnote{Figure from \cite{Clerckx2019}}
+		\end{frame}
+
+		\begin{frame}{Co-located receiver architecture}
+			Two practical receiver architecture:
+			\begin{itemize}
+				\item \textbf{Time-Switching} (TS) switches between Information Decoding (ID) and Energy Harvesting (EH) modes on time basis.
+				\item \textbf{Power-Splitting} (PS) splits the received signal into individual components for ID and EH.
+			\end{itemize}
+			\begin{figure}
+				\centering
+				\begin{subfigure}{0.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/time_switching.eps}
+					\caption{TS}
+				\end{subfigure}%
+				\begin{subfigure}{0.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/power_splitting.eps}
+					\caption{PS}
+				\end{subfigure}
+				\caption{Co-located receiver architecture}
+				\begin{block}{Design issue}
+					\begin{itemize}
+						\item TS can be achieved by a time sharing between WIT and WPT. Waveform is optimized individually for both cases.
+						\item In PS, the splitting ratio $\rho$ is coupled with the waveform design.
+					\end{itemize}
+				\end{block}
+			\end{figure}
+			\blfootnote{Figure from \cite{Clerckx2019}}
+		\end{frame}
+
+		\begin{frame}{Harvester model}
+			RF-to-DC conversion requires \textbf{rectenna} (receive antenna + rectifier), whose behavior is dominated by diode I-V characteristics.
+			\begin{figure}
+				\centering
+				\includegraphics[width=0.8\textwidth]{assets/rectenna_circuit.eps}
+				\caption{Rectenna equivalent circuit and a single diode rectifier \cite{Clerckx2018a}}
+			\end{figure}
+			Consider small-signal model and truncate its Taylor expansion to the $n_0$-th order:
+			\begin{itemize}
+				\item diode linear model (${n_o} = 2$): output power is proportional to input power
+				\item \alert{diode nonlinear model} (${n_o} > 2$): significant contribution from high-order terms
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}{Waveform design}
+			A superposed signal containing \alert{modulated information waveform} and \alert{multisine power waveform} is demonstrated to bring a two-fold benefit:
+			\begin{itemize}
+				\item \textbf{rate}: multisine is deterministic with no interference on information waveform (by waveform cancellation or translated codebook)
+				\item \textbf{energy}: multisine brings high PAPR and triggers the diode nonlinear model more often (reduce threshold from -20 \si{\dBm} to -30 \si{\dBm})
+			\end{itemize}
+			\begin{figure}
+				\centering
+				\begin{subfigure}{.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/multisine_frequency_domain.eps}
+					\caption{Frequency domain}
+				\end{subfigure}
+				\begin{subfigure}{.48\textwidth}
+					\centering
+					\includegraphics[width=0.8\linewidth]{assets/multisine_time_domain.eps}
+					\caption{Time domain}
+				\end{subfigure}
+				\caption{Multisine waveform}
+			\end{figure}
+			\blfootnote{Figure from \cite{Trotter2009}}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{IRS}
+		\begin{frame}{What is IRS?}
+			\textbf{Intelligent Reflecting Surface} (IRS) consists of multiple individual passive reflecting elements that adjust the amplitude and phase of the incident signal.
+			\begin{figure}
+				\centering
+				\begin{subfigure}{.48\textwidth}
+					\centering
+					\includegraphics[width=0.9\linewidth]{assets/irs_architecture.eps}
+					\caption{IRS architecture}
+				\end{subfigure}
+				\begin{subfigure}{.48\textwidth}
+					\centering
+					\includegraphics[width=0.9\linewidth]{assets/irs_system.eps}
+					\caption{Application scenario}
+				\end{subfigure}
+			\end{figure}
+			\begin{columns}
+				\begin{column}{0.5\textwidth}
+					\begin{itemize}
+						\item outer layer: redistribute incident signals
+						\item middle layer: avoid signal energy leakage
+						\item inner layer: adjust reflection amplitude and phase shift
+					\end{itemize}
+				\end{column}
+				\begin{column}{0.5\textwidth}
+					\begin{itemize}
+						\item enhance primary transmission by constructive reflection
+						\item null interference by destructive reflection
+					\end{itemize}
+				\end{column}
+			\end{columns}
+			\blfootnote{Figure from \cite{Wu2019,Wu2020}}
+		\end{frame}
+
+		\begin{frame}{Why IRS?}
+			\textbf{Characteristics}:
+			\begin{itemize}
+				\item passive (different from AF relay)
+				\begin{itemize}
+					\item no RF chains
+					\item low power consumption
+					\item no additional thermal noise
+					\item \alert{squared gain}: received power scales quadratically with the number of reflectors (boost receive power and array gain in equal gain transmission)
+				\end{itemize}
+				\item full-duplex
+				\item assistant (different from backscatter node)
+				\item adjustable in real-time
+			\end{itemize}
+			\vspace{1em}
+			\textbf{Challenges}:
+			\begin{itemize}
+				\item channel estimation
+				\begin{itemize}
+					\item cannot separate incident and reflective channels
+					\item large number of extra channels
+				\end{itemize}
+				\item practical restriction
+				\begin{itemize}
+					\item discrete phase shifts
+					\item phase shift are coupled with reflection amplitude (by impedance equation)
+				\end{itemize}
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}{Why IRS-aided SWIPT?}
+			\begin{itemize}
+				\item both aim at improving spectral/energy efficiency
+				\item enhanced channel boosts received power to benefit from harvester nonlinearity
+				\item extra links increase system diversity and stability, which is essential for SWIPT
+				\item SWIPT can potentially support low-power IRS
+			\end{itemize}
 		\end{frame}
@@
 \end{section}
+
+\bibliographystyle{IEEEtran}
+\bibliography{library.bib}
 \end{document}

### 2020-07-03 main.tex
:pencil: System model and problem formulation

@@
 		The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
-Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
+Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
 On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup.
@@
 		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraing}
+		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
 		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
@@
 	\end{maxi!}
-	Problem \ref{op:su} is intricate due to the non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraing} with coupled variables.
+	Problem \ref{op:su} is intricate due to the non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint} with coupled variables.
 To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.
@@
 On top of this, we formulate the FF-IRS phase shift optimization subproblem as follows.
-With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables
+With given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$, introduce auxiliary variables
 			\begin{equation}\label{eq:t}
@@
 In this case, the output DC current is also expressed in \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
-Since $z(\rho)$ is a monotonically increasing function over $\rho \in [0, 1]$, we replace the convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
+Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
 				\begin{maxi!}
@@
 
-			\begin{paragraph}{Alternating Optimization: Inner Loop}
+			\begin{paragraph}{Inner Loop}
 				As summarized in Algorithm \ref{al:inner_loop}, the inner loop updates the waveform and splitting ratio iteratively until convergence.

### 2020-07-03 slides.tex
:pencil: System model and problem formulation

@@
 
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{amsfonts}
@@
 \usepackage{hyperref}
+\usepackage{lmodern}
 \usepackage{mathtools}
@@
 \usepackage{subcaption}
+\usepackage[short]{optidef}
 
@@
 		\begin{frame}{WPT by RF waves}
-			\textbf{Energy flow}: DC $\to$ RF $\to$ RF $\to$ DC
+			\textbf{Energy flow}: DC $\to$ \alert{RF $\to$ RF $\to$ DC}
 			\begin{figure}
@@
 				\item diode linear model (${n_o} = 2$): output power is proportional to input power
-				\item \alert{diode nonlinear model} (${n_o} > 2$): significant contribution from high-order terms
+				\item \alert{diode nonlinear model} (${n_o} > 2$): contribution from high-order terms
 			\end{itemize}
+			\blfootnote{Figure from \cite{Clerckx2019}}
 		\end{frame}
@@
 	\end{subsection}
+
+	\begin{subsection}{Previous research}
+		\begin{frame}{Existing works}
+			Separated information decoder and energy harvester:
+			\begin{itemize}
+				\item \cite{Wu2019b} investigated a MISO system with energy interference and proved at most one energy beam is required to maximize the WSP subject to SINR constraints.
+				\item \cite{Tang2019} considered fairness issue for a MISO system and maximized the minimum output power based on perfect energy interference cancellation.
+				\item \cite{Pan2019a} transformed WSR maximization of MIMO SWIPT to WMMSE problem then solved by BCD with low-complexity iterative algorithms.
+				\item \cite{Wu2019c} proposed a penalty-based algorithm to minimize transmit power of MISO system subject to SINR constraints, whose inner layer updates precoders, phase shifts and auxiliary variables by BCD while the outer layer updates the penalty coefficients.
+			\end{itemize}
+		\end{frame}
+
+		\begin{frame}{Outcomes and opportunities}
+			\textbf{Outcomes}:
+			\begin{itemize}
+				\item IRS brings a significant gain to SWIPT
+				\item performance vary significantly under different configuration (distances, number of reflectors, transmit power, SNR, etc.)
+				\item dedicated energy beam is necessary to boost the harvested power
+				\item LoS links can further increase the harvested power, since rank-deficient channels are highly correlated and a single energy stream can provide large output power for multiple harvesters
+			\end{itemize}
+			\vspace{1em}
+			\textbf{Opportunities}:
+			\begin{itemize}
+				\item no works on co-located information decoder and energy harvester
+				\item no works on IRS-aided OFDM SWIPT
+				\item no works consider harvester nonlinearity
+				\item no works investigate Rate-Energy (R-E) tradeoff
+			\end{itemize}
+		\end{frame}
+	\end{subsection}
+\end{section}
+
+\begin{section}{System model}
+	\begin{subsection}{Signal and channel}
+		\begin{frame}{Signal and channel}
+			SISO, $L$-reflector IRS, $K$-user, $N$-subband
+			\begin{itemize}
+				\item transmit signal at the AP:
+				\begin{equation}
+					x(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+				\end{equation}
+				\begin{itemize}
+					\item $w_{I/P,n}$ collects magnitude and phase of the information and power signal
+					\item $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$ is the information symbol
+				\end{itemize}
+				\item composite channel for user $k$:
+				\begin{itemize}
+					\item direct: AP-user ($h_{D,k,n}$)
+					\item extra: AP-IRS ($\boldsymbol{h}_{I,n}$), \alert{IRS reflection ($\boldsymbol{\Theta}$)}, IRS-user ($\boldsymbol{h}_{R,k,n}^H$)
+					\begin{equation}
+						h_{E,k,n} = \boldsymbol{h}_{R,k,n}^H \alert{\boldsymbol{\Theta}} \boldsymbol{h}_{I,n} = \boldsymbol{v}_{k,n}^H \alert{\boldsymbol{\phi}}
+					\end{equation}
+					\item sum up and stack over all subbands:
+					\begin{equation}
+						\boldsymbol{h}_k = \boldsymbol{h}_{D,k} + \boldsymbol{V}_k^H \alert{\boldsymbol{\phi}}
+					\end{equation}
+				\end{itemize}
+				\item received signal by user $k$
+				\begin{equation}
+					y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+				\end{equation}
+			\end{itemize}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{Information decoder}
+		\begin{frame}{Information decoder}
+			The power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
+			\begin{equation}\label{eq:R_k}
+				R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,n} \rvert^2}{\sigma_n^2}\right)}
+			\end{equation}
+			\begin{itemize}
+				\item $\rho$ is the splitting ratio for energy harvesting
+				\item $\alpha_{k,n}$ is the allocation indicator:
+				\begin{equation}
+					\alpha_{k,n} =
+					\begin{cases}
+						1, & \text{if subband } n \text{ is given to user } k \\
+						0, & \text{otherwise}
+					\end{cases}
+				\end{equation}
+				\item $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion
+			\end{itemize}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{Energy harvester}
+		\begin{frame}{Energy harvester}
+			A truncated Taylor expansion of small signal model highlights the dependency of harvester output DC current on the received waveform:
+			\begin{equation}
+				z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
+			\end{equation}
+			Pick $n_0=4$ and we have:
+			\begin{figure}
+				\centering
+				\includegraphics[width=\linewidth]{assets/z.eps}
+			\end{figure}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{Rate-energy region}
+		\begin{frame}{Rate-energy region}
+			Define the achievable weighted sum \textbf{R-E region} as
+			\begin{equation}
+				\begin{split}
+					C_{R-I}(P)
+					&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
+					&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
+				\end{split}
+			\end{equation}
+			\begin{itemize}
+				\item $P$ is the transmit power budget
+				\item $u_{I/P,k}$ are the information and power weight of user $k$
+			\end{itemize}
+		\end{frame}
+	\end{subsection}
+\end{section}
+
+\begin{section}{Single-user optimization}
+	\begin{subsection}{Problem formulation}
+		\begin{frame}{Problem formulation}
+			We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
+			\begin{maxi!}
+				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
+				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
+				\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
+				\addConstraint{0 \le \rho \le 1}
+			\end{maxi!}
+			\vspace{1em}
+			$\boldsymbol{w}_{I/P},\boldsymbol{\phi},\rho$ are coupled in \ref{eq:su_target}, \ref{eq:su_rate_constraint}, consider \textbf{alternating optimization} (AO).
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{IRS phase shift}
+		\begin{frame}{Frequency-selective IRS}
+			The ideal \textbf{Frequency-Selective} (FS) IRS provides:
+			\begin{itemize}
+				\item subband-dependent reflection coefficients ($\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$)
+				\item total DoF $NL$
+			\end{itemize}
+			\vspace{1em}
+			Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ and the equality holds when the direct and IRS-aided links are aligned.
+Therefore, we simply select the phase shift of element $l$ at subband $n$ as
+			\begin{equation}
+				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
+			\end{equation}
+			That is to say, the optimal phase shift for FS-IRS is obtained in closed form in the single-user scenario, which ensures the direct, extra and composite channels have the same phase.
+		\end{frame}
+
+		\begin{frame}{Frequency-flat IRS (1)}
+			\textbf{Frequency-Flat} (FF) IRS reflects all subbands equally with a DoF of $L$.
+			\begin{block}{Semi-Definite Relaxation (SDR): rate constraint}
+				To simplify rate constraint \ref{eq:su_rate_constraint}, we observe that
+				\begin{equation}
+					\begin{split}
+						\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
+						&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
+						&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
+					\end{split}
+				\end{equation}
+				where $t$ is an auxiliary variable with unit modulus and
+				\begin{equation}\label{eq:R_n,phi}
+					\boldsymbol{R}_n=
+					\begin{bmatrix}
+						\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
+						h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
+					\end{bmatrix},
+					\quad \bar{\boldsymbol{\phi}}=\
+					\begin{bmatrix}
+						\boldsymbol{\phi} \\
+						t
+					\end{bmatrix},
+					\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
+				\end{equation}
+			\end{block}
+		\end{frame}
+
+		\begin{frame}{Frequency-flat IRS (2)}
+			We optimize $\boldsymbol{\Phi}$ with given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$.
+			\begin{block}{SDR: current expression}
+				Define $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H$ such that $\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}$. Introduce auxiliary variables
+				\begin{equation}\label{eq:t}
+					\begin{split}
+						t_{I/P,n}
+						&=\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*\boldsymbol{h}=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)=\mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*)\\
+						&=\mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H\boldsymbol{\Phi})=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
+					\end{split}
+				\end{equation}
+				Therefore, the current expression rewrites as
+				\begin{equation}\label{eq:z_irs}
+					z(\boldsymbol{\Phi})=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
+				\end{equation}
+			\end{block}
+		\end{frame}
+
+		\begin{frame}{Frequency-flat IRS (3)}
+			We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_irs}. Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ gives
+			\begin{align}
+				(t_{I,0}^{(i)})^2
+				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\
+				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
+				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
+				t_{I,0}^{(i)} t_{P,0}^{(i)}
+				& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
+				& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}
+			\end{align}
+		\end{frame}
+
+		\begin{frame}{Frequency-flat IRS (4)}
+			Hence, problem \ref{op:su} is transformed to
+			\begin{maxi!}
+				{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
+				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
+			\end{maxi!}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{Waveform}
+		\begin{frame}{Waveform (1)}
+			We optimize $\boldsymbol{w}_{I/P}$ with given IRS $\boldsymbol{\phi}$ and splitting ratio $\rho$.
+			\begin{block}{SDR: current expression}
+				Introduce auxiliary variables
+				\begin{equation}\label{eq:t'}
+					t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
+				\end{equation}
+				Therefore, the current expression rewrites as
+				\begin{equation}\label{eq:z_waveform}
+					z(\boldsymbol{W}_{I/P})=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
+				\end{equation}
+				Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we use same Taylor approximation.
+			\end{block}
+		\end{frame}
+
+		\begin{frame}{Waveform (2)}
+			Hence, problem \ref{op:su} is transformed to
+			\begin{maxi!}
+				{\boldsymbol{W}_{I/P}}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
+				\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
+				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
+				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
+			\end{maxi!}
+		\end{frame}
+	\end{subsection}
+
+	\begin{subsection}{Splitting ratio}
+		\begin{frame}{Splitting ratio}
+			We optimize $\rho$ with given IRS $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
+			\begin{maxi!}
+				{\rho}{z(\rho)}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
+				\addConstraint{0 \le \rho \le 1}
+			\end{maxi!}
+			Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace $z(\rho)$ with affine $\rho$ and solve problem \ref{op:su_ratio}.
+		\end{frame}
+	\end{subsection}
 \end{section}

### 2020-07-08 main.tex
:construction: Rebuild system model

@@
 \begin{section}{System Model}
-	Consider an IRS-aided multiuser SISO OFDM SWIPT system where the transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
+	Consider an IRS-aided multiuser MISO OFDM SWIPT system where the $M$-antenna transmitter delivers information and power simultaneously, through a single $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
 We assume a total bandwidth $B$ with evenly-spaced carriers around center frequency $f_c$.
@@
 Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$.
-The superposed transmit signal at time $t$ is
-		\begin{equation}\label{eq:x}
-			x(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+The superposed transmit signal at time $t$ on antenna $m$ ($m=1,\dots,M$) is
+		\begin{equation}\label{eq:x_m}
+			x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{equation}
-		where $w_{I/P,n}=s_{I/P,n}e^{j\psi_{I/P,n}}$ collects the magnitude and phase of the information and power signal at subband $n$.
-We further define the waveform vectors $\boldsymbol{w}_{I/P}=[w_{I/P,1},\dots,w_{I/P,N}]^T \in \mathbb{C}^{N{\times}1}$.
+		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
+We further define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ such that the transmit information and power signals write as
+		\begin{align}
+			\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_I}\\
+			\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
+		\end{align}
 	\end{subsection}
 
-	\begin{subsection}{Composite Channel Model}
-		Denote the frequency response of the AP-user $k$ direct link as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}]^T \in \mathbb{C}^{N \times 1}$.
-Let $[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}] \in \mathbb{C}^{L \times N}$ be the frequency response of AP-IRS incident channel, where $\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$ corresponds to the $n$-th incident channel.
-Similarly, let $[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}]^H \in \mathbb{C}^{N \times L}$ be the frequency response of IRS-user $k$ reflective channel, where $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$ corresponds to the $n$-th reflective channel.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the received signal by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\beta_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
-On top of this, the IRS matrix is constructed by collecting the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$.
-The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel, which for user $k$ over subband $n$ is
-		\begin{equation}\label{eq:h_{E,k,n}}
-			h_{E,k,n} = \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{h}_{I,n} = \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
+	\begin{subsection}{Composite Channel}
+		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and the IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
+The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel.
+Hence, the composite channel for user $k$ over subband $n$ is
+		\begin{equation}\label{eq:h_{k,n}}
+			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
 		\end{equation}
-		where $\boldsymbol{v}_{k,n}^H=\boldsymbol{h}_{R,k,n}^H \mathrm{diag}(\boldsymbol{h}_{I,n}) \in \mathbb{C}^{1 \times L}$ and $\boldsymbol{\phi}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}] \in \mathbb{C}^{L \times 1}$.
-Both direct and extra link contributes to the corresponding composite channel as
-		\begin{equation}\label{eq:h_{k,n}}
-			h_{k,n} = A_{k,n} e^{j\bar{\psi}_{k,n}}= h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
-		\end{equation}
-		where $A_{k,n}$ and $\bar{\psi}_{k,n}$ are the amplitude and phase of the composite channel of user $k$ at subband $n$.
-Let $\boldsymbol{V}_k^H=[\boldsymbol{v}_{k,1},\dots,\boldsymbol{v}_{k,N}]^H \in \mathbb{C}^{N \times L}$, the extra link for user $k$ is $\boldsymbol{h}_{E,k}=[h_{E,k,1},\dots,h_{E,k,N}]^T=\boldsymbol{V}_k^H \boldsymbol{\phi} \in \mathbb{C}^{N \times 1}$.
-Therefore, the composite channel of user $k$ is
-		\begin{equation}\label{eq:h_k}
-			\boldsymbol{h}_k = \boldsymbol{h}_{D,k} + \boldsymbol{V}_k^H \boldsymbol{\phi}
-		\end{equation}
+		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
+Let $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$.
+Also, define $\boldsymbol{A}_{k,n}=\lvert \boldsymbol{h}_{k,n} \rvert$ and $\boldsymbol{\varsigma}_{k,n}=\angle{\boldsymbol{h}_{k,n}}$ as the magnitude and phase of the composite channel for user $k$ over subband $n$.
 	\end{subsection}
@@
 	\begin{subsection}{Receive Signal}
-		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and IRS-aided links as
-		\begin{equation}\label{eq:y_k}
-			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left({w_{I,n}\tilde{x}_{I,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
-		\end{equation}
-		which can be divided into
+		The information and power signals received by user $k$ through both direct and IRS-aided links write as
 		\begin{align}\label{eq:y_{I/P,k}}
-			y_{I,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}{w_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
-			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}w_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
+			y_{I,k}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
+			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{align}
@@
 		\begin{equation}\label{eq:R_k}
-			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,n} \rvert^2}{\sigma_n^2}\right)}
+			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
 		\end{equation}
@@
 
-		With the assumption of evenly spaced frequencies, we have $\mathcal{E}\left\{y_k(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components.
+		With the assumption of evenly spaced frequencies, it holds that $\mathcal{E}\left\{y_k(t)^i\right\}=0$ for odd $i$ and the related terms has no contribution to DC components.
 For simplicity, we truncate the infinite series to the $n_0$-th order.
-As proved in \cite{Clerckx2016a}, maximizing a truncated \ref{eq:i_k} is equivalent to maximizing a monotonic function
+As proved in \cite{Clerckx2016a}, maximizing a truncated $i_k$ is equivalent to maximizing a monotonic function
 		\begin{equation}\label{eq:z_k}
@@
 		where $k_i=i_s/i!(nv_t)^i$.
-We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on waveform design.
+We choose $n_0=4$ to investigate fundamental nonlinearity and let $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.
 Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
 
-		For simplicity, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ as waveform matrices and channel matrix of user $k$.
-Let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{W}_{I/P}$, $\boldsymbol{H}_k$ and null the remaining entries, respectively.
+		Similar to \cite{Huang2017}, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$, $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ and let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep their $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries, respectively.
 Due to the positive definiteness of $\boldsymbol{W}_{I/P}$ and $\boldsymbol{H}_k$, we have $\boldsymbol{W}_{I/P,-n}=\boldsymbol{W}_{I/P,n}^H$ and $\boldsymbol{H}_{k,-n}=\boldsymbol{H}_{k,n}^H$.
-Let $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.
-On top of this, nonzero terms in \ref{eq:z_k} are detailed in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} such that the current expression reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
+On top of this, the nonzero terms in \ref{eq:z_k} are expressed by \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} and $z_k$ reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
 		\begin{figure*}[b]
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\label{eq:z_k_terms_begin}\\
+				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\label{eq:z_k_terms_begin}\\
 				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				& = \frac{3}{4}\left(\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\right)^2\\
+				& = \frac{3}{4}\left(\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\right)^2\\
 				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2\\
 				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				& = \frac{1}{2}\sum_n{(h_{k,n}w_{P,n})(h_{k,n}w_{P,n})^*}\\
+				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{P,n})^H}\\
 				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\
 				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{n_1}})(h_{k,{n_2}}w_{P,{n_2}})(h_{k,{n_3}}w_{P,{n_3}})^*(h_{k,{n_4}}w_{P,{n_4}})^*}\\
-				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^*\label{eq:z_k_terms_end}
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{k,{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{k,{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{k,{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{k,{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}\\
+				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H\label{eq:z_k_terms_end}
 			\end{align}
@@
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^*\right)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H\right)\nonumber\\
 				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_k_channel}\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H \right)\nonumber\\
 				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_k_waveform}
@@
 		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi})w_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
+		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
 		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
@@
 			In contrast, FF-IRS reflects all subbands equally with a DoF of $L$. We observe that
-			\begin{equation}
+			\begin{equation}\label{eq:h_n_outer_product}
 				\begin{split}
-					\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
-					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
-					&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
+					\boldsymbol{h}_n\boldsymbol{h}_n^H
+					&=(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\\
+					&=\boldsymbol{h}_{D,n}\boldsymbol{h}_{D,n}^H+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{h}_{D,n}^H+\boldsymbol{h}_{D,n}\boldsymbol{\phi}^H\boldsymbol{V}_n+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{\phi}^H\boldsymbol{V}_n\\
+					&=\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n
 				\end{split}
@@
 			where $t$ is an auxiliary variable with unit modulus and
-			\begin{equation}\label{eq:R_n,phi}
-				\boldsymbol{R}_n=
+			\begin{equation}\label{eq:M_n,phi}
+				\boldsymbol{M}_n=
 				\begin{bmatrix}
-					\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
-					h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
-				\end{bmatrix},
+					\boldsymbol{V}_n \\
+					\boldsymbol{h}_{D,n}^H
+				\end{bmatrix} \in \mathbb{C}^{(L+1) \times M},
 				\quad \bar{\boldsymbol{\phi}}=\
@@
 			\end{equation}
-			with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$.
-Therefore, the outer product of composite channel rewrites as
-			\begin{equation}\label{eq:M}
+			Therefore, it holds that
+			\begin{equation}
+				\begin{split}
+					\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2
+					&=\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
+					&=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
+					&=\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
+				\end{split}
+			\end{equation}
+			with $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Similarly, we have
+			\begin{equation}
 				\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
 			\end{equation}
-			where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$.
-On top of this, we formulate the FF-IRS phase shift optimization subproblem as follows.
-With given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$, introduce auxiliary variables
+			where
+			\begin{equation}\label{eq:M}
+				\boldsymbol{M}=
+				\begin{bmatrix}
+					\boldsymbol{V} \\
+					\boldsymbol{h}_D^H
+				\end{bmatrix} \in \mathbb{C}^{(L+1) \times MN}
+			\end{equation}
+			We then introduce auxiliary variables
 			\begin{equation}\label{eq:t}
@@
 			\end{equation}
-			where we define
-			\begin{equation}\label{eq:C_{I/P,n}}
-				\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H
-			\end{equation}
-			and $\boldsymbol{C}_{I/P,n} \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
+			with $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
 			\begin{equation}\label{eq:z_irs}

### 2020-07-10 main.tex
:pencil: Outer loop algorithm

@@
 	\begin{subsection}{Objective and Methodology}
-		In this paper, we study an IRS-aided multiuser Single-Input Single-Output (SISO) system where the IRS assists the information and energy transmission of all users.
+		In this paper, we study an IRS-aided multiuser MISO SWIPT system where the IRS assists the information and energy transmission of all users.
 A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g.
-OFDM) to boost the energy transfer efficiency with no interference.
+OFDM) to boost the energy transfer efficiency without introducing additional interference.
 The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
@@
 To reduce the design complexity, we	propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) technique.
-It was observed that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively.
-Also, FF-IRS produces a significant channel amplification and R-E enhancement especially when developed near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
+It was demonstrated that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively.
+Also, IRS brings a significant channel amplification and R-E enhancement especially when located near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
 	\end{subsection}
@@
 	Consider an IRS-aided multiuser MISO OFDM SWIPT system where the $M$-antenna transmitter delivers information and power simultaneously, through a single $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
-We assume a total bandwidth $B$ with evenly-spaced carriers around center frequency $f_c$.
-Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
-Each subband is allocated to one user per time slot.
-Perfect Channel State Information (CSI) with negligible training overhead is considered to explore the analytical upper-bound of the proposed design.
+We assume a total bandwidth $B$ with evenly-spaced subbands around center frequency $f_c$.
+Each subband is allocated to one user per time slot, and denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
+Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design.
 A quasi-static block fading channel model is considered for all links and we focus on one particular block where the channels are approximately unchanged.
@@
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into data and energy streams for ID and EH purposes, and the splitting ratio $\rho$ is coupled with waveform and IRS design.
+In comparison, PS splits the received signal into data and energy streams for ID and EH, and the splitting ratio $\rho$ is coupled with waveform and IRS design.
 Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
@@
 Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
-Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0 \ \forall k' \ne k$.
+Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0$ for $k' \ne k$.
 Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$.
@@
 		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
-We further define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ such that the transmit information and power signals write as
+Let $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ such that the transmit information and power signals write as
 		\begin{align}
@@
 		\end{align}
+		We also define $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and let $\boldsymbol{s}_{I/P}=\lvert{\boldsymbol{w}_{I/P}}\rvert$, $\boldsymbol{\psi}_{I/P}=\angle{\boldsymbol{w}_{I/P}}$ be the magnitude and phase of the waveforms.
 	\end{subsection}
@@
 	\begin{subsection}{Composite Channel}
-		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and the IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$.
+		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$.
 At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
@@
 		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Let $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$.
-Also, define $\boldsymbol{A}_{k,n}=\lvert \boldsymbol{h}_{k,n} \rvert$ and $\boldsymbol{\varsigma}_{k,n}=\angle{\boldsymbol{h}_{k,n}}$ as the magnitude and phase of the composite channel for user $k$ over subband $n$.
+Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
 	\end{subsection}
@@
 		\begin{equation}\label{eq:R_k}
-			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
+			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
 		\end{equation}
@@
 	\begin{subsection}{Energy Harvester}
-		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights the dependency of harvester output DC current on the received waveform of user $k$ as
+		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights for user $k$ the dependency of harvester output DC current on the received waveform as
 		\begin{equation}\label{eq:i_k}
@@
 			\begin{split}
-				C_{R-I}(P)
+				C_{R-Z}(P)
 				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
@@
 		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
-		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
+		\addConstraint{\lvert{\phi}\rvert=1, \quad l=1,\dots,L}
 		\addConstraint{0 \le \rho \le 1}
 	\end{maxi!}
-	Problem \ref{op:su} is intricate due to the non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint} with coupled variables.
+	Problem \ref{op:su} is intricate due to coupled variables and non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint}.
 To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.
@@
 	\begin{subsection}{IRS Phase Shift}
-		\begin{subsubsection}{Frequency-Selective IRS}\label{se:fs_irs}
-			In the ideal case, each element in FS-IRS is expected to provide subband-dependent reflection coefficients.
-Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total Degree of Freedom (DoF) of $NL$.
-Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned.
-Therefore, we simply select the phase shift of element $l$ at subband $n$ as
-			\begin{equation}\label{eq:theta}
-				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
-			\end{equation}
-			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, which ensures the direct, extra and composite channels have the same phase.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Frequency-Flat IRS}
-			In contrast, FF-IRS reflects all subbands equally with a DoF of $L$. We observe that
+		We optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{I/P,n}$ and splitting ratio $\rho$. Since
 		\begin{equation}\label{eq:h_n_outer_product}
@@
 		\end{equation}
-			with $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Similarly, we have
+		with
+		\begin{equation}\label{eq:C_n}
+			\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}
+		\end{equation}
+		Similarly, we have
 		\begin{equation}
@@
 		\end{equation}
-			We then introduce auxiliary variables
+		Next, introduce auxiliary variables
 		\begin{equation}\label{eq:t}
@@
 		\end{equation}
-			with $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as
+		with
+		\begin{equation}\label{eq:C_{I/P,n}}
+			\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
+		\end{equation}
+		Therefore, \ref{eq:z_k_channel} rewrites as
 		\begin{equation}\label{eq:z_irs}
@@
 				{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
-				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
 				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
@@
 If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD).
-Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}.
+Otherwise, a solution can be extracted through Gaussian randomization method \cite{Huang2010}.
 We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
-Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$.
-Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one maximizes the objective function \ref{eq:su_irs_target}.
+Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates by
+		\begin{equation}
+			\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}
+		\end{equation}
+		The candidate maximizing the objective function \ref{eq:su_irs_target} is chosen as the optimal solution $\bar{\boldsymbol{\phi}}^\star$.
 Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for the phase shift optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.
+The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:ff_irs}.
 		\begin{algorithm}
-				\caption{FF-IRS: Phase Shift}
+			\caption{IRS Phase Shift}
 			\label{al:ff_irs}
@@
 				\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
-					\State Construct $\boldsymbol{M},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}
-					\Repeat
+				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:M_n,phi}, \ref{eq:C_n}, \ref{eq:C_{I/P,n}}
+				\Repeat;
 				\State $i \gets i + 1$
@@
 				\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-					\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}
+				\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\bar{\boldsymbol{\phi}}^\star$ for problem \ref{op:su_irs}
 				\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
@@
 		\end{algorithm}
-		\end{subsubsection}
 	\end{subsection}
@@
 			\begin{equation}\label{eq:psi}
-				\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}
+				\boldsymbol{\psi}_{I}^{\star}=\boldsymbol{\psi}_{P}^{\star}=-\boldsymbol{\varsigma}
 			\end{equation}
@@
 			\begin{equation}
-				\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert = \lvert h_{D,n} \rvert \lvert w_{I,n} \rvert + \vert \boldsymbol{v}_n^H\boldsymbol{\phi}_n \rvert \lvert w_{I,n} \rvert
+				\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert^2=(\boldsymbol{a}_n^H\boldsymbol{s}_{I,n})^2=\sum_{m_1,m_2}\prod_{j=1}^2{a_{n,m}s_{I,n,m}} \triangleq E_n
 			\end{equation}
-			Also, denote the waveform amplitude at subband $n$ as
-			\begin{equation}\label{eq:s}
-				s_{I/P,n} = \lvert w_{I/P,n} \rvert
-			\end{equation}
-			which is further collected into $\boldsymbol{s}_{I/P} \in \mathbb{C}^{N \times 1}$. Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem
+			Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem
 			\begin{maxi!}
@@
 					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \ge \bar{R}}
+					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)E_n}{\sigma_n^2}\right)} \ge \bar{R}}
 				\end{maxi!}
@@
 						z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
-						&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
-						&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})^2\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
-						&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
+						& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \sum_{m_1,m_2} \left( \prod_{j=1}^2 {a_{n,m_j}s_{I,n,m_j}} + \prod_{j=1}^2 {a_{n,m_j}s_{P,n,m_j}} \right)\\
+						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{I,n_2,m_j} + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1}^4 a_{n_j,m_j}s_{P,n_j,m_j} \right)\\
+						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n,m_j}s_{I,n,m_j} \prod_{j=2,4} a_{n,m_j}s_{P,n,m_j} \right)
 					\end{split}
@@
 			\end{figure*}
-			with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into
+			with $z$ expressed in \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and rewrite problem \ref{op:su_gp} as
 			\begin{mini!}
-					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
+					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
 					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
 					\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
-					\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \le 1}
+					\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+{\bar{\rho}E_n}/{\sigma_n^2}\right)} \le 1}
+					\addConstraint{\rho + \bar{\rho} \le 1}
 				\end{mini!}
-			Problem \ref{op:su_gp_1} can be transformed to standard GP by first decomposing the information and power posynomials as sum of monomials, then deriving their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
-Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{m=1}^{M}{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:su_gp_1} is equivalent to
+			Problem \ref{op:su_gp_1} can be transformed into standard GP by first decomposing the information and power posynomials as sum of monomials, then deriving their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
+Specifically, define
+			\begin{align}
+				z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\\
+				1+\frac{\bar{\rho}E_n}{\sigma_n^2}&=\sum_{m_{I,n}}g_{m_{I,n}}(\boldsymbol{s}_{I,n},\bar{\rho})
+			\end{align}
+			On top of this, problem \ref{op:su_gp_1} is equivalent to
 			\begin{mini}
@@
 				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{{t''}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
+				\addConstraint{{t''}\prod_{m_P}{\left(\frac{g_{{m_P}}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{{m_P}}}\right)^{-\gamma_{{m_P}}}}\le{1}}
+				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{I,n}}\left(\frac{g_{m_{I,n}}(\boldsymbol{s}_{I,n},\bar{\rho})}{\gamma_{m_{I,n}}}\right)^{-\gamma_{m_{I,n}}}\le{1}}
 				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{mini}
-			where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m} \ge 0 \ \forall m$, and $\sum_{m=1}^{M}{\gamma_m}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require successive update.
-At iteration $i$, we choose \cite{Clerckx2018b}
+			where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$ and $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update \cite{Clerckx2018b}.
+At iteration $i$, we choose
 			\begin{align}
-				\gamma_{I,n,1}^{(i)} & = \left. 1 \middle/ \left(1+\frac{\bar{\rho}^{(i-1)}{A_n^2}(s_{I,n}^{(i-1)})^2}{\sigma_n^2}\right) \right.\label{eq:gamma_I_1}\\
-				\gamma_{I,n,2}^{(i)} & = 1 - \gamma_{I,n,1}^{(i)}\label{eq:gamma_I_2}\\
-				\gamma_{P,m}^{(i)} & =\frac{g_{P,m}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
+				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(\boldsymbol{s}_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}E_n^{(i-1)}}/{\sigma_n^2}}\label{eq:gamma_I}\\
+				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
 			\end{align}
-			and then solve problem \ref{op:su_gp_2}. The GP algorithm is summarized in Algorithm \ref{al:waveform_split_ratio_gp}.
+			then solve problem \ref{op:su_gp_2}. The GP algorithm is summarized in Algorithm \ref{al:waveform_split_ratio_gp}.
 			\begin{algorithm}
@@
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
-					\State Retrieve channel amplitude response $A_n \ \forall n$ by \ref{eq:h_{k,n}}
+					\State Retrieve channel magnitude and phase $\boldsymbol{a}, \varsigma$
 					\Repeat
 					\State $i \gets i + 1$
-					\State Update GM exponents $\{\gamma_{I,n}^{(i)},\gamma_{P}^{(i)}\}$ by \ref{eq:gamma_I_1} -- \ref{eq:gamma_P}
+					\State Update GM exponents $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ by \ref{eq:gamma_I}, \ref{eq:gamma_P}
 					\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_gp_2}
@@
 					\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-					\State Recover waveform $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:psi} and \ref{eq:s}
+					\State Recover waveform $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:psi}
 					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
@@
 				\end{equation}
-				Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound \ref{eq:z_waveform} by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.
+				Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound $z(\boldsymbol{W}_I,\boldsymbol{W}_P)$ by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.
+Also, denote $\boldsymbol{W}_{I,n}'$ as the $n$-th block in the main diagonal of $\boldsymbol{W}_{I}$ such that
+				\begin{equation}
+					\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert^2=\boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\mathrm{Tr}(\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{W}_{I,n}')
+				\end{equation}
 				Hence, problem \ref{op:su} is transformed to
@@
 					{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)W_{I,n,n}\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
+					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{W}_{I,n}')}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
 					\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
@@
 				We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
-$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can also be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{(L+1) \times 1}$, whose entries are uniformly distributed on the unit circle $r_{q,n}=e^{j\xi_{q,n}}, \ \xi_{q,n} \sim \mathcal{U}[0,2\pi) \ \forall q, n$.
+$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{MN \times 1}$ whose entries are uniformly distributed on the unit circle.
 The algorithm is summarized in Algorithm \ref{al:waveform_sdr}.
@@
 						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$ by \ref{eq:t'}
-						\State Construct $\boldsymbol{H}_n,\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
+						\State Construct $\boldsymbol{H}_n \ \forall n$
 						\Repeat
@@
 				We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
-In this case, the output DC current is also expressed in \ref{eq:z_waveform} but as a function of $\rho$ with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
-Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function $z(\rho)$ with affine $\rho$ and transform problem \ref{op:su} to
+In this case, $z(\rho)$ is also expressed in \ref{eq:z_waveform} with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
+Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function with affine $\rho$ and transform problem \ref{op:su} to
 				\begin{maxi!}
 					{\rho}{\rho}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert h_n w_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
+					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_n^H \boldsymbol{w}_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
 					\addConstraint{0 \le \rho \le 1}
@@
 	\begin{subsection}{R-E Region Characterization}
-		\begin{subsubsection}{WIT Initialization}
-			To characterize the R-E region, we initialize the algorithm to WIT mode ($\rho = 0$) and reduce the rate constraint gradually to obtain the boundary points.
-			\begin{paragraph}{FS-IRS}
-				As discussed in Section \ref{se:fs_irs}, the optimal FS-IRS and composite channel are obtained in closed form.
-We use water-filling algorithm to obtain the best power allocation $p_n^\star=\lvert w_{I,n} \rvert^2$ and combine with the waveform phase selection in \ref{eq:psi}.
-Hence, the optimal information waveform at subband $n$ is
-				\begin{equation}\label{eq:w_{I,n}}
-					w_{I,n}^\star=\sqrt{p_n^\star}e^{j \psi_{I,n}^\star}
-				\end{equation}
-			\end{paragraph}
-			\begin{paragraph}{FF-IRS}
+		To characterize the R-E region, we initialize the algorithm to WPT mode and increase the rate constraint gradually to obtain $S$ boundary points.
+At each point, information and power waveform are initialized to WIT and WPT solutions.
+		\begin{subsubsection}{WIT}
 			Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
 			\begin{maxi!}
-					{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
+					{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
 					\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
@@
 			Problem \ref{op:su_irs_wit} can be solved after SDR, and a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method.
-$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$.
-We then construct composite channel $\boldsymbol{h}$ by \ref{eq:h_k} and obtain the optimal information waveform from \ref{eq:w_{I,n}}.
-FF-IRS and information waveform are updated iteratively until convergence.
-The WIT algorithm for FF-IRS is summarized in Algorithm \ref{al:ff_wit}.
-				\begin{algorithm}
-					\caption{FF-IRS: WIT Initialization}
-					\label{al:ff_wit}
-					\begin{algorithmic}[1]
-						\State \textbf{Input} $\boldsymbol{h}_D, \boldsymbol{h}_I, \boldsymbol{h}_R, P, Q, \epsilon, \sigma_n$
-						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_I^{(0)}$
-						\State Construct $\boldsymbol{R}_n \ \forall n$ by \ref{eq:R_n,phi}
-						\Repeat
-						\State $i \gets i + 1$
-						\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
-						\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
-						\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
-						\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-						\State Select the best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
-						\State Update composite channel $(\boldsymbol{h}^{(i)})^\star$ by \ref{eq:h_k}
-						\State Obtain optimal power allocation $(p_n^{(i)})^\star \ \forall n$ by water-filling algorithm
-						\State Obtain optimal waveform phase $(\psi_{I,n}^{(i)})^\star \ \forall n$ by \ref{eq:psi}
-						\State Update information waveform $(\boldsymbol{w}_I^{(i)})^\star$ by \ref{eq:w_{I,n}}
-						\Until $\lvert (R^{(i)}-R^{(i-1)}) / R^{(i)} \rvert \le \epsilon$
-						\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-						\State \textbf{Output} $\boldsymbol{w}_I^\star,\theta_l^\star \ \forall l$
-					\end{algorithmic}
-				\end{algorithm}
-			\end{paragraph}
+$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$ and $\boldsymbol{h}$ can be constructed by \ref{eq:h_{k,n}}.
+On top of this, the optimal information waveform can be obtained by Maximum-Ratio Transmission (MRT).
+The IRS phase shift and information waveform are updated iteratively until convergence.
+		\end{subsubsection}
+
+		\begin{subsubsection}{WPT}
+			The current maximization problem can be solved by setting $\rho = 1$, removing the rate constraint in problem \ref{op:su_irs} and \ref{op:su_waveform} then solving them iteratively.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{R-E Sample}
-			Denote $S$ as the number of samples in the R-E boundary. Starting from WIT mode, we initialize each following sample with the solution of the previous sample.
-			\begin{paragraph}{FS-IRS}
-				Since the optimal composite channel is fixed, we only optimize the splitting ratio and waveform by either GP or inner loop method. The procedure is included in Algorithm \ref{al:fs_ao}.
+			We propose a two-layer AO algorithm to maximize the R-E region where the outer loop updates the phase shifts and the inner loop updates the splitting ratio and waveform until convergence.
+It is summarized in Algorithm \ref{al:ff_ao}.
 			\begin{algorithm}
-					\caption{FS-IRS: AO Algorithm}
-					\label{al:fs_ao}
-					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}, P, Q, S, \epsilon, \sigma_n \ \forall n$
-						\State \textbf{Initialize} $\rho_0^{\star} = 0$, $\boldsymbol{w}_{0,I}^{\star}$ by \ref{eq:w_{I,n}} and $\boldsymbol{w}_{0,P}^{\star} = \boldsymbol{0}$
-						\For{$s \gets 1, S$}
-						\State $i \gets 0$\label{st:inner_begin}
-						\State Initialize splitting ratio and waveform by previous solution $\rho_s^{(0)} = \rho_{s-1}^{\star}, \boldsymbol{w}_{s,I/P}^{(0)}=\boldsymbol{w}_{s-1,I/P}^{\star}$
-						\Repeat
-						\State $i \gets i + 1$
-						\State Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
-						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$
-						\State \textbf{Return} ($R_s^\star, z_s^\star$)
-						\EndFor
-					\end{algorithmic}
-				\end{algorithm}
-			\end{paragraph}
-
-			\begin{paragraph}{FF-IRS}
-				For SWIPT assisted by FF-IRS, we propose a two-layer AO algorithm to maximize the R-E region where the outer loop updates the phase shifts and the inner loop updates the splitting ratio and waveform until convergence.
-The algorithm is summarized in Algorithm \ref{al:ff_ao}.
-				\begin{algorithm}
-					\caption{FF-IRS: AO Algorithm}
+				\caption{Outer Loop: Phase Shift, Waveform and Splitting Ratio}
 				\label{al:ff_ao}
@@
 					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D, \boldsymbol{h}_I, \boldsymbol{h}_R, P, Q, S, \epsilon, \sigma_n \ \forall n$
-						\State \textbf{Initialize} $\rho_0^{\star} = 0$, $\boldsymbol{\phi}_0^{\star}, \boldsymbol{w}_{0,I}^{\star}$ by Algorithm \ref{al:ff_wit} and $\boldsymbol{w}_{0,P}^{\star} = \boldsymbol{0}$
-						\For{$s \gets 1, S$}
-						\State $i \gets 0$
-						\State Initialize IRS, splitting ratio and waveform by previous solution $\boldsymbol{\phi}_s^{(0)} = \boldsymbol{\phi}_{s-1}^{\star}, \rho_s^{(0)} = \rho_{s-1}^{\star}, \boldsymbol{w}_{s,I/P}^{(0)}=\boldsymbol{w}_{s-1,I/P}^{\star}$
-						\State Initialize composite channel $\boldsymbol{h}_s^{(0)}$ by \ref{eq:h_k}
-						\State Update splitting ratio $\rho_s^{(0)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
+					\State \textbf{Initialize} $i \gets 0, \boldsymbol{\phi}^{(0)}, \boldsymbol{h}^{(0)}, \boldsymbol{w}_{I/P}^{(0)}$ by WIT/WPT solutions
+					\State Obtain splitting ratio $\rho^{(0)}$ and waveform $\boldsymbol{w}_{I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
 					\Repeat
 					\State $i \gets i + 1$
-						\State Update IRS phase shift $\boldsymbol{\phi}_s^{(i)}$ by Algorithm \ref{al:ff_irs}
-						\State Update composite channel $\boldsymbol{h}_s^{(i)}$ by \ref{eq:h_k}
-						\State Update splitting ratio $\rho_s^{(i)}$ and waveform $\boldsymbol{w}_{s,I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
-						\Until $\lvert (z_s^{(i)}-z_s^{(i-1)}) / z_s^{(i)} \rvert \le \epsilon$
-						\State \textbf{Return} ($R_s^\star, z_s^\star$)
-						\EndFor
+					\State Update IRS phase shift $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:ff_irs}
+					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_{k,n}}
+					\State Update splitting ratio $\rho^{(i)}$ and waveform $\boldsymbol{w}_{I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
+					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}, R^{\star}, z^{\star}$
 				\end{algorithmic}
 			\end{algorithm}
-			\end{paragraph}
 		\end{subsubsection}

### 2020-07-13 src/config_distance.m
:dizzy: R-E plot

@@ -13,7 +13,7 @@ nRxs = 1;
 % number of users
 nUsers = 1;
 % average transmit power
-txPower = 1;
+txPower = 10;
 % average noise power
 noisePower = db2pow(-60);
 
@@ -41,7 +41,7 @@ tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves
-nSamples = 40;
+nSamples = 100;
 
 %% * Variable
 % AP-IRS distance

### 2020-07-13 src/config_irs.m

@@ -37,7 +37,7 @@ fadingMode = 'selective';
 % gain on each reflecting element
 irsGain = 1;
 % number of reflecting elements in IRS
-nReflectors = 1;
+nReflectors = 10;
 
 %% * Algorithm
 % minimum gain ratio per iteration
@@ -45,4 +45,4 @@ tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves
-nSamples = 40;
+nSamples = 100;

### 2020-07-13 src/config_reflector.m

@@ -13,7 +13,7 @@ nRxs = 1;
 % number of users
 nUsers = 1;
 % average transmit power
-txPower = 1;
+txPower = 10;
 % average noise power
 noisePower = db2pow(-60);
 
@@ -43,7 +43,7 @@ tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves
-nSamples = 40;
+nSamples = 100;
 
 %% * Variable
 % number of reflecting elements in IRS

### 2020-07-13 src/config_subband.m

@@ -13,7 +13,7 @@ nRxs = 1;
 % number of users
 nUsers = 1;
 % average transmit power
-txPower = 1;
+txPower = 10;
 % average noise power
 noisePower = db2pow(-60);
 
@@ -41,7 +41,7 @@ tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves
-nSamples = 40;
+nSamples = 100;
 
 %% * Variable
 % number of frequency bands

### 2020-07-13 src/ff_gp.m

@@ -1,19 +1,25 @@
 %% ! FF-IRS: R-E region by GP
 % * Initialize algorithm
-[capacity, irs, infoWaveform_] = wit_ff(irsGain, tolerance, directChannel, incidentChannel, reflectiveChannel, txPower, nCandidates, noisePower);
-[current, ~, ~, powerWaveform_] = wpt_ff(beta2, beta4, tolerance, directChannel, incidentChannel, reflectiveChannel, irs, txPower, nCandidates, noisePower);
-[compositeChannel, concatVector, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
-rateConstraint = linspace(0, (1 - tolerance) * capacity, nSamples);
+[capacity, irs_, infoWaveform_] = wit_ff(irsGain, tolerance, directChannel, incidentChannel, reflectiveChannel, txPower, nCandidates, noisePower);
+[current, irs__, ~, powerWaveform_] = wpt_ff(beta2, beta4, tolerance, directChannel, incidentChannel, reflectiveChannel, irs_, txPower, nCandidates, noisePower);
+[compositeChannel_, concatVector, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs_);
+rateConstraint = linspace((1 - tolerance) * capacity, 0, nSamples);
+    infoRatio = 1 - eps;
+    powerRatio = 1 - infoRatio;
+    irs = irs_;
+    compositeChannel = compositeChannel_;
+    infoWaveform = infoWaveform_;
+    powerWaveform = powerWaveform_;
+
 
 % * GP
 ffGpSample = zeros(3, nSamples);
 for iSample = 1 : nSamples
     % * Initialize waveform and splitting ratio for each sample
-    infoRatio = 1 - eps;
-    powerRatio = eps;
-    infoWaveform = infoWaveform_;
-    powerWaveform = powerWaveform_;
     [infoWaveform, powerWaveform, infoRatio, powerRatio, rate, current] = waveform_split_ratio_gp(beta2, beta4, txPower, rateConstraint(iSample), tolerance, infoRatio, powerRatio, noisePower, compositeChannel, infoWaveform, powerWaveform);
+
+%     infoRatio = 1 - eps;
+%     powerRatio = 1 - infoRatio;
 
     isConverged = false;
     current_ = 0;
@@ -24,6 +30,7 @@ for iSample = 1 : nSamples
[…]

### 2020-07-13 src/ff_sdr.m

@@ -1,9 +1,14 @@
 %% ! FF-IRS: R-E region by SDR
 % * Initialize algorithm
-[capacity, irs, infoWaveform_] = wit_ff(irsGain, tolerance, directChannel, incidentChannel, reflectiveChannel, txPower, nCandidates, noisePower);
-[current, ~, ~, powerWaveform_] = wpt_ff(beta2, beta4, tolerance, directChannel, incidentChannel, reflectiveChannel, irs, txPower, nCandidates, noisePower);
-[compositeChannel, concatVector, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
-rateConstraint = linspace(0, (1 - tolerance) * capacity, nSamples);
+[capacity, irs_, infoWaveform_] = wit_ff(irsGain, tolerance, directChannel, incidentChannel, reflectiveChannel, txPower, nCandidates, noisePower);
+[current, ~, ~, powerWaveform_] = wpt_ff(beta2, beta4, tolerance, directChannel, incidentChannel, reflectiveChannel, irs_, txPower, nCandidates, noisePower);
+[compositeChannel_, concatVector, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs_);
+% rateConstraint = linspace(0, (1 - tolerance) * capacity, nSamples);
+rateConstraint = linspace((1 - tolerance) * capacity, 0, nSamples);
+    irs = irs_;
+    compositeChannel = compositeChannel_;
+    infoRatio = 1;
+    powerRatio = 1 - infoRatio;
 
 % * SDR
 ffSdrSample = zeros(3, nSamples);
@@ -11,16 +16,16 @@ for iSample = 1 : nSamples
     % * Initialize waveform and splitting ratio for each sample
     infoWaveform = infoWaveform_;
     powerWaveform = powerWaveform_;
-
-    isConverged = false;
-    current_ = 0;
-    while ~isConverged
-        [infoRatio, powerRatio] = split_ratio(compositeChannel, noisePower, rateConstraint(iSample), infoWaveform);
-        [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCandidates, rateConstraint(iSample), tolerance, infoRatio, powerRatio, noisePower, compositeChannel, infoWaveform, powerWaveform);
-        [rate, current] = re_sample(beta2, beta4, compositeChannel, noisePower, infoWaveform, powerWaveform, infoRatio, powerRatio);
[…]

### 2020-07-13 src/lib/irs_ff.m

@@ -79,6 +79,8 @@ function [irs] = irs_ff(beta2, beta4, nCandidates, rateConstraint, tolerance, in
                 infoAuxiliary(iSubband + nSubbands) = trace(infoCoefMatrix{iSubband + nSubbands} * irsMatrix);
                 powerAuxiliary(iSubband + nSubbands) = trace(powerCoefMatrix{iSubband + nSubbands} * irsMatrix);
             end
+            infoAuxiliary(nSubbands) = hermitianize(infoAuxiliary(nSubbands));
+            powerAuxiliary(nSubbands) = hermitianize(powerAuxiliary(nSubbands));
             % \tilde{z}
             currentLb = (1 / 2) * beta2 * powerRatio * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
                 + (3 / 8) * beta4 * powerRatio ^ 2 * (2 * (2 * infoAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) ^ 2) + 2 * real(powerAuxiliary_' * powerAuxiliary) - powerAuxiliary_' * powerAuxiliary_) ...
@@ -118,6 +120,8 @@ function [irs] = irs_ff(beta2, beta4, nCandidates, rateConstraint, tolerance, in
             infoAuxiliary(iSubband + nSubbands) = trace(infoCoefMatrix{iSubband + nSubbands} * irsMatrix);
             powerAuxiliary(iSubband + nSubbands) = trace(powerCoefMatrix{iSubband + nSubbands} * irsMatrix);
         end
+        infoAuxiliary(nSubbands) = hermitianize(infoAuxiliary(nSubbands));
+        powerAuxiliary(nSubbands) = hermitianize(powerAuxiliary(nSubbands));
         % z
         current_ = (1 / 2) * beta2 * powerRatio * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
             + (3 / 8) * beta4 * powerRatio ^ 2 * (2 * infoAuxiliary(nSubbands) ^ 2 + (powerAuxiliary' * powerAuxiliary)) ...

### 2020-07-13 src/lib/waveform_sdr.m

@@ -48,6 +48,8 @@ function [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCa
         infoAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * infoMatrix);
         powerAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * powerMatrix);
     end
+    infoAuxiliary(nSubbands) = hermitianize(infoAuxiliary(nSubbands));
+    powerAuxiliary(nSubbands) = hermitianize(powerAuxiliary(nSubbands));
 
     % * SCA
     current_ = 0;
@@ -72,6 +74,8 @@ function [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCa
                 infoAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * infoMatrix);
                 powerAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * powerMatrix);
             end
+            infoAuxiliary(nSubbands) = hermitianize(infoAuxiliary(nSubbands));
+            powerAuxiliary(nSubbands) = hermitianize(powerAuxiliary(nSubbands));
             % \tilde{z}'
             currentLb = (1 / 2) * beta2 * powerRatio * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
                 + (3 / 8) * beta4 * powerRatio ^ 2 * (2 * (2 * infoAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) ^ 2) + 2 * real(powerAuxiliary_' * powerAuxiliary) - powerAuxiliary_' * powerAuxiliary_) ...
@@ -115,6 +119,8 @@ function [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCa
             infoAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * infoMatrix);
             powerAuxiliary(iSubband + nSubbands) = trace(conj(channelCoefMatrix{iSubband + nSubbands}) * powerMatrix);
         end
[…]

### 2020-07-13 src/ni_sdr.m

@@ -2,7 +2,9 @@
 % * Initialize algorithm
 [capacity, infoWaveform_] = wit_fs(directChannel, txPower, noisePower);
 [current, ~, powerWaveform_] = wpt_fs(beta2, beta4, tolerance, directChannel, txPower, nCandidates, noisePower);
-rateConstraint = linspace(0, (1 - tolerance) * capacity, nSamples);
+rateConstraint = linspace((1 - tolerance) * capacity, 0, nSamples);
+infoRatio = 1;
+powerRatio = 1 - infoRatio;
 
 % * SDR
 niSdrSample = zeros(3, nSamples);

### 2020-07-13 src/re_ni_gp_sdr.m

@@ -5,7 +5,7 @@ clear; clc; setup; config_ni_gp_sdr;  load('data/tap.mat');
 [directChannel] = frequency_response(nSubbands, subbandFrequency, fadingMode, nReflectors, directDistance, directTapGain, directTapDelay, 'direct');
 
 % * GP and SDR
-ni_gp;
+% ni_gp;
 ni_sdr;
 save('data/re_ni_gp_sdr.mat');
 

### 2020-07-15 main.tex
:dizzy: R-E plot
:construction: WIT

@@
 		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
+Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1},\dots,\boldsymbol{V}_{k,N}] \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
 	\end{subsection}
@@
 						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{I,n_2,m_j} + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1}^4 a_{n_j,m_j}s_{P,n_j,m_j} \right)\\
-						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n,m_j}s_{I,n,m_j} \prod_{j=2,4} a_{n,m_j}s_{P,n,m_j} \right)
+						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{P,n_2,m_j} \right)
 					\end{split}

### 2020-07-15 src/config.m

@@ -8,7 +8,7 @@ resistance = 50;
 beta2 = k2 * resistance;
 beta4 = k4 * resistance ^ 2;
 % number of transmit and receive antennas
-nTxs = 1;
+nTxs = 2;
 nRxs = 1;
 % number of users
 nUsers = 1;
@@ -37,7 +37,7 @@ fadingMode = 'selective';
 % gain on each reflecting element
 irsGain = 1;
 % number of reflecting elements in IRS
-nReflectors = 10;
+nReflectors = 3;
 
 %% * Algorithm
 % minimum gain ratio per iteration
@@ -45,4 +45,4 @@ tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves
-nSamples = 100;
+nSamples = 40;

### 2020-07-15 src/config_comp.m

@@ -41,7 +41,7 @@ nReflectors = 1;
 
 %% * Algorithm
 % minimum gain ratio per iteration
-tolerance = 1e-4;
+tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves

### 2020-07-15 src/config_ni_gp_sdr.m

@@ -41,7 +41,7 @@ nReflectors = 10;
 
 %% * Algorithm
 % minimum gain ratio per iteration
-tolerance = 1e-4;
+tolerance = 1e-3;
 %  number of CSCG random vectors to generate
 nCandidates = 1e4;
 % number of samples in R-E curves

### 2020-07-15 src/fs_sdr.m

@@ -1,26 +1,0 @@
-%% ! FS-IRS: R-E region by SDR
-% * Initialize algorithm
-[~, compositeChannel] = irs_fs(directChannel, incidentChannel, reflectiveChannel);
-[capacity, infoWaveform_] = wit_fs(compositeChannel, txPower, noisePower);
-[current, ~, powerWaveform_] = wpt_fs(beta2, beta4, tolerance, compositeChannel, txPower, nCandidates, noisePower);
-rateConstraint = linspace(0, (1 - tolerance) * capacity, nSamples);
-
-% * SDR
-fsSdrSample = zeros(3, nSamples);
-for iSample = 1 : nSamples
-    % * Initialize waveform and splitting ratio for each sample
-    infoWaveform = infoWaveform_;
-    powerWaveform = powerWaveform_;
-
-    % * AO
-    isConverged = false;
-    current_ = 0;
-    while ~isConverged
-        [infoRatio, powerRatio] = split_ratio(compositeChannel, noisePower, rateConstraint(iSample), infoWaveform);
-        [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCandidates, rateConstraint(iSample), tolerance, infoRatio, powerRatio, noisePower, compositeChannel, infoWaveform, powerWaveform);
-        [rate, current] = re_sample(beta2, beta4, compositeChannel, noisePower, infoWaveform, powerWaveform, infoRatio, powerRatio);
-        isConverged = abs(current - current_) / current <= tolerance || current <= 1e-10;
-        current_ = current;
-    end
-    fsSdrSample(:, iSample) = [rate; current; powerRatio];
-end

### 2020-07-15 src/lib/channel_capacity.m

@@ -3,7 +3,7 @@ function [capacity, subbandPower] = channel_capacity(channel, txPower, noisePowe
     %   - calculate the maximum achievable rate based on water-filling power allocation
     %
     % Input:
-    %   - channel (h) [nSubbands]: the wireless channel
+    %   - channel (h) [nSubbands * nTxs * nRxs]: the wireless channel
     %   - txPower (P): average transmit power
     %   - noisePower (\sigma_n^2): average noise power
     %
@@ -12,14 +12,19 @@ function [capacity, subbandPower] = channel_capacity(channel, txPower, noisePowe
     %   - subbandPower: optimal power allocation
     %
     % Comment:
-    %   - for SISO OFDM channels
+    %   - for MISO OFDM channels
     %
     % Author & Date: Yang (i@snowztail.com) - 28 Aug 19
 
 
 
-    subbandStrength = abs(channel) .^ 2;
+    % * MRT within each subband
+    subbandStrength = vecnorm(channel, 2, 2) .^ 2;
+
+    % * Power allocation
     subbandPower = water_filling(subbandStrength, 2 * txPower, noisePower);
+
+    % * Compute capacity
     capacity = sum(log2(1 + subbandPower .* subbandStrength / noisePower));
 
 end

### 2020-07-15 src/lib/composite_channel.m

@@ -1,4 +1,4 @@
-function [compositeChannel, concatVector, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs)
+function [compositeChannel, concatChannel, concatSubchannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs)
     % Function:
     %   - obtain the composition of direct channel and IRS-aided channel
     %
@@ -6,30 +6,36 @@ function [compositeChannel, concatVector, concatMatrix] = composite_channel(dire
     %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
     %   - incidentChannel (h_I) [nSubbands * nTxs * nReflectors]: the AP-IRS channel
     %   - reflectiveChannel (h_R) [nSubbands * nReflectors * nRxs]: the IRS-user channel
-    %   - irs (\phi) [nReflectors]: the IRS gain vector
+    %   - irs (\phi) [nReflectors]: IRS reflection coefficient
     %
     % Output:
-    %   - compositeChannel (h) [nSubbands * nTxs * nRxs]: the composite channel
-    %   - concatVector (M) [(nReflectors + 1) * nSubbands]: concatenated channel vector
-    %   - concatMatrix (R_n) [(nReflectors + 1) * (nReflectors + 1)]: rate SDR matrix
+    %   - compositeChannel (h) [nSubbands * nTxs * nRxs]: superposition of direct and extra channels
+    %   - concatChannel (V) [nReflectors * (nTxs * nSubbands)]: AP-IRS-user concatenated channel
+    %   - concatSubchannel (V_n) {nSubbands}[nReflectors * nTxs]: AP-IRS-user concatenated subchannel
     %
     % Comment:
-    %   - for frequency-flat IRS
+    %   - \boldsymbol{h}_{D,n}^H = directChannel(iSubband, :)
+    %   - \boldsymbol{H}_{I,n} = permute(incidentChannel(iSubband, :, :), [2 3 1])'
+    %   - \boldsymbol{h}_{R,n}^H = reflectiveChannel(iSubband, :)
+    %   - \boldsymbol{\Phi} = diag(irs')
     %
     % Author & Date: Yang (i@snowztail.com) - 21 May 20
 
 
 
-    [nSubbands, ~, nReflectors] = size(incidentChannel);
-    compositeChannel = zeros(size(directChannel));
-    concatMatrix = cell(nSubbands, 1);
[…]

### 2020-07-15 src/lib/fading_tgn.m

@@ -1,4 +1,4 @@
-function [fading] = fading_tgn(tapGain, tapDelay, nSubbands, subbandFrequency, fadingMode)
+function [fading] = fading_tgn(tapGain, tapDelay, subbandFrequency, fadingMode)
     % Function:
     %   - simulate channel using the power delay profile of the IEEE TGn NLOS channel model E
     %
@@ -22,8 +22,11 @@ function [fading] = fading_tgn(tapGain, tapDelay, nSubbands, subbandFrequency, f
     % Author & Date: Yang (i@snowztail.com) - 07 Mar 20
 
 
-
+    % * Get data
+    nSubbands = length(subbandFrequency);
     [~, nTxs, nRxs] = size(tapGain);
+
+    % * Obtain fading gain
     fading = zeros(nSubbands, nTxs, nRxs);
     switch fadingMode
     case 'selective'

### 2020-07-15 src/lib/frequency_response.m

@@ -1,15 +1,14 @@
-function [channel] = frequency_response(nSubbands, subbandFrequency, fadingMode, nReflectors, distance, tapGain, tapDelay, linkMode)
+function [channel] = frequency_response(tapGain, tapDelay, distance, nReflectors, subbandFrequency, fadingMode, linkMode)
     % Function:
     %   - get frequency response of direct, incident and reflective channels
     %
     % Input:
-    %   - nSubbands (N): number of frequency bands
-    %   - subbandFrequency (f_n) [nSubbands]: the center frequency of subbands
-    %   - fadingMode: fading mode 'flat' or 'selective'
-    %   - nReflectors: number of reflecting elements in IRS
-    %   - distance (d): distance between the transmitter and the receiver
     %   - tapGain [nTaps * nTxs * nRxs]: complex tap gain
     %   - tapDelay [nTaps]: tap delays
+    %   - distance (d): distance between the transmitter and the receiver
+    %   - nReflectors (L): number of reflecting elements in IRS
+    %   - subbandFrequency (f_n) [nSubbands]: the center frequency of subbands
+    %   - fadingMode: fading mode 'flat' or 'selective'
     %   - linkMode: link mode 'direct', 'incident', or 'reflective'
     %
     % Output:
@@ -30,9 +29,11 @@ function [channel] = frequency_response(nSubbands, subbandFrequency, fadingMode,
         tapGain = tapGain(:, 1 : nReflectors, :);
     end
 
-    % * Construct corresponding frequency response
+    % * Get pathloss and fading
     [pathloss] = path_loss(distance, linkMode);
-    [fading] = fading_tgn(tapGain, tapDelay, nSubbands, subbandFrequency, fadingMode);
+    [fading] = fading_tgn(tapGain, tapDelay, subbandFrequency, fadingMode);
+
+    % * Construct frequency response
     channel = fading / sqrt(pathloss);
 
 end

### 2020-07-15 src/lib/wit.m

@@ -1,0 +1,114 @@
+function [capacity, irs, infoWaveform, powerWaveform, infoRatio, powerRatio] = wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
+    % Function:
+    %   - optimize the waveform and IRS reflection coefficients to maximize user rate
+    %
+    % Input:
+    %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
+    %   - incidentChannel (h_I) [nSubbands * nTxs * nReflectors]: the AP-IRS channel
+    %   - reflectiveChannel (h_R) [nSubbands * nReflectors * nRxs]: the IRS-user channel
+    %   - txPower (P): transmit power constraint
+    %   - noisePower (\sigma_n^2): average noise power
+    %   - nCandidates (Q): number of CSCG random vectors to generate
+    %   - tolerance (\epsilon): minimum gain ratio per iteration
+    %
+    % Output:
+    %   - capacity (R): channel capacity
+    %   - irs (\phi) [nReflectors]: IRS reflection coefficients
+    %   - infoWaveform (w_I) [nSubbands]: weight on information waveform
+    %   - powerWaveform (w_P) [nSubbands]: weight on power waveform
+    %   - infoRatio (\bar{\rho}): information splitting ratio
+    %   - powerRatio (\rho): power splitting ratio
+    %
+    % Comment:
+    %   - solve SDR problem to obtain high-rank IRS outer product matrix
+    %   - use Gaussian randomization method to extract IRS vector
+    %   - construct information waveform by water-filling algorithm and matched filter
+    %
+    % Author & Date: Yang (i@snowztail.com) - 21 Jun 20
+
+
+
+    % * Get data
+    [nSubbands, nTxs, nReflectors] = size(incidentChannel);
+
+    % * Initialize IRS and composite channel
+    irs = exp(1i * 2 * pi * rand(nReflectors, 1));
+    [compositeChannel, ~, concatSubchannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
+
+    % * Construct waveform (water-filling + MRT) and splitting ratio
+    [~, subbandPower] = channel_capacity(compositeChannel, txPower, noisePower);
+    infoWaveform = zeros(nTxs, nSubbands);
+    for iSubband = 1 : nSubbands
[…]

### 2020-07-15 src/lib/wit_ff.m

@@ -1,100 +1,0 @@
-function [capacity, irs, infoWaveform, powerWaveform, infoRatio, powerRatio] = wit_ff(irsGain, tolerance, directChannel, incidentChannel, reflectiveChannel, txPower, nCandidates, noisePower)
-    % Function:
-    %   - optimize the waveform and IRS reflection coefficients to maximize user rate
-    %
-    % Input:
-    %   - irsGain (\beta): gain on each reflecting element
-    %   - tolerance (\epsilon): minimum gain ratio per iteration
-    %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
-    %   - incidentChannel (h_I) [nSubbands * nTxs * nReflectors]: the AP-IRS channel
-    %   - reflectiveChannel (h_R) [nSubbands * nReflectors * nRxs]: the IRS-user channel
-    %   - txPower (P): transmit power constraint
-    %   - nCandidates (Q): number of CSCG random vectors to generate
-    %   - noisePower (\sigma_n^2): average noise power
-    %
-    % Output:
-    %   - capacity (R): channel capacity
-    %   - irs (\phi) [nReflectors]: IRS reflection coefficients
-    %   - infoWaveform (w_I) [nSubbands]: weight on information carriers
-    %   - powerWaveform (w_P) [nSubbands]: weight on power carriers
-    %   - infoRatio (\bar{\rho}): information splitting ratio
-    %   - powerRatio (\rho): power splitting ratio
-    %
-    % Comment:
-    %   - solve SDR problem to obtain high-rank IRS outer product matrix
-    %   - use Gaussian randomization method to extract IRS vector
-    %   - construct information waveform by water-filling algorithm and matched filter
-    %
-    % Author & Date: Yang (i@snowztail.com) - 21 Jun 20
-
-
-
-    % * Initialize IRS and waveform
-    [nSubbands, nReflectors, ~] = size(reflectiveChannel);
-    % \boldsymbol{\phi}^{(0)}
-    irs = irsGain * ones(nReflectors, 1);
-    % h^{(0)}, \boldsymbol{R}_n
-    [compositeChannel, ~, concatMatrix] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
-    % p_n^{(0)}
-    [~, subbandPower] = channel_capacity(compositeChannel, txPower, noisePower);
-    % \rho
-    powerRatio = eps;
-    % \bar{\rho}
[…]

### 2020-07-15 src/main.m

@@ -1,0 +1,47 @@
+clear; clc; setup; config; load('data/tap.mat');
+
+% * Generate channels
+[directChannel] = frequency_response(directTapGain, directTapDelay, directDistance, nReflectors, subbandFrequency, fadingMode, 'direct');
+[incidentChannel] = frequency_response(incidentTapGain, incidentTapDelay, incidentDistance, nReflectors, subbandFrequency, fadingMode, 'incident');
+[reflectiveChannel] = frequency_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, nReflectors, subbandFrequency, fadingMode, 'reflective');
+
+[capacity, irs, infoWaveform, powerWaveform, infoRatio, powerRatio] = wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+irs = exp(1i * 2 * pi * rand(nReflectors, 1));
+
+[compositeChannel, concatChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
+
+rateConstraint = linspace(capacity, 0, nSamples);
+
+ffSdrSolution = cell(nSamples, 1);
+ffSdrSolution{1}.powerRatio = powerRatio;
+ffSdrSolution{1}.infoWaveform = infoWaveform;
+ffSdrSolution{1}.powerWaveform = powerWaveform;
+
+ffSdrSample = zeros(2, nSamples);
+ffSdrSample(:, 1) = [capacity; 0];
+
+% * SDR
+for iSample = 2 : nSamples
+    % * AO
+    isOuterConverged = false;
+    current_ = 0;
+    while ~isOuterConverged
+        [irs] = irs_ff(beta2, beta4, nCandidates, rateConstraint(iSample), tolerance, infoWaveform, powerWaveform, infoRatio, powerRatio, concatVector, noisePower, concatMatrix, irs);
+        [compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
+        isInnerConverged = false;
+        current__ = 0;
+        while ~isInnerConverged
+            [infoRatio, powerRatio] = split_ratio(compositeChannel, noisePower, rateConstraint(iSample), infoWaveform);
+            [infoWaveform, powerWaveform] = waveform_sdr(beta2, beta4, txPower, nCandidates, rateConstraint(iSample), tolerance, infoRatio, powerRatio, noisePower, compositeChannel, infoWaveform, powerWaveform);
[…]

### 2020-07-15 src/re_irs.m

@@ -1,27 +1,0 @@
-clear; clc; setup; config_irs; load('data/tap.mat');
-
-%% ! R-E region by no IRS, FF-IRS and FS-IRS
-% * Generate channels
-[directChannel] = frequency_response(nSubbands, subbandFrequency, fadingMode, nReflectors, directDistance, directTapGain, directTapDelay, 'direct');
-[incidentChannel] = frequency_response(nSubbands, subbandFrequency, fadingMode, nReflectors, incidentDistance, incidentTapGain, incidentTapDelay, 'incident');
-[reflectiveChannel] = frequency_response(nSubbands, subbandFrequency, fadingMode, nReflectors, reflectiveDistance, reflectiveTapGain, reflectiveTapDelay, 'reflective');
-
-% * SDR
-ni_sdr;
-ff_sdr;
-fs_sdr;
-save('data/re_irs.mat');
-
-%% * R-E plots
-figure('name', 'R-E region by no IRS, FF-IRS and FS-IRS');
-plot(niSdrSample(1, :) / nSubbands, 1e6 * niSdrSample(2, :), 'k--');
-hold on;
-plot(ffSdrSample(1, :) / nSubbands, 1e6 * ffSdrSample(2, :), 'r-');
-hold on;
-plot(fsSdrSample(1, :) / nSubbands, 1e6 * fsSdrSample(2, :), 'b-.');
-hold off;
-grid minor;
-legend('No IRS', 'FF-IRS', 'FS-IRS');
-xlabel('Rate [bps/Hz]');
-ylabel('Average output DC current [\muA]');
-savefig('plots/re_irs.fig');

### 2020-07-15 src/tap_response.m

@@ -2,10 +2,10 @@ clear; clc; setup;
 
 %% * Transceiver
 % number of transmit and receive antennas
-nTxs = 1;
+nTxs = 2;
 nRxs = 1;
 % max number of reflecting elements in IRS
-nReflectors = 25;
+nReflectors = 100;
 
 %% * Tap response
 [directTapGain, directTapDelay] = tap_tgn(nTxs, nRxs);

### 2020-07-20 problem.tex
:dizzy: Problem

\documentclass[9pt]{beamer}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cuted}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{siunitx}
\usepackage[short]{optidef}

\usetheme{Boadilla}

\begin{document}

\begin{frame}{Signal and channel}
    MISO, one $L$-reflector IRS, single-user, $N$-subband
    \begin{itemize}
        \item transmit signal at antenna $m$:
        \begin{equation}\label{eq:x_m}
            x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
        \end{equation}
        \item composite channel at subband $n$:
        \begin{itemize}
            \item AP-user direct channel $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$
            \item IRS-aided extra channel: concatenate the following terms
            \begin{itemize}
                \item AP-IRS incident channel $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$
                \item IRS reflection diagonal matrix $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$
                \item IRS-user reflective channel $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$
            \end{itemize}
        \end{itemize}
        \begin{equation}\label{eq:h_{n}}
            \boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \alert{\boldsymbol{\phi}^H} \boldsymbol{V}_{n}
        \end{equation}
        where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]\alert{^H} \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
        \item received signal
        \begin{equation}
            y(t)=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_n^H}\left({\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}+\boldsymbol{w}_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
        \end{equation}
    \end{itemize}
\end{frame}

\begin{frame}{Problem formulation}
    \begin{maxi!}
		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\addConstraint{0 \le \rho \le 1}
    \end{maxi!}
    where $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
\end{frame}

\begin{frame}{Challenge: the fourth-order term in current expression}
    \begin{equation}
        \mathcal{A}\left\{y_{P}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}
    \end{equation}
    Two known approaches so far:
    \begin{block}{GP}
        \begin{equation}
            \mathcal{A}\left\{y_{P}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4} \lVert{\boldsymbol{h}_{{n_1}}}\rVert \lVert{\boldsymbol{h}_{{n_2}}}\rVert \lVert{\boldsymbol{h}_{{n_3}}}\rVert \lVert{\boldsymbol{h}_{{n_4}}}\rVert}
        \end{equation}
        where $s_{P,n}$ is real scalar.
    \end{block}
    \begin{block}{SDP}
        \begin{equation}
            \mathcal{A}\left\{y_{P}^4(t)\right\} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}^*\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}^*\boldsymbol{h})^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H
        \end{equation}
        where $\boldsymbol{h}=[\boldsymbol{h}_{1}^T,\dots,\boldsymbol{h}_{N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries.
    \end{block}
\end{frame}

\begin{frame}{GP-based approach}
    \begin{block}{Joint design of $\boldsymbol{\phi}$, $s_{I/P,n}$, $\rho$}
        GP is not applicable for $\boldsymbol{\phi}$ since its real and imaginary parts could take negative value.
    \end{block}
    \vspace{1em}
    \begin{block}{Alternating optimization of ($s_{I/P,n}$, $\rho$) and $\boldsymbol{\phi}$}
        Cannot formulate IRS design as convex problem:
        \begin{itemize}
            \item need to approximate $\lVert{\boldsymbol{h}_{{n_1}}}\rVert \lVert{\boldsymbol{h}_{{n_2}}}\rVert \lVert{\boldsymbol{h}_{{n_3}}}\rVert \lVert{\boldsymbol{h}_{{n_4}}}\rVert$
            \item even if we provide first-order approximation to the fourth-order term above, $\lVert{\cdot}\rVert$ (reduce to $\lvert{\cdot}\rvert$ for SISO) produces convex objective function
            \begin{itemize}
                \item can solve dual problem but no idea to prove zero duality gap
            \end{itemize}
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{SDP-based approach: alternating optimization of ($\boldsymbol{w}_{I/P,n}$, $\rho$) and $\boldsymbol{\phi}$}
    IRS design problem:
    \begin{maxi!}
        {\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})=\mathrm{Tr}(\boldsymbol{A}\boldsymbol{\Phi})}{\label{op:irs}}{}
        \addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}\label{co:rate}}
        \addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
        \addConstraint{\boldsymbol{\Phi}\succeq{0}}
        \addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
    \end{maxi!}
    Despite being convex, problem \ref{op:irs} is not a standard SDP due to rate constraint \ref{co:rate}, and there is no proof that the loss from SDR would be negligible. In other words, we only obtain $\boldsymbol{\Phi}^{\star}$.
    \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{assets/sdp.eps}
    \end{figure}
\end{frame}

\begin{frame}{Simulation results}
    For SISO only, simulation show that $\boldsymbol{\Phi}^{\star}$ is (always almost) rank-1, and $\boldsymbol{\phi}^{\star}$ extracted by Gaussian randomization method achieves the same performance as $\boldsymbol{\Phi}^{\star}$.
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{assets/irs_matrix_tx_1.eps}
        \caption{Eigenvalue of $\boldsymbol{\Phi}^{\star}$ for Tx = 1}
    \end{figure}
    For MISO this is not the case.
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{assets/irs_matrix_tx_2.eps}
        \caption{Eigenvalue of $\boldsymbol{\Phi}^{\star}$ for Tx = 2}
    \end{figure}
\end{frame}

\begin{frame}{R-E plots}
    We optimize ($\boldsymbol{w}_{I/P,n}$, $\rho$) and $\boldsymbol{\phi}$ alternatively. IRS is always optimized by SDR, and the plots compare waveform optimized by GP and SDR.
    \begin{figure}[ht]
        \begin{minipage}[b]{0.5\linewidth}
            \centering
            \includegraphics[width=.65\linewidth]{assets/week_29_re_gp_sdr.eps}
            \caption{GP (black) vs SDR}
            \label{fi:gp_sdr}
        \end{minipage}%
        \begin{minipage}[b]{0.5\linewidth}
            \centering
            \includegraphics[width=.65\linewidth]{assets/week_29_re_irs.eps}
            \caption{No IRS vs single reflector}
        \end{minipage}
        \begin{minipage}[b]{0.5\linewidth}
            \centering
            \includegraphics[width=.65\linewidth]{assets/week_29_re_reflector.eps}
            \caption{Number of reflectors}
        \end{minipage}%
        \begin{minipage}[b]{0.5\linewidth}
            \centering
            \includegraphics[width=.65\linewidth]{assets/week_29_re_distance.eps}
            \caption{AP-IRS distance}
        \end{minipage}
    \end{figure}
\end{frame}

\begin{frame}{Problem}
    \begin{itemize}
        \item Although $\boldsymbol{\Phi}^{\star}$ turns out rank-1 for SISO, we have no idea on its demonstration
        \item Even if we rewrite sum-rate constraint \ref{co:rate} as quadratic form $\mathrm{Tr}(\boldsymbol{C}\boldsymbol{\Phi})$, the approximation accuracy $\gamma$ requires further check (due to this additional constraint)
    \end{itemize}
\end{frame}

\end{document}

### 2020-07-27 main.tex
:dizzy: Problem
:art: Harvester model

@@
 To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain to compensate the propagation loss and boost the energy efficiency with a low power consumption.
-This paper investigates an IRS-aided multiuser Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where the single-antenna Access Point (AP) transmits information and energy simultaneously to multiple single-antenna users under the assist of IRS.
-We aim to maximize the weighted sum Rate-Energy (R-E) region via jointly optimizing the phase shifts at the IRS, the transmit waveform at the AP, and the power splitting ratio for all users.
-The problem is equivalent to a current maximization problems subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
+This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
+We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the phase shifts at the IRS, and the splitting ratio at the user.
+The problem is formulated as current maximization problem subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
 Numerical results demonstrated that dedicated power signal is beneficial to multicarrier SWIPT, while IRS brings significant R-E region enlargement over benchmark schemes when properly configured.
@@
 
-		To the best of authors' knowledge, most existing papers assume a Frequency-Flat (FF) IRS where all elements reflect the signal of different frequency equally.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS since active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics \cite{Anwar2018}.
+		Most existing papers assume a Frequency-Flat (FF) IRS where all elements reflect different frequencies equally.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is prohibitive since active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics and unable to adjust channel adaptively \cite{Anwar2018}.
 	\end{subsection}
@@
 	\begin{subsection}{Objective and Methodology}
-		In this paper, we study an IRS-aided multiuser MISO SWIPT system where the IRS assists the information and energy transmission of all users.
+		In this paper, we study an IRS-aided broadband downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
 A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g.
@@
 The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
-Different from previous research, this paper investigates the fundamental impact of harvester nonlinearity on waveform and IRS design.
+Different from previous research, this paper focus on broadband SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design.
 We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints.
-To reduce the design complexity, we	propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) technique.
-It was demonstrated that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively.
-Also, IRS brings a significant channel amplification and R-E enhancement especially when located near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
+To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) and Geometric Programming (GP) technique.
+Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations.
+We demonstrate that dedicated power waveform boosts the energy transmission efficiency, such that TS and PS are preferred for low-rate and high-rate applications respectively.
+Also, IRS brings a significant channel amplification thus R-E enhancement especially when located near the transmitter/receiver, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
 	\end{subsection}
@@
 \begin{section}{System Model}
-	Consider an IRS-aided multiuser MISO OFDM SWIPT system where the $M$-antenna transmitter delivers information and power simultaneously, through a single $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands.
-We assume a total bandwidth $B$ with evenly-spaced subbands around center frequency $f_c$.
-Each subband is allocated to one user per time slot, and denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
+	Consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
+We assume a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$).
 Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design.
-A quasi-static block fading channel model is considered for all links and we focus on one particular block where the channels are approximately unchanged.
-We characterize and compare the R-E region achieved by TS and PS receivers.
+A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
+Two practical co-located receiver architectures are compared in terms of R-E region.
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into data and energy streams for ID and EH, and the splitting ratio $\rho$ is coupled with waveform and IRS design.
+In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design.
 Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
 	\begin{subsection}{Transmit Signal}
-		Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which belongs to one user at time $t$ and follows a capacity-achieving i.i.d.
-Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
-Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0$ for $k' \ne k$.
-Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$.
-The superposed transmit signal at time $t$ on antenna $m$ ($m=1,\dots,M$) is
+		Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows a capacity-achieving i.i.d.
+Circular Symmetric Complex Gaussian (CSCG) distribution with zero mean and unit variance $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
+The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
 		\begin{equation}\label{eq:x_m}
@@
 		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
-Let $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ such that the transmit information and power signals write as
+Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas and let $\boldsymbol{s}_{I/P,n}$, $\boldsymbol{\psi}_{I/P,n}$ be the magnitude and phase of $\boldsymbol{w}_{I/P,n}$.
+Therefore, the transmit information and power signals write as
 		\begin{align}
@@
 		\end{align}
-		We also define $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and let $\boldsymbol{s}_{I/P}=\lvert{\boldsymbol{w}_{I/P}}\rvert$, $\boldsymbol{\psi}_{I/P}=\angle{\boldsymbol{w}_{I/P}}$ be the magnitude and phase of the waveforms.
+
+		% We also define $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and let $\boldsymbol{s}_{I/P}=\lvert{\boldsymbol{w}_{I/P}}\rvert$, $\boldsymbol{\psi}_{I/P}=\angle{\boldsymbol{w}_{I/P}}$ be the waveform magnitude and phase.
 	\end{subsection}
@@
 	\begin{subsection}{Composite Channel}
-		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$.
+		At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$.
 At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
 On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel.
-Hence, the composite channel for user $k$ over subband $n$ is
-		\begin{equation}\label{eq:h_{k,n}}
-			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
+The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel.
+On top of this, the total composite channel is formed by adding the IRS-aided extra channel to the AP-user direct channel as
+		\begin{equation}\label{eq:h_n}
+			\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
 		\end{equation}
-		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1},\dots,\boldsymbol{V}_{k,N}] \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
+		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
+Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
+
+		% Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1},\dots,\boldsymbol{V}_{k,N}] \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
 	\end{subsection}
@@
 	\begin{subsection}{Receive Signal}
-		The information and power signals received by user $k$ through both direct and IRS-aided links write as
-		\begin{align}\label{eq:y_{I/P,k}}
-			y_{I,k}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
-			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
+		At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution of information and power components over $N$ subbands, where
+		\begin{align}\label{eq:y_{I/P}}
+			y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
+			y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
 		\end{align}
@@
 	\begin{subsection}{Information Decoder}
-		A major benefit of the proposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
-		\begin{equation}\label{eq:R_k}
-			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
+		A major benefit of the proposed waveform is that the determined power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
+		\begin{equation}\label{eq:R}
+			R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho)=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
 		\end{equation}
-		where $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion on tone $n$.
-Rate \ref{eq:R_k} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
+		where $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$.
+Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
 	\end{subsection}
@@
 	\begin{subsection}{Energy Harvester}
-		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights for user $k$ the dependency of harvester output DC current on the received waveform as
-		\begin{equation}\label{eq:i_k}
-			i_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
+		In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}.
+Fig.
+\ref{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
+Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network.
+Assume the voltage across matching network is negligible and the RF-band noise is too small to harvest.
+When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$) with power splitting ratio $\rho$, the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.
+
+		\begin{figure}
+			\centering
+			\begin{subfigure}[t]{0.45\linewidth}
+				\centering
+				\includegraphics[width=\linewidth]{assets/antenna_equivalent_circuit.eps}
+				\caption{Antenna equivalent circuit}
+				\label{fi:antenna_equivalent_circuit}
+			\end{subfigure}%
+			~
+			\begin{subfigure}[t]{0.45\linewidth}
+				\centering
+				\includegraphics[width=\linewidth]{assets/single_diode_rectifier.eps}
+				\caption{A single diode rectifier}
+				\label{fi:single_diode_rectifier}
+			\end{subfigure}
+			\caption{Rectenna circuit}
+		\end{figure}
+
+		Rectifiers consist of nonlinear components as diode and capacitor to produce DC and store energy \cite{Hagerty2004,Pinuela2013}.
+Consider a simplified rectifier in Fig.
+\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with load.
+Denote $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the voltage across the load.
+A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ (with $i_s$ the reverse bias saturation current, $n'$ the diode ideality factor, $v_t$ the thermal voltage) around a quiescent operating point $v_d=a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i,i=1,\dots,\infty$.
+Note that this small signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
+Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}.
+Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
+		\begin{equation}\label{eq:i_d}
+			i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i
 		\end{equation}
-		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.
-For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,n}$.
 
-		With the assumption of evenly spaced frequencies, it holds that $\mathcal{E}\left\{y_k(t)^i\right\}=0$ for odd $i$ and the related terms has no contribution to DC components.
-For simplicity, we truncate the infinite series to the $n_0$-th order.
-As proved in \cite{Clerckx2016a}, maximizing a truncated $i_k$ is equivalent to maximizing a monotonic function
-		\begin{equation}\label{eq:z_k}
-			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
+		By truncating \ref{eq:i_d} to the $n_0$-th order, discarding non-DC components, and taking expectation over symbol distribution, we approximate the average output DC current for a given channel as
+		\begin{equation}\label{eq:i_out}
+			i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}
+		\end{equation}
+
+		With the assumption of evenly spaced frequencies, it holds that $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC components.
+It is also proved in \cite{Clerckx2016a} that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
+		\begin{equation}\label{eq:z}
+			z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
 		\end{equation}
 		where $k_i=i_s/i!(nv_t)^i$.
-We choose $n_0=4$ to investigate fundamental nonlinearity and let $\beta_2={k_2}{R_{\text{ant}}}$ and $\beta_4={k_4}{R_{\text{ant}}^2}$.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+For simplicity, we choose $n_0=4$ to investigate fundamental nonlinearity and let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$ can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
 
@@
 Due to the positive definiteness of $\boldsymbol{W}_{I/P}$ and $\boldsymbol{H}_k$, we have $\boldsymbol{W}_{I/P,-n}=\boldsymbol{W}_{I/P,n}^H$ and $\boldsymbol{H}_{k,-n}=\boldsymbol{H}_{k,n}^H$.
-On top of this, the nonzero terms in \ref{eq:z_k} are expressed by \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end} and $z_k$ reduces to \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform}.
+On top of this, the nonzero terms in \ref{eq:z} are expressed by \ref{eq:z_terms_begin} -- \ref{eq:z_terms_end} and $z$ reduces to \ref{eq:z_expand} -- \ref{eq:z_waveform}.
 		\begin{figure*}[b]
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\label{eq:z_k_terms_begin}\\
+				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\label{eq:z_terms_begin}\\
 				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
@@
 				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{k,{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{k,{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{k,{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{k,{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}\\
-				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H\label{eq:z_k_terms_end}
+				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H\label{eq:z_terms_end}
 			\end{align}
@@
 			\begin{align}
-				z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
-				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_k_expand}\\
+				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
+				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_expand}\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
 				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H\right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_k_channel}\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_channel}\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
 				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_k_waveform}
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_waveform}
 			\end{align}
@@
 				C_{R-Z}(P)
-				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
+				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z,\\
 				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
@@
 		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
-		\addConstraint{\lvert{\phi}\rvert=1, \quad l=1,\dots,L}
+		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
 		\addConstraint{0 \le \rho \le 1}
@@
 		\end{equation}
-		Therefore, \ref{eq:z_k_channel} rewrites as
+		Therefore, \ref{eq:z_channel} rewrites as
 		\begin{equation}\label{eq:z_irs}
@@
 		\begin{subsubsection}{Geometric Programming}
-			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R_k} and \ref{eq:z_k_expand} -- \ref{eq:z_k_waveform} that the optimal phases of information and power waveform are both match to the composite channel as
+			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R} and \ref{eq:z_expand} -- \ref{eq:z_waveform} that the optimal phases of information and power waveform are both match to the composite channel as
 			\begin{equation}\label{eq:psi}
@@
 				\end{equation}
-				Therefore, \ref{eq:z_k_waveform} rewrites as
+				Therefore, \ref{eq:z_waveform} rewrites as
 				\begin{equation}\label{eq:z_waveform}
@@
 			Problem \ref{op:su_irs_wit} can be solved after SDR, and a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method.
-$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$ and $\boldsymbol{h}$ can be constructed by \ref{eq:h_{k,n}}.
+$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$ and $\boldsymbol{h}$ can be constructed by \ref{eq:h_n}.
 On top of this, the optimal information waveform can be obtained by Maximum-Ratio Transmission (MRT).
@@
 					\State Update IRS phase shift $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:ff_irs}
-					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_{k,n}}
+					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_n}
 					\State Update splitting ratio $\rho^{(i)}$ and waveform $\boldsymbol{w}_{I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})

### 2020-07-28 main.tex
:art: Output DC current

@@
 \ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with load.
-Denote $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the voltage across the load.
+Denote $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
 A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ (with $i_s$ the reverse bias saturation current, $n'$ the diode ideality factor, $v_t$ the thermal voltage) around a quiescent operating point $v_d=a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i,i=1,\dots,\infty$.
@@
 
-		By truncating \ref{eq:i_d} to the $n_0$-th order, discarding non-DC components, and taking expectation over symbol distribution, we approximate the average output DC current for a given channel as
+		By discarding non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
 		\begin{equation}\label{eq:i_out}
@@
 
-		With the assumption of evenly spaced frequencies, it holds that $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC components.
+		With the assumption of evenly spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC components.
 It is also proved in \cite{Clerckx2016a} that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
@@
 		where $k_i=i_s/i!(nv_t)^i$.
+It can be observed that the traditional linear harvester model, where the output DC power is the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$.
+However, due to the coupling among different frequencies, some high-order terms also cancel out non-DC components thus contribute to the output DC power.
+In other words, even terms with $i \ge 4$ account for the nonlinear behavior of the diode.
 For simplicity, we choose $n_0=4$ to investigate fundamental nonlinearity and let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$.
@@
 
-		Similar to \cite{Huang2017}, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$, $\boldsymbol{H}_k=\boldsymbol{h}_k\boldsymbol{h}_k^H$ and let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{k,n}$ keep their $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries, respectively.
-Due to the positive definiteness of $\boldsymbol{W}_{I/P}$ and $\boldsymbol{H}_k$, we have $\boldsymbol{W}_{I/P,-n}=\boldsymbol{W}_{I/P,n}^H$ and $\boldsymbol{H}_{k,-n}=\boldsymbol{H}_{k,n}^H$.
-On top of this, the nonzero terms in \ref{eq:z} are expressed by \ref{eq:z_terms_begin} -- \ref{eq:z_terms_end} and $z$ reduces to \ref{eq:z_expand} -- \ref{eq:z_waveform}.
+		Following \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+Moreover, let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{H}=\boldsymbol{h}\boldsymbol{h}^H$, $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries, respectively.
+On top of this, DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4} and $z$ is reduced to \ref{eq:z_expand} -- \ref{eq:z_expand_2}.
 		\begin{figure*}[b]
@@
 			\begin{align}
-				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\label{eq:z_terms_begin}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I\\
-				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
-				& = \frac{3}{4}\left(\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n})^H}\right)^2\\
-				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2\\
-				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
-				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{k,n}^H\boldsymbol{w}_{P,n})^H}\\
-				& = \frac{1}{2}\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P\\
-				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
-				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{k,{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{k,{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{k,{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{k,{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}\\
-				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H\label{eq:z_terms_end}
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
+				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\label{eq:y_I2}\\
+				& = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h} = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{0}\boldsymbol{w}_I\\
+				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
+				& = \frac{3}{4}\left(\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2\\
+				& = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{0}\boldsymbol{w}_I)^2\\
+				\mathcal{A}\left\{y_{P}^2(t)\right\}
+				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H}\\
+				& = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h} = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{0}\boldsymbol{w}_P\\
+				\mathcal{A}\left\{y_{P}^4(t)\right\}
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}\\
+				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{n}\boldsymbol{w}_P)^H\label{eq:y_P4}
 			\end{align}
@@
 				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
-				& = \beta_2\rho\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+\beta_4\rho^2\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\label{eq:z_expand}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k+\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^H\right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,0}\boldsymbol{h}_k)\label{eq:z_channel}\\
+				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
+				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\nonumber\\
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\label{eq:z_expand_1}\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^H \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_waveform}
+				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)^H \right)\nonumber\\
+				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_expand_2}
 			\end{align}

### 2020-07-28 main.tex
:art: System model

@@
 		\begin{equation}\label{eq:R}
-			R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho)=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
+			\begin{split}
+				R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho)
+				& = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}\\
+				& = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}
+			\end{split}
 		\end{equation}
@@
 		With the assumption of evenly spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC components.
-It is also proved in \cite{Clerckx2016a} that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
+However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
 		\begin{equation}\label{eq:z}
@@
 		where $k_i=i_s/i!(nv_t)^i$.
-It can be observed that the traditional linear harvester model, where the output DC power is the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$.
+It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$.
 However, due to the coupling among different frequencies, some high-order terms also cancel out non-DC components thus contribute to the output DC power.
@@
 
-		Following \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-Moreover, let $\boldsymbol{W}_{I/P,n}$, $\boldsymbol{H}_{n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{H}=\boldsymbol{h}\boldsymbol{h}^H$, $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries, respectively.
-On top of this, DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4} and $z$ is reduced to \ref{eq:z_expand} -- \ref{eq:z_expand_2}.
+		Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries.
+On top of this, $z$ is reduced to \ref{eq:z_expand} with DC terms expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
 		\begin{figure*}[b]
@@
 			\begin{align}
+				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
+				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
-				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\label{eq:y_I2}\\
-				& = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h} = \frac{1}{2}\boldsymbol{w}_I^H\boldsymbol{H}_{0}\boldsymbol{w}_I\\
+				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\label{eq:y_I2}\\
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
-				& = \frac{3}{4}\left(\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2\\
-				& = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{0}\boldsymbol{w}_I)^2\\
+				& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\\
 				\mathcal{A}\left\{y_{P}^2(t)\right\}
-				& = \frac{1}{2}\sum_n{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H}\\
-				& = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h} = \frac{1}{2}\boldsymbol{w}_P^H\boldsymbol{H}_{0}\boldsymbol{w}_P\\
+				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\\
 				\mathcal{A}\left\{y_{P}^4(t)\right\}
-				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H}\\
-				& = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{n}\boldsymbol{w}_P)^H\label{eq:y_P4}
+				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\label{eq:y_P4}
 			\end{align}
@@
 				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
-				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
+				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\\
 				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\nonumber\\
@@
 
-	\begin{subsection}{Weighted Sum Rate-Energy Region}
-		Define the achievable weighted sum R-E region as
+	\begin{subsection}{Rate-Energy Region}
+		Define the achievable R-E region as
 		\begin{equation}
 			\begin{split}
-				C_{R-Z}(P)
-				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z,\\
+				C_{R_{\text{ID}}-I_{\text{EH}}}(P)
+				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\\
 				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
@@
 		\end{equation}
-		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
+		where $P$ is the average transmit power budget.
 	\end{subsection}
@@
 
-\begin{section}{Single-User Optimization}
-	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$.
-We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
+\begin{section}{Problem Formulation}
+	We characterize the R-E region through multiple current maximization problems subject to transmit power, IRS magnitude, and different rate constraints
 	\begin{maxi!}
@@
 		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
+		\addConstraint{R \ge \bar{R}}\label{eq:su_rate_constraint}
 		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
@@
 	\end{maxi!}
-	Problem \ref{op:su} is intricate due to coupled variables and non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint}.
-To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.
+	Problem \ref{op:su} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}.
+To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.
 

### 2020-07-29 main.tex
:art: IRS optimization

@@
 
-		Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+		Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$.
 Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries.
@@
 				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\label{eq:y_P4}
-			\end{align}
-		\end{figure*}
-		\begin{figure*}[b]
-			\hrule
-			\begin{align}
-				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
-				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\label{eq:z_expand_1}\\
-				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
-				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)^H \right)\nonumber\\
-				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_expand_2}
 			\end{align}
@@
 	\begin{maxi!}
-		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
+		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:original}}{\label{eq:su_target}}
 		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
@@
 	\end{maxi!}
-	Problem \ref{op:su} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}.
+	Problem \ref{op:original} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}.
 To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.
@@
 	\begin{subsection}{IRS Phase Shift}
-		We optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{I/P,n}$ and splitting ratio $\rho$. Since
-		\begin{equation}\label{eq:h_n_outer_product}
+		In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
+		\begin{equation}
 			\begin{split}
-				\boldsymbol{h}_n\boldsymbol{h}_n^H
-				&=(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\\
-				&=\boldsymbol{h}_{D,n}\boldsymbol{h}_{D,n}^H+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{h}_{D,n}^H+\boldsymbol{h}_{D,n}\boldsymbol{\phi}^H\boldsymbol{V}_n+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{\phi}^H\boldsymbol{V}_n\\
-				&=\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n
+				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2
+				& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\\
+				& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\\
+				& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
+				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
+				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
 			\end{split}
 		\end{equation}
-		where $t$ is an auxiliary variable with unit modulus and
-		\begin{equation}\label{eq:M_n,phi}
-			\boldsymbol{M}_n=
-			\begin{bmatrix}
-				\boldsymbol{V}_n \\
-				\boldsymbol{h}_{D,n}^H
-			\end{bmatrix} \in \mathbb{C}^{(L+1) \times M},
-			\quad \bar{\boldsymbol{\phi}}=\
-			\begin{bmatrix}
-				\boldsymbol{\phi} \\
-				t
-			\end{bmatrix},
-			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
-		\end{equation}
-		Therefore, it holds that
+		where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+Similarly, we define $t_{I/P,n}$ ($n=-N+1,\dots,N-1$) as
 		\begin{equation}
 			\begin{split}
-				\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2
-				&=\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
-				&=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
-				&=\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
+				t_{I/P,n}
+				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\\
+				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\\
+				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\\
+				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\\
+				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\\
+				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
 			\end{split}
 		\end{equation}
-		with
-		\begin{equation}\label{eq:C_n}
-			\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}
-		\end{equation}
-		Similarly, we have
-		\begin{equation}
-			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
-		\end{equation}
-		where
-		\begin{equation}\label{eq:M}
-			\boldsymbol{M}=
-			\begin{bmatrix}
-				\boldsymbol{V} \\
-				\boldsymbol{h}_D^H
-			\end{bmatrix} \in \mathbb{C}^{(L+1) \times MN}
-		\end{equation}
-		Next, introduce auxiliary variables
-		\begin{equation}\label{eq:t}
-			\begin{split}
-				t_{I/P,n}
-				&=\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*\boldsymbol{h}\\
-				&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)\\
-				&=\mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*)\\
-				&=\mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H\boldsymbol{\Phi})\\
-				&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
-			\end{split}
-		\end{equation}
-		with
-		\begin{equation}\label{eq:C_{I/P,n}}
-			\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
-		\end{equation}
-		Therefore, \ref{eq:z_channel} rewrites as
+		where $\boldsymbol{h}_D=[\boldsymbol{h}_{D,1}^H,\dots,\boldsymbol{h}_{D,N}^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+
+		Therefore, the objective function \ref{eq:z_expand} rewrites as
 		\begin{equation}\label{eq:z_irs}
@@
 		\end{equation}
-		We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_irs}.
+
+		To maximize non-concave expression \ref{eq:z_irs}, we use first-order Taylor expansion to approximate its second-order terms.
 Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
@@
 		\end{align}
-		\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to the corresponding terms in \ref{eq:z_irs}, and the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
+		which provide lower bounds to the corresponding terms in \ref{eq:z_irs}.
+At iteration $i$, the approximated objection function $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ is detailed in \ref{eq:z_irs_approx}.
 		\begin{figure*}[b]
@@
 		\end{figure*}
-		Hence, problem \ref{op:su} is transformed to
+		Hence, problem \ref{op:original} is transformed to
 		\begin{maxi!}
-			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
-			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
+			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{eq:su_irs_target}}
+			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}\label{co:irs_rate}
 			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
@@
 		\end{maxi!}
-		We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method.
-If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD).
-Otherwise, a solution can be extracted through Gaussian randomization method \cite{Huang2010}.
-We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$.
-Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates by
-		\begin{equation}
-			\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}
-		\end{equation}
-		The candidate maximizing the objective function \ref{eq:su_irs_target} is chosen as the optimal solution $\bar{\boldsymbol{\phi}}^\star$.
-Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:ff_irs}.
+
+		Problem \ref{op:irs} is not a standard Semi-Definite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
+Therefore, even if we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
+In Section [TODO], we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
+
+		When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is obtained by Eigenvalue Decomposition (EVD).
+Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
+Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{eq:su_irs_target}.
+Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
+The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:irs}.
 		\begin{algorithm}
 			\caption{IRS Phase Shift}
-			\label{al:ff_irs}
+			\label{al:irs}
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$
-				\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
-				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:M_n,phi}, \ref{eq:C_n}, \ref{eq:C_{I/P,n}}
-				\Repeat;
+				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
+				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
+				\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$, $n=-N+1,\dots,N-1$
+				\Repeat
 					\State $i \gets i + 1$
-				\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
-				\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA
+					\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem \ref{op:irs}
 				\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-				\State Perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$
-				\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
-				\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
-				\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\bar{\boldsymbol{\phi}}^\star$ for problem \ref{op:su_irs}
-				\State Compute phase shift by $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-				\State \textbf{Output} $\theta_l^\star \ \forall l$
+				\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
+				\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
+					\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+				\Else
+					\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
+
+					\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
+					\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
+					\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
+				\EndIf
+				\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+				\State \textbf{Output} $\theta_l^\star$
 			\end{algorithmic}
@@
 			\end{equation}
-			Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem
+			Therefore, the original problem \ref{op:original} is reduced to an amplitude optimization problem
 			\begin{maxi!}
@@
 				\end{equation}
-				Hence, problem \ref{op:su} is transformed to
+				Hence, problem \ref{op:original} is transformed to
 				\begin{maxi!}
@@
 In this case, $z(\rho)$ is also expressed in \ref{eq:z_waveform} with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
-Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function with affine $\rho$ and transform problem \ref{op:su} to
+Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function with affine $\rho$ and transform problem \ref{op:original} to
 				\begin{maxi!}
@@
 		\begin{subsubsection}{WPT}
-			The current maximization problem can be solved by setting $\rho = 1$, removing the rate constraint in problem \ref{op:su_irs} and \ref{op:su_waveform} then solving them iteratively.
+			The current maximization problem can be solved by setting $\rho = 1$, removing the rate constraint in problem \ref{op:irs} and \ref{op:su_waveform} then solving them iteratively.
 		\end{subsubsection}
@@
 					\State $i \gets i + 1$
-					\State Update IRS phase shift $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:ff_irs}
+					\State Update IRS phase shift $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
 					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_n}

### 2020-07-29 main.tex
:art: Waveform optimization

@@
 We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints.
-To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) and Geometric Programming (GP) technique.
+To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) technique.
 Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations.
@@
 		\end{equation}
-		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
-Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas and let $\boldsymbol{s}_{I/P,n}$, $\boldsymbol{\psi}_{I/P,n}$ be the magnitude and phase of $\boldsymbol{w}_{I/P,n}$.
+		where $w_{I/P,n,m}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
+Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas.
 Therefore, the transmit information and power signals write as
+		% , and let $\boldsymbol{w}_{I/P,n}=\boldsymbol{s}_{I/P,n} e^{j \boldsymbol{\psi}_{I/P,n}}$ such that $\boldsymbol{s}_{I/P,n}$, $\boldsymbol{\psi}_{I/P,n} \in \mathbb{C}^{M \times 1}$ denote the magnitude and phase of the waveform at subband $n$
 		\begin{align}
@@
 		\end{align}
-
-		% We also define $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and let $\boldsymbol{s}_{I/P}=\lvert{\boldsymbol{w}_{I/P}}\rvert$, $\boldsymbol{\psi}_{I/P}=\angle{\boldsymbol{w}_{I/P}}$ be the waveform magnitude and phase.
 	\end{subsection}
@@
 		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
-
-		% Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1},\dots,\boldsymbol{V}_{k,N}] \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
+Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.% Let $\boldsymbol{h}_n=\boldsymbol{a}_n e^{j \boldsymbol{\varsigma}_n}$ such that $\boldsymbol{a}_n$, $\boldsymbol{\varsigma}_n \in \mathbb{C}^{M \times 1}$ denote the magnitude and phase of the composite channel at subband $n$.
 	\end{subsection}
@@
 		At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution of information and power components over $N$ subbands, where
-		\begin{align}\label{eq:y_{I/P}}
+		\begin{align}\label{eq:y_IP}
 			y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
@@
 				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\\
-				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
+				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right) \le P\biggr\}
 			\end{split}
 		\end{equation}
-		where $P$ is the average transmit power budget.
+		where $P$ is the average transmit power budget and the coefficient $1/2$ converts the maximum power of sine waves to the average power.
 	\end{subsection}
@@
 	\begin{maxi!}
-		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:original}}{\label{eq:su_target}}
-		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
-		\addConstraint{R \ge \bar{R}}\label{eq:su_rate_constraint}
+		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}
+		\addConstraint{R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho) \ge \bar{R}}\label{co:original_rate}
 		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
@@
 	\end{maxi!}
-	Problem \ref{op:original} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}.
+	Problem \ref{op:original} is intricate with coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
 To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.
@@
 		where $\boldsymbol{h}_D=[\boldsymbol{h}_{D,1}^H,\dots,\boldsymbol{h}_{D,N}^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-
-		Therefore, the objective function \ref{eq:z_expand} rewrites as
+Therefore, the rate and objective expressions \ref{eq:R} and \ref{eq:z_expand} rewrites as \ref{eq:R_irs} and \ref{eq:z_irs}, respectively.
+		\begin{equation}\label{eq:R_irs}
+			R(\boldsymbol{\Phi}) = \sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}
+		\end{equation}
 		\begin{equation}\label{eq:z_irs}
@@
 			(t_{I,0}^{(i)})^2
-			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\
+			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\\
 			t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
@@
 			& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
-			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}
+			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2
 		\end{align}
@@
 			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{eq:su_irs_target}}
-			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}\label{co:irs_rate}
+			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
 			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
@@
 
-		Problem \ref{op:irs} is not a standard Semi-Definite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
+		Problem \ref{op:irs} is not a standard Semidefinite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
 Therefore, even if we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
@@
 		\begin{algorithm}
-			\caption{IRS Phase Shift}
+			\caption{SDR: IRS Phase Shift}
 			\label{al:irs}
@@
 					\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem \ref{op:irs}
+					\State Compute $z^{(i)}$ by \ref{eq:z_irs}
 				\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
@@
 	\begin{subsection}{Waveform and Splitting Ratio}
-		\begin{subsubsection}{Geometric Programming}
-			Following \cite{Clerckx2018b}, it can be observed from \ref{eq:R} and \ref{eq:z_expand} -- \ref{eq:z_waveform} that the optimal phases of information and power waveform are both match to the composite channel as
-			\begin{equation}\label{eq:psi}
-				\boldsymbol{\psi}_{I}^{\star}=\boldsymbol{\psi}_{P}^{\star}=-\boldsymbol{\varsigma}
+		Next, we jointly optimize both information and power waveforms $\boldsymbol{w}_{I/P}$ together with splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
+As pointed out in \cite{Clerckx2018b}, the waveform design in frequency and spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
+		\begin{equation}\label{eq:w_IP}
+			\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n^H}{\lVert{\boldsymbol{h}_n}\rVert}
 		\end{equation}
-			By such a phase selection, we have
-			\begin{equation}
-				\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert^2=(\boldsymbol{a}_n^H\boldsymbol{s}_{I,n})^2=\sum_{m_1,m_2}\prod_{j=1}^2{a_{n,m}s_{I,n,m}} \triangleq E_n
+		That is to say, it is only necessary to determine the amplitudes $s_{I/P,n}$ at different tones for single-user MISO SWIPT, and the original waveform optimization with $2MN$ variables is converted into a power allocation problem with $2N$ nonnegative real variables.
+Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$.
+At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
+With such a beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective expressions \ref{eq:R} and \ref{eq:z_expand} reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}.
+		\begin{equation}\label{eq:R_waveform}
+			R(\boldsymbol{s}_I,\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}\biggr)\right)
 		\end{equation}
-			Therefore, the original problem \ref{op:original} is reduced to an amplitude optimization problem
-			\begin{maxi!}
-					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:su_gp}}{}
-					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)E_n}{\sigma_n^2}\right)} \ge \bar{R}}
-				\end{maxi!}
 		\begin{figure*}[b]
 			\hrule
-				\begin{equation}\label{eq:z_gp}
+			\begin{equation}\label{eq:z_waveform}
 				\begin{split}
 					z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
-						& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \sum_{m_1,m_2} \left( \prod_{j=1}^2 {a_{n,m_j}s_{I,n,m_j}} + \prod_{j=1}^2 {a_{n,m_j}s_{P,n,m_j}} \right)\\
-						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{I,n_2,m_j} + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1}^4 a_{n_j,m_j}s_{P,n_j,m_j} \right)\\
-						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{P,n_2,m_j} \right)
+					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{I,n}^2+s_{P,n}^2)\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{I,{n_j}} \right)\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 s_{I,{n_1}}^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{P,{n_2}}^2 \right)
 				\end{split}
@@
 		\end{figure*}
-			with $z$ expressed in \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and rewrite problem \ref{op:su_gp} as
+		Therefore, \ref{op:original} is reduced to an amplitude optimization problem
+		\begin{maxi!}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:waveform}}{}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right)\le{P}}
+			\addConstraint{R(\boldsymbol{s}_I,\rho) \ge \bar{R}}
+		\end{maxi!}
+		Since problem \ref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
 		\begin{mini!}
-					{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}
-					\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P}) \le P}
-					\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}
-					\addConstraint{\frac{2^{\bar{R}}}{\prod_n \left(1+{\bar{\rho}E_n}/{\sigma_n^2}\right)} \le 1}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right) \le P}
+			\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}\label{co:waveform_objective}
+			\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
 			\addConstraint{\rho + \bar{\rho} \le 1}
 		\end{mini!}
-			Problem \ref{op:su_gp_1} can be transformed into standard GP by first decomposing the information and power posynomials as sum of monomials, then deriving their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}.
-Specifically, define
+		It is observed that the denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, and we further express them in a compact form
 		\begin{align}
-				z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\\
-				1+\frac{\bar{\rho}E_n}{\sigma_n^2}&=\sum_{m_{I,n}}g_{m_{I,n}}(\boldsymbol{s}_{I,n},\bar{\rho})
+			z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\label{eq:posynomial_objective}\\
+			1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}&=\sum_{m_{I,n}}g_{m_{I,n}}(s_{I,n},\bar{\rho})\label{eq:posynomial_rate}
 		\end{align}
-			On top of this, problem \ref{op:su_gp_1} is equivalent to
+		where $m_P,m_{I,n}$ are the number of monomials in the corresponding posynomials (obviously $m_{I,n}=2$).
+It is suggested in \cite{Clerckx2018b,Chiang2005} that posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} can be upper bounded by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem \ref{op:waveform_rgp} is equivalent to
 		\begin{mini}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_2}}{}
-				\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
-				\addConstraint{{t''}\prod_{m_P}{\left(\frac{g_{{m_P}}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{{m_P}}}\right)^{-\gamma_{{m_P}}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{I,n}}\left(\frac{g_{m_{I,n}}(\boldsymbol{s}_{I,n},\bar{\rho})}{\gamma_{m_{I,n}}}\right)^{-\gamma_{m_{I,n}}}\le{1}}
+			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right)\le{P}}
+			\addConstraint{{t'}\prod_{m_P}{\left(\frac{g_{{m_P}}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{{m_P}}}\right)^{-\gamma_{{m_P}}}}\le{1}}
+			\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{I,n}}\left(\frac{g_{m_{I,n}}(s_{I,n},\bar{\rho})}{\gamma_{m_{I,n}}}\right)^{-\gamma_{m_{I,n}}}\le{1}}
 			\addConstraint{\rho + \bar{\rho} \le 1}
 		\end{mini}
-			where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$ and $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update \cite{Clerckx2018b}.
-At iteration $i$, we choose
+		where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$, $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update, and a feasible choice at iteration $i$ is \cite{Clerckx2018b}
 		\begin{align}
-				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(\boldsymbol{s}_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}E_n^{(i-1)}}/{\sigma_n^2}}\label{eq:gamma_I}\\
-				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}
+			\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\\
+			\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}/{\sigma_n^2}}\label{eq:gamma_I}
 		\end{align}
-			then solve problem \ref{op:su_gp_2}. The GP algorithm is summarized in Algorithm \ref{al:waveform_split_ratio_gp}.
+		$\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence and the GP algorithm is summarized in Algorithm \ref{al:waveform}.
+It is also known as a inner approximation algorithm that only provides a KKT solution \cite{Marks1978a}.
 		\begin{algorithm}
 			\caption{GP: Waveform and Splitting Ratio}
-				\label{al:waveform_split_ratio_gp}
+			\label{al:waveform}
 			\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\bar{R},\epsilon,\sigma_n \ \forall n$
+				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$
 				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
-					\State Retrieve channel magnitude and phase $\boldsymbol{a}, \varsigma$
 				\Repeat
 					\State $i \gets i + 1$
-					\State Update GM exponents $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ by \ref{eq:gamma_I}, \ref{eq:gamma_P}
-					\State Obtain waveform amplitude $\boldsymbol{s}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_gp_2}
-					\State Compute output DC current $z^{(i)}$ by \ref{eq:z_gp}
+					\State Update $\{\gamma_{m_P}^{(i)},\gamma_{m_{I,n}}^{(i)}\}$ by \ref{eq:gamma_P}, \ref{eq:gamma_I}
+					\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem \ref{op:waveform_gp}
+					\State Compute $z^{(i)}$ by \ref{eq:z_waveform}
 				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-					\State Recover waveform $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:psi}
+				\State Retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
 				\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
@@
 		\end{algorithm}
-		\end{subsubsection}
-
-		\begin{subsubsection}{Semi-Definite Relaxation}
-			In this case, waveform and splitting ratio are updated iteratively until convergence.
-			\begin{paragraph}{Transmit Waveform}
-				Consider the waveform optimization subproblem. Once $\boldsymbol{\phi}$ and $\rho$ are obtained, introduce auxiliary variables
-				\begin{equation}\label{eq:t'}
-					t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
-				\end{equation}
-				Therefore, \ref{eq:z_waveform} rewrites as
-				\begin{equation}\label{eq:z_waveform}
-					\begin{split}
-						z(\boldsymbol{W}_I,\boldsymbol{W}_P)
-						&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
-						&\quad+\frac{3}{8} \beta_4 \rho^2 \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\
-						&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}
-					\end{split}
-				\end{equation}
-				Since \ref{eq:z_waveform} and \ref{eq:z_irs} are in the same form, we reuse \ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} and bound $z(\boldsymbol{W}_I,\boldsymbol{W}_P)$ by replacing $t_{I/P,n}$ with $t_{I/P,n}'$ in \ref{eq:z_irs_approx}.
-Also, denote $\boldsymbol{W}_{I,n}'$ as the $n$-th block in the main diagonal of $\boldsymbol{W}_{I}$ such that
-				\begin{equation}
-					\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert^2=\boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\mathrm{Tr}(\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{W}_{I,n}')
-				\end{equation}
-				Hence, problem \ref{op:original} is transformed to
-				\begin{maxi!}
-					{\boldsymbol{W}_I,\boldsymbol{W}_P}{\tilde{z}(\boldsymbol{W}_I,\boldsymbol{W}_P)}{\label{op:su_waveform}}{\label{eq:su_waveform_target}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{W}_{I,n}')}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_waveform_constraint}}
-					\addConstraint{\frac{1}{2}\left(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P)\right) \le P}
-					\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
-					\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1\label{co:waveform_rank}}
-				\end{maxi!}
-				We then perform SDR and solve the optimal waveform matrix $\boldsymbol{W}_{I/P}^{\star}$ iteratively by interior-point method.
-$\boldsymbol{w}_I^{\star}$ and $\boldsymbol{w}_P^{\star}$ can be extracted using randomized vectors $\boldsymbol{r}_q \in \mathbb{C}^{MN \times 1}$ whose entries are uniformly distributed on the unit circle.
-The algorithm is summarized in Algorithm \ref{al:waveform_sdr}.
-				\begin{algorithm}
-					\caption{SDR: Transmit Waveform}
-					\label{al:waveform_sdr}
-					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$
-						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$ by \ref{eq:t'}
-						\State Construct $\boldsymbol{H}_n \ \forall n$
-						\Repeat
-						\State $i \gets i + 1$
-						\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ by solving problem \ref{op:su_waveform}
-						\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
-						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-						\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
-						\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
-						\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
-						\State Select the best solution $\boldsymbol{W}_{I/P}^\star$ and $\boldsymbol{w}_{I/P}^\star$ for problem \ref{op:su_waveform}
-						\State \textbf{Output} $\boldsymbol{w}_{I/P}^\star$
-					\end{algorithmic}
-				\end{algorithm}
-			\end{paragraph}
-
-			\begin{paragraph}{Receive Splitting Ratio}
-				We then optimize the power splitting ratio $\rho$ for any fixed phase shift $\boldsymbol{\phi}$ and waveform $\boldsymbol{w}_{I/P}$.
-In this case, $z(\rho)$ is also expressed in \ref{eq:z_waveform} with constant $t_{I/P,n}'$ given by \ref{eq:t'}.
-Since $z(\rho)$ is a quadratic function that monotonically increases over $\rho \in [0, 1]$, we replace the convex objective function with affine $\rho$ and transform problem \ref{op:original} to
-				\begin{maxi!}
-					{\rho}{\rho}{\label{op:su_ratio}}{\label{eq:su_ratio_target}}
-					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_n^H \boldsymbol{w}_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}\label{eq:su_ratio_constraint}}
-					\addConstraint{0 \le \rho \le 1}
-				\end{maxi!}
-				The optimal power splitting ratio $\rho^\star$ can be obtained by solving problem \ref{op:su_ratio}.
-			\end{paragraph}
-
-			\begin{paragraph}{Inner Loop}
-				As summarized in Algorithm \ref{al:inner_loop}, the inner loop updates the waveform and splitting ratio iteratively until convergence.
-				\begin{algorithm}
-					\caption{Inner Loop: Waveform and Splitting Ratio}
-					\label{al:inner_loop}
-					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,Q,\bar{R},\epsilon,\rho,\sigma_n \ \forall n$
-						\State \textbf{Initialize} $\boldsymbol{w}_{I/P}^{(0)}$
-						\State $i \gets 0$
-						\Repeat
-						\State $i \gets i + 1$
-						\State Update splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_ratio}
-						\State Update waveform $\boldsymbol{w}_{I/P}^{(i)}$ by Algorithm \ref{al:waveform_sdr}
-						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-						\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
-					\end{algorithmic}
-				\end{algorithm}
-			\end{paragraph}
-		\end{subsubsection}
 	\end{subsection}
@@
 					\State \textbf{Initialize} $i \gets 0, \boldsymbol{\phi}^{(0)}, \boldsymbol{h}^{(0)}, \boldsymbol{w}_{I/P}^{(0)}$ by WIT/WPT solutions
-					\State Obtain splitting ratio $\rho^{(0)}$ and waveform $\boldsymbol{w}_{I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
+					\State Obtain splitting ratio $\rho^{(0)}$ and waveform $\boldsymbol{w}_{I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform}) or inner loop (Algorithm \ref{al:inner_loop})
 					\Repeat
@@
 					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_n}
-					\State Update splitting ratio $\rho^{(i)}$ and waveform $\boldsymbol{w}_{I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform_split_ratio_gp}) or inner loop (Algorithm \ref{al:inner_loop})
+					\State Update splitting ratio $\rho^{(i)}$ and waveform $\boldsymbol{w}_{I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform}) or inner loop (Algorithm \ref{al:inner_loop})
 					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$

### 2020-07-31 main.tex
:lock: Convergence proof

@@
 			\begin{split}
-				R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho)
+				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho)
 				& = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}\\
@@
 		\begin{equation}\label{eq:z}
-			z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
+			z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
 		\end{equation}
@@
 			\begin{align}
-				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
+				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)
 				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
@@
 	\begin{maxi!}
-		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:original}}{\label{ob:original}}
-		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}
-		\addConstraint{R(\boldsymbol{w}_I,\boldsymbol{\phi},\rho) \ge \bar{R}}\label{co:original_rate}
-		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
+		{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
+		\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
+		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
 		\addConstraint{0 \le \rho \le 1}
@@
 
-		To maximize non-concave expression \ref{eq:z_irs}, we use first-order Taylor expansion to approximate its second-order terms.
+		To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA)-based algorithm that approximate the second-order terms by first-order Taylor expansion.
 Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
@@
 			(t_{I,0}^{(i)})^2
-			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\\
+			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:taylor_1}\\
 			t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
-			& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
+			& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\label{eq:taylor_2}\\
 			t_{I,0}^{(i)} t_{P,0}^{(i)}
@@
 			& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
-			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2
+			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:taylor_3}
 		\end{align}
@@
 		\begin{maxi!}
-			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{eq:su_irs_target}}
+			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
 			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
+			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}\label{co:irs_modulus}
 			\addConstraint{\boldsymbol{\Phi}\succeq{0}}
@@
 Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
-Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{eq:su_irs_target}.
+Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}.
 Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
@@
 		\begin{algorithm}
-			\caption{SDR: IRS Phase Shift}
+			\caption{SCA: IRS Phase Shift}
 			\label{al:irs}
@@
 				\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-				\State \textbf{Output} $\theta_l^\star$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
 			\end{algorithmic}
@@
 			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right) \le P}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right) \le P}\label{co:waveform_power}
 			\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}\label{co:waveform_objective}
@@
 		$\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence and the GP algorithm is summarized in Algorithm \ref{al:waveform}.
-It is also known as a inner approximation algorithm that only provides a KKT solution \cite{Marks1978a}.
+It is also known as a inner approximation algorithm that only provides a KKT solution \cite{Marks1978}.
 		\begin{algorithm}
@@
 				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-				\State Retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
+				\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
 				\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
@@
 
-	\begin{subsection}{R-E Region Characterization}
-		To characterize the R-E region, we initialize the algorithm to WPT mode and increase the rate constraint gradually to obtain $S$ boundary points.
-At each point, information and power waveform are initialized to WIT and WPT solutions.
-		\begin{subsubsection}{WIT}
-			Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
-			\begin{maxi!}
-					{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
-					\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
-					\addConstraint{\boldsymbol{\Phi}\succeq{0}}
-					\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
-				\end{maxi!}
-			Problem \ref{op:su_irs_wit} can be solved after SDR, and a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method.
-$\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$ and $\boldsymbol{h}$ can be constructed by \ref{eq:h_n}.
-On top of this, the optimal information waveform can be obtained by Maximum-Ratio Transmission (MRT).
-The IRS phase shift and information waveform are updated iteratively until convergence.
-		\end{subsubsection}
-
-		\begin{subsubsection}{WPT}
-			The current maximization problem can be solved by setting $\rho = 1$, removing the rate constraint in problem \ref{op:irs} and \ref{op:su_waveform} then solving them iteratively.
-		\end{subsubsection}
-
-		\begin{subsubsection}{R-E Sample}
-			We propose a two-layer AO algorithm to maximize the R-E region where the outer loop updates the phase shifts and the inner loop updates the splitting ratio and waveform until convergence.
-It is summarized in Algorithm \ref{al:ff_ao}.
+	\begin{subsection}{Alternating Optimization}
+		For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and transmit waveform together with receive splitting ratio by Algorithm \ref{al:waveform} until convergence.
+The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
 		\begin{algorithm}
-				\caption{Outer Loop: Phase Shift, Waveform and Splitting Ratio}
-				\label{al:ff_ao}
+			\caption{Alternating Algorithm for Problem \ref{op:original}}
+			\label{al:alternating}
 			\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D, \boldsymbol{h}_I, \boldsymbol{h}_R, P, Q, S, \epsilon, \sigma_n \ \forall n$
-					\State \textbf{Initialize} $i \gets 0, \boldsymbol{\phi}^{(0)}, \boldsymbol{h}^{(0)}, \boldsymbol{w}_{I/P}^{(0)}$ by WIT/WPT solutions
-					\State Obtain splitting ratio $\rho^{(0)}$ and waveform $\boldsymbol{w}_{I/P}^{(0)}$ by GP (Algorithm \ref{al:waveform}) or inner loop (Algorithm \ref{al:inner_loop})
+				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,\sigma_n,\bar{R},Q,\epsilon$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
 				\Repeat
 					\State $i \gets i + 1$
-					\State Update IRS phase shift $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
-					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_n}
-					\State Update splitting ratio $\rho^{(i)}$ and waveform $\boldsymbol{w}_{I/P}^{(i)}$ by GP (Algorithm \ref{al:waveform}) or inner loop (Algorithm \ref{al:inner_loop})
-					\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
-					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}, R^{\star}, z^{\star}$
+					\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
+					\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $n=1,\dots,N$ by \ref{eq:h_n} and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
+					\State Compute $z^{(i)}$ by \ref{eq:z_irs}
+				\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
 			\end{algorithmic}
 		\end{algorithm}
+	\end{subsection}
+
+	\begin{subsection}{Convergence and Complexity}
+		\begin{subsubsection}{Convergence}
+			The proposed alternating algorithm iteratively employs SCA-based IRS phase shift Algorithm \ref{al:irs} and GP-based waveform and splitting ratio Algorithm \ref{al:waveform} until convergence.
+
+			\textbf{Proposition 1}. \textit{For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.}
+
+			\textit{Proof:} The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
+Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}.
+Thus, Algorithm \ref{al:irs} is guaranteed to converge.
+To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$, and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
+Therefore, Algorithm \ref{al:irs} converges to a stationary point.
+
+			\textbf{Proposition 2}.
+\textit{For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.}
+
+			\textit{Proof:} See \cite{Clerckx2016a,Clerckx2018b}.
+
+			\textbf{Proposition 3}.
+\textit{Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.}
+
+			\textit{Proof:} The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
+Thus, Algorithm \ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
+As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem \ref{op:original}.
 		\end{subsubsection}

### 2020-08-06 main.tex
:ambulance: Fix MRT expression
:pencil: Parameter settings

@@
 		\begin{equation}\label{eq:w_IP}
-			\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n^H}{\lVert{\boldsymbol{h}_n}\rVert}
+			\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
 		\end{equation}
@@
 
+\begin{section}{Performance Evaluations}
+	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups through simulations.
+Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}.
+The power delay profile of the frequency-selective fading channels are obtained from IEEE TGn NLOS channel model E \cite{Erceg2004}.
+Taps are modelled as i.i.d.
+CSCG random variables with normalized total power, and we assume no spatial correlation across all channels.
+The path loss model is given by
+	\begin{equation}
+		L(d)=L_0\left(\frac{d}{d_0}\right)^{-\alpha}
+	\end{equation}
+	where $L_0$ is the path loss at a reference distance $d_0$, $d$ is the distance between transmitter and receiver, $\alpha$ is the path loss exponent.
+We set $d_0=1$ \si{\metre}, $L_0=-30$ \si{\decibel}, and let $\alpha_D=3.8$, $\alpha_I=2.2$, $\alpha_R=2.2$ be the path loss exponents of direct, incident and reflective links, respectively.
+Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
+The average transmit power is fixed to $P=4$ \si{\W} while the average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
+Each transmit/receive antenna and IRS element is assumed to have a $0$ \si{\dBi} antenna gain.
+Also, we choose a tolerance $\epsilon=10^{-8}$ and set $Q=10^{3}$ for the Gaussian randomization method.
+\end{section}
+
 \bibliographystyle{IEEEtran}

### 2020-08-12 main.tex
:pencil: Add layouts

--- 2020-07-31 main.tex
@@
 \input{packages.tex}
+
+\graphicspath{{assets/}}
 
@@
 \begin{section}{System Model}
-	Consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
-We assume a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$).
+	As shown in Figure \ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
+Suppose a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$).
 Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design.
@@
 Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
+
+	\begin{figure}
+		\centering
+		\def\svgwidth{\columnwidth}
+		\input{assets/system.pdf_tex}
+		\caption{An IRS-aided OFDM SWIPT system}
+		\label{fi:system}
+	\end{figure}
+
 	\begin{subsection}{Transmit Signal}
@@
 Therefore, the transmit information and power signals write as
-		% , and let $\boldsymbol{w}_{I/P,n}=\boldsymbol{s}_{I/P,n} e^{j \boldsymbol{\psi}_{I/P,n}}$ such that $\boldsymbol{s}_{I/P,n}$, $\boldsymbol{\psi}_{I/P,n} \in \mathbb{C}^{M \times 1}$ denote the magnitude and phase of the waveform at subband $n$
 		\begin{align}
@@
 		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.% Let $\boldsymbol{h}_n=\boldsymbol{a}_n e^{j \boldsymbol{\varsigma}_n}$ such that $\boldsymbol{a}_n$, $\boldsymbol{\varsigma}_n \in \mathbb{C}^{M \times 1}$ denote the magnitude and phase of the composite channel at subband $n$.
+Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
 	\end{subsection}
@@
 Fig.
-\ref{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
+\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
 Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network.
@@
 
-		\begin{figure}
+		\begin{figure}[h]
 			\centering
@@
 				\centering
-				\includegraphics[width=\linewidth]{assets/antenna_equivalent_circuit.eps}
+				\begin{circuitikz}[scale=0.7, transform shape]
+					\draw (0,0) to [sV=$v_s$] (0,2);
+					\draw (0,2) to [short] (1,2);
+					\draw (1,2) to [R=$R_\text{ant}$] (3,2);
+					\draw (3,2) to [short] (4,2);
+					\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
+					\draw (4,0) to [short] (2,0) node[ground](GND){};
+					\draw (2,0) to [short] (0,0);
+				\end{circuitikz}
 				\caption{Antenna equivalent circuit}
-				\label{fi:antenna_equivalent_circuit}
+				\label{ci:antenna_equivalent_circuit}
 			\end{subfigure}%
@@
 				\centering
-				\includegraphics[width=\linewidth]{assets/single_diode_rectifier.eps}
+				\begin{circuitikz}[scale=0.7, transform shape]
+					\draw (0,0) to [sV=$v_\text{in}$] (0,2);
+					\draw (0,2) to [short] (0.5,2);
+					\draw (0.5,2) to [D, v<=$v_d$, i=$i_d$] (2.5,2);
+					\draw (2.5,2) to [short, -*] (3,2);
+					\draw (3,2) to [C, l_=$C$, -*] (3,0);
+					\draw (3,2) to [short] (4.5,2);
+					\draw (4.5,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4.5,0);
+					\draw (4.5,0) to [short] (2.25,0) node[ground](GND){};
+					\draw (2.25,0) to [short] (0,0);
+				\end{circuitikz}
 				\caption{A single diode rectifier}
-				\label{fi:single_diode_rectifier}
+				\label{ci:single_diode_rectifier}
 			\end{subfigure}
-			\caption{Rectenna circuit}
+			\caption{Rectenna circuits}
 		\end{figure}
@@
 Consider a simplified rectifier in Fig.
-\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with load.
+\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with load.
 Denote $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
@@
 
+\begin{section}{Performance Evaluations}
+	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups through simulations.
+Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}.
+As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line that is parallel to the AP-user path.
+Define the projection of the AP-IRS path onto the AP-user path as $d_H$, and let the distance from the IRS to the AP-user path be $d_V$.
+Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths.
+We set $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}.
+For all channels, the path loss and power delay profile of the frequency-selective fading are obtained from IEEE TGn channel model D \cite{Erceg2004}.
+Reference path loss is set to $L_0=-35$ \si{\dB} at a distance of 1 \si{\meter}.
+Taps are modelled as i.i.d.
+CSCG random variables with normalized total power, and we assume no spatial correlation across all arrays.
+Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
+The average transmit power is fixed to $P=-36$ \si{\dBm} while the average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
+Each IRS element is assumed to have a $3$ \si{\dBi} antenna gain.
+We also choose a tolerance $\epsilon=10^{-8}$ and set $Q=10^{3}$ for the Gaussian randomization method.
+
+	\begin{figure}
+		\centering
+		\def\svgwidth{\columnwidth}
+		\input{assets/layout.pdf_tex}
+		\caption{System layout}
+		\label{fi:layout}
+	\end{figure}
+\end{section}
+
 \bibliographystyle{IEEEtran}

### 2020-08-14 main.tex
:pencil: Parameters

@@
 \begin{section}{Performance Evaluations}
-	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups through simulations.
+	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups.
 Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}.
@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average transmit power is fixed to $P=-36$ \si{\dBm} while the average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
-Each IRS element is assumed to have a $3$ \si{\dBi} antenna gain.
-We also choose a tolerance $\epsilon=10^{-8}$ and set $Q=10^{3}$ for the Gaussian randomization method.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
+We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.
+For the algorithm, the tolerance is $\epsilon=10^{-8}$ and the number of candidates in the Gaussian randomization method is $Q=10^{3}$.
 

### 2020-08-14 main.tex
:art: Convergence proof

@@
 
-			\textbf{Proposition 1}. \textit{For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.}
+			\begin{proposition}\label{pr:irs}
+				For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.
+			\end{proposition}
 
-			\textit{Proof:} The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
+			\begin{proof}\label{pf:irs}
+				The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
 Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}.
@@
 Therefore, Algorithm \ref{al:irs} converges to a stationary point.
+			\end{proof}
 
-			\textbf{Proposition 2}.
-\textit{For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.}
+			\begin{proposition}\label{pr:waveform}
+				For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.
+			\end{proposition}
 
-			\textit{Proof:} See \cite{Clerckx2016a,Clerckx2018b}.
+			\begin{proof}\label{pf:waveform}
+				See \cite{Clerckx2016a,Clerckx2018b}.
+			\end{proof}
 
-			\textbf{Proposition 3}.
-\textit{Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.}
+			\begin{proposition}\label{pr:ao}
+				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.
+			\end{proposition}
 
-			\textit{Proof:} The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
+			\begin{proof}\label{pf:ao}
+				The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
 Thus, Algorithm \ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
 As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem \ref{op:original}.
+			\end{proof}
 		\end{subsubsection}

### 2020-08-17 main.tex
:pencil: Path loss

@@
 As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line that is parallel to the AP-user path.
-Define the projection of the AP-IRS path onto the AP-user path as $d_H$, and let the distance from the IRS to the AP-user path be $d_V$.
+Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$.
 Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths.
@@
 For all channels, the path loss and power delay profile of the frequency-selective fading are obtained from IEEE TGn channel model D \cite{Erceg2004}.
-Reference path loss is set to $L_0=-35$ \si{\dB} at a distance of 1 \si{\meter}.
+Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the equivalent path loss of AP-user and AP-IRS-user links is $L=-58.61$ \si{\dB}.
 Taps are modelled as i.i.d.
@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands, corresponding to a large-scale SNR of $19.39$ \si{\dB}.
 We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.

### 2020-09-04 main.tex
:pencil: Path loss and noise power

@@
 Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths.
-We set $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}.
-For all channels, the path loss and power delay profile of the frequency-selective fading are obtained from IEEE TGn channel model D \cite{Erceg2004}.
-Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the equivalent path loss of AP-user and AP-IRS-user links is $L=-58.61$ \si{\dB}.
+We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}.
+For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}.
+Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the reference path loss of direct, incident and reflective links are $L_D=-61.16$ \si{\dB}, $L_I=-44.03$ \si{\dB} and $L_R=-59.17$ \si{\dB}, respectively.
 Taps are modelled as i.i.d.
@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands, corresponding to a large-scale SNR of $19.39$ \si{\dB}.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
 We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.

### 2020-09-04 src/config/config_distance.m
:construction: Path loss and noise power

@@ -55,11 +55,11 @@ nChannels = 1;
 % projection of AP-IRS distance to the AP-user path
 Variable.horizontalDistance = 2 : 2 : 8;
 % large-scale signal-to-noise ratio
-Variable.snr = zeros(1, length(Variable.horizontalDistance));
+snr = zeros(1, length(Variable.horizontalDistance));
 for iDistance = 1 : length(Variable.horizontalDistance)
     [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, Variable.horizontalDistance(iDistance));
     [sumPathloss] = sum_pathloss(directDistance, incidentDistance, reflectiveDistance);
-    Variable.snr(iDistance) = txPower * sumPathloss * rxGain / noisePower;
+    snr(iDistance) = txPower * sumPathloss * rxGain / noisePower;
 end
 
 %% * PBS

### 2020-09-04 src/config/config_noise.m

@@ -26,6 +26,8 @@ verticalDistance = 2;
 horizontalDistance = 2;
 % AP-IRS and IRS-user distance
 [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
+% equivalent pathloss
+[sumPathloss] = sum_pathloss(directDistance, incidentDistance, reflectiveDistance);
 % center frequency
 centerFrequency = 5.18e9;
 % bandwidth
@@ -54,8 +56,13 @@ nSamples = 30;
 nChannels = 1;
 
 %% * Variable
+% average noise power
+Variable.noisePower = db2pow(-50 : -10 : -90);
 % large-scale signal-to-noise ratio
-Variable.snr = db2pow(10 : 10 : 40);
+snr = zeros(1, length(Variable.noisePower));
+for iNoise = 1 : length(Variable.noisePower)
+    snr(iNoise) = txPower * sumPathloss * rxGain / Variable.noisePower(iNoise);
+end
 
 %% * PBS
 % number of individual jobs

### 2020-09-04 src/plot/plot_noise.m

@@ -1,0 +1,31 @@
+clear; clc; config_noise;
+
+%% * Load batch data
+reSet = cell(nBatches, length(Variable.noisePower));
+for iBatch = 1 : nBatches
+    load(sprintf('../data/re_noise_%d.mat', iBatch), 'reInstance');
+    reSet(iBatch, :) = reInstance;
+end
+
+%% * Average over batches
+reNoise = cell(1, length(Variable.noisePower));
+for iNoise = 1 : length(Variable.noisePower)
+    reNoise{iNoise} = mean(cat(3, reSet{:, iNoise}), 3);
+end
+save('../data/re_noise.mat');
+
+%% * R-E plots
+figure('name', 'R-E region vs average noise power');
+legendString = cell(1, length(Variable.noisePower));
+for iNoise = 1 : length(Variable.noisePower)
+    plot(reNoise{iNoise}(1, :) / nSubbands, 1e6 * reNoise{iNoise}(2, :));
+    legendString{iNoise} = sprintf('\sigma_n = %d dB', pow2db(Variable.noisePower(iNoise)));
+    hold on;
+end
+hold off;
+grid minor;
+legend(legendString);
+xlabel('Per-subband rate [bps/Hz]');
+ylabel('Average output DC current [\muA]');
+ylim([0 inf]);
+savefig('../figures/re_noise.fig');

### 2020-09-04 src/plot/plot_snr.m

@@ -1,31 +1,0 @@
-clear; clc; config_snr;
-
-%% * Load batch data
-reSet = cell(nBatches, length(Variable.snr));
-for iBatch = 1 : nBatches
-    load(sprintf('../data/re_snr_%d.mat', iBatch), 'reInstance');
-    reSet(iBatch, :) = reInstance;
-end
-
-%% * Average over batches
-reSnr = cell(1, length(Variable.snr));
-for iSnr = 1 : length(Variable.snr)
-    reSnr{iSnr} = mean(cat(3, reSet{:, iSnr}), 3);
-end
-save('../data/re_snr.mat');
-
-%% * R-E plots
-figure('name', 'R-E region vs large-scale SNR');
-legendString = cell(1, length(Variable.snr));
-for iSnr = 1 : length(Variable.snr)
-    plot(reSnr{iSnr}(1, :) / nSubbands, 1e6 * reSnr{iSnr}(2, :));
-    legendString{iSnr} = sprintf('SNR = %d dB', pow2db(Variable.snr(iSnr)));
-    hold on;
-end
-hold off;
-grid minor;
-legend(legendString);
-xlabel('Per-subband rate [bps/Hz]');
-ylabel('Average output DC current [\muA]');
-ylim([0 inf]);
-savefig('../figures/re_snr.fig');

### 2020-09-04 src/re_noise.m

@@ -1,8 +1,8 @@
-clear; clc; setup; config_snr;
+clear; clc; setup; config_noise;
 
 %% ! R-E region for different large-scale SNR
-reSample = cell(nChannels, length(Variable.snr));
-reSolution = cell(nChannels, length(Variable.snr));
+reSample = cell(nChannels, length(Variable.noisePower));
+reSolution = cell(nChannels, length(Variable.noisePower));
 
 for iChannel = 1 : nChannels
     % * Generate tap gains and delays
@@ -15,23 +15,20 @@ for iChannel = 1 : nChannels
     [incidentChannel] = frequency_response(incidentTapGain, incidentTapDelay, incidentDistance, rxGain, subbandFrequency, fadingMode);
     [reflectiveChannel] = frequency_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
-    % * Calculate sum pathloss
-    [sumPathloss] = sum_pathloss(directDistance, incidentDistance, reflectiveDistance);
-
-    for iSnr = 1 : length(Variable.snr)
-        % * Calculate noise power based on SNR
-        noisePower = txPower * sumPathloss * rxGain / Variable.snr(iSnr);
+    for iNoise = 1 : length(Variable.noisePower)
+        % * Get average noise power
+        noisePower = Variable.noisePower(iNoise);
 
         % * Alternating optimization
-        [reSample{iChannel, iSnr}, reSolution{iChannel, iSnr}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+        [reSample{iChannel, iNoise}, reSolution{iChannel, iNoise}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 
 % * Average over channel realizations
-reInstance = cell(1, length(Variable.snr));
-for iSnr = 1 : length(Variable.snr)
-    reInstance{iSnr} = mean(cat(3, reSample{:, iSnr}), 3);
+reInstance = cell(1, length(Variable.noisePower));
+for iNoise = 1 : length(Variable.noisePower)
+    reInstance{iNoise} = mean(cat(3, reSample{:, iNoise}), 3);
 end
 
 % * Save batch data
[…]

### 2020-09-09 main.tex
:pencil: Tikz plots

@@
 
-\input{info.tex}
 \input{packages.tex}
 
-\graphicspath{{assets/}}
-
 \begin{document}
-
-% \input{cover.tex}
 
@@
 		\def\svgwidth{\columnwidth}
-		\input{assets/system.pdf_tex}
+		\import{assets/}{system.pdf_tex}
 		\caption{An IRS-aided OFDM SWIPT system}
@@
 \begin{section}{Performance Evaluations}
-	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups.
-Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}.
-As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line that is parallel to the AP-user path.
+	\begin{figure}
+		\centering
+		\def\svgwidth{\columnwidth}
+		\import{assets/}{layout.pdf_tex}
+		\caption{System layout}
+		\label{fi:layout}
+	\end{figure}
+	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare average R-E regions under typical setups.
+Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with reference bandwidth $B=1$ \si{MHz}.
+As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path.
 Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$.
@@
 For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}.
-Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the reference path loss of direct, incident and reflective links are $L_D=-61.16$ \si{\dB}, $L_I=-44.03$ \si{\dB} and $L_R=-59.17$ \si{\dB}, respectively.
-Taps are modelled as i.i.d.
-CSCG random variables with normalized total power, and we assume no spatial correlation across all arrays.
+Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d.
+CSCG random variables with normalized total power.
+We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands.
 We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.
-For the algorithm, the tolerance is $\epsilon=10^{-8}$ and the number of candidates in the Gaussian randomization method is $Q=10^{3}$.
+For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations.
+In the R-E boundary curve, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize $z$.
+On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only.
 
@@
 		\centering
-		\def\svgwidth{\columnwidth}
-		\input{assets/layout.pdf_tex}
-		\caption{System layout}
-		\label{fi:layout}
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_subband.tex}
+		\end{adjustbox}
+		\caption{Average R-E region versus the number of subbands}
+		\label{fi:subband}
 	\end{figure}

### 2020-09-11 src/plot/plot_los.m
:construction: Fix typo

@@ -32,4 +32,4 @@ ylabel('Average output DC current [\muA]');
 xlim([0 inf]);
 ylim([0 inf]);
 savefig('../figures/re_los.fig');
-matlab2tikz('../figures/re_irs.tex');
+matlab2tikz('../figures/re_los.tex');

### 2020-09-15 assets/waveform_subband.tex
:bento: Update figures

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.5413547897652\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	1.17726395475229\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.339248611366759\\
2	2.51030400792355\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.223894740731443\\
2	1.02080999862228\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0454113496416176\\
2	0.0749432241788367\\
3	0.174436784198804\\
4	1.28942850163426\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.596937403868726\\
2	0.757813025699412\\
3	0.93101405396448\\
4	1.34495281524672\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00380240006943849\\
2	0.00503538441019884\\
3	0.00673935788269168\\
4	0.00928493526066052\\
5	0.0137641701895959\\
6	0.0224279293816095\\
7	0.0491218000319466\\
8	0.236399650887243\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.57240069726828\\
2	0.707532355159161\\
3	0.813056816207979\\
4	0.908886023167598\\
5	0.981885468475696\\
6	1.04528299395164\\
7	1.09956151160637\\
8	1.1844120256085\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00113001858729917\\
2	0.00128319910359356\\
3	0.00145615657965543\\
4	0.00165374633344438\\
5	0.00187706123944821\\
6	0.00215590582737282\\
7	0.00249082687044019\\
8	0.00291806514852023\\
9	0.00347094235515533\\
10	0.00420624059995467\\
11	0.00519447041447467\\
12	0.00655192372378942\\
13	0.00843364500565299\\
14	0.0114362629486765\\
15	0.0171822844859615\\
16	0.0313917536030629\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.407704437098618\\
2	0.463687310263386\\
3	0.512310122105\\
4	0.556819078359945\\
5	0.597811034393655\\
6	0.633731204224058\\
7	0.66976207094552\\
8	0.70029218188591\\
9	0.730728208302655\\
10	0.756260014823004\\
11	0.78063608646419\\
12	0.800901192040989\\
13	0.818115628024539\\
14	0.831455258593228\\
15	0.841240065783435\\
16	0.848873422011028\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2020-09-15 main.tex
:construction: Fix typo
:pencil: R-E region vs number of subbands

@@
 A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ (with $i_s$ the reverse bias saturation current, $n'$ the diode ideality factor, $v_t$ the thermal voltage) around a quiescent operating point $v_d=a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i,i=1,\dots,\infty$.
-Note that this small signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
+Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
 Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}.
@@
 				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
-				& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\\
+				& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\label{eq:y_I4}\\
 				\mathcal{A}\left\{y_{P}^2(t)\right\}
-				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\\
+				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\label{eq:y_P2}\\
 				\mathcal{A}\left\{y_{P}^4(t)\right\}
@@
 					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{I,n}^2+s_{P,n}^2)\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{I,{n_j}} \right)\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{P,{n_j}} \right)\\
 					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 s_{I,{n_1}}^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{P,{n_2}}^2 \right)
@@
 	\end{figure}
-	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare average R-E regions under typical setups.
-Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with reference bandwidth $B=1$ \si{MHz}.
+	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups.
+Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}.
 As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path.
@@
 Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d.
-CSCG random variables with normalized total power.
+random variables with normalized total power.
 We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays.
@@
 For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations.
-In the R-E boundary curve, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize $z$.
+In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
 On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only.
+For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.
 
@@
 		\caption{Average R-E region versus the number of subbands}
-		\label{fi:subband}
+		\label{fi:re_subband}
 	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/waveform_subband.tex}
+		\end{adjustbox}
+		\caption{Sorted waveform amplitude versus the number of subbands}
+		\label{fi:waveform_subband}
+	\end{figure}
+
+	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+The reason is that although each subband receives a smaller proportion of the total power, it introduces more balanced terms contributing to the output DC current.
+The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
+However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
 \end{section}

### 2020-09-15 src/plot/plot_subband.m
:chart_with_upwards_trend: Time sharing

@@ -30,12 +30,26 @@ save('../data/re_subband.mat');
 
 %% * R-E plots
 figure('name', 'R-E region vs number of subbands');
-legendString = cell(1, length(Variable.nSubbands));
+legendString = cell(1, length(Variable.nSubbands) + 2);
 for iSubband = 1 : length(Variable.nSubbands)
     plot(reSubband{iSubband}(1, :) / Variable.nSubbands(iSubband), 1e6 * reSubband{iSubband}(2, :));
-    legendString{iSubband} = sprintf('$N = %d$', Variable.nSubbands(iSubband));
-    hold on;
+    legendString{iSubband} = sprintf('PS: $N = %d$', Variable.nSubbands(iSubband));
+	hold on;
 end
+
+% * Optimal strategy for medium number of subbands (TS + PS)
+subbandIndex = 4;
+optIndex = convhull(transpose([0, reSubband{subbandIndex}(1, :) / Variable.nSubbands(subbandIndex); 0, 1e6 * reSubband{subbandIndex}(2, :)])) - 1;
+optIndex = optIndex(2 : end - 1);
+plot(reSubband{subbandIndex}(1, optIndex) / Variable.nSubbands(subbandIndex), 1e6 * reSubband{subbandIndex}(2, optIndex), 'r-.');
+legendString{iSubband + 1} = sprintf('TS + PS: $N = %d$', Variable.nSubbands(subbandIndex));
+hold on;
+
+% * Optimal strategy for large number of subbands (TS)
+subbandIndex = 5;
+plot([reSubband{subbandIndex}(1, end) / Variable.nSubbands(subbandIndex), reSubband{subbandIndex}(1, 1) / Variable.nSubbands(subbandIndex)], [1e6 * reSubband{iSubband}(2, end), 1e6 * reSubband{iSubband}(2, 1)], 'k--');
+legendString{iSubband + 2} = sprintf('TS: $N = %d$', Variable.nSubbands(subbandIndex));
+
 hold off;
 grid on;
 legend(legendString);

### 2020-09-15 main.tex
:pencil: R-E region vs number of subbands

@@
 	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-The reason is that although each subband receives a smaller proportion of the total power, it introduces more balanced terms contributing to the output DC current.
+\textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}.
 The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
+\textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
+This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e.
+a time sharing between the WPT point and the tangent WIPT point obtained by power splitting.
+Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.
 \end{section}

### 2020-09-16 src/plot/plot_pathloss.m
:sparkles: Path loss vs distance

@@ -1,0 +1,44 @@
+clear; clc; close all;
+
+% number of distance samples
+nSamples = 1e2;
+% AP-user distance
+directDistance = 15;
+% vertical distance from the IRS to the AP-user path
+verticalDistance = 2;
+% projection of AP-IRS distance to the AP-user path
+horizontalDistance = linspace(0, directDistance, nSamples);
+
+% AP-IRS pathloss
+incidentPathloss = zeros(nSamples, 1);
+% production of AP-IRS and IRS-user pathloss
+extraPathloss = zeros(nSamples, 1);
+for iSample = 1 : nSamples
+	% AP-IRS and IRS-user distance
+	[incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance(iSample));
+	incidentPathloss(iSample) = path_loss(incidentDistance);
+	extraPathloss(iSample) = path_loss(incidentDistance) * path_loss(reflectiveDistance);
+end
+
+%% * Waveform amplitude
+figure('name', 'Path loss vs AP-IRS horizontal distance');
+pathlossPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
+
+% * Incident pathloss
+nexttile;
+semilogy(horizontalDistance, incidentPathloss);
+grid on;
+legend('IEEE TGn D')
+xlabel('Distance [m]');
+ylabel('Path loss');
+
+% * Extra pathloss
+nexttile;
+semilogy(horizontalDistance, extraPathloss);
+grid on;
+legend('$\Lambda_I\Lambda_R$', 'location', 'se')
+xlabel('AP-IRS horizontal distance [m]');
+ylabel('Path loss product');
+
+savefig('../figures/path_loss.fig');
+matlab2tikz('../../assets/path_loss.tex');

### 2020-09-16 main.tex
:pencil: Path loss vs distance

@@
 \begin{section}{System Model}
-	As shown in Figure \ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
+	As shown in Fig.
+\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
 Suppose a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$).
@@
 Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}.
-As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path.
+As shown in Fig.
+\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path.
 Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$.
-Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths.
+Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths, such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
 We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}.
-For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}.
+For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and we regard all channels as NLoS unless otherwise mentioned.
 Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d.
@@
 
-	Figure \ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+	Fig.
+\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
 \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
 The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}.
-The result also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+Waveform amplitude in Fig.
+\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
@@
 Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_distance.tex}
+		\end{adjustbox}
+		\caption{Average R-E region versus AP-IRS horizontal distance}
+		\label{fi:re_distance}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/path_loss.tex}
+		\end{adjustbox}
+		\caption{Path loss versus distance}
+		\label{fi:path_loss}
+	\end{figure}
+
+	In Fig.
+\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
+A \textit{first} observation is that placing the IRS closer to either the AP or the user would improve the R-E tradeoff.
+This origins from the exponential path loss model, where the signal attenuation increases fast at a short range and experiences marginal effect when transmission distance is long.
+As shown in Fig.
+\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large $d$ (greater than 10 \si{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup.
+On the other hand, the result suggests that developing an IRS near the AP can effectively extend the operation range of SWIPT systems.
+Considering the passive characteristic of IRS, opportunities are that it can be directly controlled and powered by the SWIPT network.
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_reflector.tex}
+		\end{adjustbox}
+		\caption{Average R-E region versus the number of reflectors}
+		\label{fi:re_reflector}
+	\end{figure}
+
+	The impact of number of reflectors $L$ on the average R-E region is revealed in Fig. \ref{fi:re_reflector}.
 \end{section}

### 2020-09-16 src/plot/plot_reflector.m
:chart_with_upwards_trend: Better plots

@@ -23,7 +23,7 @@ figure('name', 'R-E region vs number of reflectors');
 legendString = cell(1, length(Variable.nReflectors));
 for iReflector = 1 : length(Variable.nReflectors)
     plot(reReflector{iReflector}(1, :) / nSubbands, 1e6 * reReflector{iReflector}(2, :));
-    legendString{iReflector} = sprintf('$L = %d$', Variable.nReflectors(iReflector));
+    legendString{iReflector} = sprintf('$M = %d, L = %d$', nTxs, Variable.nReflectors(iReflector));
     hold on;
 end
 hold off;

### 2020-09-16 src/plot/plot_tx.m

@@ -23,7 +23,7 @@ figure('name', 'R-E region vs number of transmit antennas');
 legendString = cell(1, length(Variable.nTxs));
 for iTx = 1 : length(Variable.nTxs)
     plot(reTx{iTx}(1, :) / nSubbands, 1e6 * reTx{iTx}(2, :));
-    legendString{iTx} = sprintf('$M = %d$', Variable.nTxs(iTx));
+    legendString{iTx} = sprintf('$M = %d, L = %d$', Variable.nTxs(iTx), nReflectors);
     hold on;
 end
 hold off;

### 2020-09-16 main.tex
:pencil: R-E region vs number of transmit antennas and IRS elements

@@
 		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_noise.tex}
+		\end{adjustbox}
+		\caption{Average R-E region versus the average noise power}
+		\label{fi:re_noise}
+	\end{figure}
+
+	The influence of the average noise power on the average R-E region is investigated in Fig.
+\ref{fi:re_noise}.
+For a sufficiently large $N$, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+As a result, TS is preferred at low SNR while PS is preferred at high SNR.
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
 			\input{assets/re_distance.tex}
@@
 As shown in Fig.
-\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large $d$ (greater than 10 \si{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup.
+\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than 10 \si{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup.
 On the other hand, the result suggests that developing an IRS near the AP can effectively extend the operation range of SWIPT systems.
-Considering the passive characteristic of IRS, opportunities are that it can be directly controlled and powered by the SWIPT network.
+Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network.
+A \textit{second} observation is that there exists two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$.
+It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
 
@@
 
-	The impact of number of reflectors $L$ on the average R-E region is revealed in Fig. \ref{fi:re_reflector}.
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_tx.tex}
+		\end{adjustbox}
+		\caption{Average R-E region versus the number of transmit antennas}
+		\label{fi:re_tx}
+	\end{figure}
+
+	The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.
+\ref{fi:re_reflector} and \ref{fi:re_tx}.
+A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the amount remains unchanged.
+Therefore, we conclude that number of transmit antennas and reflectors has negligible influence on the waveform preference and transmission strategy.
+A \textit{second} contrast suggests that the system performance is more sensitive to the variation of $M$ than $L$.
+Interestingly, the active MRT beamformer only has a transmit array gain of $M$, while the IRS collects $L$ signal copies with a receive array gain $L$ then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
+However, the system in our setup is dominated by the direct link.
+As shown in Fig.
+\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of $10^{-7}$ while the extra path loss product $\Lambda_I\Lambda_R$ is below $10^{-10}$.
+This has the consequence that despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
+
+	% TODO: FF channels in IRS plot
 \end{section}

### 2020-09-18 main.tex
:pencil: Add plots
:construction: Change noise unit to dBm

@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBm} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands.
 We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.
@@
 
+	% N increase -> more to balance, tradeoff between subbands
+	% FF channel -> closed form optimal IRS; FS channel -> tradeoff between subbands
+
 	\begin{figure}
@@
 \ref{fi:re_noise}.
-For a sufficiently large $N$, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+It is noted that for a large number of subbands ($N=16$ in this case), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+Moreover, there exists a
+
+	% This is because
+
 	As a result, TS is preferred at low SNR while PS is preferred at high SNR.
+
+	% sections -> waterfilling: \rho only vs joint
+
+	% irs, low noise power, high received power  L+->high snr, rho vs other L, M: snr and nonlinearity
+	% frequency selective less multipath loss less with FF IRS
+	% Fix subband rate
 
@@
 
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_los.tex}
+		\end{adjustbox}
+		\caption{Average R-E region for IRS-aided NLoS and LoS channels}
+		\label{fi:re_los}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\begin{adjustbox}{width=\linewidth}
+			\input{assets/re_irs.tex}
+		\end{adjustbox}
+		\caption{Average R-E region for adaptive, fixed and no IRS over $B = 10$ \si{\MHz}}
+		\label{fi:re_irs}
+	\end{figure}
+
 	% TODO: FF channels in IRS plot

### 2020-09-18 src/plot/plot_noise.m

@@ -24,7 +24,7 @@ legendString = cell(1, length(Variable.noisePower));
 plotHandle = gobjects(1, length(Variable.noisePower));
 for iNoise = 1 : length(Variable.noisePower)
     plotHandle(iNoise) = plot(reNoise{iNoise}(1, :) / nSubbands, 1e6 * reNoise{iNoise}(2, :));
-    legendString{iNoise} = sprintf('$\\sigma_n = %d$ dB', pow2db(Variable.noisePower(iNoise)));
+    legendString{iNoise} = sprintf('$\\sigma_n = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
     hold on;
 end
 hold off;

### 2020-09-21 src/plot/plot_noise.m
:sparkles: R-E region vs splitting ratio

@@ -1,12 +1,20 @@
 clear; clc; close all; config_noise;
 
 %% * Load batch data
+indexSet = 1 : nSamples;
 reSet = cell(nBatches, length(Variable.noisePower));
+powerRatio = zeros(nBatches, length(Variable.noisePower), nSamples);
 for iBatch = 1 : nBatches
     try
-        load(sprintf('../data/re_noise/re_noise_%d.mat', iBatch), 'reInstance');
+        load(sprintf('../data/re_noise/re_noise_%d.mat', iBatch), 'reInstance', 'reSolution');
         reSet(iBatch, :) = reInstance;
-    catch
+		for iNoise = 1 : length(Variable.noisePower)
+			for iSample = 1 : nSamples
+				powerRatio(iBatch, iNoise, iSample) = reSolution{iNoise}{iSample}.powerRatio;
+			end
+		end
+	catch
+		indexSet(indexSet == iBatch) = [];
         disp(iBatch);
     end
 end
@@ -14,12 +22,17 @@ end
 %% * Average over batches
 reNoise = cell(1, length(Variable.noisePower));
 for iNoise = 1 : length(Variable.noisePower)
-    reNoise{iNoise} = mean(cat(3, reSet{:, iNoise}), 3);
+    reNoise{iNoise} = mean(cat(3, reSet{indexSet, iNoise}), 3);
 end
+powerRatio = permute(mean(powerRatio(indexSet, :, :), 1), [2 3 1]);
 save('../data/re_noise.mat');
 
-%% * R-E plots
-figure('name', 'R-E region vs average noise power');
+%% * R-E and splitting ratio plots
+figure('name', 'R-E region and power splitting ratio vs average noise power');
+tiledlayout(2, 1, 'tilespacing', 'compact');
+
+% * R-E region
+nexttile;
 legendString = cell(1, length(Variable.noisePower));
 plotHandle = gobjects(1, length(Variable.noisePower));
 for iNoise = 1 : length(Variable.noisePower)
@@ -34,7 +47,22 @@ xlabel('Per-subband rate [bps/Hz]');
 ylabel('Average output DC current [$\mu$A]');
 xlim([0 inf]);
 ylim([0 inf]);
-
 apply_style(plotHandle);
+
+% * Power splitting ratio
+nexttile;
+plotHandle = gobjects(1, length(Variable.noisePower));
[…]

### 2020-09-21 assets/waveform_subband.tex
:pencil: Update plots

@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.5413547897652\\
+1	2.82172700814\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	1.17726395475229\\
+1	0.000304871216171409\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.339248611366759\\
-2	2.51030400792355\\
+1	0.576053130269644\\
+2	2.6890198112766\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.223894740731443\\
-2	1.02080999862228\\
+1	1.10889135894926e-05\\
+2	1.14015388220875e-05\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.0454113496416176\\
-2	0.0749432241788367\\
-3	0.174436784198804\\
-4	1.28942850163426\\
+1	0.0761446438182487\\
+2	0.144982805084864\\
+3	0.296816012849829\\
+4	1.29142363466971\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.596937403868726\\
-2	0.757813025699412\\
-3	0.93101405396448\\
-4	1.34495281524672\\
+1	0.591539833353852\\
+2	0.844757166782542\\
+3	1.03081211044174\\
+4	1.37773181929967\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00380240006943849\\
-2	0.00503538441019884\\
-3	0.00673935788269168\\
-4	0.00928493526066052\\
-5	0.0137641701895959\\
-6	0.0224279293816095\\
-7	0.0491218000319466\\
-8	0.236399650887243\\
+1	0.00614059608939126\\
+2	0.00859401448595302\\
+3	0.0123833441665029\\
+4	0.0177535370500449\\
+5	0.0248195484241391\\
+6	0.0333320835321464\\
+7	0.0439492095749763\\
+8	0.0573484061988145\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.57240069726828\\
-2	0.707532355159161\\
-3	0.813056816207979\\
-4	0.908886023167598\\
-5	0.981885468475696\\
-6	1.04528299395164\\
-7	1.09956151160637\\
-8	1.1844120256085\\
+1	0.609821067440242\\
+2	0.776815349798277\\
+3	0.892920455239222\\
+4	1.00042966171483\\
+5	1.06766801836801\\
+6	1.12407480396652\\
+7	1.16166550988201\\
+8	1.18062831194278\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00113001858729917\\
-2	0.00128319910359356\\
-3	0.00145615657965543\\
-4	0.00165374633344438\\
-5	0.00187706123944821\\
-6	0.00215590582737282\\
-7	0.00249082687044019\\
-8	0.00291806514852023\\
-9	0.00347094235515533\\
-10	0.00420624059995467\\
-11	0.00519447041447467\\
-12	0.00655192372378942\\
-13	0.00843364500565299\\
-14	0.0114362629486765\\
-15	0.0171822844859615\\
-16	0.0313917536030629\\
+1	0.00159254712768886\\
+2	0.00181872147522133\\
+3	0.00209479239275806\\
+4	0.0024296336516978\\
+5	0.00281222668015008\\
+6	0.0032780527552737\\
+7	0.00380135620921339\\
+8	0.00440085046230309\\
+9	0.00504657166225592\\
+10	0.00574247660897721\\
+11	0.00647282890112406\\
+12	0.00732475713633807\\
+13	0.0082485990892498\\
+14	0.00930209758929144\\
+15	0.0104899265041237\\
+16	0.0118432322249022\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.407704437098618\\
-2	0.463687310263386\\
-3	0.512310122105\\
-4	0.556819078359945\\
-5	0.597811034393655\\
-6	0.633731204224058\\
-7	0.66976207094552\\
-8	0.70029218188591\\
-9	0.730728208302655\\
-10	0.756260014823004\\
-11	0.78063608646419\\
-12	0.800901192040989\\
-13	0.818115628024539\\
-14	0.831455258593228\\
-15	0.841240065783435\\
-16	0.848873422011028\\
+1	0.42719183467558\\
+2	0.489608181929718\\
+3	0.544499613736105\\
+4	0.589949743468663\\
+5	0.629246929549485\\
+6	0.662163410085189\\
+7	0.692512510794905\\
+8	0.716054914758183\\
+9	0.740934812846251\\
+10	0.761383578308525\\
+11	0.780212428748497\\
+12	0.795813406680176\\
+13	0.808442539661251\\
+14	0.818197413331254\\
+15	0.824534054395175\\
+16	0.827852614702225\\
 };

### 2020-09-21 main.tex
:pencil: R-E region and splitting ratio vs noise

@@
 		\begin{maxi!}
-			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+			{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
 			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
@@
 Therefore, even if we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
-In Section [TODO], we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
+In Section \ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
 
@@
 
-\begin{section}{Performance Evaluations}
+\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
 	\begin{figure}
@@
 For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.
+
+	We first evaluate the performance of Algorithm \ref{al:irs} under SDR.
+It is demonstrated that $\boldsymbol{\Theta}^{\star}$ is rank-1 for all tested channel realizations with different $M$, $N$ and $L$.
+Therefore, $\boldsymbol{\theta}^{\star}$ can be directly obtained through eigenvalue decomposition and we claim Algorithm \ref{al:irs} converges to stationary points of problem \ref{op:irs} without performance loss.
 
@@
 
-	% N increase -> more to balance, tradeoff between subbands
-	% FF channel -> closed form optimal IRS; FS channel -> tradeoff between subbands
-
 	\begin{figure}
@@
 		\end{adjustbox}
-		\caption{Average R-E region versus the average noise power}
+		\caption{Average R-E region and splitting ratio versus the average noise power}
 		\label{fi:re_noise}
@@
 \ref{fi:re_noise}.
-It is noted that for a large number of subbands ($N=16$ in this case), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
-Moreover, there exists a
-
-	% This is because
-
-	As a result, TS is preferred at low SNR while PS is preferred at high SNR.
-
-	% sections -> waterfilling: \rho only vs joint
-
-	% irs, low noise power, high received power  L+->high snr, rho vs other L, M: snr and nonlinearity
-	% frequency selective less multipath loss less with FF IRS
-	% Fix subband rate
+We \textit{first} note that for a large number of subbands ($N=16$), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+Hence, TS is preferred at low SNR while PS is preferred at high SNR.
+This is because at a low SNR, the capacity-achieving Water-Filling (WF) algorithm tends to allocate more power to few strongest subbands.
+As the rate constraint $\bar{R}$ decreases, more subbands are activated such that the rectifier nonlinearity further boosts the harvested energy by introducing more balanced terms to the output DC current.
+\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40$ \si{\dBm}).
+The reason is that when $\bar{R}$ decreases slightly from the capacity, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, since a small amplitude could be inefficient for energy maximization.
+On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a composed waveform with a smaller $\rho$, due to advantage the of multisine.
+The result highlights the necessity of joint optimization of waveform and splitting ratio.
 
@@
 		\begin{adjustbox}{width=\linewidth}
-			\input{assets/re_los.tex}
-		\end{adjustbox}
-		\caption{Average R-E region for IRS-aided NLoS and LoS channels}
-		\label{fi:re_los}
-	\end{figure}
-
-	\begin{figure}
-		\centering
-		\begin{adjustbox}{width=\linewidth}
 			\input{assets/re_irs.tex}
@@
 
-	% TODO: FF channels in IRS plot
+	% Same reflection coefficient, When b small, even if n large, behaves as if ff
+	% FF channel -> closed form optimal IRS; FS channel -> tradeoff between subbands
+	% \textit{Third}, although each IRS element has the same reflection coefficient for $N$ subbands, increasing $N$ does not necessarily mean
+	% frequency selective less multipath loss less with FF IRS
+
 \end{section}

### 2020-09-22 main.tex
:pencil: Adaptive, ideal, fixed IRS

@@
 		\end{adjustbox}
-		\caption{Average R-E region for adaptive, fixed and no IRS over $B = 10$ \si{\MHz}}
+		\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B = 10$ \si{\MHz}}
 		\label{fi:re_irs}
@@
 
-	% Same reflection coefficient, When b small, even if n large, behaves as if ff
-	% FF channel -> closed form optimal IRS; FS channel -> tradeoff between subbands
-	% \textit{Third}, although each IRS element has the same reflection coefficient for $N$ subbands, increasing $N$ does not necessarily mean
-	% frequency selective less multipath loss less with FF IRS
-
+	Fig.
+\ref{fi:re_irs} and \ref{fi:re_irs} explore the average R-E region under different IRS configuration for narrowband ($B=1$ \si{\MHz}) and broadband transmission ($B=10$ \si{\MHz}).
+The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary.
+In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
+To gain some insight into the IRS behavior, we compare the results to that of no IRS and the ideal frequency-selective IRS, where the reflection coefficients of each element are assumed independent and adjustable over all subbands such that the IRS has a total DoF of $NL$.
+Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS IRS element in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely $\theta_{l,n}=e^{j2\pi\angle{(h_{D,n}/(h_{I,n,l}h_{R,n,l}))}}$.
+\textit{First}, it is observed that deploying an IRS around the AP effectively enlarges the achievable R-E region in both cases.
+This is because the IRS tweaks the weak extra channels such that they add constructively to enhance the composite channel.
+\textit{Second}, the performance gap among the adaptive, ideal and fixed IRS is negligible for narrowband transmission but obvious for broadband transmission.
+The reason is that when $B=1$ \si{\MHz}, all channels are approximately flat and the reflection coefficients of FS IRS would be the same for all subbands.
+In such cases, the IRS boils down to maximize a single term denoting the channel response at all subbands such that the adaptive, WIT-optimized and WPT-optimized IRS coincide with each other.
+On the other hand, the channel frequency selectivity becomes significant for $B=10$ \si{\MHz}, and the ideal FS IRS outperforms the others as it requires no tradeoff among subchannels.
+Note that the tradeoff for practical IRS indeed origins from frequency selectivity rather than number of subbands.
+Therefore, for narrowband SWIPT, the optimal IRS can be approximated by any candidate that roughly align the AP-IRS-user with the AP-user channels simultaneously over all subbands.
+Moreover, the WIT-optimized IRS tends to balance the channel strength for all subbands due to the preference of WF strategy at high SNR.
+In comparison, the WPT-optimized IRS is less likely to enhance few weakest subchannels when their amplitude is too small due to its inefficiency for energy harvesting.
+Hence, the adaptive IRS outperforms both fixed IRS.
 \end{section}

### 2020-09-23 main.tex
:pencil: Update styles

@@
-\documentclass{IEEEtran}
+\documentclass[journal]{IEEEtran}
 
@@
 
+\title{IRS-aided SWIPT: Joint waveform, active and passive beamforming design}
+\author{Yang Zhao, Bruno Clerckx}
+
+\maketitle
+
 \begin{abstract}
-	Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the low power level of the receive Radio-Frequency (RF) signal.
-To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain to compensate the propagation loss and boost the energy efficiency with a low power consumption.
-This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
-We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the phase shifts at the IRS, and the splitting ratio at the user.
-The problem is formulated as current maximization problem subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively.
-Numerical results demonstrated that dedicated power signal is beneficial to multicarrier SWIPT, while IRS brings significant R-E region enlargement over benchmark schemes when properly configured.
+	Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the low power level of the received Radio-Frequency (RF) signal.
+To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain.
+This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
+We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+The proposed adaptive waveform and beamforming design is compared with the cases of no IRS, fixed and ideal frequency-selective (FS) IRS.
+We confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
+Simulation results also demonstrate that IRS brings significant R-E enhancement over benchmark schemes when properly configured, and the optimal IRS for narrowband transmission can be approximated in the closed form with negligible performance loss.
 \end{abstract}
+
+\begin{IEEEkeywords}
+	Wireless information and power transfer, intelligent reflecting surface, waveform design, active and passive beamforming.
+\end{IEEEkeywords}
 
@@
 
-		\begin{figure}[h]
+		\begin{figure}
+			\begin{minipage}[b]{0.5\linewidth}
 				\centering
-			\begin{subfigure}[t]{0.45\linewidth}
-				\centering
-				\begin{circuitikz}[scale=0.7, transform shape]
+				\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
+					\resizebox{\linewidth}{!}{
+						\begin{circuitikz}[transform shape]
 							\draw (0,0) to [sV=$v_s$] (0,2);
@@
 						\end{circuitikz}
-				\caption{Antenna equivalent circuit}
-				\label{ci:antenna_equivalent_circuit}
-			\end{subfigure}%
-			~
-			\begin{subfigure}[t]{0.45\linewidth}
+					}
+				}
+			\end{minipage}%
+			\begin{minipage}[b]{0.5\linewidth}
 				\centering
-				\begin{circuitikz}[scale=0.7, transform shape]
+				\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
+					\resizebox{\linewidth}{!}{
+						\begin{circuitikz}[transform shape]
 							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
-					\draw (0,2) to [short] (0.5,2);
-					\draw (0.5,2) to [D, v<=$v_d$, i=$i_d$] (2.5,2);
-					\draw (2.5,2) to [short, -*] (3,2);
-					\draw (3,2) to [C, l_=$C$, -*] (3,0);
-					\draw (3,2) to [short] (4.5,2);
-					\draw (4.5,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4.5,0);
-					\draw (4.5,0) to [short] (2.25,0) node[ground](GND){};
-					\draw (2.25,0) to [short] (0,0);
+							\draw (0,2) to [short] (0.25,2);
+							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
+							\draw (2.25,2) to [short, -*] (2.5,2);
+							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
+							\draw (2.5,2) to [short] (4,2);
+							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
+							\draw (4,0) to [short] (2,0) node[ground](GND){};
+							\draw (2,0) to [short] (0,0);
 						\end{circuitikz}
-				\caption{A single diode rectifier}
-				\label{ci:single_diode_rectifier}
-			\end{subfigure}
+					}
+				}
+			\end{minipage}
 			\caption{Rectenna circuits}
@@
 To gain some insight into the IRS behavior, we compare the results to that of no IRS and the ideal frequency-selective IRS, where the reflection coefficients of each element are assumed independent and adjustable over all subbands such that the IRS has a total DoF of $NL$.
-Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS IRS element in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely $\theta_{l,n}=e^{j2\pi\angle{(h_{D,n}/(h_{I,n,l}h_{R,n,l}))}}$.
+Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS IRS element in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely $\theta_{l,n}^{\star}=e^{j2\pi\angle{(h_{D,n}/(h_{I,n,l}h_{R,n,l}))}}$.
 \textit{First}, it is observed that deploying an IRS around the AP effectively enlarges the achievable R-E region in both cases.

### 2020-09-24 main.tex
:art: Update styles
:pencil: Improve introduction

@@
 		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-		With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply.
+			\IEEEPARstart{W}{ith} the great advance in communication performance, the main challenge of wireless network has come to energy supply.
 Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks.
@@
 Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
-It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner.
+It provides low power in \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}.
 The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
@@
 Information and power beamforming was then considered in multiuser Multi-Input Single-Output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
-Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems.
-However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm.
+Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, scheduling schemes, and interference management for SWIPT systems.
+However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level.
+The authors also suggested a curve-fitting based parametric harvester model and proposed an iterative resource allocation algorithm.
 From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
-\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current under rate constraints.
+\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and performed waveform design accordingly.
 Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
-The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region.
+The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is employed to enlarge the R-E region.
 In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
-By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adapted conventional modulation schemes to ensure WPT is only activated at the points with large offset.
-Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin.
-It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity.
+Modulation and coding schemes for SWIPT are also becoming popular.
+By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability.
+It suggested that WPT should be activated only at constellation points with large offset.
+Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the optimal information symbols are symmetrically distributed around the origin.
+It confirmed that the superposed waveform is effective to enlarge R-E region when considering rectifier nonlinearity.
 SWIPT was also explored in the network design.
 \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user.
-In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
+SWIPT based on Rate Splitting (RS) technique was also explored in \cite{Mao2019}.
 		\end{subsection}
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-		Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency.
+			Intelligent Reflecting Surface (IRS) adapts the wireless channel to increase spectrum and energy efficiency.
 In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
-Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal.
-Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, since more reflectors boost the power collected by IRS and increase the array gain in its equal gain transmission.
+Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics with no flexibility \cite{Anwar2018}.
 
-		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
+			Inspired by the advance of real-time reconfigurable metamaterials in \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
 At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage.
@@
 By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB).
+Its application to interference cancellation and secure communication are also investigated in \cite{Zhou2020,Cui2019}.
 Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
-
-		Most existing papers assume a Frequency-Flat (FF) IRS where all elements reflect different frequencies equally.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is prohibitive since active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics and unable to adjust channel adaptively \cite{Anwar2018}.
 		\end{subsection}
@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Based on linear harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
+Assuming harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
 The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power on the assumption of perfect energy interference cancellation.
-\cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated and a single energy stream can satisfy the energy constraints of all ERs.
-In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms.
-However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
+\cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated thus a single energy stream can satisfy the energy constraints of all ERs.
+In \cite{Pan2019a}, the authors proposed low-complexity BCD algorithms to maximize the Weighted Sum-Rate (WSR) of Information Receivers (IRs) subject to the power constraint at Energy Receivers (ERs).
+However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated IRs and ERs based on an oversimplified linear harvester model.
 		\end{subsection}
@@
 		\begin{subsection}{Objective and Methodology}
-		In this paper, we study an IRS-aided broadband downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
+			In this paper, we study an IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
 A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g.
-OFDM) to boost the energy transfer efficiency without introducing additional interference.
+OFDM) to boost the energy transfer efficiency without creating additional interference.
 The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
-Different from previous research, this paper focus on broadband SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design.
-We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints.
+Different from previous research, this paper focus on multicarrier SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design.
+The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints.
 To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) technique.
 Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations.
-We demonstrate that dedicated power waveform boosts the energy transmission efficiency, such that TS and PS are preferred for low-rate and high-rate applications respectively.
-Also, IRS brings a significant channel amplification thus R-E enhancement especially when located near the transmitter/receiver, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
+We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR.
+Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed near the transmitter or the receiver.
+Finally, the proposed adaptive IRS design outperformed the benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form for narrowband transmission.
 		\end{subsection}
@@
 
-	\begin{figure}
+		\begin{figure}[!t]
 			\centering
@@
 
-		\begin{figure}
+			\begin{figure}[!t]
 				\begin{minipage}[b]{0.5\linewidth}
@@
 The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:irs}.
-		\begin{algorithm}
+			\begin{figure}[!t]
+				\forcealgorithm
+				\begin{algorithm}[H]
 					\caption{SCA: IRS Phase Shift}
@@
 				\end{algorithm}
+			\end{figure}
 		\end{subsection}
@@
 It is also known as a inner approximation algorithm that only provides a KKT solution \cite{Marks1978}.
-		\begin{algorithm}
+			\begin{figure}[!t]
+				\begin{algorithm}[H]
+					\forcealgorithm
 					\caption{GP: Waveform and Splitting Ratio}
@@
 The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
-		\begin{algorithm}
+			\begin{figure}[!t]
+				\begin{algorithm}[H]
+					\forcealgorithm
 					\caption{Alternating Algorithm for Problem \ref{op:original}}
@@
 	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
-	\begin{figure}
+		\begin{figure}[!t]
 			\centering

### 2020-09-25 main.tex
:pencil: Organization and notations

@@
 Finally, the proposed adaptive IRS design outperformed the benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form for narrowband transmission.
+
+			\textit{Organization:} The rest of this paper is organized as follows.
+Section \ref{se:system_model} introduces the signal, channel, decoder, harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
+Section \ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
+Section \ref{se:performance_evaluation} presents simulation results to evaluate the proposed design.
+Section [TODO] concludes the paper.
+
+			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters.
+$\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices.
+$\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively.
+$(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively.
+$\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity).
+For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal.
+For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank.
+For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
+The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ where $\sim$ stands for "distributed as".
+We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and variable value at iteration $i$, respectively.
 		\end{subsection}
@@
 
-	\begin{section}{System Model}
+	\begin{section}{System Model}\label{se:system_model}
 		As shown in Fig.
@@
 
-	\begin{section}{Problem Formulation}
+	\begin{section}{Problem Formulation}\label{se:problem_formulation}
 		We characterize the R-E region through multiple current maximization problems subject to transmit power, IRS magnitude, and different rate constraints

### 2020-09-26 main.tex
:pencil: Update system model and problem formulation

@@
 	\begin{abstract}
-		Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the low power level of the received Radio-Frequency (RF) signal.
+		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal.
 To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain.
-This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
+This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
 We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
-The proposed adaptive waveform and beamforming design is compared with the cases of no IRS, fixed and ideal frequency-selective (FS) IRS.
-We confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
-Simulation results also demonstrate that IRS brings significant R-E enhancement over benchmark schemes when properly configured, and the optimal IRS for narrowband transmission can be approximated in the closed form with negligible performance loss.
+The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
+Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
 	\end{abstract}
@@
 			\IEEEPARstart{W}{ith} the great advance in communication performance, the main challenge of wireless network has come to energy supply.
-Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks.
+Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost thus restricts the scale of networks.
 Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range.
@@
 It provides low power in \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}.
-The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
+The decreasing trend of electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
 
-			The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels.
+			The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
 Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
@@
 From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
-\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and performed waveform design accordingly.
+\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented waveform design for WPT.
 Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
-The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is employed to enlarge the R-E region.
+The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform was employed to enlarge the R-E region.
 In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
-Modulation and coding schemes for SWIPT are also becoming popular.
+Modulation and coding schemes for SWIPT also receive much attention.
 By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability.
-It suggested that WPT should be activated only at constellation points with large offset.
+It suggested that WPT should be activated only at constellation points with a large offset.
 Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the optimal information symbols are symmetrically distributed around the origin.
 It confirmed that the superposed waveform is effective to enlarge R-E region when considering rectifier nonlinearity.
-SWIPT was also explored in the network design.
-\cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user.
+As for the network design, \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user.
 SWIPT based on Rate Splitting (RS) technique was also explored in \cite{Mao2019}.
@@
 Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics with no flexibility \cite{Anwar2018}.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics thus not adjustable \cite{Anwar2018}.
 
@@
 The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}.
+The application of IRS in interference cancellation and secure communication are also investigated in \cite{Zhou2020,Cui2019}.
 In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off.
@@
 By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB).
-Its application to interference cancellation and secure communication are also investigated in \cite{Zhou2020,Cui2019}.
 Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Assuming harvester model and energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
-The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power on the assumption of perfect energy interference cancellation.
+Supposing energy interference and linear harvester model, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
+The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power with the assumption of perfect energy interference cancellation.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated thus a single energy stream can satisfy the energy constraints of all ERs.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs.
 In \cite{Pan2019a}, the authors proposed low-complexity BCD algorithms to maximize the Weighted Sum-Rate (WSR) of Information Receivers (IRs) subject to the power constraint at Energy Receivers (ERs).
@@
 The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
-Different from previous research, this paper focus on multicarrier SWIPT and investigates the fundamental impact of harvester nonlinearity on IRS design.
+Different from previous research, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on passive beamforming design.
 The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints.
-To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) technique.
+To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
 Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations.
-We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR.
-Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed near the transmitter or the receiver.
+We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
+Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
 Finally, the proposed adaptive IRS design outperformed the benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form for narrowband transmission.
@@
 $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity).
+For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value.
 For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal.
@@
 	\begin{section}{System Model}\label{se:system_model}
-		As shown in Fig.
-\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna transmitter delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal subbands.
-Suppose a total bandwidth $B$ with evenly-spaced subbands centered at frequency $f_n$ ($n=1,\dots,N$).
-Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design.
-A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
-Two practical co-located receiver architectures are compared in terms of R-E region.
-Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design.
-Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
-
 		\begin{figure}[!t]
@@
 
+		As shown in Fig.
+\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
+Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the upper bound of the proposed design.
+A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
+Two practical co-located receiver architectures are compared in terms of R-E region.
+Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
+In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design.
+Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
+We also assume the noise is too small to harvest.
+
 		\begin{subsection}{Transmit Signal}
 			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows a capacity-achieving i.i.d.
-Circular Symmetric Complex Gaussian (CSCG) distribution with zero mean and unit variance $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
+CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
 The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
@@
 On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel.
-On top of this, the total composite channel is formed by adding the IRS-aided extra channel to the AP-user direct channel as
+The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection, and IRS-user reflective channel.
+On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
 			\begin{equation}\label{eq:h_n}
@@
 			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
-Note that the Hermitian transpose in the definition of $\boldsymbol{\phi}$ makes its entries complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
+Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
 		\end{subsection}
@@
 		\begin{subsection}{Information Decoder}
-			A major benefit of the proposed waveform is that the determined power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
+			A major benefit of the superposed waveform is that the determined power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
 			\begin{equation}\label{eq:R}
-				\begin{split}
-					R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho)
-					& = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}\\
-					& = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}
-				\end{split}
+				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
 			\end{equation}
-			where $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$.
+			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$.
 Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
@@
 		\begin{subsection}{Energy Harvester}
-			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}.
-Fig.
-\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
-Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network.
-Assume the voltage across matching network is negligible and the RF-band noise is too small to harvest.
-When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$) with power splitting ratio $\rho$, the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.
-
 			\begin{figure}[!t]
+				\centering
+				\noindent
 				\begin{minipage}[b]{0.5\linewidth}
@@
 					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
-						\resizebox{\linewidth}{!}{
+						\resizebox{0.9\linewidth}{!}{
 							\begin{circuitikz}[transform shape]
@@
 					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
-						\resizebox{\linewidth}{!}{
+						\resizebox{0.9\linewidth}{!}{
 							\begin{circuitikz}[transform shape]
@@
 
-			Rectifiers consist of nonlinear components as diode and capacitor to produce DC and store energy \cite{Hagerty2004,Pinuela2013}.
+			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}.
+Fig.
+\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
+Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across matching network is negligible.
+When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$), the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.
+
+			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Hagerty2004,Pinuela2013}.
 Consider a simplified rectifier in Fig.
-\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with load.
-Denote $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
-A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ (with $i_s$ the reverse bias saturation current, $n'$ the diode ideality factor, $v_t$ the thermal voltage) around a quiescent operating point $v_d=a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i,i=1,\dots,\infty$.
+\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
+A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$.
 Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
@@
 
-			By discarding non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
+			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
 			\begin{equation}\label{eq:i_out}
@@
 
-			With the assumption of evenly spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC components.
+			With the assumption of evenly spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC output.
 However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
@@
 In other words, even terms with $i \ge 4$ account for the nonlinear behavior of the diode.
-For simplicity, we choose $n_0=4$ to investigate fundamental nonlinearity and let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$ can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental nonlinearity.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
 
-			Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$.
-Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries.
-On top of this, $z$ is reduced to \ref{eq:z_expand} with DC terms expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
+			Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$.
+Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries, where the blocks are of size $M \times M$.
+On top of this, $z$ is reduced to \ref{eq:z_expand} and the corresponding DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
 			\begin{figure*}[b]
@@
 					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\label{eq:y_I4}\\
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\label{eq:y_I4}
+				\end{align}
+				\begin{align}
 					\mathcal{A}\left\{y_{P}^2(t)\right\}
@@
 			Define the achievable R-E region as
-			\begin{equation}
-				\begin{split}
+			\begin{align}
 				C_{R_{\text{ID}}-I_{\text{EH}}}(P)
-					&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\\
+				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\nonumber\\
 				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right) \le P\biggr\}
-				\end{split}
-			\end{equation}
-			where $P$ is the average transmit power budget and the coefficient $1/2$ converts the maximum power of sine waves to the average power.
+			\end{align}
+			where $P$ is the average transmit power budget and the coefficient $1/2$ converts the peak power of sine waves to the average power.
 		\end{subsection}
@@
 		\end{maxi!}
-		Problem \ref{op:original} is intricate with coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
-To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.
+		Problem \ref{op:original} is intricate due to coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
+To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
 
@@
 			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
-			\begin{equation}
-				\begin{split}
+			\begin{align}
 				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2
-					& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\\
-					& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\\
-					& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
-					& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
+				& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\nonumber\\
+				& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\nonumber\\
+				& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
 				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
-				\end{split}
-			\end{equation}
+			\end{align}
 			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Similarly, we define $t_{I/P,n}$ ($n=-N+1,\dots,N-1$) as
-			\begin{equation}
-				\begin{split}
+Also, define $t_{I/P,n}$ ($n=-N+1,\dots,N-1$) as
+			\begin{align}
 				t_{I/P,n}
-					& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\\
-					& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\\
-					& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\\
-					& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\\
-					& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\\
+				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\nonumber\\
+				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
 				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
-				\end{split}
-			\end{equation}
-			where $\boldsymbol{h}_D=[\boldsymbol{h}_{D,1}^H,\dots,\boldsymbol{h}_{D,N}^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, the rate and objective expressions \ref{eq:R} and \ref{eq:z_expand} rewrites as \ref{eq:R_irs} and \ref{eq:z_irs}, respectively.
-			\begin{equation}\label{eq:R_irs}
-				R(\boldsymbol{\Phi}) = \sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}
-			\end{equation}
-			\begin{equation}\label{eq:z_irs}
-				\begin{split}
+			\end{align}
+			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+Therefore, the rate and objective expressions rewrite as
+			\begin{align}
+				R(\boldsymbol{\Phi})
+				& = \sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\label{eq:R_irs}\\
 				z(\boldsymbol{\Phi})
-					&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
-					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\\
-					&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
-				\end{split}
-			\end{equation}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\nonumber\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\'
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\label{eq:z_irs}
+			\end{align}
 
-			To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA)-based algorithm that approximate the second-order terms by first-order Taylor expansion.
+			To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA) algorithm that approximate the second-order terms by first-order Taylor expansion.
 Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
@@
 			Problem \ref{op:irs} is not a standard Semidefinite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
-Therefore, even if we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
-In Section \ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
+If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
+Luckily, in Section \ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
+A related version of problem \ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 
-			When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is obtained by Eigenvalue Decomposition (EVD).
+			When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
 Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
@@
 Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:irs}.
+The algorithm for phase shift optimization is summarized in Algorithm \ref{al:irs}.
 			\begin{figure}[!t]
@@
 					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
+						\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
 						\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
-						\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$, $n=-N+1,\dots,N-1$
+						\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$ for $n=-N+1,\dots,N-1$
 						\Repeat
@@
 							\State Compute $z^{(i)}$ by \ref{eq:z_irs}
-						\Until $\lvert (z^{(i)}-z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
 						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
 						\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
-							\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+							\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
 						\Else
-							\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
+							\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
 
@@
 						\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
-						\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+						\State \textbf{output} $\boldsymbol{\phi}^{\star}$
 					\end{algorithmic}
@@
 			\end{equation}
-			That is to say, it is only necessary to determine the amplitudes $s_{I/P,n}$ at different tones for single-user MISO SWIPT, and the original waveform optimization with $2MN$ variables is converted into a power allocation problem with $2N$ nonnegative real variables.
+			That is to say, for single-user MISO SWIPT, it is only necessary to determine the amplitudes $s_{I/P,n}$ at different tones.
+Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
 Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$.
-At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
-With such a beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective expressions \ref{eq:R} and \ref{eq:z_expand} reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}.
+At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective expressions further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}.
 			\begin{equation}\label{eq:R_waveform}
@@
 			\end{figure*}
-			Therefore, \ref{op:original} is reduced to an amplitude optimization problem
+			Therefore, problem \ref{op:original} is reduced to an amplitude optimization issue
 			\begin{maxi!}
@@
 		\end{mini!}
-			It is observed that the denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, and we further express them in a compact form
+			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, and we further rewrite them as
 			\begin{align}
@@
 			where $m_P,m_{I,n}$ are the number of monomials in the corresponding posynomials (obviously $m_{I,n}=2$).
-It is suggested in \cite{Clerckx2018b,Chiang2005} that posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} can be upper bounded by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem \ref{op:waveform_rgp} is equivalent to
+Following \cite{Clerckx2018b,Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem \ref{op:waveform_rgp} reduces to
 			\begin{mini}
@@
 			where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$, $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update, and a feasible choice at iteration $i$ is \cite{Clerckx2018b}
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update.
+As suggested in \cite{Clerckx2018b}, a feasible choice at iteration $i$ is
 			\begin{align}
@@
 			\end{align}
-			$\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence and the GP algorithm is summarized in Algorithm \ref{al:waveform}.
-It is also known as a inner approximation algorithm that only provides a KKT solution \cite{Marks1978}.
+
+			Problem \ref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+$\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
+The GP algorithm is summarized in Algorithm \ref{al:waveform}.
 			\begin{figure}[!t]
@@
 							\State Compute $z^{(i)}$ by \ref{eq:z_waveform}
-						\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+						\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
 						\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and transmit waveform together with receive splitting ratio by Algorithm \ref{al:waveform} until convergence.
+			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and update the transmit waveform with receive splitting ratio by Algorithm \ref{al:waveform} until convergence.
 The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
@@
 					\forcealgorithm
-					\caption{Alternating Algorithm for Problem \ref{op:original}}
+					\caption{AO: waveform, active and passive beamforming}
 					\label{al:alternating}
 					\begin{algorithmic}[1]
-						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,P,\sigma_n,\bar{R},Q,\epsilon$
+						\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
 						\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
@@
 							\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
-							\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $n=1,\dots,N$ by \ref{eq:h_n} and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
+							\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
 							\State Compute $z^{(i)}$ by \ref{eq:z_irs}
-						\Until $\lvert (z^{(i)} - z^{(i-1)}) / z^{(i)} \rvert \le \epsilon$
+						\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
 						\State \textbf{Output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
@@
 
-		\begin{subsection}{Convergence and Complexity}
-			\begin{subsubsection}{Convergence}
+		\begin{subsection}{Convergence}
 			The proposed alternating algorithm iteratively employs SCA-based IRS phase shift Algorithm \ref{al:irs} and GP-based waveform and splitting ratio Algorithm \ref{al:waveform} until convergence.
@@
 Thus, Algorithm \ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$, and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
+To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
 Therefore, Algorithm \ref{al:irs} converges to a stationary point.
@@
 			\end{proof}
-			\end{subsubsection}
 		\end{subsection}
@@
 		\end{figure}
-		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare the average R-E regions under typical setups.
+		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups.
 Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}.

### 2020-09-27 main.tex
:art: Update discussion and style

@@
 
-\input{packages.tex}
+\usepackage{adjustbox}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{array}
+% \usepackage{caption}
+\usepackage{cite}
+\usepackage{environ}
+\usepackage{grffile}
+\usepackage{hyperref}
+\usepackage{import}
+\usepackage{mathtools}
+\usepackage{microtype}
+\usepackage{pgfplots}
+\usepackage{siunitx}
+\usepackage{stfloats}
+\usepackage{url}
+\usepackage{xcolor}
+\usepackage[RPvoltages]{circuitikz}
+\usepackage[T1]{fontenc}
+\usepackage[caption=false,font=footnotesize]{subfig}
+% \usepackage[cmintegrals]{newtxmath}
+\usepackage[short]{optidef}
+
+\interdisplaylinepenalty=2500
+\pgfplotsset{compat=newest}
+\usetikzlibrary{plotmarks}
+\usetikzlibrary{arrows.meta}
+\usepgfplotslibrary{patchplots}
+\newtheorem{proposition}{Proposition}
+\DeclareSIUnit{\belm}{Bm}
+\DeclareSIUnit{\dBm}{\deci\belm}
+\DeclareSIUnit{\beli}{Bi}
+\DeclareSIUnit{\dBi}{\deci\beli}
+
+\makeatletter
+\newcommand{\forcealgorithm}{\let\@latex@error\@gobble}
+\makeatother
 
 \begin{document}
-
 	\title{IRS-aided SWIPT: Joint waveform, active and passive beamforming design}
-	\author{Yang Zhao, Bruno Clerckx}
-
+	\author{
+		\IEEEauthorblockN{
+			Yang~Zhao,~\IEEEmembership{Student~Member,~IEEE,}
+			Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
+			and~Zhenyuan~Feng,~\IEEEmembership{Student~Member,~IEEE}
+		}
+		\thanks{
+			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
+		}
+	}
 	\maketitle
@@
 The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
-Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
+Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for SISO narrowband transmission.
 	\end{abstract}
@@
 Modulation and coding schemes for SWIPT also receive much attention.
-By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability.
+By assuming On-Off-Keying (OOK) where bit \num{1} carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability.
 It suggested that WPT should be activated only at constellation points with a large offset.
@@
 Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
-Finally, the proposed adaptive IRS design outperformed the benchmark schemes for wideband transmission, and the optimal IRS can be approximated in closed form for narrowband transmission.
+Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband SISO transmission.
 
 			\textit{Organization:} The rest of this paper is organized as follows.
-Section \ref{se:system_model} introduces the signal, channel, decoder, harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
-Section \ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
-Section \ref{se:performance_evaluation} presents simulation results to evaluate the proposed design.
-Section [TODO] concludes the paper.
+Section~\ref{se:system_model} introduces the signal, channel, decoder, harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
+Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
+Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design.
+Section~[TODO] concludes the paper.
 
@@
 
-		As shown in Fig.
-\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
+		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
 Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the upper bound of the proposed design.
@@
 			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}.
-Fig.
-\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
+Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
 Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across matching network is negligible.
@@
 			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Hagerty2004,Pinuela2013}.
-Consider a simplified rectifier in Fig.
-\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
 Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
@@
 			\end{align}
-			where $P$ is the average transmit power budget and the coefficient $1/2$ converts the peak power of sine waves to the average power.
+			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
 		\end{subsection}
@@
 		\end{maxi!}
-		Problem \ref{op:original} is intricate due to coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
+		Problem~\ref{op:original} is intricate due to coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
 To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
@@
 				& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\'
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\
 				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\label{eq:z_irs}
@@
 			\end{figure*}
-			Hence, problem \ref{op:original} is transformed to
+			Hence, problem~\ref{op:original} is transformed to
 			\begin{maxi!}
@@
 
-			Problem \ref{op:irs} is not a standard Semidefinite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
-If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}.
-Luckily, in Section \ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
-A related version of problem \ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+			Problem~\ref{op:irs} is not a standard Semidefinite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
+If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem~\ref{op:original}.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations so that the performance loss is insignificant.
+A related version of problem~\ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 
-			When $\boldsymbol{\Phi}^{\star}$ is rank-1, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
+			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
 Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
@@
 Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for phase shift optimization is summarized in Algorithm \ref{al:irs}.
-			\begin{figure}[!t]
-				\forcealgorithm
-				\begin{algorithm}[H]
+The algorithm for phase shift optimization is summarized in Algorithm~\ref{al:irs}.
+			\begin{algorithm}[!t]
 				\caption{SCA: IRS Phase Shift}
@@
 						\State $i \gets i + 1$
-							\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem \ref{op:irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\ref{op:irs}
 						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
@@
 					\EndIf
-						\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$
+					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, construct $\boldsymbol{\phi}^{\star}$
 					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
@@
 			\end{algorithm}
-			\end{figure}
 		\end{subsection}
@@
 			\end{figure*}
-			Therefore, problem \ref{op:original} is reduced to an amplitude optimization issue
+			Therefore, problem~\ref{op:original} is reduced to an amplitude optimization issue
 			\begin{maxi!}
@@
 			\end{maxi!}
-			Since problem \ref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
+			Since problem~\ref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
 			\begin{mini!}
@@
 			where $m_P,m_{I,n}$ are the number of monomials in the corresponding posynomials (obviously $m_{I,n}=2$).
-Following \cite{Clerckx2018b,Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem \ref{op:waveform_rgp} reduces to
+Following \cite{Clerckx2018b,Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
 			\begin{mini}
@@
 
-			Problem \ref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+			Problem~\ref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 $\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
-The GP algorithm is summarized in Algorithm \ref{al:waveform}.
-			\begin{figure}[!t]
-				\begin{algorithm}[H]
-					\forcealgorithm
+The GP algorithm is summarized in Algorithm~\ref{al:waveform}.
+			\begin{algorithm}[!t]
 				\caption{GP: Waveform and Splitting Ratio}
@@
 						\State Update $\{\gamma_{m_P}^{(i)},\gamma_{m_{I,n}}^{(i)}\}$ by \ref{eq:gamma_P}, \ref{eq:gamma_I}
-							\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem \ref{op:waveform_gp}
+						\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem~\ref{op:waveform_gp}
 						\State Compute $z^{(i)}$ by \ref{eq:z_waveform}
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm \ref{al:irs} and update the transmit waveform with receive splitting ratio by Algorithm \ref{al:waveform} until convergence.
-The alternating algorithm is summarized in Algorithm \ref{al:alternating}.
-			\begin{figure}[!t]
-				\begin{algorithm}[H]
-					\forcealgorithm
-					\caption{AO: waveform, active and passive beamforming}
+			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm~\ref{al:irs} and update the transmit waveform with receive splitting ratio by Algorithm~\ref{al:waveform} until convergence.
+The alternating algorithm is summarized in Algorithm~\ref{al:alternating}.
+			\begin{algorithm}[!t]
+				\caption{AO: Waveform, Active and Passive Beamforming}
 				\label{al:alternating}
@@
 						\State $i \gets i + 1$
-							\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm \ref{al:irs}
-							\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm \ref{al:waveform}
+						\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
+						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
 						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
@@
 		\begin{subsection}{Convergence}
-			The proposed alternating algorithm iteratively employs SCA-based IRS phase shift Algorithm \ref{al:irs} and GP-based waveform and splitting ratio Algorithm \ref{al:waveform} until convergence.
+			The proposed alternating algorithm iteratively employs SCA-based IRS phase shift Algorithm~\ref{al:irs} and GP-based waveform and splitting ratio Algorithm~\ref{al:waveform} until convergence.
 
 			\begin{proposition}\label{pr:irs}
-				For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.
+				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:irs}
-				The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
+				The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem~\ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
 Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}.
-Thus, Algorithm \ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
-Therefore, Algorithm \ref{al:irs} converges to a stationary point.
+Thus, Algorithm~\ref{al:irs} is guaranteed to converge.
+To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
+Therefore, Algorithm~\ref{al:irs} converges to a stationary point.
 			\end{proof}
@@
 			\begin{proposition}\label{pr:waveform}
-				For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.
+				For any feasible initial point, the GP-based Algorithm~\ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.
 			\end{proposition}
@@
 			\begin{proposition}\label{pr:ao}
-				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.
+				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\ref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:ao}
-				The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
-Thus, Algorithm \ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
-As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem \ref{op:original}.
+				The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
+Thus, Algorithm~\ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
+As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem~\ref{op:original}.
 			\end{proof}
@@
 		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups.
-Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{\GHz} with reference bandwidth $B=1$ \si{\MHz}.
-As shown in Fig.
-\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path.
-Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$.
-Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths, such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
-We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}.
-For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and we regard all channels as NLoS unless otherwise mentioned.
-Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter}, and taps are modelled as i.i.d.
-random variables with normalized total power.
-We choose number of subbands $N=16$ as reference and assume no spatial correlation across all arrays.
-Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBm} while the reference average noise power is $\sigma_n=-40$ \si{\dBm} at all subbands.
-We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain.
-For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over 200 channel realizations.
+Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$.
+As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively.
+We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$, and choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$.
+The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}.
+Reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
+For NLoS channels, all taps are modelled as i.i.d.
+CSCG random variables.
+For LoS channels, the first tap, whose power is significantly larger, is in circular uniform distribution while the remaining taps are in i.i.d.
+CSCG distribution.
+The average sum-power of all taps is unit such that the multipath response is normalized.
+All channels are regarded as NLoS unless otherwise mentioned.
+We choose number of subbands $N=16$ as reference and assume no spatial correlation across all elements.
+Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
+With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
+We also assume \SI{0}{\dBi} IRS element gain and \SI{0}{\dBi} receive antenna gain.
+For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations.
 In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
-On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with water-filling algorithm allocating all power to modulated waveform only.
+On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only.
 For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.
 
-		We first evaluate the performance of Algorithm \ref{al:irs} under SDR.
-It is demonstrated that $\boldsymbol{\Theta}^{\star}$ is rank-1 for all tested channel realizations with different $M$, $N$ and $L$.
-Therefore, $\boldsymbol{\theta}^{\star}$ can be directly obtained through eigenvalue decomposition and we claim Algorithm \ref{al:irs} converges to stationary points of problem \ref{op:irs} without performance loss.
+		We first evaluate the performance of Algorithm~\ref{al:irs} under SDR.
+It is demonstrated that $\boldsymbol{\Theta}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$.
+Therefore, $\boldsymbol{\theta}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\ref{op:irs} without performance loss.
 
@@
 
-		Fig.
-\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
 \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as demonstrated by the scaling laws in \cite{Clerckx2018b}.
-Waveform amplitude in Fig.
-\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of 2 and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+Waveform amplitude in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
 Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
-However, an excessively large $N$ not only requires high computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
+However, an excessively large $N$ not only increases computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
 \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e.
-a time sharing between the WPT point and the tangent WIPT point obtained by power splitting.
-Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transmission strategy, both heavily depends on $N$.
+a time sharing between the WPT point and the tangent WIPT point obtained by PS.
+Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transceiving strategy, both heavily depends on $N$.
 
@@
 
-		The influence of the average noise power on the average R-E region is investigated in Fig.
-\ref{fi:re_noise}.
+		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}.
 We \textit{first} note that for a large number of subbands ($N=16$), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
 Hence, TS is preferred at low SNR while PS is preferred at high SNR.
-This is because at a low SNR, the capacity-achieving Water-Filling (WF) algorithm tends to allocate more power to few strongest subbands.
-As the rate constraint $\bar{R}$ decreases, more subbands are activated such that the rectifier nonlinearity further boosts the harvested energy by introducing more balanced terms to the output DC current.
-\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40$ \si{\dBm}).
-The reason is that when $\bar{R}$ decreases slightly from the capacity, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, since a small amplitude could be inefficient for energy maximization.
-On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a composed waveform with a smaller $\rho$, due to advantage the of multisine.
+This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands.
+As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested energy via the coupling effect by rectifier nonlinearity.
+\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$).
+The reason is that when $\bar{R}$ departs slightly from the capacity, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, since a small amplitude could be inefficient for energy maximization.
+On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine.
 The result highlights the necessity of joint optimization of waveform and splitting ratio.
@@
 
-		In Fig.
-\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
+		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
 A \textit{first} observation is that placing the IRS closer to either the AP or the user would improve the R-E tradeoff.
-This origins from the exponential path loss model, where the signal attenuation increases fast at a short range and experiences marginal effect when transmission distance is long.
-As shown in Fig.
-\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than 10 \si{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup.
-On the other hand, the result suggests that developing an IRS near the AP can effectively extend the operation range of SWIPT systems.
+This origins from the product-distance path loss model that applies to finite-size element reflection.
+As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance.
+On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems.
 Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network.
@@
 
-		The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.
-\ref{fi:re_reflector} and \ref{fi:re_tx}.
+		The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.~\ref{fi:re_reflector} and \ref{fi:re_tx}.
 A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
 This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the amount remains unchanged.
-Therefore, we conclude that number of transmit antennas and reflectors has negligible influence on the waveform preference and transmission strategy.
-A \textit{second} contrast suggests that the system performance is more sensitive to the variation of $M$ than $L$.
-Interestingly, the active MRT beamformer only has a transmit array gain of $M$, while the IRS collects $L$ signal copies with a receive array gain $L$ then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
-However, the system in our setup is dominated by the direct link.
-As shown in Fig.
-\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of $10^{-7}$ while the extra path loss product $\Lambda_I\Lambda_R$ is below $10^{-10}$.
+Therefore, we conclude that number of transmit antennas and reflectors have basically no influence on the waveform preference and transceiving strategy.
+A \textit{second} contrast suggests that the system performance is more sensitive to the variation of $M$, compared with $L$.
+Interestingly, the active MRT beamformer only has a transmit array gain of $M$.
+In contrast, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
+However, the system performance in our setup is dominated by the direct link.
+As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
 This has the consequence that despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B = 10$ \si{\MHz}}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$}
 			\label{fi:re_irs}
@@
 
-		Fig.
-\ref{fi:re_irs} and \ref{fi:re_irs} explore the average R-E region under different IRS configuration for narrowband ($B=1$ \si{\MHz}) and broadband transmission ($B=10$ \si{\MHz}).
+		Fig.~\ref{fi:re_irs} and [TODO] explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
 The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary.
 In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results to that of no IRS and the ideal frequency-selective IRS, where the reflection coefficients of each element are assumed independent and adjustable over all subbands such that the IRS has a total DoF of $NL$.
-Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS IRS element in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely $\theta_{l,n}^{\star}=e^{j2\pi\angle{(h_{D,n}/(h_{I,n,l}h_{R,n,l}))}}$.
-\textit{First}, it is observed that deploying an IRS around the AP effectively enlarges the achievable R-E region in both cases.
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has independent and adjustable reflection coefficients over all subbands such that the ideal IRS has a total DoF of $NL$.
+Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS reflector in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+		\begin{equation}
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}
+		\end{equation}
+		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases.
 This is because the IRS tweaks the weak extra channels such that they add constructively to enhance the composite channel.
-\textit{Second}, the performance gap among the adaptive, ideal and fixed IRS is negligible for narrowband transmission but obvious for broadband transmission.
-The reason is that when $B=1$ \si{\MHz}, all channels are approximately flat and the reflection coefficients of FS IRS would be the same for all subbands.
-In such cases, the IRS boils down to maximize a single term denoting the channel response at all subbands such that the adaptive, WIT-optimized and WPT-optimized IRS coincide with each other.
-On the other hand, the channel frequency selectivity becomes significant for $B=10$ \si{\MHz}, and the ideal FS IRS outperforms the others as it requires no tradeoff among subchannels.
+\textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission.
+The reason is that when $B=1\,\si{\MHz}$, all channels are approximately flat and the response of all subbands are roughly the same.
+In such cases, the additional DoF provided by the frequency selectivity of the ideal IRS would be unnecessary as the the optimal reflection coefficients of each element would almost align at all subbands.
+Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term representing the composite channel response at all subbands.
+Therefore, all IRS strategies coincide with each other, and the optimal IRS for narrowband SISO SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
+On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff among subchannels.
+Moreover, the WIT-optimized IRS tends to equalize the channel strength for all subbands as possible, due to the preference of WF strategy at high SNR.
+In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting.
+Therefore, the adaptive IRS design is more suitable for broadband SWIPT.
 Note that the tradeoff for practical IRS indeed origins from frequency selectivity rather than number of subbands.
-Therefore, for narrowband SWIPT, the optimal IRS can be approximated by any candidate that roughly align the AP-IRS-user with the AP-user channels simultaneously over all subbands.
-Moreover, the WIT-optimized IRS tends to balance the channel strength for all subbands due to the preference of WF strategy at high SNR.
-In comparison, the WPT-optimized IRS is less likely to enhance few weakest subchannels when their amplitude is too small due to its inefficiency for energy harvesting.
-Hence, the adaptive IRS outperforms both fixed IRS.
 	\end{section}
@@
 	\bibliographystyle{IEEEtran}
-	\bibliography{library.bib}
+	\bibliography{IEEEabrv,library.bib}
 \end{document}

### 2020-09-28 src/lib/tap_tgn.m
:ambulance: Fix LoS and NLoS tap gains

@@ -15,7 +15,7 @@ function [tapGain, tapDelay] = tap_tgn(corTx, corRx, propagationMode)
     %   - for single-user MIMO, consider spatial correlation
     %   - use power delay profile and path loss of IEEE TGn channel model D
     %   - for each tap, the LoS component is fixed while the NLoS component consists of spatially correlated variables
-    %   - LoS Ricean factor only apply to the first LoS tap, the remaining taps use NLoS Ricean factor
+    %   - Ricean factor varies for  LoS and NLoS conditions
     %   - LoS matrix entries are unit-modulus
     %
     % Reference:
@@ -34,8 +34,8 @@ function [tapGain, tapDelay] = tap_tgn(corTx, corRx, propagationMode)
     tapPower(1, :) = db2pow([0 -0.9 -1.7 -2.6 -3.5 -4.3 -5.2 -6.1 -6.9 -7.8 -9.0 -11.1 -13.7 -16.3 -19.3 -23.2 -inf -inf]);
     tapPower(2, :) = db2pow([-inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -6.6 -9.5 -12.1 -14.7 -17.4 -21.9 -25.5 -inf]);
     tapPower(3, :) = db2pow([-inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -inf -18.8 -23.2 -25.2 -26.7]);
-    losRiceanFactor = db2pow(3);
-    nlosRiceanFactor = db2pow(-inf);
+	losRiceanFactor = [db2pow(3), db2pow(repmat(-inf, [1, nTaps - 1]))];
+	nlosRiceanFactor = db2pow(repmat(-inf, [1, nTaps]));
 
     % * Generate LoS matrix
     losMatrix = exp(1i * 2 * pi * rand(nRxs, nTxs));
@@ -45,15 +45,16 @@ function [tapGain, tapDelay] = tap_tgn(corTx, corRx, propagationMode)
     nlosGain = zeros(nClusters, nTaps, nRxs, nTxs);
     tapGain = zeros(nClusters, nTaps, nRxs, nTxs);
     for iCluster = 1 : nClusters
-        for iTap = 1 : nTaps
-            if iTap == 1 && propagationMode == "los"
[…]

### 2020-09-28 src/re_los.m

@@ -13,8 +13,8 @@ for iChannel = 1 : nChannels
     [incidentNlosTapGain, incidentTapDelay] = tap_tgn(corTx, corIrs, 'nlos');
     [reflectiveNlosTapGain, reflectiveTapDelay] = tap_tgn(corIrs, corRx, 'nlos');
 
-    [incidentLosTapGain, ~] = tap_tgn(corTx, corIrs, 'nlos');
-    [reflectiveLosTapGain, ~] = tap_tgn(corIrs, corRx, 'nlos');
+    [incidentLosTapGain, ~] = tap_tgn(corTx, corIrs, 'los');
+    [reflectiveLosTapGain, ~] = tap_tgn(corIrs, corRx, 'los');
 
     % * Construct channels
     [directNlosChannel] = frequency_response(directNlosTapGain, directTapDelay, directDistance, rxGain, subbandFrequency, fadingMode);

### 2020-10-03 main.tex
:ambulance: Fix LoS and NLoS tap gains
:pencil: Add plots

@@
 \begin{document}
-	\title{IRS-aided SWIPT: Joint waveform, active and passive beamforming design}
+	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
 	\author{
@@
 			\begin{equation}\label{eq:i_out}
-				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}
+				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}
 			\end{equation}
@@
 						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
-
 						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
@@
 			\begin{adjustbox}{width=\linewidth}
-				\input{assets/re_irs.tex}
+				\input{assets/re_irs_1mhz.tex}
+			\end{adjustbox}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$}
+			\label{fi:re_irs_1mhz}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\begin{adjustbox}{width=\linewidth}
+				\input{assets/re_irs_10mhz.tex}
 			\end{adjustbox}
 			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$}
-			\label{fi:re_irs}
+			\label{fi:re_irs_10mhz}
 		\end{figure}
 
-		Fig.~\ref{fi:re_irs} and [TODO] explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
 The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary.

### 2020-10-04 main.tex
:art: Fix equations

@@
 
-			With the assumption of evenly spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC output.
+			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC output.
 However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
@@
 				R(\boldsymbol{\Phi})
-				& = \sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\label{eq:R_irs}\\
+				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\label{eq:R_irs}\\
 				z(\boldsymbol{\Phi})
@@
 Following \cite{Clerckx2018b,Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
-			\begin{mini}
+			\begin{mini!}
 				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
@@
 				\addConstraint{\rho + \bar{\rho} \le 1}
-			\end{mini}
+			\end{mini!}
 			where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$, $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.

### 2020-10-04 main.tex
:pencil: Add discussion

@@
 All channels are regarded as NLoS unless otherwise mentioned.
-We choose number of subbands $N=16$ as reference and assume no spatial correlation across all elements.
+We choose number of transmit antennas $M=1$, number of reflectors $L=20$, number of subbands $N=16$ as reference, and assume no spatial correlation across all elements.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
 With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
-We also assume \SI{0}{\dBi} IRS element gain and \SI{0}{\dBi} receive antenna gain.
+We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain.
 For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations.
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that placing the IRS closer to either the AP or the user would improve the R-E tradeoff.
-This origins from the product-distance path loss model that applies to finite-size element reflection.
+A \textit{first} observation is that, different from the active relay that prefers the middle point, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+It origins from the product-distance path loss model that applies to finite-size element reflection.
 As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance.

### 2020-10-06 main.tex
:triangular_flag_on_post: Create backup

@@
 		\IEEEauthorblockN{
-			Yang~Zhao,~\IEEEmembership{Student~Member,~IEEE,}
-			Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
-			and~Zhenyuan~Feng,~\IEEEmembership{Student~Member,~IEEE}
+			Yang~Zhao,~\IEEEmembership{Member,~IEEE}
+			and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
 		}
@@
 The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
-Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for SISO narrowband transmission.
+Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
 	\end{abstract}

### 2020-10-06 main.tex
:art: Rephrase abstract

@@
 This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
-We aim to maximize the Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
-The performance of the proposed waveform and beamforming design is compared with those of no IRS, fixed IRS and ideal frequency-selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH) while the optimal transceiving strategy depends on the system configuration.
-Simulation results also demonstrate that the proposed adaptive IRS design brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
+We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform, active beamforming at the AP, and passive beamforming at the IRS.
+The performance of the proposed design is compared with those of no IRS, non-adaptive IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH).
+It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
+Simulation results demonstrate that the adaptive IRS design leads to significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
 	\end{abstract}
@@
 		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-			\IEEEPARstart{W}{ith} the great advance in communication performance, the main challenge of wireless network has come to energy supply.
-Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost thus restricts the scale of networks.
-Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range.
+			\IEEEPARstart{W}{ith} the great advance in communication performance, the bottleneck of wireless networks is coming to energy supply.
+Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks.
+Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range.
 Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
-It provides low power in \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}.
-The decreasing trend of electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.
+It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
+Meantime, the reduction in electronics power consumption and the explosion of mobile devices also call for a paradigm shift from dedicated information and power sources to SWIPT.
 
-			The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
+			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
 Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.

### 2020-10-08 main.tex
:art: Rephrase literature review

@@
 Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Ng2018}, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
+It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Clerckx2018a}, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
 Meantime, the reduction in electronics power consumption and the explosion of mobile devices also call for a paradigm shift from dedicated information and power sources to SWIPT.
@@
 			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
-On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup.
-Information and power beamforming was then considered in multiuser Multi-Input Single-Output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}.
-Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, scheduling schemes, and interference management for SWIPT systems.
-However, \cite{Boshkovska2015} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level.
-The authors also suggested a curve-fitting based parametric harvester model and proposed an iterative resource allocation algorithm.
-From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency.
-\cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented waveform design for WPT.
-Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}.
-The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform was employed to enlarge the R-E region.
-In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications.
-Modulation and coding schemes for SWIPT also receive much attention.
-By assuming On-Off-Keying (OOK) where bit \num{1} carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate versus battery overflow/underflow probability.
-It suggested that WPT should be activated only at constellation points with a large offset.
-Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the optimal information symbols are symmetrically distributed around the origin.
-It confirmed that the superposed waveform is effective to enlarge R-E region when considering rectifier nonlinearity.
-As for the network design, \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user.
-SWIPT based on Rate Splitting (RS) technique was also explored in \cite{Mao2019}.
+Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
+Dedicated information and energy beamforming were then introduced in \cite{Zhang2013} to characterize the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system.
+From the perspective of Wireless Power Transfer (WPT), \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level.
+The authors recommended waveforms with large Peak-to-Average Power Ratio (PAPR), such as multisine, to improve the power efficiency and system coverage.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics.
+Simulation and experiments demonstrated the benefit of modeling harvester nonlinearity on WPT system design \cite{Kim2019,Kim2019a}.
+On the other hand, \cite{Clerckx2018b} proposed a waveform design for SWIPT where a multisine power component was superposed to a modulated information component to enlarge the R-E region.
 		\end{subsection}
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) adapts the wireless channel to increase spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
+			Intelligent Reflecting Surface (IRS) adjusts the wireless channel to increase spectrum and energy efficiency.
+In practice, an IRS consists of multiple individual reflecting elements that modify the amplitude and phase of the incident signal through passive beamforming.
 Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006,Xu2014} while passive FSS has fixed physical characteristics thus not adjustable \cite{Anwar2018}.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.
 
-			Inspired by the advance of real-time reconfigurable metamaterials in \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
-At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage.
-Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR).
-The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}.
-The application of IRS in interference cancellation and secure communication are also investigated in \cite{Zhou2020,Cui2019}.
-In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off.
-Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
-Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency-Division Multiplexing (OFDM) systems.
-\cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient.
-On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}.
-By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB).
-Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
+			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
+Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
+The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}.
+Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.	In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off.
+To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient.
+Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems.
+For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs).
+In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency \cite{Dai2020}.
 		\end{subsection}
@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-Supposing energy interference and linear harvester model, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints.
-The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power with the assumption of perfect energy interference cancellation.
+It was argued in \cite{Wu2019b} that dedicated energy beam is not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system, which is power-inefficient and may cause interference.
+On the other hand, \cite{Tang2019} suggested that if the interference from energy signals can be cancelled, multiple energy beams are generally required for the max-min harvested power problem.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power, as the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs.
-In \cite{Pan2019a}, the authors proposed low-complexity BCD algorithms to maximize the Weighted Sum-Rate (WSR) of Information Receivers (IRs) subject to the power constraint at Energy Receivers (ERs).
-However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated IRs and ERs based on an oversimplified linear harvester model.
+It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated.
+In such cases, a single energy stream can satisfy the energy constraints of all energy receivers.
+			% However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated information and energy receivers based on an oversimplified linear harvester model.
 		\end{subsection}
@@
 			\textit{Organization:} The rest of this paper is organized as follows.
-Section~\ref{se:system_model} introduces the signal, channel, decoder, harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
+Section~\ref{se:system_model} introduces the signal, channel, information decoder, energy harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
 Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
@@
 For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
-The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ where $\sim$ stands for "distributed as".
-We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and variable value at iteration $i$, respectively.
+The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean vector $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ and $\sim$ stands for "distributed as".
+We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
 		\end{subsection}

### 2020-10-08 main.tex
:art: Rephrase problem formulation

@@
 For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs).
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency \cite{Dai2020}.
+In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
 		\end{subsection}
@@
 			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters.
+$j$ refers to the imaginary unit.
 $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices.
@@
 		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
-Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the upper bound of the proposed design.
+Perfect Channel State Information (CSI) of all channels are assumed at the AP.
 A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
@@
 Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
-We also assume the noise is too small to harvest.
+We also assume the noise power is too small to be harvested.
 
 		\begin{subsection}{Transmit Signal}
-			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows a capacity-achieving i.i.d.
+			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows an i.i.d.
 CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
@@
 			\end{equation}
-			where $w_{I/P,n,m}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$.
+			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$.
 Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas.
@@
 			\begin{align}
-				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_I}\\
-				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
+				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
+				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
 			\end{align}
@@
 			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
-On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$.
-The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection, and IRS-user reflective channel.
-On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
+The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
+Hence, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
 			\begin{equation}\label{eq:h_n}
@@
 		\begin{subsection}{Receive Signal}
-			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution of information and power components over $N$ subbands, where
-			\begin{align}\label{eq:y_IP}
-				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
-				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
+			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution from information and power components over $N$ subbands, where
+			\begin{align}
+				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
+				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
 			\end{align}
@@
 		\begin{subsection}{Information Decoder}
-			A major benefit of the superposed waveform is that the determined power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
+			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
 			\begin{equation}\label{eq:R}
@@
 			\begin{equation}\label{eq:i_d}
-				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i
+				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
 			\end{equation}
-
 			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
 			\begin{equation}\label{eq:i_out}
-				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}
+				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
 			\end{equation}
-
-			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms has no contribution to DC output.
+			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output.
 However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
@@
 It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$.
-However, due to the coupling among different frequencies, some high-order terms also cancel out non-DC components thus contribute to the output DC power.
-In other words, even terms with $i \ge 4$ account for the nonlinear behavior of the diode.
+However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
+In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode.
 For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental nonlinearity.
 Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+The corresponding $z$ is detailed in \ref{eq:z_expand}.
 
 			Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$.
-Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries, where the blocks are of size $M \times M$.
-On top of this, $z$ is reduced to \ref{eq:z_expand} and the corresponding DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
+Moreover, define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and let $\boldsymbol{W}_{I/P,n}$ keep its $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries, where the blocks are of size $M \times M$.
+On top of this, relevant DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
 			\begin{figure*}[b]
 				\hrule
-				\begin{align}
-					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)
-					& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
+				\begin{equation}
+					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
+				\end{equation}
+				\hrule
+				\begin{flalign}
 					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\label{eq:y_I2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
 					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\label{eq:y_I4}
-				\end{align}
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
+				\end{flalign}
 				\begin{align}
 					\mathcal{A}\left\{y_{P}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\label{eq:y_P2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\,,\label{eq:y_P2}\\
 					\mathcal{A}\left\{y_{P}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\label{eq:y_P4}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\,.\label{eq:y_P4}
 				\end{align}
@@
 		\begin{subsection}{Rate-Energy Region}
-			Define the achievable R-E region as
+			The achievable R-E region is defined as
 			\begin{align}
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize the R-E region through multiple current maximization problems subject to transmit power, IRS magnitude, and different rate constraints
+		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and different rate constraints
 		\begin{maxi!}
@@
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
-			\addConstraint{0 \le \rho \le 1}
+			\addConstraint{0 \le \rho \le 1\,.}
 		\end{maxi!}
-		Problem~\ref{op:original} is intricate due to coupled variables involved in non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate}.
-To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
+		Problem~\ref{op:original} is intricate due to non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate} with coupled variables.
+To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
 
@@
 				R(\boldsymbol{\Phi})
-				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\label{eq:R_irs}\\
+				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\,,\label{eq:R_irs}\\
 				z(\boldsymbol{\Phi})
@@
 				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\label{eq:z_irs}
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\,.\label{eq:z_irs}
 			\end{align}
-
-			To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA) algorithm that approximate the second-order terms by first-order Taylor expansion.
-Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
+			To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA) algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
+Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
 			\begin{align}
 				(t_{I,0}^{(i)})^2
-				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:taylor_1}\\
+				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\,,\label{eq:taylor_1}\\
 				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
-				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\label{eq:taylor_2}\\
+				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\,,\label{eq:taylor_2}\\
 				t_{I,0}^{(i)} t_{P,0}^{(i)}
@@
 			which provide lower bounds to the corresponding terms in \ref{eq:z_irs}.
-At iteration $i$, the approximated objection function $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ is detailed in \ref{eq:z_irs_approx}.
+Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \ref{eq:z_irs_approx}, and problem~\ref{op:original} is transformed to
 			\begin{figure*}[b]
 				\hrule
-				\begin{equation}\label{eq:z_irs_approx}
-					\begin{split}
+				\begin{align}
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-						& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\\
-						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\\
-						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)
-					\end{split}
-				\end{equation}
+					& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}
+				\end{align}
 			\end{figure*}
-			Hence, problem~\ref{op:original} is transformed to
 			\begin{maxi!}
@@
 				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\,.\label{co:irs_rank}}
 			\end{maxi!}
-
-			Problem~\ref{op:irs} is not a standard Semidefinite Programming (SDP) due to the rate constraint \ref{co:irs_rate}.
+			Problem~\ref{op:irs} is not a standard Semidefinite Programming (SDP).
 If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem~\ref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations so that the performance loss is insignificant.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations and the performance loss is insignificant.
 A related version of problem~\ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
@@
 Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The algorithm for phase shift optimization is summarized in Algorithm~\ref{al:irs}.
+The SCA algorithm of phase shift optimization is summarized in Algorithm~\ref{al:irs}.
 			\begin{algorithm}[!t]
@@
 			\begin{equation}\label{eq:w_IP}
-				\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
+				\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}\,.
 			\end{equation}
@@
 At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective expressions further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}, respectively.
 			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_I,\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}\biggr)\right)
+				R(\boldsymbol{s}_I,\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}\biggr)\right)\,.
 			\end{equation}
@@
 				\hrule
-				\begin{equation}\label{eq:z_waveform}
-					\begin{split}
+				\begin{align}
 					z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
-						& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{I,n}^2+s_{P,n}^2)\\
-						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{P,{n_j}} \right)\\
-						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 s_{I,{n_1}}^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{P,{n_2}}^2 \right)
-					\end{split}
-				\end{equation}
+					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{I,n}^2+s_{P,n}^2)\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{P,{n_j}} \right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 s_{I,{n_1}}^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{P,{n_2}}^2 \right)\,.\label{eq:z_waveform}
+				\end{align}
 			\end{figure*}
@@
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right)\le{P}}
-				\addConstraint{R(\boldsymbol{s}_I,\rho) \ge \bar{R}}
+				\addConstraint{R(\boldsymbol{s}_I,\rho) \ge \bar{R}\,.}
 			\end{maxi!}
@@
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
-				\addConstraint{\rho + \bar{\rho} \le 1}
+				\addConstraint{\rho + \bar{\rho} \le 1\,.}
 			\end{mini!}
-			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, and we further rewrite them as
+			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, which is further decomposed as
 			\begin{align}
-				z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\label{eq:posynomial_objective}\\
+				z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\label{eq:posynomial_objective}\,,\\
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}&=\sum_{m_{I,n}}g_{m_{I,n}}(s_{I,n},\bar{\rho})\label{eq:posynomial_rate}
@@
 			where $m_P,m_{I,n}$ are the number of monomials in the corresponding posynomials (obviously $m_{I,n}=2$).
-Following \cite{Clerckx2018b,Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
+Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
 			\begin{mini!}
@@
 			\begin{align}
-				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\\
-				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}/{\sigma_n^2}}\label{eq:gamma_I}
+				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\,,\\
+				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}/{\sigma_n^2}}\,.\label{eq:gamma_I}
 			\end{align}
-
 			Problem~\ref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 $\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
-The GP algorithm is summarized in Algorithm~\ref{al:waveform}.
+The GP algorithm of waveform and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
 			\begin{algorithm}[!t]
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$
+					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
 					\Repeat
@@
 					\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
-					\State \textbf{Output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
+					\State \textbf{output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
 				\end{algorithmic}
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the IRS phase shift by Algorithm~\ref{al:irs} and update the transmit waveform with receive splitting ratio by Algorithm~\ref{al:waveform} until convergence.
-The alternating algorithm is summarized in Algorithm~\ref{al:alternating}.
+			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs} and waveform, active beamforming, splitting ratio by Algorithm~\ref{al:waveform} until convergence.
+The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
 			\begin{algorithm}[!t]
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
+					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
 					\Repeat
@@
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
+					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
 				\end{algorithmic}
@@
 		\begin{subsection}{Convergence}
-			The proposed alternating algorithm iteratively employs SCA-based IRS phase shift Algorithm~\ref{al:irs} and GP-based waveform and splitting ratio Algorithm~\ref{al:waveform} until convergence.
-
 			\begin{proposition}\label{pr:irs}
@@
 All channels are regarded as NLoS unless otherwise mentioned.
-We choose number of transmit antennas $M=1$, number of reflectors $L=20$, number of subbands $N=16$ as reference, and assume no spatial correlation across all elements.
+We choose number of transmit antennas $M=1$, number of reflectors $L=20$, number of subbands $N=16$ as reference, and assume no spatial correlation across active and passive arrays.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
@@
 		We first evaluate the performance of Algorithm~\ref{al:irs} under SDR.
-It is demonstrated that $\boldsymbol{\Theta}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$.
-Therefore, $\boldsymbol{\theta}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\ref{op:irs} without performance loss.
+It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$.
+Therefore, $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\ref{op:irs} without performance loss.
 

### 2020-10-08 src/plot/plot_reflector.m
:fire: Update labels

@@ -26,7 +26,7 @@ legendString = cell(1, length(Variable.nReflectors));
 plotHandle = gobjects(1, length(Variable.nReflectors));
 for iReflector = 1 : length(Variable.nReflectors)
     plotHandle(iReflector) = plot(reReflector{iReflector}(1, :) / nSubbands, 1e6 * reReflector{iReflector}(2, :));
-    legendString{iReflector} = sprintf('$M = %d, L = %d$', nTxs, Variable.nReflectors(iReflector));
+    legendString{iReflector} = sprintf('$L = %d$', Variable.nReflectors(iReflector));
     hold on;
 end
 hold off;

### 2020-10-08 src/plot/plot_tx.m

@@ -26,7 +26,7 @@ legendString = cell(1, length(Variable.nTxs));
 plotHandle = gobjects(1, length(Variable.nTxs));
 for iTx = 1 : length(Variable.nTxs)
     plotHandle(iTx) = plot(reTx{iTx}(1, :) / nSubbands, 1e6 * reTx{iTx}(2, :));
-    legendString{iTx} = sprintf('$M = %d, L = %d$', Variable.nTxs(iTx), nReflectors);
+    legendString{iTx} = sprintf('$M = %d$', Variable.nTxs(iTx));
     hold on;
 end
 hold off;

### 2020-10-08 main.tex
:construction: Rephrase results

@@
 Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
-Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband SISO transmission.
+Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband Single-Input Single-Output (SISO) transmission.
 
@@
 			\import{assets/}{system.pdf_tex}
-			\caption{An IRS-aided OFDM SWIPT system}
+			\caption{An IRS-aided OFDM SWIPT system.}
 			\label{fi:system}
@@
 				\end{minipage}
-				\caption{Rectenna circuits}
+				\caption{Rectenna circuits.}
 			\end{figure}
@@
 			\begin{algorithm}[!t]
-				\caption{SCA: IRS Phase Shift}
+				\caption{SCA: IRS Phase Shift.}
 				\label{al:irs}
@@
 			\begin{algorithm}[!t]
-				\caption{GP: Waveform and Splitting Ratio}
+				\caption{GP: Waveform and Splitting Ratio.}
 				\label{al:waveform}
@@
 			\begin{algorithm}[!t]
-				\caption{AO: Waveform, Active and Passive Beamforming}
+				\caption{AO: Waveform, Active and Passive Beamforming.}
 				\label{al:alternating}
@@
 			\import{assets/}{layout.pdf_tex}
-			\caption{System layout}
+			\caption{System layout in the simulation.}
 			\label{fi:layout}
@@
 CSCG random variables.
-For LoS channels, the first tap, whose power is significantly larger, is in circular uniform distribution while the remaining taps are in i.i.d.
-CSCG distribution.
 The average sum-power of all taps is unit such that the multipath response is normalized.
 All channels are regarded as NLoS unless otherwise mentioned.
-We choose number of transmit antennas $M=1$, number of reflectors $L=20$, number of subbands $N=16$ as reference, and assume no spatial correlation across active and passive arrays.
+We choose reference number of transmit antennas $M=1$, reflectors $L=20$, subbands $N=16$, and assume no spatial correlation across active and passive arrays.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus the number of subbands}
+			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_subband}
@@
 			\end{adjustbox}
-			\caption{Sorted waveform amplitude versus the number of subbands}
+			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:waveform_subband}
@@
 The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
-Waveform amplitude in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
 Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
-However, an excessively large $N$ not only increases computation complexity but also operates out of the small-signal harvester model, thus become prohibitive.
+However, an excessively large $N$ not only increases complexity but also operates out of the small-signal harvester model, thus become prohibitive.
 \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
@@
 			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus the average noise power}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_noise}
@@
 		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}.
-We \textit{first} note that for a large number of subbands ($N=16$), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+We \textit{first} note that for a large number of subbands, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
 Hence, TS is preferred at low SNR while PS is preferred at high SNR.
@@
 \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the capacity, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, since a small amplitude could be inefficient for energy maximization.
+The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, as a small amplitude could be inefficient for energy maximization.
 On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus AP-IRS horizontal distance}
+			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $B=1\,\si{\MHz}$.}
 			\label{fi:re_distance}
@@
 			\end{adjustbox}
-			\caption{Path loss versus distance}
+			\caption{Path loss versus distance for IEEE TGn channel model D.}
 			\label{fi:path_loss}
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that, different from the active relay that prefers the middle point, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+A \textit{first} observation is that, different from the active relay that favors the midpoint development, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
 It origins from the product-distance path loss model that applies to finite-size element reflection.
@@
 Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation is that there exists two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$.
+A \textit{second} observation is that there exist two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$.
 It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus the number of reflectors}
+			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_reflector}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus the number of transmit antennas}
+			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_tx}
@@
 A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the amount remains unchanged.
-Therefore, we conclude that number of transmit antennas and reflectors have basically no influence on the waveform preference and transceiving strategy.
-A \textit{second} contrast suggests that the system performance is more sensitive to the variation of $M$, compared with $L$.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number of components remains unchanged.
+Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy.
+A \textit{second} contrast suggests that active beamforming is more effective than passive beamforming, as the system performance is more sensitive to the variation of $M$ than $L$.
 Interestingly, the active MRT beamformer only has a transmit array gain of $M$.
-In contrast, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
+In comparison, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
 However, the system performance in our setup is dominated by the direct link.
 As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
-This has the consequence that despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
+Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
 
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_irs_1mhz}
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
 			\label{fi:re_irs_10mhz}
@@
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission.
 The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary.
 In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has independent and adjustable reflection coefficients over all subbands such that the ideal IRS has a total DoF of $NL$.
-Since the IRS only adapts the phase of the extra channel, the optimal strategy for each FS reflector in the SISO case would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total Degree of Freedom (DoF) of $NL$.
+Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in SISO systems would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
 		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}\,,\quad \forall n,l\,.
 		\end{equation}
 		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases.
-This is because the IRS tweaks the weak extra channels such that they add constructively to enhance the composite channel.
+This is because IRS creates and adapts the weak extra channels such that they add constructively to enhance the composite channel.
 \textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission.
 The reason is that when $B=1\,\si{\MHz}$, all channels are approximately flat and the response of all subbands are roughly the same.
-In such cases, the additional DoF provided by the frequency selectivity of the ideal IRS would be unnecessary as the the optimal reflection coefficients of each element would almost align at all subbands.
-Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term representing the composite channel response at all subbands.
-Therefore, all IRS strategies coincide with each other, and the optimal IRS for narrowband SISO SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
-On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff among subchannels.
+In such cases, the additional DoF provided by the frequency selectivity of the ideal IRS would be unnecessary, because the the optimal reflection coefficients would almost align at all subbands.
+Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term that represents the composite channel response at all subbands.
+As a consequence, all IRS strategies coincide with each other, and the optimal IRS for narrowband SISO SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
+On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.
 Moreover, the WIT-optimized IRS tends to equalize the channel strength for all subbands as possible, due to the preference of WF strategy at high SNR.

### 2020-10-09 main.tex
:art: Rephrase literature review

@@
 		\IEEEauthorblockN{
-			Yang~Zhao,~\IEEEmembership{Member,~IEEE}
-			and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
+			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
+			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
+			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
 		}
@@
 This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
-We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform, active beamforming at the AP, and passive beamforming at the IRS.
-The performance of the proposed design is compared with those of no IRS, non-adaptive IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH).
+We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH).
 It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results demonstrate that the adaptive IRS design leads to significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
+Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
 	\end{abstract}
@@
 		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-			\IEEEPARstart{W}{ith} the great advance in communication performance, the bottleneck of wireless networks is coming to energy supply.
+			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks comes to energy supply.
 Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks.
@@
 Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Clerckx2018a}, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-Meantime, the reduction in electronics power consumption and the explosion of mobile devices also call for a paradigm shift from dedicated information and power sources to SWIPT.
+It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
+The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, call for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
 
@@
 Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
-Dedicated information and energy beamforming were then introduced in \cite{Zhang2013} to characterize the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system.
-From the perspective of Wireless Power Transfer (WPT), \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level.
-The authors recommended waveforms with large Peak-to-Average Power Ratio (PAPR), such as multisine, to improve the power efficiency and system coverage.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics.
-Simulation and experiments demonstrated the benefit of modeling harvester nonlinearity on WPT system design \cite{Kim2019,Kim2019a}.
-On the other hand, \cite{Clerckx2018b} proposed a waveform design for SWIPT where a multisine power component was superposed to a modulated information component to enlarge the R-E region.
+Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
+			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
+			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
+			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level.
+It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT.
+Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2019a}.
+Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range.
+%Beyond WPT, the work in [10]
+			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely
+			\begin{itemize}
+				\item modulated and unmodulated waveforms are not equally suitable for wireless power delivery;
+				\item a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT;
+				\item combination of power splitting and time sharing is in general the best strategy;
+				\item the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG);
+				\item the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+			\end{itemize}
+			Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
+This question was answered in \cite{Varasteh2017} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019b} for multi-carrier SWIPT.
+The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g.
+modulation and waveform) strategies.
+It is now well understood from \cite{Clerckx2018b,Varasteh2017,Varasteh2019b} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+Recently, \cite{Varasteh2019a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2017} and new modulation schemes were subsequently designed.
 		\end{subsection}
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) adjusts the wireless channel to increase spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual reflecting elements that modify the amplitude and phase of the incident signal through passive beamforming.
+			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency.
+In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
 Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection.
@@
 
-			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
+			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
 Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
 The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}.
-Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.	In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off.
+Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
+In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off.
 To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient.
@@
 In such cases, a single energy stream can satisfy the energy constraints of all energy receivers.
-			% However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated information and energy receivers based on an oversimplified linear harvester model.
+
+			However, most existing IRS-assisted SWIPT papers relied on an oversimplified linear harvester model with focus on single-carrier transmission for separated information and energy receivers.
+Rectifier nonlinearity and co-localized receiver, acknowledged as key to practical and efficient SWIPT system design, have not yet been addressed in the relevant research.
+In this paper, we depart from a tractable harvester model and study an IRS-aided downlink MISO SWIPT system, where the user employs the received signal for both information decoding and energy harvesting.
+The contributions are as follows.
+
+			In this paper, we marry the benefits of joint waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS.
+The contribution of the paper are listed as follows.
+First, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
+This architecture can be seen to IRS-aided SWIPT what [40] is to SWIPT.
+Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission to a single user.
+A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform to boost the energy transfer efficiency.
+The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
+This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
+Note that existing IRS-aided SWIPT papers [36,37,38,39] focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
+On the contrary, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
+Second, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture.
+The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints.
+To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver [Not clear yet what you mean by this, maybe you can be more explicit and say that you optimize alternatively the IRS weights (passive beamforming) and the waveform and active beamforming weights] iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
+[Here I would add one sentence that says: "In contrast to [...], ...
+" to explain how th optimization of IRS-aided SWIPT changes compared to SWIPT].
+Third, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture, and that the proposed algorithm can find a stationary point for all tested channel realizations.
+We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
+Also, IRS is shown to bring a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
+Finally, the proposed adaptive IRS-aided SWIPT architecture and design outperform the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT [This last sentence is not clear to me].
+
+			[For the third contribution, we need to highlight the that the observations for SWIPT carries on to IRS-aided SWIPT, namely blablabla, but also highlight the new observations.]
+
+			\textit{First}, we extend the SWIPT waveform design in \cite{Clerckx2018b} to the IRS case and investigate the passive beamforming issue.
+
+			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency
+
+			We investigate the impact of IRS development on precoder design, waveform preference and transceiving strategy.
+Comparison is made with the no IRS case to highlight the benefit of introducing IRS in SWIPT systems.
+
+			\textit{Second},
+
+			Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that updates the IRS reflection coefficients
+
+			and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
 		\end{subsection}
@@
 			\textit{Organization:} The rest of this paper is organized as follows.
-Section~\ref{se:system_model} introduces the signal, channel, information decoder, energy harvester, and R-E tradeoff models of the IRS-aided SWIPT system.
+Section~\ref{se:system_model} introduces the signal, channel, receiver and R-E tradeoff models of the IRS-aided SWIPT system.
 Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
@@
 For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
-The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean vector $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ and $\sim$ stands for "distributed as".
+The distribution of a random vector consists of Circularly Symmetric Complex Gaussian (CSCG) variables is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$, where $\boldsymbol{\mu}$ is the mean vector and $\boldsymbol{\Sigma}$ is the covariance matrix.
+$\sim$ means "distributed as".
 We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
@@
 		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
-Perfect Channel State Information (CSI) of all channels are assumed at the AP.
+Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design.
 A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
@@
 The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
-Hence, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
+On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
 			\begin{equation}\label{eq:h_n}
@@
 		\end{maxi!}
-		Problem~\ref{op:original} is intricate due to non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate} with coupled variables.
+		Problem~\ref{op:original} is intricate due to the non-convex objective function \ref{ob:original} and the rate constraint \ref{co:original_rate} with coupled variables.
 To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
@@
 Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The SCA algorithm of phase shift optimization is summarized in Algorithm~\ref{al:irs}.
+The SCA algorithm for IRS phase shift optimization is summarized in Algorithm~\ref{al:irs}.
 			\begin{algorithm}[!t]
@@
 As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively.
-We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$, and choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$.
-The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}.
-Reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
-For NLoS channels, all taps are modelled as i.i.d.
-CSCG random variables.
-The average sum-power of all taps is unit such that the multipath response is normalized.
-All channels are regarded as NLoS unless otherwise mentioned.
-We choose reference number of transmit antennas $M=1$, reflectors $L=20$, subbands $N=16$, and assume no spatial correlation across active and passive arrays.
+We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
+Choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$.
+The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
+We assume all channels are NLoS with taps modelled as i.i.d.
+CSCG random variables of unit average sum-power to create a normalized multipath response.
+The reference numbers of transmit antennas, IRS reflectors and subbands are $M=1$, $L=20$, $N=16$, respectively.
+No spatial correlation is considered across transmit antenna and IRS arrays.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
-With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
+With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
 We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain.
@@
 In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total Degree of Freedom (DoF) of $NL$.
-Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in SISO systems would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design flexibility of $NL$.
+Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in the presence of single transmit antenna would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
 		\begin{equation}
@@
 The reason is that when $B=1\,\si{\MHz}$, all channels are approximately flat and the response of all subbands are roughly the same.
-In such cases, the additional DoF provided by the frequency selectivity of the ideal IRS would be unnecessary, because the the optimal reflection coefficients would almost align at all subbands.
+In such cases, the additional design flexibility provided by the frequency selectivity of the ideal IRS would be unnecessary, because the the optimal reflection coefficients would almost align at all subbands.
 Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term that represents the composite channel response at all subbands.
-As a consequence, all IRS strategies coincide with each other, and the optimal IRS for narrowband SISO SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
+As a consequence, all IRS strategies coincide with each other, and the optimal IRS for single transmit antenna narrowband SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
 On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.

### 2020-10-10 main.tex
:ambulance: Fix convergence proof

@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-It was argued in \cite{Wu2019b} that dedicated energy beam is not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system, which is power-inefficient and may cause interference.
-On the other hand, \cite{Tang2019} suggested that if the interference from energy signals can be cancelled, multiple energy beams are generally required for the max-min harvested power problem.
+It was argued in \cite{Wu2019b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
+On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem.
 \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
 It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated.
-In such cases, a single energy stream can satisfy the energy constraints of all energy receivers.
+In such cases, a single energy stream is enough for all energy receivers.
 
-			However, most existing IRS-assisted SWIPT papers relied on an oversimplified linear harvester model with focus on single-carrier transmission for separated information and energy receivers.
+			However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission based on an oversimplified linear harvester model for separated information and energy receivers.
 Rectifier nonlinearity and co-localized receiver, acknowledged as key to practical and efficient SWIPT system design, have not yet been addressed in the relevant research.
-In this paper, we depart from a tractable harvester model and study an IRS-aided downlink MISO SWIPT system, where the user employs the received signal for both information decoding and energy harvesting.
-The contributions are as follows.
-
 In this paper, we marry the benefits of joint waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS.
 The contribution of the paper are listed as follows.
-First, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
-This architecture can be seen to IRS-aided SWIPT what [40] is to SWIPT.
+
+			\textit{First}, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
+This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT.
 Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission to a single user.
@@
 This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-Note that existing IRS-aided SWIPT papers [36,37,38,39] focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
+Note that existing IRS-aided SWIPT papers \cite{Wu2019b,Tang2019,Wu2019c,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
 On the contrary, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
-Second, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture.
+
+			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture.
 The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints.
-To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver [Not clear yet what you mean by this, maybe you can be more explicit and say that you optimize alternatively the IRS weights (passive beamforming) and the waveform and active beamforming weights] iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
-[Here I would add one sentence that says: "In contrast to [...], ...
-" to explain how th optimization of IRS-aided SWIPT changes compared to SWIPT].
-Third, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture, and that the proposed algorithm can find a stationary point for all tested channel realizations.
-We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
+Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS 2) waveform and active beamforming at the transmitter, power splitting ratio at the receiver, until convergence.
+On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner.
+Despite no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
+
+			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture.
+It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT, namely 1)
+
+			dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
 Also, IRS is shown to bring a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
@@
 
-			\textit{First}, we extend the SWIPT waveform design in \cite{Clerckx2018b} to the IRS case and investigate the passive beamforming issue.
-
 			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency
-
-			We investigate the impact of IRS development on precoder design, waveform preference and transceiving strategy.
-Comparison is made with the no IRS case to highlight the benefit of introducing IRS in SWIPT systems.
-
-			\textit{Second},
-
-			Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that updates the IRS reflection coefficients
-
-			and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
 		\end{subsection}
@@
 		Problem~\ref{op:original} is intricate due to the non-convex objective function \ref{ob:original} and the rate constraint \ref{co:original_rate} with coupled variables.
-To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
+To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the phase shift at the IRS, the waveform and active beamforming at the transmitter, and the power splitting ratio at the receiver, until convergence.
 
@@
 			\begin{proposition}\label{pr:irs}
-				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.
+				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} can provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+(Numerical results proved that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations.)
 			\end{proposition}
@@
 To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
-Therefore, Algorithm~\ref{al:irs} converges to a stationary point.
+Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions.
 			\end{proof}

### 2020-10-10 main.tex
:art: Rephrase introduction

@@
 It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
+Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
 	\end{abstract}
@@
 %Beyond WPT, the work in [10]
-			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely
-			\begin{itemize}
-				\item modulated and unmodulated waveforms are not equally suitable for wireless power delivery;
-				\item a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT;
-				\item combination of power splitting and time sharing is in general the best strategy;
-				\item the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG);
-				\item the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
-			\end{itemize}
+			The work was extended to SWIPT in \cite{Clerckx2018b}.
+Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
@@
 The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints.
-Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS 2) waveform and active beamforming at the transmitter, power splitting ratio at the receiver, until convergence.
+Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
 On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner.
@@
 			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture.
-It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT, namely 1)
-
-			dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
-Also, IRS is shown to bring a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
-Finally, the proposed adaptive IRS-aided SWIPT architecture and design outperform the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT [This last sentence is not clear to me].
-
-			[For the third contribution, we need to highlight the that the observations for SWIPT carries on to IRS-aided SWIPT, namely blablabla, but also highlight the new observations.]
-
+It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT.
+For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively.
+Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
+In contrast to the active amplify-and-forward relay whose optimal location is around the midpoint \cite{Li2017}, we observed that the passive IRS should be placed next to either the transmitter or the receiver to further improve the R-E tradeoff, due to the product-distance path loss model.
+It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
+Also, the adaptive IRS design outperformed the fixed (information-optimized, power-optimized) IRS for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
 			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency
-		\end{subsection}
-
-		\begin{subsection}{Objective and Methodology}
-			In this paper, we study an IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
-A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g.
-OFDM) to boost the energy transfer efficiency without creating additional interference.
-The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff.
-Different from previous research, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on passive beamforming design.
-The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints.
-To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
-Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations.
-We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively.
-Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver.
-Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband Single-Input Single-Output (SISO) transmission.
 

### 2020-10-10 main.tex
:pencil: Rephrase discussion and add conclusion

@@
 		\thanks{
-			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
+			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
 		}
@@
 It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
+Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission.
+The adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
 	\end{abstract}
@@
 			The work was extended to SWIPT in \cite{Clerckx2018b}.
-Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
@@
 
-			\textit{First}, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
+			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
 This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT.
-Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission to a single user.
-A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform to boost the energy transfer efficiency.
+Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
+A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency.
 The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
@@
 Note that existing IRS-aided SWIPT papers \cite{Wu2019b,Tang2019,Wu2019c,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
-On the contrary, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
+On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
 
@@
 It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
-Also, the adaptive IRS design outperformed the fixed (information-optimized, power-optimized) IRS for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
-			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency
+Also, the adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
+
+			% single antenna, DoF -> new words. ff irs fs channel not all design flexibility; active antenna -> frequency
 
@@
 A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number of components remains unchanged.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number remains unchanged.
 Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy.
-A \textit{second} contrast suggests that active beamforming is more effective than passive beamforming, as the system performance is more sensitive to the variation of $M$ than $L$.
+A \textit{second} contrast is that the system performance is more sensitive to the variation of $M$ than $L$.
 Interestingly, the active MRT beamformer only has a transmit array gain of $M$.
@@
 Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
+Another explanation is that passive IRS has no design flexibility in the frequency domain (the reflection coefficients are the same for all subbands), while transmit antenna with RF-chains enables weight control over different subbands.
+Therefore, doubling the transmit antenna provides a bigger R-E region than doubling the IRS elements, and we conclude that active beamforming is more effective than passive beamforming.
 
@@
 In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design flexibility of $NL$.
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design design flexibility of $NL$.
 Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in the presence of single transmit antenna would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
@@
 		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases.
-This is because IRS creates and adapts the weak extra channels such that they add constructively to enhance the composite channel.
+This is because IRS creates and adapts the weak extra channels that add constructively to enhance the composite channel.
 \textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission.
-The reason is that when $B=1\,\si{\MHz}$, all channels are approximately flat and the response of all subbands are roughly the same.
-In such cases, the additional design flexibility provided by the frequency selectivity of the ideal IRS would be unnecessary, because the the optimal reflection coefficients would almost align at all subbands.
-Similarly, WIT-optimized and WPT-optimized IRS boil down to optimizing a single term that represents the composite channel response at all subbands.
-As a consequence, all IRS strategies coincide with each other, and the optimal IRS for single transmit antenna narrowband SWIPT can be approximated by any candidate that roughly align the AP-IRS-user channel with the AP-user channel simultaneously over all subbands.
+The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal passive beamforming would almost align at all subbands.
+That is to say, when the bandwidth is small, there is no enough frequency diversity for IRS to manipulate the subchannel strength such that all four IRS strategies coincide with each other.
+It implies that the passive beamforming only need to be optimized once for narrowband SWIPT, and a special case is that the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
 On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.
@@
 In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting.
-Therefore, the adaptive IRS design is more suitable for broadband SWIPT.
-Note that the tradeoff for practical IRS indeed origins from frequency selectivity rather than number of subbands.
+Therefore, adaptive IRS design is required for broadband SWIPT as information and energy receivers have different preference on the subchannel strength distribution.
+	\end{section}
+
+	\begin{section}{Conclusion and Future Works}
+		This paper proposed a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user.
+We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
+Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures.
+Efficient algorithms based on GP, SCA, SDR and AO techniques are proposed to balance the system performance and computational complexity, which are numerically demonstrated to converge to a stationary point of the original problem for all tested channel realizations under different configurations.
+We confirmed that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
+When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
+Compared with active transmit antenna, it has no design flexibility in the frequency domain, but the passive characteristic significantly reduces the power consumption and enables noise-free reflection.
+Finally, adaptive passive beamforming is required for broadband transmission while the IRS only need to be optimized once for narrowband transmission.
+		% For broadband SWIPT, adaptive passive beamforming for different R-E pairs is required, as ID and EH have different preference on the subchannel strength distribution.
+For narrowband SWIPT, the subchannel responses are very similar and the optimal passive beamforming for all R-E points coincide with each other.
+Therefore, the IRS only need to be optimized once.
+		% that brings a quadratic array gain.
+
+		The combination of IRS and SWIPT brings many possibilities and challenges.
+For example, how to optimize waveform, active and passive beamforming in a multiuser SWIPT system?
+How can multiple IRS cooperate with each other to benefit R-E tradeoff?
+How to perform channel estimation without RF-chains at the IRS?
+How to design IRS-aided SWIPT system under different multiple access techniques?
+How to implement IRS in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?
+Can IRS operation be directly supported by SWIPT?
+Answers to these questions may bring a new wireless revolution.
 	\end{section}

### 2020-10-11 main.tex
:art: Rephrase draft

@@
 Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission.
-The adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
+The adaptive passive beamforming design outperformed the benchmarks for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
 	\end{abstract}
@@
 		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks comes to energy supply.
+			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
 Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks.
@@
 			The work was extended to SWIPT in \cite{Clerckx2018b}.
-Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT 3) a combination of power splitting and time sharing is in general the best strategy 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG) 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
@@
 Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
-In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off.
+In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off.
 To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient.
@@
 A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency.
-The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
+The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
 This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
@@
 The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints.
-Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
+Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
 On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner.
@@
 			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture.
-It is demonstrated that the observations for SWIPT carries on to IRS-aided SWIPT.
+It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT.
 For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively.
@@
 Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design.
-Section~[TODO] concludes the paper.
+Section~\ref{se:conclusion_and_future_works} concludes the paper.
 
@@
 For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank.
-For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
+For a square matrix $\boldsymbol{S}$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
 The distribution of a random vector consists of Circularly Symmetric Complex Gaussian (CSCG) variables is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$, where $\boldsymbol{\mu}$ is the mean vector and $\boldsymbol{\Sigma}$ is the covariance matrix.
@@
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design.
+In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design.
 Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
@@
 			\end{equation}
-			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (RF-band and RF-to-baseband conversion) on tone $n$.
+			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$.
 Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
@@
 In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode.
-For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental nonlinearity.
+For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity.
 Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
@@
 		\end{maxi!}
-		Problem~\ref{op:original} is intricate due to the non-convex objective function \ref{ob:original} and the rate constraint \ref{co:original_rate} with coupled variables.
-To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the phase shift at the IRS, the waveform and active beamforming at the transmitter, and the power splitting ratio at the receiver, until convergence.
+		Problem~\ref{op:original} is intricate as the variables are coupled and the objective function \ref{ob:original}, the rate constraint \ref{co:original_rate}, and the IRS magnitude constraint \ref{co:original_modulus} are non-convex.
+To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
 
 		\begin{subsection}{IRS Phase Shift}
-			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
+			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that for $n=1,\dots,N$,
 			\begin{align}
@@
 			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Also, define $t_{I/P,n}$ ($n=-N+1,\dots,N-1$) as
+Also, for $n=-N+1,\dots,N-1$, define $t_{I/P,n}$ as
 			\begin{align}
@@
 			\end{align}
-			To maximize non-concave expression \ref{eq:z_irs}, we propose a Successive Convex Approximation (SCA) algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
+			To maximize non-concave expression \ref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 			Problem~\ref{op:irs} is not a standard Semidefinite Programming (SDP).
-If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem~\ref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations and the performance loss is insignificant.
+If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, and the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\ref{op:original}.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations such that the performance loss by SDR is insignificant.
 A related version of problem~\ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
@@
 Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}.
-Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The SCA algorithm for IRS phase shift optimization is summarized in Algorithm~\ref{al:irs}.
+Finally, the phase shift is retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
+The SCA algorithm for passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
 			\begin{algorithm}[!t]
@@
 					\EndIf
-					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, construct $\boldsymbol{\phi}^{\star}$
+					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, and construct $\boldsymbol{\phi}^{\star}$
 					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
@@
 					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{P,{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 s_{I,{n_1}}^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{P,{n_2}}^2 \right)\,.\label{eq:z_waveform}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{I,{n_1}}^2 s_{P,{n_2}}^2 \right)\,.\label{eq:z_waveform}
 				\end{align}
-			\end{figure*}
+			\end{figure*}%
 			Therefore, problem~\ref{op:original} is reduced to an amplitude optimization issue
@@
 				\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}\label{co:waveform_objective}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
 				\addConstraint{\rho + \bar{\rho} \le 1\,.}
 			\end{mini!}
-			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007}, which is further decomposed as
+			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007} that further decompose as
 			\begin{align}
@@
 			\end{align}
-			where $m_P,m_{I,n}$ are the number of monomials in the corresponding posynomials (obviously $m_{I,n}=2$).
+			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials in the corresponding posynomials.
 Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
@@
 				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\,,\\
-				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}/{\sigma_n^2}}\,.\label{eq:gamma_I}
+				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}\big/{\sigma_n^2}}\,.\label{eq:gamma_I}
 			\end{align}
@@
 $\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
-The GP algorithm of waveform and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
+The GP algorithm of waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
 			\begin{algorithm}[!t]
-				\caption{GP: Waveform and Splitting Ratio.}
+				\caption{GP: Waveform, Active Beamforming and Splitting Ratio.}
 				\label{al:waveform}
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs} and waveform, active beamforming, splitting ratio by Algorithm~\ref{al:waveform} until convergence.
+			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs}, and waveform, active beamforming and splitting ratio by Algorithm~\ref{al:waveform} until convergence.
 The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
@@
 				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} can provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
-(Numerical results proved that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations.)
 			\end{proposition}
@@
 The reference numbers of transmit antennas, IRS reflectors and subbands are $M=1$, $L=20$, $N=16$, respectively.
-No spatial correlation is considered across transmit antenna and IRS arrays.
+No spatial correlation is considered across transmit antennas and IRS arrays.
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
@@
 \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+The reason is that although each subband receives a smaller proportion of the total power, more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine.
-The result highlights the necessity of joint optimization of waveform and splitting ratio.
+The result highlights the benefit of multisine and the necessity of joint optimization of waveform and splitting ratio.
 
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that, different from the active relay that favors the midpoint development, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+A \textit{first} observation is that, different from the active amplify-and-forward relay that achieves optimal performance when developed around the midpoint, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
 It origins from the product-distance path loss model that applies to finite-size element reflection.
@@
 A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the components in \ref{eq:z_expand} is amplified while the number remains unchanged.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the terms in \ref{eq:z_expand} is amplified while the number remains unchanged.
 Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy.
@@
 Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
-Another explanation is that passive IRS has no design flexibility in the frequency domain (the reflection coefficients are the same for all subbands), while transmit antenna with RF-chains enables weight control over different subbands.
+Another explanation is that passive IRS has no design flexibility in the frequency domain and the reflection coefficients are the same for all subbands, while transmit antenna with RF-chains enables weight control over different subbands.
 Therefore, doubling the transmit antenna provides a bigger R-E region than doubling the IRS elements, and we conclude that active beamforming is more effective than passive beamforming.
@@
 		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission.
-The adaptive scheme optimizes the IRS and waveform alternatively for each points in the R-E boundary.
+The adaptive scheme optimizes the IRS, waveform and active beamforming alternatively for each points in the R-E boundary.
 In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where we assume each element has an independent reflection coefficient for each subband such that the ideal IRS has a total design design flexibility of $NL$.
-Since the IRS only control the phase of the concatenated channel, the optimal strategy for each FS reflector in the presence of single transmit antenna would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where each element is assumed to have an independent reflection coefficient for each subband.
+Therefore, the ideal IRS has a total design design flexibility of $NL$.
+Since the IRS only control the phase of the concatenated channel, when there is only one transmit antenna at the AP, the optimal strategy for each FS reflector would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
 		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/(h_{I,n,l}h_{R,n,l})\right)}}\,,\quad \forall n,l\,.
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/h_{I,n,l}h_{R,n,l}\right)}}\,,\quad \forall n,l\,.
 		\end{equation}
-		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region in both cases.
-This is because IRS creates and adapts the weak extra channels that add constructively to enhance the composite channel.
+		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
+This is because IRS creates and controls the weak extra channels for a constructive signal superposition.
 \textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission.
-The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal passive beamforming would almost align at all subbands.
-That is to say, when the bandwidth is small, there is no enough frequency diversity for IRS to manipulate the subchannel strength such that all four IRS strategies coincide with each other.
-It implies that the passive beamforming only need to be optimized once for narrowband SWIPT, and a special case is that the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
+The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal ideal reflection coefficients would almost align at all subbands.
+That is to say, for narrowband transmission, there is no enough diversity and incentive for IRS to manipulate the subchannel strength, and all four IRS strategies coincide with each other.
+It implies that for narrowband SWIPT, the passive beamforming only need to be optimized once to characterize the whole R-E boundary.
+As a special case, the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
 On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.
@@
 
-	\begin{section}{Conclusion and Future Works}
+	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
 		This paper proposed a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user.
@@
 We confirmed that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
-When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
-Compared with active transmit antenna, it has no design flexibility in the frequency domain, but the passive characteristic significantly reduces the power consumption and enables noise-free reflection.
+When developed near the transmitter, IRS can provide effective channel enhancement to expand the operation range and enlarge the R-E region.
+Compared with active transmit antenna, IRS elements has no design flexibility in the frequency domain, but the passive characteristic significantly reduces the power consumption and enables noise-free reflection.
 Finally, adaptive passive beamforming is required for broadband transmission while the IRS only need to be optimized once for narrowband transmission.
@@
 For example, how to optimize waveform, active and passive beamforming in a multiuser SWIPT system?
-How can multiple IRS cooperate with each other to benefit R-E tradeoff?
+How can multiple IRS cooperate with each other to further benefit R-E tradeoff?
 How to perform channel estimation without RF-chains at the IRS?
-How to design IRS-aided SWIPT system under different multiple access techniques?
+How to design IRS-aided SWIPT system for different multiple access techniques?
 How to implement IRS in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?

### 2020-10-11 main.tex
:art: Update reference

@@
 Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT.
-Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2019a}.
+Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2020a}.
 Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range.
@@
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
-This question was answered in \cite{Varasteh2017} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019b} for multi-carrier SWIPT.
+This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
 The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g.
 modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2017,Varasteh2019b} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2019a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2017} and new modulation schemes were subsequently designed.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
 		\end{subsection}
@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-It was argued in \cite{Wu2019b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
+It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
 On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem.
-\cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
+\cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
 It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated.
@@
 This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-Note that existing IRS-aided SWIPT papers \cite{Wu2019b,Tang2019,Wu2019c,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
+Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
 On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
@@
 
-			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Hagerty2004,Pinuela2013}.
+			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
 Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
@@
 Thus, Algorithm~\ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}.
+To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions.
@@
 Thus, Algorithm~\ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
-As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem~\ref{op:original}.
+As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\ref{op:original}.
 			\end{proof}

### 2020-10-11 main.tex
:book: Update reference

@@
 This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2019a} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
+Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
 On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
@@
 Also, the adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
-
-			% single antenna, DoF -> new words. ff irs fs channel not all design flexibility; active antenna -> frequency
 

### 2020-10-24 main.tex
:pencil: Active vs passive beamforming

@@
 			\begin{adjustbox}{width=\linewidth}
+				\input{assets/re_tx.tex}
+			\end{adjustbox}
+			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\label{fi:re_tx}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\begin{adjustbox}{width=\linewidth}
 				\input{assets/re_reflector.tex}
@@
 			\begin{adjustbox}{width=\linewidth}
-				\input{assets/re_tx.tex}
+				\input{assets/scaling_tx.tex}
 			\end{adjustbox}
-			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
-			\label{fi:re_tx}
+			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
+			\label{fi:scaling_tx}
 		\end{figure}
 
-		The impact of the number of transmit antennas $M$ and IRS reflectors $L$ on the average R-E tradeoff is revealed in Fig.~\ref{fi:re_reflector} and \ref{fi:re_tx}.
-A \textit{first} contrast indicates that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
+		\begin{figure}[!t]
+			\centering
+			\begin{adjustbox}{width=\linewidth}
+				\input{assets/scaling_reflector.tex}
+			\end{adjustbox}
+			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
+			\label{fi:scaling_reflector}
+		\end{figure}
+
+		The number of transmit antennas $M$ and IRS reflectors $L$ influence the average R-E tradeoff as revealed in \ref{fi:re_tx} and Fig.~\ref{fi:re_reflector}.
+\textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
 This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the terms in \ref{eq:z_expand} is amplified while the number remains unchanged.
-Therefore, we conclude that the number of transmit antennas and reflectors have no impact on the waveform preference and transceiving strategy.
-A \textit{second} contrast is that the system performance is more sensitive to the variation of $M$ than $L$.
-Interestingly, the active MRT beamformer only has a transmit array gain of $M$.
-In comparison, the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
-However, the system performance in our setup is dominated by the direct link.
+Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy.
+\textit{Second,} the R-E benefit of passive beamforming scales faster than that of active beamforming.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT versus $M$ and $L$.
+For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power.
+Due to the rectifier nonlinearity, the output DC power ends up with a nearly four-time increase, and the design based on nonlinear model notably outperforms the linear one.
+On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring an array gain up to \SI{6}{\dB}.
+An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
+As a consequence, doubling $L$ brings a [TODO]-fold boost on the received signal power that further amplifies the harvested DC power by [TODO] times.
+However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime.
+These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design.
+\textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors with a much lower complexity.
+The reason is that the system performance in our setup is dominated by the AP-user direct link with the optimal active beamformer obtained in closed form.
 As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
-Therefore, despite increasing $L$ can effectively enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the AP-user channel such that increasing $M$ is more effective to improve the system performance.
-Another explanation is that passive IRS has no design flexibility in the frequency domain and the reflection coefficients are the same for all subbands, while transmit antenna with RF-chains enables weight control over different subbands.
-Therefore, doubling the transmit antenna provides a bigger R-E region than doubling the IRS elements, and we conclude that active beamforming is more effective than passive beamforming.
+Therefore, although increasing $L$ can significantly enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
+Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of IRS restricts its benefit for broadband transmission.
+On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect.
+As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the extra channel dominates the transmission.
 

### 2020-10-28 assets/waveform_subband.tex
:chart_with_upwards_trend: Update plots

--- 2020-09-15 assets/waveform_subband.tex
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.5413547897652\\
+1	2.82172700965795\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	1.17726395475229\\
+1	0.000289213065829642\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.339248611366759\\
-2	2.51030400792355\\
+1	0.295470946033806\\
+2	2.78041553969328\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.223894740731443\\
-2	1.02080999862228\\
+1	6.88515292983531e-06\\
+2	7.11243494475005e-06\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.0454113496416176\\
-2	0.0749432241788367\\
-3	0.174436784198804\\
-4	1.28942850163426\\
+1	0.00886602819700381\\
+2	0.0237787230194659\\
+3	0.108070855596065\\
+4	1.1713310546201\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.596937403868726\\
-2	0.757813025699412\\
-3	0.93101405396448\\
-4	1.34495281524672\\
+1	0.633626542983812\\
+2	0.829836144183102\\
+3	0.976226628588797\\
+4	1.35354289111746\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00380240006943849\\
-2	0.00503538441019884\\
-3	0.00673935788269168\\
-4	0.00928493526066052\\
-5	0.0137641701895959\\
-6	0.0224279293816095\\
-7	0.0491218000319466\\
-8	0.236399650887243\\
+1	0.00167790645812327\\
+2	0.00228016548777977\\
+3	0.00318742185439004\\
+4	0.00462726511721075\\
+5	0.00716743728878421\\
+6	0.0129273763723776\\
+7	0.0308460700090715\\
+8	0.115533318647694\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.57240069726828\\
-2	0.707532355159161\\
-3	0.813056816207979\\
-4	0.908886023167598\\
-5	0.981885468475696\\
-6	1.04528299395164\\
-7	1.09956151160637\\
-8	1.1844120256085\\
+1	0.603245855871981\\
+2	0.755456602981771\\
+3	0.858512489463287\\
+4	0.953124795407537\\
+5	1.02704466315581\\
+6	1.08592420449446\\
+7	1.13090925633169\\
+8	1.18526539633296\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00113001858729917\\
-2	0.00128319910359356\\
-3	0.00145615657965543\\
-4	0.00165374633344438\\
-5	0.00187706123944821\\
-6	0.00215590582737282\\
-7	0.00249082687044019\\
-8	0.00291806514852023\\
-9	0.00347094235515533\\
-10	0.00420624059995467\\
-11	0.00519447041447467\\
-12	0.00655192372378942\\
-13	0.00843364500565299\\
-14	0.0114362629486765\\
-15	0.0171822844859615\\
-16	0.0313917536030629\\
+1	0.000617491691008369\\
+2	0.000717776254822589\\
+3	0.000835285279992789\\
+4	0.000979591082427033\\
+5	0.00115487030006212\\
+6	0.00136293515999463\\
+7	0.00161619354701616\\
+8	0.00191279748068678\\
+9	0.00227218304658774\\
+10	0.0026908090305821\\
+11	0.00319938829308565\\
+12	0.00381122202979217\\
+13	0.00474535479665619\\
+14	0.00756353464992525\\
+15	0.017474797658002\\
+16	0.0547436973724798\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.407704437098618\\
-2	0.463687310263386\\
-3	0.512310122105\\
-4	0.556819078359945\\
-5	0.597811034393655\\
-6	0.633731204224058\\
-7	0.66976207094552\\
-8	0.70029218188591\\
-9	0.730728208302655\\
-10	0.756260014823004\\
-11	0.78063608646419\\
-12	0.800901192040989\\
-13	0.818115628024539\\
-14	0.831455258593228\\
-15	0.841240065783435\\
-16	0.848873422011028\\
+1	0.418853266349202\\
+2	0.478839773751748\\
+3	0.529812149718329\\
+4	0.573539152412764\\
+5	0.611663102441733\\
+6	0.642886720358442\\
+7	0.677359347479036\\
+8	0.701877932539796\\
+9	0.729554340449397\\
+10	0.748421821359951\\
+11	0.768367609874633\\
+12	0.782658242865203\\
+13	0.796571330906253\\
+14	0.806933582871612\\
+15	0.818312174451126\\
+16	0.833414484583038\\
 };

### 2020-10-28 main.tex
:construction: Update parameters

@@
 We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
-Choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$.
+Choose as reference $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
 The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_subband}
@@
 			\end{adjustbox}
-			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:waveform_subband}
@@
 			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_noise}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $B=1\,\si{\MHz}$.}
+			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_V=2\,\si{\meter}$.}
 			\label{fi:re_distance}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_tx}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_reflector}
@@
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
 			\label{fi:scaling_tx}
@@
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
 			\label{fi:scaling_reflector}
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_irs_1mhz}
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
+			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_irs_10mhz}

### 2020-10-29 main.tex
:art: Revise manuscript

@@
 		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal.
-To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain.
-This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS.
-We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
-The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH).
-It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings effective R-E enhancement over benchmark schemes for broadband transmission.
-The adaptive passive beamforming design outperformed the benchmarks for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
+To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates propagation loss and boosts energy efficiency by adaptive passive beamforming.
+This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
+Considering rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique.
+It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
+Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy.
+Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming.
+It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
 	\end{abstract}
@@
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
-			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
-			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level.
+On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level.
 It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
@@
 Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range.
-%Beyond WPT, the work in [10]
-			The work was extended to SWIPT in \cite{Clerckx2018b}.
+Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}.
 Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
@@
 In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
-Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection.
+Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection.
 Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.
@@
 Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems.
-For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs).
+For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 
-		\begin{subsection}{IRS-aided SWIPT}
+		\begin{subsection}{IRS-Aided SWIPT}
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
@@
 It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT.
-For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, and TS and PS are preferred at low and high SNR, respectively.
+For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively.
 Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
-In contrast to the active amplify-and-forward relay whose optimal location is around the midpoint \cite{Li2017}, we observed that the passive IRS should be placed next to either the transmitter or the receiver to further improve the R-E tradeoff, due to the product-distance path loss model.
+Different from the active amplify-and-forward relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model.
 It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
-Also, the adaptive passive beamforming design slightly outperformed the fixed (information-optimized, power-optimized) design for broadband transmission, while the IRS only need to be optimized once for narrowband transmission.
+For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power.
+For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power.
+Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.
 
@@
 			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
-Consider a simplified rectifier in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
 Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
@@
 			\end{equation}
-			That is to say, for single-user MISO SWIPT, it is only necessary to determine the amplitudes $s_{I/P,n}$ at different tones.
+			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{I/P,n}$ at different tones.
 Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
@@
 			\end{align}
-			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials in the corresponding posynomials.
+			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials.
 Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
@@
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
 			\label{fi:scaling_tx}
@@
 \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that the magnitude of the terms in \ref{eq:z_expand} is amplified while the number remains unchanged.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that only the magnitude of the terms in \ref{eq:z_expand} is amplified.
 Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy.
@@
 For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power.
-Due to the rectifier nonlinearity, the output DC power ends up with a nearly four-time increase, and the design based on nonlinear model notably outperforms the linear one.
-On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring an array gain up to \SI{6}{\dB}.
-An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a reflect array gain $L$, achieving a total array gain of $L^2$.
-As a consequence, doubling $L$ brings a [TODO]-fold boost on the received signal power that further amplifies the harvested DC power by [TODO] times.
+Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
+On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring a SNR boost up to \SI{6}{\dB}, corresponding to an reflect array gain of $L^2$.
+An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
+As a consequence, doubling $L$ brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
+Besides, by considering harvester nonlinearity, the proposed design brings a \SI{20}{\dB} increase in the output DC current over conventional linear perspective.
 However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime.
 These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design.
-\textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors with a much lower complexity.
-The reason is that the system performance in our setup is dominated by the AP-user direct link with the optimal active beamformer obtained in closed form.
+\textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity.
+The reason is that the system performance in our setup is dominated by the AP-user direct link, with the optimal active beamformer obtained in closed form.
 As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
@@
 		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission.
-The adaptive scheme optimizes the IRS, waveform and active beamforming alternatively for each points in the R-E boundary.
-In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the waveform to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where each element is assumed to have an independent reflection coefficient for each subband.
-Therefore, the ideal IRS has a total design design flexibility of $NL$.
-Since the IRS only control the phase of the concatenated channel, when there is only one transmit antenna at the AP, the optimal strategy for each FS reflector would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+The adaptive scheme jointly optimize the waveform, splitting ratio, active beamforming and passive beamforming alternatively for each points in the R-E boundary.
+In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the rest to obtain the R-E curve.
+To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where each element is assumed to have an independent reflection coefficient for each subband, accounting for a total design design flexibility of $NL$.
+Since the IRS only control the phase of the concatenated channel, for single transmit antenna AP, the optimal strategy for each FS reflector would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
 		\begin{equation}
@@
 This is because IRS creates and controls the weak extra channels for a constructive signal superposition.
-\textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but noticeable for broadband transmission.
+\textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but obvious for broadband transmission.
 The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal ideal reflection coefficients would almost align at all subbands.
-That is to say, for narrowband transmission, there is no enough diversity and incentive for IRS to manipulate the subchannel strength, and all four IRS strategies coincide with each other.
-It implies that for narrowband SWIPT, the passive beamforming only need to be optimized once to characterize the whole R-E boundary.
-As a special case, the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT.
+That is to say, there is no enough diversity as well as incentive for the IRS to manipulate the subchannel strength such that all four IRS strategies coincide with each other.
+It implies that for narrowband SWIPT, the optimal passive beamforming obtained from any R-E point is also optimal for the whole R-E boundary.
 On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.
@@
 In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting.
-Therefore, adaptive IRS design is required for broadband SWIPT as information and energy receivers have different preference on the subchannel strength distribution.
+In conclusion, adaptive passive beamforming is required for broadband SWIPT as information and energy receivers have different preference on the subchannel strength control.
 	\end{section}
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper proposed a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user.
+		This paper proposes a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user.
 We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
 Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures.
-Efficient algorithms based on GP, SCA, SDR and AO techniques are proposed to balance the system performance and computational complexity, which are numerically demonstrated to converge to a stationary point of the original problem for all tested channel realizations under different configurations.
-We confirmed that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
-When developed near the transmitter, IRS can provide effective channel enhancement to expand the operation range and enlarge the R-E region.
-Compared with active transmit antenna, IRS elements has no design flexibility in the frequency domain, but the passive characteristic significantly reduces the power consumption and enables noise-free reflection.
-Finally, adaptive passive beamforming is required for broadband transmission while the IRS only need to be optimized once for narrowband transmission.
-		% For broadband SWIPT, adaptive passive beamforming for different R-E pairs is required, as ID and EH have different preference on the subchannel strength distribution.
-For narrowband SWIPT, the subchannel responses are very similar and the optimal passive beamforming for all R-E points coincide with each other.
-Therefore, the IRS only need to be optimized once.
-		% that brings a quadratic array gain.
+Efficient algorithms based on GP, SCA, SDR and AO techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
+We confirm that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
+When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
+Compared with transmit antenna, IRS element has no design flexibility in the frequency domain, but the smart reflection combats channel hardening effect to further boost the array gain and power scaling laws.
+Finally, adaptive passive beamforming is required for broadband transmission, while the optimal IRS obtained from any R-E point is also optimal for the whole R-E region for narrowband SWIPT.
 

### 2020-11-01 main.tex
:art: Illustrate block diagonal matrix

@@
 \usepackage{cite}
+\usepackage{colortbl}
 \usepackage{environ}
@@
 \usepackage{stfloats}
+\usepackage{tikz}
 \usepackage{url}
@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{remark}{Remark}
 \DeclareSIUnit{\belm}{Bm}
@@
 \DeclareSIUnit{\dBi}{\deci\beli}
+\usetikzlibrary{arrows,matrix,positioning}
 
@@
 \begin{document}
-	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
+	%\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
+	%\title{Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer: Joint Waveform, Active and Passive Beamforming Design}
+	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer}
+	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided SWIPT}
+	\title{Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
 	\author{
@@
 		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal.
-To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates propagation loss and boosts energy efficiency by adaptive passive beamforming.
-This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
-Considering rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency by provide a passive beamforming gain.
+This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
+Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
 Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique.
@@
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level.
+On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape.
 It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT.
-Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2020a}.
-Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT.
+Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}.
+Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range.
 Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}.
-Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
@@
 In such cases, a single energy stream is enough for all energy receivers.
+However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and on an inaccurate and oversimplified linear energy harvester model.
 
-			However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission based on an oversimplified linear harvester model for separated information and energy receivers.
-Rectifier nonlinearity and co-localized receiver, acknowledged as key to practical and efficient SWIPT system design, have not yet been addressed in the relevant research.
-In this paper, we marry the benefits of joint waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS.
+			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS.
 The contribution of the paper are listed as follows.
@@
 The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
-This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
+This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
 Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
@@
 			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture.
-The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints.
+The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints.
 Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
 On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner.
-Despite no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
+Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
 
@@
 For a square matrix $\boldsymbol{S}$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
-The distribution of a random vector consists of Circularly Symmetric Complex Gaussian (CSCG) variables is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$, where $\boldsymbol{\mu}$ is the mean vector and $\boldsymbol{\Sigma}$ is the covariance matrix.
-$\sim$ means "distributed as".
+The distribution of a CSCG random vector with mean vector $\boldsymbol{0}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$, and $\sim$ stands for "distributed as".
 We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
@@
 		\begin{subsection}{Transmit Signal}
-			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows an i.i.d.
-CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
+			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
 The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
@@
 			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$.
-Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas.
-Therefore, the transmit information and power signals write as
+
+			Stacking up the entries on all antennas, we define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t)=\boldsymbol{x}_{I}(t)+\boldsymbol{x}_{P}(t)$, where
 			\begin{align}
@@
 			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
-Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
 The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
@@
 			\end{equation}
-			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
+			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
 Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
+			\begin{remark}
+				The IRS reflection coefficients are constant across the frequency, i.e. the IRS is frequency-flat where independent phase shift control over subbands are prohibited due to hardware constraints.
+			\end{remark}
 		\end{subsection}
@@
 			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$.
-Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
+Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
 		\end{subsection}
@@
 			\end{equation}
-			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \ref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
+			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
 			\begin{equation}\label{eq:i_out}
@@
 			where $k_i=i_s/i!(nv_t)^i$.
-It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \ref{eq:z} with $n_0=2$.
+It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
 However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
 In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode.
-For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity.
+For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}.
 Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-The corresponding $z$ is detailed in \ref{eq:z_expand}.
+Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+Let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$.
+On top of this, we introduce $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ ($n=-N+1,\dots,N-1$) that can be viewed as $N \times N$ blocks, each of size $M \times M$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and null all other blocks.
 
-			Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$.
-Moreover, define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and let $\boldsymbol{W}_{I/P,n}$ keep its $n$-th ($n=-N+1,\dots,N-1$) block diagonal and null the remaining entries, where the blocks are of size $M \times M$.
-On top of this, relevant DC terms are expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
+			% \begin{figure}[!t]
+			% 	\begin{equation*}
+			% 		\resizebox{0.9\linewidth}{!}{
+			% 			$\boldsymbol{W}_{I/P}=
+			% 			\left(
+			% 				\begin{array}{cccc}
+			% 					\cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots                                                                 & \cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H   \\
+			% 					\cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \cellcolor[gray]{0.7}\ddots                                           & \vdots                                                                \\
+			% 					\vdots                                                              & \cellcolor[gray]{0.7}\ddots                                         & \cellcolor[gray]{0.5}\ddots                                           & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
+			% 					\cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots                                                               & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H
+			% 				\end{array}
+			% 			\right)$
+			% 		}
+			% 	\end{equation*}
+			% 	\caption{$\boldsymbol{W}_{I/P,n}$ keeps the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls the remaining entries.
+Solid, dashed and dotted diagonals correspond to $n>,=,<0$.
+For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $n$-th diagonal satisfies $n_2-n_1=n$.}
+			% 	\label{fi:block_diagonal}
+			% \end{figure}
+
+			\begin{figure*}[!t]
+				\begin{equation*}
+						\boldsymbol{W}_{I/P}=
+						\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
+							\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
+							{
+								\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H \\
+								\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \ddots & \vdots \\
+								\vdots & \ddots & \ddots & \boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
+								\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H \\
+							};
+							\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
+							\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
+							\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
+							\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
+							\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
+							\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
+							\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
+							\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
+
+						\end{tikzpicture}
+				\end{equation*}
+				\caption{$\boldsymbol{W}_{I/P}$ consists of $N \times N$ blocks of size $M \times M$.
+$\boldsymbol{W}_{I/P,k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls all remaining blocks.
+Solid, dashed and dotted blocks correspond to $n>0$, $n=0$ and $n<0$, respectively.
+For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+				\label{fi:block_diagonal}
+			\end{figure*}
+
+			On top of this, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$ and let $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ keep their $n$-th ($n=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+
+			null the remaining entries, where the blocks are of size $M \times M$. On top of this, relevant DC terms are expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 			\begin{figure*}[b]
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and different rate constraints
+		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
 		\begin{maxi!}
@@
 		\end{maxi!}
-		Problem~\ref{op:original} is intricate as the variables are coupled and the objective function \ref{ob:original}, the rate constraint \ref{co:original_rate}, and the IRS magnitude constraint \ref{co:original_modulus} are non-convex.
+		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex.
 To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
@@
 			\end{align}
-			To maximize non-concave expression \ref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
+			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 			\end{align}
-			which provide lower bounds to the corresponding terms in \ref{eq:z_irs}.
-Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \ref{eq:z_irs_approx}, and problem~\ref{op:original} is transformed to
+			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}.
+Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to
 			\begin{figure*}[b]
@@
 			\end{maxi!}
-			Problem~\ref{op:irs} is not a standard Semidefinite Programming (SDP).
-If we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, and the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\ref{op:original}.
+			Problem~\eqref{op:irs} is not a standard Semidefinite Programming (SDP).
+If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, and the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\eqref{op:original}.
 In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations such that the performance loss by SDR is insignificant.
-A related version of problem~\ref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+A related version of problem~\eqref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 
@@
 Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
-Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}.
+Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}.
 Finally, the phase shift is retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
@@
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\ref{op:irs}
-						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\eqref{op:irs}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
 					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
@@
 At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \ref{eq:R_waveform} and \ref{eq:z_waveform}, respectively.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
 			\begin{equation}\label{eq:R_waveform}
@@
 			\end{figure*}%
-			Therefore, problem~\ref{op:original} is reduced to an amplitude optimization issue
+			Therefore, problem~\eqref{op:original} is reduced to an amplitude optimization issue
 			\begin{maxi!}
@@
 			\end{maxi!}
-			Since problem~\ref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
+			Since problem~\eqref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
 			\begin{mini!}
@@
 			\end{mini!}
-			The denominators of \ref{co:waveform_objective}, \ref{co:waveform_rate} are posynomials \cite{Boyd2007} that further decompose as
+			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that further decompose as
 			\begin{align}
@@
 			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials.
-Following \cite{Chiang2005}, we upper bound posynomials \ref{eq:posynomial_objective} and \ref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\ref{op:waveform_rgp} reduces to
+Following \cite{Chiang2005}, we upper bound posynomials \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\eqref{op:waveform_rgp} reduces to
 			\begin{mini!}
@@
 			\end{align}
-			Problem~\ref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+			Problem~\eqref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 $\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
@@
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_P}^{(i)},\gamma_{m_{I,n}}^{(i)}\}$ by \ref{eq:gamma_P}, \ref{eq:gamma_I}
-						\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem~\ref{op:waveform_gp}
-						\State Compute $z^{(i)}$ by \ref{eq:z_waveform}
+						\State Update $\{\gamma_{m_P}^{(i)},\gamma_{m_{I,n}}^{(i)}\}$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
+						\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \ref{eq:w_IP}
+					\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \eqref{eq:w_IP}
 					\State \textbf{output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
@@
 						\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
-						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
-						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
+						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \eqref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
@@
 			\begin{proof}\label{pf:irs}
-				The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem~\ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
-Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}.
+				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution of problem~\eqref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
+Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions.
@@
 			\begin{proposition}\label{pr:ao}
-				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\ref{op:original}.
+				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:ao}
-				The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}.
+				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
 Thus, Algorithm~\ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
-As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\ref{op:original}.
+As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
 			\end{proof}
@@
 It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$.
-Therefore, $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\ref{op:irs} without performance loss.
+Therefore, $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\eqref{op:irs} without performance loss.
 
@@
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
 Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
@@
 \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that only the magnitude of the terms in \ref{eq:z_expand} is amplified.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that only the magnitude of the terms in \eqref{eq:z_expand} is amplified.
 Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy.

### 2020-11-02 main.tex
:construction: Update diagonal index

@@
 Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-Let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$.
-On top of this, we introduce $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ ($n=-N+1,\dots,N-1$) that can be viewed as $N \times N$ blocks, each of size $M \times M$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and null all other blocks.
-
-			% \begin{figure}[!t]
-			% 	\begin{equation*}
-			% 		\resizebox{0.9\linewidth}{!}{
-			% 			$\boldsymbol{W}_{I/P}=
-			% 			\left(
-			% 				\begin{array}{cccc}
-			% 					\cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots                                                                 & \cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H   \\
-			% 					\cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \cellcolor[gray]{0.7}\ddots                                           & \vdots                                                                \\
-			% 					\vdots                                                              & \cellcolor[gray]{0.7}\ddots                                         & \cellcolor[gray]{0.5}\ddots                                           & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
-			% 					\cellcolor[gray]{0.9}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots                                                               & \cellcolor[gray]{0.7}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \cellcolor[gray]{0.5}\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H
-			% 				\end{array}
-			% 			\right)$
-			% 		}
-			% 	\end{equation*}
-			% 	\caption{$\boldsymbol{W}_{I/P,n}$ keeps the $n$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls the remaining entries.
-Solid, dashed and dotted diagonals correspond to $n>,=,<0$.
-For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $n$-th diagonal satisfies $n_2-n_1=n$.}
-			% 	\label{fi:block_diagonal}
-			% \end{figure}
+On top of this, let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{I/P}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{I/P,k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 
@@
 $\boldsymbol{W}_{I/P,k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls all remaining blocks.
-Solid, dashed and dotted blocks correspond to $n>0$, $n=0$ and $n<0$, respectively.
+Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
 For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
@@
 
-			On top of this, we define $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$ and let $\boldsymbol{W}_{I/P,n} \in \mathbb{C}^{MN \times MN}$ keep their $n$-th ($n=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
-
-			null the remaining entries, where the blocks are of size $M \times M$. On top of this, relevant DC terms are expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 			\begin{figure*}[b]
@@
 					\mathcal{A}\left\{y_{P}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\,.\label{eq:y_P4}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})^H\,.\label{eq:y_P4}
 				\end{align}
@@
 		\begin{subsection}{IRS Phase Shift}
-			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that for $n=1,\dots,N$,
+			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
 			\begin{align}
@@
 			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Also, for $n=-N+1,\dots,N-1$, define $t_{I/P,n}$ as
+On the other hand, we define $t_{I/P,k}$ as
 			\begin{align}
-				t_{I/P,n}
-				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\nonumber\\
-				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
+				t_{I/P,k}
+				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,k}\boldsymbol{h}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,k})\nonumber\\
+				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,k}\right)\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,k})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,k}\boldsymbol{\Phi})
 			\end{align}
-			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,k}=\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 Therefore, the rate and objective expressions rewrite as
@@
 				& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\nonumber\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{k=-N+1}^{N-1}{t_{P,k}t_{P,k}^*}\right)\nonumber\\
 				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\,.\label{eq:z_irs}
@@
 				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\,,\label{eq:taylor_1}\\
-				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
-				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\,,\label{eq:taylor_2}\\
+				t_{P,k}^{(i)} (t_{P,k}^{(i)})^*
+				& \ge 2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*\,,\label{eq:taylor_2}\\
 				t_{I,0}^{(i)} t_{P,0}^{(i)}
@@
 					& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*}\right)\nonumber\\
 					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}
@@
 					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
-					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
-					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$ for $n=-N+1,\dots,N-1$
+					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$, $\boldsymbol{C}_{I/P,k}$, $\forall n,k$
+					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,k}^{(0)}, \forall k$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\eqref{op:irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,k}^{(i)}$ by solving problem~\eqref{op:irs}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}

### 2020-11-04 main.tex
:construction: Rephrase and revise

@@
 It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
+% The proposed design enables a joint control of transmitter, receiver and wireless channel.
 	\end{abstract}
@@
 		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex.
-To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
+To achieve a feasible solution, we propose a AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
+		\begin{remark}
+			At subband $n$, the MIMO incident channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element.
+Reflection coefficient $\phi_l$ is shared for the $l$-th MISO incoming channel of all subbands, namely $MN$ entries in total.
+As information and power transfer favor different channel strength distribution over frequencies, for a given channel, the passive beamforming need to be optimized for each R-E point to maximize the R-E tradeoff.
+If the IRS is frequency-selective and there is only one transmit antenna, then reflector $l$ can simply align the AP-IRS($l$)-user channel with the AP-user channel at all subbands so that the joint design of waveform, active and passive beamforming, and splitting ratio would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
+		\end{remark}
 
@@
 			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,k}=\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, the rate and objective expressions rewrite as
+Therefore, we rewrite the rate and objective expressions as
 			\begin{align}
@@
 In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations such that the performance loss by SDR is insignificant.
-A related version of problem~\eqref{op:irs} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:irs} without constraint \ref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 
@@
 			\end{mini!}
-			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that further decompose as
+			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that are further decomposed as
 			\begin{align}
@@
 			\begin{proposition}\label{pr:irs}
-				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} can provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} can provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
 			\end{proposition}
@@
 Thus, Algorithm~\ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfy the KKT conditions.
+To prove $\boldsymbol{\Phi}^{(i)}$ converges to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions.
 			\end{proof}
@@
 			\begin{proposition}\label{pr:ao}
-				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
-Choose as reference $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
+We choose as reference $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
 The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
@@
 In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
+		% - at the WPT point, power is allocated to the multisine waveform only, isn't it?
+		% - for single-carrier WPT, modulated waveform may be preferred as it has a modulation gain (also proved in Fig. 5)
 		On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only.

### 2020-11-06 main.tex
:construction: Revise manuscript

@@
 Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
-Different from the active amplify-and-forward relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model.
+Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model.
 It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
@@
 The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
-On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
+On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
 			\begin{equation}\label{eq:h_n}
@@
 Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
-			\begin{remark}
-				The IRS reflection coefficients are constant across the frequency, i.e. the IRS is frequency-flat where independent phase shift control over subbands are prohibited due to hardware constraints.
+			\begin{remark}\label{re:irs_frequency_flat}
+				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat.
+Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
+				% At subband $n$, the AP-IRS MIMO channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element.
+Reflection coefficient $\phi_l$ is shared for the $l$-th AP-IRS MISO channel of all subbands, namely $MN$ entries in total.
+				The reflection coefficient of each IRS element is shared for the AP-IRS MISO channel and over all subbands, namely $MN$ entries in total.
 			\end{remark}
@@
 To achieve a feasible solution, we propose a AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
-		\begin{remark}
-			At subband $n$, the MIMO incident channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element.
-Reflection coefficient $\phi_l$ is shared for the $l$-th MISO incoming channel of all subbands, namely $MN$ entries in total.
-As information and power transfer favor different channel strength distribution over frequencies, for a given channel, the passive beamforming need to be optimized for each R-E point to maximize the R-E tradeoff.
-If the IRS is frequency-selective and there is only one transmit antenna, then reflector $l$ can simply align the AP-IRS($l$)-user channel with the AP-user channel at all subbands so that the joint design of waveform, active and passive beamforming, and splitting ratio would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
+		\begin{remark}\label{re:irs_subchannel_alignment}
+			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of IRS introduces a resource allocation problem.
+Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands.
+In this case, the strength of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
 		\end{remark}
@@
 			\begin{proposition}\label{pr:ao}
-				Suppose $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
-Thus, Algorithm~\ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ has limit points so that Algorithm~\ref{al:alternating} is guaranteed to converge.
 As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
@@
 		On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only.
-For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.
+For a fair comparison, the $x$-axis of the plots has been normalized to average subband rate $R/N$.
 
@@
 		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-The reason is that although each subband receives a smaller proportion of the total power, more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+\textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy.
+The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
 Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
-However, an excessively large $N$ not only increases complexity but also operates out of the small-signal harvester model, thus become prohibitive.
 \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
@@
 		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}.
-We \textit{first} note that for a large number of subbands, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
+\textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
 Hence, TS is preferred at low SNR while PS is preferred at high SNR.
@@
 The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, as a small amplitude could be inefficient for energy maximization.
-On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine.
+On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage the of multisine for efficient power transfer.
 The result highlights the benefit of multisine and the necessity of joint optimization of waveform and splitting ratio.
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that, different from the active amplify-and-forward relay that achieves optimal performance when developed around the midpoint, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+A \textit{first} observation is that, different from the active AF relay that achieves optimal performance when developed around the midpoint, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
 It origins from the product-distance path loss model that applies to finite-size element reflection.
@@
 Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation is that there exist two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$.
+A \textit{second} observation is that there exist two optimal IRS development locations that minimizes the path loss production $\Lambda_I\Lambda_R$.
 It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
@@
 Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
-On the other hand, when the IRS is very closed to the transmitter or the receiver, doubling $L$ can bring a SNR boost up to \SI{6}{\dB}, corresponding to an reflect array gain of $L^2$.
+On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring a SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$.
 An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
@@
 Besides, by considering harvester nonlinearity, the proposed design brings a \SI{20}{\dB} increase in the output DC current over conventional linear perspective.
-However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime.
-These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design.
+These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design \footnote{However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime, which prevents an excessively large $M$ or $L$.}.
 \textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity.
@@
 As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
-Therefore, although increasing $L$ can significantly enhance the AP-IRS-user extra channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
+Therefore, although increasing $L$ can significantly enhance the AP-IRS-user auxiliary channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
 Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of IRS restricts its benefit for broadband transmission.
 On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect.
-As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the extra channel dominates the transmission.
+As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the auxiliary channel dominates the transmission.
 
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_irs_1mhz}
@@
 			\end{adjustbox}
-			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
 			\label{fi:re_irs_10mhz}
@@
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission and broadband transmission.
-The adaptive scheme jointly optimize the waveform, splitting ratio, active beamforming and passive beamforming alternatively for each points in the R-E boundary.
-In comparison, the WIT/WPT-based schemes only perform alternating optimization for the right-most/left-most points, then fix the IRS and update the rest to obtain the R-E curve.
-To gain some insight into the IRS behavior, we compare the results above to that of no IRS and the ideal FS IRS, where each element is assumed to have an independent reflection coefficient for each subband, accounting for a total design design flexibility of $NL$.
-Since the IRS only control the phase of the concatenated channel, for single transmit antenna AP, the optimal strategy for each FS reflector would be aligning the AP-IRS-user and AP-user channel over all subbands, namely
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband (\SI{1}{\MHz} bandwidth) transmission and broadband transmission (\SI{10}{\MHz} bandwidth).
+The adaptive IRS strategy adjusts the passive beamforming for each sample in the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shift for information and power purposes only (correspond to the points on the $x$ and $y$ axes).
+To gain some insight into the IRS behavior, we compare the results above to those of ideal frequency-selective IRS and no IRS.
+In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design design flexibility of $NL$.
+When there is only one transmit antenna, each FS reflector simply aligns the AP-IRS-user to the AP-user channel at all subbands, namely
 		\begin{equation}
@@
 		\end{equation}
-		\textit{First}, it is observed that the presence of IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
-This is because IRS creates and controls the weak extra channels for a constructive signal superposition.
-\textit{Second}, the performance gaps of the adaptive, ideal and fixed IRS are negligible for narrowband transmission but obvious for broadband transmission.
-The reason is that when $B=1\,\si{\MHz}$, the subchannel responses are very similar and the optimal ideal reflection coefficients would almost align at all subbands.
-That is to say, there is no enough diversity as well as incentive for the IRS to manipulate the subchannel strength such that all four IRS strategies coincide with each other.
-It implies that for narrowband SWIPT, the optimal passive beamforming obtained from any R-E point is also optimal for the whole R-E boundary.
-On the other hand, the channel frequency selectivity becomes significant for $B=10\,\si{\MHz}$, and the ideal FS IRS outperforms the others as it requires no tradeoff in subchannel alignments.
-Moreover, the WIT-optimized IRS tends to equalize the channel strength for all subbands as possible, due to the preference of WF strategy at high SNR.
-In comparison, the WPT-optimized IRS beams less towards few weakest subchannels, due to the inefficiency of small-amplitude tones in energy harvesting.
-In conclusion, adaptive passive beamforming is required for broadband SWIPT as information and energy receivers have different preference on the subchannel strength control.
+		\textit{First}, it is observed that the assistance of IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
+It is because the IRS enables a constructive channel composition that enhances the received signal strength.
+\textit{Second}, the performance of all four IRS strategies coincide with each other for narrowband SWIPT.
+It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region, and for a given channel, we only need to adapt the waveform and splitting ratio to achieve different rate and energy performance.
+When the bandwidth is small, all channels are approximately flat and the optimal ideal reflection coefficients would almost synchronize at all subbands so that the loss by frequency-flat IRS is negligible.
+Also, the subchannel tradeoff in Remark \ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies, and the adaptive and non-adaptive strategies end up with the same result.
+\textit{Third}, the adaptive passive beamforming is required to maximize the R-E tradeoff for broadband SWIPT.
+Recall Remark \ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
+By adaptive passive beamforming, the channel energy can either be concentrated in few strongest subbands to increase rate at a low SNR, or spread evenly over all subbands to boost the output DC power.
+The advantage of such a smart channel control is prominent for broadband SWIPT where the tradeoff between subbands becomes more obvious.
 	\end{section}
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper proposes a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the spectrum and energy efficiency of a single user.
+		This paper proposes a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
 We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
@@
 When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
-Compared with transmit antenna, IRS element has no design flexibility in the frequency domain, but the smart reflection combats channel hardening effect to further boost the array gain and power scaling laws.
-Finally, adaptive passive beamforming is required for broadband transmission, while the optimal IRS obtained from any R-E point is also optimal for the whole R-E region for narrowband SWIPT.
+Compared with transmit antenna, IRS element has no design flexibility in the frequency domain, but integrates the combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
+Finally, adaptive passive beamforming is demonstrated beneficial for broadband transmission, while the optimal IRS for any R-E point is also optimal for the whole R-E region for narrowband SWIPT.
 
@@
 
+	% ! [TODO] figure border
+
 	\bibliographystyle{IEEEtran}

### 2020-11-07 main.tex
:art: Revise manuscript

@@
 		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal.
-To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency by provide a passive beamforming gain.
+To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain.
 This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
@@
 It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy.
+Simulation results also show that the IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy.
 Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming.
@@
 Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}.
-Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
@@
 It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
+Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
 		\end{subsection}
@@
 
-			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation.
+			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at a specific frequency to mitigate signal attenuation.
 Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
-On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem.
-\cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients.
+			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT.
+It was argued in \cite{Wu2020b} that a dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
+On the other hand, \cite{Tang2019} suggested that if the interference can be canceled, multiple energy beams are generally required for the max-min harvested power problem.
+\cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update the transmit precoder and the IRS phase shifts, while the outer layer updates the penalty coefficients.
 It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated.
 In such cases, a single energy stream is enough for all energy receivers.
-However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and on an inaccurate and oversimplified linear energy harvester model.
+However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
 
-			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS.
-The contribution of the paper are listed as follows.
+			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.
+The contributions of the paper are listed as follows.
 
@@
 Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
-On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
+On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
 
-			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture.
+			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture.
 The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints.
-Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
-On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner.
+Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
+On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner.
 Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
@@
 			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture.
-It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT.
-For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively.
-Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
-Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model.
-It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
+It is confirmed that the observations for SWIPT carry on to IRS-aided SWIPT.
+For example, a dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively.
+Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
+Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model.
+It implies that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
 For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power.
@@
 			\textit{Organization:} The rest of this paper is organized as follows.
-Section~\ref{se:system_model} introduces the signal, channel, receiver and R-E tradeoff models of the IRS-aided SWIPT system.
+Section~\ref{se:system_model} introduces the signal, channel, receiver, and R-E tradeoff models of the IRS-aided SWIPT system.
 Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
@@
 			\import{assets/}{system.pdf_tex}
-			\caption{An IRS-aided OFDM SWIPT system.}
+			\caption{An IRS-aided multi-carrier SWIPT system.}
 			\label{fi:system}
@@
 A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
-Two practical co-located receiver architectures are compared in terms of R-E region.
+Two practical co-located receiver architectures are compared in terms of the R-E region.
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
 In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design.
-Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
+Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by the IRS for two and more times are omitted.
 We also assume the noise power is too small to be harvested.
@@
 			\end{equation}
-			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
+			By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
 			\begin{equation}\label{eq:i_out}
@@
 		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex.
-To achieve a feasible solution, we propose a AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
+To achieve a feasible solution, we propose an AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shifts at the IRS, and the power splitting ratio at the receiver, until convergence.
 		\begin{remark}\label{re:irs_subchannel_alignment}
-			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of IRS introduces a resource allocation problem.
+			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
 Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands.
-In this case, the strength of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
+In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
 		\end{remark}
@@
 Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}.
-Finally, the phase shift is retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
+Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
 The SCA algorithm for passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
@@
 At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
 			\begin{equation}\label{eq:R_waveform}
@@
 		On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only.
-For a fair comparison, the $x$-axis of the plots has been normalized to average subband rate $R/N$.
+For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$.
 
@@
 The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
-Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
-Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
+Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
 \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
@@
 a time sharing between the WPT point and the tangent WIPT point obtained by PS.
-Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transceiving strategy, both heavily depends on $N$.
+Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving strategy, both heavily depends on $N$.
 
@@
 Hence, TS is preferred at low SNR while PS is preferred at high SNR.
-This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands.
+This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to a few strongest subbands.
 As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested energy via the coupling effect by rectifier nonlinearity.
@@
 The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, as a small amplitude could be inefficient for energy maximization.
-On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage the of multisine for efficient power transfer.
+On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of the multisine for efficient power transfer.
 The result highlights the benefit of multisine and the necessity of joint optimization of waveform and splitting ratio.
@@
 On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems.
-Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation is that there exist two optimal IRS development locations that minimizes the path loss production $\Lambda_I\Lambda_R$.
+Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network.
+A \textit{second} observation is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$.
 It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
@@
 Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
-On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring a SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$.
+On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$.
 An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
@@
 Besides, by considering harvester nonlinearity, the proposed design brings a \SI{20}{\dB} increase in the output DC current over conventional linear perspective.
-These results emphasize the effectiveness of passive beamforming and the importance of modelling rectifier nonlinearity in the system design \footnote{However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime, which prevents an excessively large $M$ or $L$.}.
-\textit{Third,} using only few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity.
+These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the system design \footnote{However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime, which prevents an excessively large $M$ or $L$.}.
+\textit{Third,} using only a few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity.
 The reason is that the system performance in our setup is dominated by the AP-user direct link, with the optimal active beamformer obtained in closed form.
-As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is in the scope of \num{e-7} while the extra path loss product $\Lambda_I\Lambda_R$ is below \num{e-10}.
+As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is around \SI{60}{\dB} while the extra path loss product $\Lambda_I\Lambda_R$ is over \SI{100}{\dB}.
 Therefore, although increasing $L$ can significantly enhance the AP-IRS-user auxiliary channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
-Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of IRS restricts its benefit for broadband transmission.
+Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission.
 On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect.
@@
 		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband (\SI{1}{\MHz} bandwidth) transmission and broadband transmission (\SI{10}{\MHz} bandwidth).
-The adaptive IRS strategy adjusts the passive beamforming for each sample in the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shift for information and power purposes only (correspond to the points on the $x$ and $y$ axes).
-To gain some insight into the IRS behavior, we compare the results above to those of ideal frequency-selective IRS and no IRS.
-In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design design flexibility of $NL$.
+The adaptive IRS strategy adjusts the passive beamforming for each sample in the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes).
+To gain some insight into the IRS behavior, we compare the results above to ideal frequency-selective IRS and no IRS.
+In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design flexibility of $NL$.
 When there is only one transmit antenna, each FS reflector simply aligns the AP-IRS-user to the AP-user channel at all subbands, namely
@@
 		\end{equation}
-		\textit{First}, it is observed that the assistance of IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
+		\textit{First}, it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
 It is because the IRS enables a constructive channel composition that enhances the received signal strength.
@@
 It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region, and for a given channel, we only need to adapt the waveform and splitting ratio to achieve different rate and energy performance.
-When the bandwidth is small, all channels are approximately flat and the optimal ideal reflection coefficients would almost synchronize at all subbands so that the loss by frequency-flat IRS is negligible.
+When the bandwidth is small, all channels are approximately flat, and the optimal ideal reflection coefficients would almost synchronize at all subbands so that the loss by frequency-flat IRS is negligible.
 Also, the subchannel tradeoff in Remark \ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies, and the adaptive and non-adaptive strategies end up with the same result.
@@
 Recall Remark \ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
-By adaptive passive beamforming, the channel energy can either be concentrated in few strongest subbands to increase rate at a low SNR, or spread evenly over all subbands to boost the output DC power.
+By adaptive passive beamforming, the channel energy can either be concentrated in few strongest subbands to increase the rate at a low SNR, or spread evenly over all subbands to boost the output DC power.
 The advantage of such a smart channel control is prominent for broadband SWIPT where the tradeoff between subbands becomes more obvious.
@@
 We confirm that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
-When developed near the transmitter, IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
+When developed near the transmitter, the IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
 Compared with transmit antenna, IRS element has no design flexibility in the frequency domain, but integrates the combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
@@
 For example, how to optimize waveform, active and passive beamforming in a multiuser SWIPT system?
-How can multiple IRS cooperate with each other to further benefit R-E tradeoff?
+How can multiple IRS cooperate with each other to further benefit the R-E tradeoff?
 How to perform channel estimation without RF-chains at the IRS?
-How to design IRS-aided SWIPT system for different multiple access techniques?
+How to design an IRS-aided SWIPT system for different multiple access techniques?
 How to implement IRS in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?
@@
 
-	% ! [TODO] figure border
-
 	\bibliographystyle{IEEEtran}

### 2020-11-23 main.tex
:pencil: Rephrase introduction

@@
 
+% reflection coefficients vs reflector vs reflection element
+
 \begin{document}
@@
 	\begin{abstract}
-		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal.
+		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the strength of the received Radio-Frequency (RF) signal.
 To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain.
-This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
-Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
-Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique.
-It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR).
-Simulation results also show that the IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy.
-Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming.
-It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
-% The proposed design enables a joint control of transmitter, receiver and wireless channel.
+This paper investigates an effective IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
+Considering the energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+Stationary solutions are achieved based on the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.
+Despite the hardware limitations of IRS constraint the reflection elements to be Frequency-Flat (FF), results demonstrate the significant benefits of the proposed architecture based on a joint design of the waveform, active and passive beamforming to enlarge the R-E region of IRS-aided SWIPT.
 	\end{abstract}
@@
 			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks.
+Most existing mobile devices are powered by batteries that require frequent charging or replacement, which brings high maintenance cost and restricts the scale of networks.
 Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range.
@@
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, call for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
+The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
 
@@
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape.
+On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the input rectifier power and waveform shape.
 It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
@@
 Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range.
-Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}.
-Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?".
+Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}, which uniquely showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: "what is the optimal input distribution for SWIPT under nonlinearity?
+".
 This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
@@
 modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
 Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency.
+			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase the spectrum and energy efficiency.
 In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
 Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.
+Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS because active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.
 
@@
 Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
-The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}.
-Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.
-In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off.
-To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient.
-Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems.
-For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
+The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
+Moreover, \cite{Abeywickrama2019} investigated the coupling effect of reflection amplitude and phase shift based on impedance equation, and \cite{Nadeem2019} proposed a sequential cascaded channel estimation for Time-Division Duplex (TDD) systems.
+%To reduce the estimation overhead and design complexity, \cite{Yang2019} considered a group-based IRS model where adjacent elements share a common reflection coefficient.
+			A novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems was proposed in \cite{Yang2020}, which varies the reflection coefficients over consequent slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT.
-It was argued in \cite{Wu2020b} that a dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system.
-On the other hand, \cite{Tang2019} suggested that if the interference can be canceled, multiple energy beams are generally required for the max-min harvested power problem.
-\cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update the transmit precoder and the IRS phase shifts, while the outer layer updates the penalty coefficients.
-It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated.
-In such cases, a single energy stream is enough for all energy receivers.
+For a multi-user IRS-aided SWIPT system, dedicated energy beams are unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power.
+In such cases, the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers.
 However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
-
 In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.
-The contributions of the paper are listed as follows.
+We ask ourselves the important question: "How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?
+" The contributions of the paper are listed as follows.
 
@@
 This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design.
-On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.
+Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model \cite{Clerckx2019,Clerckx2016a}), which prevents from exploiting the waveform gain in SWIPT system design.
+On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the joint design of waveform, active and passive beamforming accounting for rectenna nonlinearity.
 
@@
 Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
-On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner.
-Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
+On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner.
+Numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
 
-			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture.
-It is confirmed that the observations for SWIPT carry on to IRS-aided SWIPT.
-For example, a dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively.
-Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
+			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture.
+			% Note also that the joint waveform and beamforming design and optimization (and its potential performance benefits) in IRS-aided SWIPT differs from that in SWIPT (as in \cite{Clerckx2018b,Varasteh2019d}) due to the hardware constraint that the IRS elements should be frequency-flat.
+			Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design.
+We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT.
+Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal behavior, 2) the number of transmit antenna and IRS elements have no noticeable impact on the transceiving mode, 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflect elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) the adaptive (i.e.
+rate-dependent) passive beamforming is required for broadband transmission, 6) the performance loss by the frequency-flat constraint of IRS is negligible for narrowband transmission.
+
+			% Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
 Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model.
@@
 
-		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$).
-Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design.
-A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged.
-Two practical co-located receiver architectures are compared in terms of the R-E region.
+		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands at frequency $f_n$ ($n=1,\dots,N$).
+We consider a quasi-static block fading channel model and focus on one particular block where the channel responses are constant.
+It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP.
+Two practical co-located receiver architectures, namely TS and PS, are compared in terms of the R-E region.
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
 In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design.
-Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by the IRS for two and more times are omitted.
-We also assume the noise power is too small to be harvested.
+Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.
 
@@
 Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
-The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
+The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
 On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
-With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
+With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
 We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain.
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that, different from the active AF relay that achieves optimal performance when developed around the midpoint, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay that achieves optimal performance when developed around the midpoint \cite{Li2017}, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
 It origins from the product-distance path loss model that applies to finite-size element reflection.
@@
 Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$.
+A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$.
 It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
@@
 To gain some insight into the IRS behavior, we compare the results above to ideal frequency-selective IRS and no IRS.
-In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design flexibility of $NL$.
+In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal Frequency-Selective (FS) IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design flexibility of $NL$.
 When there is only one transmit antenna, each FS reflector simply aligns the AP-IRS-user to the AP-user channel at all subbands, namely
@@
 Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures.
-Efficient algorithms based on GP, SCA, SDR and AO techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
+Efficient algorithms based on the GP, SCA, SDR and AO techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
 We confirm that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
@@
 		The combination of IRS and SWIPT brings many possibilities and challenges.
-For example, how to optimize waveform, active and passive beamforming in a multiuser SWIPT system?
+For example, how to optimize waveform, active and passive beamforming in a multi-user SWIPT system?
 How can multiple IRS cooperate with each other to further benefit the R-E tradeoff?

### 2020-11-23 main.tex
:pencil: Rephrase system model

@@
 It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP.
-Two practical co-located receiver architectures, namely TS and PS, are compared in terms of the R-E region.
+As two practical transceiving modes, TS and PS are compared in terms of the achievable R-E region.
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
@@
 		\begin{subsection}{Transmit Signal}
-			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$.
+			Denote $\tilde{x}_{\text{I,}n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\text{I,}n}\sim\mathcal{CN}(0,1)$.
 The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
 			\begin{equation}\label{eq:x_m}
-				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\text{I,}n,m}\tilde{x}_{\text{I,}n}(t)}+w_{\text{P,}n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 			\end{equation}
-			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$.
-
-			Stacking up the entries on all antennas, we define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t)=\boldsymbol{x}_{I}(t)+\boldsymbol{x}_{P}(t)$, where
+			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
+Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq \boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t)$, where
 			\begin{align}
-				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
-				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
+				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
+				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
 			\end{align}
@@
 		\begin{subsection}{Composite Channel}
-			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
-Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
+			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
 The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
@@
 			\begin{equation}\label{eq:h_n}
-				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
+				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{h}_{\text{R,}n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\text{I,}n} = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
 			\end{equation}
-			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$.
+			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\text{R,}n}^H)\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$.
 Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
@@
 Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
-				% At subband $n$, the AP-IRS MIMO channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element.
-Reflection coefficient $\phi_l$ is shared for the $l$-th AP-IRS MISO channel of all subbands, namely $MN$ entries in total.
-				The reflection coefficient of each IRS element is shared for the AP-IRS MISO channel and over all subbands, namely $MN$ entries in total.
+For each IRS element, the reflection coefficient is shared by $M$ AP-IRS-user channels over $N$ subbands.
 			\end{remark}
@@
 		\begin{subsection}{Receive Signal}
-			At the single-antenna receiver, the total received signal $y(t)=y_I(t)+y_P(t)$ captures the contribution from information and power components over $N$ subbands, where
+			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\text{I}}(t)+y_\text{P}(t)$ captures the contribution from information and power components over all subbands, where
 			\begin{align}
-				y_{I}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
-				y_{P}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
+				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
+				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
 			\end{align}
@@
 			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
+				R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n} \rvert^2}{\sigma_n^2}\right)}
 			\end{equation}
@@
 							\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_s$] (0,2);
+							\draw (0,0) to [sV=$v_{\text{S}}$] (0,2);
 							\draw (0,2) to [short] (1,2);
@@
 							\draw (0,2) to [short] (0.25,2);
-							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
+							\draw (0.25,2) to [D, v<=$v_{\text{D}}$, i=$i_{\text{D}}$] (2.25,2);
 							\draw (2.25,2) to [short, -*] (2.5,2);
@@
 							\draw (2.5,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
+							\draw (4,2) to [R=$R_\text{L}$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
 							\draw (4,0) to [short] (2,0) node[ground](GND){};
@@
 				\end{minipage}
-				\caption{Rectenna circuits.}
+				\caption{Receive antenna and energy harvester circuits.}
 			\end{figure}
 
-			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform \cite{Clerckx2016a,Clerckx2018b}.
-Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of a lossless antenna, where the incoming signal creates an voltage source $v_s(t)$ and the antenna has an impedance $R_{\text{ant}}$.
-Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across matching network is negligible.
+			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform.
+Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\text{ant}}$ and the incoming signal creates an voltage source $v_{\text{S}}(t)$.
+Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
 When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$), the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.
@@
 Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-Denote $i_s$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_t$ as the thermal voltage, $v_d(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
-A Taylor expansion of the diode characteristic equation $i_d(t)=i_s(e^{v_d(t)/n' v_t}-1)$ around a quiescent operating point $a$ writes as $i_d(t)=\sum_{i=0}^{\infty}k_i'(v_d(t)-a)^i$, where $k_0'=i_s(e^{a/n' v_t}-1)$ and $k_i'=i_se^{a/n'v_t}/i!(n'v_t)^i$ for $i=1,\dots,\infty$.
+As detailed in \cite{Clerckx2016a,Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+			\begin{equation}\label{eq:z}
+				z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
+			\end{equation}
+			where $n_0$ is the truncation order and $k_i \triangleq i_{\text{S}}/i!(n'v_{\text{T}})^i$ is the diode coefficient ($i_{\text{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\text{T}}$ is the thermal voltage).
+With a slight abuse of notation, we refer to $z$ as the average output DC current in the following context.
+It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
+In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity and define $\beta_2 \triangleq {k_2}{R_{\text{ant}}}$, $\beta_4 \triangleq {k_4}{R_{\text{ant}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+Inspired by \cite{Huang2017}, we stack up the channel and waveform vectors over all subbands as $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\text{I/P}} \triangleq [\boldsymbol{w}_{\text{I/P,}1}^T,\dots,\boldsymbol{w}_{\text{I/P,}N}^T]^T \in \mathbb{C}^{MN \times 1}$, then define $\boldsymbol{W}_{\text{I/P}} \triangleq \boldsymbol{w}_{\text{I/P}}\boldsymbol{w}_{\text{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+
+			% Denote $i_{\text{S}}$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_{\text{T}}$ as the thermal voltage, $v_{\text{D}}(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
+A Taylor expansion of the diode characteristic equation $i_{\text{D}}(t)=i_{\text{S}}(e^{v_{\text{D}}(t)/n' v_{\text{T}}}-1)$ around a quiescent operating point $a$ writes as $i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'(v_{\text{D}}(t)-a)^i$, where $k_0'=i_{\text{S}}(e^{a/n' v_{\text{T}}}-1)$ and $k_i'=i_{\text{S}}e^{a/n'v_{\text{T}}}/i!(n'v_{\text{T}})^i$ for $i=1,\dots,\infty$.
 Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
 Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}.
-Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_d(t)\}=-v_{\text{out}}$ such that
-			\begin{equation}\label{eq:i_d}
-				i_d(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
-			\end{equation}
-			By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as
-			\begin{equation}\label{eq:i_out}
-				i_{\text{out}}(t)=\mathcal{A}\{i_d(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
-			\end{equation}
-			With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output.
+Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_{\text{D}}(t)\}=-v_{\text{out}}$ such that
+			% \begin{equation}\label{eq:i_D}
+			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
+			% \end{equation}
+			% By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_D} to the $n_0$-th order, we approximate the average output DC current for a given channel as
+			% \begin{equation}\label{eq:i_out}
+			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
+			% \end{equation}
+			% With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output.
 However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
-			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
-			\end{equation}
-			where $k_i=i_s/i!(nv_t)^i$.
+			% \begin{equation}\label{eq:z}
+			% 	z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
+			% \end{equation}
+			% where $k_i=i_{\text{S}}/i!(nv_{\text{T}})^i$.
 It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
@@
 For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{I,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-On top of this, let $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{I/P}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{I/P,k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+Note that $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\text{I/P}}=[\boldsymbol{w}_{\text{I/P,}1}^T,\dots,\boldsymbol{w}_{\text{I/P,}N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+On top of this, let $\boldsymbol{W}_{\text{I/P}}=\boldsymbol{w}_{\text{I/P}}\boldsymbol{w}_{\text{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
 Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
@@
 				\begin{equation*}
-						\boldsymbol{W}_{I/P}=
+						\boldsymbol{W}_{\text{I/P}}=
 						\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
@@
 							{
-								\boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,2}^H & \dots & \boldsymbol{w}_{I/P,1}\boldsymbol{w}_{I/P,N}^H \\
-								\boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,1}^H & \boldsymbol{w}_{I/P,2}\boldsymbol{w}_{I/P,2}^H & \ddots & \vdots \\
-								\vdots & \ddots & \ddots & \boldsymbol{w}_{I/P,N-1}\boldsymbol{w}_{I/P,N}^H \\
-								\boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,1}^H & \dots & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N-1}^H & \boldsymbol{w}_{I/P,N}\boldsymbol{w}_{I/P,N}^H \\
+								\boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}1}^H & \boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}2}^H & \dots & \boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}N}^H \\
+								\boldsymbol{w}_{\text{I/P,}2}\boldsymbol{w}_{\text{I/P,}1}^H & \boldsymbol{w}_{\text{I/P,}2}\boldsymbol{w}_{\text{I/P,}2}^H & \ddots & \vdots \\
+								\vdots & \ddots & \ddots & \boldsymbol{w}_{\text{I/P,}N-1}\boldsymbol{w}_{\text{I/P,}N}^H \\
+								\boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}1}^H & \dots & \boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}N-1}^H & \boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}N}^H \\
 							};
@@
 				\end{equation*}
-				\caption{$\boldsymbol{W}_{I/P}$ consists of $N \times N$ blocks of size $M \times M$.
-$\boldsymbol{W}_{I/P,k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{I/P}$ and nulls all remaining blocks.
+				\caption{$\boldsymbol{W}_{\text{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
+$\boldsymbol{W}_{\text{I/P,}k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\text{I/P}}$ and nulls all remaining blocks.
 Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
-For $\boldsymbol{w}_{I/P,n_1}\boldsymbol{w}_{I/P,n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+For $\boldsymbol{w}_{\text{I/P,}n_1}\boldsymbol{w}_{\text{I/P,}n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
 				\label{fi:block_diagonal}
@@
 				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
 				\end{equation}
@@
 				\begin{flalign}
-					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
-					\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
+					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
+					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
 				\end{flalign}
 				\begin{align}
-					\mathcal{A}\left\{y_{P}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\,,\label{eq:y_P2}\\
-					\mathcal{A}\left\{y_{P}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,k}\boldsymbol{h})^H\,.\label{eq:y_P4}
+					\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h}\,,\label{eq:y_P2}\\
+					\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H\,.\label{eq:y_P4}
 				\end{align}
@@
 				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right) \le P\biggr\}
+				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right) \le P\biggr\}
 			\end{align}
@@
 		\begin{maxi!}
-			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
+			{\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)}{\label{op:original}}{\label{ob:original}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right)\le{P}}\label{co:original_power}
+			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) \ge \bar{R}}\label{co:original_rate}
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
@@
 		\begin{subsection}{IRS Phase Shift}
-			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
+			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{\text{I/P}}$ and splitting ratio $\rho$. We observe that
 			\begin{align}
-				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2
-				& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\nonumber\\
-				& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\nonumber\\
-				& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
+				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n} \rvert^2
+				& = \boldsymbol{w}_{\text{I,}n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}\nonumber\\
+				& = \boldsymbol{w}_{\text{I,}n}^H(\boldsymbol{h}_{\text{D,}n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\text{D,}n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\text{I,}n}\nonumber\\
+				& = \boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
 				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
 			\end{align}
-			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On the other hand, we define $t_{I/P,k}$ as
+			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On the other hand, we define $t_{\text{I/P,}k}$ as
 			\begin{align}
-				t_{I/P,k}
-				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,k})\nonumber\\
-				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,k}\right)\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,k})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,k}\boldsymbol{\Phi})
+				t_{\text{I/P,}k}
+				& = \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k})\nonumber\\
+				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\text{I/P,}k}\right)\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{C}_{\text{I/P,}k}\boldsymbol{\Phi})
 			\end{align}
-			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,k}=\boldsymbol{M}\boldsymbol{W}_{I/P,k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k}=\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 Therefore, we rewrite the rate and objective expressions as
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{k=-N+1}^{N-1}{t_{P,k}t_{P,k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}\,.\label{eq:z_irs}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\text{I,}0}+t_{\text{P,}0})\nonumber\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\text{I,}0}^2 + \sum_{k=-N+1}^{N-1}{t_{\text{P,}k}t_{\text{P,}k}^*}\right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}\,.\label{eq:z_irs}
 			\end{align}
@@
 			\begin{align}
-				(t_{I,0}^{(i)})^2
-				& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\,,\label{eq:taylor_1}\\
-				t_{P,k}^{(i)} (t_{P,k}^{(i)})^*
-				& \ge 2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*\,,\label{eq:taylor_2}\\
-				t_{I,0}^{(i)} t_{P,0}^{(i)}
-				& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:taylor_3}
+				(t_{\text{I,}0}^{(i)})^2
+				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2\,,\label{eq:taylor_1}\\
+				t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i)})^*
+				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*\,,\label{eq:taylor_2}\\
+				t_{\text{I,}0}^{(i)} t_{\text{P,}0}^{(i)}
+				& = \frac{1}{4}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\nonumber\\
+				& \ge \frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\label{eq:taylor_3}
 			\end{align}
@@
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{P,k}^{(i)} (t_{P,k}^{(i-1)})^*\right\} - t_{P,k}^{(i-1)} (t_{P,k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}
+					& = \frac{1}{2}{\beta_2}{\rho}(t_{\text{I,}0}^{(i)}+t_{\text{P,}0}^{(i)})\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{\text{I,}0}^{(i)})(t_{\text{I,}0}^{(i-1)}) - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}
 				\end{align}
@@
 In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations such that the performance loss by SDR is insignificant.
-Problem~\eqref{op:irs} without constraint \ref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
 
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
-					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$, $\boldsymbol{C}_{I/P,k}$, $\forall n,k$
-					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,k}^{(0)}, \forall k$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho,\sigma_n,\bar{R},Q,\epsilon$
+					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\text{I/P,}k}$, $\forall n,k$
+					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\text{I/P,}k}^{(0)}, \forall k$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,k}^{(i)}$ by solving problem~\eqref{op:irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{\text{I/P,}k}^{(i)}$ by solving problem~\eqref{op:irs}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize both information and power waveforms $\boldsymbol{w}_{I/P}$ together with splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
+			Next, we jointly optimize both information and power waveforms $\boldsymbol{w}_{\text{I/P}}$ together with splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
 As pointed out in \cite{Clerckx2018b}, the waveform design in frequency and spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
 			\begin{equation}\label{eq:w_IP}
-				\boldsymbol{w}_{I/P,n}=s_{I/P,n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}\,.
+				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}\,.
 			\end{equation}
-			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{I/P,n}$ at different tones.
+			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{\text{I/P,}n}$ at different tones.
 Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
-Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$.
-At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
+Let $\boldsymbol{s}_{\text{I/P}}=[s_{\text{I/P,}1},\dots,s_{\text{I/P,}N}]^T \in \mathbb{C}^{N \times 1}$.
+At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\text{I,}n}^2$ and $s_{\text{P},n}^2$, respectively.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{\text{I,}n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
 			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_I,\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}\biggr)\right)\,.
+				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right)\,.
 			\end{equation}
@@
 				\begin{align}
-					z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{I,n}^2+s_{P,n}^2)\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{I,{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{P,{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{I,{n_1}}^2 s_{P,{n_2}}^2 \right)\,.\label{eq:z_waveform}
+					z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)
+					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\text{I,}n}^2+s_{\text{P},n}^2)\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\text{I,}{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\text{P,}{n_j}} \right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right)\,.\label{eq:z_waveform}
 				\end{align}
@@
 			\begin{maxi!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\label{op:waveform}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right)\le{P}}
-				\addConstraint{R(\boldsymbol{s}_I,\rho) \ge \bar{R}\,.}
+				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho}{z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}{\label{op:waveform}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right)\le{P}}
+				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}\,.}
 			\end{maxi!}
@@
 			\begin{mini!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}\label{co:waveform_objective}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right) \le P}\label{co:waveform_power}
+				\addConstraint{\frac{t'}{z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)} \le 1}\label{co:waveform_objective}
+				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
 				\addConstraint{\rho + \bar{\rho} \le 1\,.}
@@
 			\begin{align}
-				z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)&=\sum_{m_P}{g_{m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\label{eq:posynomial_objective}\,,\\
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{I,n}^2}{\sigma_n^2}&=\sum_{m_{I,n}}g_{m_{I,n}}(s_{I,n},\bar{\rho})\label{eq:posynomial_rate}
+				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)&=\sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective}\,,\\
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}&=\sum_{m_{\text{I,}n}}g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})\label{eq:posynomial_rate}
 			\end{align}
-			where $m_P=(2N^3+6N^2+7N)/3$, $m_{I,n}=2$ are the number of monomials.
+			where $m_\text{P}=(2N^3+6N^2+7N)/3$, $m_{\text{I,}n}=2$ are the number of monomials.
 Following \cite{Chiang2005}, we upper bound posynomials \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\eqref{op:waveform_rgp} reduces to
 			\begin{mini!}
-				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_I}\rVert^2+\lVert{\boldsymbol{s}_P}\rVert^2\right)\le{P}}
-				\addConstraint{{t'}\prod_{m_P}{\left(\frac{g_{{m_P}}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{{m_P}}}\right)^{-\gamma_{{m_P}}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{I,n}}\left(\frac{g_{m_{I,n}}(s_{I,n},\bar{\rho})}{\gamma_{m_{I,n}}}\right)^{-\gamma_{m_{I,n}}}\le{1}}
+				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right)\le{P}}
+				\addConstraint{{t'}\prod_{m_\text{P}}{\left(\frac{g_{{m_\text{P}}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}{\gamma_{{m_\text{P}}}}\right)^{-\gamma_{{m_\text{P}}}}}\le{1}}
+				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\text{I,}n}}\left(\frac{g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})}{\gamma_{m_{\text{I,}n}}}\right)^{-\gamma_{m_{\text{I,}n}}}\le{1}}
 				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{mini!}
-			where $\gamma_{m_P},\gamma_{m_{I,n}} \ge 0$, $\sum_{m_P}\gamma_{m_P}=\sum_{m_{I,n}}\gamma_{m_{I,n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_P},\gamma_{m_{I,n}}\}$ that require successive update.
+			where $\gamma_{m_\text{P}},\gamma_{m_{\text{I,}n}} \ge 0$, $\sum_{m_\text{P}}\gamma_{m_\text{P}}=\sum_{m_{\text{I,}n}}\gamma_{m_{\text{I,}n}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_\text{P}},\gamma_{m_{\text{I,}n}}\}$ that require successive update.
 As suggested in \cite{Clerckx2018b}, a feasible choice at iteration $i$ is
 			\begin{align}
-				\gamma_{m_P}^{(i)} & = \frac{g_{m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\,,\\
-				\gamma_{m_{I,n}}^{(i)} & = \frac{g_{m_{I,n}}(s_{I,n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{I,n}^{(i-1)})^2}\big/{\sigma_n^2}}\,.\label{eq:gamma_I}
+				\gamma_{m_\text{P}}^{(i)} & = \frac{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\,,\\
+				\gamma_{m_{\text{I,}n}}^{(i)} & = \frac{g_{m_{\text{I,}n}}(s_{\text{I,}n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\text{I,}n}^{(i-1)})^2}\big/{\sigma_n^2}}\,.\label{eq:gamma_I}
 			\end{align}
 			Problem~\eqref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
-$\boldsymbol{s}_I,\boldsymbol{s}_P,\rho$ are updated iteratively until convergence.
+$\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho$ are updated iteratively until convergence.
 The GP algorithm of waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
@@
 					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$
-					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{s}_{I/P}^{(0)}$, $\rho^{(0)}$
+					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{s}_{\text{I/P}}^{(0)}$, $\rho^{(0)}$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_P}^{(i)},\gamma_{m_{I,n}}^{(i)}\}$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
-						\State Obtain $\boldsymbol{s}_{I/P}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+						\State Update $\{\gamma_{m_\text{P}}^{(i)},\gamma_{m_{\text{I,}n}}^{(i)}\}$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
+						\State Obtain $\boldsymbol{s}_{\text{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{I/P}^{\star}=\boldsymbol{s}_{I/P}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{I/P}^{\star}$ by \eqref{eq:w_IP}
-					\State \textbf{output} $\boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
+					\State Set $\boldsymbol{s}_{\text{I/P}}^{\star}=\boldsymbol{s}_{\text{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\text{I/P}}^{\star}$ by \eqref{eq:w_IP}
+					\State \textbf{output} $\boldsymbol{w}_{\text{I/P}}^{\star}, \rho^{\star}$
 				\end{algorithmic}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
-					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},P,\sigma_n,\bar{R},Q,\epsilon$
+					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{\text{I/P}}^{(0)},\rho^{(0)}$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
-						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \eqref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
+						\State Fix $\boldsymbol{w}_{\text{I/P}}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
+						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \eqref{eq:h_n}, and obtain $\boldsymbol{w}_{\text{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
+					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{\text{I/P}}^{\star}, \rho^{\star}$
 				\end{algorithmic}
@@
 			\begin{proposition}\label{pr:ao}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\text{I}}^{\star},\boldsymbol{w}_\text{P}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ has limit points so that Algorithm~\ref{al:alternating} is guaranteed to converge.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\text{I}}^{(i)},\boldsymbol{w}_\text{P}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho$ has limit points so that Algorithm~\ref{al:alternating} is guaranteed to converge.
 As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
@@
 As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively.
-We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$.
-We choose as reference $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
+We also denote $d_\text{D}$, $d_{\text{I}}$, $d_R$ as the length of direct, incident, reflective paths such that $d_{\text{I}}=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_\text{D}-d_H)^2+d_V^2}$.
+We choose as reference $d_\text{D}=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
 The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
@@
 \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy.
-The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_\text{P}$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
 Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
@@
 Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$.
+A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\text{I}}\Lambda_R$.
 It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
@@
 The reason is that the system performance in our setup is dominated by the AP-user direct link, with the optimal active beamformer obtained in closed form.
-As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_D$ is around \SI{60}{\dB} while the extra path loss product $\Lambda_I\Lambda_R$ is over \SI{100}{\dB}.
+As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_\text{D}$ is around \SI{60}{\dB} while the extra path loss product $\Lambda_{\text{I}}\Lambda_R$ is over \SI{100}{\dB}.
 Therefore, although increasing $L$ can significantly enhance the AP-IRS-user auxiliary channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
@@
 		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{D,n}/h_{I,n,l}h_{R,n,l}\right)}}\,,\quad \forall n,l\,.
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\text{D,}n}/h_{\text{I,}n,l}h_{\text{R,}n,l}\right)}}\,,\quad \forall n,l\,.
 		\end{equation}

### 2020-11-23 main.tex
:pencil: Rephrase passive beamforming

@@
 The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints.
-Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence.
+Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence.
 On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner.
@@
 			\begin{align}
-				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
-				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
+				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
+				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}.\label{eq:x_P}
 			\end{align}
@@
 			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
 Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
@@
 			\begin{align}
-				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
-				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
+				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
+				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}.\label{eq:y_P}
 			\end{align}
@@
 			% \begin{equation}\label{eq:i_D}
-			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.
+			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i.
 			% \end{equation}
@@
 			% \begin{equation}\label{eq:i_out}
-			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.
+			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}.
 			% \end{equation}
@@
 				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
 				\end{equation}
@@
 					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h},&&\label{eq:y_I2}\\
 					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2,&&\label{eq:y_I4}
 				\end{flalign}
-				\begin{align}
+				\begin{flalign}
 					\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h}\,,\label{eq:y_P2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h},&&\label{eq:y_P2}\\
 					\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H\,.\label{eq:y_P4}
-				\end{align}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H.&&\label{eq:y_P4}
+				\end{flalign}
 			\end{figure*}
@@
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
-			\addConstraint{0 \le \rho \le 1\,.}
+			\addConstraint{0 \le \rho \le 1.}
 		\end{maxi!}
-		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex.
-To achieve a feasible solution, we propose an AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shifts at the IRS, and the power splitting ratio at the receiver, until convergence.
+		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}.
+To obtain a feasible solution, we propose an AO algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence.
 		\begin{remark}\label{re:irs_subchannel_alignment}
@@
 			\end{align}
-			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 On the other hand, we define $t_{\text{I/P,}k}$ as
@@
 				t_{\text{I/P,}k}
-				& = \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\
+				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\
 				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k})\nonumber\\
@@
 			\end{align}
-			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k}=\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 Therefore, we rewrite the rate and objective expressions as
@@
 				R(\boldsymbol{\Phi})
-				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\,,\label{eq:R_irs}\\
+				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
 				z(\boldsymbol{\Phi})
@@
 				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\text{I,}0}^2 + \sum_{k=-N+1}^{N-1}{t_{\text{P,}k}t_{\text{P,}k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}\,.\label{eq:z_irs}
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}.\label{eq:z_irs}
 			\end{align}
-			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}.
+			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by their first-order Taylor expansion \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 				(t_{\text{I,}0}^{(i)})^2
-				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2\,,\label{eq:taylor_1}\\
+				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2,\label{eq:taylor_1}\\
 				t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i)})^*
-				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*\,,\label{eq:taylor_2}\\
+				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*,\label{eq:taylor_2}\\
 				t_{\text{I,}0}^{(i)} t_{\text{P,}0}^{(i)}
@@
 			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}.
-Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to
+Hence, the objective function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to
 			\begin{figure*}[b]
@@
 					& = \frac{1}{2}{\beta_2}{\rho}(t_{\text{I,}0}^{(i)}+t_{\text{P,}0}^{(i)})\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{\text{I,}0}^{(i)})(t_{\text{I,}0}^{(i-1)}) - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right).\label{eq:z_irs_approx}
 				\end{align}
@@
 				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\,.\label{co:irs_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
 			\end{maxi!}
 			Problem~\eqref{op:irs} is not a standard Semidefinite Programming (SDP).
-If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, and the optimal rank-\num{1} solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\eqref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations such that the performance loss by SDR is insignificant.
-Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
-
-			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
+If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the optimal rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\eqref{op:original}.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, and the performance loss by SDR is insignificant.
+When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\boldsymbol{\phi}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
 Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
@@
 Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
-The SCA algorithm for passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
+Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+The SCA algorithm for the passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
 			\begin{algorithm}[!t]
@@
 
-		\begin{subsection}{Waveform and Splitting Ratio}
+		\begin{subsection}{Waveform, Active Beamforming and Splitting Ratio}
 			Next, we jointly optimize both information and power waveforms $\boldsymbol{w}_{\text{I/P}}$ together with splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
@@
 			\begin{equation}\label{eq:w_IP}
-				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}\,.
+				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
 			\end{equation}
@@
 			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right)\,.
+				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right).
 			\end{equation}
@@
 					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\text{I,}{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\text{P,}{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right)\,.\label{eq:z_waveform}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right).\label{eq:z_waveform}
 				\end{align}
@@
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right)\le{P}}
-				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}\,.}
+				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}.}
 			\end{maxi!}
@@
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
-				\addConstraint{\rho + \bar{\rho} \le 1\,.}
+				\addConstraint{\rho + \bar{\rho} \le 1.}
 			\end{mini!}
@@
 			\begin{align}
-				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)&=\sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective}\,,\\
+				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)&=\sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective},\\
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}&=\sum_{m_{\text{I,}n}}g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})\label{eq:posynomial_rate}
@@
 			\begin{align}
-				\gamma_{m_\text{P}}^{(i)} & = \frac{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}\,,\\
-				\gamma_{m_{\text{I,}n}}^{(i)} & = \frac{g_{m_{\text{I,}n}}(s_{\text{I,}n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\text{I,}n}^{(i-1)})^2}\big/{\sigma_n^2}}\,.\label{eq:gamma_I}
+				\gamma_{m_\text{P}}^{(i)} & = \frac{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P},\\
+				\gamma_{m_{\text{I,}n}}^{(i)} & = \frac{g_{m_{\text{I,}n}}(s_{\text{I,}n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\text{I,}n}^{(i-1)})^2}\big/{\sigma_n^2}}.\label{eq:gamma_I}
 			\end{align}
@@
 		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\text{D,}n}/h_{\text{I,}n,l}h_{\text{R,}n,l}\right)}}\,,\quad \forall n,l\,.
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\text{D,}n}/h_{\text{I,}n,l}h_{\text{R,}n,l}\right)}},\quad \forall n,l.
 		\end{equation}

### 2020-11-24 main.tex
:art: Revise manuscript

@@
 
-% reflection coefficients vs reflector vs reflection element
-
 \begin{document}
-	%\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
-	%\title{Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer: Joint Waveform, Active and Passive Beamforming Design}
-	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer}
-	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided SWIPT}
 	\title{Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
@@
 To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain.
-This paper investigates an effective IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
+This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
 Considering the energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
@@
 Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
+Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2013} to characterize the R-E region for multi-antenna broadcast and interference channels.
 On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the input rectifier power and waveform shape.
 It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT.
 Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}.
@@
 Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}, which uniquely showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: "what is the optimal input distribution for SWIPT under nonlinearity?
-".
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: \textit{What is the optimal input distribution for SWIPT under nonlinearity?}
+			% quotation mark removed, ref: https://english.stackexchange.com/questions/21795/punctuation-with-the-question-is-or
 			This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
@@
 The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-Moreover, \cite{Abeywickrama2019} investigated the coupling effect of reflection amplitude and phase shift based on impedance equation, and \cite{Nadeem2019} proposed a sequential cascaded channel estimation for Time-Division Duplex (TDD) systems.
-%To reduce the estimation overhead and design complexity, \cite{Yang2019} considered a group-based IRS model where adjacent elements share a common reflection coefficient.
-			A novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems was proposed in \cite{Yang2020}, which varies the reflection coefficients over consequent slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
+Moreover, \cite{Abeywickrama2019} investigated the coupling effect between reflection amplitude and phase shift based on the impedance equation, and \cite{Nadeem2019} proposed a sequential cascaded channel estimation for Time-Division Duplex (TDD) systems.	A novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems was proposed in \cite{Yang2020}, which varies the reflection coefficients over consequent slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT.
-For a multi-user IRS-aided SWIPT system, dedicated energy beams are unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power.
-In such cases, the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers.
+For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power, where the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers.
 However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
 In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.
-We ask ourselves the important question: "How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?
-" The contributions of the paper are listed as follows.
+We ask ourselves the important question: \textit{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?} The contributions of the paper are listed as follows.
 
@@
 			% Note also that the joint waveform and beamforming design and optimization (and its potential performance benefits) in IRS-aided SWIPT differs from that in SWIPT (as in \cite{Clerckx2018b,Varasteh2019d}) due to the hardware constraint that the IRS elements should be frequency-flat.
-			Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design.
+			Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency-flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design.
 We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT.
-Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal behavior, 2) the number of transmit antenna and IRS elements have no noticeable impact on the transceiving mode, 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflect elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) the adaptive (i.e.
-rate-dependent) passive beamforming is required for broadband transmission, 6) the performance loss by the frequency-flat constraint of IRS is negligible for narrowband transmission.
-
-			% Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy.
-Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model.
-It implies that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems.
-For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power.
-For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power.
-Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.
+Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) the performance loss by the frequency-flat constraint of IRS is negligible for narrowband transmission, 6) the adaptive (i.e.
+rate-dependent) passive beamforming is required for broadband transmission.
 
@@
 The distribution of a CSCG random vector with mean vector $\boldsymbol{0}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$, and $\sim$ stands for "distributed as".
-We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
+We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as the stationary solution and the solution at iteration $i$, respectively.
 		\end{subsection}
@@
 			\centering
-			\def\svgwidth{\columnwidth}
+			\def\svgwidth{0.9\columnwidth}
 			\import{assets/}{system.pdf_tex}
@@
 It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP.
-As two practical transceiving modes, TS and PS are compared in terms of the achievable R-E region.
+Two practical transceiving modes, TS and PS, are compared in terms of the achievable R-E region.
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design.
+In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with the waveform and beamforming design.
 Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.
@@
 			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
-Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq \boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t)$, where
+Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T=\boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t) \in \mathbb{C}^{M \times 1}$, where
 			\begin{align}
@@
 			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
+At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1$, $\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
 Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
-The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
-On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
+The auxiliary link introduced by the IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
+On top of this, the total composite channel is obtained by superposing the AP-IRS-user auxiliary channel to the AP-user direct channel as
 			\begin{equation}\label{eq:h_n}
@@
 Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
-For each IRS element, the reflection coefficient is shared by $M$ AP-IRS-user channels over $N$ subbands.
+The reflection coefficient of each IRS element is shared by the corresponding $M$ AP-IRS-user channels over $N$ subbands.
 			\end{remark}
@@
 				\noindent
-				\begin{minipage}[b]{0.5\linewidth}
+				\begin{minipage}[b]{0.45\columnwidth}
 					\centering
 					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
-						\resizebox{0.9\linewidth}{!}{
+						\resizebox{\columnwidth}{!}{
 							\begin{circuitikz}[transform shape]
@@
 				\end{minipage}%
-				\begin{minipage}[b]{0.5\linewidth}
+				\begin{minipage}[b]{0.45\columnwidth}
 					\centering
 					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
-						\resizebox{0.9\linewidth}{!}{
+						\resizebox{\columnwidth}{!}{
 							\begin{circuitikz}[transform shape]
@@
 Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2016a,Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2016a,Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the non-linear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
-Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
-
-			% Denote $i_{\text{S}}$ as the reverse bias saturation current, $n'$ as the diode ideality factor, $v_{\text{T}}$ as the thermal voltage, $v_{\text{D}}(t)=v_{\text{in}}(t)-v_{\text{out}}(t)$ as the voltage across the diode where $v_{\text{out}}(t)$ is the output voltage across the load.
-A Taylor expansion of the diode characteristic equation $i_{\text{D}}(t)=i_{\text{S}}(e^{v_{\text{D}}(t)/n' v_{\text{T}}}-1)$ around a quiescent operating point $a$ writes as $i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'(v_{\text{D}}(t)-a)^i$, where $k_0'=i_{\text{S}}(e^{a/n' v_{\text{T}}}-1)$ and $k_i'=i_{\text{S}}e^{a/n'v_{\text{T}}}/i!(n'v_{\text{T}})^i$ for $i=1,\dots,\infty$.
-Note that this small-signal expansion model is only valid for the non-linear operation region, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.
-Also, an ideal low-pass filter with steady-state response can provide a constant $v_{\text{out}}$ that depends on the peak of $v_{\text{in}}(t)$ \cite{Curty2005}.
-Therefore, a proper choice of the operating voltage drop is $a=\mathcal{E}\{v_{\text{D}}(t)\}=-v_{\text{out}}$ such that
-			% \begin{equation}\label{eq:i_D}
-			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i.
-			% \end{equation}
-			% By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_D} to the $n_0$-th order, we approximate the average output DC current for a given channel as
-			% \begin{equation}\label{eq:i_out}
-			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}.
-			% \end{equation}
-			% With the assumption of evenly-spaced frequencies, it holds that $\mathcal{A}\left\{y(t)^i\right\}=0$ for odd $i$ thus the related terms have no contribution to DC output.
-However, $k_i'$ is still a function of $i_{\text{out}}$, and \cite{Clerckx2016a} proved that maximizing a truncated $i_{\text{out}}$ is equivalent to maximizing a monotonic function
-			% \begin{equation}\label{eq:z}
-			% 	z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
-			% \end{equation}
-			% where $k_i=i_{\text{S}}/i!(nv_{\text{T}})^i$.
-It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
-In other words, even-order terms with $i \ge 4$ account for the nonlinear behavior of the diode.
-For simplicity, we let $\beta_2={k_2}{R_{\text{ant}}}$, $\beta_4={k_4}{R_{\text{ant}}^2}$ and choose $n_0=4$ to investigate fundamental rectifier nonlinearity so that $z$ further reduces to \eqref{eq:z_expand}.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-Inspired by \cite{Huang2017}, we stack up channel and waveform vectors over all subbands as $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\text{I/P}}=[\boldsymbol{w}_{\text{I/P,}1}^T,\dots,\boldsymbol{w}_{\text{I/P,}N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-On top of this, let $\boldsymbol{W}_{\text{I/P}}=\boldsymbol{w}_{\text{I/P}}\boldsymbol{w}_{\text{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
-Hence, the components of the output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+Hence, the components of the average output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 
@@
 							\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
-
 						\end{tikzpicture}
@@
 			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
-Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands.
+Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands.
 In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
@@
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, we rewrite the rate and objective expressions as
+Therefore, we can rewrite the rate and average DC current expressions as
 			\begin{align}
@@
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}\label{co:irs_modulus}
+				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
 				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
@@
 			Problem~\eqref{op:irs} is not a standard Semidefinite Programming (SDP).
-If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the optimal rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ may not be a stationary point of the original problem~\eqref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, and the performance loss by SDR is insignificant.
-When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\boldsymbol{\phi}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
-Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
-Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}.
-Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$.
+If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the extracted rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ be a stationary point of the original problem~\eqref{op:original}.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, and the performance loss by SDR is negligible.
+If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the augmented phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
+Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}, where we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}.
+Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star), \ l=1,\dots,L$.
 Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho,\sigma_n,\bar{R},Q,\epsilon$
-					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\text{I/P,}k}$, $\forall n,k$
-					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\text{I/P,}k}^{(0)}, \forall k$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\text{I/P,}k}$, $\forall n,k$
+					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\text{I/P,}k}^{(0)}$, $\forall k$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{\text{I/P,}k}^{(i)}$ by solving problem~\eqref{op:irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)},t_{\text{I/P,}k}^{(i)}$, $\forall k$ by solving problem~\eqref{op:irs}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
-						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
-						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
-						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
+						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
+						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
+						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
 					\EndIf
-					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, and construct $\boldsymbol{\phi}^{\star}$
+					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
 					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
@@
 		\begin{subsection}{Waveform, Active Beamforming and Splitting Ratio}
-			Next, we jointly optimize both information and power waveforms $\boldsymbol{w}_{\text{I/P}}$ together with splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
-As pointed out in \cite{Clerckx2018b}, the waveform design in frequency and spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
+			Next, we jointly optimize the waveform and active beamforming $\boldsymbol{w}_{\text{I/P}}$ together with the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
+As pointed out in \cite{Clerckx2018b}, the waveform design in the frequency domain and the active beamformer in the spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
 			\begin{equation}\label{eq:w_IP}
@@
 			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{\text{I/P,}n}$ at different tones.
-Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
-Let $\boldsymbol{s}_{\text{I/P}}=[s_{\text{I/P,}1},\dots,s_{\text{I/P,}N}]^T \in \mathbb{C}^{N \times 1}$.
-At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\text{I,}n}^2$ and $s_{\text{P},n}^2$, respectively.
+Hence, the original waveform and active beamforming optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
+Define $\boldsymbol{s}_{\text{I/P}} \triangleq [s_{\text{I/P,}1},\dots,s_{\text{I/P,}N}]^T \in \mathbb{C}^{N \times 1}$.
+At subband $n$, the effective channel strength is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\text{I,}n}^2$ and $s_{\text{P},n}^2$, respectively.
 With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{\text{I,}n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
@@
 			\end{mini!}
-			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that are further decomposed as
+			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that can be further decomposed as
 			\begin{align}
-				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)&=\sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective},\\
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}&=\sum_{m_{\text{I,}n}}g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})\label{eq:posynomial_rate}
+				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho) &\triangleq \sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective},\\
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\text{I,}n}}g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})\label{eq:posynomial_rate}
 			\end{align}
@@
 			\end{align}
+			$\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho$ are updated iteratively until convergence.
 Problem~\eqref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
-$\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho$ are updated iteratively until convergence.
-The GP algorithm of waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
+The GP algorithm of the waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
 			\begin{algorithm}[!t]
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
 					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{s}_{\text{I/P}}^{(0)}$, $\rho^{(0)}$
@@
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_\text{P}}^{(i)},\gamma_{m_{\text{I,}n}}^{(i)}\}$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
+						\State Update $\{\gamma_{m_\text{P}}^{(i)},\gamma_{m_{\text{I,}n}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
 						\State Obtain $\boldsymbol{s}_{\text{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
@@
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\text{I/P}}^{\star}=\boldsymbol{s}_{\text{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\text{I/P}}^{\star}$ by \eqref{eq:w_IP}
+					\State Set $\boldsymbol{s}_{\text{I/P}}^{\star}=\boldsymbol{s}_{\text{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\text{I/P}}^{\star}$ by \eqref{eq:w_IP}
 					\State \textbf{output} $\boldsymbol{w}_{\text{I/P}}^{\star}, \rho^{\star}$
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs}, and waveform, active beamforming and splitting ratio by Algorithm~\ref{al:waveform} until convergence.
+			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\text{I/P}}$ together with splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
 The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
 			\begin{algorithm}[!t]
-				\caption{AO: Waveform, Active and Passive Beamforming.}
+				\caption{AO: Waveform, Active and Passive Beamforming, and Splitting Ratio.}
 				\label{al:alternating}
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},P,\sigma_n,\bar{R},Q,\epsilon$
+					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
 					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{\text{I/P}}^{(0)},\rho^{(0)}$
@@
 						\State Fix $\boldsymbol{w}_{\text{I/P}}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
-						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \eqref{eq:h_n}, and obtain $\boldsymbol{w}_{\text{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
+						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, obtain $\boldsymbol{w}_{\text{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 			\begin{proposition}\label{pr:waveform}
-				For any feasible initial point, the GP-based Algorithm~\ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.
+				For any feasible initial point, the GP-based Algorithm~\ref{al:waveform} is guaranteed to converge to a stationary point of the waveform, active beamforming and splitting ratio subproblem.
 			\end{proposition}
@@
 			\begin{proposition}\label{pr:ao}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\text{I}}^{\star},\boldsymbol{w}_\text{P}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\textnormal{I}}^{\star},\boldsymbol{w}_\textnormal{P}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\text{I}}^{(i)},\boldsymbol{w}_\text{P}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho$ has limit points so that Algorithm~\ref{al:alternating} is guaranteed to converge.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\text{I}}^{(i)},\boldsymbol{w}_\text{P}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho$ has limit points and Algorithm~\ref{al:alternating} is guaranteed to converge.
 As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
@@
 			\centering
-			\def\svgwidth{\columnwidth}
+			\def\svgwidth{0.9\columnwidth}
 			\import{assets/}{layout.pdf_tex}
@@
 		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups.
-Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$.
-As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively.
-We also denote $d_\text{D}$, $d_{\text{I}}$, $d_R$ as the length of direct, incident, reflective paths such that $d_{\text{I}}=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_\text{D}-d_H)^2+d_V^2}$.
-We choose as reference $d_\text{D}=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$.
-The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
+Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference.
+As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-user path and let $d_{\text{H}}$, $d_{\text{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
+We also denote $d_{\text{D}}$, $d_{\text{I}}$, $d_{\text{R}}$ as the length of direct, incident, reflective paths such that $d_{\text{I}}=\sqrt{d_{\text{H}}^2+d_{\text{V}}^2}$, $d_{\text{R}}=\sqrt{(d_{\text{D}}-d_{\text{H}})^2+d_{\text{V}}^2}$.
+$d_{\text{D}}=15\,\si{\meter}$, $d_{\text{V}}=2\,\si{\meter}$ and $d_{\text{H}}=2\,\si{\meter}$ are chosen as reference.
+The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
 We assume all channels are NLoS with taps modelled as i.i.d.
-CSCG random variables of unit average sum-power to create a normalized multipath response.
-The reference numbers of transmit antennas, IRS reflectors and subbands are $M=1$, $L=20$, $N=16$, respectively.
-No spatial correlation is considered across transmit antennas and IRS arrays.
-Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$.
-With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands.
-We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain.
-For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations.
+CSCG random variables of unit average sum-power, corresponding to a normalized multipath response.
+The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively.
+No spatial correlation is assumed across transmit antennas and IRS elements.
+Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
+With a \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference.
+We also assume a \SI{0}{\dBi} IRS element gain and a \SI{2}{\dBi} receive antenna gain.
+For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations.
 In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
@@
 		% - for single-carrier WPT, modulated waveform may be preferred as it has a modulation gain (also proved in Fig. 5)
-		On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only.
+		On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only.
 For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$.
@@
 		We first evaluate the performance of Algorithm~\ref{al:irs} under SDR.
-It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$.
-Therefore, $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\eqref{op:irs} without performance loss.
+It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and the Gaussian randomization step is not required.
+Therefore, we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\eqref{op:irs} without performance loss.
 
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_subband.tex}
 			\end{adjustbox}
-			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_subband}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/waveform_subband.tex}
 			\end{adjustbox}
-			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:waveform_subband}
@@
 \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy.
-The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_\text{P}$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
-Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain.
+The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\text{P}$ is increased to boost the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains.
 Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e.
-a time sharing between the WPT point and the tangent WIPT point obtained by PS.
-Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving strategy, both heavily depends on $N$.
+a time sharing between the WPT point and the tangent WIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
+Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on $N$.
 
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_noise.tex}
 			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_noise}
@@
 		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}.
-\textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level.
-Hence, TS is preferred at low SNR while PS is preferred at high SNR.
-This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to a few strongest subbands.
-As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested energy via the coupling effect by rectifier nonlinearity.
+\textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level while approximately convex for a low noise level.
+Hence, it can be concluded that TS is preferred at low SNR while PS is preferred at high SNR.
+This is because in the former case, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands.
+As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity.
 \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, as a small amplitude could be inefficient for energy maximization.
-On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of the multisine for efficient power transfer.
+The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small amplitude could be inefficient for energy maximization.
+On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer.
 The result highlights the benefit of multisine and the necessity of joint optimization of waveform and splitting ratio.
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_distance.tex}
 			\end{adjustbox}
-			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $d_{\text{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_distance}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/path_loss.tex}
@@
 
-		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$.
-A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay that achieves optimal performance when developed around the midpoint \cite{Li2017}, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff.
+		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\text{H}}$.
+A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay with the optimal development location around the midpoint \cite{Li2017}, placing the IRS closer to either the transmitter or the receiver would further improve the R-E tradeoff.
 It origins from the product-distance path loss model that applies to finite-size element reflection.
@@
 A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\text{I}}\Lambda_R$.
-It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
+It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the user.
 
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_tx.tex}
 			\end{adjustbox}
-			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_tx}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_reflector.tex}
 			\end{adjustbox}
-			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_reflector}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/scaling_tx.tex}
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\text{H}}=0$ and $d_{\text{V}}=0.5\,\si{\meter}$.}
 			\label{fi:scaling_tx}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/scaling_reflector.tex}
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\text{H}}=0$ and $d_{\text{V}}=0.5\,\si{\meter}$.}
 			\label{fi:scaling_reflector}
@@
 
-		The number of transmit antennas $M$ and IRS reflectors $L$ influence the average R-E tradeoff as revealed in \ref{fi:re_tx} and Fig.~\ref{fi:re_reflector}.
-\textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission while preserving the concavity-convexity of the R-E region.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength such that only the magnitude of the terms in \eqref{eq:z_expand} is amplified.
-Therefore, it is concluded that the number of active and passive elements have no impact on the waveform preference and transceiving strategy.
-\textit{Second,} the R-E benefit of passive beamforming scales faster than that of active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT versus $M$ and $L$.
+		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
+\textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission.
+This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength.
+\textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS).
+Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ scales both rate and current and preserves the general trend of the R-E boundary.
+		%\textit{Third,} the R-E benefit of passive beamforming scales faster than that of active beamforming.
+		\textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only.
 For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power.
@@
 On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$.
-An interpretation is that the IRS collects $L$ signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
-As a consequence, doubling $L$ brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
-Besides, by considering harvester nonlinearity, the proposed design brings a \SI{20}{\dB} increase in the output DC current over conventional linear perspective.
-These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the system design \footnote{However, the diode nonlinear model is based on a small-signal expansion and the input-output relationship would be linear in the high-power regime, which prevents an excessively large $M$ or $L$.}.
-\textit{Third,} using only a few transmit antenna can achieve the performance of numerous reflectors in a much lower complexity.
-The reason is that the system performance in our setup is dominated by the AP-user direct link, with the optimal active beamformer obtained in closed form.
-As shown in Fig.~\ref{fi:path_loss}, the direct path loss $\Lambda_\text{D}$ is around \SI{60}{\dB} while the extra path loss product $\Lambda_{\text{I}}\Lambda_R$ is over \SI{100}{\dB}.
-Therefore, although increasing $L$ can significantly enhance the AP-IRS-user auxiliary channel, its amplitude is still too small compared with the direct channel such that increasing $M$ can be more efficient for a practical configuration.
-Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission.
-On the contrary, a large number of active antennas suffer from channel hardening while the IRS can use adaptive reflection to potentially mitigate the effect.
-As a consequence, active beamforming is more effective for small-scale SWIPT where the direct channel dominates the transmission, and passive beamforming can be more effective for large-scale SWIPT where the auxiliary channel dominates the transmission.
-
+An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
+As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
+Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective.
+These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design.
+\textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming.
+As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\text{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\text{I}}\Lambda_R$ is over \SI{100}{\dB}.
+Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength.
+Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
+		% On the contrary, the ramification by the frequency-flat characteristic of the passive IRS overwhelms its benefits over the active antenna when $L$ is relatively small.
 		\begin{figure}[!t]
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_irs_1mhz.tex}
 			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_irs_1mhz}
@@
 			\centering
-			\begin{adjustbox}{width=\linewidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_irs_10mhz.tex}
 			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
 			\label{fi:re_irs_10mhz}
@@
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband (\SI{1}{\MHz} bandwidth) transmission and broadband transmission (\SI{10}{\MHz} bandwidth).
-The adaptive IRS strategy adjusts the passive beamforming for each sample in the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes).
-To gain some insight into the IRS behavior, we compare the results above to ideal frequency-selective IRS and no IRS.
-In contrast to Remark \ref{re:irs_frequency_flat}, each element in the ideal Frequency-Selective (FS) IRS is assumed to have an independent reflection coefficient for each subband, accounting for a total design flexibility of $NL$.
-When there is only one transmit antenna, each FS reflector simply aligns the AP-IRS-user to the AP-user channel at all subbands, namely
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
+The adaptive rate-dependent IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
+To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS.
+In contrast to Remark~\ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for $NL$ variables in total.
+When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-user channel to the AP-user channel at all subbands, namely
 		\begin{equation}
@@
 		\textit{First}, it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
-It is because the IRS enables a constructive channel composition that enhances the received signal strength.
 \textit{Second}, the performance of all four IRS strategies coincide with each other for narrowband SWIPT.
-It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region, and for a given channel, we only need to adapt the waveform and splitting ratio to achieve different rate and energy performance.
-When the bandwidth is small, all channels are approximately flat, and the optimal ideal reflection coefficients would almost synchronize at all subbands so that the loss by frequency-flat IRS is negligible.
-Also, the subchannel tradeoff in Remark \ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies, and the adaptive and non-adaptive strategies end up with the same result.
-\textit{Third}, the adaptive passive beamforming is required to maximize the R-E tradeoff for broadband SWIPT.
-Recall Remark \ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
-By adaptive passive beamforming, the channel energy can either be concentrated in few strongest subbands to increase the rate at a low SNR, or spread evenly over all subbands to boost the output DC power.
-The advantage of such a smart channel control is prominent for broadband SWIPT where the tradeoff between subbands becomes more obvious.
+It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region.
+Therefore, for a given channel, we can fix the active and passive beamforming and only adapt the waveform and splitting ratio to achieve different R-E performance.
+This is because when the bandwidth is small, all channels are approximately flat and the optimal ideal reflection coefficients would almost align at all subbands, such that the loss by the frequency-flat IRS is negligible.
+Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies.
+\textit{Third}, a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT.
+Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
+By adaptive rate-dependent passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power.
+The advantage of such a smart channel control is prominent for broadband SWIPT where the strength difference between subbands becomes more obvious.
 	\end{section}
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper proposes a novel multi-carrier IRS-aided downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
+		This paper proposes a novel IRS-aided multi-carrier downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
 We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
 Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures.
-Efficient algorithms based on the GP, SCA, SDR and AO techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
-We confirm that considering harvester nonlinearity, dedicated power waveform and beam are generally required to boost the R-E tradeoff.
+Efficient algorithms based on the AO, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
+We confirm that considering harvester nonlinearity, a dedicated power waveform is generally required to boost the R-E tradeoff.
 When developed near the transmitter, the IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
-Compared with transmit antenna, IRS element has no design flexibility in the frequency domain, but integrates the combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
-Finally, adaptive passive beamforming is demonstrated beneficial for broadband transmission, while the optimal IRS for any R-E point is also optimal for the whole R-E region for narrowband SWIPT.
+Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
+Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region for narrowband SWIPT, and the adaptive rate-dependent passive beamforming is beneficial for broadband transmission.
 
 		The combination of IRS and SWIPT brings many possibilities and challenges.
-For example, how to optimize waveform, active and passive beamforming in a multi-user SWIPT system?
+For example, how to optimize the waveform, active and passive beamforming in a multi-user SWIPT system?
 How can multiple IRS cooperate with each other to further benefit the R-E tradeoff?

### 2020-11-27 main.tex
:art: Update layout

@@
 
-\makeatletter
-\newcommand{\forcealgorithm}{\let\@latex@error\@gobble}
-\makeatother
+\algrenewcommand{\algorithmicwhile}{\textbf{While}}
+\algrenewcommand{\algorithmicif}{\textbf{If}}
+\algrenewcommand{\algorithmicthen}{\textbf{Then}}
+\algrenewcommand{\algorithmicelse}{\textbf{Else}}
+\algrenewcommand{\algorithmicend}{\textbf{End}}
+\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
+\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
 
@@
 It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power, where the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers.
-However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
+However, to the best of our knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
 In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.
@@
 $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively.
-$\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity).
+$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathbb{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity).
 For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value.
@@
 		\begin{subsection}{Transmit Signal}
-			Denote $\tilde{x}_{\text{I,}n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\text{I,}n}\sim\mathcal{CN}(0,1)$.
+			Denote $\tilde{x}_{\mathrm{I},n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$.
 The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
 			\begin{equation}\label{eq:x_m}
-				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\text{I,}n,m}\tilde{x}_{\text{I,}n}(t)}+w_{\text{P,}n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
+				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\mathrm{I},n,m}\tilde{x}_{\mathrm{I},n}(t)}+w_{\mathrm{P},n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
 			\end{equation}
-			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
-Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T=\boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t) \in \mathbb{C}^{M \times 1}$, where
+			where $w_{\mathrm{I/P},n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
+Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T=\boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
 			\begin{align}
-				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
-				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}.\label{eq:x_P}
+				\boldsymbol{x}_{\mathrm{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
+				\boldsymbol{x}_{\mathrm{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}.\label{eq:x_P}
 			\end{align}
@@
 		\begin{subsection}{Composite Channel}
-			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$.
+			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
 At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1$, $\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
@@
 			\begin{equation}\label{eq:h_n}
-				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{h}_{\text{R,}n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\text{I,}n} = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
+				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
 			\end{equation}
-			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\text{R,}n}^H)\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$.
+			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
@@
 		\begin{subsection}{Receive Signal}
-			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\text{I}}(t)+y_\text{P}(t)$ captures the contribution from information and power components over all subbands, where
+			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$ captures the contribution from information and power components over all subbands, where
 			\begin{align}
-				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
-				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}.\label{eq:y_P}
+				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
+				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}.\label{eq:y_P}
 			\end{align}
@@
 			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n} \rvert^2}{\sigma_n^2}\right)}
+				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
 			\end{equation}
@@
 							\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\text{S}}$] (0,2);
+							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
 							\draw (0,2) to [short] (1,2);
-							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
+							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
 							\draw (3,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
+							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
 							\draw (4,0) to [short] (2,0) node[ground](GND){};
@@
 							\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
+							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
 							\draw (0,2) to [short] (0.25,2);
-							\draw (0.25,2) to [D, v<=$v_{\text{D}}$, i=$i_{\text{D}}$] (2.25,2);
+							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
 							\draw (2.25,2) to [short, -*] (2.5,2);
@@
 							\draw (2.5,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_\text{L}$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
+							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
 							\draw (4,0) to [short] (2,0) node[ground](GND){};
@@
 			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform.
-Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\text{ant}}$ and the incoming signal creates an voltage source $v_{\text{S}}(t)$.
-Let $R_{\text{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
-When perfectly matched ($R_{\text{in}}=R_{\text{ant}}$), the rectifier input voltage is $v_{\text{in}}(t)=y(t)\sqrt{\rho R_{\text{ant}}}$.
+Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
+Let $R_{\mathrm{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
+When perfectly matched ($R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
 
@@
 			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y(t)^i\right\}\right\}}
+				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
 			\end{equation}
-			where $n_0$ is the truncation order and $k_i \triangleq i_{\text{S}}/i!(n'v_{\text{T}})^i$ is the diode coefficient ($i_{\text{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\text{T}}$ is the thermal voltage).
+			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
 With a slight abuse of notation, we refer to $z$ as the average output DC current in the following context.
@@
 In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity and define $\beta_2 \triangleq {k_2}{R_{\text{ant}}}$, $\beta_4 \triangleq {k_4}{R_{\text{ant}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^2\right\}=1$ but $\mathcal{E}\left\{\lvert\tilde{x}_{\text{I,}n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-Inspired by \cite{Huang2017}, we stack up the channel and waveform vectors over all subbands as $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\text{I/P}} \triangleq [\boldsymbol{w}_{\text{I/P,}1}^T,\dots,\boldsymbol{w}_{\text{I/P,}N}^T]^T \in \mathbb{C}^{MN \times 1}$, then define $\boldsymbol{W}_{\text{I/P}} \triangleq \boldsymbol{w}_{\text{I/P}}\boldsymbol{w}_{\text{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\text{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\text{I/P,}k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+Inspired by \cite{Huang2017}, we stack up the channel and waveform vectors over all subbands as $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, then define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
 Hence, the components of the average output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
@@
 				\begin{equation*}
-						\boldsymbol{W}_{\text{I/P}}=
+						\boldsymbol{W}_{\mathrm{I/P}}=
 						\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
@@
 							{
-								\boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}1}^H & \boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}2}^H & \dots & \boldsymbol{w}_{\text{I/P,}1}\boldsymbol{w}_{\text{I/P,}N}^H \\
-								\boldsymbol{w}_{\text{I/P,}2}\boldsymbol{w}_{\text{I/P,}1}^H & \boldsymbol{w}_{\text{I/P,}2}\boldsymbol{w}_{\text{I/P,}2}^H & \ddots & \vdots \\
-								\vdots & \ddots & \ddots & \boldsymbol{w}_{\text{I/P,}N-1}\boldsymbol{w}_{\text{I/P,}N}^H \\
-								\boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}1}^H & \dots & \boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}N-1}^H & \boldsymbol{w}_{\text{I/P,}N}\boldsymbol{w}_{\text{I/P,}N}^H \\
+								\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+								\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
+								\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+								\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
 							};
@@
 				\end{equation*}
-				\caption{$\boldsymbol{W}_{\text{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
-$\boldsymbol{W}_{\text{I/P,}k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\text{I/P}}$ and nulls all remaining blocks.
+				\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
+$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
 Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
-For $\boldsymbol{w}_{\text{I/P,}n_1}\boldsymbol{w}_{\text{I/P,}n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
 				\label{fi:block_diagonal}
@@
 				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
 				\end{equation}
@@
 				\begin{flalign}
-					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h},&&\label{eq:y_I2}\\
-					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2,&&\label{eq:y_I4}
+					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
+					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
 				\end{flalign}
 				\begin{flalign}
-					\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h},&&\label{eq:y_P2}\\
-					\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H.&&\label{eq:y_P4}
+					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
+					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
 				\end{flalign}
@@
 			\begin{align}
-				C_{R_{\text{ID}}-I_{\text{EH}}}(P)
-				&\triangleq \biggl\{(R_{\text{ID}}, I_{\text{EH}}): R_{\text{ID}} \le R, I_{\text{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right) \le P\biggr\}
+				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
+				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
+				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
 			\end{align}
@@
 		\begin{maxi!}
-			{\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)}{\label{op:original}}{\label{ob:original}}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) \ge \bar{R}}\label{co:original_rate}
+			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
+			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
@@
 		\begin{subsection}{IRS Phase Shift}
-			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{\text{I/P}}$ and splitting ratio $\rho$. We observe that
+			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. We observe that
 			\begin{align}
-				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n} \rvert^2
-				& = \boldsymbol{w}_{\text{I,}n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}\nonumber\\
-				& = \boldsymbol{w}_{\text{I,}n}^H(\boldsymbol{h}_{\text{D,}n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\text{D,}n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\text{I,}n}\nonumber\\
-				& = \boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
+				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
+				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
 				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
 			\end{align}
-			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On the other hand, we define $t_{\text{I/P,}k}$ as
+			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On the other hand, we define $t_{\mathrm{I/P},k}$ as
 			\begin{align}
-				t_{\text{I/P,}k}
-				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k})\nonumber\\
-				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\text{I/P,}k}\right)\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_{\text{I/P,}k}\boldsymbol{\Phi})
+				t_{\mathrm{I/P},k}
+				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})
 			\end{align}
-			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 Therefore, we can rewrite the rate and average DC current expressions as
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\text{I,}0}+t_{\text{P,}0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\text{I,}0}^2 + \sum_{k=-N+1}^{N-1}{t_{\text{P,}k}t_{\text{P,}k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}.\label{eq:z_irs}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
 			\end{align}
@@
 			\begin{align}
-				(t_{\text{I,}0}^{(i)})^2
-				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2,\label{eq:taylor_1}\\
-				t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i)})^*
-				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*,\label{eq:taylor_2}\\
-				t_{\text{I,}0}^{(i)} t_{\text{P,}0}^{(i)}
-				& = \frac{1}{4}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\label{eq:taylor_3}
+				(t_{\mathrm{I},0}^{(i)})^2
+				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
+				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
+				& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
+				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
+				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
+				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
 			\end{align}
@@
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{\text{I,}0}^{(i)}+t_{\text{P,}0}^{(i)})\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right).\label{eq:z_irs_approx}
+					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)})\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
 				\end{align}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\text{I/P,}k}$, $\forall n,k$
-					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\text{I/P,}k}^{(0)}$, $\forall k$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{H}_{\mathrm{I},n},\boldsymbol{h}_{\mathrm{R},n},\boldsymbol{w}_{\mathrm{I/P}},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\mathrm{I/P},k}^{(0)}$, $\forall k$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)},t_{\text{I/P,}k}^{(i)}$, $\forall k$ by solving problem~\eqref{op:irs}
+						\State Obtain $\boldsymbol{\Phi}^{(i)},t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by solving problem~\eqref{op:irs}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
-					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
 				\end{algorithmic}
@@
 		\begin{subsection}{Waveform, Active Beamforming and Splitting Ratio}
-			Next, we jointly optimize the waveform and active beamforming $\boldsymbol{w}_{\text{I/P}}$ together with the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
+			Next, we jointly optimize the waveform and active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
 As pointed out in \cite{Clerckx2018b}, the waveform design in the frequency domain and the active beamformer in the spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
 			\begin{equation}\label{eq:w_IP}
-				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
+				\boldsymbol{w}_{\mathrm{I/P},n}=s_{\mathrm{I/P},n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
 			\end{equation}
-			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{\text{I/P,}n}$ at different tones.
+			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{\mathrm{I/P},n}$ at different tones.
 Hence, the original waveform and active beamforming optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
-Define $\boldsymbol{s}_{\text{I/P}} \triangleq [s_{\text{I/P,}1},\dots,s_{\text{I/P,}N}]^T \in \mathbb{C}^{N \times 1}$.
-At subband $n$, the effective channel strength is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\text{I,}n}^2$ and $s_{\text{P},n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{\text{I,}n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{\text{I,}n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$.
+At subband $n$, the effective channel strength is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\mathrm{I},n}^2$ and $s_{\mathrm{P},n}^2$, respectively.
+With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I},n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
 			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right).
+				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\biggr)\right).
 			\end{equation}
@@
 				\begin{align}
-					z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\text{I,}n}^2+s_{\text{P},n}^2)\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\text{I,}{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\text{P,}{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right).\label{eq:z_waveform}
+					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
+					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2)\nonumber\\
+					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
 				\end{align}
@@
 			\begin{maxi!}
-				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho}{z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}{\label{op:waveform}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right)\le{P}}
-				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}.}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
+				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}.}
 			\end{maxi!}
@@
 			\begin{mini!}
-				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\frac{t'}{z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)} \le 1}\label{co:waveform_objective}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
+				\addConstraint{\frac{t'}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
 				\addConstraint{\rho + \bar{\rho} \le 1.}
@@
 			\begin{align}
-				z(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho) &\triangleq \sum_{m_\text{P}}{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}\label{eq:posynomial_objective},\\
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\text{I,}n}}g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})\label{eq:posynomial_rate}
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:posynomial_objective},\\
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:posynomial_rate}
 			\end{align}
-			where $m_\text{P}=(2N^3+6N^2+7N)/3$, $m_{\text{I,}n}=2$ are the number of monomials.
+			where $m_\mathrm{P}=(2N^3+6N^2+7N)/3$, $m_{\mathrm{I},n}=2$ are the number of monomials.
 Following \cite{Chiang2005}, we upper bound posynomials \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\eqref{op:waveform_rgp} reduces to
 			\begin{mini!}
-				{\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{s}_\text{P}}\rVert^2\right)\le{P}}
-				\addConstraint{{t'}\prod_{m_\text{P}}{\left(\frac{g_{{m_\text{P}}}(\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho)}{\gamma_{{m_\text{P}}}}\right)^{-\gamma_{{m_\text{P}}}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\text{I,}n}}\left(\frac{g_{m_{\text{I,}n}}(s_{\text{I,}n},\bar{\rho})}{\gamma_{m_{\text{I,}n}}}\right)^{-\gamma_{m_{\text{I,}n}}}\le{1}}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
+				\addConstraint{{t'}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
+				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
 				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{mini!}
-			where $\gamma_{m_\text{P}},\gamma_{m_{\text{I,}n}} \ge 0$, $\sum_{m_\text{P}}\gamma_{m_\text{P}}=\sum_{m_{\text{I,}n}}\gamma_{m_{\text{I,}n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_\text{P}},\gamma_{m_{\text{I,}n}}\}$ that require successive update.
+			where $\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}} \ge 0$, $\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update.
 As suggested in \cite{Clerckx2018b}, a feasible choice at iteration $i$ is
 			\begin{align}
-				\gamma_{m_\text{P}}^{(i)} & = \frac{g_{m_\text{P}}(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\text{I}}^{(i-1)},\boldsymbol{s}_\text{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P},\\
-				\gamma_{m_{\text{I,}n}}^{(i)} & = \frac{g_{m_{\text{I,}n}}(s_{\text{I,}n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\text{I,}n}^{(i-1)})^2}\big/{\sigma_n^2}}.\label{eq:gamma_I}
+				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P},\\
+				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}.\label{eq:gamma_I}
 			\end{align}
-			$\boldsymbol{s}_{\text{I}},\boldsymbol{s}_\text{P},\rho$ are updated iteratively until convergence.
+			$\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho$ are updated iteratively until convergence.
 Problem~\eqref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
-					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{s}_{\text{I/P}}^{(0)}$, $\rho^{(0)}$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_\text{P}}^{(i)},\gamma_{m_{\text{I,}n}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
-						\State Obtain $\boldsymbol{s}_{\text{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+						\State Update $\{\gamma_{m_\mathrm{P}}^{(i)},\gamma_{m_{\mathrm{I},n}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
+						\State Obtain $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\text{I/P}}^{\star}=\boldsymbol{s}_{\text{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\text{I/P}}^{\star}$ by \eqref{eq:w_IP}
-					\State \textbf{output} $\boldsymbol{w}_{\text{I/P}}^{\star}, \rho^{\star}$
+					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\mathrm{I/P}}^{\star}$ by \eqref{eq:w_IP}
+					\State \textbf{Output} $\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
 				\end{algorithmic}
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\text{I/P}}$ together with splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
+			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
 The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{\text{D,}n},\boldsymbol{H}_{\text{I,}n},\boldsymbol{h}_{\text{R,}n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
-					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{\text{I/P}}^{(0)},\rho^{(0)}$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{H}_{\mathrm{I},n},\boldsymbol{h}_{\mathrm{R},n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$
 					\Repeat
 						\State $i \gets i + 1$
-						\State Fix $\boldsymbol{w}_{\text{I/P}}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
-						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, obtain $\boldsymbol{w}_{\text{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
+						\State Fix $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
+						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, obtain $\boldsymbol{w}_{\mathrm{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{\text{I/P}}^{\star}, \rho^{\star}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
 				\end{algorithmic}
@@
 			\begin{proposition}\label{pr:ao}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\textnormal{I}}^{\star},\boldsymbol{w}_\textnormal{P}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\text{I}}^{(i)},\boldsymbol{w}_\text{P}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho$ has limit points and Algorithm~\ref{al:alternating} is guaranteed to converge.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I}}^{(i)},\boldsymbol{w}_{\mathrm{P}}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho$ has limit points and Algorithm~\ref{al:alternating} is guaranteed to converge.
 As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
@@
 Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference.
-As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-user path and let $d_{\text{H}}$, $d_{\text{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
-We also denote $d_{\text{D}}$, $d_{\text{I}}$, $d_{\text{R}}$ as the length of direct, incident, reflective paths such that $d_{\text{I}}=\sqrt{d_{\text{H}}^2+d_{\text{V}}^2}$, $d_{\text{R}}=\sqrt{(d_{\text{D}}-d_{\text{H}})^2+d_{\text{V}}^2}$.
-$d_{\text{D}}=15\,\si{\meter}$, $d_{\text{V}}=2\,\si{\meter}$ and $d_{\text{H}}=2\,\si{\meter}$ are chosen as reference.
+As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-user path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
+We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$.
+$d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference.
 The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
@@
 No spatial correlation is assumed across transmit antennas and IRS elements.
-Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-With a \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference.
+Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference.
 We also assume a \SI{0}{\dBi} IRS element gain and a \SI{2}{\dBi} receive antenna gain.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_subband}
@@
 			\end{adjustbox}
-			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:waveform_subband}
@@
 \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy.
-The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\text{P}$ is increased to boost the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains.
+As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains.
 Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
@@
 			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_noise}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $d_{\text{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_distance}
@@
 
-		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\text{H}}$.
+		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
 A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay with the optimal development location around the midpoint \cite{Li2017}, placing the IRS closer to either the transmitter or the receiver would further improve the R-E tradeoff.
@@
 Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\text{I}}\Lambda_R$.
+A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\mathrm{I}}\Lambda_R$.
 It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the user.
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_tx}
@@
 			\end{adjustbox}
-			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_reflector}
@@
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\text{H}}=0$ and $d_{\text{V}}=0.5\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 			\label{fi:scaling_tx}
@@
 			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\text{H}}=0$ and $d_{\text{V}}=0.5\,\si{\meter}$.}
+			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 			\label{fi:scaling_reflector}
@@
 \textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming.
-As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\text{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\text{I}}\Lambda_R$ is over \SI{100}{\dB}.
+As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}.
 Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength.
@@
 			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_irs_1mhz}
@@
 			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\text{H}}=d_{\text{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_irs_10mhz}
@@
 		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\text{D,}n}/h_{\text{I,}n,l}h_{\text{R,}n,l}\right)}},\quad \forall n,l.
+			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\mathrm{D},n}/h_{\mathrm{I},n,l}h_{\mathrm{R},n,l}\right)}},\quad \forall n,l.
 		\end{equation}

### 2020-11-28 main.tex
:pencil: Rephrase abstract

@@
 This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
-Considering the energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
 Stationary solutions are achieved based on the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.

### 2020-11-30 main.tex
:triangular_flag_on_post: TCom draft 301120

@@
-\documentclass[journal]{IEEEtran}
+\documentclass[journal,12pt,onecolumn,draftcls]{IEEEtran}
 
@@
 			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
+			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE,}
 			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
@@
 		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the strength of the received Radio-Frequency (RF) signal.
-To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain.
+To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by a passive beamforming gain.
 This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
 Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
-Stationary solutions are achieved based on the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.
-Despite the hardware limitations of IRS constraint the reflection elements to be Frequency-Flat (FF), results demonstrate the significant benefits of the proposed architecture based on a joint design of the waveform, active and passive beamforming to enlarge the R-E region of IRS-aided SWIPT.
+Stationary solutions are achieved by the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.
+Although practical IRS is limited to Frequency-Flat (FF) reflection, results demonstrate significant benefits of the proposed architecture based on a joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT.
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		Wireless information and power transfer, intelligent reflecting surface, waveform design, active and passive beamforming.
+		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, active and passive beamforming.
 	\end{IEEEkeywords}
@@
 Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}, which uniquely showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \textit{What is the optimal input distribution for SWIPT under nonlinearity?}
-			% quotation mark removed, ref: https://english.stackexchange.com/questions/21795/punctuation-with-the-question-is-or
-			This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: \textit{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
 The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g.
 modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
 Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
@@
 This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT.
-Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
+Specifically, we consider a IRS-aided multi-carrier downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
 A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency.
-The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
+The power and information waveforms and the active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
 This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
@@
 			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture.
-			% Note also that the joint waveform and beamforming design and optimization (and its potential performance benefits) in IRS-aided SWIPT differs from that in SWIPT (as in \cite{Clerckx2018b,Varasteh2019d}) due to the hardware constraint that the IRS elements should be frequency-flat.
 Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency-flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design.
 We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT.
-Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) the performance loss by the frequency-flat constraint of IRS is negligible for narrowband transmission, 6) the adaptive (i.e.
+Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) only the waveform and splitting ratio need to be updated for the R-E boundary of narrowband transmission, 6) the adaptive (i.e.
 rate-dependent) passive beamforming is required for broadband transmission.
@@
 Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with the waveform and beamforming design.
+In comparison, PS splits the received signal into individual information and power streams such that the splitting ratio $\rho$ is coupled with the waveform and beamforming design.
 Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.
@@
 			where $w_{\mathrm{I/P},n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
-Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T=\boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
+Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T \triangleq \boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
 			\begin{align}
@@
 				\centering
-				\noindent
-				\begin{minipage}[b]{0.45\columnwidth}
-					\centering
 				\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
-						\resizebox{\columnwidth}{!}{
+					\resizebox{0.45\columnwidth}{!}{
 						\begin{circuitikz}[transform shape]
@@
 				}
-				\end{minipage}%
-				\begin{minipage}[b]{0.45\columnwidth}
-					\centering
 				\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
-						\resizebox{\columnwidth}{!}{
+					\resizebox{0.45\columnwidth}{!}{
 						\begin{circuitikz}[transform shape]
@@
 				}
-				\end{minipage}
 				\caption{Receive antenna and energy harvester circuits.}
@@
 It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
+However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
 In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
 Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
@@
 
-			\begin{figure*}[b]
+			\begin{figure*}[!b]
 				\hrule
-				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
-				\end{equation}
+				\begin{align}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
+					& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+				\end{align}
 				\hrule
-				\begin{flalign}
+				\begin{align}
 					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
 					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
-				\end{flalign}
-				\begin{flalign}
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
 					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
 					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
-				\end{flalign}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
+					& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+				\end{align}
 			\end{figure*}
@@
 			The achievable R-E region is defined as
-			\begin{align}
-				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
-			\end{align}
+			\begin{equation}
+				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
+			\end{equation}
 			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
@@
 			\end{align}
-			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 On the other hand, we define $t_{\mathrm{I/P},k}$ as
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
 			\end{align}
@@
 				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
+				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
 			\end{align}
@@
 Hence, the objective function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to
-			\begin{figure*}[b]
+			\begin{figure*}[!b]
 				\hrule
@@
 If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the extracted rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ be a stationary point of the original problem~\eqref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, and the performance loss by SDR is negligible.
+In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, where the performance loss by SDR is negligible.
 If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the augmented phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
@@
 Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star), \ l=1,\dots,L$.
-Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
 The SCA algorithm for the passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
@@
 			\end{equation}
-			\begin{figure*}[b]
+			\begin{figure*}[!b]
 				\hrule
@@
 			$\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho$ are updated iteratively until convergence.
-Problem~\eqref{op:waveform_gp} can be solved using existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
 The GP algorithm of the waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
@@
 		\begin{subsection}{Alternating Optimization}
-			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
+			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
 The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
@@
 The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference.
-We also assume a \SI{0}{\dBi} IRS element gain and a \SI{2}{\dBi} receive antenna gain.
+We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain.
 For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations.
 In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
-		% - at the WPT point, power is allocated to the multisine waveform only, isn't it?
-		% - for single-carrier WPT, modulated waveform may be preferred as it has a modulation gain (also proved in Fig. 5)
 On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only.
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_subband.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/waveform_subband.tex}
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e.
-a time sharing between the WPT point and the tangent WIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
+a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
 Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on $N$.
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_noise.tex}
@@
 \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small amplitude could be inefficient for energy maximization.
+The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization.
 On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer.
-The result highlights the benefit of multisine and the necessity of joint optimization of waveform and splitting ratio.
+The result highlights the benefit of dedicated power waveform and the necessity of joint optimization of waveform and splitting ratio.
 
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_distance.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/path_loss.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_tx.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_reflector.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/scaling_tx.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/scaling_reflector.tex}
@@
 \textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS).
-Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ scales both rate and current and preserves the general trend of the R-E boundary.
-		%\textit{Third,} the R-E benefit of passive beamforming scales faster than that of active beamforming.
+Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary.
 \textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming.
@@
 Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
-		% On the contrary, the ramification by the frequency-flat characteristic of the passive IRS overwhelms its benefits over the active antenna when $L$ is relatively small.
 		\begin{figure}[!t]
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_irs_1mhz.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\begin{adjustbox}{width=0.25\columnwidth}
 				\input{assets/re_irs_10mhz.tex}
@@
 It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region.
-Therefore, for a given channel, we can fix the active and passive beamforming and only adapt the waveform and splitting ratio to achieve different R-E performance.
-This is because when the bandwidth is small, all channels are approximately flat and the optimal ideal reflection coefficients would almost align at all subbands, such that the loss by the frequency-flat IRS is negligible.
+Therefore, for a given channel, we can fix the active and passive beamforming, and only adapt the waveform and splitting ratio to achieve different R-E performance.
+This is because when the bandwidth is small, all channels are approximately flat such that the optimal ideal reflection coefficients at all subbands are approximately the same.
 Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies.
@@
 By adaptive rate-dependent passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power.
-The advantage of such a smart channel control is prominent for broadband SWIPT where the strength difference between subbands becomes more obvious.
+The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.
 	\end{section}
@@
 We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
-Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission with practical co-localized receiver architectures.
+Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission for practical co-localized receiver architectures.
 Efficient algorithms based on the AO, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
@@
 Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
-Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region for narrowband SWIPT, and the adaptive rate-dependent passive beamforming is beneficial for broadband transmission.
+Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the adaptive rate-dependent passive beamforming is beneficial for broadband transmission.
 
@@
 How to design an IRS-aided SWIPT system for different multiple access techniques?
-How to implement IRS in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?
+How to develop SWIPT in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?
 Can IRS operation be directly supported by SWIPT?

### 2020-11-30 main.tex
:art: Update layout

@@
-\documentclass[journal,12pt,onecolumn,draftcls]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 
@@
 We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT.
-Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) only the waveform and splitting ratio need to be updated for the R-E boundary of narrowband transmission, 6) the adaptive (i.e.
-rate-dependent) passive beamforming is required for broadband transmission.
+Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) for narrowband transmission, the optimal active and passive beamforming are fixed for a given channel, and one only need to update the waveform and splitting ratio to draw the whole R-E boundary, 6) for broadband transmission, the frequency diversity enables rate-dependent adaptive passive beamforming to control the subchannel strength distribution and improve the R-E tradeoff.
 
@@
 				\hrule
-				\begin{align}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
-					& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
-				\end{align}
+				\begin{equation}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+				\end{equation}
 				\hrule
-				\begin{align}
+				\begin{flalign}
 					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
 					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
+				\end{flalign}
+				\begin{flalign}
 					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
 					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
-					& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
-				\end{align}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
+				\end{flalign}
 			\end{figure*}
+			% \begin{figure*}[!b]
+			% 	\hrule
+			% 	\begin{align}
+			% 		z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
+			% 		& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+			% 	\end{align}
+			% 	\hrule
+			% 	\begin{align}
+			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
+			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
+			% 		& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+			% 		\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
+			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+			% 		\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
+			% 		& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
+			% 		& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+			% 	\end{align}
+			% \end{figure*}
 		\end{subsection}
@@
 			The achievable R-E region is defined as
-			\begin{equation}
-				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
-			\end{equation}
+			\begin{align}
+				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
+				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
+				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
+			\end{align}
+			% \begin{equation}
+			% 	C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
+			% \end{equation}
 			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
 			\end{align}
+			% \begin{align}
+			% 	R(\boldsymbol{\Phi})
+			% 	& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
+			% 	z(\boldsymbol{\Phi})
+			% 	& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+			% \end{align}
 			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by their first-order Taylor expansion \cite{Adali2010}.
@@
 				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
+				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
+				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
 			\end{align}
+			% \begin{align}
+			% 	(t_{\mathrm{I},0}^{(i)})^2
+			% 	& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
+			% 	t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
+			% 	& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
+			% 	t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
+			% 	& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
+			% 	& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
+			% \end{align}
 			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}.
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_subband.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/waveform_subband.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_noise.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_distance.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/path_loss.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_tx.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_reflector.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/scaling_tx.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/scaling_reflector.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_irs_1mhz.tex}
@@
 			\centering
-			\begin{adjustbox}{width=0.25\columnwidth}
+			\begin{adjustbox}{width=0.9\columnwidth}
 				\input{assets/re_irs_10mhz.tex}
@@
 		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
-The adaptive rate-dependent IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
+The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
 To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS.
@@
 Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
-By adaptive rate-dependent passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power.
+By adaptive passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power.
 The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.
@@
 Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
-Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the adaptive rate-dependent passive beamforming is beneficial for broadband transmission.
+Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the rate-dependent adaptive passive beamforming is beneficial for broadband transmission.
 

### 2021-01-28 letter.tex
:memo: Initialize response letter

\documentclass[a4paper, 10pt]{letter}

\name{Yang Zhao, Bruno Clerckx and Zhenyuan Feng}
\date{}

\begin{document}
	\begin{letter}{Prof. Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design)}
		\opening{Dear Prof. Liang Xiao and Reviewers,}

		We would like to express our appreciation for the time and effort dedicated to the reviewing of our paper. The manuscript has been revised carefully based on your valuable comments and suggestions. In particular, we attempted to clarify the motivations and contributions of this work. To answer the questions and concerns, we include a point-to-point response below, which also describes all modifications made to the manuscript. We hope that the revisions are to the satisfaction of the editor and reviewers.

		\closing{Best Regards,}
	\end{letter}
\end{document}

### 2021-01-29 response.tex
:memo: Update response letter

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{pdfpages}

\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

\newcommand{\reviewersection}
	{\stepcounter{reviewer} \bigskip \hrule \section*{Reviewer \thereviewer}}

\renewcommand{\thepoint}
	{\thereviewer.\arabic{point}}

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter.pdf}

	\begin{reviewersection}
		\begin{point}
			This paper assumed that the perfect channel state information (CSI) of the whole system is available at the base station. However, since the IRS is in general not equipped with a radio frequency chain, the accurate CSI of the reflecting links established by the IRS is very challenging to obtain. The reviewer wonders if the proposed algorithm can also be applied to a case where the imperfect CSI of the network is available at the base station.
			\label{pt:1.1}
		\end{point}

		\begin{response}
			Thank you for pointing out the issue of CSI acquisition in presence of IRS. Practical protocols based on element-wise on/off switching \cite{Nadeem2019}, joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed to estimate the cascaded AP-IRS-user link for specific applications, yet channel estimation and codebook design for multi-carrier SWIPT remain unresolved and are beyond our current scope. The proposed algorithm is based on the assumption of cascaded CSIT (not individual AP-IRS and IRS-user ones) and can be readily extended to the imperfect CSIT case, where the joint waveform and beamforming design is based on a quantized CSI feedback.
			\label{re:1.1}
		\end{response}

		\begin{point}
			This paper considered a relatively simple system model where there is only one user in the system. However, in practice, there can be many users co-existing in the SWIPT systems and there may also be two different and independent quality of service requirements: energy harvesting requirement and information decoding requirement. It could be better if the authors can clarify if the proposed algorithm can be employed in a more general case where the base station and the IRS cooperate to serve multiple users in the same time slot.
		\end{point}

		\begin{response}
			We appreciate your suggestion on IRS-aided multi-user SWIPT and believe it would be very promising. To achieve this, we would need to tackle 1) the passive beamforming design with tradeoff across frequency and spatial domains, 2) the waveform and active beamforming design for multi-user SWIPT considering harvester nonlinearity. Although the proposed algorithm can be extended to address the first issue, the second issue is still unknown in SWIPT literatures. Extending our problem to the multi-user case would require first to solve relevant problems in the non-IRS case, and is not the intention of this paper.
		\end{response}

		\begin{point}
			It is well known that after employing semidefinite programming for handling the phase shift matrix at the IRS, it is very unlikely to obtain a rank-one phase shift matrix without any further modification. The reviewer notices that the authors proposed the Gaussian randomization method to ensure a rank-one solution. Also, the convergence of the proposed overall algorithm also relies on the unit-rank solution. Therefore, to make this paper more comprehensive and convincing, it is suggested to provide more results (such as figures, tables, and data analysis) in the simulation part to show that the rank-one solution can always be obtained even without applying the Gaussian randomization. As this is a very important and interesting conclusion to the colleagues working in the same area, it could be better if the authors can further discuss, interpret, and clarify this in a remark.
		\end{point}

		\begin{response}
			% TODO
		\end{response}

		\begin{point}
			The figures in the current version are relatively small, it is suggested to provide larger figures to help the readers better understand the results.
		\end{point}

		\begin{response}
			We apologize for the inconvenience. The figures would be amplified in future versions.
		\end{response}

		\begin{point}
			In the current version, the authors claimed that by applying semidefinite relaxation and omitting the rank-one constraint, the performance loss is negligible. The reviewer wonders if this is because of the relatively simple system model, as there is only one single user who has both power and information requirements. It could be better if the authors can further discuss this issue for a more general multiple user scenario.
		\end{point}

		\begin{response}
			% TODO
		\end{response}
	\end{reviewersection}

	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

### 2021-02-02 response.tex
:memo: Update response letter

@@
 \usepackage[utf8]{inputenc}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{fullpage}
@@
 			We appreciate your suggestion on IRS-aided multi-user SWIPT and believe it would be very promising.
-To achieve this, we would need to tackle 1) the passive beamforming design with tradeoff across frequency and spatial domains, 2) the waveform and active beamforming design for multi-user SWIPT considering harvester nonlinearity.
-Although the proposed algorithm can be extended to address the first issue, the second issue is still unknown in SWIPT literatures.
-Extending our problem to the multi-user case would require first to solve relevant problems in the non-IRS case, and is not the intention of this paper.
+To extend the current work, we would first need to tackle the waveform and active beamforming design for a multi-user SWIPT system.
+For a multi-carrier network, each subcarrier only serves one information user but may serve all power user simultaneously (as whole received signal can be used for energy harvesting), and it involves an additional resource allocation problem that cannot be solved by the proposed GP algorithm.
+
+			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT [see TODO] with corresponding waveform as
+			\begin{equation}
+				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \frac{\boldsymbol{h}_{n}}{\lVert{\boldsymbol{h}_{n}}\rVert}
+				\label{eq:decouple_waveform}
+			\end{equation}
+			which decouples the design in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) thus satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
+Apparently, picking $s_{\mathrm{I/P}, n}$ as nonnegative value would maximize (27) and make (28) a real-value optimization problem, thus enable GP tools.
+
+			However, this is not generally the case in a multi-user scenario.
+For any optimal information and power waveform $\boldsymbol{w}_{\mathrm{I}, n}^{\star}, \boldsymbol{w}_{\mathrm{P}, n}^{\star}$ on subband $n$, they generally cannot be decoupled as \eqref{eq:decouple_waveform} because users have different channel response, and the optimization should be performed over complex field.
+Some attempts were made for WPT in \cite{Huang2017a}, but the extension to SWIPT is not straightforward as the power splitting ratio at all users require a joint update as well.
+
+			Extending our problem to the multi-user case would require first to solve relevant problems in the non-IRS case above.
+It is not the intention of this paper and may be considered in our further research.
 		\end{response}
@@
 
+	\begin{reviewersection}
+		\begin{point}
+			New RIS models are now being adopted as in \cite{Abeywickrama2019} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Why  is MRT considered as precoder by (25) rather than optimizing it? Is it globally optimal too?
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Some strong assumptions like perfect CSI availability limit the practical utility of the proposed analytical results.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			All the assumptions and relaxations adopted used in the derivation of results as in (23) need to be explicitly mentioned along with appropriate justification for the same.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Some transformations have been made while solving the original problem, but it has not been explicitly mentioned whether it is equivalent to transformation or not.
+		\end{point}
+
+		\begin{point}
+			Are the proposed solutions locally optimal or globally optimal? It is not clear whether the convergence of proposed solution methodologies is local or global? Also, how fast is it?
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			The time complexity of the proposed algorithms, especially involving branch and bound methods, seems to be high especially applications assuming perfectly CSI availability as the coherence times are practically pretty low.
+So, the authors would like to justify it so that the proposed solution can be obtained over relatively short coherence intervals.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			How practical is it to consider lossless reflection from the RIS? Specifically, by considering the magnitude to be 1, the reflection losses at the RIS have been ignored.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Minor comment: The size of all the numerical results figures is too small.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+	\end{reviewersection}
+
+	\begin{reviewersection}
+		\begin{point}
+			First of all, motivations of studying the IRS on SWIPT is very unclear to me. Please clarify.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Also, the contributions of this work are rather unclear, and thus, those should be better mentioned.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Please explain the derived results more intuitively for better understanding.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			Authors assumed the unrealistic situation: the channels are assumed to be perfectly known.
+However, in practice, the channel should be estimated, e.g., as studied in \cite{You2019}, \cite{Kang2020}.
+It would be much better to discuss the channel estimation issue by citing the above references.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			More simulation results should be added to better and aggregately validate the effectiveness of the proposed method.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+
+		\begin{point}
+			The sizes of figures are too small.
+		\end{point}
+
+		\begin{response}
+			% TODO
+		\end{response}
+	\end{reviewersection}
+
 	\bibliographystyle{IEEEtran}

### 2021-02-03 response.tex
:memo: Update response letter

@@
 \usepackage{pdfpages}
+\usepackage{siunitx}
 
@@
 
-			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT [see TODO] with corresponding waveform as
-			\begin{equation}
-				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \frac{\boldsymbol{h}_{n}}{\lVert{\boldsymbol{h}_{n}}\rVert}
-				\label{eq:decouple_waveform}
-			\end{equation}
-			which decouples the design in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) thus satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
+			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT [see TODO] with corresponding waveform as given by (25), which decouples the design in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) thus satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
 Apparently, picking $s_{\mathrm{I/P}, n}$ as nonnegative value would maximize (27) and make (28) a real-value optimization problem, thus enable GP tools.
@@
 		\begin{response}
-			% TODO
+			The rank-\num{1} property of $\boldsymbol{\Phi}$ to the relaxed problem (24) is suggested by simulation under different configurations.
+As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is hard to prove in theory due to the nonlinear objection function (24a) and the sum rate constraint (24b).
+Instead, we considered \num{300} individual channel realizations for different $M$, $N$ and $L$.
+The extensive numerical results show that the proposed SCA Algorithm 1 returned unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
+Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 is feasible to address the passive beamforming issue in IRS-aided SWIPT systems.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			[How do we answer this question?]
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			Thank you for sharing!
+This acknowledged paper investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
+It also proposed an analytical IRS model together with an AO algorithm to maximize the achievable rate by passive beamforming.
+Simulation results emphasized the importance of modeling such a relationship in practical IRS design.
+We actually thought about integrating these new models in our system design, but finally decided to use the most common and simplest IRS model in the current stage to reduce the design complexity and provide a primary benchmark for IRS-aided SWIPT.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			The waveform design involves the optimization in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$).
+For the single-user scenario, MRT is global optimal for both information and power transmission.
+This is because the sum rate (7) and DC components (10) -- (13) only involve waveform in terms of $\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n}$ thus can be simultaneously maximized by MRT precoder.
+However, this is not the case for multi-user SWIPT (since users have different channels) where the beamformer and power allocation require a joint optimization.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			The reviewer is referred to our response to Comment \ref{pt:1.1}.
+Indeed, the assumption of perfect CSIT is very ideal and the existing protocols may not provide a good enough estimation in practice.
+We follow the convention of most existing papers on this topic and expect some breakthroughs in future research.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			We appreciate your suggestion.
+The original objective function (19) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by their first-order local Taylor expansions (20) -- (22) to formulate a series of convex problems.
+These problems are SCA to the original passive beamforming problem (maximize (19) s.t.
+(24b) -- (24e)), and the objective function (23) is obtained by plugging (20) -- (22) into (19), which is an affine and satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$.
+We start from any feasible point and approach the original solution by SCA.
 		\end{response}
@@
 		\end{point}
+
+		\begin{response}
+			Thank you for pointing this out. All transformations are equivalent to their original form and we would make this clear in the revised manuscript.
+		\end{response}
 

### 2021-02-05 response.tex
:memo: Update response letter

@@
 		\begin{response}
-			% TODO
+			Algorithm 1 -- 3 only provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
+For different sum rate constraints, we use water-filling with MRT to initialize the modulated waveform while use scaled matched filter to initialize the unmodulated waveform (corresponding to a transmit power of $2P$, regulated afterwards).
+We also initialize the IRS phase shift by uniform distribution over $[0, 2\pi)$.
+Nevertheless, as the solutions are locally optimal, some result points on the R-E boundary may be strictly worse (with lower rate and energy) than another, especially for a large $M$ and $L$.
+To address this, we draw the R-E boundary from high-rate low-energy (lower right) points to low-rate high-energy (upper left) points.
+If the issue above happens, we discard the dominated result and reinitialize the waveform and IRS phase shift by the solution at the previous point.
+
+			% TODO: complexity
 		\end{response}

### 2021-02-06 response.tex
:memo: Update response letter

@@
 \usepackage{siunitx}
+
+\DeclareSIUnit{\belm}{Bm}
+\DeclareSIUnit{\dBm}{\deci\belm}
+\DeclareSIUnit{\beli}{Bi}
+\DeclareSIUnit{\dBi}{\deci\beli}
 
@@
 			However, this is not generally the case in a multi-user scenario.
-For any optimal information and power waveform $\boldsymbol{w}_{\mathrm{I}, n}^{\star}, \boldsymbol{w}_{\mathrm{P}, n}^{\star}$ on subband $n$, they generally cannot be decoupled as \eqref{eq:decouple_waveform} because users have different channel response, and the optimization should be performed over complex field.
+For any optimal information and power waveform $\boldsymbol{w}_{\mathrm{I}, n}^{\star}, \boldsymbol{w}_{\mathrm{P}, n}^{\star}$ on subband $n$, they generally cannot be decoupled as (25) because users have different channel response, and the optimization should be performed over complex field.
 Some attempts were made for WPT in \cite{Huang2017a}, but the extension to SWIPT is not straightforward as the power splitting ratio at all users require a joint update as well.
@@
 		\begin{response}
-			Thank you for sharing!
-This acknowledged paper investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
+			Thank you for sharing this acknowledged paper, which investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
 It also proposed an analytical IRS model together with an AO algorithm to maximize the achievable rate by passive beamforming.
@@
 
-			% TODO: complexity
+			For a tolerance of $\epsilon=10^{-8}$, the SDR-based Algorithm 1 usually converge within 3 iterations while the GP-based Algorithm 2 tends to converge within 8 iterations.
+The AO-based Algorithm 3 typically converge within 3 iterations.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			We agree with the reviewer that the proposed algorithm (especially Algorithm 2) could be too time-consuming for practical applications with relatively short coherence time.
+The proposed algorithms ensure best performance by iteratively solving intricate optimization problems and may not be implemented in practice, while suboptimal design (e.g.
+scaled matched filter) is expected to achieve a good performance.
+
+			% TODO: branch and bound / complexity analysis
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			Green's decomposition indicates that the backscattered/reflected signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
+The reflection coefficient of the $l$-th IRS element is thus defined as
+			\begin{equation}
+				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0}
+			\end{equation}
+			where $Z_0$ is the characteristic impedance and $Z_l = R_l + j X_l$ is the impedance of the $l$-th IRS element.
+It implies that $\lvert{\phi_l}\rvert \le 1$ for $R_l \ge 0$, and we assume $Z_l$ is pure reactive such that
+			\begin{equation}
+				\phi_l = \frac{j X_l - Z_0}{j X_l + Z_0} = e^{j \theta_{l}}
+			\end{equation}
+			which corresponds to the lossless reflection model adopted in the paper.
+Nevertheless, due to the non-zero power consumption at the IRS in practice, $R_l$ would be positive and $\lvert{\phi_l}\rvert$ indeed depends on the
+			the reflection coefficient not only has a magnitude smaller than 1 but also depends on the phase shift.
+\cite{Abeywickrama2019} found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			We apologize for the inconvenience. The figures would be amplified in future versions.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			We appreciate your suggestion and have modified the manuscript to emphasize this point.
+A major challenge for SWIPT is that the information decoder and energy harvester have different sensitivity -- although conventional radios as Wi-Fi and Bluetooth can support a signal strength of \num{-90} to \SI{-100}{\dBm}, most existing harvesters only capture signals at \num{-20} to \SI{-30}{\dBm}.
+Since the transmit power is strictly subject to regulations, it is crucial to increase the energy efficiency to boost the signal strength and extend the system coverage.
+Therefore, we believe the effective channel enhancement and the low power consumption of IRS is a perfect match for SWIPT.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			Thank you for the opinion and the manuscript has been revised accordingly.
+This paper proposed an IRS-aided SWIPT network and considered a joint waveform and beamforming design over spatial and frequency domains under energy harvester nonlinearity.
+To the best of our knowledge, relevant existing papers assumed linear harvester model where the RF-to-DC conversion efficiency is a constant regardless of its input.
+However, the harvester consists of an antenna to intercept RF signal and a diode rectifier (nonlinear device) to produce DC power, and the RF-to-DC efficiency indeed depends on the power and shape of the input waveform.
+By exploiting the joint impact of passive beamforming and harvester nonlinearity, we found that:
+			\begin{itemize}
+				\item the IRS should be developed next to the transmitter or the receiver due to double fading;
+				\item the optimal transceiving mode depends on the SNR and the number of subbands;
+				\item the power scaling laws of active and passive beamforming are in the order of $M^2$ and $L^4$, respectively;
+				\item the IRS reflection coefficient cannot be designed per subband and there exists a tradeoff in subchannel enhancement;
+				\item the optimal passive beamforming can be approximated in closed form for narrowband transmission but varies at different R-E points for broadband transmission.
+			\end{itemize}
 		\end{response}

### 2021-02-06 main.tex
:triangular_flag_on_post: arXiv draft 101220
:memo: Update response letter

@@
 			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
+
+			This paper has been submitted for publication.
 		}
@@
 An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
-As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by 16 times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
+As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
 Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective.

### 2021-02-07 response.tex
:memo: Update response letter

@@
 \setcounter{point}{0}
+\newcounter{response}[reviewer]
+\setcounter{response}{0}
+
+\let\svbibcite\bibcite
+\def\bibcite#1#2{\svbibcite{#1}{R#2}}
+\makeatletter
+\let\svbiblabel\@biblabel
+\def\@biblabel#1{\svbiblabel{R#1}}
+\makeatother
 
@@
 
+\renewcommand{\theresponse}
+	{\thereviewer.\arabic{response}}
+
 \newenvironment{point}
@@
 \newenvironment{response}
-	{\medskip \noindent \textbf{Response:}\ }
+	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
 	{\medskip}
@@
 			Thank you for pointing out the issue of CSI acquisition in presence of IRS.
-Practical protocols based on element-wise on/off switching \cite{Nadeem2019}, joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed to estimate the cascaded AP-IRS-user link for specific applications, yet channel estimation and codebook design for multi-carrier SWIPT remain unresolved and are beyond our current scope.
+Practical protocols based on element-wise on/off switching [24], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed to estimate the cascaded AP-IRS-user link for specific applications, yet channel estimation and codebook design for multi-carrier SWIPT remain unresolved and are beyond our current scope.
 The proposed algorithm is based on the assumption of cascaded CSIT (not individual AP-IRS and IRS-user ones) and can be readily extended to the imperfect CSIT case, where the joint waveform and beamforming design is based on a quantized CSI feedback.
@@
 It could be better if the authors can clarify if the proposed algorithm can be employed in a more general case where the base station and the IRS cooperate to serve multiple users in the same time slot.
+			\label{pt:1.2}
 		\end{point}
@@
 For any optimal information and power waveform $\boldsymbol{w}_{\mathrm{I}, n}^{\star}, \boldsymbol{w}_{\mathrm{P}, n}^{\star}$ on subband $n$, they generally cannot be decoupled as (25) because users have different channel response, and the optimization should be performed over complex field.
-Some attempts were made for WPT in \cite{Huang2017a}, but the extension to SWIPT is not straightforward as the power splitting ratio at all users require a joint update as well.
+Some attempts were made for WPT in [32], but the extension to SWIPT is not straightforward as the power splitting ratio at all users require a joint update as well.
 
@@
 It is not the intention of this paper and may be considered in our further research.
+			\label{re:1.2}
 		\end{response}
@@
 		\begin{response}
-			[How do we answer this question?]
+			We agree with the reviewer that the performance loss by relaxing the rank-one constraint deserves more attention.
+In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP to enable SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
+However, due to the reason mentioned in Response \ref{re:1.2}, we did not extend the work to multi-user SWIPT in this paper.
+
+			In contrast, the performance guarantee of rank relaxation in our single-user problem is only demonstrated by simulation.
+Due to the coupling of the information and power waveform, the objective function (23) involves
+			\begin{equation}
+				(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2 = \left(\mathrm{Tr}(\boldsymbol{C}_{\mathrm{I},0}\boldsymbol{\Phi^{(i)}}) - \mathrm{Tr}(\boldsymbol{C}_{\mathrm{P},0}\boldsymbol{\Phi^{(i)}})\right)^2 = \mathrm{Tr}\left((\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi^{(i)}}\right)^2
+			\end{equation}
+			which is not a semidefinite objective (due to the square).
+Also, the sum-rate constraint (24b) is not a semidefinite constraint.
+Therefore, existing SDR bounds cannot be applied directly to problem (24).
 		\end{response}
@@
 		\begin{point}
-			New RIS models are now being adopted as in \cite{Abeywickrama2019} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+			New RIS models are now being adopted as in [23] where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
 		\end{point}
@@
 		\begin{response}
-			The reviewer is referred to our response to Comment \ref{pt:1.1}.
+			The reviewer is referred to Response \ref{re:1.1}.
 Indeed, the assumption of perfect CSIT is very ideal and the existing protocols may not provide a good enough estimation in practice.
@@
 			the reflection coefficient not only has a magnitude smaller than 1 but also depends on the phase shift.
-\cite{Abeywickrama2019} found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.
+[23] found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.
 		\end{response}
@@
 		\begin{response}
-			% TODO
+			TODO
 		\end{response}
@@
 			Authors assumed the unrealistic situation: the channels are assumed to be perfectly known.
-However, in practice, the channel should be estimated, e.g., as studied in \cite{You2019}, \cite{Kang2020}.
+However, in practice, the channel should be estimated, e.g., as studied in \cite{Kang2020}, \cite{You2019}.
 It would be much better to discuss the channel estimation issue by citing the above references.
@@
 		\begin{response}
-			% TODO
+			The reviewer is referred to Response \ref{re:1.1}. We have incorporated the channel estimation issue into the revised manuscript by citing those references.
 		\end{response}

### 2021-02-15 response.tex
:memo: Update response letter

@@
 		\begin{response}
-			Thank you for pointing out the issue of CSI acquisition in presence of IRS.
-Practical protocols based on element-wise on/off switching [24], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed to estimate the cascaded AP-IRS-user link for specific applications, yet channel estimation and codebook design for multi-carrier SWIPT remain unresolved and are beyond our current scope.
-The proposed algorithm is based on the assumption of cascaded CSIT (not individual AP-IRS and IRS-user ones) and can be readily extended to the imperfect CSIT case, where the joint waveform and beamforming design is based on a quantized CSI feedback.
+			Thank you for pointing out the CSI acquisition issue in presence of IRS.
+To estimate the cascaded Tx-IRS-Rx link, practical protocols based on element-wise on/off switching [24], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed for specific networks.
+The proposed algorithm relies on such cascaded CSI (not individual Tx-IRS and IRS-Rx channels) at the transmitter (CSIT) and can be readily applied to the quantized CSIT case.
+However, the codebook design for SWIPT with harvester nonlinearity remains as an open issue and one particular challenge is how to evolve from the information codebook to satisfy the power demand.
 			\label{re:1.1}
@@
 			We appreciate your suggestion on IRS-aided multi-user SWIPT and believe it would be very promising.
-To extend the current work, we would first need to tackle the waveform and active beamforming design for a multi-user SWIPT system.
-For a multi-carrier network, each subcarrier only serves one information user but may serve all power user simultaneously (as whole received signal can be used for energy harvesting), and it involves an additional resource allocation problem that cannot be solved by the proposed GP algorithm.
+To that end, we would first need to tackle the waveform and beamforming design for a multi-user SWIPT system without IRS.
+Interestingly, in a multi-carrier network, each subcarrier only serves one information user but may serve all energy user simultaneously (the entire signal can be used for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
 
-			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT [see TODO] with corresponding waveform as given by (25), which decouples the design in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) thus satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
-Apparently, picking $s_{\mathrm{I/P}, n}$ as nonnegative value would maximize (27) and make (28) a real-value optimization problem, thus enable GP tools.
+			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT (see Response \ref{pt:2.2} for details) and the optimal waveform is given by (25), which decouples the design in the spatial domain (beamforming) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) to ensure the term involved in the sum rate (7) and DC components (10) -- (13) satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
+Apparently, picking $s_{\mathrm{I/P}, n}$ as nonnegative real value would not only maximize (27) but also make (28) an amplitude optimization problem and enable GP tools.
 
-			However, this is not generally the case in a multi-user scenario.
-For any optimal information and power waveform $\boldsymbol{w}_{\mathrm{I}, n}^{\star}, \boldsymbol{w}_{\mathrm{P}, n}^{\star}$ on subband $n$, they generally cannot be decoupled as (25) because users have different channel response, and the optimization should be performed over complex field.
-Some attempts were made for WPT in [32], but the extension to SWIPT is not straightforward as the power splitting ratio at all users require a joint update as well.
-
-			Extending our problem to the multi-user case would require first to solve relevant problems in the non-IRS case above.
-It is not the intention of this paper and may be considered in our further research.
+			However, this may not be the case in a multi-user scenario.
+At subband $n$, the composite channel is now $\boldsymbol{h}_{k, n}$ for user $k$ and the term above becomes $\boldsymbol{h}_{k, n}^H\boldsymbol{w}_{\mathrm{I/P},n}$.
+It is generally complex and require approaches other than GP to solve the highly non-convex optimization problem in complex field.
+Although the waveform and beamforming design for multi-user multi-carrier WPT was investigated in [32], the extension to SWIPT is not straightforward because the power splitting ratio of all users require a joint update as well.
 			\label{re:1.2}
@@
 As this is a very important and interesting conclusion to the colleagues working in the same area, it could be better if the authors can further discuss, interpret, and clarify this in a remark.
+			\label{pt:1.3}
 		\end{point}
@@
 		\begin{response}
+			Thank you for raising this issue.
 The rank-\num{1} property of $\boldsymbol{\Phi}$ to the relaxed problem (24) is suggested by simulation under different configurations.
-As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is hard to prove in theory due to the nonlinear objection function (24a) and the sum rate constraint (24b).
+As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is intricate to provide a mathematical proof due to the coupled objective (24a) and the sum log constraint (24b).
 Instead, we considered \num{300} individual channel realizations for different $M$, $N$ and $L$.
 The extensive numerical results show that the proposed SCA Algorithm 1 returned unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
-Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 is feasible to address the passive beamforming issue in IRS-aided SWIPT systems.
+
+			% TODO figs?
+
+			Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can return a feasible and reliable solution for general passive beamforming design.
+			\label{re:1.3}
 		\end{response}
@@
 			The figures in the current version are relatively small, it is suggested to provide larger figures to help the readers better understand the results.
+			\label{pt:1.4}
 		\end{point}
@@
 			We apologize for the inconvenience. The figures would be amplified in future versions.
+			\label{re:1.4}
 		\end{response}
@@
 It could be better if the authors can further discuss this issue for a more general multiple user scenario.
+			\label{pt:1.5}
 		\end{point}
@@
 Therefore, existing SDR bounds cannot be applied directly to problem (24).
+			\label{re:1.5}
 		\end{response}
@@
 			New RIS models are now being adopted as in [23] where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+			\label{pt:2.1}
 		\end{point}
@@
 We actually thought about integrating these new models in our system design, but finally decided to use the most common and simplest IRS model in the current stage to reduce the design complexity and provide a primary benchmark for IRS-aided SWIPT.
+			\label{re:2.1}
 		\end{response}
@@
 			Why is MRT considered as precoder by (25) rather than optimizing it? Is it globally optimal too?
+			\label{pt:2.2}
 		\end{point}
@@
 However, this is not the case for multi-user SWIPT (since users have different channels) where the beamformer and power allocation require a joint optimization.
+			\label{re:2.2}
 		\end{response}
@@
 			Some strong assumptions like perfect CSI availability limit the practical utility of the proposed analytical results.
+			\label{pt:2.3}
 		\end{point}
@@
 We follow the convention of most existing papers on this topic and expect some breakthroughs in future research.
+			\label{re:2.3}
 		\end{response}
@@
 			All the assumptions and relaxations adopted used in the derivation of results as in (23) need to be explicitly mentioned along with appropriate justification for the same.
+			\label{pt:2.4}
 		\end{point}
@@
 We start from any feasible point and approach the original solution by SCA.
+			\label{re:2.4}
 		\end{response}
@@
 			Some transformations have been made while solving the original problem, but it has not been explicitly mentioned whether it is equivalent to transformation or not.
+			\label{pt:2.5}
 		\end{point}
@@
 			Thank you for pointing this out. All transformations are equivalent to their original form and we would make this clear in the revised manuscript.
+			\label{re:2.5}
 		\end{response}
@@
 			Are the proposed solutions locally optimal or globally optimal? It is not clear whether the convergence of proposed solution methodologies is local or global? Also, how fast is it?
+			\label{pt:2.6}
 		\end{point}
@@
 The AO-based Algorithm 3 typically converge within 3 iterations.
+			\label{re:2.6}
 		\end{response}
@@
 So, the authors would like to justify it so that the proposed solution can be obtained over relatively short coherence intervals.
+			\label{pt:2.7}
 		\end{point}
@@
 			% TODO: branch and bound / complexity analysis
+			\label{re:2.7}
 		\end{response}
@@
 			How practical is it to consider lossless reflection from the RIS? Specifically, by considering the magnitude to be 1, the reflection losses at the RIS have been ignored.
+			\label{pt:2.8}
 		\end{point}
@@
 [23] found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.
+			\label{re:2.8}
 		\end{response}
@@
 			Minor comment: The size of all the numerical results figures is too small.
+			\label{pt:2.9}
 		\end{point}
@@
 			We apologize for the inconvenience. The figures would be amplified in future versions.
+			\label{re:2.9}
 		\end{response}
@@
 			First of all, motivations of studying the IRS on SWIPT is very unclear to me. Please clarify.
+			\label{pt:3.1}
 		\end{point}
@@
 Therefore, we believe the effective channel enhancement and the low power consumption of IRS is a perfect match for SWIPT.
+			\label{re:3.1}
 		\end{response}
@@
 			Also, the contributions of this work are rather unclear, and thus, those should be better mentioned.
+			\label{pt:3.2}
 		\end{point}
@@
 			\end{itemize}
+			\label{re:3.2}
 		\end{response}
@@
 			Please explain the derived results more intuitively for better understanding.
+			\label{pt:3.3}
 		\end{point}
@@
 			TODO
+			\label{re:3.3}
 		\end{response}
@@
 It would be much better to discuss the channel estimation issue by citing the above references.
+			\label{pt:3.4}
 		\end{point}
@@
 			The reviewer is referred to Response \ref{re:1.1}. We have incorporated the channel estimation issue into the revised manuscript by citing those references.
+			\label{re:3.4}
 		\end{response}
@@
 			More simulation results should be added to better and aggregately validate the effectiveness of the proposed method.
+			\label{pt:3.5}
 		\end{point}
@@
 			TODO
+			\label{re:3.5}
 		\end{response}
@@
 			The sizes of figures are too small.
+			\label{pt:3.6}
 		\end{point}
@@
 			We apologize for the inconvenience. The figures would be amplified in future versions.
+			\label{re:3.6}
 		\end{response}

### 2021-02-18 response.tex
:memo: Update response letter

@@
 To estimate the cascaded Tx-IRS-Rx link, practical protocols based on element-wise on/off switching [24], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed for specific networks.
-The proposed algorithm relies on such cascaded CSI (not individual Tx-IRS and IRS-Rx channels) at the transmitter (CSIT) and can be readily applied to the quantized CSIT case.
+The proposed Algorithm 1 relies on such cascaded CSI (not individual Tx-IRS and IRS-Rx channels) at the transmitter (CSIT) and can be readily applied to the quantized CSIT case.
 However, the codebook design for SWIPT with harvester nonlinearity remains as an open issue and one particular challenge is how to evolve from the information codebook to satisfy the power demand.
@@
 To that end, we would first need to tackle the waveform and beamforming design for a multi-user SWIPT system without IRS.
-Interestingly, in a multi-carrier network, each subcarrier only serves one information user but may serve all energy user simultaneously (the entire signal can be used for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
+Interestingly, in a multi-carrier network, each subcarrier only serves one information user at a time but may serve all energy user simultaneously (use the entire signal for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
 
@@
 At subband $n$, the composite channel is now $\boldsymbol{h}_{k, n}$ for user $k$ and the term above becomes $\boldsymbol{h}_{k, n}^H\boldsymbol{w}_{\mathrm{I/P},n}$.
-It is generally complex and require approaches other than GP to solve the highly non-convex optimization problem in complex field.
-Although the waveform and beamforming design for multi-user multi-carrier WPT was investigated in [32], the extension to SWIPT is not straightforward because the power splitting ratio of all users require a joint update as well.
+It is generally complex and require other approaches to solve the highly non-convex optimization problem in the complex field.
+Although the waveform and beamforming design for multi-user multi-carrier WPT has been investigated in [32], the extension to SWIPT is not straightforward as the power splitting ratio of all users also require a joint update, which prevents the SDR method to be directly applied.
 			\label{re:1.2}
@@
 			Thank you for raising this issue.
-The rank-\num{1} property of $\boldsymbol{\Phi}$ to the relaxed problem (24) is suggested by simulation under different configurations.
-As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is intricate to provide a mathematical proof due to the coupled objective (24a) and the sum log constraint (24b).
-Instead, we considered \num{300} individual channel realizations for different $M$, $N$ and $L$.
-The extensive numerical results show that the proposed SCA Algorithm 1 returned unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
+The rank-\num{1} property of $\boldsymbol{\Phi}$ to the relaxed problem (24) is suggested by CVX toolbox under different configurations.
+As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is intricate to provide a mathematical proof due to the coupled objective (24a) and the log sum constraint (24b).
+Instead, we considered \num{300} individual channel realizations for different $M$, $N$, $L$ and employed \num{30} samples (corresponding to \num{30} sum rate constraints) for each individual R-E region.	The extensive numerical results show that the proposed SCA Algorithm 1 returned unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
 
@@
 
-			Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can return a feasible and reliable solution for general passive beamforming design.
+			Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can provide a feasible and reliable passive beamformer in general SWIPT systems.
 			\label{re:1.3}
@@
 		\begin{response}
-			We apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
 			\label{re:1.4}
@@
 			We agree with the reviewer that the performance loss by relaxing the rank-one constraint deserves more attention.
-In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP to enable SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
+In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user multi-carrier WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP to enable SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
 However, due to the reason mentioned in Response \ref{re:1.2}, we did not extend the work to multi-user SWIPT in this paper.
@@
 			\end{equation}
-			which is not a semidefinite objective (due to the square).
-Also, the sum-rate constraint (24b) is not a semidefinite constraint.
-Therefore, existing SDR bounds cannot be applied directly to problem (24).
+			which consists of trace square and is not a semidefinite expression.
+Compared with standard SDP, problem (24) also introduces an additional log sum constraint (24b) for communication purpose, and the existing SDR bounds cannot be applied directly for performance guarantee.
 			\label{re:1.5}
@@
 		\begin{response}
-			Thank you for sharing this acknowledged paper, which investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
+			Thank you for sharing this acknowledged paper.
+It investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
 It also proposed an analytical IRS model together with an AO algorithm to maximize the achievable rate by passive beamforming.
 Simulation results emphasized the importance of modeling such a relationship in practical IRS design.
-We actually thought about integrating these new models in our system design, but finally decided to use the most common and simplest IRS model in the current stage to reduce the design complexity and provide a primary benchmark for IRS-aided SWIPT.
+We actually thought about integrating these new models in our system design, but finally decided to use the most common and simplest IRS model in the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
 			\label{re:2.1}
@@
 		\begin{response}
-			The waveform design involves the optimization in the spatial domain (beamformer) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$).
-For the single-user scenario, MRT is global optimal for both information and power transmission.
-This is because the sum rate (7) and DC components (10) -- (13) only involve waveform in terms of $\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n}$ thus can be simultaneously maximized by MRT precoder.
-However, this is not the case for multi-user SWIPT (since users have different channels) where the beamformer and power allocation require a joint optimization.
+			In the single-user scenario, MRT is the global optimal information and power precoder. We decouple the waveform in the spatial and frequency domain by
+			\begin{equation}
+				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \bar{\boldsymbol{w}}_{\mathrm{I/P}, n}
+			\end{equation}
+			where $s_{\mathrm{I/P},n}^2$ denote the power allocated to the information/power waveform at subband $n$, and $\bar{\boldsymbol{w}}_{\mathrm{I/P}, n}$ is the active beamformer at subband $n$.
+For simplicity, we define $s_{\mathrm{I/P}, n}$ as nonnegative real value (as the phase can be included in the beamformer).	From the information perspective, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = s_{\mathrm{I}, n} \lvert{\boldsymbol{h}_{n}^H \bar{\boldsymbol{w}}_{\mathrm{I}, n}}\rvert$ thus maximizes the sum rate (7).
+From the energy perspective, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^*$ thus maximizes the second and fourth order DC terms (10) -- (13).
+Therefore, MRT is the global optimal information and power precoder.
+However, this is not the case for the multi-user scenario where the beamformer and power allocation require a joint optimization.
 			\label{re:2.2}
@@
 Indeed, the assumption of perfect CSIT is very ideal and the existing protocols may not provide a good enough estimation in practice.
-We follow the convention of most existing papers on this topic and expect some breakthroughs in future research.
+We follow the convention of most existing papers on this topic and expect some breakthroughs in the future research.
 			\label{re:2.3}
@@
 		\begin{response}
-			We appreciate your suggestion.
-The original objective function (19) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by their first-order local Taylor expansions (20) -- (22) to formulate a series of convex problems.
-These problems are SCA to the original passive beamforming problem (maximize (19) s.t.
-(24b) -- (24e)), and the objective function (23) is obtained by plugging (20) -- (22) into (19), which is an affine and satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$.
-We start from any feasible point and approach the original solution by SCA.
+			We appreciate your suggestion and have revised the manuscript correspondingly.
+The original objective function (19) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (20) -- (22) to formulate SCA problems of the original passive beamforming problem, i.e.
+maximize (19) s.t.
+(24b) -- (24e).
+Specifically, the objective affine function (23) is obtained by plugging (20) -- (22) into (19) and it satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$.
 			\label{re:2.4}
@@
 		\begin{response}
-			Thank you for pointing this out. All transformations are equivalent to their original form and we would make this clear in the revised manuscript.
+			Thank you for the reminder. All transformations are equivalent to their original form and we have make this clear in the revised manuscript.
 			\label{re:2.5}
@@
 			Algorithm 1 -- 3 only provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
-For different sum rate constraints, we use water-filling with MRT to initialize the modulated waveform while use scaled matched filter to initialize the unmodulated waveform (corresponding to a transmit power of $2P$, regulated afterwards).
-We also initialize the IRS phase shift by uniform distribution over $[0, 2\pi)$.
-Nevertheless, as the solutions are locally optimal, some result points on the R-E boundary may be strictly worse (with lower rate and energy) than another, especially for a large $M$ and $L$.
-To address this, we draw the R-E boundary from high-rate low-energy (lower right) points to low-rate high-energy (upper left) points.
-If the issue above happens, we discard the dominated result and reinitialize the waveform and IRS phase shift by the solution at the previous point.
+For different sum rate constraints, we use water-filling with MRT to initialize the modulated waveform while use scaled matched filter to initialize the unmodulated waveform (corresponding to a total power of $2P$, regulated afterwards).
+The phase shift of each IRS element is initialized as i.i.d.
+uniform random variables over $[0, 2\pi)$.
+Nevertheless, as the algorithms only converge to local optimal, few R-E points might be strictly worse (in terms of both rate and energy) than the others, especially when $M$ and $L$ are very large.
+To address this issue, we draw the R-E boundary from the high-rate low-energy (lower right) points to the low-rate high-energy (upper left) points.
+If a point is strictly dominated, we discard the candidate, reinitialize the waveform and IRS phase shift by the solution at the previous point, then perform the optimization again.
 
-			For a tolerance of $\epsilon=10^{-8}$, the SDR-based Algorithm 1 usually converge within 3 iterations while the GP-based Algorithm 2 tends to converge within 8 iterations.
-The AO-based Algorithm 3 typically converge within 3 iterations.
+			For a tolerance of $\epsilon=10^{-8}$, the SDR-based Algorithm 1 usually converge within 2 iterations while the GP-based Algorithm 2 tends to converge within 8 iterations.
+The AO-based Algorithm 3 typically converge within 2 iterations.
+Unfortunately, the complexity analysis is very challenging as the optimization problems are in intricate form.
+			and the existing works
 			\label{re:2.6}
@@
 		\begin{response}
-			We agree with the reviewer that the proposed algorithm (especially Algorithm 2) could be too time-consuming for practical applications with relatively short coherence time.
-The proposed algorithms ensure best performance by iteratively solving intricate optimization problems and may not be implemented in practice, while suboptimal design (e.g.
-scaled matched filter) is expected to achieve a good performance.
+			We agree that the proposed algorithm (especially Algorithm 2) could be very time-consuming for applications with short coherence time.
+The proposed algorithms ensure optimal performance by iteratively solving intricate optimization problems.
+Although suboptimal design in closed form (e.g.
+scaled matched filter) has been proved effective in practical WPT systems, the extension to SWIPT is much more challenging because the two waveforms and the splitting ratio need to be jointly designed under the influence of SNR.
 
@@
 		\begin{response}
-			We apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
 			\label{re:2.9}
@@
 		\begin{response}
-			We apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
 			\label{re:3.6}

### 2021-02-19 response.tex
:memo: Update response letter

@@
 The proposed Algorithm 1 relies on such cascaded CSI (not individual Tx-IRS and IRS-Rx channels) at the transmitter (CSIT) and can be readily applied to the quantized CSIT case.
-However, the codebook design for SWIPT with harvester nonlinearity remains as an open issue and one particular challenge is how to evolve from the information codebook to satisfy the power demand.
+However, the codebook design for SWIPT with harvester nonlinearity remains an open issue and one particular challenge is how to evolve from the information codebook to satisfy the power demand.
 			\label{re:1.1}
@@
 To that end, we would first need to tackle the waveform and beamforming design for a multi-user SWIPT system without IRS.
-Interestingly, in a multi-carrier network, each subcarrier only serves one information user at a time but may serve all energy user simultaneously (use the entire signal for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
+Note that in a multi-carrier network, each subcarrier only serves one information user at a time but may serve all energy user simultaneously (use the entire signal for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
 
@@
 It is generally complex and require other approaches to solve the highly non-convex optimization problem in the complex field.
-Although the waveform and beamforming design for multi-user multi-carrier WPT has been investigated in [32], the extension to SWIPT is not straightforward as the power splitting ratio of all users also require a joint update, which prevents the SDR method to be directly applied.
+Although the waveform and beamforming design for multi-user multi-carrier WPT has been investigated in [32], the extension to SWIPT is not straightforward as the power splitting ratio of all users also require a joint update and the SDR method cannot be applied directly.
 			\label{re:1.2}
@@
 As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is intricate to provide a mathematical proof due to the coupled objective (24a) and the log sum constraint (24b).
-Instead, we considered \num{300} individual channel realizations for different $M$, $N$, $L$ and employed \num{30} samples (corresponding to \num{30} sum rate constraints) for each individual R-E region.	The extensive numerical results show that the proposed SCA Algorithm 1 returned unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
+Instead, we considered \num{300} individual channel realizations for different $M$, $N$, $L$ and employed \num{30} samples (corresponding to \num{30} problems with different sum rate constraints) for each individual R-E region.
+The extensive numerical results show that the proposed SCA Algorithm 1 found a unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
+Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can provide a feasible and reliable passive beamformer in general SWIPT systems.
 
-			% TODO figs?
-
-			Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can provide a feasible and reliable passive beamformer in general SWIPT systems.
+			[To add a CDF plot of max eigenvalue over sum eigenvalue, which is almost always 1. The simulation is still running.]
 			\label{re:1.3}
@@
 			We agree with the reviewer that the performance loss by relaxing the rank-one constraint deserves more attention.
-In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user multi-carrier WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP to enable SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
+In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user multi-carrier WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP, enabling an SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
 However, due to the reason mentioned in Response \ref{re:1.2}, we did not extend the work to multi-user SWIPT in this paper.
 
-			In contrast, the performance guarantee of rank relaxation in our single-user problem is only demonstrated by simulation.
+			In contrast, the performance guarantee of rank relaxation in our single-user problem is simply demonstrated by simulation.
 Due to the coupling of the information and power waveform, the objective function (23) involves
@@
 			which consists of trace square and is not a semidefinite expression.
-Compared with standard SDP, problem (24) also introduces an additional log sum constraint (24b) for communication purpose, and the existing SDR bounds cannot be applied directly for performance guarantee.
+Compared with standard SDP, problem (24) also introduces an additional log sum constraint (24b) for communication purpose, and the existing SDR bounds cannot be applied directly in this case.
 			\label{re:1.5}
@@
 		\begin{response}
-			In the single-user scenario, MRT is the global optimal information and power precoder. We decouple the waveform in the spatial and frequency domain by
+			In the single-user scenario, MRT is the global optimal information and power precoder. We can decouple the waveform in the spatial and frequency domain by
 			\begin{equation}
@@
 			where $s_{\mathrm{I/P},n}^2$ denote the power allocated to the information/power waveform at subband $n$, and $\bar{\boldsymbol{w}}_{\mathrm{I/P}, n}$ is the active beamformer at subband $n$.
-For simplicity, we define $s_{\mathrm{I/P}, n}$ as nonnegative real value (as the phase can be included in the beamformer).	From the information perspective, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = s_{\mathrm{I}, n} \lvert{\boldsymbol{h}_{n}^H \bar{\boldsymbol{w}}_{\mathrm{I}, n}}\rvert$ thus maximizes the sum rate (7).
+For simplicity, we define $s_{\mathrm{I/P}, n}$ as nonnegative real value (as the phase can be included in the beamformer).
+From the information perspective, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = s_{\mathrm{I}, n} \lvert{\boldsymbol{h}_{n}^H \bar{\boldsymbol{w}}_{\mathrm{I}, n}}\rvert$ thus maximizes the sum rate (7).
 From the energy perspective, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^*$ thus maximizes the second and fourth order DC terms (10) -- (13).
@@
 The AO-based Algorithm 3 typically converge within 2 iterations.
-Unfortunately, the complexity analysis is very challenging as the optimization problems are in intricate form.
-			and the existing works
+Unfortunately, the complexity analysis is very challenging as problem (24) and (32) are both in intricate form.
 			\label{re:2.6}
@@
 The proposed algorithms ensure optimal performance by iteratively solving intricate optimization problems.
-Although suboptimal design in closed form (e.g.
-scaled matched filter) has been proved effective in practical WPT systems, the extension to SWIPT is much more challenging because the two waveforms and the splitting ratio need to be jointly designed under the influence of SNR.
-
-			% TODO: branch and bound / complexity analysis
+Although the effectiveness of suboptimal design in closed form (e.g.
+scaled matched filter) has been validated in practical WPT systems, the extension to SWIPT is much more challenging because both waveforms and the splitting ratio need to be balanced under the influence of SNR.
 			\label{re:2.7}
@@
 		\begin{response}
-			Green's decomposition indicates that the backscattered/reflected signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+			Green's decomposition suggests that the backscattered/reflected signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
 The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
@@
 			which corresponds to the lossless reflection model adopted in the paper.
-Nevertheless, due to the non-zero power consumption at the IRS in practice, $R_l$ would be positive and $\lvert{\phi_l}\rvert$ indeed depends on the
-			the reflection coefficient not only has a magnitude smaller than 1 but also depends on the phase shift.
+Nevertheless, due to the non-zero power consumption at the IRS in practice, $R_l$ would be positive and the reflection coefficient $\phi_l$ not only has a magnitude smaller than 1 but also depends on the phase shift.
 [23] found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.

### 2021-02-25 main.tex
:sparkles: Low-complexity design

@@
 		\end{subsection}
+
+		\begin{subsection}{Low-Complexity Adaptive Design}
+			The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
+			\begin{equation}
+				s_{\mathrm{I}, n} = \sqrt{\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+			\end{equation}
+			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+The closed-form solution can be obtained by iterative power allocation and the details are omitted here.
+On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT.
+It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
+			\begin{equation}
+				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
+			\end{equation}
+			where the only design variable $\beta \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
+$\beta = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\beta > 1$ further elevates the strong subchannels and suppresses the weak ones.
+The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.
+
+			To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	The low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \alpha$ and dedicated energy session with proportion $\alpha$, then performs WF and SMF respectively.
+Varying $\alpha$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point.
+In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
+			\begin{align}
+				s_{\mathrm{I}, n} &= \sqrt{(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
+			\end{align}
+			That is to say, the suboptimal TS scheme only need to design $\beta$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
+		\end{subsection}
 	\end{section}

### 2021-02-28 main.tex
:pencil: Add reflection pattern

@@
 To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by a passive beamforming gain.
-This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS.
-Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user.
+This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS.
+Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the UE.
 Stationary solutions are achieved by the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.
@@
 
-		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands at frequency $f_n$ ($n=1,\dots,N$).
-We consider a quasi-static block fading channel model and focus on one particular block where the channel responses are constant.
-It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP.
-Two practical transceiving modes, TS and PS, are compared in terms of the achievable R-E region.
-Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT).
-In comparison, PS splits the received signal into individual information and power streams such that the splitting ratio $\rho$ is coupled with the waveform and beamforming design.
-Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.
+		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna User Equipment (UE) over $N$ orthogonal evenly-spaced subbands.
+We consider a quasi-static block fading model and focus on an instance where all channels are constant.
+The AP is assumed to have partial or perfect Channel State Information (CSI) of the AP-UE channel and the cascaded AP-IRS-UE channel.
+We also omit the signals reflected two and more times and assume the noise power is too small to be harvested.
 
-		\begin{subsection}{Transmit Signal}
-			Denote $\tilde{x}_{\mathrm{I},n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$.
-The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
+		\begin{subsection}{Transmitted Signal}
+			Denote $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ as the information symbol transmitted over subband $n \in \{1, \dots, N\}$.
+The superposed signal transmitted on antenna $m \in \{1, \dots, M\}$ at time $t$ is
 			\begin{equation}\label{eq:x_m}
@@
 			\end{equation}
-			where $w_{\mathrm{I/P},n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$.
-Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T \triangleq \boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
+			where $w_{\mathrm{I/P},n,m}$ denotes the complex weight of the modulated/multisine waveform transmitted at subband $n$ on antenna $m$, and $f_n$ is the frequency of subband $n$.
+On top of this, we stack up $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T \triangleq \boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
 			\begin{align}
 				\boldsymbol{x}_{\mathrm{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
-				\boldsymbol{x}_{\mathrm{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}.\label{eq:x_P}
+				\boldsymbol{x}_{\mathrm{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
 			\end{align}
+			are the modulated and multisine components, respectively.
 		\end{subsection}
 
-		\begin{subsection}{Composite Channel}
-			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1$, $\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}.
-Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries.
-The auxiliary link introduced by the IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel.
-On top of this, the total composite channel is obtained by superposing the AP-IRS-user auxiliary channel to the AP-user direct channel as
+		\begin{subsection}{Reflection Pattern and Composite Channel}
+			Green's decomposition \cite{Hansen1989} suggests that the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
+IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ in a fully passive manner to reflect the incoming signal, and the reflection coefficient is defined as
+			\begin{equation}
+				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
+			\end{equation}
+			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude, and $\theta_l \in [0,2\pi)$ is the phase shift~\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and depends on $\theta_l$.
+This paper sticks to the commonest and simplest IRS model where the reflection coefficient is assumed unit.}.
+We also denote $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ as the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
+
+			\begin{remark}\label{re:reflection_coefficient}
+				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
+Since the reactance $X_l$ depends on frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
+In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficients of each IRS element are the same at all subbands.
+That is to say, $\phi_l$ is shared by $M$ AP-IRS-UE channels over $N$ subbands.
+			\end{remark}
+
+			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary link provided by the IRS can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
+Therefore, the composite equivalent channel reduces to
 			\begin{equation}\label{eq:h_n}
@@
 			\end{equation}
-			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
-Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
-			\begin{remark}\label{re:irs_frequency_flat}
-				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat.
-Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
-The reflection coefficient of each IRS element is shared by the corresponding $M$ AP-IRS-user channels over $N$ subbands.
-			\end{remark}
+			where we define $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 		\end{subsection}
 
-		\begin{subsection}{Receive Signal}
-			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$ captures the contribution from information and power components over all subbands, where
+		\begin{subsection}{Received Signal}
+			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
 			\begin{align}
 				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
-				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}.\label{eq:y_P}
+				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
 			\end{align}
+			capture the contribution of modulated and multisine waveforms over all subbands.
+Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information purpose.
+		\end{subsection}
+
+		\begin{subsection}{Transceiving Modes}
+			Consider TS and PS as two practical transceiving modes in the SWIPT system design.
+TS relies on perfect clock synchronization, where the transmitter divides each slot into dedicated data session with length $1 - \eta$ and energy session with length $\eta$, then designs the waveform for WIT and WPT independently.
+At the receiver end, only information decoder or energy harvester would be activated in the corresponding session.
+Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E segment from WIT point to WPT point.
+
+			On the other hand, the PS transmitter optimizes the superposed waveform that remains unchanged in the entire slot, and the receiver splits the incoming signal into individual data stream with power proportion $1 - \rho$ and energy stream with power proportion $\rho$.
+Note that in PS the splitting ratio $\rho$ and the superposed waveform are coupled thus require a joint design, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
+Therefore, we focus on PS in the following context since TS can be obtained by a direct time sharing between WIT and WPT.
 		\end{subsection}
@@
 		\begin{subsection}{Information Decoder}
-			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
+			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
 			\begin{equation}\label{eq:R}
@@
 
-			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received waveform.
+			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received signal.
 Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
@@
 Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
-Inspired by \cite{Huang2017}, we stack up the channel and waveform vectors over all subbands as $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, then define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
@@
 			% \end{equation}
-			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sine waves to the average power.
+			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sinewaves to the average power.
 		\end{subsection}
@@
 			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
-Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands.
+Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands.
 In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
@@
 
-		\begin{subsection}{IRS Phase Shift}
-			In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. We observe that
+		\begin{subsection}{Passive Beamforming}
+			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
 			\begin{align}
@@
 
-		\begin{subsection}{Waveform, Active Beamforming and Splitting Ratio}
+		\begin{subsection}{Active Beamforming}
+			In the single-user scenario, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
+			\begin{equation}
+				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
+			\end{equation}
+			where $s_{\mathrm{I/P},n}$ are the amplitude of modulated/multisine waveform at tone $n$ and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denote the corresponding precoders.
+The optimal MRT precoder at subband $n$ is given by
+			\begin{equation}
+				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
+			\end{equation}
+			From the perspective of data transmission, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the sum rate \eqref{eq:R}.
+From the perspective of energy harvesting, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+Hence, MRT is the global optimal precoder and no dedicated energy beams are required in the single-user SWIPT.
+		\end{subsection}
+
+		\begin{subsection}{Waveform and Splitting Ratio}
 			Next, we jointly optimize the waveform and active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
+			\begin{subsubsection}{Waveform and Active Beamforming}
 				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
@@
 
-			To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	The low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \alpha$ and dedicated energy session with proportion $\alpha$, then performs WF and SMF respectively.
-Varying $\alpha$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point.
+				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively.
+Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point.
 In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
@@
 				That is to say, the suboptimal TS scheme only need to design $\beta$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
+			\end{subsubsection}
 		\end{subsection}
@@
 Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference.
-As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-user path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
+As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
 We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$.
@@
 A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\mathrm{I}}\Lambda_R$.
-It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the user.
+It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the UE.
 
@@
 In contrast to Remark~\ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for $NL$ variables in total.
-When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-user channel to the AP-user channel at all subbands, namely
+When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-UE channel to the AP-UE channel at all subbands, namely
 		\begin{equation}

### 2021-03-05 src/config/config_re_reflector.m
:art: Improve logic

@@ -4,6 +4,8 @@ k2 = 0.0034;
 k4 = 0.3829;
 % antenna resistance
 resistance = 50;
+% scale ratio of SMF
+alpha = 1;
 % coefficients on current terms
 beta2 = k2 * resistance;
 beta4 = k4 * resistance ^ 2;

### 2021-03-05 src/lib/current_sdr.m

@@ -1,0 +1,48 @@
+function [current] = current_sdr(beta2, beta4, channelAmplitude, infoAmplitude, powerAmplitude, powerRatio)
+    % Function:
+    %   - formulate output DC current as a function of waveform amplitudes
+    %
+    % Input:
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
+    %   - channelAmplitude (a) [nSubbands * 1]: channel amplitude response
+    %   - infoAmplitude (s_I) [1 * nSubbands]: amplitude on information carriers
+    %   - powerAmplitude (s_P) [1 * nSubbands]: amplitude on power carriers
+    %   - powerRatio (\rho): power splitting ratio
+    %
+    % Output:
+    %	- current (z): objective function to maximize output DC current
+    %
+    % Comment:
+    %   - based on SDR expression
+    %
+    % Author & Date: Yang (i@snowztail.com) - 05 Mar 21
+
+
+	% * Get data
+	nSubbands = size(channelAmplitude, 1);
+
+	% * Construct coefficient matrices
+    % \boldsymbol{S}_{I/P}
+    infoMatrix = vec(infoAmplitude) * vec(infoAmplitude)';
+	powerMatrix = vec(powerAmplitude) * vec(powerAmplitude)';
+
+    % \boldsymbol{A}_n
+    channelMatrix = channelAmplitude * channelAmplitude';
+	channelBlkDiag = block_diagonal(channelMatrix, 1, nSubbands);
+
+    % * Initialize auxiliaries
+    % t'_{I/P,n}
+    infoAuxiliary = zeros(2 * nSubbands - 1, 1);
+    powerAuxiliary = zeros(2 * nSubbands - 1, 1);
+    for iSubband = - nSubbands + 1 : nSubbands - 1
+        infoAuxiliary(iSubband + nSubbands) = trace(channelBlkDiag{iSubband + nSubbands} * infoMatrix);
+        powerAuxiliary(iSubband + nSubbands) = trace(channelBlkDiag{iSubband + nSubbands} * powerMatrix);
+    end
+
+	% * Update output current
+	current = (1 / 2) * beta2 * powerRatio * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
[…]

### 2021-03-05 src/lib/initialize_waveform.m

@@ -1,8 +1,11 @@
-function [infoAmplitude, powerAmplitude, infoRatio, powerRatio] = initialize_waveform(channel, txPower, noisePower)
+function [infoAmplitude, powerAmplitude, infoRatio, powerRatio] = initialize_waveform(alpha, beta2, beta4, channel, txPower, noisePower)
     % Function:
     %   - initialize waveform and splitting ratio for GP algorithm
     %
     % Input:
+    %   - alpha: scale ratio of SMF
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
     %   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
     %   - txPower (P): average transmit power budget
     %   - noisePower (\sigma_n^2): average noise power
@@ -14,30 +17,32 @@ function [infoAmplitude, powerAmplitude, infoRatio, powerRatio] = initialize_wav
     %   - powerRatio (\rho): power splitting ratio
     %
     % Comment:
-    %   - the iterative GP algorithm is sensitive to initialization (only converges to stationary point)
+    %   - the iterative GP algorithm is sensitive to initialization (only converges to stationary points)
     %   - GP requires nonzero entries thus use eps to replace zero
     %   - cvx crashes when initial rate is far from constraint
     %       - use scaled matched filter to initialize power waveform with power P
     %       - use water-filling + MRT to initialize information waveform with power P
     %       - initialize both splitting ratio to 1
+	%		- regulated over iterations
+	%	- if the number of subbands is too small, it is unnecessary to use multisine waveform
     %
     % Author & Date: Yang (i@snowztail.com) - 31 Jul 20
 
 
-    % * Get equivalent channel gain
-    channelAmplitude = vecnorm(channel, 2, 2);
+	% * Get data
+	nSubbands = size(channel, 1);
 
-    % * Initialize algorithm
-    infoRatio = 1;
-    powerRatio = 1;
+	% * Initialize modulated waveform by WF
 	[~, infoAmplitude] = water_filling(channel, txPower, noisePower);
 
-	% * If number of subbands is too small, it is unnecessary to use power waveform
-	nSubbands = size(channel, 1);
+	% * If necessary, initialize multisine waveform by SMF
 	if nSubbands <= 2
 		powerAmplitude = zeros(1, nSubbands) + eps;
 	else
[…]

### 2021-03-05 src/lib/re_sample_swipt_gp.m

@@ -1,8 +1,9 @@
-function [sample, solution] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance)
+function [sample, solution] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance)
     % Function:
     %   - sample R-E region by computing the output DC current and rate
     %
     % Input:
+    %   - alpha: scale ratio of SMF
     %   - beta2: coefficients on second-order current terms
     %   - beta4: coefficients on fourth-order current terms
     %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
@@ -19,7 +20,7 @@ function [sample, solution] = re_sample(beta2, beta4, directChannel, incidentCha
     %   - solution: IRS reflection coefficient, composite channel, waveform, splitting ratio and eigenvalue ratio
     %
     % Comment:
-    %   - suboptimal algorithm only converge to stationary points
+    %   - AO algorithm only converge to stationary points
     %   - proceed from high rate points to high current points
     %   - results are sensitive to initialization
     %   - under default initialization, some samples may be strictly worse than previous ones (especially for a large number of transmit antennas or reflectors)
@@ -32,7 +33,8 @@ function [sample, solution] = re_sample(beta2, beta4, directChannel, incidentCha
     solution = cell(nSamples, 1);
 
     % * Initialize algorithm by WIT point and set rate constraints
-    [sample(:, 1), solution{1}] = re_sample_wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+    [sample(:, 1), solution{1}] = re_sample_wit_wf(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+	irs = solution{1}.irs;
     compositeChannel = solution{1}.compositeChannel;
     rateConstraint = linspace(sample(1, 1), 0, nSamples);
 
@@ -42,12 +44,12 @@ function [sample, solution] = re_sample(beta2, beta4, directChannel, incidentCha
         while true
             if ~isDominated
                 % * Default initialization
[…]

### 2021-03-05 src/lib/re_sample_swipt_gp_benchmark.m

@@ -1,8 +1,9 @@
-function [sample, solution] = re_sample_nonadaptive_channel(beta2, beta4, channel, txPower, noisePower, nSamples, tolerance)
+function [sample, solution] = re_sample_swipt_gp_benchmark(alpha, beta2, beta4, channel, txPower, noisePower, nSamples, tolerance)
     % Function:
     %   - sample R-E region by computing the output DC current and rate
     %
     % Input:
+    %   - alpha: scale ratio of SMF
     %   - beta2: coefficients on second-order current terms
     %   - beta4: coefficients on fourth-order current terms
     %   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
@@ -45,13 +46,13 @@ function [sample, solution] = re_sample_nonadaptive_channel(beta2, beta4, channe
         while true
             if ~isDominated
                 % * Default initialization
-                [infoAmplitude, powerAmplitude, infoRatio, powerRatio] = initialize_waveform(channel, txPower, noisePower);
+                [infoAmplitude, powerAmplitude, infoRatio, powerRatio] = initialize_waveform(alpha, beta2, beta4, channel, txPower, noisePower);
             else
                 % * Initialize with previous solution
                 struct2variables(solution{iSample - 1});
             end
             % * Optimize waveform with WIT-optimized IRS
-            [infoAmplitude, powerAmplitude, infoRatio, powerRatio, rate, current] = waveform_gp(beta2, beta4, channel, infoAmplitude, powerAmplitude, infoRatio, powerRatio, txPower, noisePower, rateConstraint(iSample), tolerance);
+            [rate, current, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = waveform_gp(beta2, beta4, channel, infoAmplitude, powerAmplitude, infoRatio, powerRatio, txPower, noisePower, rateConstraint(iSample), tolerance);
 
             % * Check whether strictly dominated
             isDominated = current <= sample(2, iSample - 1);

### 2021-03-05 src/lib/re_sample_wit_wf.m

@@ -1,4 +1,4 @@
-function [sample, solution] = re_sample_wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
+function [sample, solution] = re_sample_wit_wf(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
     % Function:
     %   - optimize the waveform and IRS reflection coefficients to maximize user rate
     %
@@ -32,7 +32,7 @@ function [sample, solution] = re_sample_wit(directChannel, incidentChannel, refl
 
     % * Construct waveform (water-filling + MRT) and initialize splitting ratio
     [~, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = water_filling(compositeChannel, txPower, noisePower);
-    [infoWaveform, ~] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
+    [infoWaveform] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
 
     % * Obtain coefficients
     % \boldsymbol{M}_n, \boldsymbol{C}_n
@@ -94,7 +94,7 @@ function [sample, solution] = re_sample_wit(directChannel, incidentChannel, refl
         % * Update composite channel and optimal waveform
         [compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
         [capacity, infoAmplitude] = water_filling(compositeChannel, txPower, noisePower);
-        [infoWaveform, ~] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
+        [infoWaveform] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
 
         % * Update coefficients
         for iSubband = 1 : nSubbands

### 2021-03-05 src/lib/re_sample_wpt_ass.m

@@ -1,0 +1,54 @@
+function [sample, solution] = re_sample_wpt_ass(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
+    % Function:
+    %   - optimize the waveform and IRS reflection coefficients based on linear harvetser model to maximize average output DC current
+    %
+    % Input:
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
+    %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
+    %   - incidentChannel (h_I) [nSubbands * nTxs * nReflectors]: the AP-IRS channel
+    %   - reflectiveChannel (h_R) [nSubbands * nReflectors * nRxs]: the IRS-user channel
+    %   - txPower (P): average transmit power budget
+    %   - noisePower (\sigma_n^2): average noise power
+    %   - nCandidates (Q): number of CSCG random vectors to generate
+    %   - tolerance (\epsilon): minimum current gain per iteration
+    %
+    % Output:
+    %   - sample [2 * nSamples]: rate-energy sample
+    %   - solution: IRS reflection coefficient, composite channel, waveform, splitting ratio and eigenvalue ratio
+    %
+    % Comment:
+    %   - for linear harvester model, the optimal power allocation is adaptive single sine
+    %
+    % Author & Date: Yang (i@snowztail.com) - 10 Oct 20
+
+
+    % * Get data
+	nReflectors = size(incidentChannel, 3);
+
+    % * Initialize IRS and composite channel
+    irs = exp(1i * 2 * pi * rand(nReflectors, 1));
+    [compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
+
+    % * Initialize waveform and splitting ratio
+	[~, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = waveform_ass(beta2, beta4, channel, txPower);
+	[infoWaveform, powerWaveform] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
+
+    % * AO
+    isConverged = false;
+    current_ = 0;
+	rateConstraint = 0;
+	eigRatio = [];
+    while ~isConverged
[…]

### 2021-03-05 src/lib/re_sample_wpt_sdr.m

@@ -1,4 +1,4 @@
-function [sample, solution] = re_sample_wpt(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
+function [sample, solution] = re_sample_wpt_sdr(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
     % Function:
     %   - optimize the waveform and IRS reflection coefficients to maximize average output DC current
     %
@@ -24,21 +24,15 @@ function [sample, solution] = re_sample_wpt(beta2, beta4, directChannel, inciden
 
 
     % * Get data
-	[nSubbands, ~, nReflectors] = size(incidentChannel);
+	nReflectors = size(incidentChannel, 3);
 
     % * Initialize IRS and composite channel
     irs = exp(1i * 2 * pi * rand(nReflectors, 1));
     [compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
 
-    % * Get equivalent channel gain
-    channelAmplitude = vecnorm(compositeChannel, 2, 2);
-
     % * Initialize waveform and splitting ratio
-    infoAmplitude = zeros(1, nSubbands) + eps;
-    powerAmplitude = sqrt(2 * txPower) * channelAmplitude' ./ norm(channelAmplitude);
+	[~, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = scaled_matched_filter(alpha, beta2, beta4, channel, txPower);
 	[infoWaveform, powerWaveform] = precoder_mrt(compositeChannel, infoAmplitude, powerAmplitude);
-    infoRatio = eps;
-    powerRatio = 1 - infoRatio;
 
     % * AO
     isConverged = false;
@@ -48,7 +42,7 @@ function [sample, solution] = re_sample_wpt(beta2, beta4, directChannel, inciden
     while ~isConverged
 		[irs, eigRatio(end + 1)] = irs_sdr(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, irs, infoWaveform, powerWaveform, infoRatio, powerRatio, noisePower, rateConstraint, nCandidates, tolerance);
 		[compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
[…]

### 2021-03-05 src/lib/re_sample_wpt_smf.m

@@ -1,6 +1,6 @@
-function [sample, solution] = re_sample_wpt_linear(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
+function [sample, solution] = re_sample_wpt_smf(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance)
     % Function:
-    %   - optimize the waveform and IRS reflection coefficients based on linear harvetser model to maximize average output DC current
+    %   - optimize the waveform and IRS reflection coefficients to maximize average output DC current
     %
     % Input:
     %   - beta2: coefficients on second-order current terms
@@ -11,31 +11,29 @@ function [sample, solution] = re_sample_wpt_linear(beta2, beta4, directChannel, 
     %   - txPower (P): average transmit power budget
     %   - noisePower (\sigma_n^2): average noise power
     %   - nCandidates (Q): number of CSCG random vectors to generate
-    %   - tolerance (\epsilon): minimum current gain per iteration
+	%   - tolerance (\epsilon): minimum current gain per iteration
     %
     % Output:
     %   - sample [2 * nSamples]: rate-energy sample
     %   - solution: IRS reflection coefficient, composite channel, waveform, splitting ratio and eigenvalue ratio
     %
     % Comment:
-    %   - based on linear harvester model
+    %   - solve IRS reflection coefficients by SDR
+	%	- obtain waveform by SMF
     %
-    % Author & Date: Yang (i@snowztail.com) - 10 Oct 20
+    % Author & Date: Yang (i@snowztail.com) - 21 Jun 20
 
 
     % * Get data
-	[nSubbands, ~, nReflectors] = size(incidentChannel);
+	nReflectors = size(incidentChannel, 3);
 
     % * Initialize IRS and composite channel
     irs = exp(1i * 2 * pi * rand(nReflectors, 1));
     [compositeChannel] = composite_channel(directChannel, incidentChannel, reflectiveChannel, irs);
 
     % * Initialize waveform and splitting ratio
-	infoAmplitude = zeros(1, nSubbands) + eps;
-    powerAmplitude = sqrt(2 * txPower / nSubbands) * ones(1, nSubbands);
[…]

### 2021-03-05 src/lib/scaled_matched_filter.m

@@ -1,0 +1,46 @@
+function [current, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = scaled_matched_filter(alpha, beta2, beta4, channel, txPower, waveformRatio)
+    % Function:
+    %   - power allocation based on scaled matched filter for OFDM channels
+    %
+    % Input:
+    %   - alpha: scale ratio of SMF
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
+    %   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
+    %   - txPower (P): average transmit power budget
+	%	- waveformRatio (\delta): balancing ratio for modulated and multisine waveforms
+    %
+    % Output:
+	%	- current (z): objective function to maximize output DC current
+    %   - infoAmplitude (s_I) [1 * nSubbands]: amplitude of information waveform in frequency domain
+    %   - powerAmplitude (s_P) [1 * nSubbands]: amplitude of power waveform in frequency domain
+    %   - infoRatio (\bar{\rho}): information splitting ratio
+    %   - powerRatio (\rho): power splitting ratio
+    %
+    % Comment:
+    %   - for MISO OFDM channels
+	%	- convert waveform amplitude to peak value by multiplying sqrt(2)
+	%	- assign no power to modulated waveform and set splitting ratio to 1
+    %
+    % Author & Date: Yang (i@snowztail.com) - 05 Mar 21
+
+
+	if nargin == 5
+		waveformRatio = 1;
+	end
+    % * Get data
+    nSubbands = size(channel, 1);
+    channelAmplitude = vecnorm(channel, 2, 2);
+
+    % * SMF power allocation based on equivalent channel strength
+	powerAmplitude = sqrt(2 * waveformRatio * txPower / sum(channelAmplitude .^ (2 * alpha))) * channelAmplitude' .^ alpha;
+
+	% * Assign modulated waveform and splitting ratio
+    infoAmplitude = zeros(1, nSubbands) + eps;
+    infoRatio = eps;
+    powerRatio = 1 - eps;
+
+	% * Update output current
+	[current] = current_sdr(beta2, beta4, channelAmplitude, infoAmplitude, powerAmplitude, powerRatio);
+
+end

### 2021-03-05 src/lib/water_filling.m

@@ -1,4 +1,4 @@
-function [capacity, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = water_filling(channel, txPower, noisePower)
+function [capacity, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = water_filling(channel, txPower, noisePower, waveformRatio)
     % Function:
     %   - water-filling power allocation for OFDM channels
     %
@@ -6,6 +6,7 @@ function [capacity, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = wate
     %   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
     %   - txPower (P): average transmit power budget
     %   - noisePower (\sigma_n^2): average noise power
+	%	- waveformRatio (\delta): balancing ratio for modulated and multisine waveforms
     %
     % Output:
     %   - capacity: maximum achievable sum rate over all subbands
@@ -21,6 +22,10 @@ function [capacity, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = wate
     %
     % Author & Date: Yang (i@snowztail.com) - 28 Aug 19
 
+
+	if nargin == 3
+		waveformRatio = 0;
+	end
 
     % * Get data
     nSubbands = size(channel, 1);
@@ -46,7 +51,7 @@ function [capacity, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = wate
 
 	% * Recover order and normalize transmit power
     channelAmplitude(index) = channelAmplitude;
-    subbandPower(index) = txPower * (subbandPower ./ sum(subbandPower));
+    subbandPower(index) = (1 - waveformRatio) * txPower * (subbandPower ./ sum(subbandPower));
 
     % * Obtain waveform amplitude and capacity
     infoAmplitude = sqrt(2 * subbandPower);

### 2021-03-05 src/lib/waveform_ass.m

@@ -1,0 +1,46 @@
+function [current, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = waveform_ass(beta2, beta4, channel, txPower)
+    % Function:
+    %   - optimize the information and power waveform amplitude for WPT
+    %
+    % Input:
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
+	%   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
+    %   - txPower (P): average transmit power budget
+    %   - infoRatio (\bar{\rho}): information splitting ratio
+    %   - powerRatio (\rho): power splitting ratio
+    %
+	% Output:
+	%	- current (z): objective function to maximize output DC current
+	%   - infoAmplitude (s_I) [1 * nSubbands]: amplitude of information waveform in frequency domain
+	%   - powerAmplitude (s_P) [1 * nSubbands]: amplitude of power waveform in frequency domain
+    %
+	% Comment:
+	%	- based on linear harvester model
+    %   - for linear WPT, the optimal frequency allocation is ASS and the optimal spatial beamformer is MRT
+    %
+    % Author & Date: Yang (i@snowztail.com) - 16 Oct 20
+
+
+
+
+    % * Get data
+	[nSubbands] = size(channel, 1);
+
+    % * Initialize algorithm
+    % \boldsymbol{a}, \boldsymbol{s}_{I/P}
+	channelAmplitude = vecnorm(channel, 2, 2);
+
+	% * Adaptive single sine
+	infoAmplitude = zeros(1, nSubbands) + eps;
+	powerAmplitude = zeros(1, nSubbands) + eps;
+	powerAmplitude(channelAmplitude == max(channelAmplitude)) = sqrt(2 * txPower);
+
+	% * Splitting ratio
+	infoRatio = eps;
+	powerRatio = 1 - eps;
+
+	% * Update output current
+	[current] = current_sdr(beta2, beta4, channelAmplitude, infoAmplitude, powerAmplitude, powerRatio);
+
+end

### 2021-03-05 src/lib/waveform_gp.m

@@ -1,4 +1,4 @@
-function [infoAmplitude, powerAmplitude, infoRatio, powerRatio, rate, current] = waveform_gp(beta2, beta4, channel, infoAmplitude, powerAmplitude, infoRatio, powerRatio, txPower, noisePower, rateConstraint, tolerance)
+function [rate, current, infoAmplitude, powerAmplitude, infoRatio, powerRatio] = waveform_gp(beta2, beta4, channel, infoAmplitude, powerAmplitude, infoRatio, powerRatio, txPower, noisePower, rateConstraint, tolerance)
     % Function:
     %   - jointly optimize waveform amplitude and splitting ratio to maximize the R-E region
     %
@@ -16,12 +16,12 @@ function [infoAmplitude, powerAmplitude, infoRatio, powerRatio, rate, current] =
     %   - tolerance (\epsilon): minimum current gain per iteration
     %
     % Output:
+	%	- rate (R): achievable sum rate of all subbands
+	%	- current (z): objective function to maximize output DC current
     %   - infoAmplitude (s_I) [1 * nSubbands]: amplitude of information waveform in frequency domain
     %   - powerAmplitude (s_P) [1 * nSubbands]: amplitude of power waveform in frequency domain
     %   - infoRatio (\bar{\rho}): information splitting ratio
 	%   - powerRatio (\rho): power splitting ratio
-	%	- rate (R): achievable sum rate of all subbands
-	%	- current (z): objective function to maximize output DC current
     %
     % Comment:
     %   - obtain waveform amplitude in frequency domain

### 2021-03-05 src/lib/waveform_linear.m

@@ -1,62 +1,0 @@
-function [infoAmplitude, powerAmplitude, current] = waveform_linear(beta2, beta4, channel, txPower)
-    % Function:
-    %   - optimize the information and power waveform amplitude to maximize the R-E region
-    %
-    % Input:
-    %   - beta2: coefficients on second-order current terms
-    %   - beta4: coefficients on fourth-order current terms
-	%   - channel (h) [nSubbands * nTxs * nRxs]: channel frequency response
-    %   - txPower (P): average transmit power budget
-    %
-	% Output:
-	%   - infoAmplitude (s_I) [1 * nSubbands]: amplitude of information waveform in frequency domain
-	%   - powerAmplitude (s_P) [1 * nSubbands]: amplitude of power waveform in frequency domain
-	%	- current (z): objective function to maximize output DC current
-    %
-	% Comment:
-	%	- based on linear harvester model
-    %   - for WPT, the optimal frequency allocation is ASS and the optimal spatial beamformer is MRT
-    %   - solve SDR problem to obtain high-rank amplitude outer product matrices
-    %   - use Gaussian randomization method to extract amplitude vectors
-    %
-    % Author & Date: Yang (i@snowztail.com) - 16 Oct 20
-
-
-
-
-    % * Get data
-	[nSubbands] = size(channel, 1);
-
-    % * Initialize algorithm
-    % \boldsymbol{a}, \boldsymbol{s}_{I/P}
-	channelAmplitude = vecnorm(channel, 2, 2);
-
-	% * Adaptive single sine
-	infoAmplitude = zeros(1, nSubbands) + eps;
-	powerAmplitude = zeros(1, nSubbands) + eps;
-	powerAmplitude(channelAmplitude == max(channelAmplitude)) = sqrt(2 * txPower);
-
-    % * Construct coefficient matrices
-    % \boldsymbol{S}_{I/P}
-    infoMatrix = vec(infoAmplitude) * vec(infoAmplitude)';
-	powerMatrix = vec(powerAmplitude) * vec(powerAmplitude)';
-
-    % \boldsymbol{A}_n
-    channelMatrix = channelAmplitude * channelAmplitude';
-	channelBlkDiag = block_diagonal(channelMatrix, 1, nSubbands);
-
-    % * Initialize auxiliaries
-    % t'_{I/P,n}
[…]

### 2021-03-05 src/lib/waveform_sdr.m

@@ -1,4 +1,4 @@
-function [infoAmplitude, powerAmplitude, current] = waveform_sdr(beta2, beta4, channel, infoAmplitude, powerAmplitude, txPower, nCandidates, tolerance)
+function [current, infoAmplitude, powerAmplitude] = waveform_sdr(beta2, beta4, channel, infoAmplitude, powerAmplitude, txPower, nCandidates, tolerance)
     % Function:
     %   - optimize the information and power waveform amplitude to maximize the R-E region
     %
@@ -13,9 +13,9 @@ function [infoAmplitude, powerAmplitude, current] = waveform_sdr(beta2, beta4, c
     %   - tolerance (\epsilon): minimum current gain per iteration
     %
     % Output:
+	%	- current (z): objective function to maximize output DC current
     %   - infoAmplitude (s_I) [1 * nSubbands]: amplitude of information waveform in frequency domain
 	%   - powerAmplitude (s_P) [1 * nSubbands]: amplitude of power waveform in frequency domain
-	%	- current (z): objective function to maximize output DC current
     %
     % Comment:
     %   - suitable for WPT

### 2021-03-05 src/re_distance.m

@@ -23,7 +23,7 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
         % * Alternating optimization
-        [reSample{iChannel, iDistance}, reSolution{iChannel, iDistance}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+        [reSample{iChannel, iDistance}, reSolution{iChannel, iDistance}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 

### 2021-03-05 src/re_irs.m

@@ -30,21 +30,21 @@ for iChannel = 1 : nChannels
 
 		% * Upper bound by frequency-selective IRS
 		[idealCompositeChannel] = composite_channel_ideal(directChannel, incidentChannel, reflectiveChannel);
-		[reIdealIrsSample{iChannel, iBandwidth}, reIdealIrsSolution{iChannel, iBandwidth}] = re_sample_nonadaptive_channel(beta2, beta4, idealCompositeChannel, txPower, noisePower, nSamples, tolerance);
+		[reIdealIrsSample{iChannel, iBandwidth}, reIdealIrsSolution{iChannel, iBandwidth}] = re_sample_swipt_gp_benchmark(alpha, beta2, beta4, idealCompositeChannel, txPower, noisePower, nSamples, tolerance);
 
 		% * Adaptive IRS and waveform design
-		[reAdaptiveIrsSample{iChannel, iBandwidth}, reAdaptiveIrsSolution{iChannel, iBandwidth}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+		[reAdaptiveIrsSample{iChannel, iBandwidth}, reAdaptiveIrsSolution{iChannel, iBandwidth}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
 		witCompositeChannel = reAdaptiveIrsSolution{iChannel, iBandwidth}{1}.compositeChannel;
 		wptCompositeChannel = reAdaptiveIrsSolution{iChannel, iBandwidth}{end}.compositeChannel;
 
 		% * Waveform optimization with nonadaptive WIT-optimized IRS
-		[reWitIrsSample{iChannel, iBandwidth}, reWitIrsSolution{iChannel, iBandwidth}] = re_sample_nonadaptive_channel(beta2, beta4, witCompositeChannel, txPower, noisePower, nSamples, tolerance);
+		[reWitIrsSample{iChannel, iBandwidth}, reWitIrsSolution{iChannel, iBandwidth}] = re_sample_swipt_gp_benchmark(alpha, beta2, beta4, witCompositeChannel, txPower, noisePower, nSamples, tolerance);
 
 		% * Waveform optimization with nonadaptive WPT-optimized IRS
[…]

### 2021-03-05 src/re_los.m

@@ -13,8 +13,8 @@ for iChannel = 1 : nChannels
     [incidentNlosTapGain, incidentTapDelay] = tap_tgn(corTx, corIrs, 'nlos');
     [reflectiveNlosTapGain, reflectiveTapDelay] = tap_tgn(corIrs, corRx, 'nlos');
 
-    [incidentLosTapGain, ~] = tap_tgn(corTx, corIrs, 'los');
-    [reflectiveLosTapGain, ~] = tap_tgn(corIrs, corRx, 'los');
+    [incidentLosTapGain] = tap_tgn(corTx, corIrs, 'los');
+    [reflectiveLosTapGain] = tap_tgn(corIrs, corRx, 'los');
 
     % * Construct channels
     [directNlosChannel] = channel_response(directNlosTapGain, directTapDelay, directDistance, rxGain, subbandFrequency, fadingMode);
@@ -25,10 +25,10 @@ for iChannel = 1 : nChannels
     [reflectiveLosChannel] = channel_response(reflectiveLosTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
     % * Optimization based on NLoS channels
-    [reNlosSample{iChannel}, reNlosSolution{iChannel}] = re_sample(beta2, beta4, directNlosChannel, incidentNlosChannel, reflectiveNlosChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+    [reNlosSample{iChannel}, reNlosSolution{iChannel}] = re_sample_swipt_gp(alpha, beta2, beta4, directNlosChannel, incidentNlosChannel, reflectiveNlosChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
 
     % * Optimization based on NLoS direct channel and LoS incident and reflective channels
-    [reLosSample{iChannel}, reLosSolution{iChannel}] = re_sample(beta2, beta4, directNlosChannel, incidentLosChannel, reflectiveLosChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+    [reLosSample{iChannel}, reLosSolution{iChannel}] = re_sample_swipt_gp(alpha, beta2, beta4, directNlosChannel, incidentLosChannel, reflectiveLosChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
 end
 
 % * Average over channel realizations

### 2021-03-05 src/re_noise.m

@@ -20,7 +20,7 @@ for iChannel = 1 : nChannels
         noisePower = Variable.noisePower(iNoise);
 
         % * Alternating optimization
-        [reSample{iChannel, iNoise}, reSolution{iChannel, iNoise}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+        [reSample{iChannel, iNoise}, reSolution{iChannel, iNoise}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 

### 2021-03-05 src/re_reflector.m

@@ -21,7 +21,7 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
         % * Alternating optimization
-        [reSample{iChannel, iReflector}, reSolution{iChannel, iReflector}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+        [reSample{iChannel, iReflector}, reSolution{iChannel, iReflector}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 

### 2021-03-05 src/re_subband.m

@@ -21,7 +21,7 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
         % * Alternating optimization
-		[reSample{iChannel, iSubband}, reSolution{iChannel, iSubband}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+		[reSample{iChannel, iSubband}, reSolution{iChannel, iSubband}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 

### 2021-03-05 src/re_tx.m

@@ -21,7 +21,7 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
         % * Alternating optimization
-        [reSample{iChannel, iTx}, reSolution{iChannel, iTx}] = re_sample(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+        [reSample{iChannel, iTx}, reSolution{iChannel, iTx}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
     end
 end
 

### 2021-03-05 src/scaling_reflector.m

@@ -26,13 +26,13 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
 		% * WIT
-		[witSample(iChannel, iReflector, :), witSolution{iChannel, iReflector}] = re_sample_wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[witSample(iChannel, iReflector, :), witSolution{iChannel, iReflector}] = re_sample_wit_wf(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
 
 		% * WPT by linear harvester model
-		[wptLinearSample(iChannel, iReflector, :), wptLinearSolution{iChannel, iReflector}] = re_sample_wpt_linear(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[wptLinearSample(iChannel, iReflector, :), wptLinearSolution{iChannel, iReflector}] = re_sample_wpt_ass(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
 
 		% * WPT by nonlinear harvester model
-		[wptNonlinearSample(iChannel, iReflector, :), wptNonlinearSolution{iChannel, iReflector}] = re_sample_wpt(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[wptNonlinearSample(iChannel, iReflector, :), wptNonlinearSolution{iChannel, iReflector}] = re_sample_wpt_sdr(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
     end
 end
 

### 2021-03-05 src/scaling_tx.m

@@ -26,13 +26,13 @@ for iChannel = 1 : nChannels
         [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
 
 		% * WIT
-		[witSample(iChannel, iTx, :), witSolution{iChannel, iTx}] = re_sample_wit(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[witSample(iChannel, iTx, :), witSolution{iChannel, iTx}] = re_sample_wit_wf(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
 
 		% * WPT by linear harvester model
-		[wptLinearSample(iChannel, iTx, :), wptLinearSolution{iChannel, iTx}] = re_sample_wpt_linear(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[wptLinearSample(iChannel, iTx, :), wptLinearSolution{iChannel, iTx}] = re_sample_wpt_ass(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
 
 		% * WPT by nonlinear harvester model
-		[wptNonlinearSample(iChannel, iTx, :), wptNonlinearSolution{iChannel, iTx}] = re_sample_wpt(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+		[wptNonlinearSample(iChannel, iTx, :), wptNonlinearSolution{iChannel, iTx}] = re_sample_wpt_sdr(beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
     end
 end
 

### 2021-03-05 src/setup.m

@@ -7,9 +7,9 @@ set(groot, 'defaultlegendinterpreter', 'latex');
 set(groot, 'defaultlinelinewidth', 2);
 set(groot, 'defaultstemlinewidth', 2);
 
-run('/rds/general/user/yz16718/home/cvx/cvx_setup.m');
-% run('/rds/general/user/yx2718/home/yang/cvx/cvx_setup.m');
-
-iBatch = str2double(getenv('PBS_ARRAY_INDEX'));
-disp(iBatch);
-rng(iBatch);
+% run('/rds/general/user/yz16718/home/cvx/cvx_setup.m');
+% % run('/rds/general/user/yx2718/home/yang/cvx/cvx_setup.m');
+% 
+% iBatch = str2double(getenv('PBS_ARRAY_INDEX'));
+% disp(iBatch);
+% rng(iBatch);

### 2021-03-05 main.tex
:pencil: Fix multisine amplitude
:pencil: Update notation

@@
 				\begin{equation}
-					s_{\mathrm{I}, n} = \sqrt{\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
 				\end{equation}
@@
 				\begin{equation}
-					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
+					s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
 				\end{equation}
-				where the only design variable $\beta \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-$\beta = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\beta > 1$ further elevates the strong subchannels and suppresses the weak ones.
+				where the only design variable $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
+$\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subchannels and suppresses the weak ones.
 The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.
@@
 				\begin{align}
-					s_{\mathrm{I}, n} &= \sqrt{(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
-					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \beta}}}}\lVert{\boldsymbol{h}_n}\rVert^\beta
+					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
+					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
 				\end{align}
-				That is to say, the suboptimal TS scheme only need to design $\beta$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
+				That is to say, the suboptimal TS scheme only need to design $\alpha$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
 			\end{subsubsection}

### 2021-03-05 src/config/config_re_low_complexity.m
:sparkles: Low-complexity design

@@ -1,0 +1,68 @@
+%% * Transceiver
+% diode k-parameter
+k2 = 0.0034;
+k4 = 0.3829;
+% antenna resistance
+resistance = 50;
+% coefficients on current terms
+beta2 = k2 * resistance;
+beta4 = k4 * resistance ^ 2;
+% number of transmit and receive antennas
+nTxs = 1;
+nRxs = 1;
+% number of users
+nUsers = 1;
+% average transmit power
+txPower = db2pow(6);
+% average noise power
+noisePower = db2pow(-70);
+% IRS element gain
+irsGain = db2pow(2);
+% receive antenna gain
+rxGain = db2pow(2);
+
+%% * Channel
+% AP-user distance
+directDistance = 15;
+% vertical distance from the IRS to the AP-user path
+verticalDistance = 2;
+% projection of AP-IRS distance to the AP-user path
+horizontalDistance = 2;
+% AP-IRS and IRS-user distance
+[incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
+% center frequency
+centerFrequency = 5.18e9;
+% bandwidth
+bandwidth = 1e6;
+% number of frequency bands
+nSubbands = 16;
+% channel fading mode ('flat' or 'selective')
+fadingMode = 'selective';
+% carrier frequency
+[subbandFrequency] = subband_frequency(centerFrequency, bandwidth, nSubbands);
+% number of reflecting elements in IRS
+nReflectors = 20;
+% spatial correlation
+corTx = eye(nTxs);
+corRx = eye(nRxs);
+corIrs = eye(nReflectors);
+
+%% * Algorithm
+% minimum gain per iteration
+tolerance = 1e-8;
+% number of CSCG random vectors to generate
+nCandidates = 1e3;
+% number of samples in R-E curves
+nSamples = 30;
+% number of channel realizations
+nChannels = 1;
+% number of cases to investigate (LoS, NLoS)
+nCases = 2;
+
+%% * Variables
+% scale ratio of SMF
+Variable.alpha = 1 : 3;
+
+%% * PBS
+% number of individual jobs
+nBatches = 3e2;

### 2021-03-05 src/lib/re_sample_swipt_low_complexity.m

@@ -1,0 +1,73 @@
+function [sample, solution] = re_sample_swipt_low_complexity(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance)
+    % Function:
+    %   - sample R-E region by computing the output DC current and rate
+    %
+    % Input:
+    %   - alpha: scale ratio of SMF
+    %   - beta2: coefficients on second-order current terms
+    %   - beta4: coefficients on fourth-order current terms
+    %   - directChannel (h_D) [nSubbands * nTxs * nRxs]: the AP-user channel
+    %   - incidentChannel (h_I) [nSubbands * nTxs * nReflectors]: the AP-IRS channel
+    %   - reflectiveChannel (h_R) [nSubbands * nReflectors * nRxs]: the IRS-user channel
+    %   - txPower (P): average transmit power budget
+    %   - noisePower (\sigma_n^2): average noise power
+    %   - nCandidates (Q): number of CSCG random vectors to generate
+    %   - nSamples (S): number of samples in R-E region
+    %   - tolerance (\epsilon): minimum current gain per iteration
+    %
+    % Output:
+    %   - sample [2 * nSamples]: rate-energy sample
+    %   - solution: IRS reflection coefficient, composite channel, waveform, splitting ratio and eigenvalue ratio
+    %
+    % Comment:
+    %   - time sharing between WPT point achieved by SMF and WIT point achieved by WF
+    %
+    % Author & Date: Yang (i@snowztail.com) - 21 Jun 20
+
+
+    sample = zeros(2, nSamples);
+    solution = cell(nSamples, 1);
+
+	% * WIT point
+    [sample(:, 1), solution{1}] = re_sample_wit_wf(directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, tolerance);
+	irs = solution{1}.irs;
+    compositeChannel = solution{1}.compositeChannel;
+
+	% * Remove rate constraint as R-E boundary is obtained by varying the waveform and splitting ratios
+	rateConstraint = 0;
+
+	for iSample = 2 : nSamples
+		% * Update splitting ratio
+		infoRatio = (nSamples - iSample) / (nSamples - 1);
+		powerRatio = 1 - infoRatio;
+
+		% TODO Update waveform ratio
+		waveformRatio = powerRatio;
+
[…]

### 2021-03-05 src/re_low_complexity.m

@@ -1,0 +1,35 @@
+clear; clc; setup; config_re_low_complexity;
+
+%% ! R-E region for IRS-aided NLoS and LoS channels
+reLcSample = cell(nChannels, 1);
+reGpSample = cell(nChannels, 1);
+
+reLcSolution = cell(nChannels, 1);
+reGpSolution = cell(nChannels, 1);
+
+for iChannel = 1 : nChannels
+    % * Generate tap gains and delays
+    [directTapGain, directTapDelay] = tap_tgn(corTx, corRx, 'nlos');
+    [incidentTapGain, incidentTapDelay] = tap_tgn(corTx, corIrs, 'nlos');
+    [reflectiveTapGain, reflectiveTapDelay] = tap_tgn(corIrs, corRx, 'nlos');
+
+    % * Construct channels
+    [directChannel] = channel_response(directTapGain, directTapDelay, directDistance, rxGain, subbandFrequency, fadingMode);
+    [incidentChannel] = channel_response(incidentTapGain, incidentTapDelay, incidentDistance, irsGain, subbandFrequency, fadingMode);
+    [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
+
+	for iAlpha = 1 : length(Variable.alpha)
+		% * Get alpha for SMF
+		alpha = Variable.alpha(iAlpha);
+
+		% * Optimize IRS for given waveform
+		[reLcSample, reLcSolution] = re_sample_swipt_low_complexity(alpha, beta2, beta4, directChannel, incidentChannel, reflectiveChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+	end
+end
+
+% * Average over channel realizations
+reNlosInstance = mean(cat(3, reLcSample{:}), 3);
+reLosInstance = mean(cat(3, reGpSample{:}), 3);
+
+% * Save batch data
+save(sprintf('data/re_los/re_los_%d.mat', iBatch));

### 2021-03-08 main.tex
:sparkles: Imperfect CSIT and quantized IRS

@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna User Equipment (UE) over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and focus on an instance where all channels are constant.
-The AP is assumed to have partial or perfect Channel State Information (CSI) of the AP-UE channel and the cascaded AP-IRS-UE channel.
-We also omit the signals reflected two and more times and assume the noise power is too small to be harvested.
+We assume perfect or partial Channel State Information at the Transmitter (CSIT) regarding the quasi-static AP-UE and AP-IRS-UE cascaded channels.
+The signals reflected two or more times are omitted and the noise power is assumed too small to be harvested.
 
@@
 			\end{equation}
-			where we define $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+			where we define the cascaded AP-IRS-UE channel without reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 		\end{subsection}
@@
 For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$.
+We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.
+
+		\begin{subsection}{Imperfect CSIT}
+			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially when the coherence time is short.
+Hence, we consider an imperfect CSIT model and denote the estimation of direct and cascaded links at subband $n$ as
+			\begin{align}
+				\hat{\boldsymbol{h}}_{\mathrm{D},n} &= \boldsymbol{h}_{\mathrm{D},n} + \tilde{\boldsymbol{h}}_{\mathrm{D},n} \\
+				\hat{\boldsymbol{V}}_{n} &= \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+			\end{align}
+			where $\tilde{\boldsymbol{h}}_{\mathrm{D},n}$ and $\tilde{\boldsymbol{V}}_{n}$ are the corresponding estimation errors, whose entries follow i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{\mathrm{D},n}^2)$ and $\mathcal{CN}(0, \epsilon_{n}^2)$, respectively.
+Perfect CSIT can be regarded as a special case with $\epsilon_{\mathrm{D},n} = \epsilon_{n} = 0$.
+% For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
+		\end{subsection}
+
+		\begin{subsection}{Quantized IRS}
+			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient.
+To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and quantize each reflection coefficient by $b$ bits.
+		\end{subsection}
 

### 2021-03-10 src/plot/plot_eigenratio.m
:paintbrush: Update plot functions

@@ -61,7 +61,7 @@ end
 clearvars -except eigRatioSubband eigRatioTx eigRatioReflector;
 
 %% * Eigenratio plots
-figure('name', 'Max eigenvalue of the relaxed solution over sum eigenvalue of the relaxed solution under different configurations');
+figure('name', 'Max eigenvalue of the relaxed solution over sum eigenvalue of the relaxed solution under different configurations', 'position', [0, 0, 500, 400]);
 eigenRatioPlot = tiledlayout(3, 1, 'tilespacing', 'compact');
 
 config_re_subband;
@@ -119,4 +119,4 @@ ylabel('');
 apply_style(plotHandle);
 
 savefig('../figures/cdf_eigenratio.fig');
-matlab2tikz('../../assets/cdf_eigenratio.tex');
+matlab2tikz('../../assets/cdf_eigenratio.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_pathloss.m

@@ -22,28 +22,14 @@ for iSample = 1 : nSamples
 	auxiliaryPathloss(iSample) = path_loss(incidentDistance) * path_loss(reflectiveDistance);
 end
 
-%% * Waveform amplitude
-figure('name', 'Path loss vs AP-IRS horizontal distance');
-pathlossPlot = tiledlayout(nCases, 1, 'tilespacing', 'compact');
-plotHandle = gobjects(1, nCases);
-
-% * Incident pathloss
-nexttile;
-plotHandle(1) = plot(horizontalDistance, pow2db(1 ./ incidentPathloss));
-grid on;
-legend('$\Lambda_D$', 'location', 'se')
-xlabel('AP-user distance [m]');
-ylabel('Path loss [dB]');
-box on;
-
-% * Extra pathloss
-nexttile;
-plotHandle(2) = plot(horizontalDistance, pow2db(1 ./ auxiliaryPathloss));
+%% * Auxiliary path loss
+figure('name', 'Auxiliary path loss product vs AP-IRS horizontal distance', 'position', [0, 0, 500, 400]);
+plotHandle = plot(horizontalDistance, pow2db(1 ./ auxiliaryPathloss));
 grid on;
 legend('$\Lambda_I\Lambda_R$', 'location', 'ne')
 xlabel('AP-IRS horizontal distance [m]');
-ylabel('Path loss product [dB]');
+ylabel('Auxiliary path loss product [dB]');
 box on;
 
 savefig('../figures/path_loss.fig');
-matlab2tikz('../../assets/path_loss.tex');
+matlab2tikz('../../assets/path_loss.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_re_distance.m

@@ -21,7 +21,7 @@ end
 save('../data/re_distance.mat');
 
 %% * R-E plots
-figure('name', 'Average R-E region vs AP-IRS horizontal distance');
+figure('name', 'Average R-E region vs AP-IRS horizontal distance', 'position', [0, 0, 500, 400]);
 legendString = cell(1, length(Variable.horizontalDistance));
 plotHandle = gobjects(1, length(Variable.horizontalDistance));
 for iDistance = 1 : length(Variable.horizontalDistance)
@@ -40,4 +40,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/re_distance.fig');
-matlab2tikz('../../assets/re_distance.tex');
+matlab2tikz('../../assets/re_distance.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_re_irs.m

@@ -38,7 +38,7 @@ save('../data/re_irs.mat');
 
 %% * R-E plots
 for iBandwidth = 1 : length(Variable.bandwidth)
-	figure('name', sprintf('Average R-E region for ideal, adaptive, nonadaptive and no IRS for $B = %d$ MHz', Variable.bandwidth(iBandwidth) / 1e6));
+	figure('name', sprintf('Average R-E region for ideal, adaptive, nonadaptive and no IRS for $B = %d$ MHz', Variable.bandwidth(iBandwidth) / 1e6), 'position', [0, 0, 500, 400]);
 	plotHandle = gobjects(1, length(Variable.bandwidth));
 	hold all;
 	plotHandle(1) = plot(reIdealIrs{iBandwidth}(1, :) / nSubbands, 1e6 * reIdealIrs{iBandwidth}(2, :));
@@ -57,6 +57,6 @@ for iBandwidth = 1 : length(Variable.bandwidth)
 	apply_style(plotHandle);
 
 	savefig(sprintf('../figures/re_irs_%dmhz.fig', Variable.bandwidth(iBandwidth) / 1e6));
-	matlab2tikz(sprintf('../../assets/re_irs_%dmhz.tex', Variable.bandwidth(iBandwidth) / 1e6));
+	matlab2tikz(sprintf('../../assets/re_irs_%dmhz.tex', Variable.bandwidth(iBandwidth) / 1e6), 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);
 	close;
 end

### 2021-03-10 src/plot/plot_re_los.m

@@ -29,7 +29,7 @@ reLos = mean(cat(3, reLosSet{indexSet}), 3);
 save('../data/re_los.mat');
 
 %% * R-E plots
-figure('name', 'Average R-E region for IRS-aided NLoS and LoS channels');
+figure('name', 'Average R-E region for IRS-aided NLoS and LoS channels', 'position', [0, 0, 500, 400]);
 plotHandle = gobjects(1, nCases);
 hold all;
 plotHandle(1) = plot(reNlos(1, :) / nSubbands, 1e6 * reNlos(2, :));
@@ -45,11 +45,11 @@ box on;
 
 apply_style(plotHandle);
 savefig('../figures/re_los.fig');
-matlab2tikz('../../assets/re_los.tex');
+matlab2tikz('../../assets/re_los.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);
 close;
 
 %% * CDF plots
-figure('name', 'WIT and WPT CDF for IRS-aided NLoS and LoS channels');
+figure('name', 'WIT and WPT CDF for IRS-aided NLoS and LoS channels', 'position', [0, 0, 500, 400]);
 cdfPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
 
 nexttile;
@@ -79,4 +79,4 @@ ylim([0 inf]);
 box on;
 
 savefig('../figures/cdf_los.fig');
-matlab2tikz('../../assets/cdf_los.tex');
+matlab2tikz('../../assets/cdf_los.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_re_noise.m

@@ -28,11 +28,7 @@ powerRatio = permute(mean(powerRatio(indexSet, :, :), 1), [2 3 1]);
 save('../data/re_noise.mat');
 
 %% * R-E and splitting ratio plots
-figure('name', 'Average R-E region and power splitting ratio vs average noise power');
-tiledlayout(2, 1, 'tilespacing', 'compact');
-
-% * R-E region
-nexttile;
+figure('name', 'Average R-E region vs average noise power', 'position', [0, 0, 500, 400]);
 legendString = cell(1, length(Variable.noisePower));
 plotHandle = gobjects(1, length(Variable.noisePower));
 for iNoise = 1 : length(Variable.noisePower)
@@ -49,9 +45,12 @@ xlim([0 inf]);
 ylim([0 inf]);
 box on;
 apply_style(plotHandle);
+savefig('../figures/re_noise.fig');
+matlab2tikz('../../assets/re_noise.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);
+close;
 
 % * Power splitting ratio
-nexttile;
+figure('name', 'Average splitting ratio vs average noise power', 'position', [0, 0, 500, 400]);
 plotHandle = gobjects(1, length(Variable.noisePower));
 for iNoise = 1 : length(Variable.noisePower)
     plotHandle(iNoise) = plot(reNoise{iNoise}(1, :) / nSubbands, powerRatio(iNoise, :));
@@ -67,4 +66,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/re_noise.fig');
-matlab2tikz('../../assets/re_noise.tex');
+matlab2tikz('../../assets/re_noise.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_re_reflector.m

@@ -21,7 +21,7 @@ end
 save('../data/re_reflector.mat');
 
 %% * R-E plots
-figure('name', 'Average R-E region vs number of reflectors');
+figure('name', 'Average R-E region vs number of reflectors', 'position', [0, 0, 500, 400]);
 legendString = cell(1, length(Variable.nReflectors));
 plotHandle = gobjects(1, length(Variable.nReflectors));
 for iReflector = 1 : length(Variable.nReflectors)
@@ -40,4 +40,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/re_reflector.fig');
-matlab2tikz('../../assets/re_reflector.tex');
+matlab2tikz('../../assets/re_reflector.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_re_subband.m

@@ -31,13 +31,13 @@ end
 save('../data/re_subband.mat');
 
 %% * R-E plots
-figure('name', 'Average R-E region vs number of subbands');
+figure('name', 'Average R-E region vs number of subbands', 'position', [0, 0, 500, 400]);
 legendString = cell(1, length(Variable.nSubbands) + 2);
 plotHandle = gobjects(1, length(Variable.nSubbands) + 2);
+hold all;
 for iSubband = 1 : length(Variable.nSubbands)
     plotHandle(iSubband) = plot(reSubband{iSubband}(1, :) / Variable.nSubbands(iSubband), 1e6 * reSubband{iSubband}(2, :));
     legendString{iSubband} = sprintf('PS: $N = %d$', Variable.nSubbands(iSubband));
-	hold on;
 end
 
 % * Optimal strategy for medium number of subbands (TS + PS)
@@ -46,13 +46,11 @@ optIndex = convhull(transpose([0, reSubband{subbandIndex}(1, :) / Variable.nSubb
 optIndex = optIndex(2 : end - 1);
 plotHandle(iSubband + 1) = plot(reSubband{subbandIndex}(1, optIndex) / Variable.nSubbands(subbandIndex), 1e6 * reSubband{subbandIndex}(2, optIndex), 'r');
 legendString{iSubband + 1} = sprintf('TS + PS: $N = %d$', Variable.nSubbands(subbandIndex));
-hold on;
 
 % * Optimal strategy for large number of subbands (TS)
 subbandIndex = 5;
 plotHandle(iSubband + 2) = plot([reSubband{subbandIndex}(1, end) / Variable.nSubbands(subbandIndex), reSubband{subbandIndex}(1, 1) / Variable.nSubbands(subbandIndex)], [1e6 * reSubband{iSubband}(2, end), 1e6 * reSubband{iSubband}(2, 1)], 'k');
 legendString{iSubband + 2} = sprintf('TS: $N = %d$', Variable.nSubbands(subbandIndex));
-
 hold off;
 grid on;
 legend(legendString);
@@ -61,14 +59,14 @@ ylabel('Average output DC current [$\mu$A]');
 xlim([0 inf]);
 ylim([0 inf]);
 box on;
-
 apply_style(plotHandle);
+
 savefig('../figures/re_subband.fig');
-matlab2tikz('../../assets/re_subband.tex');
[…]

### 2021-03-10 src/plot/plot_re_tx.m

@@ -21,7 +21,7 @@ end
 save('../data/re_tx.mat');
 
 %% * R-E plots
-figure('name', 'Average R-E region vs number of transmit antennas');
+figure('name', 'Average R-E region vs number of transmit antennas', 'position', [0, 0, 500, 400]);
 legendString = cell(1, length(Variable.nTxs));
 plotHandle = gobjects(1, length(Variable.nTxs));
 for iTx = 1 : length(Variable.nTxs)
@@ -40,4 +40,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/re_tx.fig');
-matlab2tikz('../../assets/re_tx.tex');
+matlab2tikz('../../assets/re_tx.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_scaling_reflector.m

@@ -28,7 +28,7 @@ snrDb = pow2db(2 .^ (rateWf / nSubbands));
 save('../data/scaling_reflector.mat');
 
 %% * SNR and power plots
-figure('name', 'Average SNR and harvested DC power vs number of reflectors');
+figure('name', 'Average SNR and harvested DC power vs number of reflectors', 'position', [0, 0, 500, 400]);
 pathlossPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
 
 % * SNR plot
@@ -62,4 +62,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/scaling_reflector.fig');
-matlab2tikz('../../assets/scaling_reflector.tex');
+matlab2tikz('../../assets/scaling_reflector.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 src/plot/plot_scaling_tx.m

@@ -28,7 +28,7 @@ snrDb = pow2db(2 .^ (rateWf / nSubbands));
 save('../data/scaling_tx.mat');
 
 %% * Rate and current plots
-figure('name', 'Average SNR and harvested DC power vs number of transmit antennas');
+figure('name', 'Average SNR and harvested DC power vs number of transmit antennas', 'position', [0, 0, 500, 400]);
 pathlossPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
 
 % * SNR plot
@@ -62,4 +62,4 @@ box on;
 apply_style(plotHandle);
 
 savefig('../figures/scaling_tx.fig');
-matlab2tikz('../../assets/scaling_tx.tex');
+matlab2tikz('../../assets/scaling_tx.tex', 'extraaxisoptions', ['title style={font=\huge}, ' 'label style={font=\huge}, ' 'ticklabel style={font=\LARGE}, ' 'legend style={font=\LARGE}']);

### 2021-03-10 assets/waveform_subband.tex
:art: Update labels
:art: Update layout
:construction: Update manuscript

@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black}
+legend style={legend cell align=left, align=left, draw=white!15!black},
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
@@
 };
-\addlegendentry{$s_I$}
+\addlegendentry{$\boldsymbol{s}_{\mathrm{I}}$}
 
@@
 };
-\addlegendentry{$s_P$}
+\addlegendentry{$\boldsymbol{s}_{\mathrm{P}}$}
 
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+legend style={legend cell align=left, align=left, draw=white!15!black},
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
@@
 xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
+ytick={ 0, 0.4, 0.8},
 xlabel style={font=\color{white!15!black}},

### 2021-03-10 main.tex
:construction: Update manuscript

@@
 \usepackage[caption=false,font=footnotesize]{subfig}
+% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
 % \usepackage[cmintegrals]{newtxmath}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[R-E region\label{fi:re_subband}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_subband.tex}
-			\end{adjustbox}
-			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_subband}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+				}
+			}
+			\subfloat[Waveform amplitude\label{fi:waveform_subband}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/waveform_subband.tex}
-			\end{adjustbox}
-			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:waveform_subband}
+				}
+			}
+			\caption{Average R-E region and waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[R-E region\label{fi:re_distance}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_distance.tex}
-			\end{adjustbox}
-			\caption{Average R-E region versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_distance}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+				}
+			}
+			\subfloat[Path loss\label{fi:path_loss}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/path_loss.tex}
-			\end{adjustbox}
-			\caption{Path loss versus distance for IEEE TGn channel model D.}
-			\label{fi:path_loss}
+				}
+			}
+			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[R-E region\label{fi:re_tx}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_tx.tex}
-			\end{adjustbox}
-			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_tx}
+				}
+			}
+			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/scaling_tx.tex}
+				}
+			}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[R-E region\label{fi:re_reflector}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_reflector.tex}
-			\end{adjustbox}
-			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_reflector}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
-				\input{assets/scaling_tx.tex}
-			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
-			\label{fi:scaling_tx}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+				}
+			}
+			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/scaling_reflector.tex}
-			\end{adjustbox}
-			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
-			\label{fi:scaling_reflector}
+				}
+			}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
-		\begin{figure}[!t]
-			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
-				\input{assets/re_irs_1mhz.tex}
-			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_irs_1mhz}
-		\end{figure}
 
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[$B=1\,\si{\MHz}$\label{fi:re_irs_1mhz}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/re_irs_1mhz.tex}
+				}
+			}
+			\subfloat[$B=10\,\si{\MHz}$\label{fi:re_irs_10mhz}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_irs_10mhz.tex}
-			\end{adjustbox}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_irs_10mhz}
+				}
+			}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}

### 2021-03-10 main.tex
:wrench: Update config

@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 		\end{figure}

### 2021-03-10 src/config/config_re_reflector.m

@@ -27,9 +27,9 @@ rxGain = db2pow(2);
 % AP-user distance
 directDistance = 12;
 % vertical distance from the IRS to the AP-user path
-verticalDistance = 2;
+verticalDistance = 0.5;
 % projection of AP-IRS distance to the AP-user path
-horizontalDistance = 2;
+horizontalDistance = 0.5;
 % AP-IRS and IRS-user distance
 [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
 % center frequency

### 2021-03-10 src/config/config_re_tx.m

@@ -26,9 +26,9 @@ rxGain = db2pow(2);
 % AP-user distance
 directDistance = 12;
 % vertical distance from the IRS to the AP-user path
-verticalDistance = 2;
+verticalDistance = 0.5;
 % projection of AP-IRS distance to the AP-user path
-horizontalDistance = 2;
+horizontalDistance = 0.5;
 % AP-IRS and IRS-user distance
 [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
 % center frequency

### 2021-03-10 src/config/config_scaling_reflector.m

@@ -29,7 +29,7 @@ directDistance = 12;
 % vertical distance from the IRS to the AP-user path
 verticalDistance = 0.5;
 % projection of AP-IRS distance to the AP-user path
-horizontalDistance = 0;
+horizontalDistance = 0.5;
 % AP-IRS and IRS-user distance
 [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
 % center frequency

### 2021-03-10 src/config/config_scaling_tx.m

@@ -28,7 +28,7 @@ directDistance = 12;
 % vertical distance from the IRS to the AP-user path
 verticalDistance = 0.5;
 % projection of AP-IRS distance to the AP-user path
-horizontalDistance = 0;
+horizontalDistance = 0.5;
 % AP-IRS and IRS-user distance
 [incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
 % center frequency

### 2021-03-12 main.tex
:ambulance: Fix noise variance notation

--- 2021-03-10 main.tex
@@
 				\begin{equation}
-					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+					s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
 				\end{equation}
@@
 				\begin{align}
-					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
+					s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
 					s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
@@
 Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n^2=-40\,\si{\dBm}$ at all subbands as reference.
 We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain.
@@
 		\begin{subsection}{Imperfect CSIT}
-			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially when the coherence time is short.
-Hence, we consider an imperfect CSIT model and denote the estimation of direct and cascaded links at subband $n$ as
-			\begin{align}
-				\hat{\boldsymbol{h}}_{\mathrm{D},n} &= \boldsymbol{h}_{\mathrm{D},n} + \tilde{\boldsymbol{h}}_{\mathrm{D},n} \\
-				\hat{\boldsymbol{V}}_{n} &= \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
-			\end{align}
-			where $\tilde{\boldsymbol{h}}_{\mathrm{D},n}$ and $\tilde{\boldsymbol{V}}_{n}$ are the corresponding estimation errors, whose entries follow i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{\mathrm{D},n}^2)$ and $\mathcal{CN}(0, \epsilon_{n}^2)$, respectively.
-Perfect CSIT can be regarded as a special case with $\epsilon_{\mathrm{D},n} = \epsilon_{n} = 0$.
+			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time.
+Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
+			\begin{equation}
+				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+			\end{equation}
+			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
+Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$.
 % For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
@@
 			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient.
-To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and quantize each reflection coefficient by $b$ bits.
+To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
 		\end{subsection}
@@
 			}
-			\subfloat[Waveform amplitude\label{fi:waveform_subband}]{
+			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\caption{Average R-E region and waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 			\label{fi:re_noise}
@@
 As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity.
-\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$).
+\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n^2 \le -40\,\si{\dBm}$).
 The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization.
@@
 			}
-			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
 		\end{figure}

### 2021-03-12 src/plot/plot_re_noise.m

@@ -42,8 +42,8 @@ hold all;
 for iNoise = 1 : length(Variable.noisePower)
     plotHandle(1, iNoise) = plot(reAoNoise{iNoise}(1, :) / nSubbands, 1e6 * reAoNoise{iNoise}(2, :));
     plotHandle(2, iNoise) = plot(reLcNoise{iNoise}(1, :) / nSubbands, 1e6 * reLcNoise{iNoise}(2, :));
-    legendString{1, iNoise} = sprintf('AO: $\\sigma_n = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
-    legendString{2, iNoise} = sprintf('LC (PS): $\\sigma_n = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
+    legendString{1, iNoise} = sprintf('AO: $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
+    legendString{2, iNoise} = sprintf('LC (PS): $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
 end
 hold off;
 grid on;

### 2021-03-15 main.tex
:pencil: Update abstract

@@
 	\begin{abstract}
-		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the strength of the received Radio-Frequency (RF) signal.
-To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by a passive beamforming gain.
-This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS.
-Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the UE.
-Stationary solutions are achieved by the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique.
-Although practical IRS is limited to Frequency-Flat (FF) reflection, results demonstrate significant benefits of the proposed architecture based on a joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT.
+		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength.
+To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency.
+This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS.
+Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
+This non-convex problem is then solved by the Alternating Optimization (AO) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
+Since the complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation.
+Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, active and passive beamforming.
+		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, beamforming design, energy harvester nonlinearity.
 	\end{IEEEkeywords}

### 2021-03-16 main.tex
:pencil: Update literature review

@@
 			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-Most existing mobile devices are powered by batteries that require frequent charging or replacement, which brings high maintenance cost and restricts the scale of networks.
+			% Most existing mobile devices are powered by batteries that require frequent charging or replacement, which brings high maintenance cost and restricts the scale of networks.
 Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range.
@@
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
+The rapid increase in the number of wireless devices, together with the steady decrease in electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
 
 			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components.
+\cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e.
+Time Switching (TS) and Power Splitting (PS).
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2013} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the input rectifier power and waveform shape.
+On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency of rectifiers depends on the input power and waveform shape.
 It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
 Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT.
-Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}.
-Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range.
-Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}, which uniquely showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2020}.
+A low-complexity adaptive waveform design was then proposed in \cite{Clerckx2017} that utilizes the rectifier nonlinearity by Scaled Matched Filter (SMF).
+Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \textit{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
@@
 It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
+Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
 		\end{subsection}
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming.
-Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection.
-Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS because active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.
+			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to enhance the spectrum and energy efficiency.
+In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incoming signal for a smart reflection (i.e.
+passive beamforming).
+Different from relay, backscatter and Frequency-Selective Surface (FSS) \cite{Kim2006,Anwar2018}, IRS adaptively assists the primary transmission by passive components to suppress thermal noise but is limited to frequency-dependent reflection.
 
@@
 Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
-The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-Moreover, \cite{Abeywickrama2019} investigated the coupling effect between reflection amplitude and phase shift based on the impedance equation, and \cite{Nadeem2019} proposed a sequential cascaded channel estimation for Time-Division Duplex (TDD) systems.	A novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems was proposed in \cite{Yang2020}, which varies the reflection coefficients over consequent slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
+The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
+In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift when power dissipation is considered at the IRS.
+To estimate the cascaded AP-IRS-User Equipment (UE) link, practical protocols based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} have been invented with no RF-chains at the IRS.
+\cite{Yang2020} proposed a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT.
+			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power, where the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers.
-However, to the best of our knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power since one energy beam can satisfy all energy receivers under rank-deficient channels.
+However, to the best of our knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission with inaccurate linear energy harvester model.
 In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.

### 2021-03-18 main.tex
:pencil: Update contributions

@@
 This non-convex problem is then solved by the Alternating Optimization (AO) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
-Since the complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation.
+Since the computational complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation.
 Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
@@
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The rapid increase in the number of wireless devices, together with the steady decrease in electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
+The upsurge in the number of wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
 
@@
 Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2020}.
-A low-complexity adaptive waveform design was then proposed in \cite{Clerckx2017} that utilizes the rectifier nonlinearity by Scaled Matched Filter (SMF).
+A low-complexity adaptive waveform design was then proposed in \cite{Clerckx2017} to enjoy the advantage of the rectifier nonlinearity by Scaled Matched Filter (SMF).
 Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \textit{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
 The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g.
@@
 		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incoming signal for a smart reflection (i.e.
+			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
+In practice, an IRS consists of multiple individual reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e.
 passive beamforming).
-Different from relay, backscatter and Frequency-Selective Surface (FSS) \cite{Kim2006,Anwar2018}, IRS adaptively assists the primary transmission by passive components to suppress thermal noise but is limited to frequency-dependent reflection.
+Different from relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, IRS adaptively assists the primary transmission by passive components to suppress thermal noise but is limited to frequency-dependent reflection.
 
@@
 The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift when power dissipation is considered at the IRS.
-To estimate the cascaded AP-IRS-User Equipment (UE) link, practical protocols based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} have been invented with no RF-chains at the IRS.
-\cite{Yang2020} proposed a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
+In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
+To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} have been proposed.
+\cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power since one energy beam can satisfy all energy receivers under rank-deficient channels.
-However, to the best of our knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission with inaccurate linear energy harvester model.
-In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS.
-We ask ourselves the important question: \textit{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?} The contributions of the paper are listed as follows.
+For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the WSP since rank-deficient channels require less energy beams.
+However, the above papers only consider single-carrier transmission based on inaccurate linear energy harvester model.
+Motivated by this, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS in this paper.
+We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
 
-			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design.
-This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT.
-Specifically, we consider a IRS-aided multi-carrier downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user.
-A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency.
-The power and information waveforms and the active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity.
-This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model \cite{Clerckx2019,Clerckx2016a}), which prevents from exploiting the waveform gain in SWIPT system design.
-On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the joint design of waveform, active and passive beamforming accounting for rectenna nonlinearity.
+			% 1. propose the system
+			% 2. formulate the problem and propose the algorithm
+			% 3. propose low-complexity waveform design
+			% 4. evaluate the performance and reach some conclusion
+			% 5. test the performance under imperfect csit and quantized irs
 
-			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture.
-The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints.
-Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence.
-On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner.
-Numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.
+			\textit{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
+To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under two practical transceiving modes.
+The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+This is the first paper to tackle energy harvester nonlinearity, multi-carrier transmission, and co-localized receiver for IRS-aided SWIPT.
 
-			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture.
-Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency-flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design.
-We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT.
-Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal performance, 2) the number of transmit antenna and IRS elements have no noticeable impact on the optimal transceiving mode (TS/PS), 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflecting elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) for narrowband transmission, the optimal active and passive beamforming are fixed for a given channel, and one only need to update the waveform and splitting ratio to draw the whole R-E boundary, 6) for broadband transmission, the frequency diversity enables rate-dependent adaptive passive beamforming to control the subchannel strength distribution and improve the R-E tradeoff.
+			\textit{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Alternating Optimization (AO) algorithm based on Channel State Information at the Transmitter (CSIT).
+For active beamforming, we uniquely prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) precoder under rectifier nonlinearity.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relaxation-then-extraction method.
+Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
+Numerical results demonstrate the strict convergence of the proposed AO algorithm under various configurations.
 
-			\textit{Organization:} The rest of this paper is organized as follows.
-Section~\ref{se:system_model} introduces the signal, channel, receiver, and R-E tradeoff models of the IRS-aided SWIPT system.
-Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization.
-Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design.
+			\textit{Third}, we introduce two low-complexity adaptive waveform design to avoid the exponential complexity of the GP algorithm.
+The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
+
+			\textit{Fourth}, we provide numerical results to evaluate the performance of proposed algorithms.
+It is concluded that 1) the multisine waveform is beneficial to multi-carrier energy transfer especially when number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) Wireless Information Transfer (WIT) and WPT prefer different passive beamforming especially when the bandwidth is large.
+These observations demonstrate the advantage of the proposed IRS-aided SWIPT architecture and emphasize the importance of accounting harvester nonlinearity in the system design.
+
+			\textit{Fifth}, since the IRS is generally passive and with finite reflection states, we investigate the influence of imperfect CSIT and quantized IRS on the overall R-E behavior.
+The adaptive algorithms are proved robust and effective under different channel estimation errors, and only ?
+quantization bits are required for each IRS element to offer a decent performance.
+It suggests that the proposed waveform and beamforming design
+
+			\textit{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving mode and rectifier nonlinearity.
+Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization.
+Section~\ref{se:performance_evaluation} presents the simulation results and evaluates the proposed algorithms.
 Section~\ref{se:conclusion_and_future_works} concludes the paper.
 
-			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters.
-$j$ refers to the imaginary unit.
+			\textit{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case and bold upper-case letters.
+$j$ denotes the imaginary unit.
 $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices.
-$\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively.
-$(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively.
-$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathbb{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity).
-For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value.
-For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal.
-For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank.
-For a square matrix $\boldsymbol{S}$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite.
-The distribution of a CSCG random vector with mean vector $\boldsymbol{0}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$, and $\sim$ stands for "distributed as".
-We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as the stationary solution and the solution at iteration $i$, respectively.
+$\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
+$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators.
+$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{Tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote the argument, rank, trace, and a square matrix with input elements on the main diagonal.
+$\boldsymbol{S} \succeq 0$ means $\boldsymbol{S}$ is positive semi-definite.
+$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
+$\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity).
+The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
+$\sim$ means "distributed as".
+$(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
 		\end{subsection}

### 2021-03-19 main.tex
:pencil: Update system model

@@
 Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This non-convex problem is then solved by the Alternating Optimization (AO) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
+This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
 Since the computational complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation.
@@
 For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the WSP since rank-deficient channels require less energy beams.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the WSP because rank-deficient channels require less energy beams.
 However, the above papers only consider single-carrier transmission based on inaccurate linear energy harvester model.
@@
 
-			\textit{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
-To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under two practical transceiving modes.
+			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
+To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
 The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
@@
 
-			\textit{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Alternating Optimization (AO) algorithm based on Channel State Information at the Transmitter (CSIT).
-For active beamforming, we uniquely prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) precoder under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relaxation-then-extraction method.
+			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relax-then-extract method.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
-Numerical results demonstrate the strict convergence of the proposed AO algorithm under various configurations.
+Numerical results demonstrate the strict convergence of the proposed BCD algorithm under various configurations.
 
-			\textit{Third}, we introduce two low-complexity adaptive waveform design to avoid the exponential complexity of the GP algorithm.
+			\emph{Third}, we introduce two low-complexity adaptive waveform design to avoid the exponential complexity of the GP algorithm.
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
 
-			\textit{Fourth}, we provide numerical results to evaluate the performance of proposed algorithms.
-It is concluded that 1) the multisine waveform is beneficial to multi-carrier energy transfer especially when number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) Wireless Information Transfer (WIT) and WPT prefer different passive beamforming especially when the bandwidth is large.
+			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) Wireless Information Transfer (WIT) and WPT prefer different passive beamforming especially when the bandwidth is large.
 These observations demonstrate the advantage of the proposed IRS-aided SWIPT architecture and emphasize the importance of accounting harvester nonlinearity in the system design.
 
-			\textit{Fifth}, since the IRS is generally passive and with finite reflection states, we investigate the influence of imperfect CSIT and quantized IRS on the overall R-E behavior.
+			\emph{Fifth}, since the IRS is generally passive and with finite reflection states, we investigate the influence of imperfect CSIT and quantized IRS on overall R-E behavior.
 The adaptive algorithms are proved robust and effective under different channel estimation errors, and only ?
-quantization bits are required for each IRS element to offer a decent performance.
-It suggests that the proposed waveform and beamforming design
+quantization bits are required for each IRS element to provide a decent performance.
+% It suggests that the proposed waveform and beamforming design
 
-			\textit{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving mode and rectifier nonlinearity.
+			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving mode and rectifier nonlinearity.
 Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization.
@@
 
-			\textit{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case and bold upper-case letters.
+			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case and bold upper-case letters.
 $j$ denotes the imaginary unit.
@@
 
-		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna User Equipment (UE) over $N$ orthogonal evenly-spaced subbands.
-We assume perfect or partial Channel State Information at the Transmitter (CSIT) regarding the quasi-static AP-UE and AP-IRS-UE cascaded channels.
-The signals reflected two or more times are omitted and the noise power is assumed too small to be harvested.
+		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
+We consider quasi-static block fading and assume the CSIT of AP-UE and AP-IRS-UE cascaded channels are given.
+The signals reflected by two or more times are omitted and the noise power is assumed too small to be harvested.
 
@@
 		\begin{subsection}{Reflection Pattern and Composite Channel}
-			Green's decomposition \cite{Hansen1989} suggests that the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
 The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
@@
 This paper sticks to the commonest and simplest IRS model where the reflection coefficient is assumed unit.}.
-We also denote $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ as the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
+We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
 
@@
 				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
-Since the reactance $X_l$ depends on frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
+Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
 In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficients of each IRS element are the same at all subbands.
-That is to say, $\phi_l$ is shared by $M$ AP-IRS-UE channels over $N$ subbands.
+That is to say, $\phi_l$ is shared by $M$ auxiliary channels over $N$ subbands.
 			\end{remark}
@@
 The auxiliary link provided by the IRS can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
-Therefore, the composite equivalent channel reduces to
+Hence, the composite equivalent channel reduces to
 			\begin{equation}\label{eq:h_n}
@@
 			\end{equation}
-			where we define the cascaded AP-IRS-UE channel without reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+			where we define the cascaded AP-IRS-UE channel (without IRS reflection) as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 		\end{subsection}
@@
 		\begin{subsection}{Transceiving Modes}
-			Consider TS and PS as two practical transceiving modes in the SWIPT system design.
+			Consider TS and PS as two practical transceiving modes for SWIPT.
 TS relies on perfect clock synchronization, where the transmitter divides each slot into dedicated data session with length $1 - \eta$ and energy session with length $\eta$, then designs the waveform for WIT and WPT independently.
-At the receiver end, only information decoder or energy harvester would be activated in the corresponding session.
-Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E segment from WIT point to WPT point.
+At the receiver, only information decoder or energy harvester is activated at a time.
+Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E segment from the WIT point to the WPT point.
 
-			On the other hand, the PS transmitter optimizes the superposed waveform that remains unchanged in the entire slot, and the receiver splits the incoming signal into individual data stream with power proportion $1 - \rho$ and energy stream with power proportion $\rho$.
-Note that in PS the splitting ratio $\rho$ and the superposed waveform are coupled thus require a joint design, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
-Therefore, we focus on PS in the following context since TS can be obtained by a direct time sharing between WIT and WPT.
+			On the other hand, the PS waveform consists of modulated and multisine components, and the receiver splits the incoming signal into individual data stream with power ratio $1 - \rho$ and energy stream with power ratio $\rho$.
+Note that in PS the splitting ratio $\rho$ and the superposed waveform require a joint design, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
+Therefore, we focus on PS in the following context since TS can be regard as a special case (a time sharing between WIT and WPT).
 		\end{subsection}
@@
 			\end{equation}
-			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$.
+			where $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$.
 Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
-Hence, the components of the average output DC current $z$ can be expressed in \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 
@@
 				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}
 				\end{equation}
-				\hrule
 				\begin{flalign}
@@
 			% \end{equation}
-			where $P$ is the average transmit power budget and the coefficient \num{1/2} converts the peak power of sinewaves to the average power.
+			where $P$ is the average transmit power budget and \num{1/2} converts the peak value to the average value.
 		\end{subsection}
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
+		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint
 		\begin{maxi!}
@@
 		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose an AO algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence.
-		\begin{remark}\label{re:irs_subchannel_alignment}
-			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
+To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
+		% \begin{remark}\label{re:irs_subchannel_alignment}
+		% 	As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
 Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands.
 In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
-		\end{remark}
+		% \end{remark}
 
@@
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, we can rewrite the rate and average DC current expressions as
+Therefore, we can rewrite \ref{eq:R} and \ref{eq:z_expand} as
 			\begin{align}
@@
 			% \end{align}
-			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by their first-order Taylor expansion \cite{Adali2010}.
+			To maximize the non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm and lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 			% \end{align}
-			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}.
-Hence, the objective function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to
+			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 			\end{maxi!}
-			Problem~\eqref{op:irs} is not a standard Semidefinite Programming (SDP).
+			Problem~\eqref{op:irs} is not a Semidefinite Programming (SDP).
 If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the extracted rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ be a stationary point of the original problem~\eqref{op:original}.
@@
 
-		\begin{subsection}{Alternating Optimization}
+		\begin{subsection}{Block Coordinate Descent}
 			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
-The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
+The BCD algorithm is summarized in Algorithm~\ref{al:alternating}.
 			\begin{algorithm}[!t]
-				\caption{AO: Waveform, Active and Passive Beamforming, and Splitting Ratio.}
+				\caption{BCD: Waveform, Active and Passive Beamforming, and Splitting Ratio.}
 				\label{al:alternating}
@@
 		This paper proposes a novel IRS-aided multi-carrier downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
-We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the power splitting ratio at the receiver to enlarge the achievable R-E region.
+We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the splitting ratio at the receiver to enlarge the achievable R-E region.
 Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission for practical co-localized receiver architectures.
-Efficient algorithms based on the AO, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
+Efficient algorithms based on the BCD, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
 We confirm that considering harvester nonlinearity, a dedicated power waveform is generally required to boost the R-E tradeoff.

### 2021-03-20 main.tex
:pencil: Update algorithms

@@
 				\hrule
-				\begin{equation}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}
-				\end{equation}
+				\begin{flalign}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),&&\label{eq:z_expand}
+				\end{flalign}
 				\begin{flalign}
@@
 			\end{figure*}
-			% \begin{figure*}[!b]
-			% 	\hrule
-			% 	\begin{align}
-			% 		z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
-			% 		& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
-			% 	\end{align}
-			% 	\hrule
-			% 	\begin{align}
-			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
-			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
-			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
-			% 		& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
-			% 		\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
-			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
-			% 		\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
-			% 		& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
-			% 		& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
-			% 	\end{align}
-			% \end{figure*}
 		\end{subsection}
@@
 			\end{align}
-			% \begin{equation}
-			% 	C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
-			% \end{equation}
 			where $P$ is the average transmit power budget and \num{1/2} converts the peak value to the average value.
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint
+		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint as
 		\begin{maxi!}
@@
 		\end{maxi!}
+
 		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}.
@@
 			\end{align}
-			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
 On the other hand, we define $t_{\mathrm{I/P},k}$ as
@@
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-Therefore, we can rewrite \ref{eq:R} and \ref{eq:z_expand} as
+On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce to
 			\begin{align}
@@
 			\end{align}
-			% \begin{align}
-			% 	R(\boldsymbol{\Phi})
-			% 	& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-			% 	z(\boldsymbol{\Phi})
-			% 	& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
-			% \end{align}
+
 			To maximize the non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm and lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
@@
 			\end{align}
-			% \begin{align}
-			% 	(t_{\mathrm{I},0}^{(i)})^2
-			% 	& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
-			% 	t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
-			% 	& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
-			% 	t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
-			% 	& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
-			% 	& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
-			% \end{align}
-			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+
+			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
+				\addConstraint{\boldsymbol{\Phi}\succeq{0}}\label{co:irs_sd}
 				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
 			\end{maxi!}
-			Problem~\eqref{op:irs} is not a Semidefinite Programming (SDP).
-If we relax the rank constraint \eqref{co:irs_rank} to formulate a convex problem, there is no guarantee that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} and the extracted rank-\num{1} solution $\boldsymbol{\phi}^{\star}$ be a stationary point of the original problem~\eqref{op:original}.
-In Section~\ref{se:performance_evaluation}, we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations under different configurations, where the performance loss by SDR is negligible.
-If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the augmented phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD).
-Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}, where we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \eqref{ob:irs}.
-Finally, the phase shifts are retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star), \ l=1,\dots,L$.
-Problem~\eqref{op:irs} without constraint \eqref{co:irs_rank} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
-The SCA algorithm for the passive beamforming optimization is summarized in Algorithm~\ref{al:irs}.
+
+			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee.
+In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
+It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible impact and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD).
+In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
+Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
+Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
+Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}.
+The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:irs}.
 			\begin{algorithm}[!t]
@@
 						\State $i \gets i + 1$
-						\State Obtain $\boldsymbol{\Phi}^{(i)},t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by solving problem~\eqref{op:irs}
+						\State Get $\boldsymbol{\Phi}^{(i)},t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
-						\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
 					\Else
-						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
+						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
 						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
 						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
-						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
+						\State Set $q^{\star}=\arg\max_q{\tilde{z}(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
 					\EndIf
@@
 			\end{equation}
-			where $s_{\mathrm{I/P},n}$ are the amplitude of modulated/multisine waveform at tone $n$ and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denote the corresponding precoders.
-The optimal MRT precoder at subband $n$ is given by
-			\begin{equation}
+			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the information/power precoder.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$.
+On the other hand, the MRT precoder at subband $n$ is given by
+			\begin{equation}\label{eq:b}
 				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
 			\end{equation}
-			From the perspective of data transmission, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the sum rate \eqref{eq:R}.
+
+			From the perspective of communication, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes rate \eqref{eq:R}.
 From the perspective of energy harvesting, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
@@
 		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize the waveform and active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$.
-As pointed out in \cite{Clerckx2018b}, the waveform design in the frequency domain and the active beamformer in the spatial domain can be decoupled without performance loss, and the optimal spatial weight is given by Maximum-Ratio Transmission (MRT) beamformer
-			\begin{equation}\label{eq:w_IP}
-				\boldsymbol{w}_{\mathrm{I/P},n}=s_{\mathrm{I/P},n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
-			\end{equation}
-			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{\mathrm{I/P},n}$ at different tones.
-Hence, the original waveform and active beamforming optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$.
-At subband $n$, the effective channel strength is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{\mathrm{I},n}^2$ and $s_{\mathrm{P},n}^2$, respectively.
-With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I},n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.
-			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\biggr)\right).
-			\end{equation}
+			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}, n}$, $\forall n$.
+On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
+Hence, rate \eqref{eq:R} and DC current \eqref{eq:z_expand} reduce respectively to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, and problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
@@
 				\begin{align}
+					R(\boldsymbol{s}_{\mathrm{I}},\rho)
+					& = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\biggr)\right),\label{eq:R_waveform}\\
 					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2)\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
+					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).&&\label{eq:z_waveform}
 				\end{align}
 			\end{figure*}%
-			Therefore, problem~\eqref{op:original} is reduced to an amplitude optimization issue
 			\begin{maxi!}
@@
 			\end{maxi!}
-			Since problem~\eqref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
+
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform it into a reversed GP
 			\begin{mini!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_rgp}}{}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\frac{t'}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
@@
 			\end{mini!}
-			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} that can be further decomposed as
+
+			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} which can be decomposed as sums of monomials
 			\begin{align}
@@
 			\end{align}
-			where $m_\mathrm{P}=(2N^3+6N^2+7N)/3$, $m_{\mathrm{I},n}=2$ are the number of monomials.
-Following \cite{Chiang2005}, we upper bound posynomials \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality such that problem~\eqref{op:waveform_rgp} reduces to
+			where $m_\mathrm{P}=(2N^3+6N^2+7N)/3$ and $m_{\mathrm{I},n}=2$.
+We then upper bound \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 			\begin{mini!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:waveform_gp}}{}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
-				\addConstraint{{t'}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
+				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
 				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
@@
 			where $\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}} \ge 0$, $\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update.
-As suggested in \cite{Clerckx2018b}, a feasible choice at iteration $i$ is
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update \cite{Clerckx2018b}, and a feasible choice at iteration $i$ is
 			\begin{align}
@@
 			\end{align}
+
 			$\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho$ are updated iteratively until convergence.
 Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
-The GP algorithm of the waveform, active beamforming and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
+The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
 			\begin{algorithm}[!t]
-				\caption{GP: Waveform, Active Beamforming and Splitting Ratio.}
+				\caption{GP: Waveform Amplitude and Splitting Ratio.}
 				\label{al:waveform}
@@
 						\State Update $\{\gamma_{m_\mathrm{P}}^{(i)},\gamma_{m_{\mathrm{I},n}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
-						\State Obtain $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$, retrieve $\boldsymbol{w}_{\mathrm{I/P}}^{\star}$ by \eqref{eq:w_IP}
-					\State \textbf{Output} $\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
+					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
+					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star},\boldsymbol{s}_{\mathrm{P}}^{\star},\rho^{\star}$
 				\end{algorithmic}
@@
 						\State $i \gets i + 1$
-						\State Fix $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
+						\State Fix $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$, get $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
 						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, obtain $\boldsymbol{w}_{\mathrm{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}

### 2021-03-21 main.tex
:pencil: Update algorithms

@@
 Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its $k$-th ($k=-N+1,\dots,N-1$) block diagonal and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$.
 Hence, the components of $z$ reduce to \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
@@
 				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})
+				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
 			\end{align}
@@
 In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible impact and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD).
-In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}.
+It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD).
+In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Huang2010}.
 Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
@@
 Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}.
-The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:irs}.
+The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
 			\begin{algorithm}[!t]
 				\caption{SCA: IRS Phase Shift.}
-				\label{al:irs}
+				\label{al:sca}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{H}_{\mathrm{I},n},\boldsymbol{h}_{\mathrm{R},n},\boldsymbol{w}_{\mathrm{I/P}},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-					\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{\mathrm{I/P},k}^{(0)}$, $\forall k$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\Phi}^{(i)},t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
+						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
+						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
 						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
@@
 			\end{algorithm}
+
+			\begin{proposition}\label{pr:sca}
+				For any feasible initial point, the proposed SCA Algorithm~\ref{al:sca} can provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+			\end{proposition}
+
+			\begin{proof}\label{pf:sca}
+				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution of problem~\eqref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
+Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
+To prove $\boldsymbol{\Phi}^{(i)}$ converges to stationary points, we notice that the SCA-based Algorithm~\ref{al:sca} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Therefore, Algorithm~\ref{al:sca} is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions.
+			\end{proof}
 		\end{subsection}
@@
 			In the single-user scenario, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
-			\begin{equation}
+			\begin{equation}\label{eq:w}
 				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
@@
 			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$.
-On the other hand, the MRT precoder at subband $n$ is given by
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$ and $\boldsymbol{b}_{\mathrm{I/P}} \triangleq [\boldsymbol{b}_{\mathrm{I/P}, 1}^T,\dots,\boldsymbol{b}_{\mathrm{I/P}, N}^T]^T \in \mathbb{C}^{MN \times 1}$ for simplicity.
+The MRT precoder at subband $n$ is given by
 			\begin{equation}\label{eq:b}
@@
 
-			From the perspective of communication, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes rate \eqref{eq:R}.
+			From the perspective of communications, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes rate \eqref{eq:R}.
 From the perspective of energy harvesting, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
-Hence, MRT is the global optimal precoder and no dedicated energy beams are required in the single-user SWIPT.
+Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
 		\end{subsection}
@@
 		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}, n}$, $\forall n$.
+			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}}$.
 On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
@@
 Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
-The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:waveform}.
+The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:gp}.
 			\begin{algorithm}[!t]
 				\caption{GP: Waveform Amplitude and Splitting Ratio.}
-				\label{al:waveform}
+				\label{al:gp}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_n,P,\sigma_n,\bar{R},\epsilon$, $\forall n$
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
@@
 			\end{algorithm}
+
+			\begin{proposition}\label{pr:gp}
+				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to a local optimal point of the waveform amplitude and splitting ratio problem \eqref{op:waveform}.
+			\end{proposition}
+
+			\begin{proof}\label{pf:gp}
+				See \cite{Clerckx2016a,Clerckx2018b}.
+			\end{proof}
 		\end{subsection}
@@
 		\begin{subsection}{Block Coordinate Descent}
-			For any direct, incident and reflective channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:irs}, and the waveform, active beamforming $\boldsymbol{w}_{\mathrm{I/P}}$ together with the splitting ratio $\rho$ by Algorithm~\ref{al:waveform} until convergence.
-The BCD algorithm is summarized in Algorithm~\ref{al:alternating}.
+			Based on the CSIT of direct and cascaded channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+The BCD algorithm is summarized in Algorithm~\ref{al:bcd}.
 			\begin{algorithm}[!t]
-				\caption{BCD: Waveform, Active and Passive Beamforming, and Splitting Ratio.}
-				\label{al:alternating}
+				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
+				\label{al:bcd}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{H}_{\mathrm{I},n},\boldsymbol{h}_{\mathrm{R},n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P}}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$
+					\State Get $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Fix $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$, get $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
-						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, obtain $\boldsymbol{w}_{\mathrm{I/P}}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+						\State Update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ based on $\boldsymbol{h}_n^{(i)}$, $\forall n$ by Algorithm~\ref{al:gp}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
@@
 			\end{algorithm}
-		\end{subsection}
 
-		\begin{subsection}{Convergence}
-			\begin{proposition}\label{pr:irs}
-				For any feasible initial point, the proposed SCA-based Algorithm~\ref{al:irs} can provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+			\begin{proposition}\label{pr:bcd}
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD algorithm is a local optimal point of the original problem~\eqref{op:original}.
 			\end{proposition}
 
-			\begin{proof}\label{pf:irs}
-				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution of problem~\eqref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
-Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
-Thus, Algorithm~\ref{al:irs} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converges to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm~\ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, Algorithm~\ref{al:irs} is guaranteed to provide a feasible $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions.
-			\end{proof}
-
-			\begin{proposition}\label{pr:waveform}
-				For any feasible initial point, the GP-based Algorithm~\ref{al:waveform} is guaranteed to converge to a stationary point of the waveform, active beamforming and splitting ratio subproblem.
-			\end{proposition}
-
-			\begin{proof}\label{pf:waveform}
-				See \cite{Clerckx2016a,Clerckx2018b}.
-			\end{proof}
-
-			\begin{proposition}\label{pr:ao}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem~\eqref{op:original}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:ao}
-				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the average transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be obtained by EVD without performance loss, and the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I}}^{(i)},\boldsymbol{w}_{\mathrm{P}}^{(i)},\rho^{(i)}\}$ generated by alternatively optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho$ has limit points and Algorithm~\ref{al:alternating} is guaranteed to converge.
-As demonstrated in \cite{Grippo2000}, the solution is a stationary point of problem~\eqref{op:original}.
+			\begin{proof}\label{pf:bcd}
+				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be extracted without performance loss and strict convergence of Algorithm~\ref{al:bcd} is guaranteed.
+As demonstrated in \cite{Grippo2000}, the limit point obtained by alternatively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P}}$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via BCD is a local optimal solution of problem~\eqref{op:original}.
 			\end{proof}
@@
 
-		We first evaluate the performance of Algorithm~\ref{al:irs} under SDR.
+		We first evaluate the performance of Algorithm~\ref{al:sca} under SDR.
 It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and the Gaussian randomization step is not required.
-Therefore, we claim Algorithm~\ref{al:irs} converges to stationary points of problem~\eqref{op:irs} without performance loss.
+Therefore, we claim Algorithm~\ref{al:sca} converges to stationary points of problem~\eqref{op:irs} without performance loss.
 

### 2021-03-22 main.tex
:construction: Low-complexity algorithms

@@
 Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2020}.
-A low-complexity adaptive waveform design was then proposed in \cite{Clerckx2017} to enjoy the advantage of the rectifier nonlinearity by Scaled Matched Filter (SMF).
+A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
 Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
@@
 We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
-
-			% 1. propose the system
-			% 2. formulate the problem and propose the algorithm
-			% 3. propose low-complexity waveform design
-			% 4. evaluate the performance and reach some conclusion
-			% 5. test the performance under imperfect csit and quantized irs
 
@@
 $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators.
+$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm operators.
 $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{Tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote the argument, rank, trace, and a square matrix with input elements on the main diagonal.
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			\begin{subsubsection}{Waveform and Active Beamforming}
-				The optimal resource allocation for WIT corresponds to the Water-Filling (WF) strategy that assigns the amplitude of modulated tone $n$ by
-				\begin{equation}
+			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity w.r.t.
+the number of subbands \cite{Chiang2005}.
+To facilitate practical SWIPT implementation, we propose two low-complexity waveform amplitude design by combining WF and SMF under TS and PS setups.
+The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
+			\begin{equation}\label{eq:wf}
 				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
@@
 			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation and the details are omitted here.
-On the other hand, the Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} as a suboptimal resource allocation scheme for WPT.
-It involves no modulated waveform and assigns the amplitude of sinewave $n$ by
-				\begin{equation}
+The closed-form solution can be obtained by iterative power allocation \cite{Tse2005} and the details are omitted here.
+On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
+			\begin{equation}\label{eq:smf}
 				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
 			\end{equation}
-				where the only design variable $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-$\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subchannels and suppresses the weak ones.
-The advantage of SMF has been experimentally demonstrated in a practical WPT system with channel acquisition \cite{Kim2017}.
+			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
+$\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subbands and suppresses the weak ones.
 
-				To facilitate practical SWIPT implementation, we provide two low-complexity adaptive design by combining WF and SMF under TS and PS setups.	Specifically, the low-complexity TS scheme divides each time slot into dedicated data session with proportion $1 - \eta$ and dedicated energy session with proportion $\eta$, then performs WF and SMF respectively.
-Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E line from WIT point to WPT point.
-In contrast, the low-complexity PS scheme involves the design of splitting ratio $\rho$ as well as a superposed waveform, where the proportion of WF and SMF are controlled by a balancing ratio $\delta$ as
+			In the low-complexity TS waveform design, modulated waveform is used in the data session while multisine waveform is used in the energy session, and their amplitudes are given respectively by \eqref{eq:wf} and \eqref{eq:smf}.
+The R-E boundary is a segment between the WIT point ($\eta=0$) and the WPT point ($\eta=1$).
+
+			% For the WIT point, we
+
+			On the other hand, the low-complexity PS scheme controls the superposed waveform by balancing ratio $\delta$ and involves the design of splitting ratio $\rho$.
+The amplitude of modulated and multisine components are
 			\begin{align}
@@
 			\end{align}
-				That is to say, the suboptimal TS scheme only need to design $\alpha$ while the suboptimal PS scheme should also consider $\rho$ and $\delta$ for different R-E tradeoff.
-			\end{subsubsection}
+
+			Note that the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform while the splitting ratio $\rho$ denotes the proportion used for energy harvesting.
+For low-complexity PS design, we characterize the achievable R-E region by varying $\delta$ and $\rho$ from \num{0} to \num{1} such that the rate constraint \eqref{co:irs_rate} in the passive beamforming problem can be dropped (i.e.
+set $\bar{R}=0$).
+
+			Moreover, the low-complexity TS design can be regarded as a special case where
+
+			The low-complexity algorithm for joint waveform, active and passive beamforming design under TS and PS modes is summarized in Algorithm~.
+
+			% In contrast, the R-E boundary of low-complexity TS design is a segment
+
+			\begin{algorithm}[!t]
+				\caption{Low-Complexity Design under TS and PS Modes.}
+				\label{al:lc}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\delta,\rho,\sigma_n,\bar{R}=0,Q,\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P}}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$
+					\State Get $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\Repeat
+						\State $i \gets i + 1$
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:sca}
+						\State Update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$ based on $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:wf}, {eq:smf}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
 		\end{subsection}

### 2021-03-23 main.tex
:pencil: Low-complexity algorithm

@@
 						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
-						\State Set $q^{\star}=\arg\max_q{\tilde{z}(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
+						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
 					\EndIf
@@
 On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
-Hence, rate \eqref{eq:R} and DC current \eqref{eq:z_expand} reduce respectively to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, and problem~\eqref{op:original} boils down to
+Hence, rate \eqref{eq:R} reduces to
+			\begin{equation}\label{eq:R_waveform}
+				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right)
+			\end{equation}
+			and DC current \eqref{eq:z_expand} reduces to \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
@@
 				\begin{align}
-					R(\boldsymbol{s}_{\mathrm{I}},\rho)
-					& = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\biggr)\right),\label{eq:R_waveform}\\
 					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
@@
 				\end{align}
-			\end{figure*}%
+			\end{figure*}
 			\begin{maxi!}
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity w.r.t.
-the number of subbands \cite{Chiang2005}.
+			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity \cite{Chiang2005}.
 To facilitate practical SWIPT implementation, we propose two low-complexity waveform amplitude design by combining WF and SMF under TS and PS setups.
@@
 			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-$\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subbands and suppresses the weak ones.
-
-			In the low-complexity TS waveform design, modulated waveform is used in the data session while multisine waveform is used in the energy session, and their amplitudes are given respectively by \eqref{eq:wf} and \eqref{eq:smf}.
-The R-E boundary is a segment between the WIT point ($\eta=0$) and the WPT point ($\eta=1$).
-
-			% For the WIT point, we
-
-			On the other hand, the low-complexity PS scheme controls the superposed waveform by balancing ratio $\delta$ and involves the design of splitting ratio $\rho$.
-The amplitude of modulated and multisine components are
+In the low-complexity TS waveform design, modulated waveform \eqref{eq:wf} is used in the data session while multisine waveform \eqref{eq:smf} is used in the energy session.
+In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and the amplitude of modulated and multisine components are given by
 			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
+				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
 			\end{align}
 
-			Note that the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform while the splitting ratio $\rho$ denotes the proportion used for energy harvesting.
-For low-complexity PS design, we characterize the achievable R-E region by varying $\delta$ and $\rho$ from \num{0} to \num{1} such that the rate constraint \eqref{co:irs_rate} in the passive beamforming problem can be dropped (i.e.
-set $\bar{R}=0$).
-
-			Moreover, the low-complexity TS design can be regarded as a special case where
-
-			The low-complexity algorithm for joint waveform, active and passive beamforming design under TS and PS modes is summarized in Algorithm~.
-
-			% In contrast, the R-E boundary of low-complexity TS design is a segment
+			Besides, minor modification is required for passive beamforming to cooperate with the low-complexity waveform schemes.
+To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying $\eta$, $\delta$ and $\rho$.
+Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.
 
 			\begin{algorithm}[!t]
-				\caption{Low-Complexity Design under TS and PS Modes.}
+				\caption{Modified: IRS Phase Shift.}
 				\label{al:lc}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\delta,\rho,\sigma_n,\bar{R}=0,Q,\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P}}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$
-					\State Get $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,Q,\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+					\If{$\rho=0$}
+						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} w.r.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+					\Else
 						\Repeat
 							\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$ based on $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:wf}, {eq:smf}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
+								\State Set $\bar{R}=0$
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
+								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
+					\EndIf
+					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
+						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+					\Else
+						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
+						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
+						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
+						\State Set $q^{\star}=\arg\max_q{R(\boldsymbol{\Phi}_q)}$ or $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
+					\EndIf
+					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
 				\end{algorithmic}
 			\end{algorithm}
+
+			Similar to Algorithm~\ref{al:bcd}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
 		\end{subsection}
@@
 We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.
+
+		% (denotes the proportion allocated to the multisine waveform) (denotes the proportion used for energy harvesting)
+		% The R-E boundary is a segment between the WIT point and the WPT point.
+		% where the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform and the splitting ratio $\rho$ denotes the proportion used for energy harvesting.
+The R-E region is characterized under different $\delta$ and $\rho$ from \num{0} to \num{1}.
 

### 2021-03-24 main.tex
:lipstick: Update layout plots
:pencil: Update configuration

@@
 			\import{assets/}{layout.pdf_tex}
-			\caption{System layout in the simulation.}
+			\caption{System layout in simulation.}
 			\label{fi:layout}
 		\end{figure}
-		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups.
-Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference.
-As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively.
-We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$.
-$d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference.
-The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$.
-We assume all channels are NLoS with taps modelled as i.i.d.
+		To evaluate the performance of the proposed IRS-aided SWIPT system, we suppose a layout as Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links.
+Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
+All channels are assumed NLoS with taps modelled as i.i.d.
 CSCG random variables of unit average sum-power, corresponding to a normalized multipath response.
-The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively.
-No spatial correlation is assumed across transmit antennas and IRS elements.
-Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n^2=-40\,\si{\dBm}$ at all subbands as reference.
-We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain.
-For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations.
-In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current.
-On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only.
-For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$.
-We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.
-
-		% (denotes the proportion allocated to the multisine waveform) (denotes the proportion used for energy harvesting)
-		% The R-E boundary is a segment between the WIT point and the WPT point.
-		% where the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform and the splitting ratio $\rho$ denotes the proportion used for energy harvesting.
-The R-E region is characterized under different $\delta$ and $\rho$ from \num{0} to \num{1}.
-
-		\begin{subsection}{Imperfect CSIT}
-			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time.
-Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
-			\begin{equation}
-				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
-			\end{equation}
-			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
-Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$.
-% For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
-		\end{subsection}
-
-		\begin{subsection}{Quantized IRS}
-			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient.
-To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
-		\end{subsection}
+Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}.
+For the algorithms, the tolerance is $\epsilon=10^{-8}$, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, and we assume $\delta=\rho$ for simplicity.
+All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis has been normalized to per-subband rate $R/N$.
 
@@
 The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.
+
+		\begin{subsection}{Imperfect CSIT}
+			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time.
+Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
+			\begin{equation}
+				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+			\end{equation}
+			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
+Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$.
+% For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
+		\end{subsection}
+
+		\begin{subsection}{Quantized IRS}
+			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient.
+To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
+		\end{subsection}
 	\end{section}

### 2021-03-24 main.tex
:pencil: Update notations

@@
 In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD).
-In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Huang2010}.
-Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
+It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through eigen decomposition.
+In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
+Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
 Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
@@
 					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
-						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+						\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
 					\Else
-						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
-						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
-						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
+						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
+						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
+						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
 						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
@@
 					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
-						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+						\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
 					\Else
-						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
-						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
-						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
+						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
+						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
+						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
 						\State Set $q^{\star}=\arg\max_q{R(\boldsymbol{\Phi}_q)}$ or $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
@@
 			Similar to Algorithm~\ref{al:bcd}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
+Similar to Proposition \ref{pr:bcd}, strict convergence and local optimality of the low-complexity BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
 		\end{subsection}
@@
 
+		We first provide numerical proof on the strict convergence and local optimality of the proposed BCD algorithms.
+Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
+Table~ shows the minimum value of $\nu$ during both BCD algorithms for all tested channel realizations.
+
+		evaluate the rank of IRS matrix $\boldsymbol{\Phi}^\star$ obtained by Algorithm~\ref{al:sca} and \ref{al:lc}.
+
 		We first evaluate the performance of Algorithm~\ref{al:sca} under SDR.
-It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through EVD and the Gaussian randomization step is not required.
+It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through eigen decomposition and the Gaussian randomization step is not required.
 Therefore, we claim Algorithm~\ref{al:sca} converges to stationary points of problem~\eqref{op:irs} without performance loss.

### 2021-04-08 src/plot/eval_eigenratio.m
:paintbrush: Update plot functions

@@ -1,0 +1,108 @@
+%% * Max eigenvalue over sum eigenvalue vs number of subbands
+clear; clc; close all;
+config_re_subband;
+indexSet = 1 : nBatches;
+eigRatioAoSubband = cell(nBatches, length(Variable.nSubbands), nSamples);
+eigRatioLcSubband = cell(nBatches, length(Variable.nSubbands), nSamples);
+for iBatch = 1 : nBatches
+    try
+        load(sprintf('../data/re_subband/re_subband_%d.mat', iBatch), 'reSolution');
+		for iSubband = 1 : length(Variable.nSubbands)
+			for iSample = 1 : nSamples
+				eigRatioAoSubband{iBatch, iSubband, iSample} = reSolution{iSubband}{iSample}.eigRatio;
+				eigRatioLcSubband{iBatch, iSubband, iSample} = reSolution{iSubband}{iSample}.eigRatio;
+			end
+		end
+    catch
+		indexSet(indexSet == iBatch) = [];
+        disp(iBatch);
+    end
+end
+
+eigRatioSubband = zeros(length(Variable.nSubbands), 2);
+for iSubband = 1 : length(Variable.nSubbands)
+	eigRatioSubband(iSubband, 1) = min([eigRatioAoSubband{:, iSubband, :}]);
+	eigRatioSubband(iSubband, 2) = min([eigRatioLcSubband{:, iSubband, :}]);
+end
+disp(1 - eigRatioSubband);
+
+%% * Max eigenvalue over sum eigenvalue vs number of transmit antennas
+clear; clc; close all;
+config_re_tx;
+indexSet = 1 : nBatches;
+eigRatioAoTx = cell(nBatches, length(Variable.nTxs), nSamples);
+eigRatioLcTx = cell(nBatches, length(Variable.nTxs), nSamples);
+for iBatch = 1 : nBatches
+    try
+        load(sprintf('../data/re_tx/re_tx_%d.mat', iBatch), 'reAoSolution', 'reLcSolution');
+		for iTx = 1 : length(Variable.nTxs)
+			for iSample = 1 : nSamples
+				eigRatioAoTx{iBatch, iTx, iSample} = reAoSolution{iTx}{iSample}.eigRatio;
+				eigRatioLcTx{iBatch, iTx, iSample} = reLcSolution{iTx}{iSample}.eigRatio;
+			end
+		end
+    catch
+		indexSet(indexSet == iBatch) = [];
[…]

### 2021-04-08 src/plot/plot_eigenratio.m

@@ -1,119 +1,0 @@
-clear; clc; close all;
-
-%% * Max eigenvalue over sum eigenvalue vs number of subbands
-config_re_subband;
-indexSet = 1 : nBatches;
-eigRatioSubband = cell(nBatches, length(Variable.nSubbands), nSamples);
-for iBatch = 1 : nBatches
-    try
-        load(sprintf('../data/re_subband/re_subband_%d.mat', iBatch), 'reSolution');
-		for iSubband = 1 : length(Variable.nSubbands)
-			for iSample = 1 : nSamples
-				eigRatioSubband{iBatch, iSubband, iSample} = reSolution{iSubband}{iSample}.eigRatio;
-			end
-		end
-    catch
-		indexSet(indexSet == iBatch) = [];
-        disp(iBatch);
-    end
-end
-clearvars -except eigRatioSubband;
-
-%% * Max eigenvalue over sum eigenvalue vs number of transmit antennas
-config_re_tx;
-indexSet = 1 : nBatches;
-eigRatioTx = cell(nBatches, length(Variable.nTxs), nSamples);
-for iBatch = 1 : nBatches
-    try
-        load(sprintf('../data/re_tx/re_tx_%d.mat', iBatch), 'reAoSolution');
-		for iTx = 1 : length(Variable.nTxs)
-			for iSample = 1 : nSamples
-				eigRatioTx{iBatch, iTx, iSample} = reAoSolution{iTx}{iSample}.eigRatio;
-			end
-		end
-    catch
-		indexSet(indexSet == iBatch) = [];
-        disp(iBatch);
-    end
-end
-clearvars -except eigRatioSubband eigRatioTx;
-
-%% * Max eigenvalue over sum eigenvalue vs number of IRS elements
-config_re_reflector;
-indexSet = 1 : nBatches;
-eigRatioReflector = cell(nBatches, length(Variable.nReflectors), nSamples);
-for iBatch = 1 : nBatches
-    try
-        load(sprintf('../data/re_reflector/re_reflector_%d.mat', iBatch), 'reAoSolution');
-		for iReflector = 1 : length(Variable.nReflectors)
-			for iSample = 1 : nSamples
-				eigRatioReflector{iBatch, iReflector, iSample} = reAoSolution{iReflector}{iSample}.eigRatio;
-			end
-		end
-    catch
-		indexSet(indexSet == iBatch) = [];
-        disp(iBatch);
-    end
-end
[…]

### 2021-04-08 src/plot/plot_re_csi.m

@@ -35,7 +35,7 @@ for iSubband = 1 : length(Variable.nSubbands)
 	nSubbands = Variable.nSubbands(iSubband);
 	for iError = 1 : length(Variable.cascadedErrorVariance)
 		plotHandle(iSubband, iError) = plot(reErrorCsi{iSubband, iError}(1, :) / nSubbands, 1e6 * reErrorCsi{iSubband, iError}(2, :));
-		legendString{iSubband, iError} = sprintf('$\\epsilon_n^2 = %s \\Lambda_I\\Lambda_R (N = %s)$', num2str(Variable.cascadedErrorVarianceRatio(iError)), num2str(Variable.nSubbands(iSubband)));
+		legendString{iSubband, iError} = sprintf('$\\epsilon_n^2 = %s \\Lambda_I\\Lambda_R$ $(N = %s)$', num2str(Variable.cascadedErrorVarianceRatio(iError)), num2str(Variable.nSubbands(iSubband)));
 	end
 	plotHandle(iSubband, iError + 1) = plot(reRandomCsi{iSubband}(1, :) / nSubbands, 1e6 * reRandomCsi{iSubband}(2, :));
 	legendString{iSubband, iError + 1} = sprintf('Random IRS $(N = %s)$', num2str(Variable.nSubbands(iSubband)));

### 2021-04-08 src/plot/plot_re_distance.m

@@ -32,8 +32,8 @@ hold all;
 for iDistance = 1 : length(Variable.horizontalDistance)
     plotHandle(1, iDistance) = plot(reAoDistance{iDistance}(1, :) / nSubbands, 1e6 * reAoDistance{iDistance}(2, :));
     plotHandle(2, iDistance) = plot(reLcDistance{iDistance}(1, :) / nSubbands, 1e6 * reLcDistance{iDistance}(2, :));
-    legendString{1, iDistance} = sprintf('AO: $d_H = %s$ m', num2str(Variable.horizontalDistance(iDistance)));
-    legendString{2, iDistance} = sprintf('LC (PS): $d_H = %s$ m', num2str(Variable.horizontalDistance(iDistance)));
+    legendString{1, iDistance} = sprintf('BCD: $d_H = %s$ m', num2str(Variable.horizontalDistance(iDistance)));
+    legendString{2, iDistance} = sprintf('LC-BCD: $d_H = %s$ m', num2str(Variable.horizontalDistance(iDistance)));
 end
 hold off;
 grid on;

### 2021-04-08 src/plot/plot_re_lc.m

@@ -33,12 +33,12 @@ for iSubband = 1 : length(Variable.nSubbands)
 	plotHandle = gobjects(2, length(Variable.alpha) + 1);
 	hold all;
 	plotHandle(1, 1) = plot(reAoSubband{iSubband}(1, :) / Variable.nSubbands(iSubband), 1e6 * reAoSubband{iSubband}(2, :));
-	legendString{1, 1} = 'AO (PS)';
+	legendString{1, 1} = 'BCD';
 	plotHandle(2, 1) = plot([reAoSubband{iSubband}(1, end) / Variable.nSubbands(iSubband), reAoSubband{iSubband}(1, 1) / Variable.nSubbands(iSubband)], [1e6 * reAoSubband{iSubband}(2, end), 1e6 * reAoSubband{iSubband}(2, 1)]);
 	legendString{2, 1} = 'AO (TS)';
 	for iAlpha = 1 : length(Variable.alpha)
 		plotHandle(1, iAlpha + 1) = plot(reLcSubband{iSubband, iAlpha}(1, :) / Variable.nSubbands(iSubband), 1e6 * reLcSubband{iSubband, iAlpha}(2, :));
-		legendString{1, iAlpha + 1} = sprintf('LC (PS): $\\alpha = %s$', num2str(Variable.alpha(iAlpha)));
+		legendString{1, iAlpha + 1} = sprintf('LC-BCD: $\\alpha = %s$', num2str(Variable.alpha(iAlpha)));
 		plotHandle(2, iAlpha + 1) = plot([reLcSubband{iSubband, iAlpha}(1, end) / Variable.nSubbands(iSubband), reLcSubband{iSubband, iAlpha}(1, 1) / Variable.nSubbands(iSubband)], [1e6 * reLcSubband{iSubband, iAlpha}(2, end), 1e6 * reLcSubband{iSubband, iAlpha}(2, 1)]);
 		legendString{2, iAlpha + 1} = sprintf('LC (TS): $\\alpha = %s$', num2str(Variable.alpha(iAlpha)));
 	end

### 2021-04-08 src/plot/plot_re_noise.m

@@ -42,8 +42,8 @@ hold all;
 for iNoise = 1 : length(Variable.noisePower)
     plotHandle(1, iNoise) = plot(reAoNoise{iNoise}(1, :) / nSubbands, 1e6 * reAoNoise{iNoise}(2, :));
     plotHandle(2, iNoise) = plot(reLcNoise{iNoise}(1, :) / nSubbands, 1e6 * reLcNoise{iNoise}(2, :));
-    legendString{1, iNoise} = sprintf('AO: $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
-    legendString{2, iNoise} = sprintf('LC (PS): $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
+    legendString{1, iNoise} = sprintf('BCD: $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
+    legendString{2, iNoise} = sprintf('LC-BCD: $\\sigma_n^2 = %d$ dBm', pow2db(Variable.noisePower(iNoise)) + 30);
 end
 hold off;
 grid on;

### 2021-04-08 src/plot/plot_re_reflector.m

@@ -32,8 +32,8 @@ hold all;
 for iReflector = 1 : length(Variable.nReflectors)
     plotHandle(1, iReflector) = plot(reAoReflector{iReflector}(1, :) / nSubbands, 1e6 * reAoReflector{iReflector}(2, :));
     plotHandle(2, iReflector) = plot(reLcReflector{iReflector}(1, :) / nSubbands, 1e6 * reLcReflector{iReflector}(2, :));
-	legendString{1, iReflector} = sprintf('AO: $L = %d$', Variable.nReflectors(iReflector));
-	legendString{2, iReflector} = sprintf('LC (PS): $L = %d$', Variable.nReflectors(iReflector));
+	legendString{1, iReflector} = sprintf('BCD: $L = %d$', Variable.nReflectors(iReflector));
+	legendString{2, iReflector} = sprintf('LC-BCD: $L = %d$', Variable.nReflectors(iReflector));
 end
 hold off;
 grid on;

### 2021-04-08 src/plot/plot_re_subband.m

@@ -7,11 +7,11 @@ infoAmplitudeSet = cell(nBatches, length(Variable.nSubbands));
 powerAmplitudeSet = cell(nBatches, length(Variable.nSubbands));
 for iBatch = 1 : nBatches
     try
-        load(sprintf('../data/re_subband/re_subband_%d.mat', iBatch), 'reInstance', 'reSolution');
-		reSet(iBatch, :) = reInstance;
+        load(sprintf('../data/re_subband/re_subband_%d.mat', iBatch), 'reAoInstance', 'reAoSolution');
+		reSet(iBatch, :) = reAoInstance;
 		for iSubband = 1 : length(Variable.nSubbands)
-			infoAmplitudeSet{iBatch, iSubband} = sort(reSolution{iSubband}{end}.infoAmplitude);
-			powerAmplitudeSet{iBatch, iSubband} = sort(reSolution{iSubband}{end}.powerAmplitude);
+			infoAmplitudeSet{iBatch, iSubband} = sort(reAoSolution{iSubband}{end}.infoAmplitude);
+			powerAmplitudeSet{iBatch, iSubband} = sort(reAoSolution{iSubband}{end}.powerAmplitude);
 		end
     catch
 		indexSet(indexSet == iBatch) = [];

### 2021-04-08 src/plot/plot_re_tx.m

@@ -32,8 +32,8 @@ hold all;
 for iTx = 1 : length(Variable.nTxs)
     plotHandle(1, iTx) = plot(reAoTx{iTx}(1, :) / nSubbands, 1e6 * reAoTx{iTx}(2, :));
     plotHandle(2, iTx) = plot(reLcTx{iTx}(1, :) / nSubbands, 1e6 * reLcTx{iTx}(2, :));
-	legendString{1, iTx} = sprintf('AO: $M = %d$', Variable.nTxs(iTx));
-	legendString{2, iTx} = sprintf('LC (PS): $M = %d$', Variable.nTxs(iTx));
+	legendString{1, iTx} = sprintf('BCD: $M = %d$', Variable.nTxs(iTx));
+	legendString{2, iTx} = sprintf('LC-BCD: $M = %d$', Variable.nTxs(iTx));
 end
 hold off;
 grid on;

### 2021-04-08 src/plot/plot_scaling_reflector.m

@@ -35,9 +35,9 @@ pathlossPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
 nexttile;
 plotHandle = plot(Variable.nReflectors, snrDb);
 grid on;
-legend('WF', 'location', 'nw');
+legend('WF', 'location', 'se');
 xlabel('Number of reflectors');
-ylabel('Per-subband SNR [dB]');
+ylabel('SNR [dB]');
 xlim([Variable.nReflectors(1), Variable.nReflectors(end)]);
 xticks(Variable.nReflectors(1 : 2 : end));
 box on;
@@ -52,7 +52,7 @@ plotHandle(2) = plot(Variable.nReflectors, mag2db(currentSmf));
 plotHandle(3) = plot(Variable.nReflectors, mag2db(currentSdr));
 hold off;
 grid on;
-legend('ASS', 'SMF', 'SDR', 'location', 'nw');
+legend('ASS', 'SMF', 'GP', 'location', 'se');
 xlabel('Number of reflectors');
 ylabel('Output DC current [dBA]');
 xlim([Variable.nReflectors(1), Variable.nReflectors(end)]);

### 2021-04-08 src/plot/plot_scaling_tx.m

@@ -35,9 +35,9 @@ pathlossPlot = tiledlayout(2, 1, 'tilespacing', 'compact');
 nexttile;
 plotHandle = plot(Variable.nTxs, snrDb);
 grid on;
-legend('WF', 'location', 'nw');
+legend('WF', 'location', 'se');
 xlabel('Number of transmit antennas');
-ylabel('Per-subband SNR [dB]');
+ylabel('SNR [dB]');
 xlim([Variable.nTxs(1), Variable.nTxs(end)]);
 xticks(Variable.nTxs([1, 2 : 2 : end]));
 box on;
@@ -52,7 +52,7 @@ plotHandle(2) = plot(Variable.nTxs, mag2db(currentSmf));
 plotHandle(3) = plot(Variable.nTxs, mag2db(currentSdr));
 hold off;
 grid on;
-legend('ASS', 'SMF', 'SDR', 'location', 'nw');
+legend('ASS', 'SMF', 'GP', 'location', 'se');
 xlabel('Number of transmit antennas');
 ylabel('Output DC current [dBA]');
 xlim([Variable.nTxs(1), Variable.nTxs(end)]);

### 2021-04-08 assets/waveform_subband.tex
:chart_with_upwards_trend: Update plots

--- 2020-09-21 assets/waveform_subband.tex
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,3.503in)},
+width=4.036in,
+height=0.481in,
+at={(0.677in,3.374in)},
 scale only axis,
@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black}
+legend style={legend cell align=left, align=left, draw=white!15!black},
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.82172700814\\
+1	2.82172701356454\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000304871216171409\\
+1	0.000255961727675924\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,2.747in)},
+width=4.036in,
+height=0.481in,
+at={(0.677in,2.645in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.576053130269644\\
-2	2.6890198112766\\
+1	0.19551151069007\\
+2	2.79441682266723\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.10889135894926e-05\\
-2	1.14015388220875e-05\\
+1	6.76001760054032e-06\\
+2	6.94107248595388e-06\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,1.992in)},
+width=4.036in,
+height=0.481in,
+at={(0.677in,1.916in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.0761446438182487\\
-2	0.144982805084864\\
-3	0.296816012849829\\
-4	1.29142363466971\\
+1	0.00471916738670986\\
+2	0.0113013795751173\\
+3	0.0524973569625421\\
+4	1.11631746294063\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.591539833353852\\
-2	0.844757166782542\\
-3	1.03081211044174\\
-4	1.37773181929967\\
+1	0.666856968017446\\
+2	0.826759550766013\\
+3	0.96159816303766\\
+4	1.2653467150935\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,1.237in)},
+width=4.036in,
+height=0.481in,
+at={(0.677in,1.187in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00614059608939126\\
-2	0.00859401448595302\\
-3	0.0123833441665029\\
-4	0.0177535370500449\\
-5	0.0248195484241391\\
-6	0.0333320835321464\\
-7	0.0439492095749763\\
-8	0.0573484061988145\\
+1	0.000872616544376037\\
+2	0.00117960004406015\\
+3	0.00161605407069224\\
+4	0.00228266132463128\\
+5	0.00326342365821\\
+6	0.00487936277124623\\
+7	0.00881039674196349\\
+8	0.0419634199055652\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.609821067440242\\
-2	0.776815349798277\\
-3	0.892920455239222\\
-4	1.00042966171483\\
-5	1.06766801836801\\
-6	1.12407480396652\\
-7	1.16166550988201\\
-8	1.18062831194278\\
+1	0.633590459263079\\
+2	0.785594177316295\\
+3	0.891389674009387\\
+4	0.98505471211105\\
+5	1.05090474986801\\
+6	1.10664902589546\\
+7	1.1412268011736\\
+8	1.16708811938208\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,0.481in)},
+width=4.036in,
+height=0.481in,
+at={(0.677in,0.458in)},
 scale only axis,
@@
 ymin=0,
+ytick={  0, 0.4, 0.8},
 axis background/.style={fill=white},
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00159254712768886\\
-2	0.00181872147522133\\
-3	0.00209479239275806\\
-4	0.0024296336516978\\
-5	0.00281222668015008\\
-6	0.0032780527552737\\
-7	0.00380135620921339\\
-8	0.00440085046230309\\
-9	0.00504657166225592\\
-10	0.00574247660897721\\
-11	0.00647282890112406\\
-12	0.00732475713633807\\
-13	0.0082485990892498\\
-14	0.00930209758929144\\
-15	0.0104899265041237\\
-16	0.0118432322249022\\
+1	0.000310341555926487\\
+2	0.00035799764238\\
+3	0.00041670813086453\\
+4	0.000484920116868764\\
+5	0.000569098471381299\\
+6	0.000669877208860123\\
+7	0.000793268903064817\\
+8	0.000939331113982085\\
+9	0.0011175247904389\\
+10	0.00132972829292326\\
+11	0.0015875351976808\\
+12	0.00189182501786478\\
+13	0.00226771472661325\\
+14	0.00272021545715682\\
+15	0.00331689397668614\\
+16	0.00407528165955271\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.42719183467558\\
-2	0.489608181929718\\
-3	0.544499613736105\\
-4	0.589949743468663\\
-5	0.629246929549485\\
-6	0.662163410085189\\
-7	0.692512510794905\\
-8	0.716054914758183\\
-9	0.740934812846251\\
-10	0.761383578308525\\
-11	0.780212428748497\\
-12	0.795813406680176\\
-13	0.808442539661251\\
-14	0.818197413331254\\
-15	0.824534054395175\\
-16	0.827852614702225\\
+1	0.428729933737136\\
+2	0.489701018897442\\
+3	0.539263608495876\\
+4	0.585347098517275\\
+5	0.624083102405944\\
+6	0.657759147074073\\
+7	0.689461005203993\\
+8	0.715900755845553\\
+9	0.741047135425173\\
+10	0.761923826165851\\
+11	0.78165448191713\\
+12	0.796874354752371\\
+13	0.810144534289869\\
+14	0.819572643230985\\
+15	0.826293720140692\\
+16	0.829491639456529\\
 };

### 2021-04-08 main.tex
:pencil: Update numerical proof

@@
 \usepackage{microtype}
+\usepackage{multirow}
 \usepackage{pgfplots}
@@
 In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through eigen decomposition.
+It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be obtained by eigen decomposition.
 In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
@@
 			\begin{proposition}\label{pr:bcd}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD algorithm is a local optimal point of the original problem~\eqref{op:original}.
+				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD Algorithm \ref{al:bcd} is a local optimal point of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 
-			Besides, minor modification is required for passive beamforming to cooperate with the low-complexity waveform schemes.
+			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
@@
 
-			Similar to Algorithm~\ref{al:bcd}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
-Similar to Proposition \ref{pr:bcd}, strict convergence and local optimality of the low-complexity BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
+			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
+Similar to Proposition~\ref{pr:bcd}, strict convergence and local optimality of the LC-BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
 		\end{subsection}
@@
 		\end{figure}
-		To evaluate the performance of the proposed IRS-aided SWIPT system, we suppose a layout as Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path.
+		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path.
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links.
@@
 CSCG random variables of unit average sum-power, corresponding to a normalized multipath response.
-Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}.
-For the algorithms, the tolerance is $\epsilon=10^{-8}$, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, and we assume $\delta=\rho$ for simplicity.
-All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis has been normalized to per-subband rate $R/N$.
+Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}.
+For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
+All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
-		We first provide numerical proof on the strict convergence and local optimality of the proposed BCD algorithms.
+		\begin{table*}[!t]
+			\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
+			\label{ta:eigen_ratio}
+			\centering
+			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+			\hline
+			\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
+			\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
+			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
+			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
+			\end{tabular}
+		\end{table*}
+
+		We first provide numerical proof on the strict convergence (thus local optimality) of both BCD algorithms.
 Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
-Table~ shows the minimum value of $\nu$ during both BCD algorithms for all tested channel realizations.
-
-		evaluate the rank of IRS matrix $\boldsymbol{\Phi}^\star$ obtained by Algorithm~\ref{al:sca} and \ref{al:lc}.
-
-		We first evaluate the performance of Algorithm~\ref{al:sca} under SDR.
-It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through eigen decomposition and the Gaussian randomization step is not required.
-Therefore, we claim Algorithm~\ref{al:sca} converges to stationary points of problem~\eqref{op:irs} without performance loss.
+$\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, and we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
+Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms.
+With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
+It suggests that the rank constraint \ref{co:irs_rank} can be dropped without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
 
@@
 			}
-			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
@@
 		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy.
-The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}.
+\textit{First}, it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
+The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, confirming the scaling laws in \cite{Clerckx2018b}.
 Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 			\centering
-			\begin{adjustbox}{width=0.9\columnwidth}
+			\subfloat[R-E region\label{fi:re_noise}]{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/re_noise.tex}
-			\end{adjustbox}
-			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
-			\label{fi:re_noise}
+				}
+			}
+			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/splitting_ratio_noise.tex}
+				}
+			}
+			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
 
-		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}.
-\textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level while approximately convex for a low noise level.
-Hence, it can be concluded that TS is preferred at low SNR while PS is preferred at high SNR.
-This is because in the former case, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands.
-As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity.
-\textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n^2 \le -40\,\si{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization.
-On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer.
-The result highlights the benefit of dedicated power waveform and the necessity of joint optimization of waveform and splitting ratio.
+		The influence of the average noise power on the R-E region is investigated in Fig.~\ref{fi:re_noise}.
+\textit{First}, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
+This is because the WF strategy tends to concentrate power on few strongest subbands at low SNR.
+As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the frequency compensation effect and harvester nonlinearity.
+\textit{Second}, there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
+The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy maximization.
+As $\bar{R}$ further decreases, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, owing to the high energy efficiency of multisine.
+The result highlights the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
 
@@
 			}
-			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
 		\end{figure}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
 		\end{figure}
@@
 			\centering
-			\subfloat[$B=1\,\si{\MHz}$\label{fi:re_irs_1mhz}]{
+			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\subfloat[$B=10\,\si{\MHz}$\label{fi:re_irs_10mhz}]{
+			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
+			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$).
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=\SI{1}{\MHz}$) and broadband transmission ($B=\SI{10}{\MHz}$).
 The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
@@
 To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
+
+			\begin{figure}[!t]
+				\centering
+				\subfloat[Quantized IRS\label{fi:re_quantization}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_quantization.tex}
+					}
+				}
+				\subfloat[Imperfect CSIT\label{fi:re_csi}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_csi.tex}
+					}
+				}
+				\caption{Average R-E region with quantized IRS and imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\end{figure}
 		\end{subsection}

### 2021-04-09 main.tex
:pencil: Update existing discussions

@@
 Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficients of each IRS element are the same at all subbands.
+In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
 That is to say, $\phi_l$ is shared by $M$ auxiliary channels over $N$ subbands.
+			\end{remark}
+
+			\begin{remark}\label{re:subband_tradeoff}
+				The cascaded channel response varies at different frequencies.
+Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary channel design in the frequency domain.
+Moreover, each IRS element simultaneously assists all transmit antennas such that the reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
 			\end{remark}
@@
 Similar to Proposition~\ref{pr:bcd}, strict convergence and local optimality of the LC-BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
+Details are omitted here for simplicity.
 		\end{subsection}
@@
 Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
-$\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, and we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
+Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
 Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms.
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \ref{co:irs_rank} can be dropped without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
+It suggests that the rank constraint \ref{co:irs_rank} can be relaxed without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
 
@@
 		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\textit{First}, it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
-The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, confirming the scaling laws in \cite{Clerckx2018b}.
-Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains.
-Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4).
-\textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
+\textit{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
+It is because each subband receives less power but more balanced DC terms are introduced to boost the harvested energy.
+On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
+It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+This observation origins from the rectifier nonlinearity.
+Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order DC terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials.
+Hence, the benefit of multisine outstands for a sufficiently large $N$.
+\textit{Second,} the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
@@
 a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
-Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on $N$.
+Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on the number of subbands.
 
@@
 
-		The influence of the average noise power on the R-E region is investigated in Fig.~\ref{fi:re_noise}.
-\textit{First}, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
-This is because the WF strategy tends to concentrate power on few strongest subbands at low SNR.
-As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the frequency compensation effect and harvester nonlinearity.
-\textit{Second}, there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy maximization.
-As $\bar{R}$ further decreases, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, owing to the high energy efficiency of multisine.
-The result highlights the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
+		The average noise power influences the R-E region as in Fig.~\ref{fi:re_noise}.
+\textit{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
+At low SNR, the power is allocated to the modulated waveform on few strongest subbands to achieve a high rate.
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency balancing and harvester nonlinearity.
+\textit{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
+The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy purpose.
+As $\bar{R}$ further decreases, due to the advantage of multisine, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$.
+The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
 
@@
 
-		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
-\textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission.
-This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength.
-\textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS).
-Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary.
-\textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only.
-For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power.
-Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
-On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$.
-An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$.
-As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$.
-Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective.
-These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design.
-\textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming.
-As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}.
-Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength.
-Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
+		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
+\textit{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer.
+Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are amplified that preserves the general trend of the R-E boundary.
+\textit{Second,} the passive beamforming has a larger array gain and power scaling order than the active beamforming.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for the linear harvester model \cite{Clerckx2016a}.
+For the MRT active precoder, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
+Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that validates the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
+On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB} that implies a reflect array gain of $L^2$.
+An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
+Hence, doubling IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
+Compared with active antennas, the IRS achieves higher array gain and power scaling order by passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} gap with SMF and GP.
+These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.
 
@@
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=\SI{1}{\MHz}$) and broadband transmission ($B=\SI{10}{\MHz}$).
-The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
+		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
+The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
+The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}.
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e.
+the boundary is obtained by varying the waveform amplitude and splitting ratio).
+\textit{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
+Their achievable R-E regions coincide because the antenna mode reflection of the random IRS is cancelled out after averaging over channel realizations.
+\textit{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes unobvious and the auxiliary channels can be roughly maximized at all subbands.
+It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in the closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP.
+On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain.
+By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
+
+		% The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
 To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS.
-In contrast to Remark~\ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for $NL$ variables in total.
-When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-UE channel to the AP-UE channel at all subbands, namely
-		\begin{equation}
-			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\mathrm{D},n}/h_{\mathrm{I},n,l}h_{\mathrm{R},n,l}\right)}},\quad \forall n,l.
-		\end{equation}
-		\textit{First}, it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
-\textit{Second}, the performance of all four IRS strategies coincide with each other for narrowband SWIPT.
+
+		% \textit{First,} it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
+		% performance of all four IRS strategies coincide with each other for narrowband SWIPT.
 It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region.
@@
 Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies.
-\textit{Third}, a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT.
+\textit{Third,} a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT.
 Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.

### 2021-04-11 assets/waveform_subband.tex
:bento: Update assets

--- 2020-10-28 assets/waveform_subband.tex
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,3.503in)},
+width=4.036in,
+height=0.485in,
+at={(0.677in,3.369in)},
 scale only axis,
@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black}
+legend style={legend cell align=left, align=left, draw=white!15!black},
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.82172700965795\\
+1	2.82172701256397\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000289213065829642\\
+1	0.000265479925168544\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,2.747in)},
+width=4.036in,
+height=0.485in,
+at={(0.677in,2.641in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.295470946033806\\
-2	2.78041553969328\\
+1	0.305941511463392\\
+2	2.76242712267536\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	6.88515292983531e-06\\
-2	7.11243494475005e-06\\
+1	6.71549962409912e-06\\
+2	6.78915225846286e-06\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,1.992in)},
+width=4.036in,
+height=0.485in,
+at={(0.677in,1.914in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00886602819700381\\
-2	0.0237787230194659\\
-3	0.108070855596065\\
-4	1.1713310546201\\
+1	0.007350356637722\\
+2	0.0147094858376509\\
+3	0.0590793778157153\\
+4	1.02788897323282\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.633626542983812\\
-2	0.829836144183102\\
-3	0.976226628588797\\
-4	1.35354289111746\\
+1	0.711002949351241\\
+2	0.867986174604486\\
+3	1.02417325240103\\
+4	1.34410968002342\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,1.237in)},
+width=4.036in,
+height=0.485in,
+at={(0.677in,1.186in)},
 scale only axis,
@@
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00167790645812327\\
-2	0.00228016548777977\\
-3	0.00318742185439004\\
-4	0.00462726511721075\\
-5	0.00716743728878421\\
-6	0.0129273763723776\\
-7	0.0308460700090715\\
-8	0.115533318647694\\
+1	0.00126526562881413\\
+2	0.00163389424667508\\
+3	0.00214228814037994\\
+4	0.00291473026101762\\
+5	0.00404484067642897\\
+6	0.00591327046970132\\
+7	0.0122792439934077\\
+8	0.0818816961284654\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.603245855871981\\
-2	0.755456602981771\\
-3	0.858512489463287\\
-4	0.953124795407537\\
-5	1.02704466315581\\
-6	1.08592420449446\\
-7	1.13090925633169\\
-8	1.18526539633296\\
+1	0.633029580480129\\
+2	0.771481626745736\\
+3	0.873536833990131\\
+4	0.968051760825038\\
+5	1.03324782087805\\
+6	1.09291316442134\\
+7	1.12974439643375\\
+8	1.17077692579217\\
 };
@@
 \begin{axis}[%
-width=4.521in,
-height=0.544in,
-at={(0.758in,0.481in)},
+width=4.036in,
+height=0.485in,
+at={(0.677in,0.458in)},
 scale only axis,
@@
 ymin=0,
+ytick={  0, 0.4, 0.8},
 axis background/.style={fill=white},
 xmajorgrids,
-ymajorgrids
+ymajorgrids,
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
 ]
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000617491691008369\\
-2	0.000717776254822589\\
-3	0.000835285279992789\\
-4	0.000979591082427033\\
-5	0.00115487030006212\\
-6	0.00136293515999463\\
-7	0.00161619354701616\\
-8	0.00191279748068678\\
-9	0.00227218304658774\\
-10	0.0026908090305821\\
-11	0.00319938829308565\\
-12	0.00381122202979217\\
-13	0.00474535479665619\\
-14	0.00756353464992525\\
-15	0.017474797658002\\
-16	0.0547436973724798\\
+1	0.000465023983221312\\
+2	0.00052438501576905\\
+3	0.000598178789998686\\
+4	0.000676629883061283\\
+5	0.000779645514114207\\
+6	0.000891058787067234\\
+7	0.00103482618212732\\
+8	0.00120004374054558\\
+9	0.00140039988214198\\
+10	0.00164300972889049\\
+11	0.00194088588142548\\
+12	0.00233328546477028\\
+13	0.00288323717596057\\
+14	0.0036883861713129\\
+15	0.00495722356981356\\
+16	0.00703735366203068\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.418853266349202\\
-2	0.478839773751748\\
-3	0.529812149718329\\
-4	0.573539152412764\\
-5	0.611663102441733\\
-6	0.642886720358442\\
-7	0.677359347479036\\
-8	0.701877932539796\\
-9	0.729554340449397\\
-10	0.748421821359951\\
-11	0.768367609874633\\
-12	0.782658242865203\\
-13	0.796571330906253\\
-14	0.806933582871612\\
-15	0.818312174451126\\
-16	0.833414484583038\\
+1	0.429987185652732\\
+2	0.486975650168299\\
+3	0.533174859894872\\
+4	0.576333984439071\\
+5	0.61391168211896\\
+6	0.648236185996695\\
+7	0.680465320861151\\
+8	0.708130047574106\\
+9	0.735885034607608\\
+10	0.758476599592402\\
+11	0.780983741629149\\
+12	0.797703057712941\\
+13	0.813882700419696\\
+14	0.824241120475894\\
+15	0.832517663389794\\
+16	0.8354347465423\\
 };

### 2021-04-11 main.tex
:pencil: Update discussions

@@
 To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
-		% \begin{remark}\label{re:irs_subchannel_alignment}
-		% 	As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem.
-Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands.
-In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
-		% \end{remark}
 
@@
 Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
+Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links.
 All channels are assumed NLoS with taps modelled as i.i.d.
@@
 For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
-All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 			\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
-			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
-			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
+			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
+			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
 			\end{tabular}
@@
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \ref{co:irs_rank} can be relaxed without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
+It suggests that the rank constraint \ref{co:irs_rank} can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
 
@@
 \textit{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
-It is because each subband receives less power but more balanced DC terms are introduced to boost the harvested energy.
+It is because less power is given to each subband but more balanced DC terms are introduced to boost the harvested energy.
 On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
@@
 This observation origins from the rectifier nonlinearity.
-Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order DC terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials.
+Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials.
 Hence, the benefit of multisine outstands for a sufficiently large $N$.
-\textit{Second,} the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$.
+\textit{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$.
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
-A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay with the optimal development location around the midpoint \cite{Li2017}, placing the IRS closer to either the transmitter or the receiver would further improve the R-E tradeoff.
-It origins from the product-distance path loss model that applies to finite-size element reflection.
-As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance.
-On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems.
-Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network.
-A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\mathrm{I}}\Lambda_R$.
-It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the UE.
+Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020}.
+Moreover, there exist two optimal IRS coordinates with $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
+It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
+Considering the passive characteristic of the IRS, chances are that it can be directly supported by the SWIPT network.
 
@@
 Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are amplified that preserves the general trend of the R-E boundary.
-\textit{Second,} the passive beamforming has a larger array gain and power scaling order than the active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for the linear harvester model \cite{Clerckx2016a}.
-For the MRT active precoder, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
+\textit{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
+For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
 Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that validates the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
@@
 Hence, doubling IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
-Compared with active antennas, the IRS achieves higher array gain and power scaling order by passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} gap with SMF and GP.
+Compared with active antennas, the IRS achieves higher array gain and power scaling order using passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap with SMF and GP.
 These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.
@@
 \textit{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes unobvious and the auxiliary channels can be roughly maximized at all subbands.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant and the auxiliary channels can be roughly maximized at all subbands.
 It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in the closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP.
@@
 By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
-
-		% The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively).
-To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS.
-
-		% \textit{First,} it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
-		% performance of all four IRS strategies coincide with each other for narrowband SWIPT.
-It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region.
-Therefore, for a given channel, we can fix the active and passive beamforming, and only adapt the waveform and splitting ratio to achieve different R-E performance.
-This is because when the bandwidth is small, all channels are approximately flat such that the optimal ideal reflection coefficients at all subbands are approximately the same.
-Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies.
-\textit{Third,} a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT.
-Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution.
-By adaptive passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power.
-The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.
-
-		\begin{subsection}{Imperfect CSIT}
-			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time.
-Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
-			\begin{equation}
-				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
-			\end{equation}
-			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
-Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$.
-% For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
-		\end{subsection}
-
-		\begin{subsection}{Quantized IRS}
-			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient.
-To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
+It shows the R-E advantage of adaptive passive beamforming via Algorithm~\ref{al:sca} for broadband SWIPT.
 
@@
 			\centering
+			\subfloat[Imperfect CSIT\label{fi:re_csi}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/re_csi.tex}
+				}
+			}
 			\subfloat[Quantized IRS\label{fi:re_quantization}]{
@@
 			}
-				\subfloat[Imperfect CSIT\label{fi:re_csi}]{
-					\resizebox{0.45\columnwidth}{!}{
-						\input{assets/re_csi.tex}
-					}
-				}
-				\caption{Average R-E region with quantized IRS and imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
-		\end{subsection}
+
+		We then explore the impact of imperfect cascaded CSIT and quantized IRS on the R-E performance.
+Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
+Consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
+		\begin{equation}
+			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+		\end{equation}
+		where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
+Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$.
+Note that the estimation at different subbands are independent but the subchannel responses are correlated.
+Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for different $L$.
+
+		Since the available reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
+Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e.
+two-state reflection) brings considerable R-E gain over the benchmark scheme, and the performance gap between $b=4$ and unquantized IRS is negligible.
 	\end{section}
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper proposes a novel IRS-aided multi-carrier downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
+		This paper proposes a novel IRS-aided multi-carrier MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
 We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the splitting ratio at the receiver to enlarge the achievable R-E region.

### 2021-04-12 main.tex
:pencil: Update introduction and conclusion

@@
 			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-			% Most existing mobile devices are powered by batteries that require frequent charging or replacement, which brings high maintenance cost and restricts the scale of networks.
-Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range.
-			Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band.
+Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic waves in the Radio-Frequency (RF) band.
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
@@
 
-			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at a specific frequency to mitigate signal attenuation.
+			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
 Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
@@
 It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the WSP because rank-deficient channels require less energy beams.
-However, the above papers only consider single-carrier transmission based on inaccurate linear energy harvester model.
+However, the above papers only consider single-carrier transmission based on an inaccurate linear energy harvester model.
 Motivated by this, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS in this paper.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
+We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
 
@@
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
-Numerical results demonstrate the strict convergence of the proposed BCD algorithm under various configurations.
+The IRS phase shift, active precoder and waveform amplitude are updated iteratively until convergence.
 
-			\emph{Third}, we introduce two low-complexity adaptive waveform design to avoid the exponential complexity of the GP algorithm.
+			\emph{Third}, we introduce two low-complexity adaptive waveform design in the closed form to avoid the exponential complexity of the GP algorithm.
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
+To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
+The performance of the low-complexity design is proved close to the BCD algorithm under different configurations.
 
 			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) Wireless Information Transfer (WIT) and WPT prefer different passive beamforming especially when the bandwidth is large.
-These observations demonstrate the advantage of the proposed IRS-aided SWIPT architecture and emphasize the importance of accounting harvester nonlinearity in the system design.
-
-			\emph{Fifth}, since the IRS is generally passive and with finite reflection states, we investigate the influence of imperfect CSIT and quantized IRS on overall R-E behavior.
-The adaptive algorithms are proved robust and effective under different channel estimation errors, and only ?
-quantization bits are required for each IRS element to provide a decent performance.
-% It suggests that the proposed waveform and beamforming design
+It is concluded that 1) the proposed BCD algorithm always converge to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider quasi-static block fading and assume the CSIT of AP-UE and AP-IRS-UE cascaded channels are given.
+We consider quasi-static block fading and assume the CSIT of AP-UE and AP-IRS-UE cascaded channels are known.
 The signals reflected by two or more times are omitted and the noise power is assumed too small to be harvested.
@@
 In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
-That is to say, $\phi_l$ is shared by $M$ auxiliary channels over $N$ subbands.
 			\end{remark}
@@
 			capture the contribution of modulated and multisine waveforms over all subbands.
-Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information purpose.
+Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
 		\end{subsection}
@@
 		\begin{subsection}{Transceiving Modes}
-			Consider TS and PS as two practical transceiving modes for SWIPT.
-TS relies on perfect clock synchronization, where the transmitter divides each slot into dedicated data session with length $1 - \eta$ and energy session with length $\eta$, then designs the waveform for WIT and WPT independently.
+			TS and PS are acknowledged as two practical transceiving modes for SWIPT.
+TS relies on perfect clock synchronization, where the transmitter divides each slot into dedicated data session with length $1 - \eta$ and energy session with length $\eta$, then designs the waveform for Wireless Information Transfer (WIT) and WPT independently.
 At the receiver, only information decoder or energy harvester is activated at a time.
 Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E segment from the WIT point to the WPT point.
-
 On the other hand, the PS waveform consists of modulated and multisine components, and the receiver splits the incoming signal into individual data stream with power ratio $1 - \rho$ and energy stream with power ratio $\rho$.
-Note that in PS the splitting ratio $\rho$ and the superposed waveform require a joint design, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
-Therefore, we focus on PS in the following context since TS can be regard as a special case (a time sharing between WIT and WPT).
+Note that in PS the splitting ratio $\rho$ and the superposed waveform require a joint optimization, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
+Therefore, we focus on PS in the following context as TS can be regard as a special case.
 		\end{subsection}
@@
 			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC current in the following context.
+With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper.
 It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
@@
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain on the nonlinear terms of the output DC current.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current.
 Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
@@
 			\end{align}
-			where $P$ is the average transmit power budget and \num{1/2} converts the peak value to the average value.
+			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of sine waves to the average value.
 		\end{subsection}
@@
 		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
+To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
+				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2.\label{eq:taylor_3}
 			\end{align}
@@
 
-			From the perspective of communications, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes rate \eqref{eq:R}.
+			From the perspective of communications, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
 From the perspective of energy harvesting, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
@@
 			where $\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}} \ge 0$, $\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update \cite{Clerckx2018b}, and a feasible choice at iteration $i$ is
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update, and a feasible choice at iteration $i$ is
 			\begin{align}
@@
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying $\eta$, $\delta$ and $\rho$.
+To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta,\rho$.
 Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.
@@
 			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
-Similar to Proposition~\ref{pr:bcd}, strict convergence and local optimality of the LC-BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
-Details are omitted here for simplicity.
+Similar to Proposition~\ref{pr:bcd}, strict convergence of the LC-BCD algorithm is guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}, and the details are omitted here for simplicity.
 		\end{subsection}
@@
 
-		We first provide numerical proof on the strict convergence (thus local optimality) of both BCD algorithms.
+		We first provide numerical proof on the strict convergence of both BCD algorithms.
 Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
 Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms.
+Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples for both BCD algorithms.
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \ref{co:irs_rank} can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.
+It suggests that the rank constraint \ref{co:irs_rank} can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that the BCD Algorithm~\ref{al:bcd} converges to local optimal points.
 
@@
 		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\textit{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
+\emph{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
 It is because less power is given to each subband but more balanced DC terms are introduced to boost the harvested energy.
@@
 Hence, the benefit of multisine outstands for a sufficiently large $N$.
-\textit{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$.
+\emph{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$.
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
@@
 		The average noise power influences the R-E region as in Fig.~\ref{fi:re_noise}.
-\textit{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
+\emph{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
 At low SNR, the power is allocated to the modulated waveform on few strongest subbands to achieve a high rate.
-As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency balancing and harvester nonlinearity.
-\textit{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency coupling and harvester nonlinearity.
+\emph{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
 The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy purpose.
@@
 Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020}.
-Moreover, there exist two optimal IRS coordinates with $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
+Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
 It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
@@
 		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
-\textit{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer.
-Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are amplified that preserves the general trend of the R-E boundary.
-\textit{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
+\emph{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer.
+Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are proportionally amplified to preserve the general trend of the R-E boundary.
+\emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
 For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
@@
 the boundary is obtained by varying the waveform amplitude and splitting ratio).
-\textit{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
+\emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
 Their achievable R-E regions coincide because the antenna mode reflection of the random IRS is cancelled out after averaging over channel realizations.
-\textit{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
+\emph{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant and the auxiliary channels can be roughly maximized at all subbands.
@@
 By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
-It shows the R-E advantage of adaptive passive beamforming via Algorithm~\ref{al:sca} for broadband SWIPT.
+It shows the R-E advantage of adaptive passive beamforming Algorithm~\ref{al:sca} for broadband SWIPT.
 
@@
 Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for different $L$.
-
-		Since the available reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
+On the other hand, since the practical reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
 Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e.
-two-state reflection) brings considerable R-E gain over the benchmark scheme, and the performance gap between $b=4$ and unquantized IRS is negligible.
+two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
 	\end{section}
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper proposes a novel IRS-aided multi-carrier MISO SWIPT system to enhance the rate and energy tradeoff of a single user.
-We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the splitting ratio at the receiver to enlarge the achievable R-E region.
-Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission for practical co-localized receiver architectures.
-Efficient algorithms based on the BCD, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations.
-We confirm that considering harvester nonlinearity, a dedicated power waveform is generally required to boost the R-E tradeoff.
-When developed near the transmitter, the IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range.
-Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects.
-Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the rate-dependent adaptive passive beamforming is beneficial for broadband transmission.
+		This paper investigated the single-user R-E tradeoff in a novel IRS-aided multi-carrier MISO SWIPT system.
+Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity and practical transceiving strategies to maximize the achievable R-E region.
+A three-stage BCD algorithm is proposed to solve the problem.
+In the first stage, the IRS phase shift is obtained by combining the SCA technique with an relax-then-extract step.
+In the second and third stages, the active precoder is derived in the closed form and the waveform amplitude is optimized by the reversed GP method.
+We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm with near-optimal performance.
+Numerical results prove the convergence of both BCD algorithms and reveal significant R-E gains by accounting harvester nonlinearity in the passive beamforming design.
+Compared with active antennas, IRS elements are limited to frequency-dependent reflection but are able to integrate coherent combining and equal gain transmission in a fully passive manner to further boost the array gain and power scaling order.
+However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.
 
-		The combination of IRS and SWIPT brings many possibilities and challenges.
-For example, how to optimize the waveform, active and passive beamforming in a multi-user SWIPT system?
-How can multiple IRS cooperate with each other to further benefit the R-E tradeoff?
-How to perform channel estimation without RF-chains at the IRS?
-How to design an IRS-aided SWIPT system for different multiple access techniques?
-How to develop SWIPT in new networks, such as cell-free massive Multiple-Input Multiple-Output (MIMO)?
-Can IRS operation be directly supported by SWIPT?
-Answers to these questions may bring a new wireless revolution.
+		One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
 	\end{section}

### 2021-04-13 main.tex
:pencil: Update manuscript

@@
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)})\nonumber\\
-					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
+					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
 					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
@@
 It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be obtained by eigen decomposition.
-In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
+In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a high-quality solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
 Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
@@
 To prove $\boldsymbol{\Phi}^{(i)}$ converges to stationary points, we notice that the SCA-based Algorithm~\ref{al:sca} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, Algorithm~\ref{al:sca} is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions.
+Therefore, Algorithm~\ref{al:sca} is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ of the original passive beamforming problem (i.e.
+maximize \eqref{eq:z_irs} s.t.
+\eqref{co:irs_rate} -- \eqref{co:irs_sd}) that satisfies the KKT conditions.
 			\end{proof}
@@
 
-			From the perspective of communications, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
-From the perspective of energy harvesting, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
 Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
@@
 			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity \cite{Chiang2005}.
-To facilitate practical SWIPT implementation, we propose two low-complexity waveform amplitude design by combining WF and SMF under TS and PS setups.
+To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
 The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
@@
 					\If{$\rho=0$}
-						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} w.r.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 					\Else
@@
 Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples for both BCD algorithms.
+Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over \num{20} R-E samples of \num{300} tested channel realizations for both BCD algorithms.
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
@@
 Note that the estimation at different subbands are independent but the subchannel responses are correlated.
-Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for different $L$.
+Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
 On the other hand, since the practical reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.

### 2021-04-13 response.tex
:pencil: Update response letter

@@
 
-\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage{adjustbox}
 \usepackage{amsfonts}
@@
 \usepackage{amsthm}
+\usepackage{cite}
 \usepackage{fullpage}
+\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{microtype}
+\usepackage{multirow}
 \usepackage{pdfpages}
+\usepackage{pgfplots}
 \usepackage{siunitx}
@@
 		\begin{response}
-			Thank you for pointing out the CSI acquisition issue in presence of IRS.
-To estimate the cascaded Tx-IRS-Rx link, practical protocols based on element-wise on/off switching [24], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} have been developed for specific networks.
-The proposed Algorithm 1 relies on such cascaded CSI (not individual Tx-IRS and IRS-Rx channels) at the transmitter (CSIT) and can be readily applied to the quantized CSIT case.
-However, the codebook design for SWIPT with harvester nonlinearity remains an open issue and one particular challenge is how to evolve from the information codebook to satisfy the power demand.
+			Thank you for pointing out the CSI acquisition issue regarding the cascaded AP-IRS-UE link.
+The proposed passive beamforming algorithms rely on such cascaded CSIT, and recent researches proposed element-wise on/off switching [25], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} techniques to solve this issue.
+Those references have been cited in the literature review.
+To address the reviewer' comments, we consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
+			\begin{equation}
+				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+			\end{equation}
+			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
+Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.
+
+			\begin{figure}[!h]
+				\centering
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/re_csi.tex}
+				}
+				\label{fi:re_csi}
+				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\end{figure}
+
 			\label{re:1.1}
@@
 		\begin{response}
-			We appreciate your suggestion on IRS-aided multi-user SWIPT and believe it would be very promising.
-To that end, we would first need to tackle the waveform and beamforming design for a multi-user SWIPT system without IRS.
-Note that in a multi-carrier network, each subcarrier only serves one information user at a time but may serve all energy user simultaneously (use the entire signal for energy purpose), and it involves an additional resource allocation problem that cannot be solved by the GP algorithm proposed in this paper.
+			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the reasons explained below.
 
-			To see the reason, recall that in the single-user scenario, the optimal information beamformer and power beamformer coincide at MRT (see Response \ref{pt:2.2} for details) and the optimal waveform is given by (25), which decouples the design in the spatial domain (beamforming) and frequency domain (power allocation $s_{\mathrm{I/P},n}^2$) to ensure the term involved in the sum rate (7) and DC components (10) -- (13) satisfy $\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I/P},n}=\lVert{\boldsymbol{h}_n}\rVert s_{\mathrm{I/P},n}$.
-Apparently, picking $s_{\mathrm{I/P}, n}$ as nonnegative real value would not only maximize (27) but also make (28) an amplitude optimization problem and enable GP tools.
+			First, it is important to remind the reviewer that the problem of joint waveform and beamforming design for a multi-user SWIPT system without IRS has never been studied in the literature.
+In other words, it would not make sense at this stage to address this multiuser IRS-aided SWIPT since the underlying building block of multiuser SWIPT is not known.
+Only once the problem of multiuser joint waveform and beamforming for multi-user SWIPT has been addressed, can we investigate the multiuser joint waveform and beamforming design for IRS-aided SWIPT.
+Those problems could be addressed in future research, but are not the scope of this paper.
 
-			However, this may not be the case in a multi-user scenario.
-At subband $n$, the composite channel is now $\boldsymbol{h}_{k, n}$ for user $k$ and the term above becomes $\boldsymbol{h}_{k, n}^H\boldsymbol{w}_{\mathrm{I/P},n}$.
-It is generally complex and require other approaches to solve the highly non-convex optimization problem in the complex field.
-Although the waveform and beamforming design for multi-user multi-carrier WPT has been investigated in [32], the extension to SWIPT is not straightforward as the power splitting ratio of all users also require a joint update and the SDR method cannot be applied directly.
+			Second, the emphasis is on single-user because we believe a proper understanding of the single-user case is crucial before jumping into multi-user scenarios.
+Our modeling of SWIPT is not "simple": not only we transmit both information and power, we deal with joint space and frequency optimization through a joint beamforming and waveform problem that is challenging due to the nonlinearity of the rectifier that induces coupling among frequencies components.
+This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction [31 -- 33].
+
+			Third, multi-user WPT leads to its own set of challenges compared single-user WPT.
+Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in [8, 36].
+Consequently, single-user and multi-user WPT are designed differently in [8, 36].
+Though the SWIPT case has not been studied, the same set of problems is expected to occur between single user and multiuser case and would be even more challenging since communication is delivered simultaneously with power.
+Adding IRS into the picture would make it even more complicated.
 			\label{re:1.2}
@@
 			Thank you for raising this issue.
-The rank-\num{1} property of $\boldsymbol{\Phi}$ to the relaxed problem (24) is suggested by CVX toolbox under different configurations.
-As indicated by the comment, the strict convergence of the AO algorithm relies on this conclusion (as $\boldsymbol{\phi}$ can be retrieved without performance loss), but it is intricate to provide a mathematical proof due to the coupled objective (24a) and the log sum constraint (24b).
-Instead, we considered \num{300} individual channel realizations for different $M$, $N$, $L$ and employed \num{30} samples (corresponding to \num{30} problems with different sum rate constraints) for each individual R-E region.
-The extensive numerical results show that the proposed SCA Algorithm 1 found a unit-rank solution $\boldsymbol{\Phi}$ for all channel realizations, at all rate constraints, and during all iterations.
-Therefore, the convergence and performance are guaranteed for all tested scenario, and we believe that Algorithm 1 can provide a feasible and reliable passive beamformer in general SWIPT systems.
+The rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$ to the relaxed problem (25a) -- (25d) is suggested by the CVX software [39] under different configurations.
+Although the strict convergence and local optimality of the BCD Algorithm~3 relies on this conclusion, it is intricate to provide a mathematical proof due to the coupled objective (24) and the log sum constraint (25b).
+Instead, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
+Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
+Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over \num{20} R-E samples of \num{300} tested channel realizations for both BCD algorithms.
+With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
+It suggests that the rank constraint (25e) can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~3 always hold such that the BCD Algorithm~3 converges to local optimal points.
 
-			[To add a CDF plot of max eigenvalue over sum eigenvalue, which is almost always 1. The simulation is still running.]
+			\begin{table*}[!h]
+				\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
+				\label{ta:eigen_ratio}
+				\centering
+				\resizebox{\columnwidth}{!}{
+					\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+						\hline
+						\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
+						\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
+						$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
+						$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
+					\end{tabular}
+				}
+			\end{table*}
+
 			\label{re:1.3}
@@
 		\begin{response}
-			We agree with the reviewer that the performance loss by relaxing the rank-one constraint deserves more attention.
-In \cite{Feng2021}, we investigated the joint waveform and beamforming design for multi-user multi-carrier WPT (with no information waveform and rate requirements) and formulated the WSE problem as complex constant-modulus QP, enabling an SDR with at least $\gamma = \pi / 4$ approximation to the original objective function.
-However, due to the reason mentioned in Response \ref{re:1.2}, we did not extend the work to multi-user SWIPT in this paper.
-
-			In contrast, the performance guarantee of rank relaxation in our single-user problem is simply demonstrated by simulation.
-Due to the coupling of the information and power waveform, the objective function (23) involves
-			\begin{equation}
-				(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2 = \left(\mathrm{Tr}(\boldsymbol{C}_{\mathrm{I},0}\boldsymbol{\Phi^{(i)}}) - \mathrm{Tr}(\boldsymbol{C}_{\mathrm{P},0}\boldsymbol{\Phi^{(i)}})\right)^2 = \mathrm{Tr}\left((\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi^{(i)}}\right)^2
-			\end{equation}
-			which consists of trace square and is not a semidefinite expression.
-Compared with standard SDP, problem (24) also introduces an additional log sum constraint (24b) for communication purpose, and the existing SDR bounds cannot be applied directly in this case.
+			We agree with the reviewer that the relaxation on the rank-one constraint deserves more attention.
+However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general ideas to address this issue.
+For any passive beamforming problem with unit-rank constraint (which is non-convex), we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint $\mathrm{rank}(\boldsymbol{\Phi})=1$ with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
+Both techniques are expected to provide a unit-rank solution with performance very close to the original solution.
 			\label{re:1.5}
@@
 		\begin{point}
-			New RIS models are now being adopted as in [23] where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+			New RIS models are now being adopted as in [24] where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
 			\label{pt:2.1}
@@
 		\begin{response}
-			Thank you for sharing this acknowledged paper.
+			Thank you for sharing this paper.
 It investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS.
-It also proposed an analytical IRS model together with an AO algorithm to maximize the achievable rate by passive beamforming.
+It also proposed an analytical IRS model together with an BCD algorithm to maximize the achievable rate by passive beamforming.
 Simulation results emphasized the importance of modeling such a relationship in practical IRS design.
-We actually thought about integrating these new models in our system design, but finally decided to use the most common and simplest IRS model in the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
+There exist various refined models of IRS in the literature, however, we have finally decided to use the most common and simplest IRS model at the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
 			\label{re:2.1}
@@
 		\begin{point}
-			Why is MRT considered as precoder by (25) rather than optimizing it? Is it globally optimal too?
+			Why is MRT considered as precoder by (27) rather than optimizing it? Is it globally optimal too?
 			\label{pt:2.2}
@@
 		\begin{response}
-			In the single-user scenario, MRT is the global optimal information and power precoder. We can decouple the waveform in the spatial and frequency domain by
-			\begin{equation}
-				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \bar{\boldsymbol{w}}_{\mathrm{I/P}, n}
+			In the single-user scenario, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
+			\begin{equation}\label{eq:w}
+				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
 			\end{equation}
-			where $s_{\mathrm{I/P},n}^2$ denote the power allocated to the information/power waveform at subband $n$, and $\bar{\boldsymbol{w}}_{\mathrm{I/P}, n}$ is the active beamformer at subband $n$.
-For simplicity, we define $s_{\mathrm{I/P}, n}$ as nonnegative real value (as the phase can be included in the beamformer).
-From the information perspective, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = s_{\mathrm{I}, n} \lvert{\boldsymbol{h}_{n}^H \bar{\boldsymbol{w}}_{\mathrm{I}, n}}\rvert$ thus maximizes the sum rate (7).
-From the energy perspective, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^*$ thus maximizes the second and fourth order DC terms (10) -- (13).
-Therefore, MRT is the global optimal information and power precoder.
-However, this is not the case for the multi-user scenario where the beamformer and power allocation require a joint optimization.
+			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the information/power precoder.
+The MRT precoder at subband $n$ is given by
+			\begin{equation}\label{eq:b}
+				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
+			\end{equation}
+
+			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate (8).
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms (11) -- (14).
+Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
+We have separated the active beamforming design from the waveform design in the revised manuscript to clarify this point.
 			\label{re:2.2}
@@
 			The reviewer is referred to Response \ref{re:1.1}.
-Indeed, the assumption of perfect CSIT is very ideal and the existing protocols may not provide a good enough estimation in practice.
-We follow the convention of most existing papers on this topic and expect some breakthroughs in the future research.
+Indeed, the assumption of perfect CSIT is very ideal and the existing channel estimation protocols may not provide decent results in practice.
+We have investigated the impact of CSIT estimation error of the cascaded AP-IRS-UE link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy.
 			\label{re:2.3}
@@
 		\begin{point}
-			All the assumptions and relaxations adopted used in the derivation of results as in (23) need to be explicitly mentioned along with appropriate justification for the same.
+			All the assumptions and relaxations adopted used in the derivation of results as in (24) need to be explicitly mentioned along with appropriate justification for the same.
 			\label{pt:2.4}
@@
 			We appreciate your suggestion and have revised the manuscript correspondingly.
-The original objective function (19) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (20) -- (22) to formulate SCA problems of the original passive beamforming problem, i.e.
-maximize (19) s.t.
-(24b) -- (24e).
-Specifically, the objective affine function (23) is obtained by plugging (20) -- (22) into (19) and it satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$.
+The original objective function (20) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (21) -- (23) to formulate SCA problems of the original passive beamforming problem (i.e.
+maximize (20) s.t.
+(25b) -- (25e)).
+The objective affine function (24) is obtained by plugging (21) -- (23) into (20).
+It satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$ such that solving (25) iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem.
 			\label{re:2.4}
@@
 		\begin{response}
-			Thank you for the reminder. All transformations are equivalent to their original form and we have make this clear in the revised manuscript.
+			Thank you for the reminder. All transformations are equivalent to their original form and we have mentioned this point explicitly in the revised manuscript.
 			\label{re:2.5}
@@
 		\begin{response}
-			Algorithm 1 -- 3 only provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
-For different sum rate constraints, we use water-filling with MRT to initialize the modulated waveform while use scaled matched filter to initialize the unmodulated waveform (corresponding to a total power of $2P$, regulated afterwards).
-The phase shift of each IRS element is initialized as i.i.d.
+			Algorithm~1 -- 4 only provide local optimal solutions with analytical/numerical local convergence proof, and the performance indeed depends on the initialization.
+For the passive beamforming Algorithm~1, we initialize the phase shift of all IRS elements as i.i.d.
 uniform random variables over $[0, 2\pi)$.
-Nevertheless, as the algorithms only converge to local optimal, few R-E points might be strictly worse (in terms of both rate and energy) than the others, especially when $M$ and $L$ are very large.
+For the waveform amplitude and splitting ratio Algorithm~2, we initialize the modulated waveform by the Water-Filling (WF) strategy (37) and the multisine waveform by the Scaled Matched Filter (SMF) scheme (38), and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$.
+These parameters are used for general initialization and regulated by the algorithm afterwards.
+However, as Algorithm~3 only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
 To address this issue, we draw the R-E boundary from the high-rate low-energy (lower right) points to the low-rate high-energy (upper left) points.
-If a point is strictly dominated, we discard the candidate, reinitialize the waveform and IRS phase shift by the solution at the previous point, then perform the optimization again.
-
-			For a tolerance of $\epsilon=10^{-8}$, the SDR-based Algorithm 1 usually converge within 2 iterations while the GP-based Algorithm 2 tends to converge within 8 iterations.
-The AO-based Algorithm 3 typically converge within 2 iterations.
-Unfortunately, the complexity analysis is very challenging as problem (24) and (32) are both in intricate form.
+If a point is strictly dominated, we discard the candidate, reinitialize Algorithm~3 by the solution at the previous point, then perform the optimization again.
+For a tolerance of $\epsilon=10^{-8}$, Algorithm~1 -- 4 typically converge within 2, 7, 2, 2 iterations, respectively.
 			\label{re:2.6}
@@
 		\begin{response}
-			We agree that the proposed algorithm (especially Algorithm 2) could be very time-consuming for applications with short coherence time.
-The proposed algorithms ensure optimal performance by iteratively solving intricate optimization problems.
-Although the effectiveness of suboptimal design in closed form (e.g.
-scaled matched filter) has been validated in practical WPT systems, the extension to SWIPT is much more challenging because both waveforms and the splitting ratio need to be balanced under the influence of SNR.
+			Problem (25) is not a Semidefinite Programming (SDP) due to the $(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2$ term in (24).
+Hence, existing complexity analysis tools cannot be direct applied to Algorithm~1 and 4.
+For Algorithm~2, the computational complexity scales exponentially with the number of subbands [36, 43], but an analytical expression cannot be derived on top of relevant literatures.
+To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
+The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
+			\begin{equation}\label{eq:wf}
+				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+			\end{equation}
+			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+The closed-form solution can be obtained by iterative power allocation [45] and the details are omitted here.
+On the other hand, SMF was proposed in [12] as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
+			\begin{equation}\label{eq:smf}
+				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
+			\end{equation}
+			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
+In the low-complexity TS waveform design, modulated waveform \eqref{eq:wf} is used in the data session while multisine waveform \eqref{eq:smf} is used in the energy session.
+In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and the amplitude of modulated and multisine components are given by
+			\begin{align}
+				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
+			\end{align}
+			Fig.~\ref{fi:re_noise} -- \ref{fi:re_reflector} demonstrate that the low-complexity BCD algorithm achieves near-optimal performance under different configurations.
+
+			\begin{figure}[!h]
+				\centering
+				\subfloat[Average noise power\label{fi:re_noise}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_noise.tex}
+					}
+				}
+				\subfloat[AP-IRS horizontal distance\label{fi:re_distance}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_distance.tex}
+					}
+				}
+				\\
+				\subfloat[Transmit antennas\label{fi:re_tx}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_tx.tex}
+					}
+				}
+				\subfloat[Reflecting elements\label{fi:re_reflector}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/re_reflector.tex}
+					}
+				}
+				\caption{Average achievable R-E region under different configurations.}
+			\end{figure}
 			\label{re:2.7}

### 2021-04-13 letter.tex
:pencil: Update response letter

@@
 The manuscript has been revised carefully based on your valuable comments and suggestions.
-In particular, we attempted to clarify the motivations and contributions of this work.
+In particular, we clarified the motivations and contributions of this work, added two low-complexity designs with near-optimal rate-energy performance, and considered the cases of imperfect cascaded CSIT and finite IRS reflection states.
 To answer the questions and concerns, we include a point-to-point response below, which also describes all modifications made to the manuscript.

### 2021-04-14 main.tex
:pencil: Update manuscript

@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+			Both SWIPT and IRS aim to achieve spectrum and energy efficient transmission, and the effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
@@
 		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
-Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020}.
+Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
 Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.

### 2021-04-14 response.tex
:pencil: Update response letter

@@
 Those references have been cited in the literature review.
-To address the reviewer' comments, we consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
+To address the comment, we consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
 			\begin{equation}
@@
 				}
+				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 				\label{fi:re_csi}
-				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 			\end{figure}
@@
 
-			First, it is important to remind the reviewer that the problem of joint waveform and beamforming design for a multi-user SWIPT system without IRS has never been studied in the literature.
+			\emph{First}, it is important to remind the reviewer that the problem of joint waveform and beamforming design for a multi-user SWIPT system without IRS has never been studied in the literature.
 In other words, it would not make sense at this stage to address this multiuser IRS-aided SWIPT since the underlying building block of multiuser SWIPT is not known.
@@
 
-			Second, the emphasis is on single-user because we believe a proper understanding of the single-user case is crucial before jumping into multi-user scenarios.
+			\emph{Second}, the emphasis is on single-user because we believe a proper understanding of the single-user case is crucial before jumping into multi-user scenarios.
 Our modeling of SWIPT is not "simple": not only we transmit both information and power, we deal with joint space and frequency optimization through a joint beamforming and waveform problem that is challenging due to the nonlinearity of the rectifier that induces coupling among frequencies components.
@@
 
-			Third, multi-user WPT leads to its own set of challenges compared single-user WPT.
+			\emph{Third}, multi-user WPT leads to its own set of challenges compared single-user WPT.
 Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in [8, 36].
@@
 		\begin{response}
-			Green's decomposition suggests that the backscattered/reflected signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
-The reflection coefficient of the $l$-th IRS element is thus defined as
-			\begin{equation}
-				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0}
-			\end{equation}
-			where $Z_0$ is the characteristic impedance and $Z_l = R_l + j X_l$ is the impedance of the $l$-th IRS element.
-It implies that $\lvert{\phi_l}\rvert \le 1$ for $R_l \ge 0$, and we assume $Z_l$ is pure reactive such that
-			\begin{equation}
-				\phi_l = \frac{j X_l - Z_0}{j X_l + Z_0} = e^{j \theta_{l}}
-			\end{equation}
-			which corresponds to the lossless reflection model adopted in the paper.
-Nevertheless, due to the non-zero power consumption at the IRS in practice, $R_l$ would be positive and the reflection coefficient $\phi_l$ not only has a magnitude smaller than 1 but also depends on the phase shift.
-[23] found that $\lvert{\phi}_l\rvert$ experiences a trough as low as \num{0.2} for $R_l = 2.5\,\si{\ohm}$ at zero phase shift, which suggests that the position and direction of the IRS should be carefully designed.
+			The assumption of lossless reflection is indeed very ideal.
+Based on the circuit analysis, the authors of [24] shows that the reflection amplitude depends on the phase shift, which experiences a trough at \num{0} phase shift and is negatively correlated to the element resistance.
+For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} at a phase shift of $\pi$ but around \num{0.6} at a phase shift of \num{0}.
+From the perspective of field and propagation, \cite{Ozdogan2020} points out that if the dimension of IRS element is much larger than the wavelength, the beamwidth would become small and the scattered field strength would depend on the observation angle.
+However, to reduce the design complexity and provide a preliminary insight, we considered the commonest lossless reflection pattern at the IRS in this paper.
 			\label{re:2.8}
@@
 			We appreciate your suggestion and have modified the manuscript to emphasize this point.
-A major challenge for SWIPT is that the information decoder and energy harvester have different sensitivity -- although conventional radios as Wi-Fi and Bluetooth can support a signal strength of \num{-90} to \SI{-100}{\dBm}, most existing harvesters only capture signals at \num{-20} to \SI{-30}{\dBm}.
-Since the transmit power is strictly subject to regulations, it is crucial to increase the energy efficiency to boost the signal strength and extend the system coverage.
-Therefore, we believe the effective channel enhancement and the low power consumption of IRS is a perfect match for SWIPT.
+Both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal.
+Although conventional radios as Wi-Fi and Bluetooth can support a signal strength of \num{-90} to \SI{-100}{\dBm}, most existing harvesters can only capture signals at \num{-20} to \SI{-30}{\dBm} power level.
+Since the transmit power is strictly constrained by government regulations, it is crucial to increase the end-to-end power transfer efficiency to boost the harvested power and extend the system coverage.
+Therefore, we believe the passive beamforming ability of the IRS can significantly enhance WPT and SWIPT performance.
 			\label{re:3.1}
@@
 		\begin{response}
-			Thank you for the opinion and the manuscript has been revised accordingly.
-This paper proposed an IRS-aided SWIPT network and considered a joint waveform and beamforming design over spatial and frequency domains under energy harvester nonlinearity.
-To the best of our knowledge, relevant existing papers assumed linear harvester model where the RF-to-DC conversion efficiency is a constant regardless of its input.
-However, the harvester consists of an antenna to intercept RF signal and a diode rectifier (nonlinear device) to produce DC power, and the RF-to-DC efficiency indeed depends on the power and shape of the input waveform.
-By exploiting the joint impact of passive beamforming and harvester nonlinearity, we found that:
-			\begin{itemize}
-				\item the IRS should be developed next to the transmitter or the receiver due to double fading;
-				\item the optimal transceiving mode depends on the SNR and the number of subbands;
-				\item the power scaling laws of active and passive beamforming are in the order of $M^2$ and $L^4$, respectively;
-				\item the IRS reflection coefficient cannot be designed per subband and there exists a tradeoff in subchannel enhancement;
-				\item the optimal passive beamforming can be approximated in closed form for narrowband transmission but varies at different R-E points for broadband transmission.
-			\end{itemize}
+			We have resummarized the contribution of this paper as follows.
+
+			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
+To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
+The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+This is the first paper to tackle energy harvester nonlinearity, multi-carrier transmission, and co-localized receiver for IRS-aided SWIPT.
+
+			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relax-then-extract method.
+Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
+The IRS phase shift, active precoder and waveform amplitude are updated iteratively until convergence.
+
+			\emph{Third}, we introduce two low-complexity adaptive waveform design in the closed form to avoid the exponential complexity of the GP algorithm.
+The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
+To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
+The performance of the low-complexity design is proved close to the BCD algorithm under different configurations.
+
+			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
+It is concluded that 1) the proposed BCD algorithm always converge to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}
@@
 		\begin{response}
-			TODO
+			We have updated the discussion carefully and the reviewer is referred to the updated manuscript.
 			\label{re:3.3}
@@
 		\begin{response}
-			The reviewer is referred to Response \ref{re:1.1}. We have incorporated the channel estimation issue into the revised manuscript by citing those references.
+			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance. The reviewer is referred to Response \ref{re:1.1} for details.
 			\label{re:3.4}
@@
 		\begin{response}
-			TODO
+			Thank you for the suggestion.
+On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD algorithm.
+Fig.~\ref{fi:re_noise} -- \ref{fi:re_reflector} demonstrate that the low-complexity BCD algorithm achieves near-optimal performance under different configurations.
+Moreover, we have investigated the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization}.
+It can be concluded that the proposed algorithms are robust to CSIT inaccuracy of the AP-IRS-UE link, and even $b=1$ (i.e.
+two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS.
+These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
+
+			\begin{figure}[!h]
+				\centering
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/re_quantization.tex}
+				}
+				\caption{Average R-E region with quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\label{fi:re_quantization}
+			\end{figure}
 			\label{re:3.5}

### 2021-04-15 response.tex
:pencil: Update response letter

@@
 The rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$ to the relaxed problem (25a) -- (25d) is suggested by the CVX software [39] under different configurations.
-Although the strict convergence and local optimality of the BCD Algorithm~3 relies on this conclusion, it is intricate to provide a mathematical proof due to the coupled objective (24) and the log sum constraint (25b).
+Although the local optimality of the BCD Algorithm~3 relies on this conclusion, it is intricate to provide a mathematical proof due to the coupled objective (24) and the log sum constraint (25b).
 Instead, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
 Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over \num{20} R-E samples of \num{300} tested channel realizations for both BCD algorithms.
+For all intermediate $\boldsymbol{\Phi}$ achieved by Algorithm~1, Table~1 shows the maximum value of $1-\nu$ of \num{20} R-E samples over \num{300} tested channel realizations for both BCD algorithms.
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint (25e) can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~3 always hold such that the BCD Algorithm~3 converges to local optimal points.
+It suggests that the rank constraint (25e) can be relaxed, the phase shift $\boldsymbol{\phi}$ can be extracted by eigen decomposition without performance loss, and Algorithm~1, 3 and 4 converge to local optimal points.
 
 			\begin{table*}[!h]
-				\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
+				\caption{The maximum value of $1-\nu$ of all R-E samples over all tested channel realizations for BCD and LC-BCD algorithms}
 				\label{ta:eigen_ratio}
@@
 						$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
-						$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
+						$[\times \num{e-16}]$ & LC-BCD & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
 					\end{tabular}
@@
 			We agree with the reviewer that the relaxation on the rank-one constraint deserves more attention.
-However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general ideas to address this issue.
-For any passive beamforming problem with unit-rank constraint (which is non-convex), we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint $\mathrm{rank}(\boldsymbol{\Phi})=1$ with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
+However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general approaches to address this issue.
+For any passive beamforming problem with unit-rank constraint (which is non-convex), we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
 Both techniques are expected to provide a unit-rank solution with performance very close to the original solution.
@@
 		\begin{response}
-			Problem (25) is not a Semidefinite Programming (SDP) due to the $(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2$ term in (24).
+			Problem (25) is not a Semidefinite Programming (SDP) due to the squared term in the objective function.
 Hence, existing complexity analysis tools cannot be direct applied to Algorithm~1 and 4.
@@
 			We appreciate your suggestion and have modified the manuscript to emphasize this point.
-Both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+Both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal.
@@
 		\begin{response}
-			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance. The reviewer is referred to Response \ref{re:1.1} for details.
+			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance.
+The reviewer is referred to Response \ref{re:1.1} for details.
+Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.
 			\label{re:3.4}

### 2021-04-15 main.tex
:pencil: Update manuscript

@@
 Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
-Since the computational complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation.
+This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
+Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation.
 Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
@@
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The upsurge in the number of wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
+The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
 
             The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e.
-Time Switching (TS) and Power Splitting (PS).
+\cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2013} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency of rectifiers depends on the input power and waveform shape.
-It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
+On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
+It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
 Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT.
@@
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g.
-modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
+The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
 Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
@@
 			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e.
-passive beamforming).
-Different from relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, IRS adaptively assists the primary transmission by passive components to suppress thermal noise but is limited to frequency-dependent reflection.
+In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming).
+Different from the relay, backscatter, and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.
 
@@
 In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} have been proposed.
-\cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
+To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			Both SWIPT and IRS aim to achieve spectrum and energy efficient transmission, and the effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT.
-For a multi-user IRS-aided SWIPT system, dedicated energy beams are proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the WSP because rank-deficient channels require less energy beams.
-However, the above papers only consider single-carrier transmission based on an inaccurate linear energy harvester model.
+			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams.
+However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model.
 Motivated by this, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS in this paper.
@@
 To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
-The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
 This is the first paper to tackle energy harvester nonlinearity, multi-carrier transmission, and co-localized receiver for IRS-aided SWIPT.
 
-			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relax-then-extract method.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder and waveform amplitude are updated iteratively until convergence.
+The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
 
-			\emph{Third}, we introduce two low-complexity adaptive waveform design in the closed form to avoid the exponential complexity of the GP algorithm.
+			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
 To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
-The performance of the low-complexity design is proved close to the BCD algorithm under different configurations.
+The performances of both low-complexity designs are proved close to the BCD algorithm under different configurations.
 
 			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
-It is concluded that 1) the proposed BCD algorithm always converge to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) the proposed BCD algorithm always converges to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
 
-			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving mode and rectifier nonlinearity.
+			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving modes, rectifier nonlinearity and R-E tradeoff.
 Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization.
-Section~\ref{se:performance_evaluation} presents the simulation results and evaluates the proposed algorithms.
+Section~\ref{se:performance_evaluation} evaluates the proposed algorithms by simulation results.
 Section~\ref{se:conclusion_and_future_works} concludes the paper.
 
-			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case and bold upper-case letters.
+			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
 $j$ denotes the imaginary unit.
@@
 $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm operators.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{Tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote the argument, rank, trace, and a square matrix with input elements on the main diagonal.
+$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
+$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote respectively the argument, rank, trace, and a square matrix with input elements on the main diagonal.
 $\boldsymbol{S} \succeq 0$ means $\boldsymbol{S}$ is positive semi-definite.
@@
 The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-$\sim$ means "distributed as".
+$\sim$ means ``distributed as''.
 $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider quasi-static block fading and assume the CSIT of AP-UE and AP-IRS-UE cascaded channels are known.
-The signals reflected by two or more times are omitted and the noise power is assumed too small to be harvested.
+We consider a quasi-static block fading model and assume the CSIT of AP-UE direct channel and AP-IRS-UE cascaded channel are known.
+The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
 
@@
 The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
-IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ in a fully passive manner to reflect the incoming signal, and the reflection coefficient is defined as
+IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
 			\begin{equation}
@@
 			\end{equation}
-			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude, and $\theta_l \in [0,2\pi)$ is the phase shift~\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and depends on $\theta_l$.
-This paper sticks to the commonest and simplest IRS model where the reflection coefficient is assumed unit.}.
+			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude~\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
+This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
 We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
@@
 
-			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel response varies at different frequencies.
-Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary channel design in the frequency domain.
-Moreover, each IRS element simultaneously assists all transmit antennas such that the reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
-			\end{remark}
-
-			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary link provided by the IRS can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
+			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
 Hence, the composite equivalent channel reduces to
@@
 			where we define the cascaded AP-IRS-UE channel (without IRS reflection) as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+
+			\begin{remark}\label{re:subband_tradeoff}
+				The cascaded channel response varies at different frequencies.
+Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary channel control in the frequency domain.
+Moreover, each IRS element simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
+			\end{remark}
 		\end{subsection}
@@
 		\begin{subsection}{Transceiving Modes}
-			TS and PS are acknowledged as two practical transceiving modes for SWIPT.
-TS relies on perfect clock synchronization, where the transmitter divides each slot into dedicated data session with length $1 - \eta$ and energy session with length $\eta$, then designs the waveform for Wireless Information Transfer (WIT) and WPT independently.
-At the receiver, only information decoder or energy harvester is activated at a time.
-Varying $\eta$ from \num{0} to \num{1} corresponds to a R-E segment from the WIT point to the WPT point.
-On the other hand, the PS waveform consists of modulated and multisine components, and the receiver splits the incoming signal into individual data stream with power ratio $1 - \rho$ and energy stream with power ratio $\rho$.
-Note that in PS the splitting ratio $\rho$ and the superposed waveform require a joint optimization, but in TS the duration ratio $\eta$ is irrelevant to the waveform design in both sessions.
-Therefore, we focus on PS in the following context as TS can be regard as a special case.
+			TS and PS were proposed in \cite{Zhou2013} as two practical transceiving modes for co-located SWIPT.
+TS heavily relies on clock synchronization.
+The transmitter divides each slot into a data session with length $1 - \eta$ and an energy session with length $\eta$, then designs the waveform for Wireless Information Transfer (WIT) and WPT independently.
+At the receiver, only the information decoder or energy harvester is activated in the corresponding session.
+Varying $\eta$ from \num{0} to \num{1} draws a R-E segment from the WIT point to the WPT point.
+On the other hand, the PS waveform consists of modulated and multisine components, and the receiver splits the incoming signal into an individual data stream with power ratio $1 - \rho$ and an energy stream with power ratio $\rho$.
+Note that the splitting ratio $\rho$ and the superposed waveform require a joint optimization for PS, but the duration ratio $\eta$ is irrelevant to the waveform design in both sessions for TS.
+Therefore, we focus on PS in the following context as TS can be regarded as a time sharing between $\rho=0$ (WIT) and $\rho=1$ (WPT).
 		\end{subsection}
@@
 			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received signal.
-Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an impedance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
-Let $R_{\mathrm{in}}$ be the total input impedance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
-When perfectly matched ($R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
+Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
+Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
+When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
 
-			Rectifiers consist of nonlinear components as diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
+			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
 Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2016a,Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the non-linear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
@@
 
-		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
+		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
+To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
+				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
 			\end{align}
@@
 				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
+				& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+				& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
 			\end{align}
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce to
+On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
 			\begin{align}
 				R(\boldsymbol{\Phi})
-				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
+				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
 				z(\boldsymbol{\Phi})
@@
 
-			To maximize the non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm and lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 
-			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee.
+			Since \eqref{eq:z_irs_approx} is not an affine, problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee.
 In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
@@
 In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a high-quality solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
-Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution.
+Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}_{q^{\star}}$ that maximizes \eqref{ob:irs} as the solution.
 Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
-Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}.
 The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
@@
 			\begin{proposition}\label{pr:sca}
-				For any feasible initial point, the proposed SCA Algorithm~\ref{al:sca} can provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions, although there is no guarantee $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+				For any feasible initial point, the SCA Algorithm~\ref{al:sca} can provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions of the relaxed passive beamforming problem (i.e., maximize \eqref{eq:z_irs} s.t.
+\eqref{co:irs_rate} -- \eqref{co:irs_sd}).
+If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, then the extracted phase shift vector $\boldsymbol{\phi}^{\star}$ is local optimal to the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:sca}
-				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution of problem~\eqref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$.
-Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \ref{ob:irs} -- \ref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
+Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-To prove $\boldsymbol{\Phi}^{(i)}$ converges to stationary points, we notice that the SCA-based Algorithm~\ref{al:sca} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, Algorithm~\ref{al:sca} is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ of the original passive beamforming problem (i.e.
-maximize \eqref{eq:z_irs} s.t.
-\eqref{co:irs_rate} -- \eqref{co:irs_sd}) that satisfies the KKT conditions.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
+If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, then $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
 			\end{proof}
@@
 		\begin{subsection}{Active Beamforming}
-			In the single-user scenario, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
+			For single-user SWIPT, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
 			\begin{equation}\label{eq:w}
@@
 			\end{equation}
-			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the information/power precoder.
+			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
 Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$ and $\boldsymbol{b}_{\mathrm{I/P}} \triangleq [\boldsymbol{b}_{\mathrm{I/P}, 1}^T,\dots,\boldsymbol{b}_{\mathrm{I/P}, N}^T]^T \in \mathbb{C}^{MN \times 1}$ for simplicity.
@@
 From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
-Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
+Hence, MRT is the global optimal active precoder and no dedicated energy beams are required for single-user SWIPT.
 		\end{subsection}
@@
 On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
-Hence, rate \eqref{eq:R} reduces to
+Hence, the rate \eqref{eq:R} reduces to
 			\begin{equation}\label{eq:R_waveform}
@@
 			\end{equation}
-			and DC current \eqref{eq:z_expand} reduces to \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+			and the DC current \eqref{eq:z_expand} reduces to \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
@@
 
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform it into a reversed GP
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\ref{op:waveform} into a reversed GP
 			\begin{mini!}
@@
 			where $m_\mathrm{P}=(2N^3+6N^2+7N)/3$ and $m_{\mathrm{I},n}=2$.
-We then upper bound \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+We upper bound \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 			\begin{mini!}
@@
 			where $\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}} \ge 0$, $\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that require successive update, and a feasible choice at iteration $i$ is
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that needs successive update, and a feasible choice at iteration $i$ is
 			\begin{align}
@@
 			$\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho$ are updated iteratively until convergence.
-Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2013}.
+Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
 The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:gp}.
@@
 			\begin{proposition}\label{pr:gp}
-				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to a local optimal point of the waveform amplitude and splitting ratio problem \eqref{op:waveform}.
+				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
 			\end{proposition}
@@
 		\begin{subsection}{Block Coordinate Descent}
-			Based on the CSIT of direct and cascaded channels, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
 The BCD algorithm is summarized in Algorithm~\ref{al:bcd}.
@@
 						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ based on $\boldsymbol{h}_n^{(i)}$, $\forall n$ by Algorithm~\ref{al:gp}
+						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ based on $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by Algorithm~\ref{al:gp}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
@@
 			\begin{proposition}\label{pr:bcd}
-				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD Algorithm \ref{al:bcd} is a local optimal point of the original problem~\eqref{op:original}.
+				Suppose the $\boldsymbol{\Phi}$ obtained from Algorithm~\ref{al:sca} is rank-\num{1}, the limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD Algorithm \ref{al:bcd} is local optimal to the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:bcd}
-				The objective function \eqref{ob:original} is non-decreasing over iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then $\boldsymbol{\phi}$ can be extracted without performance loss and strict convergence of Algorithm~\ref{al:bcd} is guaranteed.
-As demonstrated in \cite{Grippo2000}, the limit point obtained by alternatively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P}}$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via BCD is a local optimal solution of problem~\eqref{op:original}.
+				The objective function \eqref{ob:original} is non-decreasing over the iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
+If $\boldsymbol{\Phi}$ is rank-\num{1}, then by Proposition~\ref{pr:sca}, the corresponding phase shift vector $\boldsymbol{\phi}$ is local optimal to the original problem \ref{op:original}.
+Since the active precoder by \eqref{eq:b} is global optimal and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P}}$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
 			\end{proof}
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity \cite{Chiang2005}.
-To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
+			The GP Algorithm~\ref{al:gp} achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF under TS and PS setups.
 The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
@@
 			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation \cite{Tse2005} and the details are omitted here.
+The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
 On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
@@
 			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-In the low-complexity TS waveform design, modulated waveform \eqref{eq:wf} is used in the data session while multisine waveform \eqref{eq:smf} is used in the energy session.
-In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and the amplitude of modulated and multisine components are given by
+In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session, while multisine amplitude \eqref{eq:smf} is used in the energy session.
+In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
 			\begin{align}
@@
 
-			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
+			Besides, minor modifications are required for passive beamforming to cooperate with both low-complexity waveform schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta,\rho$.
-Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.
+To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
+Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup, and its local optimality is guaranteed if $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
 
@@
 							\State $i \gets i + 1$
-								\State Set $\bar{R}=0$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \ref{co:irs_sd}
 								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 
-			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
-Similar to Proposition~\ref{pr:bcd}, strict convergence of the LC-BCD algorithm is guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}, and the details are omitted here for simplicity.
+			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
 		\end{subsection}
@@
 		\end{figure}
-		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path.
+		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links.
@@
 Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}.
+The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}.
 For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
@@
 		\begin{table*}[!t]
-			\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
+			\caption{The maximum value of $1-\nu$ of all R-E samples over all tested channel realizations for BCD and LC-BCD algorithms}
 			\label{ta:eigen_ratio}
@@
 				$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
-				$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
+				$[\times \num{e-16}]$ & LC-BCD & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
 			\end{tabular}
@@
 
-		We first provide numerical proof on the strict convergence of both BCD algorithms.
-Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
+		We first provide numerical proof on the rank-\num{1} property of $\boldsymbol{\Phi}$ thus the local optimality of Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc}.
+To see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
 Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over \num{20} R-E samples of \num{300} tested channel realizations for both BCD algorithms.
+For all intermediate $\boldsymbol{\Phi}$ achieved by Algorithm~\ref{al:sca}, Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ of \num{20} R-E samples over \num{300} tested channel realizations for both BCD algorithms.
 With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \ref{co:irs_rank} can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that the BCD Algorithm~\ref{al:bcd} converges to local optimal points.
+It suggests that the rank constraint \ref{co:irs_rank} can be relaxed, the phase shift $\boldsymbol{\phi}$ can be extracted by eigen decomposition without performance loss, and Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc} converge to local optimal points.
 
@@
 		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\emph{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy.
-It is because less power is given to each subband but more balanced DC terms are introduced to boost the harvested energy.
+\emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy.
 On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
@@
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e.
-a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
-Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on the number of subbands.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
+Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depend on the number of subbands.
 
@@
 \emph{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy purpose.
-As $\bar{R}$ further decreases, due to the advantage of multisine, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$.
+The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
+As $\bar{R}$ further decreases, due to the advantage of multisine, a modulated waveform with a very large $\rho$ is outperformed by a superposed waveform with a smaller $\rho$.
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
@@
 Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
+Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ thus maximize the R-E tradeoff.
 It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
@@
 		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
-\emph{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer.
-Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are proportionally amplified to preserve the general trend of the R-E boundary.
+\emph{First,} adding either active or passive elements enhances the equivalent channel strength to boost both information and power transfer.
+Interestingly, it has negligible influence on the optimal transceiving strategy because the rate and current are proportionally amplified that preserves the general trend of the R-E boundary.
 \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
+This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT.
+As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the sine wave at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
 For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
-Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that validates the active scaling law in the order of $M^2$ \cite{Clerckx2016a}.
+Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that suggests an active scaling law in the order of $M^2$.
 On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB} that implies a reflect array gain of $L^2$.
@@
 Compared with active antennas, the IRS achieves higher array gain and power scaling order using passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap with SMF and GP.
+Moreover, the ASS strategy exploits no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap with SMF and GP.
 These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.
@@
 The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e.
-the boundary is obtained by varying the waveform amplitude and splitting ratio).
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
 \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their achievable R-E regions coincide because the antenna mode reflection of the random IRS is cancelled out after averaging over channel realizations.
+Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over channel realizations.
 \emph{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant and the auxiliary channels can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in the closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary channels can be roughly maximized at all subbands.
+It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP.
 On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain.
 By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
-It shows the R-E advantage of adaptive passive beamforming Algorithm~\ref{al:sca} for broadband SWIPT.
+It emphasizes the R-E advantage of adaptive passive beamforming Algorithm~\ref{al:sca} for broadband SWIPT.
 
@@
 Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$.
-Note that the estimation at different subbands are independent but the subchannel responses are correlated.
+Note that the estimations at different subbands are independent, but the subchannel responses are correlated.
 Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
 On the other hand, since the practical reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
-Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e.
-two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper investigated the single-user R-E tradeoff in a novel IRS-aided multi-carrier MISO SWIPT system.
+		This paper investigated the R-E tradeoff of a single user in a novel IRS-aided multi-carrier MISO SWIPT system.
 Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity and practical transceiving strategies to maximize the achievable R-E region.
 A three-stage BCD algorithm is proposed to solve the problem.
-In the first stage, the IRS phase shift is obtained by combining the SCA technique with an relax-then-extract step.
-In the second and third stages, the active precoder is derived in the closed form and the waveform amplitude is optimized by the reversed GP method.
+In the first stage, the IRS phase shift is obtained by combining the SCA technique with a relax-then-extract step.
+In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude is optimized by the reversed GP method.
 We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm with near-optimal performance.
-Numerical results prove the convergence of both BCD algorithms and reveal significant R-E gains by accounting harvester nonlinearity in the passive beamforming design.
-Compared with active antennas, IRS elements are limited to frequency-dependent reflection but are able to integrate coherent combining and equal gain transmission in a fully passive manner to further boost the array gain and power scaling order.
+Numerical results prove the local optimality of the BCD algorithm and reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
+Compared with active antennas, IRS elements are limited to frequency-dependent reflection but able to integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
 However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.
@@
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
+Also, practical IRS patterns with direction- and frequency-dependent reflection could be considered in future works.
 	\end{section}

### 2021-04-16 assets/waveform_subband.tex
:bento: Update assets

--- 2021-04-08 assets/waveform_subband.tex
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,3.374in)},
+height=0.491in,
+at={(0.677in,3.363in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.82172701356454\\
+1	2.821727013159\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000255961727675924\\
+1	0.000259587806229199\\
 };
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,2.645in)},
+height=0.491in,
+at={(0.677in,2.637in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.19551151069007\\
-2	2.79441682266723\\
+1	0.274209781976626\\
+2	2.76985839517448\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	6.76001760054032e-06\\
-2	6.94107248595388e-06\\
+1	7.29255431750488e-06\\
+2	7.41275007486677e-06\\
 };
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,1.916in)},
+height=0.491in,
+at={(0.677in,1.911in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00471916738670986\\
-2	0.0113013795751173\\
-3	0.0524973569625421\\
-4	1.11631746294063\\
+1	0.00906914399366857\\
+2	0.0191780945021875\\
+3	0.0728112091555182\\
+4	1.15645756112447\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.666856968017446\\
-2	0.826759550766013\\
-3	0.96159816303766\\
-4	1.2653467150935\\
+1	0.65161979775128\\
+2	0.797812683770198\\
+3	0.949573699600353\\
+4	1.29650400585771\\
 };
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,1.187in)},
+height=0.491in,
+at={(0.677in,1.184in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000872616544376037\\
-2	0.00117960004406015\\
-3	0.00161605407069224\\
-4	0.00228266132463128\\
-5	0.00326342365821\\
-6	0.00487936277124623\\
-7	0.00881039674196349\\
-8	0.0419634199055652\\
+1	0.00122290635412822\\
+2	0.00162605944227885\\
+3	0.00219881563728839\\
+4	0.00308343653686168\\
+5	0.00446835221941886\\
+6	0.00730773383230549\\
+7	0.018778542482244\\
+8	0.156996809294451\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.633590459263079\\
-2	0.785594177316295\\
-3	0.891389674009387\\
-4	0.98505471211105\\
-5	1.05090474986801\\
-6	1.10664902589546\\
-7	1.1412268011736\\
-8	1.16708811938208\\
+1	0.604492899882458\\
+2	0.741597181612563\\
+3	0.847995036254347\\
+4	0.93677567011772\\
+5	1.00740091437702\\
+6	1.06242371388309\\
+7	1.10606359542287\\
+8	1.16708516593263\\
 };
@@
 width=4.036in,
-height=0.481in,
+height=0.491in,
 at={(0.677in,0.458in)},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000310341555926487\\
-2	0.00035799764238\\
-3	0.00041670813086453\\
-4	0.000484920116868764\\
-5	0.000569098471381299\\
-6	0.000669877208860123\\
-7	0.000793268903064817\\
-8	0.000939331113982085\\
-9	0.0011175247904389\\
-10	0.00132972829292326\\
-11	0.0015875351976808\\
-12	0.00189182501786478\\
-13	0.00226771472661325\\
-14	0.00272021545715682\\
-15	0.00331689397668614\\
-16	0.00407528165955271\\
+1	0.000441546073916646\\
+2	0.000505313371521773\\
+3	0.000579072140308781\\
+4	0.000665955723611611\\
+5	0.000770614004522113\\
+6	0.000892853558400096\\
+7	0.00104199146112475\\
+8	0.00121812704068694\\
+9	0.0014365060772557\\
+10	0.00170548951516733\\
+11	0.00204996483051139\\
+12	0.00251037543116691\\
+13	0.00316602847896381\\
+14	0.00413663959831382\\
+15	0.00569434862540457\\
+16	0.00825748611983488\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.428729933737136\\
-2	0.489701018897442\\
-3	0.539263608495876\\
-4	0.585347098517275\\
-5	0.624083102405944\\
-6	0.657759147074073\\
-7	0.689461005203993\\
-8	0.715900755845553\\
-9	0.741047135425173\\
-10	0.761923826165851\\
-11	0.78165448191713\\
-12	0.796874354752371\\
-13	0.810144534289869\\
-14	0.819572643230985\\
-15	0.826293720140692\\
-16	0.829491639456529\\
+1	0.415766467786655\\
+2	0.472429517994175\\
+3	0.521046798847998\\
+4	0.566100676905971\\
+5	0.605416399739846\\
+6	0.641331572087823\\
+7	0.675743455874702\\
+8	0.705629790631534\\
+9	0.735011238747164\\
+10	0.759950967519761\\
+11	0.784031990499284\\
+12	0.802981219380124\\
+13	0.820186543633863\\
+14	0.831767285739736\\
+15	0.840123349700173\\
+16	0.843558402787778\\
 };

### 2021-04-19 main.tex
:pencil: Update manuscript
:pencil: Update notations

@@
 Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique.
+This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique.
 Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation.
-Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
+Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states.
+Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming design.
 	\end{abstract}
@@
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
@@
 To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
-The performances of both low-complexity designs are proved close to the BCD algorithm under different configurations.
+The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
 
-			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
-It is concluded that 1) the proposed BCD algorithm always converges to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
+			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
+$\boldsymbol{0}$ denotes zero vector or matrix.
+$\boldsymbol{I}$ denotes the identity matrix.
 $j$ denotes the imaginary unit.
-$\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices.
+$\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices.
 $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ denote respectively the argument, rank, trace, and a square matrix with input elements on the main diagonal.
-$\boldsymbol{S} \succeq 0$ means $\boldsymbol{S}$ is positive semi-definite.
+$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector as the main diagonal of the input matrix.
+$\boldsymbol{x} \succeq \boldsymbol{0}$ means every element of $\boldsymbol{x}$ is nonnegative, and $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
 $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
@@
 			\end{equation}
-			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude~\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
+			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
 This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector~\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
+We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
 
@@
 Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function \footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
@@
 				\begin{flalign}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),&&\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).&&\label{eq:z_expand}
 				\end{flalign}
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint as
+		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
 		\begin{maxi!}
 			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
 			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
 			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
@@
 		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose a suboptimal BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{0}}\label{co:irs_sd}
+				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
 				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
 			\end{maxi!}
+			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
+Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}.
+The tightness of rank relaxation is verified below.
 
-			Since \eqref{eq:z_irs_approx} is not an affine, problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee.
-In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be obtained by eigen decomposition.
-In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a high-quality solution can be extracted via the Gaussian randomization method \cite{Luo2010}.
-Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}_{q^{\star}}$ that maximizes \eqref{ob:irs} as the solution.
-Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
-Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+			\begin{proposition}\label{pr:relaxation}
+				Any solution $\boldsymbol{\Phi}$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi})=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
+			\end{proposition}
+
+			\begin{proof}\label{pf:relaxation}
+				See Appendix~\ref{ap:relaxation}.
+			\end{proof}
+
+			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}, and $\boldsymbol{\Phi}^{(i)}$ is updated until convergence.
+We then extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition and retrieve the phase shift of element $l$ by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
 The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\bar{R},\epsilon$, $\forall n$
 					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
+						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs} -- \eqref{co:irs_sd}
 						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
-					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
 					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
-					\Else
-						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
-						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
-						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
-						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
-					\EndIf
 					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
@@
 			\begin{proposition}\label{pr:sca}
-				For any feasible initial point, the SCA Algorithm~\ref{al:sca} can provide a local optimal $\boldsymbol{\Phi}^{\star}$ that satisfies the KKT conditions of the relaxed passive beamforming problem (i.e., maximize \eqref{eq:z_irs} s.t.
-\eqref{co:irs_rate} -- \eqref{co:irs_sd}).
-If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, then the extracted phase shift vector $\boldsymbol{\phi}^{\star}$ is local optimal to the original problem~\eqref{op:original}.
+				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal phase shifts of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:sca}
-				The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \ref{ob:irs} -- \ref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
-Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
-If $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, then $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
+				See Appendix~\ref{ap:sca}.
 			\end{proof}
@@
 		\begin{subsection}{Active Beamforming}
-			For single-user SWIPT, the global optimal information and power precoders coincide at MRT. To prove this, we decouple the waveform in the spatial and frequency domains by
+			We decouple the waveform in the spatial and frequency domains by
 			\begin{equation}\label{eq:w}
@@
 			\end{equation}
-			where $s_{\mathrm{I/P},n}$ denotes the amplitude of modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{C}^{N \times 1}$ and $\boldsymbol{b}_{\mathrm{I/P}} \triangleq [\boldsymbol{b}_{\mathrm{I/P}, 1}^T,\dots,\boldsymbol{b}_{\mathrm{I/P}, N}^T]^T \in \mathbb{C}^{MN \times 1}$ for simplicity.
+			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}^{N \times 1}$.
 The MRT precoder at subband $n$ is given by
-			\begin{equation}\label{eq:b}
-				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}
+			\begin{equation}\label{eq:b_n}
+				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
 			\end{equation}
 
-			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
-Hence, MRT is the global optimal active precoder and no dedicated energy beams are required for single-user SWIPT.
+			\begin{proposition}\label{pr:mrt}
+				For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
+			\end{proposition}
+
+			\begin{proof}\label{pf:mrt}
+				See Appendix~\ref{ap:mrt}.
+			\end{proof}
+
+			Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
 		\end{subsection}
@@
 		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}}$.
-On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
+			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
+With the MRT precoder \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
 Hence, the rate \eqref{eq:R} reduces to
@@
 				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
-				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}.}
+				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
 			\end{maxi!}
 
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\ref{op:waveform} into a reversed GP
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
 			\begin{mini!}
 				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
 				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
 				\addConstraint{\rho + \bar{\rho} \le 1.}
@@
 
-			The denominators of \eqref{co:waveform_objective}, \eqref{co:waveform_rate} are posynomials \cite{Boyd2007} which can be decomposed as sums of monomials
+			The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
 			\begin{align}
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:posynomial_objective},\\
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:posynomial_rate}
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
 			\end{align}
-			where $m_\mathrm{P}=(2N^3+6N^2+7N)/3$ and $m_{\mathrm{I},n}=2$.
-We upper bound \eqref{eq:posynomial_objective} and \eqref{eq:posynomial_rate} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+			where $m_{\mathrm{I},n}=2$ and $m_\mathrm{P}=(2N^3+6N^2+7N)/3$.
+We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 			\begin{mini!}
 				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
 				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
 				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
+				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
 				\addConstraint{\rho + \bar{\rho} \le 1}
 			\end{mini!}
-			where $\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}} \ge 0$, $\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_\mathrm{P}},\gamma_{m_{\mathrm{I},n}}\}$ that needs successive update, and a feasible choice at iteration $i$ is
+			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$ that needs successive update, and a feasible choice at iteration $i$ is
 			\begin{align}
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P},\\
-				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}.\label{eq:gamma_I}
+				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
+				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
 			\end{align}
 
-			$\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho$ are updated iteratively until convergence.
-Problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+			On top of \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+$\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ are updated iteratively until convergence.
 The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:gp}.
@@
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
+					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_\mathrm{P}}^{(i)},\gamma_{m_{\mathrm{I},n}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_P}, \eqref{eq:gamma_I}
+						\State Update $\{\gamma_{m_{\mathrm{I},n}}^{(i)},\gamma_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
 						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
@@
 		\begin{subsection}{Block Coordinate Descent}
-			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
 The BCD algorithm is summarized in Algorithm~\ref{al:bcd}.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P}}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$
-					\State Get $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
+					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
 					\Repeat
@@
 						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ based on $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by Algorithm~\ref{al:gp}
+						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
@@
 			\begin{proposition}\label{pr:bcd}
-				Suppose the $\boldsymbol{\Phi}$ obtained from Algorithm~\ref{al:sca} is rank-\num{1}, the limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD Algorithm \ref{al:bcd} is local optimal to the original problem~\eqref{op:original}.
+				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
 			\end{proposition}
@@
 			\begin{proof}\label{pf:bcd}
-				The objective function \eqref{ob:original} is non-decreasing over the iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
-If $\boldsymbol{\Phi}$ is rank-\num{1}, then by Proposition~\ref{pr:sca}, the corresponding phase shift vector $\boldsymbol{\phi}$ is local optimal to the original problem \ref{op:original}.
-Since the active precoder by \eqref{eq:b} is global optimal and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P}}$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
+				See Appendix~\ref{ap:bcd}
 			\end{proof}
@@
 			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session, while multisine amplitude \eqref{eq:smf} is used in the energy session.
+In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
 In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
@@
 
-			Besides, minor modifications are required for passive beamforming to cooperate with both low-complexity waveform schemes.
+			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
 To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
-Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup, and its local optimality is guaranteed if $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}.
+Algorithm~\ref{al:m-sca} summarizes the modified passive beamforming design for low-complexity PS mode.
+The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca}, and the details are omitted here.
 
@@
 				\caption{Modified: IRS Phase Shift.}
-				\label{al:lc}
+				\label{al:m-sca}
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,Q,\epsilon$, $\forall n$
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\epsilon$, $\forall n$
 					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
@@
 					\Else
+						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
 						\Repeat
 							\State $i \gets i + 1$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \ref{co:irs_sd}
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 					\EndIf
-					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
 					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
-					\Else
-						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
-						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
-						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
-						\State Set $q^{\star}=\arg\max_q{R(\boldsymbol{\Phi}_q)}$ or $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
-					\EndIf
 					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
@@
 
-			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
+			On top of the closed-form waveform schemes and the modified passive beamforming strategy, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the phase shift $\boldsymbol{\phi}$ by Algorithm~\ref{al:m-sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
+The LC-BCD algorithm for PS mode is summarized in Algorithm~\ref{al:lc-bcd}.
+
+			\begin{algorithm}[!t]
+				\caption{LC-BCD: Waveform and Beamforming.}
+				\label{al:lc-bcd}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\Repeat
+						\State $i \gets i + 1$
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m-sca}
+						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
 		\end{subsection}
@@
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
-
-		\begin{table*}[!t]
-			\caption{The maximum value of $1-\nu$ of all R-E samples over all tested channel realizations for BCD and LC-BCD algorithms}
-			\label{ta:eigen_ratio}
-			\centering
-			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-				\hline
-				\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
-				\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
-				$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
-				$[\times \num{e-16}]$ & LC-BCD & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
-			\end{tabular}
-		\end{table*}
-
-		We first provide numerical proof on the rank-\num{1} property of $\boldsymbol{\Phi}$ thus the local optimality of Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc}.
-To see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
-Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-For all intermediate $\boldsymbol{\Phi}$ achieved by Algorithm~\ref{al:sca}, Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ of \num{20} R-E samples over \num{300} tested channel realizations for both BCD algorithms.
-With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint \ref{co:irs_rank} can be relaxed, the phase shift $\boldsymbol{\phi}$ can be extracted by eigen decomposition without performance loss, and Algorithm~\ref{al:sca}, \ref{al:bcd} and \ref{al:lc} converge to local optimal points.
 
@@
 The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m-sca} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
 \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
@@
 			\centering
-			\subfloat[Imperfect CSIT\label{fi:re_csi}]{
+			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude is optimized by the reversed GP method.
-We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm with near-optimal performance.
-Numerical results prove the local optimality of the BCD algorithm and reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
+We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance.
+Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
 Compared with active antennas, IRS elements are limited to frequency-dependent reflection but able to integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
@@
 
+	\begin{appendix}
+		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
+			Problem~\eqref{op:irs} after rank constraint relaxation is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, hence strong duality holds and the duality gap is zero.
+The Lagrangian function of problem \eqref{ob:irs} -- \eqref{co:irs_sd} at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_rate}, \eqref{co:irs_modulus} and \eqref{co:irs_sd}.
+$\zeta$ collects all constant terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
+			\begin{figure*}[!b]
+				\hrule
+				\begin{align}\label{eq:lagrangian}
+					\mathcal{L}
+					&= - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
+							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
+							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
+								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
+							\Bigr) + \sum_{k=-N+1}^{N-1} 2 \Re\Bigl\{
+								(t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
+									\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
+								\Bigr)
+							\Bigr\}\nonumber\\
+					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
+								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+							\Bigr) - \mathrm{tr}^2 \Bigl(
+								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+							\Bigr)
+						\Biggr)\nonumber + \mu \Biggl(
+						2^{\bar{R}} - \prod_{n=1}^N \biggl(
+							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
+								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
+							\Bigr)}{\sigma_n^2}
+						\biggr)
+					\Biggr)\nonumber\\
+					&\quad+ \mathrm{tr}\biggl(
+						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
+							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
+						\Bigr)
+					\biggr) - \mathrm{tr} \Bigl(
+						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
+					\Bigr) + \zeta
+				\end{align}
+			\end{figure*}
+			The corresponding Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions can be expressed as
+
+			\begin{subequations}
+				\begin{equation}\label{eq:lagrange_multiplier}
+					\mu^\star \ge 0, \boldsymbol{\nu}^\star \succeq \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
+				\end{equation}
+				\begin{equation}\label{eq:complementary_slackness}
+					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
+				\end{equation}
+				\begin{equation}\label{eq:gradient}
+					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
+				\end{equation}
+			\end{subequations}
+
+		\end{subsection}
+
+		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
+			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs} -- \eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
+Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
+According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
+		\end{subsection}
+
+		\begin{subsection}{Proof of Proposition~\ref{pr:mrt}}\label{ap:mrt}
+			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+Therefore, MRT is the global optimal information and power precoder.
+		\end{subsection}
+
+		\begin{subsection}{Proof of Proposition~\ref{pr:bcd}}\label{ap:bcd}
+			The objective function \eqref{ob:original} is non-decreasing over the iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
+Therefore, Algorithm~\ref{al:bcd} is guaranteed to converge.
+Since the IRS phase shift retrieved by Algorithm~\ref{al:sca} is local optimal, the active precoder obtained by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio returned by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
+		\end{subsection}
+	\end{appendix}
+
 	\bibliographystyle{IEEEtran}

### 2021-04-20 main.tex
:lock: Rank relaxation proof

@@
 			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
-$\boldsymbol{0}$ denotes zero vector or matrix.
+$j$ denotes the imaginary unit.
+$\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
 $\boldsymbol{I}$ denotes the identity matrix.
-$j$ denotes the imaginary unit.
 $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices.
@@
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector as the main diagonal of the input matrix.
-$\boldsymbol{x} \succeq \boldsymbol{0}$ means every element of $\boldsymbol{x}$ is nonnegative, and $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
+$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector that retrieves the main diagonal of the input matrix.
+$\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
 $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
@@
 			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
+			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
 			\addConstraint{0 \le \rho \le 1.}
@@
 
-			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real and we have
+
+			\begin{equation}\label{eq:coupled_terms}
+				\sum_{k=-N+1}^{N-1} \Re\left\{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} 2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*
+			\end{equation}
+
+			Plugging \eqref{eq:taylor_1} -- \eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
+					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
 					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
@@
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
+				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
 				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
 			\end{maxi!}
 			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
-Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}.
+Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP \cite{Luo2010a} to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}.
 The tightness of rank relaxation is verified below.
@@
 			\begin{proposition}\label{pr:relaxation}
-				Any solution $\boldsymbol{\Phi}$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi})=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
+				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
 			\end{proposition}
@@
 				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
 			\end{align}
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
-			Problem~\eqref{op:irs} after rank constraint relaxation is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, hence strong duality holds and the duality gap is zero.
-The Lagrangian function of problem \eqref{ob:irs} -- \eqref{co:irs_sd} at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_rate}, \eqref{co:irs_modulus} and \eqref{co:irs_sd}.
-$\zeta$ collects all constant terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
+			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always hold due to the modulus constraint~\eqref{co:irs_modulus}.
+Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and formulate an equivalent problem as
+			\begin{maxi!}
+				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
+				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
+				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
+				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_equivalent_rank}}
+			\end{maxi!}
+
+			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent} -- \eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
+The corresponding Lagrangian function at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
 			\begin{figure*}[!b]
 				\hrule
-				\begin{align}\label{eq:lagrangian}
+				\begin{flalign}\label{eq:lagrangian}
 					\mathcal{L}
-					&= - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
+					&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
 							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
@@
 								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-							\Bigr) + \sum_{k=-N+1}^{N-1} 2 \Re\Bigl\{
-								(t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
+							\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
 								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
 							\Bigr)
-							\Bigr\}\nonumber\\
+							&&\nonumber\\
 					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
@@
 							\Bigr)
-						\Biggr)\nonumber + \mu \Biggl(
+						\Biggr) + \mu \Biggl(
 						2^{\bar{R}} - \prod_{n=1}^N \biggl(
@@
 						\biggr)
-					\Biggr)\nonumber\\
+					\Biggr)&&\nonumber\\
 					&\quad+ \mathrm{tr}\biggl(
@@
 						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta
-				\end{align}
+					\Bigr) + \zeta,&&
+				\end{flalign}
 			\end{figure*}
-			The corresponding Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions can be expressed as
-
+			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
 			\begin{subequations}
 				\begin{equation}\label{eq:lagrange_multiplier}
-					\mu^\star \ge 0, \boldsymbol{\nu}^\star \succeq \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
+					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
 				\end{equation}
@@
 
+			We derive the gradient explicitly and rewrite \eqref{eq:gradient} as
+			\begin{equation}
+				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
+			\end{equation}
+			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
+			\begin{figure*}[!b]
+				\begin{flalign}\label{eq:delta}
+					\boldsymbol{\Delta}^\star
+					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
+						\Biggl(
+							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
+					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
+								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
+							\Bigr)
+						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
+						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
+							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
+						\Bigr)}{\sigma_{n'}^2}
+					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
+				\end{flalign}
+			\end{figure*}
+			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
+By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
+On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.
+Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$.
+Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
+			% \begin{figure*}[!b]
+			% 	\begin{flalign}\label{eq:lagrangian_gradient}
+			% 		\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L}
+			% 		&= \boldsymbol{I} - \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) - \frac{3}{4} \beta_4 \rho^2
+			% 			\Biggl(
+			% 				2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
+			% 		&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
+			% 					(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
+			% 				\Bigr)
+			% 			\Biggr) - \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
+			% 			1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
+			% 				\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
+			% 			\Bigr)}{\sigma_{n'}^2}
+			% 		\Biggr)&&\nonumber\\
+			% 		&\quad+ \mathrm{diag}(\boldsymbol{\nu^\star}) - \boldsymbol{\Upsilon}^\star.&&
+			% 	\end{flalign}
+			% \end{figure*}
 		\end{subsection}

### 2021-04-22 main.tex
:pencil: Update manuscript

@@
 \begin{document}
-	\title{Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
+	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
 	\author{
@@
 \cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2013} to characterize the R-E region for multi-antenna broadcast and interference channels.
+Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
 On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
@@
 Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT.
-Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2020}.
+Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
 A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
@@
 			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
-To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
 The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
-This is the first paper to tackle energy harvester nonlinearity, multi-carrier transmission, and co-localized receiver for IRS-aided SWIPT.
+This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
+By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.
 
@@
 The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
+This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
 
@@
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
-To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
+To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
 The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E boundary points, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 			\end{equation}
-			where we define the cascaded AP-IRS-UE channel (without IRS reflection) as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+			where we define the cascaded channel without IRS reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
 
@@
 				\begin{flalign}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).&&\label{eq:z_expand}
+					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),&&\label{eq:z_expand}
 				\end{flalign}
@@
 
-			Plugging \eqref{eq:taylor_1} -- \eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
-Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP \cite{Luo2010a} to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}.
+Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP \cite{Luo2010} to formulate a convex problem~\eqref{ob:irs}--\eqref{co:irs_sd}.
 The tightness of rank relaxation is verified below.
@@
 			\begin{proposition}\label{pr:relaxation}
-				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
+				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
 			\end{proposition}
@@
 						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs} -- \eqref{co:irs_sd}
+						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
 						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
-			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always hold due to the modulus constraint~\eqref{co:irs_modulus}.
+			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{co:irs_modulus}.
 Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and formulate an equivalent problem as
@@
 
-			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent} -- \eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
+			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
 The corresponding Lagrangian function at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
@@
 				\begin{equation}\label{eq:gradient}
-					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
+					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0,
 				\end{equation}
 			\end{subequations}
-
-			We derive the gradient explicitly and rewrite \eqref{eq:gradient} as
+			and we derive the gradient explicitly and rewrite \eqref{eq:gradient} as
 			\begin{equation}
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
-			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs} -- \eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
+			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
 Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
@@
 			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2} -- \eqref{eq:y_P4}.
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}.
 Therefore, MRT is the global optimal information and power precoder.

### 2021-04-22 response.tex
:bento: Update assets
:pencil: Update response letter

@@
 \usepackage[T1]{fontenc}
+\usepackage[short]{optidef}
 \usepackage[caption=false,font=footnotesize]{subfig}
@@
 
-\newcommand{\reviewersection}
+\newcommand{\reviewer}
 	{\stepcounter{reviewer} \bigskip \hrule \section*{Reviewer \thereviewer}}
@@
 
-	\begin{reviewersection}
+	\begin{reviewer}
 		\begin{point}
@@
 		\begin{response}
-			Thank you for pointing out the CSI acquisition issue regarding the cascaded AP-IRS-UE link.
+			Thank you for pointing out the CSI acquisition issue regarding the cascaded link.
 The proposed passive beamforming algorithms rely on such cascaded CSIT, and recent researches proposed element-wise on/off switching [25], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} techniques to solve this issue.
 Those references have been cited in the literature review.
-To address the comment, we consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
+To address the comment, we have revised the simulation results and applied the proposed algorithms to an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
 			\begin{equation}
@@
 				}
-				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\caption{Average R-E region with imperfect cascaded CSIT for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 				\label{fi:re_csi}
@@
 		\begin{response}
-			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the reasons explained below.
+			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the ``don't run before we can walk'' reasons explained below.
 
 			\emph{First}, it is important to remind the reviewer that the problem of joint waveform and beamforming design for a multi-user SWIPT system without IRS has never been studied in the literature.
-In other words, it would not make sense at this stage to address this multiuser IRS-aided SWIPT since the underlying building block of multiuser SWIPT is not known.
+In other words, it would be premature at this stage to address this multiuser IRS-aided SWIPT since the underlying building block of multiuser SWIPT is not known.
 Only once the problem of multiuser joint waveform and beamforming for multi-user SWIPT has been addressed, can we investigate the multiuser joint waveform and beamforming design for IRS-aided SWIPT.
@@
 Our modeling of SWIPT is not "simple": not only we transmit both information and power, we deal with joint space and frequency optimization through a joint beamforming and waveform problem that is challenging due to the nonlinearity of the rectifier that induces coupling among frequencies components.
-This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction [31 -- 33].
+This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction [31--33].
+To reflect this aspect, we have revised the title to ``IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model''.
 
 			\emph{Third}, multi-user WPT leads to its own set of challenges compared single-user WPT.
-Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in [8, 36].
-Consequently, single-user and multi-user WPT are designed differently in [8, 36].
+Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in [8,36].
+Consequently, single-user and multi-user WPT are designed differently in [8,36].
 Though the SWIPT case has not been studied, the same set of problems is expected to occur between single user and multiuser case and would be even more challenging since communication is delivered simultaneously with power.
@@
 			Thank you for raising this issue.
-The rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$ to the relaxed problem (25a) -- (25d) is suggested by the CVX software [39] under different configurations.
-Although the local optimality of the BCD Algorithm~3 relies on this conclusion, it is intricate to provide a mathematical proof due to the coupled objective (24) and the log sum constraint (25b).
-Instead, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$.
-Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$.
-For all intermediate $\boldsymbol{\Phi}$ achieved by Algorithm~1, Table~1 shows the maximum value of $1-\nu$ of \num{20} R-E samples over \num{300} tested channel realizations for both BCD algorithms.
-With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations.
-It suggests that the rank constraint (25e) can be relaxed, the phase shift $\boldsymbol{\phi}$ can be extracted by eigen decomposition without performance loss, and Algorithm~1, 3 and 4 converge to local optimal points.
+To prove the rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$, we notice that for any feasible $\boldsymbol{\Phi}$ to problem~(26), $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~(26c).
+Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to (26a) and formulate an equivalent problem as
+			\begin{maxi!}
+				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
+				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
+				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
+				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_equivalent_rank}}
+			\end{maxi!}
 
-			\begin{table*}[!h]
-				\caption{The maximum value of $1-\nu$ of all R-E samples over all tested channel realizations for BCD and LC-BCD algorithms}
-				\label{ta:eigen_ratio}
-				\centering
-				\resizebox{\columnwidth}{!}{
-					\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
-						\hline
-						\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
-						\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
-						$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
-						$[\times \num{e-16}]$ & LC-BCD & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
-					\end{tabular}
-				}
-			\end{table*}
-
+			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition [47], thus strong duality holds.
+The corresponding Lagrangian function at iteration $i$ is given by
+			\begin{align}\label{eq:lagrangian}
+				\mathcal{L}
+				&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
+						(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+					\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
+						4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
+							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
+						\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
+							\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
+						\Bigr)
+						\nonumber\\
+				&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
+							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+						\Bigr) - \mathrm{tr}^2 \Bigl(
+							(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+						\Bigr)
+					\Biggr)\nonumber\\
+				&\quad+ \mu \Biggl(
+					2^{\bar{R}} - \prod_{n=1}^N \biggl(
+						1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
+							\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
+						\Bigr)}{\sigma_n^2}
+					\biggr)
+				\Biggr) + \mathrm{tr}\biggl(
+					\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
+						\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
+					\Bigr)
+				\biggr) - \mathrm{tr} \Bigl(
+					\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
+				\Bigr) + \zeta,
+			\end{align}
+			where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
+The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
+			\begin{subequations}
+				\begin{equation}\label{eq:lagrange_multiplier}
+					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
+				\end{equation}
+				\begin{equation}\label{eq:complementary_slackness}
+					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
+				\end{equation}
+				\begin{equation}\label{eq:gradient}
+					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0,
+				\end{equation}
+			\end{subequations}
+			and we derive the gradient explicitly and rewrite \eqref{eq:gradient} as
+			\begin{equation}
+				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
+			\end{equation}
+			with $\boldsymbol{\Delta}^\star$ given by
+			\begin{align}\label{eq:delta}
+				\boldsymbol{\Delta}^\star
+				&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
+					\Biggl(
+						2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})\nonumber\\
+				&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
+							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
+						\Bigr)
+					\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
+					1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
+						\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
+					\Bigr)}{\sigma_{n'}^2}
+				\Biggr)\nonumber\\
+				&\quad- \mathrm{diag}(\boldsymbol{\nu^\star}).
+			\end{align}
+			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
+By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
+On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.
+Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$.
+Due to the equivalence between (26a) and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~(26).
+We have clarified this point in Proposition~1.
 			\label{re:1.3}
@@
 		\begin{response}
-			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
 			\label{re:1.4}
@@
 However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general approaches to address this issue.
-For any passive beamforming problem with unit-rank constraint (which is non-convex), we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
+For any passive beamforming problem with unit-rank constraint (which is non-convex), if the proof to Proposition~1 is unavailable, we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
 Both techniques are expected to provide a unit-rank solution with performance very close to the original solution.
@@
 		\end{response}
-	\end{reviewersection}
+	\end{reviewer}
 
-	\begin{reviewersection}
+	\begin{reviewer}
 		\begin{point}
@@
 			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate (8).
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms (11) -- (14).
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms (11)--(14).
 Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
@@
 Indeed, the assumption of perfect CSIT is very ideal and the existing channel estimation protocols may not provide decent results in practice.
-We have investigated the impact of CSIT estimation error of the cascaded AP-IRS-UE link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy.
+We have investigated the impact of CSIT estimation error of the cascaded link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy.
 			\label{re:2.3}
@@
 			We appreciate your suggestion and have revised the manuscript correspondingly.
-The original objective function (20) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (21) -- (23) to formulate SCA problems of the original passive beamforming problem (i.e.
+The original objective function (20) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (21)--(23) to formulate SCA problems of the original passive beamforming problem (i.e.
 maximize (20) s.t.
-(25b) -- (25e)).
-The objective affine function (24) is obtained by plugging (21) -- (23) into (20).
-It satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$ such that solving (25) iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem.
+(26b)--(26e)).
+The quadratic objective function (25) is obtained by plugging (21)--(24) into (20).
+It satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$ such that solving (26) iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem.
 			\label{re:2.4}
@@
 		\begin{response}
-			Algorithm~1 -- 4 only provide local optimal solutions with analytical/numerical local convergence proof, and the performance indeed depends on the initialization.
+			Algorithm~1--5 provide local optimal solutions with analytical/numerical local convergence proof, and the performance indeed depends on the initialization.
 For the passive beamforming Algorithm~1, we initialize the phase shift of all IRS elements as i.i.d.
 uniform random variables over $[0, 2\pi)$.
-For the waveform amplitude and splitting ratio Algorithm~2, we initialize the modulated waveform by the Water-Filling (WF) strategy (37) and the multisine waveform by the Scaled Matched Filter (SMF) scheme (38), and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$.
-These parameters are used for general initialization and regulated by the algorithm afterwards.
+For Algorithm~2, we initialize the modulated waveform by the Water-Filling (WF) strategy (38) and the multisine waveform by the Scaled Matched Filter (SMF) scheme (39), and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$.
+These parameters are used for general initialization and regulated automatically afterwards.
 However, as Algorithm~3 only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
@@
 If a point is strictly dominated, we discard the candidate, reinitialize Algorithm~3 by the solution at the previous point, then perform the optimization again.
-For a tolerance of $\epsilon=10^{-8}$, Algorithm~1 -- 4 typically converge within 2, 7, 2, 2 iterations, respectively.
+For a tolerance of $\epsilon=10^{-8}$, Algorithm~1--5 typically converge within 2, 7, 2, 2, 3 iterations, respectively.
+
+			We also would like to point out that, even in the absence of IRS, the problem of joint waveform and beamforming design for SWIPT is also non-convex and algorithms only converging toward a local optimum have been identified, with the global optimum remaining unsolved.
 			\label{re:2.6}
@@
 		\begin{response}
-			Problem (25) is not a Semidefinite Programming (SDP) due to the squared term in the objective function.
+			Problem (26) is not a Semidefinite Programming (SDP) due to the squared term in the objective function.
 Hence, existing complexity analysis tools cannot be direct applied to Algorithm~1 and 4.
-For Algorithm~2, the computational complexity scales exponentially with the number of subbands [36, 43], but an analytical expression cannot be derived on top of relevant literatures.
-To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
+For Algorithm~2, the computational complexity scales exponentially with the number of subbands [36,41] but an analytical expression cannot be derived on top of relevant literatures.
+To facilitate practical SWIPT implementation and address the reviewer's comment, we have added in the revised manuscript two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
 The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
@@
 			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation [45] and the details are omitted here.
+The closed-form solution can be obtained by iterative power allocation [42] and the details are omitted here.
 On the other hand, SMF was proposed in [12] as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
@@
 			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-In the low-complexity TS waveform design, modulated waveform \eqref{eq:wf} is used in the data session while multisine waveform \eqref{eq:smf} is used in the energy session.
-In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and the amplitude of modulated and multisine components are given by
+In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
+In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
 			\begin{align}
 				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
 			\end{align}
-			Fig.~\ref{fi:re_noise} -- \ref{fi:re_reflector} demonstrate that the low-complexity BCD algorithm achieves near-optimal performance under different configurations.
+
+			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
+To achieve the WIT point ($\eta=\rho=0$), the achievable rate (19) instead of the DC current (25) should be maximized.
+To achievable non-WIT points, the rate constraint (26b) should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
+Algorithm~\ref{al:m-sca} summarizes the modified passive beamforming design for low-complexity PS mode.
+The tightness of rank relaxation and local optimality can be proved similar to Proposition~1 and 2, and the details are omitted here.
+
+			Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD algorithm achieves near-optimal performance under different configurations.
 
@@
 		\begin{response}
-			The assumption of lossless reflection is indeed very ideal.
-Based on the circuit analysis, the authors of [24] shows that the reflection amplitude depends on the phase shift, which experiences a trough at \num{0} phase shift and is negatively correlated to the element resistance.
+			The assumption of lossless reflection is indeed ideal, but similar models are widely considered in microwave theory (e.g., \cite{Shen2020a}).
+Based on the circuit analysis, the authors of [24] shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance.
 For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} at a phase shift of $\pi$ but around \num{0.6} at a phase shift of \num{0}.
 From the perspective of field and propagation, \cite{Ozdogan2020} points out that if the dimension of IRS element is much larger than the wavelength, the beamwidth would become small and the scattered field strength would depend on the observation angle.
-However, to reduce the design complexity and provide a preliminary insight, we considered the commonest lossless reflection pattern at the IRS in this paper.
+However, to reduce the design complexity and provide a preliminary insight, we considered the lossless reflection pattern at the IRS in this paper.
 			\label{re:2.8}
@@
 		\begin{response}
-			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
 			\label{re:2.9}
 		\end{response}
-	\end{reviewersection}
+	\end{reviewer}
 
-	\begin{reviewersection}
+	\begin{reviewer}
 		\begin{point}
@@
 			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
-To elevate the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
-The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
-This is the first paper to tackle energy harvester nonlinearity, multi-carrier transmission, and co-localized receiver for IRS-aided SWIPT.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
+The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
+By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.
 
-			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints, and solve each R-E boundary point by an Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS reflection coefficient by relax-then-extract method.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder and waveform amplitude are updated iteratively until convergence.
+The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
+This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
 
-			\emph{Third}, we introduce two low-complexity adaptive waveform design in the closed form to avoid the exponential complexity of the GP algorithm.
+			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
-To cooperate with the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
-The performance of the low-complexity design is proved close to the BCD algorithm under different configurations.
+To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
+The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
 
-			\emph{Fourth}, we provide numerical results to evaluate the performance of the proposed algorithms.
-It is concluded that 1) the proposed BCD algorithm always converge to local optimal points, 2) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 6) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 7) at different R-E points, the optimal IRS reflection coefficients coincide for narrowband SWIPT but differ for broadband SWIPT, 8) the proposed algorithms are robust to practical limitations as inaccurate cascaded CSIT and finite IRS reflection states.
+			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E boundary points, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}
@@
 The reviewer is referred to Response \ref{re:1.1} for details.
-Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.
+Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed joint waveform, active and passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.
 			\label{re:3.4}
@@
 On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD algorithm.
-Fig.~\ref{fi:re_noise} -- \ref{fi:re_reflector} demonstrate that the low-complexity BCD algorithm achieves near-optimal performance under different configurations.
+Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD algorithm achieves near-optimal performance under different configurations.
 Moreover, we have investigated the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization}.
@@
 		\begin{response}
-			We sincerely apologize for the inconvenience. The figures would be amplified in future versions.
+			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
 			\label{re:3.6}
 		\end{response}
-	\end{reviewersection}
+	\end{reviewer}
 

### 2021-04-22 letter.tex
:pencil: Update response letter

--- 2021-01-28 letter.tex
@@
 	\begin{letter}{Prof.
-Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design)}
+Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model)}
 		\opening{Dear Prof. Liang Xiao and Reviewers,}
@@
 The manuscript has been revised carefully based on your valuable comments and suggestions.
-In particular, we attempted to clarify the motivations and contributions of this work.
+In particular, we clarified the motivations and contributions of this work, proved the unit-rank property of the obtained IRS matrix, added two low-complexity designs with near-optimal rate-energy performance, and considered the cases of imperfect cascaded CSIT and finite IRS reflection states.
 To answer the questions and concerns, we include a point-to-point response below, which also describes all modifications made to the manuscript.

### 2021-04-23 main.tex
:pencil: Update manuscript

@@
 In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
 The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E boundary points, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E tradeoff, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
-Algorithm~\ref{al:m-sca} summarizes the modified passive beamforming design for low-complexity PS mode.
+Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode.
 The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca}, and the details are omitted here.
@@
 				\caption{Modified: IRS Phase Shift.}
-				\label{al:m-sca}
+				\label{al:m_sca}
 				\begin{algorithmic}[1]
@@
 
-			On top of the closed-form waveform schemes and the modified passive beamforming strategy, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the phase shift $\boldsymbol{\phi}$ by Algorithm~\ref{al:m-sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
-The LC-BCD algorithm for PS mode is summarized in Algorithm~\ref{al:lc-bcd}.
+			On top of the closed-form waveform schemes and the modified passive beamforming strategy, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the phase shift $\boldsymbol{\phi}$ by Algorithm~\ref{al:m_sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
+The LC-BCD algorithm for PS mode is summarized in Algorithm~\ref{al:lc_bcd}.
 
@@
 				\caption{LC-BCD: Waveform and Beamforming.}
-				\label{al:lc-bcd}
+				\label{al:lc_bcd}
 				\begin{algorithmic}[1]
@@
 						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m-sca}
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
 						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
@@
 The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m-sca} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
 \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
@@
 				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_equivalent_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
 			\end{maxi!}
@@
 				\begin{equation}\label{eq:gradient}
-					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0,
+					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
 				\end{equation}
 			\end{subequations}
-			and we derive the gradient explicitly and rewrite \eqref{eq:gradient} as
+
+			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
 			\begin{equation}
@@
 			\end{figure*}
+
 			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
@@
 Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
-			% \begin{figure*}[!b]
-			% 	\begin{flalign}\label{eq:lagrangian_gradient}
-			% 		\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L}
-			% 		&= \boldsymbol{I} - \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) - \frac{3}{4} \beta_4 \rho^2
-			% 			\Biggl(
-			% 				2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
-			% 		&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
-			% 					(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
-			% 				\Bigr)
-			% 			\Biggr) - \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
-			% 			1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
-			% 				\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
-			% 			\Bigr)}{\sigma_{n'}^2}
-			% 		\Biggr)&&\nonumber\\
-			% 		&\quad+ \mathrm{diag}(\boldsymbol{\nu^\star}) - \boldsymbol{\Upsilon}^\star.&&
-			% 	\end{flalign}
-			% \end{figure*}
 		\end{subsection}

### 2021-04-23 response.tex
:pencil: Update response letter

@@
 \usepackage{fullpage}
-\usepackage{hyperref}
 \usepackage{mathtools}
@@
 \usepackage{siunitx}
+\usepackage{xr-hyper}
+\usepackage{hyperref}
+
+\externaldocument[M-]{main}
 
@@
 \makeatother
+
+\renewcommand{\theequation}
+	{E\arabic{equation}}
+
+\renewcommand{\thefigure}
+	{F\arabic{figure}}
+
+\renewcommand{\thetable}
+	{T\arabic{table}}
 
@@
 			Thank you for pointing out the CSI acquisition issue regarding the cascaded link.
-The proposed passive beamforming algorithms rely on such cascaded CSIT, and recent researches proposed element-wise on/off switching [25], joint training sequence and reflection pattern design \cite{Kang2020} and compressed sensing \cite{Wang2020} techniques to solve this issue.
+The proposed passive beamforming algorithms rely on such cascaded CSIT, and recent researches proposed element-wise on/off switching \cite{M-Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020} techniques to solve this issue.
 Those references have been cited in the literature review.
@@
 		\begin{response}
-			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the ``don't run before we can walk'' reasons explained below.
+			Multi-user IRS-aided SWIPT is very interesting and should be investigated in the future, but is left for future work for the ``don't run before we can walk'' reasons explained below:
 
@@
 Our modeling of SWIPT is not "simple": not only we transmit both information and power, we deal with joint space and frequency optimization through a joint beamforming and waveform problem that is challenging due to the nonlinearity of the rectifier that induces coupling among frequencies components.
-This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction [31--33].
+This completely contrasts with any existing IRS-aided SWIPT work as discussed in the introduction \cite{M-Wu2020b,M-Tang2019,M-Wu2020a}.
 To reflect this aspect, we have revised the title to ``IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model''.
@@
 			\emph{Third}, multi-user WPT leads to its own set of challenges compared single-user WPT.
-Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in [8,36].
-Consequently, single-user and multi-user WPT are designed differently in [8,36].
+Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in \cite{M-Clerckx2016a,M-Huang2017}.
+Consequently, single-user and multi-user WPT are designed differently in \cite{M-Clerckx2016a,M-Huang2017}.
 Though the SWIPT case has not been studied, the same set of problems is expected to occur between single user and multiuser case and would be even more challenging since communication is delivered simultaneously with power.
@@
 			Thank you for raising this issue.
-To prove the rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$, we notice that for any feasible $\boldsymbol{\Phi}$ to problem~(26), $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~(26c).
-Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to (26a) and formulate an equivalent problem as
+To prove the rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$, we notice that for any feasible $\boldsymbol{\Phi}$ to problem~\eqref{M-op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{M-co:irs_modulus}.
+Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{M-ob:irs} and formulate an equivalent problem as
 			\begin{maxi!}
@@
 				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_equivalent_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
 			\end{maxi!}
 
-			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition [47], thus strong duality holds.
+			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{M-Boyd2004}, thus strong duality holds.
 The corresponding Lagrangian function at iteration $i$ is given by
@@
 				\begin{equation}\label{eq:gradient}
-					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0,
+					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
 				\end{equation}
 			\end{subequations}
-			and we derive the gradient explicitly and rewrite \eqref{eq:gradient} as
+			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
 			\begin{equation}
@@
 Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$.
-Due to the equivalence between (26a) and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~(26).
-We have clarified this point in Proposition~1.
+Due to the equivalence between \eqref{M-ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{M-op:irs}.
+We have clarified this point in Proposition~\ref{M-pr:relaxation}.
 			\label{re:1.3}
@@
 			We agree with the reviewer that the relaxation on the rank-one constraint deserves more attention.
-However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general approaches to address this issue.
-For any passive beamforming problem with unit-rank constraint (which is non-convex), if the proof to Proposition~1 is unavailable, we can either relax the constraint and use Gaussian randomization method to obtain a high-quality solution [38], or replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method [33], \cite{Wu2021}.
-Both techniques are expected to provide a unit-rank solution with performance very close to the original solution.
+However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general ideas to address this issue.
+For any passive beamforming problem with non-convex unit-rank constraint, if the proof to Proposition~\ref{M-pr:relaxation} is unavailable, existing approaches include 1) relax the constraint and use Gaussian randomization method to obtain a high-quality solution \cite{M-Luo2010}, 2) replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method \cite{M-Wu2020a}, \cite{Wu2021}, 3) apply the gradient descent in the manifold space \cite{Zuo2020}.
+All three techniques are expected to provide a unit-rank solution with performance very close to the original solution.
 			\label{re:1.5}
@@
 		\begin{point}
-			New RIS models are now being adopted as in [24] where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+			New RIS models are now being adopted as in \cite{M-Abeywickrama2019} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
 			\label{pt:2.1}
@@
 		\begin{point}
-			Why is MRT considered as precoder by (27) rather than optimizing it? Is it globally optimal too?
+			Why is MRT considered as precoder by \eqref{M-eq:b_n} rather than optimizing it? Is it globally optimal too?
 			\label{pt:2.2}
@@
 			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate (8).
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms (11)--(14).
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{M-eq:y_I2}--\eqref{M-eq:y_P4}.
 Hence, MRT is the global optimal active precoder and no dedicated energy beams are required in the single-user SWIPT.
-We have separated the active beamforming design from the waveform design in the revised manuscript to clarify this point.
+We have separated the active beamforming design from the waveform design in the revised manuscript, summarized the conclusion in Proposition~\ref{M-pr:mrt}, and add the proof above to clarify this point.
 			\label{re:2.2}
@@
 Indeed, the assumption of perfect CSIT is very ideal and the existing channel estimation protocols may not provide decent results in practice.
-We have investigated the impact of CSIT estimation error of the cascaded link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy.
+We have investigated the impact of CSIT estimation error of the cascaded link on the R-E performance, and Fig.~\ref{fi:re_csi} shows that the proposed algorithms are robust to CSIT inaccuracy for different $L$.
 			\label{re:2.3}
@@
 		\begin{point}
-			All the assumptions and relaxations adopted used in the derivation of results as in (24) need to be explicitly mentioned along with appropriate justification for the same.
+			All the assumptions and relaxations adopted used in the derivation of results as in \eqref{M-eq:z_irs_approx} need to be explicitly mentioned along with appropriate justification for the same.
 			\label{pt:2.4}
@@
 			We appreciate your suggestion and have revised the manuscript correspondingly.
-The original objective function (20) is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions (21)--(23) to formulate SCA problems of the original passive beamforming problem (i.e.
-maximize (20) s.t.
-(26b)--(26e)).
-The quadratic objective function (25) is obtained by plugging (21)--(24) into (20).
-It satisfies $\tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i)}) = z(\boldsymbol{\Phi}^{(i)}) \ge \tilde{z}(\boldsymbol{\Phi}^{(i)}, \boldsymbol{\Phi}^{(i-1)})$ such that solving (26) iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem.
+The original objective function \eqref{M-eq:z_irs} is differentiable and non-concave in $\mathbb{C}^{4N - 2}$, and we approximate (linearize) the second-order terms by the first-order Taylor expansions \eqref{M-eq:taylor_1}--\eqref{M-eq:taylor_3} to formulate SCA problems of the original passive beamforming problem (i.e.
+maximize \eqref{M-eq:z_irs} s.t.
+\eqref{M-co:irs_rate}--\eqref{M-co:irs_rank}).
+Also, \eqref{M-eq:coupled_terms} holds due to symmetrical summation.
+Hence, the quadratic objective function \eqref{M-eq:z_irs_approx} is obtained by plugging \eqref{M-eq:taylor_1}--\eqref{M-eq:coupled_terms} into \eqref{M-eq:z_irs}.
+Solving relaxed problem \eqref{M-op:irs} iteratively is guaranteed to converge to a local optimal point of the original passive beamforming problem, and the proof is provided in Appendix~\ref{M-ap:sca}.
 			\label{re:2.4}
@@
 		\begin{response}
-			Algorithm~1--5 provide local optimal solutions with analytical/numerical local convergence proof, and the performance indeed depends on the initialization.
-For the passive beamforming Algorithm~1, we initialize the phase shift of all IRS elements as i.i.d.
+			Algorithm~\ref{M-al:sca}--\ref{M-al:lc_bcd} provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
+For the passive beamforming Algorithm~\ref{M-al:sca} and \ref{M-al:m_sca}, we initialize the phase shift of all IRS elements as i.i.d.
 uniform random variables over $[0, 2\pi)$.
-For Algorithm~2, we initialize the modulated waveform by the Water-Filling (WF) strategy (38) and the multisine waveform by the Scaled Matched Filter (SMF) scheme (39), and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$.
+For Algorithm~\ref{M-al:gp}, we initialize the modulated waveform by the Water-Filling (WF) strategy \ref{eq:wf} and the multisine waveform by the Scaled Matched Filter (SMF) scheme \ref{eq:smf}, and assume $\rho^{(0)}=\bar{\rho}^{(0)}=1$.
 These parameters are used for general initialization and regulated automatically afterwards.
-However, as Algorithm~3 only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
+However, as Algorithm~\ref{M-al:bcd} and \ref{M-al:lc_bcd} only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
 To address this issue, we draw the R-E boundary from the high-rate low-energy (lower right) points to the low-rate high-energy (upper left) points.
-If a point is strictly dominated, we discard the candidate, reinitialize Algorithm~3 by the solution at the previous point, then perform the optimization again.
-For a tolerance of $\epsilon=10^{-8}$, Algorithm~1--5 typically converge within 2, 7, 2, 2, 3 iterations, respectively.
+If a point is strictly dominated, we discard the candidate, reinitialize Algorithm~\ref{M-al:bcd} and \ref{M-al:lc_bcd} by the solution at the previous point, then perform the optimization again.
+For a tolerance of $\epsilon=10^{-8}$, Algorithm~\ref{M-al:sca}--\ref{M-al:lc_bcd} typically converge within 2, 7, 3, 2, 3 iterations, respectively.
 
@@
 		\begin{response}
-			Problem (26) is not a Semidefinite Programming (SDP) due to the squared term in the objective function.
-Hence, existing complexity analysis tools cannot be direct applied to Algorithm~1 and 4.
-For Algorithm~2, the computational complexity scales exponentially with the number of subbands [36,41] but an analytical expression cannot be derived on top of relevant literatures.
+			Problem \eqref{M-op:irs} is not a Semidefinite Programming (SDP) due to the squared term in the objective function.
+Hence, existing complexity analysis tools cannot be direct applied to Algorithm~\ref{M-al:sca} and \ref{M-al:m_sca}.
+For Algorithm~\ref{M-al:gp}, the computational complexity scales exponentially with the number of subbands \cite{M-Huang2017,M-Chiang2005} but an analytical expression cannot be derived on top of relevant literatures.
 To facilitate practical SWIPT implementation and address the reviewer's comment, we have added in the revised manuscript two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
@@
 			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation [42] and the details are omitted here.
-On the other hand, SMF was proposed in [12] as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
+The closed-form solution can be obtained by iterative power allocation \cite{M-Tse2005} and the details are omitted here.
+On the other hand, SMF was proposed in \cite{M-Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
 			\begin{equation}\label{eq:smf}
@@
 			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
-To achieve the WIT point ($\eta=\rho=0$), the achievable rate (19) instead of the DC current (25) should be maximized.
-To achievable non-WIT points, the rate constraint (26b) should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
-Algorithm~\ref{al:m-sca} summarizes the modified passive beamforming design for low-complexity PS mode.
-The tightness of rank relaxation and local optimality can be proved similar to Proposition~1 and 2, and the details are omitted here.
-
-			Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD algorithm achieves near-optimal performance under different configurations.
+To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
+To achievable non-WIT points, the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
+Algorithm~\ref{M-al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode.
+The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{M-pr:relaxation} and \ref{M-pr:sca}, and the details are omitted here.
+Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations.
 
@@
 		\begin{response}
-			The assumption of lossless reflection is indeed ideal, but similar models are widely considered in microwave theory (e.g., \cite{Shen2020a}).
-Based on the circuit analysis, the authors of [24] shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance.
-For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} at a phase shift of $\pi$ but around \num{0.6} at a phase shift of \num{0}.
+			The assumption of lossless reflection is indeed ideal but common in microwave theory (e.g., \cite{Shen2020a}).
+Based on the circuit analysis, the authors of \cite{M-Abeywickrama2019} shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance.
+For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} for $\theta_l=\pi$ but around \num{0.6} for $\theta_l=\num{0}$.
 From the perspective of field and propagation, \cite{Ozdogan2020} points out that if the dimension of IRS element is much larger than the wavelength, the beamwidth would become small and the scattered field strength would depend on the observation angle.
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E boundary points, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E tradeoff, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}
@@
 			Authors assumed the unrealistic situation: the channels are assumed to be perfectly known.
-However, in practice, the channel should be estimated, e.g., as studied in \cite{Kang2020}, \cite{You2019}.
+However, in practice, the channel should be estimated, e.g., as studied in \cite{You2019,Kang2020}.
 It would be much better to discuss the channel estimation issue by citing the above references.
@@
 The reviewer is referred to Response \ref{re:1.1} for details.
-Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed joint waveform, active and passive beamforming algorithm to cascaded CSIT inaccuracy for broadband SWIPT with different number of IRS elements.
+Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed joint waveform, active and passive beamforming algorithm to cascaded CSIT inaccuracy with different number of IRS elements.
 			\label{re:3.4}
@@
 			Thank you for the suggestion.
-On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD algorithm.
-Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD algorithm achieves near-optimal performance under different configurations.
-Moreover, we have investigated the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization}.
-It can be concluded that the proposed algorithms are robust to CSIT inaccuracy of the AP-IRS-UE link, and even $b=1$ (i.e.
+On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD Algorithm~\ref{M-al:bcd}.
+Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations.
+Moreover, we have investigated in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization} the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region.
+It can be concluded that the proposed algorithms are robust to CSIT inaccuracy of the cascaded link, and even $b=1$ (i.e.
 two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS.

### 2021-04-24 main.tex
:pencil: Update manuscript

@@
 This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS.
-Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This non-convex problem is then solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique.
-Since the computational complexity of the GP algorithm scales exponentially with the number of subbands, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation.
+Considering energy harvester nonlinearity and practical receiving modes, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
+This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique.
+Since the computational complexity of the GP algorithm scales exponentially with the number of carriers, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation.
 Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states.
-Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming design.
+Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
 	\end{abstract}
@@
             The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-localized information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
+\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
 Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
@@
 However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model.
-Motivated by this, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS in this paper.
+Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
+In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS.
 We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
@@
 The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
-To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
+To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the combining and splitting ratios for PS.
 The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
@@
 
-			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, transceiving modes, rectifier nonlinearity and R-E tradeoff.
+			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, receiving modes, rectifier nonlinearity and R-E tradeoff.
 Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization.
@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the CSIT of AP-UE direct channel and AP-IRS-UE cascaded channel are known.
+We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels are known.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
@@
 			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the commonest and simplest IRS model where the reflection amplitude is always assumed unit to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
+This paper sticks to the most common and simplest IRS model where the reflection amplitude is always assumed equal to \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
 We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
@@
 Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is incomparable to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
+In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
 			\end{remark}
@@
 			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
+The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
 Hence, the composite equivalent channel reduces to
@@
 				The cascaded channel response varies at different frequencies.
-Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary channel control in the frequency domain.
+Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain.
 Moreover, each IRS element simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
@@
 
-		\begin{subsection}{Transceiving Modes}
-			TS and PS were proposed in \cite{Zhou2013} as two practical transceiving modes for co-located SWIPT.
-TS heavily relies on clock synchronization.
-The transmitter divides each slot into a data session with length $1 - \eta$ and an energy session with length $\eta$, then designs the waveform for Wireless Information Transfer (WIT) and WPT independently.
-At the receiver, only the information decoder or energy harvester is activated in the corresponding session.
-Varying $\eta$ from \num{0} to \num{1} draws a R-E segment from the WIT point to the WPT point.
-On the other hand, the PS waveform consists of modulated and multisine components, and the receiver splits the incoming signal into an individual data stream with power ratio $1 - \rho$ and an energy stream with power ratio $\rho$.
-Note that the splitting ratio $\rho$ and the superposed waveform require a joint optimization for PS, but the duration ratio $\eta$ is irrelevant to the waveform design in both sessions for TS.
-Therefore, we focus on PS in the following context as TS can be regarded as a time sharing between $\rho=0$ (WIT) and $\rho=1$ (WPT).
+		\begin{subsection}{Receiving Modes}
+			As illustrated in Fig.TODO, there are two practical schemes \cite{Zhou2013} for the co-located information decoder and energy harvester to utilize the superposed signal.
+The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
+During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver actives the information decoder or the energy harvester correspondingly.
+Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point.
+On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
+The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
+In the following context, we focus on the analysis over the PS receiver because the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
-In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
+In contrast, the low-complexity PS scheme jointly designs the combining ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
 			\begin{align}
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
-Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depend on the number of subbands.
+Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
 
@@
 \emph{First,} adding either active or passive elements enhances the equivalent channel strength to boost both information and power transfer.
-Interestingly, it has negligible influence on the optimal transceiving strategy because the rate and current are proportionally amplified that preserves the general trend of the R-E boundary.
+Interestingly, it has negligible influence on the optimal receiving mode because the rate and current are proportionally amplified that preserves the general trend of the R-E boundary.
 \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
@@
 \emph{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary channels can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary links can be roughly maximized at all subbands.
+It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary link with the direct channel) when a single transmit antenna is used at the AP.
 On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain.
@@
 		This paper investigated the R-E tradeoff of a single user in a novel IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity and practical transceiving strategies to maximize the achievable R-E region.
+Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity and practical receiving modes to maximize the achievable R-E region.
 A three-stage BCD algorithm is proposed to solve the problem.

### 2021-04-25 main.tex
:pencil: Update manuscript

@@
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and obtain the IRS phase shift by eigen decomposition with optimality proof.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
@@
 		\begin{subsection}{Receiving Modes}
-			As illustrated in Fig.TODO, there are two practical schemes \cite{Zhou2013} for the co-located information decoder and energy harvester to utilize the superposed signal.
+			\begin{figure}[!t]
+				\centering
+				\subfloat[TS receiver\label{fi:ts_receiver}]{
+					\resizebox{0.9\columnwidth}{!}{
+						\centering
+						\begin{circuitikz}[transform shape]
+							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
+								to[short,-o] ++(0,-1) node[below]{Time Switcher}
+								to[short] node[spdt,anchor=in](s){} ++(0.5,0);
+
+							\draw (s.out 1) node[above right]{$1-\eta$}
+								to ++(1.25,0)
+								to ++(0,0.5)
+								to ++(1,0)
+								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
+
+							\draw (s.out 2) node[below right]{$\eta$}
+								to ++(1.25,0)
+								to ++(0,-0.5)
+								to ++(1,0)
+								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
+						\end{circuitikz}
+					}
+				}
+				\\
+				\subfloat[PS receiver\label{fi:ps_receiver}]{
+					\resizebox{0.9\columnwidth}{!}{
+						\begin{circuitikz}[transform shape]
+							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
+								to[short,-o] ++(0,-1)
+								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
+							\draw (c.right up)
+								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
+								to ++(0,0.5)
+								to ++(1,0)
+								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
+							\draw (c.right down)
+								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
+								to ++(0,-0.5)
+								to ++(1,0)
+								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
+						\end{circuitikz}
+					}
+				}
+				\caption{Practical co-located receiving modes.}
+				\label{fi:receiver}
+			\end{figure}
+
+			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes \cite{Zhou2013} for the co-located information decoder and energy harvester to utilize the superposed signal.
 The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
@@
 				\centering
-				\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
+				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-				\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
+				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-			In this section, we briefly revisit a tractable nonlinear rectenna model that relates the harvester output DC current to the received signal.
-Fig.~\ref{ci:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
+			Importantly the rectenna model used in this section, taken from \cite{Clerckx2016a}, captures the dependency of the output DC current on both the power and shape of the received signal.
+This is critical for efficient signal designs in WPT and SWIPT \cite{Clerckx2021}.
+Fig.~\ref{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
 Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
@@
 			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
-Consider a simplified rectifier model in Fig.~\ref{ci:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
 As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
@@
 			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
+			where the scaling ratio $\alpha \ge 1$ is assumed known and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity.
 In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
@@
 
-			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
+			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform power allocation schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achievable any non-WIT point (i.e., with non-zero DC current), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
 Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode.
@@
 			}
-			\subfloat[Path loss\label{fi:path_loss}]{
+			\subfloat[Path loss product\label{fi:path_loss}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
-\emph{First,} adding either active or passive elements enhances the equivalent channel strength to boost both information and power transfer.
-Interestingly, it has negligible influence on the optimal receiving mode because the rate and current are proportionally amplified that preserves the general trend of the R-E boundary.
+\emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
 \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
@@
 As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the sine wave at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
-For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power.
-Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that suggests an active scaling law in the order of $M^2$.
-On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB} that implies a reflect array gain of $L^2$.
+For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ and a doubled harvester input power.
+Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which suggests an active scaling law in the order of $M^2$.
+On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-Hence, doubling IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
+Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
 Compared with active antennas, the IRS achieves higher array gain and power scaling order using passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-Moreover, the ASS strategy exploits no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap with SMF and GP.
-These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.
+Moreover, the ASS strategy does not exploit the harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
+These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.
 
@@
 The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
-The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., the boundary is obtained by varying the waveform amplitude and splitting ratio).
+The adaptive IRS adjusts the passive beamforming by Algorithm~\ref{al:sca} under different rate constraints, and the WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only update the waveform amplitude and splitting ratio).
+Random IRS means the phase shift of all elements are modelled as i.i.d.
+uniform random variables over $[0, 2\pi)$.
 \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over channel realizations.
-\emph{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary links can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary link with the direct channel) when a single transmit antenna is used at the AP.
+Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations.
+\emph{Second,} the performance of ideal, adaptive and fixed IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
+It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is close to optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary link with the direct channel) when a single transmit antenna is used at the AP.
 On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain.
-By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
+By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
 It emphasizes the R-E advantage of adaptive passive beamforming Algorithm~\ref{al:sca} for broadband SWIPT.
@@
 A three-stage BCD algorithm is proposed to solve the problem.
-In the first stage, the IRS phase shift is obtained by combining the SCA technique with a relax-then-extract step.
+In the first stage, the IRS phase shift is obtained by combining the SCA technique with eigen decomposition.
 In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude is optimized by the reversed GP method.
@@
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, practical IRS patterns with direction- and frequency-dependent reflection could be considered in future works.
+Also, the use of more involved IRS architecture based on partially/fully-connected and/or direction- and frequency-dependent reflection could be considered in future works.
 	\end{section}

### 2021-04-26 main.tex
:pencil: Update manuscript

@@
 To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency.
-This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS.
-Considering energy harvester nonlinearity and practical receiving modes, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
+This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) under practical receiving schemes.
+Considering energy harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
 This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique.
@@
 			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic waves in the Radio-Frequency (RF) band.
+Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via Radio-Frequency (RF) waves.
 It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
@@
 In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming).
-Different from the relay, backscatter, and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.
+Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.
 
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
 For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
@@
 			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes.
 The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
@@
 
-			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and obtain the IRS phase shift by eigen decomposition with optimality proof.
+			\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
@@
 			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
-To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the combining and splitting ratios for PS.
-The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
+The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time domain and power domain to facilitate practical SWIPT implementation.
+To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode.
+The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.
 
@@
 
-			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, receiving modes, rectifier nonlinearity and R-E tradeoff.
-Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization.
-Section~\ref{se:performance_evaluation} evaluates the proposed algorithms by simulation results.
+			\emph{Organization:} Section~\ref{se:system_model} introduces the system model.
+Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design.
+Section~\ref{se:performance_evaluation} provides simulation results.
 Section~\ref{se:conclusion_and_future_works} concludes the paper.
@@
 $\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices.
+$\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices.
 $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector that retrieves the main diagonal of the input matrix.
+$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
 $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
 $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-$\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity).
+$\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t.
+random variable $X$ ($X$ is omitted for simplicity).
 The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
 $\sim$ means ``distributed as''.
-$(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
+$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
 		\end{subsection}
@@
 			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
+The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
 IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
@@
 			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common and simplest IRS model where the reflection amplitude is always assumed equal to \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.
+This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.
 
@@
 			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel response varies at different frequencies.
-Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain.
-Moreover, each IRS element simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
+				The cascaded channel varies at different frequencies.
+Since we regard the reflection as frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain.
+Moreover, the IRS simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
 			\end{remark}
@@
 			\end{align}
-			capture the contribution of modulated and multisine waveforms over all subbands.
-Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
+			capture respectively the modulated and multisine components.
+Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
 		\end{subsection}
@@
 
-			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes \cite{Zhou2013} for the co-located information decoder and energy harvester to utilize the superposed signal.
+			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes for the co-located information decoder and energy harvester \cite{Zhou2013} to utilize the superposed signal.
 The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
-During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver actives the information decoder or the energy harvester correspondingly.
+During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
 Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point.
@@
 During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
-In the following context, we focus on the analysis over the PS receiver because the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+In the following context, we focus on the analysis over the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 			\end{equation}
-			where $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$.
-Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
+			where $\sigma_n^2$ is the variance of the noise at RF-band and during RF-to-baseband conversion on tone $n$.
+Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
 		\end{subsection}
@@
 Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
 Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
@@
 		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a suboptimal BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 
-			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real and we have
+			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real.
+Due to symmetry, we have
 
@@
 			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
-Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP \cite{Luo2010} to formulate a convex problem~\eqref{ob:irs}--\eqref{co:irs_sd}.
+The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it \cite{Luo2010} to formulate a convex problem.
 The tightness of rank relaxation is verified below.
@@
 
-			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}, and $\boldsymbol{\Phi}^{(i)}$ is updated until convergence.
-We then extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition and retrieve the phase shift of element $l$ by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
-The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
+			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+We update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
+The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}.
 			\begin{algorithm}[!t]
@@
 			\begin{proposition}\label{pr:sca}
-				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal phase shifts of the original problem~\eqref{op:original}.
+				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
 			\end{proposition}
@@
 
-			Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
+			% Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
 		\end{subsection}
@@
 			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-With the MRT precoder \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$.
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
 Hence, the rate \eqref{eq:R} reduces to
@@
 			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$ that needs successive update, and a feasible choice at iteration $i$ is
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
 			\begin{align}
@@
 
-			On top of \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
-$\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ are updated iteratively until convergence.
-The GP algorithm of joint waveform amplitude and splitting ratio optimization is summarized in Algorithm~\ref{al:gp}.
+			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
+The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}.
 			\begin{algorithm}[!t]
@@
 
-		\begin{subsection}{Block Coordinate Descent}
-			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The BCD algorithm is summarized in Algorithm~\ref{al:bcd}.
-			\begin{algorithm}[!t]
-				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
-				\label{al:bcd}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
-					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{proposition}\label{pr:bcd}
-				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:bcd}
-				See Appendix~\ref{ap:bcd}
-			\end{proof}
-		\end{subsection}
-
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			The GP Algorithm~\ref{al:gp} achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
-To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF under TS and PS setups.
-The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
+			The GP Algorithm~\ref{al:gp} achieves local optimality with exponential computational complexity \cite{Chiang2005}.
+To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time domain and power domain.
+For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
 			\begin{equation}\label{eq:wf}
@@
 			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ is assumed known and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity.
-In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
-In contrast, the low-complexity PS scheme jointly designs the combining ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
+			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity.
+When the receiver works in TS mode, there is no superposition in the suboptimal waveform design.
+Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session.
+When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
 			\begin{align}
@@
 
-			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform power allocation schemes.
+			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achievable any non-WIT point (i.e., with non-zero DC current), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
-Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode.
-The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca}, and the details are omitted here.
+To achievable any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+The M-SCA Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
+The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.
 
 			\begin{algorithm}[!t]
-				\caption{Modified: IRS Phase Shift.}
+				\caption{M-SCA: IRS Phase Shift.}
 				\label{al:m_sca}
@@
 			\end{algorithm}
-
-			On top of the closed-form waveform schemes and the modified passive beamforming strategy, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively updates the phase shift $\boldsymbol{\phi}$ by Algorithm~\ref{al:m_sca}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
-The LC-BCD algorithm for PS mode is summarized in Algorithm~\ref{al:lc_bcd}.
+		\end{subsection}
+
+		\begin{subsection}{Block Coordinate Descent}
+			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+The steps are summarized in the BCD Algorithm~\ref{al:bcd}.
+For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+The steps are summarized in the Low-Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+			\begin{algorithm}[!t]
+				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
+				\label{al:bcd}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
+					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\Repeat
+						\State $i \gets i + 1$
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
 
@@
 			\end{algorithm}
+
+			\begin{proposition}\label{pr:bcd}
+				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
+			\end{proposition}
+
+			\begin{proof}\label{pf:bcd}
+				See Appendix~\ref{ap:bcd}
+			\end{proof}
 		\end{subsection}
@@
 
-			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
+			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
+$\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
 The corresponding Lagrangian function at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.

### 2021-04-27 response.tex
:pencil: Update response letter

@@
 \usepackage{adjustbox}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{amsfonts}
@@
 	{T\arabic{table}}
+
+\renewcommand{\thealgorithm}
+	{A\arabic{algorithm}}
 
@@
 To prove the rank-\num{1} property of the IRS matrix $\boldsymbol{\Phi}$, we notice that for any feasible $\boldsymbol{\Phi}$ to problem~\eqref{M-op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{M-co:irs_modulus}.
-Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{M-ob:irs} and formulate an equivalent problem as
+Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{M-ob:irs} and recast problem~\eqref{M-op:irs} as
 			\begin{maxi!}
@@
 \eqref{M-co:irs_rate}--\eqref{M-co:irs_rank}).
-Also, \eqref{M-eq:coupled_terms} holds due to symmetrical summation.
+Also, \eqref{M-eq:coupled_terms} holds due to symmetry.
 Hence, the quadratic objective function \eqref{M-eq:z_irs_approx} is obtained by plugging \eqref{M-eq:taylor_1}--\eqref{M-eq:coupled_terms} into \eqref{M-eq:z_irs}.
@@
 		\begin{response}
-			Algorithm~\ref{M-al:sca}--\ref{M-al:lc_bcd} provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
+			Algorithm~\ref{M-al:sca}--\ref{M-al:bcd} provide local optimal solutions with local convergence proof, and the performance indeed depends on the initialization.
 For the passive beamforming Algorithm~\ref{M-al:sca} and \ref{M-al:m_sca}, we initialize the phase shift of all IRS elements as i.i.d.
@@
 These parameters are used for general initialization and regulated automatically afterwards.
-However, as Algorithm~\ref{M-al:bcd} and \ref{M-al:lc_bcd} only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
+However, as Algorithm~\ref{M-al:sca}, \ref{M-al:gp} and \ref{M-al:m_sca} only converge to local optimal solutions, few R-E points might be strictly worse (with less rate and energy) than the others especially when $N$ is very large.
 To address this issue, we draw the R-E boundary from the high-rate low-energy (lower right) points to the low-rate high-energy (upper left) points.
@@
 For Algorithm~\ref{M-al:gp}, the computational complexity scales exponentially with the number of subbands \cite{M-Huang2017,M-Chiang2005} but an analytical expression cannot be derived on top of relevant literatures.
-To facilitate practical SWIPT implementation and address the reviewer's comment, we have added in the revised manuscript two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups.
-The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
+To facilitate practical SWIPT implementation and address the reviewer's comment, we have added in the revised manuscript two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains.
+For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
 			\begin{equation}\label{eq:wf}
-				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
 			\end{equation}
-			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation \cite{M-Tse2005} and the details are omitted here.
+			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+The closed-form solution can be obtained by iterative power allocation \cite{M-Tse2005}, and the details are omitted here.
 On the other hand, SMF was proposed in \cite{M-Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
@@
 			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity.
-In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session.
-In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
+			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity.
+When the receiver works in TS mode, there is no superposition in the suboptimal waveform design.
+Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session.
+When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
 			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
+				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
 				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
@@
 
-			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes.
+			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
 To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
-To achievable non-WIT points, the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$.
-Algorithm~\ref{M-al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode.
-The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{M-pr:relaxation} and \ref{M-pr:sca}, and the details are omitted here.
-Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations.
+To achievable any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
+The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{M-pr:relaxation} and \ref{M-pr:sca} thus omitted here.
+			\begin{algorithm}[!h]
+				\caption{M-SCA: IRS Phase Shift.}
+				\label{al:m_sca}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+					\If{$\rho=0$}
+						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{M-eq:R_irs} s.t. \eqref{M-co:irs_modulus}, \eqref{M-co:irs_sd}
+					\Else
+						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{M-eq:t_k}
+						\Repeat
+							\State $i \gets i + 1$
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{M-eq:z_irs_approx} s.t. \eqref{M-co:irs_modulus}, \eqref{M-co:irs_sd}
+								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{M-eq:t_k}
+								\State Compute $z^{(i)}$ by \eqref{M-eq:z_irs}
+						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
+					\EndIf
+					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
+					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
+			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+			\begin{algorithm}[!h]
+				\caption{LC-BCD: Waveform and Beamforming.}
+				\label{al:lc_bcd}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{M-eq:w}
+					\Repeat
+						\State $i \gets i + 1$
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
+						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
+						\State Compute $R^{(i)},z^{(i)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
+					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
+			Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{al:lc_bcd} achieves near-optimal performance under different configurations.
 
@@
 
-			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible.
+			\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
+For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
 Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
@@
 			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation.
-To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS.
-The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.
+The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time domain and power domain to facilitate practical SWIPT implementation.
+To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode.
+The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.
 
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E tradeoff, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on the R-E tradeoff and require adaptive design, 8) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}
@@
 			Thank you for the suggestion.
-On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD Algorithm~\ref{M-al:bcd}.
-Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations.
+On top of the previous version, we have introduced two closed-form adaptive waveform design and compared the results with the original BCD Algorithm~\ref{M-al:bcd}.
+Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{al:lc_bcd} achieves near-optimal performance under different configurations.
 Moreover, we have investigated in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization} the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region.

### 2021-04-27 main.tex
:pencil: Update manuscript

@@
 To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency.
-This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) under practical receiving schemes.
+This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes.
 Considering energy harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E tradeoff, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on the R-E tradeoff and require adaptive design, 8) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.
+We also define respectively $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.
 
@@
 During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
-In the following context, we focus on the analysis over the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+In the following context, we focus on the analysis with the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper.
-It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
 However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
@@
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current.
-Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms.
+Moreover, we define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
@@
 
-			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real.
-Due to symmetry, we have
+			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
+Due to symmetry \cite{Huang2017}, we have
 
 			\begin{equation}\label{eq:coupled_terms}
-				\sum_{k=-N+1}^{N-1} \Re\left\{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} 2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*
+				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
 			\end{equation}
@@
 			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
-The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it \cite{Luo2010} to formulate a convex problem.
+The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it to formulate a convex problem \cite{Luo2010}.
 The tightness of rank relaxation is verified below.
@@
 			\begin{proposition}\label{pr:relaxation}
-				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
+				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
 			\end{proposition}
@@
 			\end{proof}
-
-			% Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
 		\end{subsection}
@@
 			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
-Hence, the rate \eqref{eq:R} reduces to
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ such that the rate \eqref{eq:R} reduces to
 			\begin{equation}\label{eq:R_waveform}
@@
 			\end{equation}
-			and the DC current \eqref{eq:z_expand} reduces to \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+			and the DC current \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
-				\hrule
 				\begin{align}
@@
 			The GP Algorithm~\ref{al:gp} achieves local optimality with exponential computational complexity \cite{Chiang2005}.
-To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time domain and power domain.
+To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains.
 For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
 			\begin{equation}\label{eq:wf}
-				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
-			\end{equation}
-			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+			\end{equation}
+			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
 The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
@@
 			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
+				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
 				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
@@
 To achievable any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
-The M-SCA Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
+The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
 The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.
@@
 For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-The steps are summarized in the Low-Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
 			\begin{algorithm}[!t]
@@
 This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT.
-As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the sine wave at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
+As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
 For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ and a doubled harvester input power.
@@
 Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
-Compared with active antennas, the IRS achieves higher array gain and power scaling order using passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
 Moreover, the ASS strategy does not exploit the harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
@@
 The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
-The adaptive IRS adjusts the passive beamforming by Algorithm~\ref{al:sca} under different rate constraints, and the WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only update the waveform amplitude and splitting ratio).
-Random IRS means the phase shift of all elements are modelled as i.i.d.
+The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only update the waveform amplitude and splitting ratio).
+The random IRS models the phase shift of all elements as i.i.d.
 uniform random variables over $[0, 2\pi)$.
@@
 Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations.
-\emph{Second,} the performance of ideal, adaptive and fixed IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
+\emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is close to optimal for the whole R-E region, which can be approximated in closed form (by aligning the auxiliary link with the direct channel) when a single transmit antenna is used at the AP.
-On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain.
+It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
+On the other hand, since the information decoder and energy harvester prefer different channel strength distribution in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
 By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
-It emphasizes the R-E advantage of adaptive passive beamforming Algorithm~\ref{al:sca} for broadband SWIPT.
+It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.
 
@@
 Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
 Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper investigated the R-E tradeoff of a single user in a novel IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity and practical receiving modes to maximize the achievable R-E region.
+		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in a novel IRS-aided multi-carrier MISO SWIPT system.
+Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
 A three-stage BCD algorithm is proposed to solve the problem.
-In the first stage, the IRS phase shift is obtained by combining the SCA technique with eigen decomposition.
-In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude is optimized by the reversed GP method.
+In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition.
+In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method.
 We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance.
 Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
-Compared with active antennas, IRS elements are limited to frequency-dependent reflection but able to integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
+Compared with active antennas, IRS elements cannot provide frequency-independent reflection can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
 However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.
@@
 			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{co:irs_modulus}.
-Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and formulate an equivalent problem as
+Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and recast problem~\eqref{op:irs} as
 			\begin{maxi!}
@@
 $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
-The corresponding Lagrangian function at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
+The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
 			\begin{figure*}[!b]
@@
 						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta,&&
+					\Bigr) + \zeta.&&
 				\end{flalign}
@@
 			\end{figure*}
-
 			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
@@
 On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.
-Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$.
+Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}.
 Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
@@
 Therefore, Algorithm~\ref{al:bcd} is guaranteed to converge.
-Since the IRS phase shift retrieved by Algorithm~\ref{al:sca} is local optimal, the active precoder obtained by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio returned by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
+Since the IRS phase shift by Algorithm~\ref{al:sca} is local optimal, the active precoder by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
 		\end{subsection}

### 2021-04-28 response.tex
:pencil: Update response letter

@@
 
-			\emph{Third}, multi-user WPT leads to its own set of challenges compared single-user WPT.
+			\emph{Third}, multi-user WPT leads to its own set of challenges compared with single-user WPT.
 Taking an non-IRS-aided WPT, frequency and spatial domains can be decoupled in single-user case, while they cannot be decoupled in the multi-user case, as shown in \cite{M-Clerckx2016a,M-Huang2017}.
@@
 There exist various refined models of IRS in the literature, however, we have finally decided to use the most common and simplest IRS model at the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
+We have mentioned in the conclusion that ``Also, the use of more involved IRS architecture based on partially/fully connected and/or direction- and frequency-dependent reflection could be considered in future works.''
 			\label{re:2.1}
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
-To achievable any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achieve the WIT point ($\eta=\rho=0$), the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
+To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 			We appreciate your suggestion and have modified the manuscript to emphasize this point.
-Both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+The major issue of WPT and SWIPT is the low harvested DC power.
+To increase it, boosting the harvester input power level would be very helpful.
+This is achieved by the help of IRS.
+Indeed, both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal.
@@
 To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, a beamforming gain, and the channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
 This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on the R-E tradeoff and require adaptive design, 8) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}
@@
 		\begin{response}
-			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance.
+			We have added those references and considered the influence of imperfect cascaded CSIT on the R-E performance.
 The reviewer is referred to Response \ref{re:1.1} for details.
@@
 			Thank you for the suggestion.
-On top of the previous version, we have introduced two closed-form adaptive waveform design and compared the results with the original BCD Algorithm~\ref{M-al:bcd}.
+To address this comment, we have introduced two closed-form adaptive waveform design and compared the results with the original BCD Algorithm~\ref{M-al:bcd}.
 Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{al:lc_bcd} achieves near-optimal performance under different configurations.

### 2021-04-28 main.tex
:pencil: Update manuscript

@@
 Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states.
-Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
+Results also emphasize the importance of accounting for harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
 	\end{abstract}
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on the R-E tradeoff and require adaptive design, 8) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achievable any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achieve the WIT point ($\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only update the waveform amplitude and splitting ratio).
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only vary the waveform amplitude and splitting ratio).
 The random IRS models the phase shift of all elements as i.i.d.
@@
 It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-On the other hand, since the information decoder and energy harvester prefer different channel strength distribution in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
+On the other hand, since the information decoder and energy harvester prefer different power allocation in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
 By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
@@
 Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
-Compared with active antennas, IRS elements cannot provide frequency-independent reflection can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
+Compared with active antennas, IRS elements cannot be designed independently at different frequencies but integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
 However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.

### 2021-04-28 response.tex
:pencil: Update response letter

@@
 		\begin{point}
-			New RIS models are now being adopted as in \cite{M-Abeywickrama2019} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
+			New RIS models are now being adopted as in \cite{M-Abeywickrama2020} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
 			\label{pt:2.1}
@@
 There exist various refined models of IRS in the literature, however, we have finally decided to use the most common and simplest IRS model at the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.
-We have mentioned in the conclusion that ``Also, the use of more involved IRS architecture based on partially/fully connected and/or direction- and frequency-dependent reflection could be considered in future works.''
+We have mentioned in the conclusion that ``Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{M-Abeywickrama2020} and/or partially/fully-connected reflection \cite{M-Shen2020a} could be considered in future works.''
 			\label{re:2.1}
@@
 			The assumption of lossless reflection is indeed ideal but common in microwave theory (e.g., \cite{Shen2020a}).
-Based on the circuit analysis, the authors of \cite{M-Abeywickrama2019} shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance.
+Based on the circuit analysis, the authors of \cite{M-Abeywickrama2020} shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance.
 For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} for $\theta_l=\pi$ but around \num{0.6} for $\theta_l=\num{0}$.
@@
 To increase it, boosting the harvester input power level would be very helpful.
-This is achieved by the help of IRS.
-Indeed, both SWIPT and IRS aim to achieve spectrum and energy efficient communication, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+This is achieved by the IRS that can engineer the channels such that the power level at the receiver gets amplified, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal.
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 			\label{re:3.2}

### 2021-04-28 main.tex
:pencil: Update manuscript

@@
 The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
+In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
 To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-On the other hand, since the information decoder and energy harvester prefer different power allocation in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
+On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
 By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
@@
 Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
-Compared with active antennas, IRS elements cannot be designed independently at different frequencies but integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
+Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
 However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.
@@
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, the use of more involved IRS architecture based on partially/fully-connected and/or direction- and frequency-dependent reflection could be considered in future works.
+Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
 	\end{section}
@@
 			\end{subequations}
-
 			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as

### 2021-04-28 response.tex
:triangular_flag_on_post: arXiv and TCom 280421

@@
 			\end{subequations}
+
 			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
@@
 			\end{align}
+
 			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point ($\eta=\rho=0$), the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
+To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
 To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
@@
 To increase it, boosting the harvester input power level would be very helpful.
-This is achieved by the IRS that can engineer the channels such that the power level at the receiver gets amplified, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
+This is achieved by the IRS that can engineer the channels such that the power level at the receiver gets amplified.
+The smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT.
 A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal.
@@
 			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time domain and power domain to facilitate practical SWIPT implementation.
+The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time and power domains to facilitate practical SWIPT implementation.
 To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode.

### 2021-04-28 main.tex
:triangular_flag_on_post: arXiv and TCom 280421

--- 2021-04-28 main.tex
@@
 This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes.
-Considering energy harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique.
-Since the computational complexity of the GP algorithm scales exponentially with the number of carriers, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation.
-Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states.
-Results also emphasize the importance of accounting for harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
+Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
+This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique.
+To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes.
+Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states.
+Results also emphasize the importance of modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
 	\end{abstract}
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
+			The major issue of WPT and SWIPT is the low harvested DC power.
+To increase it, we introduce an IRS that enhances the end-to-end energy efficiency and boosts the harvester input power level.
+The smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
 For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
@@
 			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances.
+The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
 IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
@@
 Since we regard the reflection as frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain.
-Moreover, the IRS simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
+Moreover, each IRS element simultaneously assists all transmit antennas such that the reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
 			\end{remark}
@@
 During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
-In the following context, we focus on the analysis with the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+In the following context, we consider the analysis based on the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ such that the rate \eqref{eq:R} reduces to
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the rate \eqref{eq:R} reduces to
 			\begin{equation}\label{eq:R_waveform}
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point ($\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
 To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
@@
 The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}.
-For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
+For the algorithms, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
-As $\bar{R}$ further decreases, due to the advantage of multisine, a modulated waveform with a very large $\rho$ is outperformed by a superposed waveform with a smaller $\rho$.
+As $\bar{R}$ further decreases, due to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
@@
 
-		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
+		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
 \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
@@
 The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only vary the waveform amplitude and splitting ratio).
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region.
 The random IRS models the phase shift of all elements as i.i.d.
@@
 Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations.
-\emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large.
+\emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS when the bandwidth is large.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
 It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-On the other hand, since the information decoder and energy harvester prefer different power allocation in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT.
-By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
+Hence, the achievable R-E region is obtained by varying the waveform amplitude and splitting ratio.
+On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoff points for broadband SWIPT.
+By adaptive passive beamforming, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
 It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.
@@
 
-		We then explore the impact of imperfect cascaded CSIT and quantized IRS on the R-E performance.
+		We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance.
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
@@
 Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$.
-Note that the estimations at different subbands are independent, but the subchannel responses are correlated.
+Note that the estimations at different subbands are independent, but the subchannel responses are indeed correlated.
 Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
@@
 Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage BCD algorithm is proposed to solve the problem.
+A three-stage local optimal BCD algorithm is proposed to solve the problem.
 In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition.
 In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method.
-We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance.
-Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design.
-Compared with active antennas, IRS elements cannot be designed independently at different frequencies but integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
+We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance in different scenarios.
+Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
+Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
 However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.

### 2021-04-29 main.tex
:triangular_flag_on_post: arXiv and TCom 290421

@@
 \usepackage[short]{optidef}
+\usepackage[subtle]{savetrees}
 
@@
 $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices.
-$\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity.
+$\Re\{\cdot\}$ retrieves the real part of a complex entity.
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
@@
 Due to symmetry \cite{Huang2017}, we have
-
 			\begin{equation}\label{eq:coupled_terms}
@@
 		\end{figure}
+
 		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
@@
 The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}.
-For the algorithms, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
+Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 			\end{equation}
-			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
+			where $\boldsymbol{\Delta}^\star$ is given by \eqref{eq:delta}.
 			\begin{figure*}[!b]

### 2021-05-08 main.tex
:art: Update layout

@@
 \usepackage{array}
-% \usepackage{caption}
 \usepackage{cite}
@@
 $\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices.
+$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real nonnegative and complex $x \times y$ matrices.
 $\Re\{\cdot\}$ retrieves the real part of a complex entity.
@@
 $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
+$\odot$ denotes the Hadamard product.
 $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
@@
 		\begin{subsection}{Received Signal}
-			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
+			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)+n(t)$, where
 			\begin{align}
@@
 			\end{align}
-			capture respectively the modulated and multisine components.
+			capture respectively the modulated and multisine components, and $n(t)$ is the noise at the RF-band.
 Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
@@
 						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
+							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
 								to[short,-o] ++(0,-1) node[below]{Time Switcher}
@@
 						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
+							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
 								to[short,-o] ++(0,-1)
@@
 			\end{equation}
-			where $\sigma_n^2$ is the variance of the noise at RF-band and during RF-to-baseband conversion on tone $n$.
+			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$.
 Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
@@
 As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
-			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
+			\begin{equation}\label{eq:I}
+				I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
 			\end{equation}
 			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper.
-It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+With a slight abuse of notation, we refer to $I$ as the average output DC current in this paper.
+It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:I} with $n_0=2$.
 However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
 In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $I$ by \eqref{eq:I_expand}.
 Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms.
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
+Hence, the components of $I$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
 
@@
 				\hrule
-				\begin{flalign}
-					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).&&\label{eq:z_expand}
-				\end{flalign}
-				\begin{flalign}
-					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
-					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
-					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
-				\end{flalign}
-				\begin{flalign}
-					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
-					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
-					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
-					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
-				\end{flalign}
+				\begin{align}
+					&I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:I_expand}\\
+					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+					&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+					&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+				\end{align}
 			\end{figure*}
@@
 			\begin{align}
-				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
+				\mathcal{C}_{\mathrm{R-E}}
+				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le I,\nonumber\\
 				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
@@
 		\begin{maxi!}
-			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
 			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
@@
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
+On top of this, \eqref{eq:R} and \eqref{eq:I_expand} reduce respectively to
 			\begin{align}
@@
 				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-				z(\boldsymbol{\Phi})
+				I(\boldsymbol{\Phi})
 				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
 				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
-			\end{align}
-
-			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:I_irs}
+			\end{align}
+
+			To maximize the non-concave expression \eqref{eq:I_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:I_irs}, we obtain the DC current approximation $\tilde{I}$ as \eqref{eq:I_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 				\begin{align}
-					\tilde{z}(\boldsymbol{\Phi}^{(i)})
+					\tilde{I}(\boldsymbol{\Phi}^{(i)})
 					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:I_irs_approx}
 				\end{align}
@@
 			\begin{maxi!}
-				{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+				{\boldsymbol{\Phi}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
@@
 			\end{maxi!}
-			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}.
+			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:I_irs_approx}.
 The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it to formulate a convex problem \cite{Luo2010}.
@@
 						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+						\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
+					\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
@@
 			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}^{N \times 1}$.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
 The MRT precoder at subband $n$ is given by
@@
 			\end{equation}
-			and the DC current \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+			and the DC current \eqref{eq:I_expand} rewrites as \eqref{eq:I_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
 				\begin{align}
-					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
+					I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
 					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).&&\label{eq:z_waveform}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:I_waveform}
 				\end{align}
@@
 			\begin{maxi!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
 				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
@@
 				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+				\addConstraint{\frac{t''}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
@@
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
+				I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
 			\end{align}
@@
 				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{I(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
 			\end{align}
@@
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
-					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Compute $R^{(0)},I^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
 					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
@@
 						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
 						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:I_irs_approx} should be maximized.
+To achieve any non-WIT point (i.e., $I \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 							\State $i \gets i + 1$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:I_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+								\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
+						\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
 						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
@@
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+						\State Compute $I^{(i)}$ by \eqref{eq:I_waveform}
+					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
@@
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
+					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
@@
 			\begin{maxi!}
-				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
+				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
@@
 				\hrule
-				\begin{flalign}\label{eq:lagrangian}
+				\begin{align}\label{eq:lagrangian}
 					\mathcal{L}
@@
 							\Bigr)
-							&&\nonumber\\
+							\nonumber\\
 					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
@@
 						\biggr)
-					\Biggr)&&\nonumber\\
+					\Biggr)\nonumber\\
 					&\quad+ \mathrm{tr}\biggl(
@@
 						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta.&&
-				\end{flalign}
+					\Bigr) + \zeta.
+				\end{align}
 			\end{figure*}
@@
 			\begin{figure*}[!b]
-				\begin{flalign}\label{eq:delta}
+				\begin{align}\label{eq:delta}
 					\boldsymbol{\Delta}^\star
@@
 						\Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
+							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})\nonumber\\
 					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
@@
 						\Bigr)}{\sigma_{n'}^2}
-					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
-				\end{flalign}
+					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).
+				\end{align}
 			\end{figure*}
@@
 			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+Also, the sequence $\{\tilde{I}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{I}(\boldsymbol{\Phi}) \le I(\boldsymbol{\Phi})$, $\partial\tilde{I}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial I(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.

### 2021-06-10 src/lib/irs_sdr.m
:zap: Improve SCA objective

@@ -101,7 +101,7 @@ function [irs, eigRatio] = irs_sdr(beta2, beta4, directChannel, cascadedChannel,
             % \tilde{z}
             currentSca = (1 / 2) * beta2 * powerRatio * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
                 + (3 / 8) * beta4 * powerRatio ^ 2 * (2 * (2 * infoAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) ^ 2) + 2 * real(powerAuxiliary_' * powerAuxiliary) - powerAuxiliary_' * powerAuxiliary_) ...
-                + (3 / 2) * beta4 * powerRatio ^ 2 * ((1 / 2) * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) * (infoAuxiliary_(nSubbands) + powerAuxiliary_(nSubbands)) - (1 / 4) * (infoAuxiliary_(nSubbands) + powerAuxiliary_(nSubbands)) ^ 2 - (1 / 4) * (infoAuxiliary(nSubbands) - powerAuxiliary(nSubbands)) ^ 2);
+                + (3 / 2) * beta4 * powerRatio ^ 2 * (infoAuxiliary(nSubbands) * powerAuxiliary_(nSubbands) + powerAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) * powerAuxiliary_(nSubbands));
             % \gamma
             for iSubband = 1 : nSubbands
                 snr(iSubband) = infoRatio * trace(rateMatrix{iSubband} * irsMatrix) / noisePower;

### 2021-06-10 src/lib/waveform_sdr.m

@@ -73,7 +73,7 @@ function [current, infoAmplitude, powerAmplitude] = waveform_sdr(beta2, beta4, c
             % \tilde{z}
             currentSca = (1 / 2) * beta2 * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) ...
                 + (3 / 8) * beta4 * (2 * (2 * infoAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) ^ 2) + 2 * real(powerAuxiliary_' * powerAuxiliary) - powerAuxiliary_' * powerAuxiliary_) ...
-                + (3 / 2) * beta4 * ((1 / 2) * (infoAuxiliary(nSubbands) + powerAuxiliary(nSubbands)) * (infoAuxiliary_(nSubbands) + powerAuxiliary_(nSubbands)) - (1 / 4) * (infoAuxiliary_(nSubbands) + powerAuxiliary_(nSubbands)) ^ 2 - (1 / 4) * (infoAuxiliary(nSubbands) - powerAuxiliary(nSubbands)) ^ 2);
+				+ (3 / 2) * beta4 * (infoAuxiliary(nSubbands) * powerAuxiliary_(nSubbands) + powerAuxiliary(nSubbands) * infoAuxiliary_(nSubbands) - infoAuxiliary_(nSubbands) * powerAuxiliary_(nSubbands));
             maximize currentSca;
             subject to
                 (1 / 2) * (trace(infoMatrix) + trace(powerMatrix)) <= txPower;

### 2021-06-10 main.tex
:pencil: Update SCA objective

@@
 		\end{maxi!}
-
 		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
@@
 			\end{align}
-
 			To maximize the non-concave expression \eqref{eq:I_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
@@
 				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
-				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
-				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
-				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2.\label{eq:taylor_3}
-			\end{align}
-
+				& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
+			\end{align}
 			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
@@
 			\end{equation}
-
 			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:I_irs}, we obtain the DC current approximation $\tilde{I}$ as \eqref{eq:I_irs_approx} and transform problem~\eqref{op:original} to
@@
 					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:I_irs_approx}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:I_irs_approx}
 				\end{align}
@@
 			\end{maxi!}
-
 			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
@@
 			\end{mini!}
-
 			The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
@@
 			\end{align}
-
 			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
@@
 			\end{align}
-
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
@@
 			\end{maxi!}
-
 			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
@@
 					\mathcal{L}
-					&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
+					& = \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
 							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
-						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
-							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
+						\Bigr) - \frac{3}{4} \beta_4 \rho^2 \Biggl(
+							2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
 								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-							\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
+							\Bigr) + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
 								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
-							\Bigr)
-							\nonumber\\
-					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
-								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
-							\Bigr) - \mathrm{tr}^2 \Bigl(
-								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
+							\Bigr)\nonumber\\
+					& \quad + 2 t_{\mathrm{P},0}^{(i-1)} \mathrm{tr}\Bigl(
+							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
+						\Bigr) + 2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
+							\boldsymbol{C}_{\mathrm{P},0} \boldsymbol{\Phi}^{(i)}
 						\Bigr)
@@
 					\Biggr)\nonumber\\
-					&\quad+ \mathrm{tr}\biggl(
+					& \quad + \mathrm{tr}\biggl(
 						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
@@
 					\boldsymbol{\Delta}^\star
-					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
+					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
 						\Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})\nonumber\\
-					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
-								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
-							\Bigr)
-						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
+							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + 2 t_{\mathrm{P},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + 2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{P},0}
+						\Biggr)\nonumber\\
+					& \quad + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
 						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(

### 2021-06-11 main.tex
:pencil: Add complexity analysis

@@
 				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
+				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
 			\end{maxi!}
-			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:I_irs_approx}.
-The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it to formulate a convex problem \cite{Luo2010}.
-The tightness of rank relaxation is verified below.
+			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.
+In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+This conclusion is summarized below.
 
 			\begin{proposition}\label{pr:relaxation}
-				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
+				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
 			\end{proposition}
@@
 
-			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}.
-We update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
-The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}.
+			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
+The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.
+
 			\begin{algorithm}[!t]
@@
 We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
-The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}.
+The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+
 			\begin{algorithm}[!t]
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			The GP Algorithm~\ref{al:gp} achieves local optimality with exponential computational complexity \cite{Chiang2005}.
 			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains.
@@
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.
+The proofs of SDR tightness and local optimality are similar to Appendices~\ref{ap:relaxation} and \ref{ap:sca} thus omitted here.
+Compared with Algorithm~\ref{al:sca}, the rate constraint \eqref{co:irs_rate} is dropped and each SDP in Algorithm~\ref{al:m_sca} involves $(L+1)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
 
@@
 			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}.
-For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+The steps are summarized in the BCD Algorithm~\ref{al:bcd}, which achieves local optimality with exponential computational complexity.
+
 			\begin{algorithm}[!t]
@@
 
+			\begin{proposition}\label{pr:bcd}
+				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
+			\end{proposition}
+
+			\begin{proof}\label{pf:bcd}
+				See Appendix~\ref{ap:bcd}
+			\end{proof}
+
+			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
+
 			\begin{algorithm}[!t]
@@
 			\end{algorithm}
-
-			\begin{proposition}\label{pr:bcd}
-				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:bcd}
-				See Appendix~\ref{ap:bcd}
-			\end{proof}
 		\end{subsection}
@@
 			\end{maxi!}
-			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
+			By applying SDR, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
 $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.

### 2021-07-05 main.tex
:pencil: Fix wording

@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels are known.
+We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels are known.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
@@
 
-			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel.
+			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflected channel.
 Hence, the composite equivalent channel reduces to
@@
 		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
 Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
-Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links.
+Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links.
 All channels are assumed NLoS with taps modelled as i.i.d.

### 2021-07-23 main.tex
:pencil: Update parameter description
:pencil: Update parameters
:art: Update font size

@@
 		\begin{maxi!}
-			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
 			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
@@
 			\begin{maxi!}
-				{\boldsymbol{\Phi}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
@@
 			\begin{maxi!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
 				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
@@
 			\begin{mini!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
+				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
 				\addConstraint{\frac{t''}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
@@
 			\begin{mini!}
-				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
+				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
 				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
@@
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
+$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
 Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
@@
 All channels are assumed NLoS with taps modelled as i.i.d.
-CSCG random variables of unit average sum-power, corresponding to a normalized multipath response.
+CSCG random variables.
 Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
@@
 			\begin{maxi!}
-				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
+				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}

### 2021-07-24 main.tex
:pencil: Update notations

@@
 
-			Importantly the rectenna model used in this section, taken from \cite{Clerckx2016a}, captures the dependency of the output DC current on both the power and shape of the received signal.
+			Importantly, the rectenna model used in this section taken from \cite{Clerckx2016a} captures the dependency of the output DC current on both the power and shape of the received signal.
 This is critical for efficient signal designs in WPT and SWIPT \cite{Clerckx2021}.
@@
 As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
-			\begin{equation}\label{eq:I}
-				I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
+			\begin{equation}\label{eq:z}
+				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
 			\end{equation}
 			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $I$ as the average output DC current in this paper.
-It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:I} with $n_0=2$.
+With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper.
+It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
 However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
 In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $I$ by \eqref{eq:I_expand}.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
 Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms.
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $I$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
 
@@
 				\begin{align}
-					&I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:I_expand}\\
+					&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
 					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
@@
 				\mathcal{C}_{\mathrm{R-E}}
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le I,\nonumber\\
+				&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
 				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
 			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
@@
 		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On top of this, \eqref{eq:R} and \eqref{eq:I_expand} reduce respectively to
+On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
 			\begin{align}
@@
 				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-				I(\boldsymbol{\Phi})
+				z(\boldsymbol{\Phi})
 				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
 				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:I_irs}
-			\end{align}
-			To maximize the non-concave expression \eqref{eq:I_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+			\end{align}
+			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
 Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
@@
 			\end{equation}
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:I_irs}, we obtain the DC current approximation $\tilde{I}$ as \eqref{eq:I_irs_approx} and transform problem~\eqref{op:original} to
+			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 				\begin{align}
-					\tilde{I}(\boldsymbol{\Phi}^{(i)})
+					\tilde{z}(\boldsymbol{\Phi}^{(i)})
 					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:I_irs_approx}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
 				\end{align}
@@
 			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
@@
 			\begin{proof}\label{pf:relaxation}
-				See Appendix~\ref{ap:relaxation}.
+				Please refer to Appendix~\ref{ap:relaxation}.
 			\end{proof}
@@
 					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
 					\Repeat
@@
 						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
-					\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
+						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
@@
 			\begin{proof}\label{pf:sca}
-				See Appendix~\ref{ap:sca}.
+				Please refer to Appendix~\ref{ap:sca}.
 			\end{proof}
@@
 			\begin{proof}\label{pf:mrt}
-				See Appendix~\ref{ap:mrt}.
+				Please refer to Appendix~\ref{ap:mrt}.
 			\end{proof}
@@
 			\end{equation}
-			and the DC current \eqref{eq:I_expand} rewrites as \eqref{eq:I_waveform}, so that problem~\eqref{op:original} boils down to
+			and the DC current \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
 				\begin{align}
-					I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
+					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
 					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:I_waveform}
+					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
 				\end{align}
@@
 			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
 				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
@@
 			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It is trivial to conclude $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP
 			\begin{mini!}
 				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{t''}{I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
 				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\rho + \bar{\rho} \le 1.}
+				\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
 			\end{mini!}
@@
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				I(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
 			\end{align}
@@
 				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{I(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
 			\end{align}
@@
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
-					\State Compute $R^{(0)},I^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
+					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
@@
 						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
+						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
+					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
@@
 			\begin{proof}\label{pf:gp}
-				See \cite{Clerckx2016a,Clerckx2018b}.
+				Please refer to \cite{Clerckx2016a,Clerckx2018b}.
 			\end{proof}
@@
 			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:I_irs_approx} should be maximized.
-To achieve any non-WIT point (i.e., $I \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+						\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
 						\Repeat
 							\State $i \gets i + 1$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:I_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-								\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
-						\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
+								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
 						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
@@
 					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
 					\Repeat
@@
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $I^{(i)}$ by \eqref{eq:I_waveform}
-					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
+						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
@@
 			\begin{proof}\label{pf:bcd}
-				See Appendix~\ref{ap:bcd}
+				Please refer to Appendix~\ref{ap:bcd}
 			\end{proof}
@@
 					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 					\Repeat
@@
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
-					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
+						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
 					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
@@
 $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
-Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
+We consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
 Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links.
@@
 			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{I}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
+				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
 				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
@@
 			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{I}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{I}(\boldsymbol{\Phi}) \le I(\boldsymbol{\Phi})$, $\partial\tilde{I}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial I(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.

### 2021-07-26 main.tex
:pencil: Update manuscript

@@
 
-		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels are known.
+		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
+We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
@@
 			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It is trivial to conclude $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It can be concluded $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal component is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP
 			\begin{mini!}
@@
 $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
-We consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}.
-Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflected links.
-All channels are assumed NLoS with taps modelled as i.i.d.
+We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency with \SI{40}{\dB} free-space path loss at \SI{1}{\meter}.
+The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
+All channels are assumed Non-Line-of-Sight (NLoS) where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the taps are modeled as i.i.d.
 CSCG random variables.
-Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}.
-Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity.
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity.
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
-It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 This observation origins from the rectifier nonlinearity.
@@
 Hence, the benefit of multisine outstands for a sufficiently large $N$.
-\emph{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$.
+\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$.
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
@@
 			}
-			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.
+$\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and unquantized IRS.}
 		\end{figure}

### 2021-07-26 main.tex
:pencil: Update punctuation and figure handles

@@
 \usepackage[T1]{fontenc}
-\usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
 % \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
@@
 $\Re\{\cdot\}$ retrieves the real part of a complex entity.
+$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ elements of a vector.
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
@@
 		\begin{subsection}{Transmitted Signal}
-			Denote $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ as the information symbol transmitted over subband $n \in \{1, \dots, N\}$.
-The superposed signal transmitted on antenna $m \in \{1, \dots, M\}$ at time $t$ is
-			\begin{equation}\label{eq:x_m}
-				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\mathrm{I},n,m}\tilde{x}_{\mathrm{I},n}(t)}+w_{\mathrm{P},n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
-			\end{equation}
-			where $w_{\mathrm{I/P},n,m}$ denotes the complex weight of the modulated/multisine waveform transmitted at subband $n$ on antenna $m$, and $f_n$ is the frequency of subband $n$.
-On top of this, we stack up $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T \triangleq \boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
-			\begin{align}
-				\boldsymbol{x}_{\mathrm{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
-				\boldsymbol{x}_{\mathrm{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
-			\end{align}
-			are the modulated and multisine components, respectively.
+			As suggested in \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
+The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
+			\end{equation}
+			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
+On the other hand, the power signal transmitted over subband $n$ at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+			\end{equation}
+			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+			\end{equation}
+			For simplicity, we define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
 		\end{subsection}
@@
 The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
+IRS element $l \in \mathcal{L} \triangleq \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
 			\begin{equation}
-				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
-			\end{equation}
-			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
+				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
+			\end{equation}
+			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, in practice $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
 This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define respectively $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}, respectively.
 
@@
 			\begin{equation}\label{eq:h_n}
-				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
+				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
 			\end{equation}
 			where we define the cascaded channel without IRS reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+For simplicity, we also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
 
@@
 				The cascaded channel varies at different frequencies.
-Since we regard the reflection as frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain.
-Moreover, each IRS element simultaneously assists all transmit antennas such that the reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
+Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+This is essentially a resource allocation opportunity at the channel enabled by the IRS.
+In the MISO case, a similar effect also exists in the spatial domain.
+Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
 			\end{remark}
@@
 		\begin{subsection}{Received Signal}
-			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)+n(t)$, where
-			\begin{align}
-				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
-				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
-			\end{align}
-			capture respectively the modulated and multisine components, and $n(t)$ is the noise at the RF-band.
-Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
+			The received superposed signal at the single-antenna UE is\footnote{It is assumed that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+			\begin{equation}
+				y(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})}{e^{j2{\pi}{f_n}{t}}}+w_n(t)\right\},
+			\end{equation}
+			where $w_n(t)$ is the noise at RF band $n$.
+Note that $y_{\mathrm{I}}(t)$ can be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ carries no information and cannot be used for decoding.
 		\end{subsection}
@@
 		\begin{subsection}{Information Decoder}
-			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
+			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
+Therefore, the achievable rate is\footnote{This rate is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
 			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
+				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2},\right)}
 			\end{equation}
 			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$.
-Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
 		\end{subsection}
@@
 This is critical for efficient signal designs in WPT and SWIPT \cite{Clerckx2021}.
-Fig.~\ref{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
+Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
 Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
@@
 			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
-Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
 As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
+				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
 			\end{equation}
@@
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms.
-Moreover, we define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the nonlinear DC terms.
+Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \mathcal{K} \triangleq \{{-N+1},\dots,{N-1}\}$ and set all other blocks to $\boldsymbol{0}$.
 Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
@@
 				&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
+				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
 			\end{align}
@@
 				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
+				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
 			\end{align}
@@
 				& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
+				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
 			\end{align}
@@
 
-			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$.
+			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
 The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\bar{R},\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
@@
 					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
-					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
+					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 		\begin{subsection}{Active Beamforming}
-			We decouple the waveform in the spatial and frequency domains by
+			To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.
+The weight on subband $n$ is essentially
 			\begin{equation}\label{eq:w}
-				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
+				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
 			\end{equation}
@@
 			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right)
+				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
 			\end{equation}
@@
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P},
 			\end{align}
@@
 				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
-				\addConstraint{\rho + \bar{\rho} \le 1}
+				\addConstraint{\rho + \bar{\rho} \le 1,}
 			\end{mini!}
-			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
+			where $\gamma_{m_{\mathrm{I},n}} \ge 0$, $\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
 The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_n,P,\sigma_n,\bar{R},\epsilon$, $\forall n$
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
-					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Update $\{\gamma_{m_{\mathrm{I},n}}^{(i)},\gamma_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star},\boldsymbol{s}_{\mathrm{P}}^{\star},\rho^{\star}$
+					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$
+					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
 				\end{algorithmic}
@@
 			\begin{equation}\label{eq:wf}
-				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
+				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
 			\end{equation}
@@
 			\begin{equation}\label{eq:smf}
-				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
+				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
 			\end{equation}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
+					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
 					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
@@
 					\EndIf
-					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
+					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
 					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
@@
 						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
@@
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
 				\end{algorithmic}
@@
 				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
 					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 					\Repeat
@@
 						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
-						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
 				\end{algorithmic}
@@
 
-		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+		Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
 \emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
 It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy.
-On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
+On the other hand, Fig.~\subref*{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
 It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}).
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\subref*{fi:re_subband}).
 Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
@@
 
-		The average noise power influences the R-E region as in Fig.~\ref{fi:re_noise}.
+		The average noise power influences the R-E region as in Fig.~\subref*{fi:re_noise}.
 \emph{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
@@
 
-		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
+		In Fig.~\subref*{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
 Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
@@
 
-		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}.
+		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Fig.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
 \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
 \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT.
+This behavior is more obvious in Fig.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector} for the case of WIT and WPT.
 As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
@@
 
-		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
+		Fig.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
 The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
@@
 		\begin{equation}
-			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
+			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n},
 		\end{equation}
@@
 Note that the estimations at different subbands are independent, but the subchannel responses are indeed correlated.
-Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
+Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
 On the other hand, since the practical reflection coefficient depends on the available element impedances, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
-Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
@@
 			\begin{equation}
-				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
+				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star,
 			\end{equation}

### 2021-07-27 review/response_2.tex
:pencil: Initialize response letter

\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[short]{optidef}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xr-hyper}
\usepackage{hyperref}

\externaldocument[M-]{submit}

\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}
\newcounter{response}[reviewer]
\setcounter{response}{0}

\let\svbibcite\bibcite
\def\bibcite#1#2{\svbibcite{#1}{R#2}}
\makeatletter
\let\svbiblabel\@biblabel
\def\@biblabel#1{\svbiblabel{R#1}}
\makeatother

\renewcommand{\theequation}
	{E\arabic{equation}}

\renewcommand{\thefigure}
	{F\arabic{figure}}

\renewcommand{\thetable}
	{T\arabic{table}}

\renewcommand{\thealgorithm}
	{A\arabic{algorithm}}

\newcommand{\reviewer}
	{\stepcounter{reviewer} \bigskip \hrule \section*{Reviewer \thereviewer}}

\renewcommand{\thepoint}
	{\thereviewer.\arabic{point}}

\renewcommand{\theresponse}
	{\thereviewer.\arabic{response}}

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter_1.pdf}

	\begin{reviewer}
		\begin{point}
			As this paper proposed a BCD-based algorithm and LC-BCD algorithm, it could be better if the authors can further discuss the complexity and provide some measurements or some simulation results.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The reviewer noticed that in Algorithm 5, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Although this paper reveals many useful insights, most of them are obtained via simulation and then explained via text. The overall theoretical contributions can be greatly improved if the authors can analytically verify or prove some of them, especially those unique to this paper. The authors may conduct the analysis under some simplified or special cases. If some of the observations and findings have been verified in existing papers, the authors can cite and echo these papers wherever necessary.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In (14), the authors integrated the waveform design and active beamforming design into $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$. However, they separately optimized them later. Is it possible to directly optimize $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ as a whole?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$. In Algorithm 5, both of them are input. Did the authors perform a two-dimensional search here? Besides, they were assumed to be identical in the simulation. How will this assumption influence the performance loss?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			If possible, in Fig.11, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It was shown via simulation that PS is not always superior to TS, unlike the linear model. Is it possible to develop some analytical preconditions to determine which one is better?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Is it possible to give the complexity order of the algorithms presented in this paper?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The expressions of signals in (1), (2), and (5) are not conventional. It may be better to give a per-band signal instead of their superposition. Besides, it is better to first introduce the functionalities of the modulated and multisine waveforms before giving (1).
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In Remark 2, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs. 9(b) and 10(b), the text in the y-axis is too long. Please divide it into two rows. Besides, the text in the x-axis of the upper figure is covered by the lower one.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Proposition 5 is questionable. The algorithm may not converge to a local optimal due to the coupling constraint 14b.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The figures are too small. For example, Fig 10, the axis legend is not fully shown.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It is said that the reference path loss is -35 dB at 1m, while for the center frequency at 5.18 GHz, even adopting the free space path loss model also will lead a much sever path loss at 1 m. It is not clear how the authors calculate this.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The authors considered the practical reflection coefficient beamforming in the simulkation results. It is not cleaer how the authors obtain the discrte phase shift results. Direct quantization method and some other customized optimization technqiues for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}. Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			There are also some other practical phase shift models and nonlinear energy harvesting models such as saturation model for IRS-aided SWIPT in existing works, which may be discussed as related works such as amplitude-dependent phase shift model.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some early magazine papers and recent tutorial papers related to IRS-aided WPT/WIT may be further discussed.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			What is the computational complexity of the proposed algorithm?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some related works are worth citing, such as \cite{Yang2021}.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

### 2021-07-28 main.tex
:pencil: Update manuscript

@@
 To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+In such case, the current expression is dropped and no SCA is involved.
 To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
@@
 Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
+Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
 
@@
 			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by adjusting the combining and splitting ratios from \num{1} to \num{0}.
+For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
@@
 						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+						\If{$\rho=0$}
+							\State $\Delta = R^{(i)} - R^{(i-1)}$
+						\Else
+							\State $\Delta = z^{(i)} - z^{(i-1)}$
+						\EndIf
+					\Until $\lvert \Delta \rvert \le \epsilon$
 					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$

### 2021-07-28 review/response_2.tex
:pencil: Update response letter

@@
 \usepackage{cite}
+\usepackage{framed}
 \usepackage{fullpage}
@@
 
-\externaldocument[M-]{submit}
+\externaldocument[M-]{../main}
 
@@
 \begin{document}
-	\includepdf{letter_1.pdf}
+	\includepdf{letter_2.pdf}
 
@@
 		\begin{response}
-			TODO
+			We appreciate your suggestion and agree that complexity analysis is necessary in algorithm evaluation.
+
+			For SCA Algorithm~\ref{M-al:sca}, in the previous manuscript, we applied SCA on $t_{\mathrm{I},0} t_{\mathrm{P},0}$ at iteration $i$ as
+			\begin{align}
+				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
+				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
+				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2,
+			\end{align}
+			which is generally feasible and widely adopted when $t_{\mathrm{I},0}$ and $t_{\mathrm{P},0}$ are variables.
+Hence, we claimed Algorithm~\ref{M-al:sca} ``is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{M-eq:z_irs_approx}''.
+During revision, we realized that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ are essentially linear real expressions related to optimization variable $\boldsymbol{\Phi}$, and the SCA can be further reduced to
+			\begin{equation}
+				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)} \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.
+			\end{equation}
+			Therefore, the quadratic term in the objective function \eqref{M-eq:z_irs_approx} is eliminated and the updated problem~\ref{M-op:irs} is indeed an SDP.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{M-Luo2010}.
+In the updated manuscript, we made the revision as follows.
+			\begin{framed}
+				The passive beamforming design is summarized in the SCA Algorithm~\ref{M-al:sca}, where the relaxed problem \eqref{M-ob:irs}--\eqref{M-co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{M-Luo2010}.
+			\end{framed}
+
+			For GP Algorithm~\ref{M-al:gp}, the computational complexity is exponential w.r.t. the number of subbands \cite{M-Chiang2005}.
+			\begin{framed}
+				The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{M-al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{M-Chiang2005}.
+			\end{framed}
+
+			For M-SCA Algorithm~\ref{M-al:m_sca}, each optimization problem involved is an SDP with $(L+1)$ variables and linear constraints, and the computational complexity is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$ where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations.
+			\begin{framed}
+				Compared with Algorithm~\ref{M-al:sca}, the rate constraint \eqref{M-co:irs_rate} is dropped and each SDP in Algorithm~\ref{M-al:m_sca} involves $(L+1)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}.
+Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
+			\end{framed}
+
+			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
+			\begin{framed}
+				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, which achieves local optimality with exponential computational complexity. [TODO]
+			\end{framed}
+
+			For LC-BCD Algorithm~\ref{M-al:lc_bcd}, both waveform and active beamforming are obtained in closed form, and the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
+			\begin{framed}
+				Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
+			\end{framed}
 		\end{response}
@@
 		\begin{point}
-			The reviewer noticed that in Algorithm 5, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
+			The reviewer noticed that in Algorithm~\ref{M-al:lc_bcd}, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
 		\end{point}
@@
 		\begin{response}
-			TODO
+			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}.
+In each iteration, Algorithm~\ref{M-al:m_sca} is called.
+To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved.
+To clarify this point, we first updated the description on Algorithm~\ref{M-al:m_sca} as follows.
+			\begin{framed}
+				To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
+In such case, the current expression is dropped and no SCA is involved.
+			\end{framed}
+			Correspondingly, to achieve the WIT point, the LC-BCD Algorithm~\ref{M-al:lc_bcd} should maximizes $R$ instead of $z$.
+Line~\ref{li:convergence_begin}--\ref{li:convergence_end} was modified to avoid ambiguity and Algorithm~\ref{M-al:lc_bcd} is indexed below by \ref{al:lc_bcd} .
+			\begin{algorithm}[!h]
+				\caption{LC-BCD: Waveform and Beamforming.}
+				\label{al:lc_bcd}
+				\begin{algorithmic}[1]
+					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
+					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{M-eq:w}
+					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
+					\Repeat
+						\State $i \gets i + 1$
+						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{M-al:m_sca}
+						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_i}, \eqref{M-eq:s_p}
+						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
+						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
+						\If{$\rho=0$} \label{li:convergence_begin}
+							\State $\Delta = R^{(i)} - R^{(i-1)}$
+						\Else
+							\State $\Delta = z^{(i)} - z^{(i-1)}$
+						\EndIf
+					\Until $\lvert \Delta \rvert \le \epsilon$ \label{li:convergence_end}
+					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
+				\end{algorithmic}
+			\end{algorithm}
+			The description was also updated as follows.
+			\begin{framed}
+				In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnotemark to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by adjusting the combining and splitting ratios from \num{1} to \num{0}.
+For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
+			\end{framed}
+			\footnotetext{{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}}
 		\end{response}
@@
 		\begin{point}
-			The authors considered the practical reflection coefficient beamforming in the simulkation results.
-It is not cleaer how the authors obtain the discrte phase shift results.
-Direct quantization method and some other customized optimization technqiues for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}.
+			The authors considered the practical reflection coefficient beamforming in the simulation results.
+It is not clear how the authors obtain the discrete phase shift results.
+Direct quantization method and some other customized optimization techniques for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}.
 Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
@@
 	\bibliographystyle{IEEEtran}
-	\bibliography{IEEEabrv,library.bib}
+	\bibliography{IEEEabrv,../library.bib}
 \end{document}

### 2021-07-29 main.tex
:pencil: Update manuscript

@@
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
+Deep reinforcement learning tools were also applied in \cite{Yang2021} to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
 		\end{subsection}
@@
 			The major issue of WPT and SWIPT is the low harvested DC power.
-To increase it, we introduce an IRS that enhances the end-to-end energy efficiency and boosts the harvester input power level.
+To tackle this, we introduce an IRS that enhances the end-to-end energy efficiency and boosts the harvester input power level.
 The smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
 For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams.
-However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model.
-Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS.
+It was also claimed that Line-of-Sight (LoS) links could boost the WSP as rank-deficient channels tend to require fewer energy beams \cite{Wu2020a}.
+However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
+In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model.
+To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
 We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
@@
 Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead\footnote{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS).
+The readers are referred to \cite{Wu2020c} for details.}.
 Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.

### 2021-07-29 review/response_2.tex
:pencil: Update response letter

@@
 Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{M-Luo2010}.
-In the updated manuscript, we made the revision as follows.
+We have revised the manuscript as follows.
 			\begin{framed}
@@
 		\begin{response}
-			TODO
+			Thank you for sharing this paper.
+Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff.
+The model also adapts well to practical IRS models accounting AoA and AoD.
+In contrast, our paper is more focused on waveform design and rate-energy tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
+We have updated the manuscript as follows.
+			\begin{framed}
+				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model accounting AoA and AoD.
+To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
+			\end{framed}
 		\end{response}
@@
 To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved.
-To clarify this point, we first updated the description on Algorithm~\ref{M-al:m_sca} as follows.
+To clarify this point, we have updated the description on Algorithm~\ref{M-al:m_sca} as follows.
 			\begin{framed}
@@
 			\end{algorithm}
-			The description was also updated as follows.
+			The description on Algorithm~\ref{M-al:lc_bcd} have been updated as follows.
 			\begin{framed}
@@
 			\end{framed}
-			\footnotetext{{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}}
+			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}
 		\end{response}
@@
 		\begin{response}
-			TODO
+			Thank you for the clarification.
+The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$.
+We are aware that direct quantization can lead to performance loss compared with optimization over feasible phase shift set.
+In the revised manuscript, we have emphasized this point as follows.
+			\begin{framed}
+				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead\footnotemark.
+			\end{framed}
+			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS).
+The readers are referred to \cite{Wu2020c} for details.}
 		\end{response}
@@
 		\begin{response}
-			TODO
+			Thank you for mentioning this paper. The literature review has been updated accordingly as follows.
+			\begin{framed}
+				Deep reinforcement learning tools were also applied in \cite{Yang2021} to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
+			\end{framed}
 		\end{response}

### 2021-07-29 main.tex
:pencil: Update manuscript

@@
 Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain.
+The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
@@
 
-		\begin{subsection}{Energy Harvester}
+		\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
 			\begin{figure}[!t]
@@
 				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
-			\end{align}
+				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
+			\end{align}
+			where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
+Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}.
 Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
+To achieve the WIT point, the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
 In such case, the current expression is dropped and no SCA is involved.
-To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$.
+To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate depends on either $\eta$ or $\{\delta,\rho\}$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
+Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since no current expression thus no SCA is involved.
 
@@
 			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by adjusting the combining and splitting ratios from \num{1} to \num{0}.
+In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
 For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
@@
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
-$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
+$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference\footnote{We set the AP-UE distance to be larger than SWIPT literatures \cite{Clerckx2018b} and experiments \cite{Kim2020a} thanks to the IRS.}.
 We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency with \SI{40}{\dB} free-space path loss at \SI{1}{\meter}.
@@
 CSCG random variables.
-Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity.
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{Clerckx2016a}.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
+\emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$.
+This conclusion is also verified in the following plots.
 
@@
 
-		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Fig.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
+		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
 \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
 \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in Fig.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector} for the case of WIT and WPT.
+This behavior is more obvious in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector} for the case of WIT and WPT.
 As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
@@
 
-		Fig.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
+		Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
 The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.

### 2021-07-29 review/response_2.tex
:pencil: Update response letter

@@
 			\end{framed}
+			\label{re:1.1}
 		\end{response}
@@
 		\begin{response}
-			TODO
+			The system layout follows \cite{M-Wu2019} and we set the AP-UE distance to be larger than SWIPT literatures \cite{M-Clerckx2018b} and experiments \cite{M-Kim2020a} thanks to the IRS.
+For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties.
+Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in many IRS papers.
+In the previous manuscript, we made a mistake in the choice of reference path loss.
+As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}.
+To fix this issue, we updated the path loss model as IEEE TGn channel model D \cite{M-Erceg2004}, where the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance (\SI{10}{\meter} in model D) and \num{3.5} onwards.
+This has a similar effect to most IRS literatures that assign a large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
+As for the rectenna parameters, we forgot to mention that the parameters are taken from \cite{M-Clerckx2016a} and have added the reference to the revised manuscript.
 		\end{response}
@@
 		\begin{point}
-			In (14), the authors integrated the waveform design and active beamforming design into $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
+			In \ref{M-op:original}, the authors integrated the waveform design and active beamforming design into $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$.
 However, they separately optimized them later.
-Is it possible to directly optimize $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ as a whole?
+Is it possible to directly optimize $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ as a whole?
 		\end{point}
@@
 		\begin{response}
-			TODO
+			For the single-user case, direct optimization on $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ is possible.
+The reviewer is referred to Algorithm 1 of \cite{M-Clerckx2018b} for more details, and the idea is briefly described as follows.
+First, $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ are complex variables of size $MN \times 1$.
+To enable GP tools (which apply to problems involving real-valued variables), we notice that the optimal phase of $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ should be designed to compensate the phase of the corresponding composite channel $\boldsymbol{h}$, namely
+			\begin{equation}
+				\arg(\boldsymbol{w}_{\mathrm{I}}) = \arg(\boldsymbol{w}_{\mathrm{P}}) = -\arg(\boldsymbol{h})
+			\end{equation}
+			such that, from the perspective of phase design, the current expression \ref{M-eq:z_expand} is maximized (where all $\cos$ terms peak at \num{1}) and the rate expression is maximized (where the phases align with those of matched filters).
+Therefore, the direct optimization on $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ boils down to amplitude optimization on $\boldsymbol{s}_{\mathrm{I}}$ and $\boldsymbol{s}_{\mathrm{P}}$, where $\boldsymbol{s}_{\mathrm{I/P}}=\lvert \boldsymbol{w}_{\mathrm{I/P}} \rvert$.
+GP tools can be applied at this stage and the number of real-valued variables are $2MN$.
+In contrast, the proposed Algorithm~\ref{M-al:gp} decoupled the design in the spatial and frequency domains, derived the global optimal active precoder, and leaves an resource allocation issue with $2N$ real-valued variables in the frequency domain.
+Since the computational complexity of GP scales exponentially with the number of variables, optimizing $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ as a whole can be very inefficient and not discussed in the manuscript.
+Accordingly, we have revised the manuscript as follows.
+			\begin{framed}
+				To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.
+			\end{framed}
 		\end{response}
@@
 			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$.
-In Algorithm 5, both of them are input.
+In Algorithm~\ref{M-al:lc_bcd}, both of them are input.
 Did the authors perform a two-dimensional search here?
@@
 		\begin{response}
-			TODO
+			Thank you for raising this point.
+The combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.
+We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
+Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff.
+Indeed, the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
+However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead.
+The results show that even a one-dimensional search for the LC-BCD algorithm can achieve a very good performance.
+We have summarized the point in the manuscript as follows.
+			\begin{framed}
+				\textellipsis where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.
+
+				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
+
+				\textellipsis assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+
+				\textellipsis \emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$.
+This conclusion is also verified in the following plots.
+			\end{framed}
+			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
+Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
 		\end{response}
@@
 		\begin{point}
-			If possible, in Fig.11, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
+			If possible, in Fig.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
 		\end{point}
@@
 		\begin{response}
-			TODO
+			We have added complexity analysis in the revised manuscript. The reviewer is referred to Response~\ref{re:1.1} for details.
 		\end{response}
@@
 		\begin{response}
-			TODO
+			We agree with the reviewer that the signal model requires more description. The manuscript has been updated as follows.
+			\begin{framed}
+				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
+The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
+			\end{equation}
+			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
+On the other hand, the power signal transmitted over subband $n$ at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+			\end{equation}
+			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
+			\begin{equation}
+				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+			\end{equation}
+			\end{framed}
 		\end{response}
@@
 		\begin{point}
-			In Remark 2, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
+			In Remark~\ref{M-re:subband_tradeoff}, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
+		\end{point}
+
+		\begin{response}
+			By ``auxiliary link control in the frequency domain'', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS.
+The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+We have updated the Remark~\ref{M-re:subband_tradeoff} as follows.
+			\begin{framed}
+				The cascaded channel varies at different frequencies.
+Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain.
+The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+This is essentially a resource allocation opportunity at the channel enabled by the IRS.
+In the MISO case, a similar effect also exists in the spatial domain.
+Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
+			\end{framed}
+		\end{response}
+
+		\begin{point}
+			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, the text in the y-axis is too long.
+Please divide it into two rows.
+Besides, the text in the x-axis of the upper figure is covered by the lower one.
+		\end{point}
+
+		\begin{response}
+			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will endeavor to avoid similar issues in the future.
+		\end{response}
+	\end{reviewer}
+
+	\begin{reviewer}
+		\begin{point}
+			Proposition~\ref{M-pr:bcd} is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
 		\end{point}
@@
 		\begin{point}
-			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs.
-9(b) and 10(b), the text in the y-axis is too long.
-Please divide it into two rows.
-Besides, the text in the x-axis of the upper figure is covered by the lower one.
+			The figures are too small. For example, Fig.~\ref{M-fi:scaling_reflector}, the axis legend is not fully shown.
 		\end{point}
@@
 		\begin{response}
-			TODO
-		\end{response}
-	\end{reviewer}
-
-	\begin{reviewer}
-		\begin{point}
-			Proposition 5 is questionable. The algorithm may not converge to a local optimal due to the coupling constraint 14b.
-		\end{point}
-
-		\begin{response}
-			TODO
+			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
 		\end{response}
@@
 		\begin{point}
-			The figures are too small. For example, Fig 10, the axis legend is not fully shown.
-		\end{point}
-
-		\begin{response}
-			TODO
-		\end{response}
-
-		\begin{point}
-			It is said that the reference path loss is -35 dB at 1m, while for the center frequency at 5.18 GHz, even adopting the free space path loss model also will lead a much sever path loss at 1 m.
+			It is said that the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}.
 It is not clear how the authors calculate this.
+			\label{pt:3.3}
 		\end{point}

### 2021-07-29 main.tex
:pencil: Update manuscript

@@
 To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
 The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			The major issue of WPT and SWIPT is the low harvested DC power.
-To tackle this, we introduce an IRS that enhances the end-to-end energy efficiency and boosts the harvester input power level.
+			The major issue of WPT and SWIPT is the low harvested DC power, and the passive beamforming provided by the IRS can enhance the end-to-end energy efficiency and boost the harvester input power level.
 The smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
@@
 It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model.
+A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
 To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.

### 2021-07-29 review/response_2.tex
:pencil: Update response letter

@@
 For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties.
-Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in many IRS papers.
+Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in most IRS papers.
 In the previous manuscript, we made a mistake in the choice of reference path loss.
 As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}.
-To fix this issue, we updated the path loss model as IEEE TGn channel model D \cite{M-Erceg2004}, where the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance (\SI{10}{\meter} in model D) and \num{3.5} onwards.
-This has a similar effect to most IRS literatures that assign a large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
+To fix this issue, we updated the path loss model as IEEE TGn channel model D that is representative of small environments such as residential homes and small offices \cite{M-Erceg2004}.
+It has three clusters with \SI{50}{\ns} r.m.s.
+delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards.
+This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
 As for the rectenna parameters, we forgot to mention that the parameters are taken from \cite{M-Clerckx2016a} and have added the reference to the revised manuscript.
@@
 		\begin{response}
-			TODO
+			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue.
+The parameter \SI{-35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without a second consideration.
+In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{-40}{\dB} at \SI{1}{\meter}.
+The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards.
+This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
 		\end{response}
@@
 		\begin{response}
-			TODO
+			We have added reference \cite{Xu2021} in the updated manuscript that models the saturation effect of energy harvesters and physical properties of the IRS.
+Its contributions have been summarized in the manuscript as follows.
+			\begin{framed}
+				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model accounting AoA and AoD.
+			\end{framed}
 		\end{response}
@@
 		\begin{response}
-			TODO
+			We have incorporated the reference into the manuscript as follows.
+			\begin{framed}
+				\textellipsis The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
+
+				\textellipsis A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
+			\end{framed}
 		\end{response}
@@
 		\begin{response}
-			Thank you for mentioning this paper. The literature review has been updated accordingly as follows.
+			We have incorporated the reference into the manuscript as follows.
 			\begin{framed}

### 2021-07-30 main.tex
:pencil: Update manuscript

@@
 
-			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design.
+			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{Clerckx2016a}.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
 To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes.
@@
 To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode.
-The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.
+The proposed low-complexity designs achieve decent R-E performance in different scenarios.
 
@@
 			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}, which achieves local optimality with exponential computational complexity.
+The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
 
@@
 			\begin{proposition}\label{pr:bcd}
-				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
+				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge.
 			\end{proposition}
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\subref*{fi:re_subband}).
-Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
+For a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any R-E point (this is verified in simulation).
+In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary).
+However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
+In conclusion, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
 \emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$.
@@
 Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage local optimal BCD algorithm is proposed to solve the problem.
+A three-stage BCD algorithm is proposed to solve the problem.
 In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition.
 In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method.
-We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance in different scenarios.
+We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves decent performance in different scenarios.
 Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:bcd}}\label{ap:bcd}
-			The objective function \eqref{ob:original} is non-decreasing over the iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
+			The objective function \eqref{ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{al:sca} is local optimal, the active precoder by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal.
+\eqref{ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
 Therefore, Algorithm~\ref{al:bcd} is guaranteed to converge.
-Since the IRS phase shift by Algorithm~\ref{al:sca} is local optimal, the active precoder by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
+However, it may not converge to optimal points since variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
 		\end{subsection}

### 2021-07-30 review/response_2.tex
:pencil: Update response letter

@@
 		\begin{response}
-			TODO
+			We believe this is an important issue and have modified the manuscript accordingly as follows.
+			\begin{framed}
+				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
+			\end{framed}
 		\end{response}
@@
 		\begin{response}
-			TODO
+			We concluded that PS outperforms TS when the number of subcarrier is relatively small or when the SNR is relatively large.
+However, the analytical preconditions in the proposed system can be very hard to obtain because SNR can depend on many factors (e.g., distance of all paths, number of IRS elements, average noise power, etc.).
+Essentially, this behavior origins from the waveform selection and we would like to analyze it in a nutshell.
+
+			TS only performs a naive time-sharing between the WIT point and the WPT point.
+At the WIT point, only modulated waveform is used to maximize the achievable rate.
+At the WPT point, the optimal waveform depends on the number of subcarriers $N$.
+Although the modulated waveform has an modulation gain of \num{2} that outstands for a small $N$, it creates no DC coupling between frequencies and is outperformed by multisine for a large $N$.
+Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation).
+In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary).
+However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point due to its power benefit under nonlinear harvester model.
+It creates some concavity in the high-power region and accounts for the superiority of TS.
+
+			Similar effect exists for SNR.
+At high SNR, the SWIPT user can achieve a decent rate even if a small fraction of transmit power is allocated to the modulated waveform.
+Therefore, one can approach high-rate region fast at a small cost of DC power at high SNR.
+This is however impossible at low SNR.
 		\end{response}
@@
 		\begin{response}
-			TODO
+			We sincerely appreciate the reviewer for pointing out this issue.
+Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together.
+We have removed the claim on optimality and updated Proposition~\ref{M-pr:bcd} as follows.
+			\begin{framed}
+				For any feasible initial point, the BCD Algorithm~\ref{M-al:bcd} is guaranteed to converge.
+			\end{framed}
+			The proof has been modified correspondingly.
+			\begin{framed}
+				The objective function \eqref{M-ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{M-al:sca} is local optimal, the active precoder by \eqref{M-eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{M-al:gp} are local optimal.
+\eqref{M-ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{M-co:original_modulus} and the transmit power constraint \eqref{M-co:original_power}.
+Therefore, Algorithm~\ref{M-al:bcd} is guaranteed to converge.
+However, it may not converge to optimal points since variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
+			\end{framed}
 		\end{response}

### 2021-08-01 src/config/config_re_waveform.m
:sparkles: Waveform with and without IRS

@@ -1,0 +1,64 @@
+%% * Transceiver
+% diode k-parameter
+k2 = 0.0034;
+k4 = 0.3829;
+% antenna resistance
+resistance = 50;
+% scale ratio of SMF
+alpha = 2;
+% coefficients on current terms
+beta2 = k2 * resistance;
+beta4 = k4 * resistance ^ 2;
+% number of transmit and receive antennas
+nTxs = 1;
+nRxs = 1;
+% number of users
+nUsers = 1;
+% average transmit power
+txPower = db2pow(10);
+% average noise power
+noisePower = db2pow(-70);
+% IRS element gain
+irsGain = 1;
+% receive antenna gain
+rxGain = db2pow(3);
+
+%% * Channel
+% AP-user distance
+directDistance = 12;
+% vertical distance from the IRS to the AP-user path
+verticalDistance = 2;
+% projection of AP-IRS distance to the AP-user path
+horizontalDistance = 2;
+% AP-IRS and IRS-user distance
+[incidentDistance, reflectiveDistance] = coordinate(directDistance, verticalDistance, horizontalDistance);
+% center frequency
+centerFrequency = 2.4e9;
+% bandwidth
+bandwidth = 1e7;
+% channel fading mode ('flat' or 'selective')
+fadingMode = 'selective';
+% number of reflecting elements in IRS
+nReflectors = 20;
+% spatial correlation
+corTx = eye(nTxs);
+corRx = eye(nRxs);
+corIrs = eye(nReflectors);
+
+%% * Algorithm
+% minimum gain per iteration
+tolerance = 1e-8;
+% number of CSCG random vectors to generate
+nCandidates = 1e3;
+% number of samples in R-E curves
+nSamples = 2;
+% number of channel realizations
+nChannels = 1;
+
+%% * Variable
+% number of frequency bands
+Variable.nSubbands = 2 .^ (0 : 4);
+
+%% * PBS
+% number of individual jobs
+nBatches = 3e2;

### 2021-08-01 src/plot/plot_re_waveform.m

@@ -1,0 +1,99 @@
+clear; clc; close all; config_re_waveform;
+
+%% * Load data
+load('../data/re_waveform.mat', 'reIrsSolution', 'reNoIrsSolution');
+
+witIrsInfoAmplitude = cell(1, length(Variable.nSubbands));
+witNoIrsInfoAmplitude = cell(1, length(Variable.nSubbands));
+witIrsPowerAmplitude = cell(1, length(Variable.nSubbands));
+witNoIrsPowerAmplitude = cell(1, length(Variable.nSubbands));
+wptIrsInfoAmplitude = cell(1, length(Variable.nSubbands));
+wptNoIrsInfoAmplitude = cell(1, length(Variable.nSubbands));
+wptIrsPowerAmplitude = cell(1, length(Variable.nSubbands));
+wptNoIrsPowerAmplitude = cell(1, length(Variable.nSubbands));
+
+for iSubband = 1 : length(Variable.nSubbands)
+	witIrsInfoAmplitude{iSubband} = sort(reIrsSolution{iSubband}{1}.infoAmplitude);
+	witNoIrsInfoAmplitude{iSubband} = sort(reNoIrsSolution{iSubband}{1}.infoAmplitude);
+	witIrsPowerAmplitude{iSubband} = sort(reIrsSolution{iSubband}{1}.powerAmplitude);
+	witNoIrsPowerAmplitude{iSubband} = sort(reNoIrsSolution{iSubband}{1}.powerAmplitude);
+
+	wptIrsInfoAmplitude{iSubband} = sort(reIrsSolution{iSubband}{2}.infoAmplitude);
+	wptNoIrsInfoAmplitude{iSubband} = sort(reNoIrsSolution{iSubband}{2}.infoAmplitude);
+	wptIrsPowerAmplitude{iSubband} = sort(reIrsSolution{iSubband}{2}.powerAmplitude);
+	wptNoIrsPowerAmplitude{iSubband} = sort(reNoIrsSolution{iSubband}{2}.powerAmplitude);
+end
+
+%% * Waveform amplitude
+figure('name', 'Sorted WIT/WPT waveform amplitude with and without IRS vs number of subbands', 'position', [0, 0, 500, 400]);
+% * WIT modulated
+witInfoPlot = tiledlayout(length(Variable.nSubbands), 1, 'tilespacing', 'compact');
+for iSubband = 1 : length(Variable.nSubbands)
+	nexttile;
[…]

### 2021-08-01 src/re_waveform.m

@@ -1,0 +1,49 @@
+clear; clc; setup; config_re_waveform;
+
+%% ! WIT/WPT waveform with and without IRS vs number of subbands
+reIrsSample = cell(nChannels, length(Variable.nSubbands));
+reNoIrsSample = cell(nChannels, length(Variable.nSubbands));
+
+reIrsSolution = cell(nChannels, length(Variable.nSubbands));
+reNoIrsSolution = cell(nChannels, length(Variable.nSubbands));
+
+for iChannel = 1 : nChannels
+    % * Generate tap gains and delays
+    [directTapGain, directTapDelay] = tap_tgn(corTx, corRx, 'nlos');
+    [incidentTapGain, incidentTapDelay] = tap_tgn(corTx, corIrs, 'nlos');
+    [reflectiveTapGain, reflectiveTapDelay] = tap_tgn(corIrs, corRx, 'nlos');
+
+    for iSubband = 1 : length(Variable.nSubbands)
+        % * Get number of subbands and subband frequency
+        nSubbands = Variable.nSubbands(iSubband);
+        [subbandFrequency] = subband_frequency(centerFrequency, bandwidth, nSubbands);
+
+        % * Construct channels
+        [directChannel] = channel_response(directTapGain, directTapDelay, directDistance, rxGain, subbandFrequency, fadingMode);
+        [incidentChannel] = channel_response(incidentTapGain, incidentTapDelay, incidentDistance, irsGain, subbandFrequency, fadingMode);
+        [reflectiveChannel] = channel_response(reflectiveTapGain, reflectiveTapDelay, reflectiveDistance, rxGain, subbandFrequency, fadingMode);
+		[cascadedChannel] = cascaded_channel(incidentChannel, reflectiveChannel);
+
+		% * IRS
+		[reIrsSample{iChannel, iSubband}, reIrsSolution{iChannel, iSubband}] = re_sample_swipt_gp(alpha, beta2, beta4, directChannel, cascadedChannel, txPower, noisePower, nCandidates, nSamples, tolerance);
+
+		% * No IRS
+		[reNoIrsSample{iChannel, iSubband}, reNoIrsSolution{iChannel, iSubband}] = re_sample_swipt_benchmark(alpha, beta2, beta4, directChannel, txPower, noisePower, nSamples, tolerance);
+    end
+end
+
+% * Average over channel realizations
[…]

### 2021-08-01 main.tex
:pencil: Update manuscript

@@
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
-$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference\footnote{We set the AP-UE distance to be larger than SWIPT literatures \cite{Clerckx2018b} and experiments \cite{Kim2020a} thanks to the IRS.}.
-We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency with \SI{40}{\dB} free-space path loss at \SI{1}{\meter}.
+$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
 The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-All channels are assumed Non-Line-of-Sight (NLoS) where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the taps are modeled as i.i.d.
-CSCG random variables.
+We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{Erceg2004}.
+Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
+All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D.
+The tap gains are modeled as i.i.d.
+CSCG variables.
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{Clerckx2016a}.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{36}{\dBm}$, the receive antenna gain as \SI{2}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
-\emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector} for the case of WIT and WPT.
-As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}.
-For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ and a doubled harvester input power.
-Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which suggests an active scaling law in the order of $M^2$.
-On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$.
+\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design.
+To show the underlying performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
+\emph{Third,} passive beamforming has a larger array gain and power scaling order than active beamforming.
+This behavior is more obvious for the case of WIT and WPT.
+For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power.
+Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}.
+On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$ \cite{Wu2019}.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
@@
 Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-Moreover, the ASS strategy does not exploit the harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
 These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.
@@
 			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.
-$\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and unquantized IRS.}
+$\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
 		\end{figure}

### 2021-08-01 review/response_2.tex
:pencil: Update response letter

@@
 			\begin{framed}
-				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, which achieves local optimality with exponential computational complexity. [TODO]
+				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
 			\end{framed}
@@
 It has three clusters with \SI{50}{\ns} r.m.s.
-delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards.
+delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and set to \num{3.5} onwards.
 This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
@@
 		\begin{response}
-			TODO
+			We believe the reviewer was referring to the array gain and scaling law suggested by Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}.
+Recall that $M$ refers to the number of transmit antenna, $N$ refers to the number of subbands, and $L$ refers to the number of IRS elements.
+From the perspective of WIT, coherent transmission achieves an array gain of $M$ \cite{M-Tse2005} and coherent reflection achieves an array gain of $L^2$ \cite{M-Wu2019}.
+From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the multisine waveform.
+Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC current scales quadratically with $M$.
+We have cited those papers in the revised manuscript.
+
+			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario.
+Consider a SISO WPT system in a frequency-flat channel.
+We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted.
+With uniform power allocation ($s_n = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
+			\begin{equation}
+				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
+			\end{equation}
+			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
+			\begin{equation}
+				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N}.
+			\end{equation}
+			Taking expectation over $\lvert X \rvert$, we have
+			\begin{equation}
+				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
+			\end{equation}
+			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
 		\end{response}
@@
 		\begin{response}
-			TODO
+			Thank you for the suggestion.
 		\end{response}
@@
 		\begin{point}
-			If possible, in Fig.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
+			If possible, in Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
 		\end{point}
@@
 		\begin{response}
-			TODO
+			We would like to clarify that the performance loss under the conventional linear harvester model is revealed instead in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}.
+Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz} are intended to compare different IRS strategies when both waveform and passive beamforming are designed under nonlinear harvester model.
+The authors believe that to design passive beamforming under linear harvester model when the waveform is designed under nonlinear harvester model might confuse the readers.
+On the other hand, we agree with the reviewer that the performance loss under linear harvester deserves more attention, and have changed the label in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector} from `ASS' to `LEH' and revised the manuscript as follows to make this point clear.
+			\begin{framed}
+				\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design.
+To show the underlying performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
+As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
+			\end{framed}
 		\end{response}
@@
 		\begin{point}
-			It is said that the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}.
+			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}.
 It is not clear how the authors calculate this.
@@
 			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue.
-The parameter \SI{-35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without a second consideration.
-In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{-40}{\dB} at \SI{1}{\meter}.
+The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without a second consideration.
+In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}.
 The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards.
 This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
+
+			To avoid rerunning the simulation, in the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference.
+Please refer to the following specification for details.
+			\begin{framed}
+				We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}.
+Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
+All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D.
+The tap gains are modeled as i.i.d.
+CSCG variables.
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{M-Clerckx2016a}.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+			\end{framed}
 		\end{response}

### 2021-08-01 assets/waveform_wit_modulated.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16127375477314\\
2	3.16328124696217\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16000164000459\\
2	3.16455204336543\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23287518822941\\
2	2.2349269985345\\
3	2.23712082213722\\
4	2.2393436833526\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.23243942623434\\
2	2.23535811809091\\
3	2.23559687073864\\
4	2.24086923394096\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.56947570711734\\
2	1.57851757716824\\
3	1.58044033841813\\
4	1.58155392693919\\
5	1.58198101788601\\
6	1.58501068613205\\
7	1.5854415059255\\
8	1.58662414938375\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.56539227519679\\
2	1.57784161002588\\
3	1.57927371173129\\
4	1.58176667731984\\
5	1.58367655185228\\
6	1.58456745246925\\
7	1.58798555735369\\
8	1.58848608357287\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10024627987476\\
2	1.10664679147412\\
3	1.11204358490005\\
4	1.11548794498246\\
5	1.11636022580843\\
6	1.11667878555116\\
7	1.11706894724375\\
8	1.11773783143934\\
9	1.11958645829829\\
10	1.12088764958973\\
11	1.1221919201651\\
12	1.12315337822569\\
13	1.12435794296855\\
14	1.12469670812645\\
15	1.12549793104218\\
16	1.12556826383419\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.09504669861652\\
2	1.10317579191466\\
3	1.11227601228037\\
4	1.11361418816502\\
5	1.11483774301138\\
6	1.11656722620907\\
7	1.11743910790233\\
8	1.11769734992669\\
9	1.11854798737502\\
10	1.12003038718696\\
11	1.12377646668063\\
12	1.12467567262626\\
13	1.12655148101693\\
14	1.1274126433068\\
15	1.12796634097065\\
16	1.12836437582839\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-01 assets/waveform_wpt_modulated.tex
:bento: Update assets

--- 2021-08-01 assets/waveform_wit_modulated.tex
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	4.47213594256269\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	4.47213594337198\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	3.16127375477314\\
-2	3.16328124696217\\
+1	0.0184995683160857\\
+2	4.47209768702344\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	3.16000164000459\\
-2	3.16455204336543\\
+1	0.129245877350812\\
+2	4.47026793562064\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	2.23287518822941\\
-2	2.2349269985345\\
-3	2.23712082213722\\
-4	2.2393436833526\\
+1	1.22062490140461e-05\\
+2	1.39192509615866e-05\\
+3	0.000167256169027754\\
+4	4.30544303806377\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.23243942623434\\
-2	2.23535811809091\\
-3	2.23559687073864\\
-4	2.24086923394096\\
+1	9.33422606187999e-05\\
+2	0.00147978695861402\\
+3	0.00191364123320196\\
+4	4.17157348848167\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.56947570711734\\
-2	1.57851757716824\\
-3	1.58044033841813\\
-4	1.58155392693919\\
-5	1.58198101788601\\
-6	1.58501068613205\\
-7	1.5854415059255\\
-8	1.58662414938375\\
+1	1.79407563422514e-05\\
+2	1.85714620268948e-05\\
+3	1.93369863129044e-05\\
+4	2.05312064086965e-05\\
+5	2.39372760743564e-05\\
+6	0.000270300028092872\\
+7	0.0016215086351542\\
+8	0.0160756710767743\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.56539227519679\\
-2	1.57784161002588\\
-3	1.57927371173129\\
-4	1.58176667731984\\
-5	1.58367655185228\\
-6	1.58456745246925\\
-7	1.58798555735369\\
-8	1.58848608357287\\
+1	2.10931097834311e-05\\
+2	0.000139552824561586\\
+3	0.000276023439508691\\
+4	0.00106782286234867\\
+5	0.00351285453513694\\
+6	0.00648184617722918\\
+7	0.107736181700373\\
+8	0.176305935466697\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.10024627987476\\
-2	1.10664679147412\\
-3	1.11204358490005\\
-4	1.11548794498246\\
-5	1.11636022580843\\
-6	1.11667878555116\\
-7	1.11706894724375\\
-8	1.11773783143934\\
-9	1.11958645829829\\
-10	1.12088764958973\\
-11	1.1221919201651\\
-12	1.12315337822569\\
-13	1.12435794296855\\
-14	1.12469670812645\\
-15	1.12549793104218\\
-16	1.12556826383419\\
+1	2.1710720676869e-05\\
+2	2.17376236559091e-05\\
+3	2.17546727036312e-05\\
+4	2.17704747375875e-05\\
+5	2.1794882595919e-05\\
+6	2.18143527307804e-05\\
+7	2.18457881093868e-05\\
+8	2.19305951527728e-05\\
+9	2.19328455198334e-05\\
+10	2.21325751565748e-05\\
+11	2.22071274039942e-05\\
+12	2.25919792561307e-05\\
+13	2.32407144765052e-05\\
+14	3.96822628633167e-05\\
+15	7.14362303625945e-05\\
+16	0.000113723656309437\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.09504669861652\\
-2	1.10317579191466\\
-3	1.11227601228037\\
-4	1.11361418816502\\
-5	1.11483774301138\\
-6	1.11656722620907\\
-7	1.11743910790233\\
-8	1.11769734992669\\
-9	1.11854798737502\\
-10	1.12003038718696\\
-11	1.12377646668063\\
-12	1.12467567262626\\
-13	1.12655148101693\\
-14	1.1274126433068\\
-15	1.12796634097065\\
-16	1.12836437582839\\
+1	2.55678240861943e-05\\
+2	2.83329978735535e-05\\
+3	0.000111062823999827\\
+4	0.000152254112563635\\
+5	0.000208409153895756\\
+6	0.000340769670268019\\
+7	0.000442331617111308\\
+8	0.000478575211543757\\
+9	0.000624300142407434\\
+10	0.00101777812439063\\
+11	0.00411301301403382\\
+12	0.00600022404275364\\
+13	0.0141022990885949\\
+14	0.0215927071517045\\
+15	0.0287996793460057\\
+16	0.035646104685323\\
 };

### 2021-08-01 assets/waveform_wpt_multisine.tex
:bento: Update assets

--- 2021-08-01 assets/waveform_wit_modulated.tex
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	0.000331092582051402\\
 };
@@
 };
-\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}
+\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}
 
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	0.000301200841788861\\
 };
@@
 };
-\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}
+\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{P}}$}
 
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	3.16127375477314\\
-2	3.16328124696217\\
+1	8.31476170438795e-06\\
+2	8.59623838841982e-06\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	3.16000164000459\\
-2	3.16455204336543\\
+1	2.51350625686209e-05\\
+2	2.5738452816653e-05\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	2.23287518822941\\
-2	2.2349269985345\\
-3	2.23712082213722\\
-4	2.2393436833526\\
+1	1.81401011150761e-05\\
+2	7.63567990520219e-05\\
+3	0.000347720308108743\\
+4	1.20961154306659\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.23243942623434\\
-2	2.23535811809091\\
-3	2.23559687073864\\
-4	2.24086923394096\\
+1	0.00111014489403298\\
+2	0.00243652079053788\\
+3	0.00358274270606404\\
+4	1.61181535442991\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.56947570711734\\
-2	1.57851757716824\\
-3	1.58044033841813\\
-4	1.58155392693919\\
-5	1.58198101788601\\
-6	1.58501068613205\\
-7	1.5854415059255\\
-8	1.58662414938375\\
+1	0.406193755485101\\
+2	0.6086191375554\\
+3	0.70781380097226\\
+4	1.11700551493449\\
+5	1.39413019214519\\
+6	1.89924922357725\\
+7	2.27606557910904\\
+8	2.64280256661518\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.56539227519679\\
-2	1.57784161002588\\
-3	1.57927371173129\\
-4	1.58176667731984\\
-5	1.58367655185228\\
-6	1.58456745246925\\
-7	1.58798555735369\\
-8	1.58848608357287\\
+1	0.621345098069754\\
+2	0.710296651693143\\
+3	0.908023988477654\\
+4	1.12050035456782\\
+5	1.44244708781013\\
+6	1.77492365099369\\
+7	2.30702814170141\\
+8	2.53638471775812\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.10024627987476\\
-2	1.10664679147412\\
-3	1.11204358490005\\
-4	1.11548794498246\\
-5	1.11636022580843\\
-6	1.11667878555116\\
-7	1.11706894724375\\
-8	1.11773783143934\\
-9	1.11958645829829\\
-10	1.12088764958973\\
-11	1.1221919201651\\
-12	1.12315337822569\\
-13	1.12435794296855\\
-14	1.12469670812645\\
-15	1.12549793104218\\
-16	1.12556826383419\\
+1	0.280439553353647\\
+2	0.384605443069534\\
+3	0.416114603863305\\
+4	0.499024317224016\\
+5	0.571268128602638\\
+6	0.621900186283823\\
+7	0.763344617968865\\
+8	0.858693319856245\\
+9	0.954356161751161\\
+10	1.16907743761735\\
+11	1.21561270661726\\
+12	1.45089690540298\\
+13	1.51204499963039\\
+14	1.68681223326519\\
+15	1.74569476977388\\
+16	1.81071246294588\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.09504669861652\\
-2	1.10317579191466\\
-3	1.11227601228037\\
-4	1.11361418816502\\
-5	1.11483774301138\\
-6	1.11656722620907\\
-7	1.11743910790233\\
-8	1.11769734992669\\
-9	1.11854798737502\\
-10	1.12003038718696\\
-11	1.12377646668063\\
-12	1.12467567262626\\
-13	1.12655148101693\\
-14	1.1274126433068\\
-15	1.12796634097065\\
-16	1.12836437582839\\
+1	0.447567787711277\\
+2	0.504906671531525\\
+3	0.589458291557858\\
+4	0.619646960375962\\
+5	0.691059903147371\\
+6	0.741736916016998\\
+7	0.810826698348076\\
+8	0.887751406400927\\
+9	0.941910732226763\\
+10	1.15698606523739\\
+11	1.20259880483264\\
+12	1.42353667332449\\
+13	1.46532152628089\\
+14	1.65027292091107\\
+15	1.65828648619566\\
+16	1.73730645060792\\
 };

### 2021-08-02 assets/channel_amplitude.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,3.397in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS}

\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00757609645318138\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: WIT}

\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00757609644840316\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: WPT}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,2.663in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.928in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.193in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/channel_amplitude_100reflectors.tex
:bento: Update assets

--- 2021-08-02 assets/channel_amplitude.tex
@@
 width=4.036in,
-height=0.457in,
-at={(0.677in,3.397in)},
+height=0.407in,
+at={(0.677in,3.198in)},
 scale only axis,
@@
 ymax=0.01,
+ytick={   0, 0.01},
 axis background/.style={fill=white},
@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black},
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]
@@
 width=4.036in,
-height=0.457in,
-at={(0.677in,2.663in)},
+height=0.407in,
+at={(0.677in,2.513in)},
 scale only axis,
@@
 ymajorgrids,
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]
@@
 width=4.036in,
-height=0.457in,
-at={(0.677in,1.928in)},
+height=0.407in,
+at={(0.677in,1.828in)},
 scale only axis,
@@
 ymax=0.01,
+ytick={   0, 0.01},
 ylabel style={font=\color{white!15!black}},
@@
 width=4.036in,
-height=0.457in,
-at={(0.677in,1.193in)},
+height=0.407in,
+at={(0.677in,1.143in)},
 scale only axis,
@@
 width=4.036in,
-height=0.457in,
+height=0.407in,
 at={(0.677in,0.458in)},

### 2021-08-02 assets/convergence_bcd.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,2.455in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=0,
ymax=23.9521333022272,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.9477142509994\\
3	23.9521333022272\\
4	23.9521333022272\\
5	23.9521333022272\\
6	23.9521333022272\\
7	23.9521333022272\\
8	23.9521333022272\\
9	23.9521333022272\\
10	23.9521333022272\\
11	23.9521333022272\\
12	23.9521333022272\\
13	23.9521333022272\\
14	23.9521333022272\\
15	23.9521333022272\\
};
\addlegendentry{BCD}

\end{axis}

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=0,
ymax=23.4661978529908,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.4267512312375\\
3	23.4652236267543\\
4	23.4661978529908\\
5	23.4661978529908\\
6	23.4661978529908\\
7	23.4661978529908\\
8	23.4661978529908\\
9	23.4661978529908\\
10	23.4661978529908\\
11	23.4661978529908\\
12	23.4661978529908\\
13	23.4661978529908\\
14	23.4661978529908\\
15	23.4661978529908\\
};
\addlegendentry{LC-BCD}

\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/convergence_sca.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,2.433in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=23.6,
ymax=24,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	23.6339898147867\\
2	23.9359168430033\\
3	23.9359212944279\\
4	23.9359212944279\\
5	23.9359212944279\\
6	23.9359212944279\\
7	23.9359212944279\\
8	23.9359212944279\\
9	23.9359212944279\\
10	23.9359212944279\\
11	23.9359212944279\\
12	23.9359212944279\\
13	23.9359212944279\\
14	23.9359212944279\\
15	23.9359212944279\\
};
\addlegendentry{SCA}

\end{axis}

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=23.1,
ymax=23.4267428478373,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	23.1650475635163\\
2	23.4267359303359\\
3	23.4267428478373\\
4	23.4267428478373\\
5	23.4267428478373\\
6	23.4267428478373\\
7	23.4267428478373\\
8	23.4267428478373\\
9	23.4267428478373\\
10	23.4267428478373\\
11	23.4267428478373\\
12	23.4267428478373\\
13	23.4267428478373\\
14	23.4267428478373\\
15	23.4267428478373\\
};
\addlegendentry{M-SCA}

\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/waveform_subband.tex
:bento: Update assets

--- 2021-04-08 assets/waveform_subband.tex
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,3.374in)},
+height=0.438in,
+at={(0.677in,3.233in)},
 scale only axis,
@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black},
+legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
 title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	2.82172701356454\\
+1	4.47213593413934\\
 };
@@
 };
-\addlegendentry{$s_I$}
+\addlegendentry{{\boldmath${s}$}$_{\mathrm{I}}$}
 
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000255961727675924\\
+1	0.000411418946938571\\
 };
@@
 };
-\addlegendentry{$s_P$}
+\addlegendentry{{\boldmath${s}$}$_{\mathrm{P}}$}
 
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,2.645in)},
+height=0.438in,
+at={(0.677in,2.54in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.19551151069007\\
-2	2.79441682266723\\
+1	0.434593216761001\\
+2	4.3899297145933\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	6.76001760054032e-06\\
-2	6.94107248595388e-06\\
+1	1.15579196934664e-05\\
+2	1.1748417131072e-05\\
 };
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,1.916in)},
+height=0.438in,
+at={(0.677in,1.846in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00471916738670986\\
-2	0.0113013795751173\\
-3	0.0524973569625421\\
-4	1.11631746294063\\
+1	0.0143736245770149\\
+2	0.0303952314208929\\
+3	0.115397989725443\\
+4	1.83286171599636\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.666856968017446\\
-2	0.826759550766013\\
-3	0.96159816303766\\
-4	1.2653467150935\\
+1	1.03274778152889\\
+2	1.26444789136652\\
+3	1.50497289223671\\
+4	2.05482037288244\\
 };
@@
 width=4.036in,
-height=0.481in,
-at={(0.677in,1.187in)},
+height=0.438in,
+at={(0.677in,1.152in)},
 scale only axis,
@@
 ymin=0,
+ytick={0, 1},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000872616544376037\\
-2	0.00117960004406015\\
-3	0.00161605407069224\\
-4	0.00228266132463128\\
-5	0.00326342365821\\
-6	0.00487936277124623\\
-7	0.00881039674196349\\
-8	0.0419634199055652\\
+1	0.00193817595567525\\
+2	0.00257713054060487\\
+3	0.00348488793501541\\
+4	0.00488691757665795\\
+5	0.00708186101407546\\
+6	0.0115819776031387\\
+7	0.0297619841444503\\
+8	0.248823174288891\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.633590459263079\\
-2	0.785594177316295\\
-3	0.891389674009387\\
-4	0.98505471211105\\
-5	1.05090474986801\\
-6	1.10664902589546\\
-7	1.1412268011736\\
-8	1.16708811938208\\
+1	0.958056681914786\\
+2	1.1753523246861\\
+3	1.34398156020033\\
+4	1.48468938243277\\
+5	1.59662285127524\\
+6	1.68382811164256\\
+7	1.75299266281476\\
+8	1.84970533450897\\
 };
@@
 width=4.036in,
-height=0.481in,
+height=0.438in,
 at={(0.677in,0.458in)},
@@
 ymin=0,
-ytick={  0, 0.4, 0.8},
+ytick={0, 1},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000310341555926487\\
-2	0.00035799764238\\
-3	0.00041670813086453\\
-4	0.000484920116868764\\
-5	0.000569098471381299\\
-6	0.000669877208860123\\
-7	0.000793268903064817\\
-8	0.000939331113982085\\
-9	0.0011175247904389\\
-10	0.00132972829292326\\
-11	0.0015875351976808\\
-12	0.00189182501786478\\
-13	0.00226771472661325\\
-14	0.00272021545715682\\
-15	0.00331689397668614\\
-16	0.00407528165955271\\
+1	0.000699803366708424\\
+2	0.000800867722584431\\
+3	0.000917767493119273\\
+4	0.00105546869283256\\
+5	0.0012213408897823\\
+6	0.00141507752657299\\
+7	0.00165144517333923\\
+8	0.00193060125433753\\
+9	0.00227670870277157\\
+10	0.0027030187224025\\
+11	0.00324897530466221\\
+12	0.00397867693137808\\
+13	0.00501781698344776\\
+14	0.00655613193903264\\
+15	0.009024934371904\\
+16	0.0130872335381684\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.428729933737136\\
-2	0.489701018897442\\
-3	0.539263608495876\\
-4	0.585347098517275\\
-5	0.624083102405944\\
-6	0.657759147074073\\
-7	0.689461005203993\\
-8	0.715900755845553\\
-9	0.741047135425173\\
-10	0.761923826165851\\
-11	0.78165448191713\\
-12	0.796874354752371\\
-13	0.810144534289869\\
-14	0.819572643230985\\
-15	0.826293720140692\\
-16	0.829491639456529\\
+1	0.658945444448673\\
+2	0.748750326986652\\
+3	0.825803524447847\\
+4	0.897209109075901\\
+5	0.959520330551997\\
+6	1.01644204271237\\
+7	1.07098120306596\\
+8	1.11834785156968\\
+9	1.16491430867279\\
+10	1.20444111502631\\
+11	1.24260696441405\\
+12	1.27263946826968\\
+13	1.29990806955352\\
+14	1.31826230888077\\
+15	1.33150577776743\\
+16	1.33694997002172\\
 };

### 2021-08-02 assets/waveform_wit_modulated_100reflectors.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.429in,
at={(0.677in,3.242in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.429in,
at={(0.677in,2.546in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16197544010622\\
2	3.16257985135002\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16115798980538\\
2	3.16339693422903\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.429in,
at={(0.677in,1.85in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23378952118842\\
2	2.23654464483002\\
3	2.23679993610816\\
4	2.23713622127432\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.22545319620151\\
2	2.23919103086275\\
3	2.23937811584463\\
4	2.24021589430493\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.429in,
at={(0.677in,1.154in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.57492536161738\\
2	1.58019558798915\\
3	1.58142030797172\\
4	1.58199169722726\\
5	1.58244513043393\\
6	1.58255247448636\\
7	1.58277901011216\\
8	1.58278544606781\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.54658301793324\\
2	1.57890604600973\\
3	1.58567053153604\\
4	1.58602764687811\\
5	1.58742152113889\\
6	1.58776504632019\\
7	1.58809335949322\\
8	1.5881928373826\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.429in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10693759886133\\
2	1.11152957304454\\
3	1.1153740214668\\
4	1.11770662066146\\
5	1.11834620668734\\
6	1.11879936603067\\
7	1.11890444505621\\
8	1.11953756000214\\
9	1.11961027059849\\
10	1.1199195311366\\
11	1.12011494881618\\
12	1.12017416958603\\
13	1.12033284686217\\
14	1.12033895948864\\
15	1.12040846172897\\
16	1.12041390652564\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.05608889731275\\
2	1.08431501210806\\
3	1.10834050856176\\
4	1.11891055117252\\
5	1.12321530567299\\
6	1.12470216682288\\
7	1.12523793678797\\
8	1.12552298915589\\
9	1.12642268676024\\
10	1.12689100352585\\
11	1.127202079253\\
12	1.12763006638833\\
13	1.12766695997673\\
14	1.12788476342969\\
15	1.1278991085713\\
16	1.12794901573584\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/waveform_wpt_modulated_100reflectors.tex
:bento: Update assets

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.474in,
at={(0.677in,3.198in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595034367\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213593685897\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.474in,
at={(0.677in,2.513in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000570870326956724\\
2	4.4721359179404\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0110856763978608\\
2	4.47212221176042\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.474in,
at={(0.677in,1.828in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.82810775851695e-05\\
2	3.53085892593064e-05\\
3	3.54347120351704e-05\\
4	4.42555930751421\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.22676166428777e-05\\
2	2.19662118918467e-05\\
3	2.35611473414708e-05\\
4	4.38314990531919\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.474in,
at={(0.677in,1.143in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	6.25263040326118e-06\\
2	6.27921380470113e-06\\
3	6.34955721457943e-06\\
4	6.35150273149039e-06\\
5	6.42390701416729e-06\\
6	6.42457974220412e-06\\
7	6.47741859691329e-06\\
8	6.47969375628299e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.07597912435039e-05\\
2	2.10621157490525e-05\\
3	2.27177871268911e-05\\
4	2.34764127724776e-05\\
5	0.000633429285281999\\
6	0.00299168089473067\\
7	0.0168627108170759\\
8	0.0302609478988545\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.474in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.46841221768753e-06\\
2	1.46853581584948e-06\\
3	1.46888556831603e-06\\
4	1.46960879811052e-06\\
5	1.47063822579491e-06\\
6	1.47112726920342e-06\\
7	1.47158812622008e-06\\
8	1.47177039924161e-06\\
9	1.47273523214333e-06\\
10	1.47288042283048e-06\\
11	1.47389962773962e-06\\
12	1.47396082891411e-06\\
13	1.47467419234042e-06\\
14	1.47476166458671e-06\\
15	1.47506643379659e-06\\
16	1.47509099313304e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.08632407458004e-05\\
2	1.08877007745949e-05\\
3	1.09594364217047e-05\\
4	1.10938027865036e-05\\
5	1.12827891666553e-05\\
6	1.15378065652616e-05\\
7	1.19617266900702e-05\\
8	1.41613520483063e-05\\
9	6.92466622068608e-05\\
10	0.000224790946436711\\
11	0.000536194940235116\\
12	0.0020179447121528\\
13	0.00228142595005787\\
14	0.00484194141261625\\
15	0.00509975660438143\\
16	0.00611499201390601\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-02 assets/waveform_wpt_multisine_100reflectors.tex
:bento: Update assets

--- 2021-08-02 assets/waveform_wpt_modulated_100reflectors.tex
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	4.47213595034367\\
+1	0.000179640013528533\\
 };
@@
 };
-\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}
+\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}
 
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	4.47213593685897\\
+1	0.000397123673947016\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000570870326956724\\
-2	4.4721359179404\\
+1	3.79500700797208e-06\\
+2	4.08912055500049e-06\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.0110856763978608\\
-2	4.47212221176042\\
+1	1.49290916575988e-05\\
+2	1.5984007495811e-05\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.82810775851695e-05\\
-2	3.53085892593064e-05\\
-3	3.54347120351704e-05\\
-4	4.42555930751421\\
+1	1.7047574186968e-05\\
+2	5.43653691324513e-05\\
+3	5.45654270177953e-05\\
+4	0.643758338055473\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.22676166428777e-05\\
-2	2.19662118918467e-05\\
-3	2.35611473414708e-05\\
-4	4.38314990531919\\
+1	1.36848368645437e-05\\
+2	2.47445070835246e-05\\
+3	2.69448998495505e-05\\
+4	0.887691893042722\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	6.25263040326118e-06\\
-2	6.27921380470113e-06\\
-3	6.34955721457943e-06\\
-4	6.35150273149039e-06\\
-5	6.42390701416729e-06\\
-6	6.42457974220412e-06\\
-7	6.47741859691329e-06\\
-8	6.47969375628299e-06\\
+1	0.0867788582585271\\
+2	0.354584687432597\\
+3	0.978311956865194\\
+4	1.00526014633142\\
+5	1.77421254564815\\
+6	1.81146146011329\\
+7	2.39316922290828\\
+8	2.39637542235877\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.07597912435039e-05\\
-2	2.10621157490525e-05\\
-3	2.27177871268911e-05\\
-4	2.34764127724776e-05\\
-5	0.000633429285281999\\
-6	0.00299168089473067\\
-7	0.0168627108170759\\
-8	0.0302609478988545\\
+1	0.0902176300392888\\
+2	0.346545381997116\\
+3	0.920392715728033\\
+4	1.00603974348273\\
+5	1.68636658487784\\
+6	1.88211529376329\\
+7	2.36040788303805\\
+8	2.46040714408403\\
 };
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.46841221768753e-06\\
-2	1.46853581584948e-06\\
-3	1.46888556831603e-06\\
-4	1.46960879811052e-06\\
-5	1.47063822579491e-06\\
-6	1.47112726920342e-06\\
-7	1.47158812622008e-06\\
-8	1.47177039924161e-06\\
-9	1.47273523214333e-06\\
-10	1.47288042283048e-06\\
-11	1.47389962773962e-06\\
-12	1.47396082891411e-06\\
-13	1.47467419234042e-06\\
-14	1.47476166458671e-06\\
-15	1.47506643379659e-06\\
-16	1.47509099313304e-06\\
+1	0.0464370103565898\\
+2	0.0888998754115983\\
+3	0.182477468723257\\
+4	0.351067698858224\\
+5	0.586511157963407\\
+6	0.614337078252067\\
+7	0.810319773242887\\
+8	0.860994249853337\\
+9	1.10132170987082\\
+10	1.14707079761106\\
+11	1.39883656543765\\
+12	1.41535986846215\\
+13	1.61724209266044\\
+14	1.62252465458191\\
+15	1.72749872908311\\
+16	1.73005229015507\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.08632407458004e-05\\
-2	1.08877007745949e-05\\
-3	1.09594364217047e-05\\
-4	1.10938027865036e-05\\
-5	1.12827891666553e-05\\
-6	1.15378065652616e-05\\
-7	1.19617266900702e-05\\
-8	1.41613520483063e-05\\
-9	6.92466622068608e-05\\
-10	0.000224790946436711\\
-11	0.000536194940235116\\
-12	0.0020179447121528\\
-13	0.00228142595005787\\
-14	0.00484194141261625\\
-15	0.00509975660438143\\
-16	0.00611499201390601\\
+1	0.0510852453116461\\
+2	0.0931309188028207\\
+3	0.185327611314329\\
+4	0.340208570070271\\
+5	0.54797982875002\\
+6	0.640935330786823\\
+7	0.791412536150533\\
+8	0.84579943866006\\
+9	1.06112099796475\\
+10	1.16793555562456\\
+11	1.33939925851288\\
+12	1.47707717171709\\
+13	1.57685904146789\\
+14	1.6756197826186\\
+15	1.71965928671636\\
+16	1.75172173644803\\
 };

### 2021-08-02 main.tex
:pencil: Update manuscript

@@
 In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
 A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
@@
 			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
+In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.
 For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
@@
 
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\subfloat[Channel]{
+		% 		\resizebox{0.45\columnwidth}{!}{
+		% 			\input{assets/channel_amplitude_100reflectors.tex}
+		% 		}
+		% 	}
+		% 	\subfloat[WIT waveform: modulated]{
+		% 		\resizebox{0.45\columnwidth}{!}{
+		% 			\input{assets/waveform_wit_modulated_100reflectors.tex}
+		% 		}
+		% 	}\\
+		% 	\subfloat[WPT waveform: modulated]{
+		% 		\resizebox{0.45\columnwidth}{!}{
+		% 			\input{assets/waveform_wpt_modulated_100reflectors.tex}
+		% 		}
+		% 	}
+		% 	\subfloat[WPT waveform: multisine]{
+		% 		\resizebox{0.45\columnwidth}{!}{
+		% 			\input{assets/waveform_wpt_multisine_100reflectors.tex}
+		% 		}
+		% 	}
+		% 	\caption{Sorted channel and waveform amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+		% 	\label{fi:amplitude}
+		% \end{figure}
+
 		\begin{figure}[!t]
@@
 To show the underlying performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to the nonlinear model-based SMF and GP.
 \emph{Third,} passive beamforming has a larger array gain and power scaling order than active beamforming.

### 2021-08-02 review/response_2.tex
:pencil: Update response letter

@@
 \usepackage{cite}
+\usepackage{graphicx}
 \usepackage{framed}
@@
 
+\newcommand{\editor}
+	{\bigskip \hrule \section*{Editor}}
+
 \newcommand{\reviewer}
@@
 	\includepdf{letter_2.pdf}
+
+	\begin{editor}
+		\begin{point}
+			Please double-check Proposition~\ref{M-pr:bcd} and the algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
+		\end{point}
+
+		\begin{response}
+			Thank you for pointing this out. The editor is referred to Response~\ref{re:3.1}.
+		\end{response}
+
+		\begin{point}
+			Please discuss the convergence criteria in details and justify the formulated optimization problem.
+		\end{point}
+
+		\begin{response}
+			Please refer to Response~\ref{re:1.4}.
+		\end{response}
+
+		\begin{point}
+			How does the IRS passive beamforming impact on the waveform design compared with existing systems?
+		\end{point}
+
+		\begin{response}
+			Please refer to Response~\ref{re:2.2}.
+		\end{response}
+
+		\begin{point}
+			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
+		\end{point}
+
+		\begin{response}
+			Please refer to Response~\ref{re:2.3}.
+		\end{response}
+	\end{editor}
 
@@
 			\end{framed}
+
+			% As for the measurements, we evaluate the converging speed of all proposed algorithms.
+Figs.~\ref{fi:convergence_sca}--\ref{fi:convergence_bcd} show the output DC current versus the number of iterations for one channel realization at the WPT point.
+It is observed that the SCA- and BCD-based algorithms typically converge within \num{3} iterations while the GP-based algorithm takes around \num{9} iterations to converge.
+Those figures are not added to the manuscript due to the space constraint.
+			% \begin{figure}[!t]
+			% 	\centering
+			% 	\subfloat[SCA-based\label{fi:convergence_sca}]{
+			% 		\resizebox{0.32\columnwidth}{!}{
+			% 			\input{../assets/convergence_sca.tex}
+			% 		}
+			% 	}
+			% 	\subfloat[GP-based\label{fi:convergence_gp}]{
+			% 		\resizebox{0.32\columnwidth}{!}{
+			% 			\input{../assets/convergence_gp.tex}
+			% 		}
+			% 	}
+			% 	\subfloat[BCD-based\label{fi:convergence_bcd}]{
+			% 		\resizebox{0.32\columnwidth}{!}{
+			% 			\input{../assets/convergence_bcd.tex}
+			% 		}
+			% 	}
+			% 	\caption{Converging trend of the proposed algorithms for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$..}
+			% \end{figure}
 			\label{re:1.1}
@@
 				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model accounting AoA and AoD.
-To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
+
+				\textellipsis To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
 In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
@@
 			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}
+			\label{re:1.4}
 		\end{response}
@@
 From the perspective of WIT, coherent transmission achieves an array gain of $M$ \cite{M-Tse2005} and coherent reflection achieves an array gain of $L^2$ \cite{M-Wu2019}.
-From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the multisine waveform.
+From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the modulated and multisine waveforms.
 Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC current scales quadratically with $M$.
@@
 We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted.
-With uniform power allocation ($s_n = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
+With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
 			\begin{equation}
@@
 			\begin{equation}
-				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N}.
+				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N} P^2.
 			\end{equation}
@@
 			Thank you for the suggestion.
+Too see this, we first show two realizations of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}.
+It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).
+
+			\begin{figure}[!h]
+				\centering
+				\resizebox{0.6\columnwidth}{!}{
+					\includegraphics{../assets/channel_amplitude_100reflectors}
+				}
+				\caption{Channel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\label{fi:channel_amplitude}
+			\end{figure}
+
+			On the other hand, the corresponding amplitude of modulated and multisine waveforms are shown in Fig.~\ref{fi:waveform_amplitude}.
+Note that no multisine is used for WIT and the case is not shown.
+It is observed that although passive beamforming can enable a flexible resource allocation opportunity at the channel (please refer to Response~\ref{re:2.10} for details), its impact on waveform design is unobvious.
+
+			\begin{figure}[!h]
+				\centering
+				\subfloat[WIT waveform: modulated]{
+				\resizebox{0.32\columnwidth}{!}{
+						\input{../assets/waveform_wit_modulated_100reflectors.tex}
+					}
+				}
+				\subfloat[WPT waveform: modulated]{
+					\resizebox{0.32\columnwidth}{!}{
+						\input{../assets/waveform_wpt_modulated_100reflectors.tex}
+					}
+				}
+				\subfloat[WPT waveform: multisine]{
+					\resizebox{0.32\columnwidth}{!}{
+						\input{../assets/waveform_wpt_multisine_100reflectors.tex}
+					}
+				}
+				\caption{Sorted modulated and multisine amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\label{fi:waveform_amplitude}
+			\end{figure}
+			\label{re:2.2}
 		\end{response}
@@
 				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and non-concavity from high-order objective function.
 			\end{framed}
+			\label{re:2.3}
 		\end{response}
@@
 Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff.
-Indeed, the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
+Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.
 However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead.
@@
 
-				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
+				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.
 
@@
 To show the underlying performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
-As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
+As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to the nonlinear model-based SMF and GP.
 			\end{framed}
@@
 		\begin{response}
-			By ``auxiliary link control in the frequency domain'', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS.
+			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS.
 The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
@@
 			\end{framed}
+			\label{re:2.10}
 		\end{response}
@@
 		\begin{response}
-			We sincerely appreciate the reviewer for pointing out this issue.
+			Thank you for pointing out this issue.
 Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together.
@@
 			\end{framed}
+			\label{re:3.1}
 		\end{response}
@@
 			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue.
-The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without a second consideration.
+The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without careful consideration.
 In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}.
-The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards.
+The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
 This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
 
-			To avoid rerunning the simulation, in the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference.
+			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference and maintain the simulation results in the same level.
 Please refer to the following specification for details.
@@
 The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$.
-We are aware that direct quantization can lead to performance loss compared with optimization over feasible phase shift set.
+We are aware that quantization can lead to performance loss compared with direct optimization over feasible phase shift set.
 In the revised manuscript, we have emphasized this point as follows.
@@
 				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model accounting AoA and AoD.
+It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
 			\end{framed}
@@
 		\begin{response}
-			We have incorporated the reference into the manuscript as follows.
+			We have incorporated aforementioned references into the manuscript as follows.
 			\begin{framed}

### 2021-08-02 src/config/config_re_waveform.m
:wrench: Update config

@@ -39,7 +39,7 @@ bandwidth = 1e7;
 % channel fading mode ('flat' or 'selective')
 fadingMode = 'selective';
 % number of reflecting elements in IRS
-nReflectors = 20;
+nReflectors = 1e2;
 % spatial correlation
 corTx = eye(nTxs);
 corRx = eye(nRxs);

### 2021-08-03 assets/waveform_wit_modulated.tex
:bento: Update assets

@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,3.312in)},
+width=4.036in,
+height=0.376in,
+at={(0.677in,3.296in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=5,
+ytick={0, 2, 4},
 axis background/.style={fill=white},
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,2.598in)},
+width=4.036in,
+height=0.376in,
+at={(0.677in,2.586in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=3.16339693422903,
+ytick={0, 2, 4},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	3.16127375477314\\
-2	3.16328124696217\\
+1	3.16197544010622\\
+2	3.16257985135002\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	3.16000164000459\\
-2	3.16455204336543\\
+1	3.16115798980538\\
+2	3.16339693422903\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.883in)},
+width=4.036in,
+height=0.376in,
+at={(0.677in,1.877in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=2.24021589430493,
+ytick={0, 2, 4},
 ylabel style={font=\color{white!15!black}},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	2.23287518822941\\
-2	2.2349269985345\\
-3	2.23712082213722\\
-4	2.2393436833526\\
+1	2.23378952118842\\
+2	2.23654464483002\\
+3	2.23679993610816\\
+4	2.23713622127432\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.23243942623434\\
-2	2.23535811809091\\
-3	2.23559687073864\\
-4	2.24086923394096\\
+1	2.22545319620151\\
+2	2.23919103086275\\
+3	2.23937811584463\\
+4	2.24021589430493\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.168in)},
+width=4.036in,
+height=0.376in,
+at={(0.677in,1.168in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=2,
+ytick={0, 1, 2},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.56947570711734\\
-2	1.57851757716824\\
-3	1.58044033841813\\
-4	1.58155392693919\\
-5	1.58198101788601\\
-6	1.58501068613205\\
-7	1.5854415059255\\
-8	1.58662414938375\\
+1	1.57492536161738\\
+2	1.58019558798915\\
+3	1.58142030797172\\
+4	1.58199169722726\\
+5	1.58244513043393\\
+6	1.58255247448636\\
+7	1.58277901011216\\
+8	1.58278544606781\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.56539227519679\\
-2	1.57784161002588\\
-3	1.57927371173129\\
-4	1.58176667731984\\
-5	1.58367655185228\\
-6	1.58456745246925\\
-7	1.58798555735369\\
-8	1.58848608357287\\
+1	1.54658301793324\\
+2	1.57890604600973\\
+3	1.58567053153604\\
+4	1.58602764687811\\
+5	1.58742152113889\\
+6	1.58776504632019\\
+7	1.58809335949322\\
+8	1.5881928373826\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,0.454in)},
+width=4.036in,
+height=0.376in,
+at={(0.677in,0.458in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.10024627987476\\
-2	1.10664679147412\\
-3	1.11204358490005\\
-4	1.11548794498246\\
-5	1.11636022580843\\
-6	1.11667878555116\\
-7	1.11706894724375\\
-8	1.11773783143934\\
-9	1.11958645829829\\
-10	1.12088764958973\\
-11	1.1221919201651\\
-12	1.12315337822569\\
-13	1.12435794296855\\
-14	1.12469670812645\\
-15	1.12549793104218\\
-16	1.12556826383419\\
+1	1.10693759886133\\
+2	1.11152957304454\\
+3	1.1153740214668\\
+4	1.11770662066146\\
+5	1.11834620668734\\
+6	1.11879936603067\\
+7	1.11890444505621\\
+8	1.11953756000214\\
+9	1.11961027059849\\
+10	1.1199195311366\\
+11	1.12011494881618\\
+12	1.12017416958603\\
+13	1.12033284686217\\
+14	1.12033895948864\\
+15	1.12040846172897\\
+16	1.12041390652564\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.09504669861652\\
-2	1.10317579191466\\
-3	1.11227601228037\\
-4	1.11361418816502\\
-5	1.11483774301138\\
-6	1.11656722620907\\
-7	1.11743910790233\\
-8	1.11769734992669\\
-9	1.11854798737502\\
-10	1.12003038718696\\
-11	1.12377646668063\\
-12	1.12467567262626\\
-13	1.12655148101693\\
-14	1.1274126433068\\
-15	1.12796634097065\\
-16	1.12836437582839\\
+1	1.05608889731275\\
+2	1.08431501210806\\
+3	1.10834050856176\\
+4	1.11891055117252\\
+5	1.12321530567299\\
+6	1.12470216682288\\
+7	1.12523793678797\\
+8	1.12552298915589\\
+9	1.12642268676024\\
+10	1.12689100352585\\
+11	1.127202079253\\
+12	1.12763006638833\\
+13	1.12766695997673\\
+14	1.12788476342969\\
+15	1.1278991085713\\
+16	1.12794901573584\\
 };

### 2021-08-03 assets/waveform_wpt_modulated.tex
:bento: Update assets

--- 2021-08-01 assets/waveform_wit_modulated.tex
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,3.312in)},
+width=4.036in,
+height=0.42in,
+at={(0.677in,3.251in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	4.47213595034367\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	4.47213595499958\\
+1	4.47213593685897\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,2.598in)},
+width=4.036in,
+height=0.42in,
+at={(0.677in,2.553in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	3.16127375477314\\
-2	3.16328124696217\\
+1	0.000570870326956724\\
+2	4.4721359179404\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	3.16000164000459\\
-2	3.16455204336543\\
+1	0.0110856763978608\\
+2	4.47212221176042\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.883in)},
+width=4.036in,
+height=0.42in,
+at={(0.677in,1.855in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=5,
+ytick={0, 2, 4},
 ylabel style={font=\color{white!15!black}},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	2.23287518822941\\
-2	2.2349269985345\\
-3	2.23712082213722\\
-4	2.2393436833526\\
+1	1.82810775851695e-05\\
+2	3.53085892593064e-05\\
+3	3.54347120351704e-05\\
+4	4.42555930751421\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.23243942623434\\
-2	2.23535811809091\\
-3	2.23559687073864\\
-4	2.24086923394096\\
+1	1.22676166428777e-05\\
+2	2.19662118918467e-05\\
+3	2.35611473414708e-05\\
+4	4.38314990531919\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.168in)},
+width=4.036in,
+height=0.42in,
+at={(0.677in,1.157in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=1,
+ytick={0, 1},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.56947570711734\\
-2	1.57851757716824\\
-3	1.58044033841813\\
-4	1.58155392693919\\
-5	1.58198101788601\\
-6	1.58501068613205\\
-7	1.5854415059255\\
-8	1.58662414938375\\
+1	6.25263040326118e-06\\
+2	6.27921380470113e-06\\
+3	6.34955721457943e-06\\
+4	6.35150273149039e-06\\
+5	6.42390701416729e-06\\
+6	6.42457974220412e-06\\
+7	6.47741859691329e-06\\
+8	6.47969375628299e-06\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.56539227519679\\
-2	1.57784161002588\\
-3	1.57927371173129\\
-4	1.58176667731984\\
-5	1.58367655185228\\
-6	1.58456745246925\\
-7	1.58798555735369\\
-8	1.58848608357287\\
+1	2.07597912435039e-05\\
+2	2.10621157490525e-05\\
+3	2.27177871268911e-05\\
+4	2.34764127724776e-05\\
+5	0.000633429285281999\\
+6	0.00299168089473067\\
+7	0.0168627108170759\\
+8	0.0302609478988545\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,0.454in)},
+width=4.036in,
+height=0.42in,
+at={(0.677in,0.458in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.10024627987476\\
-2	1.10664679147412\\
-3	1.11204358490005\\
-4	1.11548794498246\\
-5	1.11636022580843\\
-6	1.11667878555116\\
-7	1.11706894724375\\
-8	1.11773783143934\\
-9	1.11958645829829\\
-10	1.12088764958973\\
-11	1.1221919201651\\
-12	1.12315337822569\\
-13	1.12435794296855\\
-14	1.12469670812645\\
-15	1.12549793104218\\
-16	1.12556826383419\\
+1	1.46841221768753e-06\\
+2	1.46853581584948e-06\\
+3	1.46888556831603e-06\\
+4	1.46960879811052e-06\\
+5	1.47063822579491e-06\\
+6	1.47112726920342e-06\\
+7	1.47158812622008e-06\\
+8	1.47177039924161e-06\\
+9	1.47273523214333e-06\\
+10	1.47288042283048e-06\\
+11	1.47389962773962e-06\\
+12	1.47396082891411e-06\\
+13	1.47467419234042e-06\\
+14	1.47476166458671e-06\\
+15	1.47506643379659e-06\\
+16	1.47509099313304e-06\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.09504669861652\\
-2	1.10317579191466\\
-3	1.11227601228037\\
-4	1.11361418816502\\
-5	1.11483774301138\\
-6	1.11656722620907\\
-7	1.11743910790233\\
-8	1.11769734992669\\
-9	1.11854798737502\\
-10	1.12003038718696\\
-11	1.12377646668063\\
-12	1.12467567262626\\
-13	1.12655148101693\\
-14	1.1274126433068\\
-15	1.12796634097065\\
-16	1.12836437582839\\
+1	1.08632407458004e-05\\
+2	1.08877007745949e-05\\
+3	1.09594364217047e-05\\
+4	1.10938027865036e-05\\
+5	1.12827891666553e-05\\
+6	1.15378065652616e-05\\
+7	1.19617266900702e-05\\
+8	1.41613520483063e-05\\
+9	6.92466622068608e-05\\
+10	0.000224790946436711\\
+11	0.000536194940235116\\
+12	0.0020179447121528\\
+13	0.00228142595005787\\
+14	0.00484194141261625\\
+15	0.00509975660438143\\
+16	0.00611499201390601\\
 };

### 2021-08-03 assets/waveform_wpt_multisine.tex
:bento: Update assets

@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,3.312in)},
+width=4.036in,
+height=0.407in,
+at={(0.677in,3.198in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	0.000331092582051402\\
+1	0.000179640013528533\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000301200841788861\\
+1	0.000397123673947016\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,2.598in)},
+width=4.036in,
+height=0.407in,
+at={(0.677in,2.513in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	8.31476170438795e-06\\
-2	8.59623838841982e-06\\
+1	3.79500700797208e-06\\
+2	4.08912055500049e-06\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	2.51350625686209e-05\\
-2	2.5738452816653e-05\\
+1	1.49290916575988e-05\\
+2	1.5984007495811e-05\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.883in)},
+width=4.036in,
+height=0.407in,
+at={(0.677in,1.828in)},
 scale only axis,
@@
 ymin=0,
-ymax=4.47213595499958,
+ymax=1,
+ytick={0, 1},
 ylabel style={font=\color{white!15!black}},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	1.81401011150761e-05\\
-2	7.63567990520219e-05\\
-3	0.000347720308108743\\
-4	1.20961154306659\\
+1	1.7047574186968e-05\\
+2	5.43653691324513e-05\\
+3	5.45654270177953e-05\\
+4	0.643758338055473\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.00111014489403298\\
-2	0.00243652079053788\\
-3	0.00358274270606404\\
-4	1.61181535442991\\
+1	1.36848368645437e-05\\
+2	2.47445070835246e-05\\
+3	2.69448998495505e-05\\
+4	0.887691893042722\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,1.168in)},
+width=4.036in,
+height=0.407in,
+at={(0.677in,1.143in)},
 scale only axis,
@@
 ymax=4.47213595499958,
+ytick={0, 2, 4},
 axis background/.style={fill=white},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.406193755485101\\
-2	0.6086191375554\\
-3	0.70781380097226\\
-4	1.11700551493449\\
-5	1.39413019214519\\
-6	1.89924922357725\\
-7	2.27606557910904\\
-8	2.64280256661518\\
+1	0.0867788582585271\\
+2	0.354584687432597\\
+3	0.978311956865194\\
+4	1.00526014633142\\
+5	1.77421254564815\\
+6	1.81146146011329\\
+7	2.39316922290828\\
+8	2.39637542235877\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.621345098069754\\
-2	0.710296651693143\\
-3	0.908023988477654\\
-4	1.12050035456782\\
-5	1.44244708781013\\
-6	1.77492365099369\\
-7	2.30702814170141\\
-8	2.53638471775812\\
+1	0.0902176300392888\\
+2	0.346545381997116\\
+3	0.920392715728033\\
+4	1.00603974348273\\
+5	1.68636658487784\\
+6	1.88211529376329\\
+7	2.36040788303805\\
+8	2.46040714408403\\
 };
@@
 \begin{axis}[%
-width=3.972in,
-height=0.503in,
-at={(0.666in,0.454in)},
+width=4.036in,
+height=0.407in,
+at={(0.677in,0.458in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.280439553353647\\
-2	0.384605443069534\\
-3	0.416114603863305\\
-4	0.499024317224016\\
-5	0.571268128602638\\
-6	0.621900186283823\\
-7	0.763344617968865\\
-8	0.858693319856245\\
-9	0.954356161751161\\
-10	1.16907743761735\\
-11	1.21561270661726\\
-12	1.45089690540298\\
-13	1.51204499963039\\
-14	1.68681223326519\\
-15	1.74569476977388\\
-16	1.81071246294588\\
+1	0.0464370103565898\\
+2	0.0888998754115983\\
+3	0.182477468723257\\
+4	0.351067698858224\\
+5	0.586511157963407\\
+6	0.614337078252067\\
+7	0.810319773242887\\
+8	0.860994249853337\\
+9	1.10132170987082\\
+10	1.14707079761106\\
+11	1.39883656543765\\
+12	1.41535986846215\\
+13	1.61724209266044\\
+14	1.62252465458191\\
+15	1.72749872908311\\
+16	1.73005229015507\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.447567787711277\\
-2	0.504906671531525\\
-3	0.589458291557858\\
-4	0.619646960375962\\
-5	0.691059903147371\\
-6	0.741736916016998\\
-7	0.810826698348076\\
-8	0.887751406400927\\
-9	0.941910732226763\\
-10	1.15698606523739\\
-11	1.20259880483264\\
-12	1.42353667332449\\
-13	1.46532152628089\\
-14	1.65027292091107\\
-15	1.65828648619566\\
-16	1.73730645060792\\
+1	0.0510852453116461\\
+2	0.0931309188028207\\
+3	0.185327611314329\\
+4	0.340208570070271\\
+5	0.54797982875002\\
+6	0.640935330786823\\
+7	0.791412536150533\\
+8	0.84579943866006\\
+9	1.06112099796475\\
+10	1.16793555562456\\
+11	1.33939925851288\\
+12	1.47707717171709\\
+13	1.57685904146789\\
+14	1.6756197826186\\
+15	1.71965928671636\\
+16	1.75172173644803\\
 };

### 2021-08-03 main.tex
:pencil: Update manuscript

--- 2021-08-01 main.tex
@@
 \usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-% \usepackage[cmintegrals]{newtxmath}
 \usepackage[short]{optidef}
@@
 \begin{document}
-	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
+	\title{IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
 	\author{
@@
 Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states.
-Results also emphasize the importance of modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
+Results also emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
 	\end{abstract}
@@
 			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming).
-Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.
+In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
 
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			The major issue of WPT and SWIPT is the low harvested DC power, and the passive beamforming provided by the IRS can enhance the end-to-end energy efficiency and boost the harvester input power level.
-The smart channel control and low power consumption of IRS can bring more opportunities to SWIPT.
-For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+			In IRS-aided SWIPT, the effective channel enhancement can improve the end-to-end energy efficiency and the smart reflection control can enhance the R-E tradeoff.
+For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
 It was also claimed that Line-of-Sight (LoS) links could boost the WSP as rank-deficient channels tend to require fewer energy beams \cite{Wu2020a}.
 However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model.
+In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage.
+It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
 A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
-To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
 In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
@@
 This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.
 
@@
 			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 $\Re\{\cdot\}$ retrieves the real part of a complex entity.
-$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ elements of a vector.
+$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
 $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
@@
 			\end{equation}
-			For simplicity, we define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+			We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
 		\end{subsection}
@@
 			where we define the cascaded channel without IRS reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
-For simplicity, we also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
+We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
 
@@
 				The cascaded channel varies at different frequencies.
-Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain.
-The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
+Since the reflection cannot be designed independently at different subbands, there exists a tradeoff for the passive beamforming design in the frequency domain.
+The composite channel can be tuned flexibly to meet the specific requirement of multi-carrier SWIPT.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
@@
 			where $w_n(t)$ is the noise at RF band $n$.
-Note that $y_{\mathrm{I}}(t)$ can be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ carries no information and cannot be used for decoding.
+Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
 		\end{subsection}
@@
 
-			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes for the co-located information decoder and energy harvester \cite{Zhou2013} to utilize the superposed signal.
+			As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013} to function.
 The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \mathcal{K} \triangleq \{{-N+1},\dots,{N-1}\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
 
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
-				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
 				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
@@
 			\end{align}
-			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
-Due to symmetry \cite{Huang2017}, we have
+			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
+Due to symmetry \cite{Golub2013}, we have
 			\begin{equation}\label{eq:coupled_terms}
@@
 			\begin{figure*}[!b]
-				\hrule
 				\begin{align}
@@
 			\begin{figure*}[!b]
+				\hrule
 				\begin{align}
@@
 			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$\footnote{It can be concluded $\bar{\rho}^{\star}=1-\rho^{\star}$ because the R-E tradeoff is maximized when no signal component is wasted at the receiver.} and transform problem~\eqref{op:waveform} into a reversed GP
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP\footnote{It can be concluded $\bar{\rho}^{\star}=1-\rho^{\star}$ as no signal is wasted at the receiver.}
 			\begin{mini!}
@@
 In such case, the current expression is dropped and no SCA is involved.
-To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate depends on either $\eta$ or $\{\delta,\rho\}$.
+To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is bounded by either $\eta$ or $\{\delta,\rho\}$.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
@@
 Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since no current expression thus no SCA is involved.
+Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point where no SCA is involved.
 
@@
 			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.
-For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
+Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}, and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
+For the WIT point, $C_{\max}$ can be obtained in the special case where $\rho=0$ and the objective function becomes $R$ instead of $z$.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
@@
 Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
-All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D.
+All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified in model D.
 The tap gains are modeled as i.i.d.
 CSCG variables.
-Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{Clerckx2016a}.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
 Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order.
+On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
 It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 This observation origins from the rectifier nonlinearity.
-Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials.
-Hence, the benefit of multisine outstands for a sufficiently large $N$.
-\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$.
-This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\subref*{fi:re_subband}).
-For a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any R-E point (this is verified in simulation).
-In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary).
-However, as $N$ becomes sufficiently large, multisine waveform further boosts the WPT point and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
-In conclusion, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.
-\emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$.
-This conclusion is also verified in the following plots.
+Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
+\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can deduct that no multisine waveform is needed for the entire R-E region.
+It aligns with the conventional linear harvester model where the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
+Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+\emph{Third,} the LC-BCD algorithm achieves a decent R-E region even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}, which achieves a good balance between performance and complexity.
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Channel\label{fi:channel_amplitude}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/channel_amplitude.tex}
+				}
+			}
+			\subfloat[WIT: modulated\label{fi:waveform_wit_modulated}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wit_modulated.tex}
+				}
+			}\\
+			\subfloat[WPT: modulated\label{fi:waveform_wpt_modulated}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wpt_modulated.tex}
+				}
+			}
+			\subfloat[WPT: multisine\label{fi:waveform_wpt_multisine}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wpt_multisine.tex}
+				}
+			}
+			\caption{Sorted channel and waveform amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+		\end{figure}
+
+		Fig.~\subref*{fi:channel_amplitude} reveals how passive beamforming influence the channel amplitude and waveform design for one channel realization.
+\emph{First,} the passive beamforming enables a resource allocation opportunity at the channel as discussed in Remark~\ref{re:subband_tradeoff}.
+Under the specified configuration, the WPT-optimized IRS concentrates channel energy on strong subbands to widen the strength disparity.
+Correspondingly, the transmit power is focused on strong subbands to improve the energy efficiency, as observed in \subref*{fi:waveform_wpt_modulated} and \subref*{fi:waveform_wpt_multisine}.
+On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the water-filling scheme at high SNR, but the resource allocation is performed at the channel by passive beamforming.
+\emph{Second,} the impact of passive beamforming on waveform design is subtle.
+The amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\subref*{fi:waveform_wit_modulated}--\subref*{fi:waveform_wpt_multisine}.
+Note that no multisine is used for WIT and the case is not shown.
 
@@
 On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoff points for broadband SWIPT.
-By adaptive passive beamforming, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.
-It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.
+By adaptive passive beamforming, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power, as shown in Fig.~\subref*{fi:channel_amplitude}.
+It emphasizes the R-E advantage of passive beamforming design for broadband SWIPT.
 
@@
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-Consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
+Consider an imperfect CSIT model where the cascaded link at subband $n$ is
 		\begin{equation}
-			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n},
-		\end{equation}
-		where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+			\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
+		\end{equation}
+		where $\hat{\boldsymbol{V}}_{n}$ is the estimated channel and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
 CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
 Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$.
-Note that the estimations at different subbands are independent, but the subchannel responses are indeed correlated.
+The estimations at different subbands can be independent but the subchannel responses are correlated.
 Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
@@
 We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves decent performance in different scenarios.
-Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
+Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
 Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
@@
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
+Also, harvester saturation effect and more involved IRS model based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
 	\end{section}

### 2021-08-03 review/response_2.tex
:pencil: Update response letter

@@
 Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}.
-Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
+Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point where no SCA is involved.
 			\end{framed}
@@
 			\end{framed}
-
-			% As for the measurements, we evaluate the converging speed of all proposed algorithms.
-Figs.~\ref{fi:convergence_sca}--\ref{fi:convergence_bcd} show the output DC current versus the number of iterations for one channel realization at the WPT point.
-It is observed that the SCA- and BCD-based algorithms typically converge within \num{3} iterations while the GP-based algorithm takes around \num{9} iterations to converge.
-Those figures are not added to the manuscript due to the space constraint.
-			% \begin{figure}[!t]
-			% 	\centering
-			% 	\subfloat[SCA-based\label{fi:convergence_sca}]{
-			% 		\resizebox{0.32\columnwidth}{!}{
-			% 			\input{../assets/convergence_sca.tex}
-			% 		}
-			% 	}
-			% 	\subfloat[GP-based\label{fi:convergence_gp}]{
-			% 		\resizebox{0.32\columnwidth}{!}{
-			% 			\input{../assets/convergence_gp.tex}
-			% 		}
-			% 	}
-			% 	\subfloat[BCD-based\label{fi:convergence_bcd}]{
-			% 		\resizebox{0.32\columnwidth}{!}{
-			% 			\input{../assets/convergence_bcd.tex}
-			% 		}
-			% 	}
-			% 	\caption{Converging trend of the proposed algorithms for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$..}
-			% \end{figure}
 			\label{re:1.1}
@@
 			\begin{framed}
-				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
+				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage.
+It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
 
-				\textellipsis To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+				\textellipsis To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
 In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
@@
 		\begin{response}
-			The system layout follows \cite{M-Wu2019} and we set the AP-UE distance to be larger than SWIPT literatures \cite{M-Clerckx2018b} and experiments \cite{M-Kim2020a} thanks to the IRS.
+			The system layout follows \cite{M-Wu2019}.
 For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties.
@@
 This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
-As for the rectenna parameters, we forgot to mention that the parameters are taken from \cite{M-Clerckx2016a} and have added the reference to the revised manuscript.
+We also raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi}.
+As for the rectenna parameters, the parameters are taken from \cite{M-Clerckx2016a} and the reference have been added to the revised manuscript.
 		\end{response}
@@
 		\begin{response}
-			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}.
-In each iteration, Algorithm~\ref{M-al:m_sca} is called.
+			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}, where Algorithm~\ref{M-al:m_sca} is called during each iteration.
 To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved.
@@
 			\begin{framed}
-				To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
+				To achieve the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
 In such case, the current expression is dropped and no SCA is involved.
@@
 			\begin{framed}
-				In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnotemark to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by adjusting the combining and splitting ratios from \num{1} to \num{0}.
-For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$.
+				Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$\footnotemark, and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
+For the WIT point, $C_{\max}$ can be obtained in the special case where $\rho=0$ and the objective function becomes $R$ instead of $z$.
 			\end{framed}
@@
 			Thank you for the suggestion.
-Too see this, we first show two realizations of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}.
+Too see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}.
 It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).
@@
 				\resizebox{0.6\columnwidth}{!}{
-					\includegraphics{../assets/channel_amplitude_100reflectors}
+					\includegraphics{../assets/channel_amplitude}
 				}
@@
 				\resizebox{0.32\columnwidth}{!}{
-						\input{../assets/waveform_wit_modulated_100reflectors.tex}
+						\input{../assets/waveform_wit_modulated.tex}
 					}
@@
 					\resizebox{0.32\columnwidth}{!}{
-						\input{../assets/waveform_wpt_modulated_100reflectors.tex}
+						\input{../assets/waveform_wpt_modulated.tex}
 					}
@@
 					\resizebox{0.32\columnwidth}{!}{
-						\input{../assets/waveform_wpt_multisine_100reflectors.tex}
+						\input{../assets/waveform_wpt_multisine.tex}
 					}
@@
 			\end{figure}
+
+			We have modified the manuscript as follows to emphasize this point.
+			\begin{framed}
+				Fig.~\ref{M-fi:channel_amplitude} reveals how passive beamforming influence the channel amplitude and waveform design for one channel realization.
+\emph{First,} the passive beamforming enables a resource allocation opportunity at the channel as discussed in Remark~\ref{M-re:subband_tradeoff}.
+Under the specified configuration, the WPT-optimized IRS concentrates channel energy on strong subbands to widen the strength disparity.
+Correspondingly, the transmit power is focused on strong subbands to improve the energy efficiency, as observed in \ref{M-fi:waveform_wpt_modulated} and \ref{M-fi:waveform_wpt_multisine}.
+On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the water-filling scheme at high SNR, but the resource allocation is performed at the channel by passive beamforming.
+\emph{Second,} the impact of passive beamforming on waveform design is subtle.
+The amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\ref{M-fi:waveform_wit_modulated}--\ref{M-fi:waveform_wpt_multisine}.
+Note that no multisine is used for WIT and the case is not shown.
+			\end{framed}
 			\label{re:2.2}
@@
 			\begin{equation}
-				\arg(\boldsymbol{w}_{\mathrm{I}}) = \arg(\boldsymbol{w}_{\mathrm{P}}) = -\arg(\boldsymbol{h})
+				\arg(\boldsymbol{w}_{\mathrm{I}}) = \arg(\boldsymbol{w}_{\mathrm{P}}) = -\arg(\boldsymbol{h}),
 			\end{equation}
@@
 Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff.
-Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.
+Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{0} to \num{1}.
 However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead.
@@
 
-				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{1} to \num{0}.
+				\textellipsis and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
 
-				\textellipsis assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+				\textellipsis assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
 
-				\textellipsis \emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$.
-This conclusion is also verified in the following plots.
+				\textellipsis  \emph{Third,} the LC-BCD algorithm achieves a decent R-E region even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}, which achieves a good balance between performance and complexity.
 			\end{framed}
@@
 This is however impossible at low SNR.
+
+			The manuscript has been updated as follows.
+			\begin{framed}
+				\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\ref{M-fi:re_subband}).
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can deduct that no multisine waveform is needed for the entire R-E region.
+It aligns with the conventional linear harvester model where the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
+Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+			\end{framed}
 		\end{response}
@@
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-We have updated the Remark~\ref{M-re:subband_tradeoff} as follows.
+We have added Fig.~\ref{fi:channel_amplitude} and updated the Remark~\ref{M-re:subband_tradeoff} to clarify this point.
 			\begin{framed}
 				The cascaded channel varies at different frequencies.
-Since we regard the reflection as frequency-flat, there exists a tradeoff for the passive beamforming design in the frequency domain.
-The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
+Since the reflection cannot be designed independently at different subbands, there exists a tradeoff for the passive beamforming design in the frequency domain.
+The composite channel can be tuned flexibly to meet the specific requirement of multi-carrier SWIPT.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
@@
 
-			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference and maintain the simulation results in the same level.
+			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference.
 Please refer to the following specification for details.
@@
 Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
-All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D.
+All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified in model D.
 The tap gains are modeled as i.i.d.
 CSCG variables.
-Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{M-Clerckx2016a}.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
 			\end{framed}
@@
 The discrete phase shift is obtained by quantizing the continuous phase shift obtained by Algorithm~\ref{M-al:bcd} to the uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$.
-We are aware that quantization can lead to performance loss compared with direct optimization over feasible phase shift set.
+We are aware that quantization can lead to performance loss compared with direct optimization over the feasible phase shift set.
 In the revised manuscript, we have emphasized this point as follows.
@@
 			\end{framed}
+			The future works has been updated as follows.
+			\begin{framed}
+				Also, harvester saturation effect and more involved IRS model based on direction- and frequency-dependent reflection \cite{M-Abeywickrama2020} and/or partially/fully-connected reflection \cite{M-Shen2020a} could be considered in future works.
+			\end{framed}
 		\end{response}
@@
 		\begin{response}
-			We have incorporated aforementioned references into the manuscript as follows.
+			We have incorporated those references into the manuscript as follows.
 			\begin{framed}

### 2021-08-07 main.tex
:pencil: Update manuscript

@@
 To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes.
-Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states.
-Results also emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
+Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states, and emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
 	\end{abstract}
@@
 On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
-It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT.
+It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT.
 Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
 A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
@@
 In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
+Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
 
 			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
-Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
+\cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
 The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS.
+In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift for practical IRS.
 To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
 The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
-The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs).
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
-Deep reinforcement learning tools were also applied in \cite{Yang2021} to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
 		\end{subsection}
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			In IRS-aided SWIPT, the effective channel enhancement can improve the end-to-end energy efficiency and the smart reflection control can enhance the R-E tradeoff.
+			By integrating IRS with SWIPT, its smart and effective reflection can enhance the R-E tradeoff and improve the end-to-end power efficiency.
 For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also claimed that Line-of-Sight (LoS) links could boost the WSP as rank-deficient channels tend to require fewer energy beams \cite{Wu2020a}.
+It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
 However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage.
-It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
-A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
+Based on practical IRS and energy harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
+The proposed framework provides a flexible balance between performance and complexity.
 To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
@@
 
-			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, a beamforming gain, and the channel selectivity across spatial and frequency domains to enlarge the achievable R-E region.
+			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model in \cite{Clerckx2016a}.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
+The proposed joint waveform, active and passive beamforming architecture exploits across frequency and spatial domains the rectifier nonlinearity, the channel selectivity, and a beamforming gain to enlarge the achievable R-E region.
 This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
 
-			\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+			\emph{Second,} we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
@@
 
-			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
+			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
 The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time and power domains to facilitate practical SWIPT implementation.
-To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode.
-The proposed low-complexity designs achieve decent R-E performance in different scenarios.
-
-			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+Some modifications are then made on the passive beamforming design to accommodate the low-complexity waveform schemes.
+In this case, the R-E region is obtained by varying the duration ratio under the TS mode and varying the combining and splitting ratios under the PS mode.
+The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
+
+			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
+It is concluded that 1) IRS not only enhances the equivalent channel but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 $\sim$ means ``distributed as''.
-$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
+$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
 		\end{subsection}
@@
 		\begin{subsection}{Transmitted Signal}
-			As suggested in \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
-The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
+			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
+The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
 			\begin{equation}
@@
 The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-IRS element $l \in \mathcal{L} \triangleq \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
+IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
 			\begin{equation}
@@
 			\end{equation}
-			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, in practice $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}, respectively.
+			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, in practice $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
+This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}
 
@@
 			\end{equation}
-			where we define the cascaded channel without IRS reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+			where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
 We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
@@
 			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel varies at different frequencies.
-Since the reflection cannot be designed independently at different subbands, there exists a tradeoff for the passive beamforming design in the frequency domain.
-The composite channel can be tuned flexibly to meet the specific requirement of multi-carrier SWIPT.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-This is essentially a resource allocation opportunity at the channel enabled by the IRS.
+				The cascaded channel varies at different subbands but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite channel should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+That is to say, IRS essentially enables an flexible subchannel design.
 In the MISO case, a similar effect also exists in the spatial domain.
@@
 		\begin{subsection}{Received Signal}
-			The received superposed signal at the single-antenna UE is\footnote{It is assumed that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
 			\begin{equation}
-				y(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})}{e^{j2{\pi}{f_n}{t}}}+w_n(t)\right\},
-			\end{equation}
-			where $w_n(t)$ is the noise at RF band $n$.
+				y(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})}{e^{j2{\pi}{f_n}{t}}}+y_n(t)\right\},
+			\end{equation}
+			where $y_n(t)$ is the noise at RF band $n$.
 Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
@@
 
-			As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013} to function.
+			As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
 The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
@@
 During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
-In the following context, we consider the analysis based on the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+In the following context, we consider the analysis based on the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{This rate is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+Therefore, the achievable rate is\footnote{It is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
 			\begin{equation}\label{eq:R}
@@
 
-			Importantly, the rectenna model used in this section taken from \cite{Clerckx2016a} captures the dependency of the output DC current on both the power and shape of the received signal.
-This is critical for efficient signal designs in WPT and SWIPT \cite{Clerckx2021}.
-Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$.
+			Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC current on both the power and shape of the received signal.
+Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
 Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
 When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
-
-			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}.
 Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
@@
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the nonlinear DC terms.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
 Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \mathcal{K} \triangleq \{{-N+1},\dots,{N-1}\}$ and set all other blocks to $\boldsymbol{0}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
 Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
@@
 			\end{align}
-			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of sine waves to the average value.
+			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of the sine waves to the average value.
 		\end{subsection}
@@
 		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift; 2) the active precoder; 3) the waveform amplitude and splitting ratio, until convergence.
 
@@
 			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the rate \eqref{eq:R} reduces to
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
+Hence, the rate \eqref{eq:R} reduces to
 			\begin{equation}\label{eq:R_waveform}
@@
 				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P},
-			\end{align}
-			where $m_{\mathrm{I},n}=2$ and $m_\mathrm{P}=(2N^3+6N^2+7N)/3$.
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
+			\end{align}
 			We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
@@
 			\end{mini!}
-			where $\gamma_{m_{\mathrm{I},n}} \ge 0$, $\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
+			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
 The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
@@
 			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity.
+			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
 When the receiver works in TS mode, there is no superposition in the suboptimal waveform design.
@@
 			\end{align}
-			where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}.
-Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes.
-To achieve the WIT point, the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized.
-In such case, the current expression is dropped and no SCA is involved.
-To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is bounded by either $\eta$ or $\{\delta,\rho\}$.
+			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
+
+			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
+The rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} should be dropped, and no SCA is involved.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-The proofs of SDR tightness and local optimality are similar to Appendices~\ref{ap:relaxation} and \ref{ap:sca} thus omitted here.
-Compared with Algorithm~\ref{al:sca}, the rate constraint \eqref{co:irs_rate} is dropped and each SDP in Algorithm~\ref{al:m_sca} involves $(L+1)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point where no SCA is involved.
+Similarly, no loss is introduced by SDR and local optimality is guaranteed, and the proofs are omitted.
+Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
+Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
 
@@
 
-			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}, and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
-For the WIT point, $C_{\max}$ can be obtained in the special case where $\rho=0$ and the objective function becomes $R$ instead of $z$.
+			For the low-complexity design under PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
 
@@
 
-		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
+		To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
 Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
@@
 The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
-All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified in model D.
-The tap gains are modeled as i.i.d.
+We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel is modeled by IEEE TGn channel model D \cite{Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter} and \num{3.5} onwards to further penalize the channels with large distance.
+All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
 CSCG variables.
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
-Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
+Each R-E point is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Channel\label{fi:channel_amplitude}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/channel_amplitude.tex}
+				}
+			}
+			\subfloat[WIT: modulated\label{fi:waveform_wit_modulated}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wit_modulated.tex}
+				}
+			}\\
+			\subfloat[WPT: modulated\label{fi:waveform_wpt_modulated}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wpt_modulated.tex}
+				}
+			}
+			\subfloat[WPT: multisine\label{fi:waveform_wpt_multisine}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/waveform_wpt_multisine.tex}
+				}
+			}
+			\caption{Sorted channel and waveform amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+		\end{figure}
+
+		Fig.~\subref*{fi:channel_amplitude} reveals how IRS influences the (sorted) channel amplitude and waveform design for one channel realization.
+Thanks to the flexible subchannel design enabled by passive beamforming, the optimal subchannel strength distribution for WIT and WPT are dissimilar.
+Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
+On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the water-filling scheme at high SNR, but is realized by channel alignment instead of resource allocation.
+Moreover, the amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\subref*{fi:waveform_wit_modulated}--\subref*{fi:waveform_wpt_multisine}.\footnote{Note that no multisine is used for WIT and the case is not shown.} It is concluded that adding an IRS to the SWIPT system has subtle impact on the waveform design.
 
@@
 		Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-\emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy.
+First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+This is because less power is allocated to each subband but more balanced DC terms are introduced by frequency coupling to boost the harvested energy.
 On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
@@
 Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
-\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can deduct that no multisine waveform is needed for the entire R-E region.
-It aligns with the conventional linear harvester model where the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can infer that no multisine waveform is needed for the entire R-E region.
+It aligns with the conclusion based on conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
 As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
 Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
-\emph{Third,} the LC-BCD algorithm achieves a decent R-E region even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}, which achieves a good balance between performance and complexity.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Channel\label{fi:channel_amplitude}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/channel_amplitude.tex}
-				}
-			}
-			\subfloat[WIT: modulated\label{fi:waveform_wit_modulated}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wit_modulated.tex}
-				}
-			}\\
-			\subfloat[WPT: modulated\label{fi:waveform_wpt_modulated}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wpt_modulated.tex}
-				}
-			}
-			\subfloat[WPT: multisine\label{fi:waveform_wpt_multisine}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wpt_multisine.tex}
-				}
-			}
-			\caption{Sorted channel and waveform amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		Fig.~\subref*{fi:channel_amplitude} reveals how passive beamforming influence the channel amplitude and waveform design for one channel realization.
-\emph{First,} the passive beamforming enables a resource allocation opportunity at the channel as discussed in Remark~\ref{re:subband_tradeoff}.
-Under the specified configuration, the WPT-optimized IRS concentrates channel energy on strong subbands to widen the strength disparity.
-Correspondingly, the transmit power is focused on strong subbands to improve the energy efficiency, as observed in \subref*{fi:waveform_wpt_modulated} and \subref*{fi:waveform_wpt_multisine}.
-On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the water-filling scheme at high SNR, but the resource allocation is performed at the channel by passive beamforming.
-\emph{Second,} the impact of passive beamforming on waveform design is subtle.
-The amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\subref*{fi:waveform_wit_modulated}--\subref*{fi:waveform_wpt_multisine}.
-Note that no multisine is used for WIT and the case is not shown.
 
@@
 
-		The average noise power influences the R-E region as in Fig.~\subref*{fi:re_noise}.
-\emph{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
+		The average noise power influences the R-E region as shown in Fig.~\subref*{fi:re_noise}.
+First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
 At low SNR, the power is allocated to the modulated waveform on few strongest subbands to achieve a high rate.
 As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency coupling and harvester nonlinearity.
-\emph{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
+Second, there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
 The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
@@
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
+Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
 
@@
 		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-\emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
-\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design.
-To show the underlying performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to the nonlinear model-based SMF and GP.
-\emph{Third,} passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious for the case of WIT and WPT.
+First, adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
+Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
+To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} gap compared to the nonlinear model-based SMF and GP designs.
+Third, passive beamforming has a larger array gain and power scaling order than active beamforming.
+This behavior is more obvious in the case of WIT and WPT.
 For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power.
@@
 Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.
+These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
 
@@
 uniform random variables over $[0, 2\pi)$.
-\emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations.
-\emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS when the bandwidth is large.
+First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
+Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after average.
+Second, the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS when the bandwidth is large.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
 It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-Hence, the achievable R-E region is obtained by varying the waveform amplitude and splitting ratio.
+Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
 On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoff points for broadband SWIPT.
-By adaptive passive beamforming, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power, as shown in Fig.~\subref*{fi:channel_amplitude}.
-It emphasizes the R-E advantage of passive beamforming design for broadband SWIPT.
+As shown in Fig.~\subref*{fi:channel_amplitude}, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power, thanks to adaptive passive beamforming.
 
@@
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-Consider an imperfect CSIT model where the cascaded link at subband $n$ is
+Consider an imperfect CSIT model where the cascaded channel at subband $n$ is
 		\begin{equation}
@@
 		\end{equation}
-		where $\hat{\boldsymbol{V}}_{n}$ is the estimated channel and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.
-Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$.
-The estimations at different subbands can be independent but the subchannel responses are correlated.
+		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Perfect CSIT and no CSIT can be regarded as special cases with $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$.
 Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead\footnote{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS).
-The readers are referred to \cite{Wu2020c} for details.}.
-Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
@@
 	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in a novel IRS-aided multi-carrier MISO SWIPT system.
+		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
 Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
@@
 In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method.
-We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves decent performance in different scenarios.
+We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves good balance between performance and complexity.
 Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
 Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
-However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.
+However, a large number of reflecting elements may be required to compensate the double fading effect in the auxiliary link.
 
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, harvester saturation effect and more involved IRS model based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
+Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
 	\end{section}

### 2021-08-07 review/response_2.tex
:pencil: Update response letter

@@
 			\end{align}
-			which is generally feasible and widely adopted when $t_{\mathrm{I},0}$ and $t_{\mathrm{P},0}$ are variables.
-Hence, we claimed Algorithm~\ref{M-al:sca} ``is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{M-eq:z_irs_approx}''.
+			which is feasible for any $t_{\mathrm{I/P},0}^{(i)} \in \mathbb{R}$ and widely adopted when $t_{\mathrm{I},0}$ and $t_{\mathrm{P},0}$ are variables.
+Hence, we claimed Algorithm~\ref{M-al:sca} `is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{M-eq:z_irs_approx}'.
 During revision, we realized that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ are essentially linear real expressions related to optimization variable $\boldsymbol{\Phi}$, and the SCA can be further reduced to
@@
 			\begin{framed}
-				Compared with Algorithm~\ref{M-al:sca}, the rate constraint \eqref{M-co:irs_rate} is dropped and each SDP in Algorithm~\ref{M-al:m_sca} involves $(L+1)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}.
-Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point where no SCA is involved.
+				Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}.
+Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
 			\end{framed}
@@
 			\begin{framed}
-				Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
+				The computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
 			\end{framed}
@@
 The model also adapts well to practical IRS models accounting AoA and AoD.
-In contrast, our paper is more focused on waveform design and rate-energy tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
-We have updated the manuscript as follows.
+We would like to kindly highlight that \cite{Xu2021} was not available at the time of submission of this manuscript.
+\cite{Xu2021} was indeed submitted in April 2021, i.e.
+several months after our submission to TCOM in Nov 2020.
+We therefore believe it is for authors of \cite{Xu2021} to further enrich the survey part of their manuscript by making it more comprehensive and discuss the difference between \cite{Xu2021} and this paper.
+Nevertheless to address the reviewer comments, we now compare with \cite{Xu2021c} which appeared on arXiv shortly before our submission.
 			\begin{framed}
-				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage.
-It was concluded that the proposed two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
+				Based on practical IRS and energy harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
+The proposed framework provides a flexible balance between performance and complexity.
 
@@
 It has three clusters with \SI{50}{\ns} r.m.s.
-delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and set to \num{3.5} onwards.
-This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
+delay spread, and the path loss exponent is \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards to further penalize channels with large distance.
 We also raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi}.
@@
 			\begin{framed}
-				To achieve the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized.
-In such case, the current expression is dropped and no SCA is involved.
+				Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
+The rate constraint \eqref{M-co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized, the current expression \eqref{M-eq:z_irs_approx} should be dropped, and no SCA is involved.
 			\end{framed}
@@
 			\begin{framed}
-				Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$\footnotemark, and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
-For the WIT point, $C_{\max}$ can be obtained in the special case where $\rho=0$ and the objective function becomes $R$ instead of $z$.
+				To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnotemark Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 			\end{framed}
-			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.}
+			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that different subchannel designs lead to different capacities.}
 			\label{re:1.4}
@@
 			Thank you for the suggestion.
-Too see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}.
+To see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}.
 It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).
@@
 			\begin{framed}
-				Fig.~\ref{M-fi:channel_amplitude} reveals how passive beamforming influence the channel amplitude and waveform design for one channel realization.
-\emph{First,} the passive beamforming enables a resource allocation opportunity at the channel as discussed in Remark~\ref{M-re:subband_tradeoff}.
-Under the specified configuration, the WPT-optimized IRS concentrates channel energy on strong subbands to widen the strength disparity.
-Correspondingly, the transmit power is focused on strong subbands to improve the energy efficiency, as observed in \ref{M-fi:waveform_wpt_modulated} and \ref{M-fi:waveform_wpt_multisine}.
+				Fig.~\ref{M-fi:channel_amplitude} reveals how IRS influences the (sorted) channel amplitude and waveform design for one channel realization.
+Thanks to the flexible subchannel design enabled by passive beamforming, the optimal subchannel strength distribution for WIT and WPT are dissimilar.
+Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
 On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the water-filling scheme at high SNR, but the resource allocation is performed at the channel by passive beamforming.
-\emph{Second,} the impact of passive beamforming on waveform design is subtle.
-The amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\ref{M-fi:waveform_wit_modulated}--\ref{M-fi:waveform_wpt_multisine}.
-Note that no multisine is used for WIT and the case is not shown.
+This is reminiscent of the water-filling scheme at high SNR, but is realized by channel alignment instead of resource allocation.
+Moreover, the amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\ref{M-fi:waveform_wit_modulated}--\ref{M-fi:waveform_wpt_multisine}.\footnotemark It is concluded that adding an IRS to the SWIPT system has subtle impact on the waveform design.
 			\end{framed}
+			\footnotetext{Note that no multisine is used for WIT and the case is not shown.}
 			\label{re:2.2}
@@
 			\begin{framed}
-				\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model proposed in \cite{M-Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency compensation (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and non-concavity from high-order objective function.
+				Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
 			\end{framed}
@@
 GP tools can be applied at this stage and the number of real-valued variables are $2MN$.
-In contrast, the proposed Algorithm~\ref{M-al:gp} decoupled the design in the spatial and frequency domains, derived the global optimal active precoder, and leaves an resource allocation issue with $2N$ real-valued variables in the frequency domain.
+In contrast, the proposed design decouples the design in the spatial and frequency domains, derives the global optimal active precoder, and leaves a resource allocation issue with $2N$ real-valued variables in the frequency domain.
 Since the computational complexity of GP scales exponentially with the number of variables, optimizing $\boldsymbol{w}_{\mathrm{I}}$ and $\boldsymbol{w}_{\mathrm{P}}$ as a whole can be very inefficient and not discussed in the manuscript.
@@
 			Thank you for raising this point.
-The combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.
-We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
+The combining ratio $\delta$ determines the priority on multisine power waveform at the transmitter, while the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.
+We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
 Heuristically, $\delta$ and $\rho$ should approximately equal at each point to boost R-E tradeoff.
@@
 			\begin{framed}
-				\textellipsis where the combining ratio $\delta$ determines the weight on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.
+				\textellipsis where the combining ratio $\delta$ determines the priority on multisine power waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver\footnotemark.
 
-				\textellipsis and the LC-BCD algorithm characterizes the R-E tradeoff via two-dimensional search over $\delta$, $\rho$ from \num{0} to \num{1}.
+				\textellipsis Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 
-				\textellipsis assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
+				\textellipsis assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
 
-				\textellipsis  \emph{Third,} the LC-BCD algorithm achieves a decent R-E region even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}, which achieves a good balance between performance and complexity.
+				\textellipsis  Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
 			\end{framed}
-			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point.
+			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
 Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
@@
 			\begin{framed}
-				\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design.
-To show the underlying performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
-As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to the nonlinear model-based SMF and GP.
+				Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
+To investigate the performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
+As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} gap compared to the nonlinear model-based SMF and GP designs.
 			\end{framed}
@@
 			\begin{framed}
-				\emph{Second,} the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+				Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\ref{M-fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can deduct that no multisine waveform is needed for the entire R-E region.
-It aligns with the conventional linear harvester model where the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can infer that no multisine waveform is needed for the entire R-E region.
+It aligns with the conclusion based on conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
 As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
@@
 		\begin{response}
-			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and a resource allocation opportunity at the channel arises thanks to the IRS.
-The composite channel can be tuned flexibly to satisfy the specific requirement of the multi-carrier transmission.
+			By `auxiliary link control in the frequency domain', we intended to emphasize that the auxiliary link cannot be designed independently at different frequencies, and subchannel design flexibility arises in the presence of IRS.
+The composite channel can be tuned adaptively to satisfy the specific requirement of the multi-carrier transmission.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
@@
 			\begin{framed}
-				The cascaded channel varies at different frequencies.
-Since the reflection cannot be designed independently at different subbands, there exists a tradeoff for the passive beamforming design in the frequency domain.
-The composite channel can be tuned flexibly to meet the specific requirement of multi-carrier SWIPT.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-This is essentially a resource allocation opportunity at the channel enabled by the IRS.
+				The cascaded channel varies at different subbands but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite channel should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+That is to say, IRS essentially enables an flexible subchannel design.
 In the MISO case, a similar effect also exists in the spatial domain.
@@
 		\begin{response}
-			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will endeavor to avoid similar issues in the future.
+			We sincerely appreciate your careful reading and rigorous feedbacks. The manuscript have been revised accordingly and we will avoid similar issues as possible.
 		\end{response}
@@
 In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}.
-The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
-This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.
+The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and \num{3.5} onwards to penalize the channels with large distance.
 
@@
 			\begin{framed}
-				We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}.
-Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards.
-All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified in model D.
-The tap gains are modeled as i.i.d.
+				We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter} and \num{3.5} onwards to further penalize the channels with large distance.
+All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
 CSCG variables.
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search for the R-E region).
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
 			\end{framed}
@@
 			\begin{framed}
-				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients returned by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead\footnotemark.
+				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients obtained by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead.\footnotemark
 			\end{framed}
-			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS).
-The readers are referred to \cite{Wu2020c} for details.}
+			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.}
 		\end{response}
@@
 			\begin{framed}
-				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity.
-It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to practical IRS and harvester models.
+				Based on practical IRS and energy harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
+The proposed framework provides a flexible balance between performance and complexity.
 			\end{framed}
@@
 			\begin{framed}
-				Also, harvester saturation effect and more involved IRS model based on direction- and frequency-dependent reflection \cite{M-Abeywickrama2020} and/or partially/fully-connected reflection \cite{M-Shen2020a} could be considered in future works.
+				Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{M-Abeywickrama2020}, angle-dependent reflection \cite{M-Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{M-Shen2020a} could be considered in future works.
 			\end{framed}
@@
 		\begin{response}
-			We have incorporated those references into the manuscript as follows.
+			Thank you for the suggestion and we have incorporated one magazine paper \cite{Wu2020} into the manuscript.
+A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
+However, the aforementioned paper appeared on arXiv after ours and have cited our work, and we decided not to cite it.
 			\begin{framed}
 				\textellipsis The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
-
-				\textellipsis A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
 			\end{framed}
@@
 		\begin{response}
-			We have incorporated the reference into the manuscript as follows.
-			\begin{framed}
-				Deep reinforcement learning tools were also applied in \cite{Yang2021} to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
-			\end{framed}
+			We appreciate the reviewer for sharing this manuscript.
+It seeks deep reinforcement learning tools to assist practical secure beamforming and reflection pattern design under QoS constraints for time-varying channels.
+However, we have found this reference not very closely related to SWIPT and therefore decided not to cite it.
 		\end{response}

### 2021-08-09 main.tex
:pencil: Fix noise notation
:pencil: Update notations
:pencil: Update manuscript

@@
 			\begin{equation}
-				y(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})}{e^{j2{\pi}{f_n}{t}}}+y_n(t)\right\},
-			\end{equation}
-			where $y_n(t)$ is the noise at RF band $n$.
+				y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
+			\end{equation}
+			where $\tilde{n}_n(t)$ is the noise at RF band $n$.
 Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
@@
 			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{It is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+Therefore, the achievable rate is\footnote{Requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
 			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2},\right)}
+				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
 			\end{equation}
@@
 					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
+					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
 					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$
+					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
 					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
@@
 						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
+						\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
 					\EndIf
 					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$
+					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
@@
 						\If{$\rho=0$}
-							\State $\Delta = R^{(i)} - R^{(i-1)}$
+							\State $\Delta \gets R^{(i)} - R^{(i-1)}$
 						\Else
-							\State $\Delta = z^{(i)} - z^{(i-1)}$
+							\State $\Delta \gets z^{(i)} - z^{(i-1)}$
 						\EndIf
 					\Until $\lvert \Delta \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
@@
 			\begin{figure*}[!b]
+				\hrule
 				\begin{align}\label{eq:delta}

### 2021-08-11 main.tex
:pencil: Update manuscript

@@
 \DeclareSIUnit{\dBi}{\deci\beli}
+\DeclareSIUnit{\belA}{BA}
+\DeclareSIUnit{\dBA}{\deci\belA}
 \usetikzlibrary{arrows,matrix,positioning}
@@
 Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
-A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
+A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
+Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
+The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
 It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
@@
 The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift for practical IRS.
+In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
 To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
+The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
+In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
 		\end{subsection}
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			By integrating IRS with SWIPT, its smart and effective reflection can enhance the R-E tradeoff and improve the end-to-end power efficiency.
-For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+			By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
+In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
 It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
-However, \cite{Wu2020b,Tang2019,Wu2020a} were based on an inaccurate linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and energy harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
-The proposed framework provides a flexible balance between performance and complexity.
+However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
+Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+The proposed framework provides a flexible tradeoff between performance and complexity.
 To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
+In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
 We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
 
-			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model in \cite{Clerckx2016a}.
+			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
 Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
 To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits across frequency and spatial domains the rectifier nonlinearity, the channel selectivity, and a beamforming gain to enlarge the achievable R-E region.
+The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
 This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
 
-			\emph{Second,} we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
+			\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
+The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
 For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
 For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
-Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique.
+Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique.
 The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
@@
 			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time and power domains to facilitate practical SWIPT implementation.
-Some modifications are then made on the passive beamforming design to accommodate the low-complexity waveform schemes.
-In this case, the R-E region is obtained by varying the duration ratio under the TS mode and varying the combining and splitting ratios under the PS mode.
+To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
+The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
 The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
@@
 			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS not only enhances the equivalent channel but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 $\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real nonnegative and complex $x \times y$ matrices.
+$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
 $\Re\{\cdot\}$ retrieves the real part of a complex entity.
@@
 			\import{assets/}{system.pdf_tex}
-			\caption{An IRS-aided multi-carrier SWIPT system.}
+			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
 			\label{fi:system}
@@
 		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider the quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
+We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
@@
 		\begin{subsection}{Transmitted Signal}
-			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
+			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
 The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
@@
 			\end{equation}
-			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, in practice $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$.
+			where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
 This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.
 
@@
 			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel varies at different subbands but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite channel should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-That is to say, IRS essentially enables an flexible subchannel design.
+That is to say, IRS essentially enables a flexible subchannel design.
 In the MISO case, a similar effect also exists in the spatial domain.
@@
 			where $\tilde{n}_n(t)$ is the noise at RF band $n$.
-Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
+Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
 		\end{subsection}
@@
 				}
-				\caption{Practical co-located receiving modes.}
+				\caption{Diagrams of practical co-located receivers.}
 				\label{fi:receiver}
@@
 The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
-During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff.
-In the following context, we consider the analysis based on the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoffs.
+In the following context, we consider the optimization with the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 		\end{subsection}
@@
 			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{Requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
 			\begin{equation}\label{eq:R}
@@
 			\end{equation}
-			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$.
+			where $\sigma_n^2$ is the noise variance at the RF-band and during the RF-to-baseband conversion on tone $n$.
 		\end{subsection}
@@
 				}
-				\caption{Receive antenna and energy harvester circuits.}
+				\caption{Equivalent circuits of receive antenna and energy harvester.}
 			\end{figure}
 
-			Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC current on both the power and shape of the received signal.
+			Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC on both the power and shape of the received signal.
 Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
@@
 Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 			\begin{equation}\label{eq:z}
@@
 			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper.
+With a slight abuse of notation, we refer to $z$ as the average output DC in this paper.
 It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power.
-In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior.
+However, due to the coupling effect among different frequencies, some high-order AC components compensate each other in frequency and further contribute to the output DC power.
+In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
@@
 	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
+		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
 		\begin{maxi!}
@@
 		\end{maxi!}
-		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
+		Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
 To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift; 2) the active precoder; 3) the waveform amplitude and splitting ratio, until convergence.
@@
 			\end{equation}
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 			\begin{figure*}[!b]
@@
 			\end{equation}
-			and the DC current \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+			and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 			\begin{figure*}[!b]
@@
 			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP\footnote{It can be concluded $\bar{\rho}^{\star}=1-\rho^{\star}$ as no signal is wasted at the receiver.}
+			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
 			\begin{mini!}
@@
 			\end{mini!}
+			It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
 The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
@@
 		\begin{subsection}{Low-Complexity Adaptive Design}
-			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains.
+			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively.
 For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
@@
 			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
-When the receiver works in TS mode, there is no superposition in the suboptimal waveform design.
-Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session.
+When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
 When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
@@
 			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
+			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
 
 			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-The rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} should be dropped, and no SCA is involved.
+Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
 The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-Similarly, no loss is introduced by SDR and local optimality is guaranteed, and the proofs are omitted.
+Similarly, no loss is introduced by SDR and local optimality is guaranteed.
+The proofs are omitted here.
 Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
@@
 The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
+It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
 
@@
 
-			\begin{proposition}\label{pr:bcd}
-				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge.
-			\end{proposition}
-
-			\begin{proof}\label{pf:bcd}
-				Please refer to Appendix~\ref{ap:bcd}
-			\end{proof}
-
-			For the low-complexity design under PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
+			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
@@
 The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel is modeled by IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter} and \num{3.5} onwards to further penalize the channels with large distance.
+We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
 All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
@@
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
-Each R-E point is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
+Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 			\centering
-			\subfloat[Channel\label{fi:channel_amplitude}]{
-				\resizebox{0.45\columnwidth}{!}{
+			\resizebox{0.8\columnwidth}{!}{
 				\input{assets/channel_amplitude.tex}
 			}
-			}
-			\subfloat[WIT: modulated\label{fi:waveform_wit_modulated}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wit_modulated.tex}
-				}
-			}\\
-			\subfloat[WPT: modulated\label{fi:waveform_wpt_modulated}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wpt_modulated.tex}
-				}
-			}
-			\subfloat[WPT: multisine\label{fi:waveform_wpt_multisine}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_wpt_multisine.tex}
-				}
-			}
-			\caption{Sorted channel and waveform amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\label{fi:channel_amplitude}
 		\end{figure}
 
-		Fig.~\subref*{fi:channel_amplitude} reveals how IRS influences the (sorted) channel amplitude and waveform design for one channel realization.
-Thanks to the flexible subchannel design enabled by passive beamforming, the optimal subchannel strength distribution for WIT and WPT are dissimilar.
+		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
+Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
 Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
 On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the water-filling scheme at high SNR, but is realized by channel alignment instead of resource allocation.
-Moreover, the amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\subref*{fi:waveform_wit_modulated}--\subref*{fi:waveform_wpt_multisine}.\footnote{Note that no multisine is used for WIT and the case is not shown.} It is concluded that adding an IRS to the SWIPT system has subtle impact on the waveform design.
+This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
+Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
+In other words, IRS has a subtle impact on the waveform design.
 
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can infer that no multisine waveform is needed for the entire R-E region.
-It aligns with the conclusion based on conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
+It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
 Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
@@
 First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
-At low SNR, the power is allocated to the modulated waveform on few strongest subbands to achieve a high rate.
-As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency coupling and harvester nonlinearity.
-Second, there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
+At low SNR, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power because of frequency coupling and harvester nonlinearity.
+Second, there exists a turning point in the R-E region, especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
 The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
-As $\bar{R}$ further decreases, due to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
+As $\bar{R}$ further decreases, thanks to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
@@
 Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ thus maximize the R-E tradeoff.
+Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
 It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
-Considering the passive characteristic of the IRS, chances are that it can be directly supported by the SWIPT network.
 
@@
 			}
-			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
+			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
 		\end{figure}
@@
 			}
-			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
+			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
 		\end{figure}
@@
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} gap compared to the nonlinear model-based SMF and GP designs.
+To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
 Third, passive beamforming has a larger array gain and power scaling order than active beamforming.
 This behavior is more obvious in the case of WIT and WPT.
-For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power.
-Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}.
-On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$ \cite{Wu2019}.
+For active beamforming, doubling $M$ brings a \SI{3}{\dBA} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power.
+Thanks to the rectenna nonlinearity, the output DC ends up with a nearly four-time (\SI{12}{\dBA}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}.
+On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dBA}, which implies a reflect array gain of $L^2$ \cite{Wu2019}.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$.
+Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC by \num{16} times (\SI{24}{\dBA}), corresponding to a passive scaling law in the order of $L^4$.
 Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
@@
 First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after average.
-Second, the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS when the bandwidth is large.
+Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after averaging.
+Second, when the bandwidth is small, the performance of ideal, adaptive, and WIT/WPT-optimized IRS are similar; when the bandwidth is large, the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
@@
 Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
-On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoff points for broadband SWIPT.
-As shown in Fig.~\subref*{fi:channel_amplitude}, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power, thanks to adaptive passive beamforming.
+On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoffs points for broadband SWIPT.
+As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high SNR, or focused on a few strongest subbands to boost the output DC, thanks to adaptive passive beamforming.
 
@@
 			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.
-$\epsilon_n^2 \to \infty$ corresponds to no CSIT and random IRS; $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
+$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
 		\end{figure}
@@
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-Consider an imperfect CSIT model where the cascaded channel at subband $n$ is
+We assume the cascaded channel at subband $n$ is
 		\begin{equation}
@@
 		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Perfect CSIT and no CSIT can be regarded as special cases with $\epsilon_{n}=0$ and $\epsilon_{n}=\infty$.
-Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
@@
 		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage BCD algorithm is proposed to solve the problem.
-In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition.
-In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method.
-We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves good balance between performance and complexity.
-Numerical results reveal significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
+Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
+A three-stage BCD algorithm was proposed to solve the problem.
+In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition.
+In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method.
+We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity.
+Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
 Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
-			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{co:irs_modulus}.
+			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds because of the modulus constraint~\eqref{co:irs_modulus}.
 Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and recast problem~\eqref{op:irs} as
@@
 			By applying SDR, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
-$\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds.
+$\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, and strong duality holds.
 The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
@@
 			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}.
+Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above because of the unit-modulus constraint \eqref{co:irs_modulus}.
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
@@
 		\begin{subsection}{Proof of Proposition~\ref{pr:mrt}}\label{ap:mrt}
-			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}.
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}.
+			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ and maximizes the rate \eqref{eq:R}.
+From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ and maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}.
 Therefore, MRT is the global optimal information and power precoder.
-		\end{subsection}
-
-		\begin{subsection}{Proof of Proposition~\ref{pr:bcd}}\label{ap:bcd}
-			The objective function \eqref{ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{al:sca} is local optimal, the active precoder by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal.
-\eqref{ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}.
-Therefore, Algorithm~\ref{al:bcd} is guaranteed to converge.
-However, it may not converge to optimal points since variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
 		\end{subsection}

### 2021-08-11 review/response_2.tex
:pencil: Update notations
:pencil: Update response letter

@@
 
-\externaldocument[M-]{../main}
+\externaldocument[M-]{../submit_2}
 
@@
 \DeclareSIUnit{\dBi}{\deci\beli}
+\DeclareSIUnit{\belA}{BA}
+\DeclareSIUnit{\dBA}{\deci\belA}
 
@@
 		\begin{point}
-			Please double-check Proposition~\ref{M-pr:bcd} and the algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
+			Please double-check Proposition~5 and the algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
 		\end{point}
@@
 			\begin{framed}
-				Based on practical IRS and energy harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
-The proposed framework provides a flexible balance between performance and complexity.
-
-				\textellipsis To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
+				Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+The proposed framework provides a flexible tradeoff between performance and complexity.
+To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
 			\end{framed}
@@
 			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}, where Algorithm~\ref{M-al:m_sca} is called during each iteration.
-To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved.
+To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved.
 To clarify this point, we have updated the description on Algorithm~\ref{M-al:m_sca} as follows.
@@
 				Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-The rate constraint \eqref{M-co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized, the current expression \eqref{M-eq:z_irs_approx} should be dropped, and no SCA is involved.
+Specifically, the rate constraint \eqref{M-co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized, the current expression \eqref{M-eq:z_irs_approx} is not needed and no SCA is involved.
 			\end{framed}
@@
 						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
-						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_i}, \eqref{M-eq:s_p}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_ip}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
@@
 						\If{$\rho=0$} \label{li:convergence_begin}
-							\State $\Delta = R^{(i)} - R^{(i-1)}$
+							\State $\Delta \gets  R^{(i)} - R^{(i-1)}$
 						\Else
-							\State $\Delta = z^{(i)} - z^{(i-1)}$
+							\State $\Delta \gets  z^{(i)} - z^{(i-1)}$
 						\EndIf
 					\Until $\lvert \Delta \rvert \le \epsilon$ \label{li:convergence_end}
-					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+					\State Set $\boldsymbol{\phi}^{\star}\gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}\gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
@@
 			\begin{framed}
-				To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnotemark Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
+				To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnotemark Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 			\end{framed}
@@
 From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the modulated and multisine waveforms.
-Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC current scales quadratically with $M$.
+Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC scales quadratically with $M$.
 We have cited those papers in the revised manuscript.
 
-			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario.
+			Next, we verify the last observation where the expectation of the DC scales quartically with $L$ in a much simplified scenario.
 Consider a SISO WPT system in a frequency-flat channel.
 We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted.
-With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
+With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC writes as
 			\begin{equation}
@@
 				}
-				\caption{Channel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 				\label{fi:channel_amplitude}
@@
 			\begin{framed}
-				Fig.~\ref{M-fi:channel_amplitude} reveals how IRS influences the (sorted) channel amplitude and waveform design for one channel realization.
-Thanks to the flexible subchannel design enabled by passive beamforming, the optimal subchannel strength distribution for WIT and WPT are dissimilar.
+				Fig.~6 reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
+Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
 Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
 On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the water-filling scheme at high SNR, but is realized by channel alignment instead of resource allocation.
-Moreover, the amplitude of modulated and multisine waveforms with and without IRS are shown in Figs.~\ref{M-fi:waveform_wit_modulated}--\ref{M-fi:waveform_wpt_multisine}.\footnotemark It is concluded that adding an IRS to the SWIPT system has subtle impact on the waveform design.
+This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
+Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
+In other words, IRS has a subtle impact on the waveform design.
 			\end{framed}
-			\footnotetext{Note that no multisine is used for WIT and the case is not shown.}
 			\label{re:2.2}
@@
 Indeed, the LC-BCD algorithm intends to draw the R-E tradeoff by performing a two-dimensional search that adjusts $\delta$ and $\rho$ from \num{0} to \num{1}.
-However, based on the deduction above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead.
+However, based on the reasoning above, we set $\delta=\rho$ is the simulation and obtain the R-E region by one-dimensional search instead.
 The results show that even a one-dimensional search for the LC-BCD algorithm can achieve a very good performance.
@@
 
-				\textellipsis Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
+				\textellipsis Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 
-				\textellipsis assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
+				\textellipsis assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
 
@@
 		\begin{response}
-			We would like to clarify that the performance loss under the conventional linear harvester model is revealed instead in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}.
+			We would like to clarify that the performance loss under the conventional linear harvester model is revealed in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}.
 Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz} are intended to compare different IRS strategies when both waveform and passive beamforming are designed under nonlinear harvester model.
@@
 				Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
-As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} gap compared to the nonlinear model-based SMF and GP designs.
+To investigate the performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}.
+As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
 			\end{framed}
@@
 Although the modulated waveform has an modulation gain of \num{2} that outstands for a small $N$, it creates no DC coupling between frequencies and is outperformed by multisine for a large $N$.
-Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT point, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation).
+Therefore, for a relatively small $N$, the modulated waveform is used at both WIT and WPT points, and one can heuristically infer that no multisine waveform is needed for any point (this is verified in simulation).
 In this case, the R-E region is convex, which aligns with the conventional linear harvester model (PS outperforms TS and dedicated power waveform is unnecessary).
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\ref{M-fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT point, and one can infer that no multisine waveform is needed for the entire R-E region.
-It aligns with the conclusion based on conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under nonlinear harvester model.
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
+It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
 Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
@@
 			\begin{framed}
-				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated waveform (deterministic multisine) to boost the spectrum and energy efficiency.
+				As suggested in \cite{M-Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
 The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
@@
 			\begin{framed}
-				The cascaded channel varies at different subbands but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite channel should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-That is to say, IRS essentially enables an flexible subchannel design.
+That is to say, IRS essentially enables a flexible subchannel design.
 In the MISO case, a similar effect also exists in the spatial domain.
@@
 		\begin{point}
-			Proposition~\ref{M-pr:bcd} is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
+			Proposition~5 is questionable. The algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
 		\end{point}
@@
 Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together.
-We have removed the claim on optimality and updated Proposition~\ref{M-pr:bcd} as follows.
+We have removed the claim on optimality and updated the manuscript as follows.
 			\begin{framed}
-				For any feasible initial point, the BCD Algorithm~\ref{M-al:bcd} is guaranteed to converge.
-			\end{framed}
-			The proof has been modified correspondingly.
-			\begin{framed}
-				The objective function \eqref{M-ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{M-al:sca} is local optimal, the active precoder by \eqref{M-eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{M-al:gp} are local optimal.
-\eqref{M-ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{M-co:original_modulus} and the transmit power constraint \eqref{M-co:original_power}.
-Therefore, Algorithm~\ref{M-al:bcd} is guaranteed to converge.
-However, it may not converge to optimal points since variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
+				\textellipsis It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
 			\end{framed}
@@
 			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference.
+Moreover, all plots are re-simulated over \num{100} channel realizations.
 Please refer to the following specification for details.
 			\begin{framed}
-				We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter} and \num{3.5} onwards to further penalize the channels with large distance.
+				We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{M-Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
 All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
@@
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{M-Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (thus one-dimensional search to obtain the R-E region).
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
+Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 			\end{framed}
@@
 			\begin{framed}
-				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete uniform IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and perform quantization on the continuous reflection coefficients obtained by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead.\footnotemark
+				On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{M-al:bcd} to reduce the circuit complexity and control overhead.\footnotemark
 			\end{framed}
-			\footnotetext{Note that this relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.}
+			\footnotetext{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.}
 		\end{response}
@@
 			\begin{framed}
-				Based on practical IRS and energy harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage.
-The proposed framework provides a flexible balance between performance and complexity.
+				Based on practical IRS and harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+The proposed framework provides a flexible tradeoff between performance and complexity.
 			\end{framed}
@@
 		\begin{response}
-			Thank you for the suggestion and we have incorporated one magazine paper \cite{Wu2020} into the manuscript.
+			Thank you for the suggestion.
 A recent tutorial paper \cite{Wu2021c} provided a comprehensive overview on IRS-aided wireless-powered networks, where channel estimation, resource allocation and practical constraints are discussed in detail.
 However, the aforementioned paper appeared on arXiv after ours and have cited our work, and we decided not to cite it.
+We have incorporated one magazine paper \cite{Wu2020} into the manuscript.
 			\begin{framed}
-				\textellipsis The hardware architecture, design challenges and application opportunities of practical IRS are covered in \cite{Wu2020}.
+				\textellipsis The hardware architecture, design challenges, and application opportunities of practical IRS are covered in \cite{Wu2020}.
 			\end{framed}

### 2021-08-12 assets/channel_amplitude.tex
:bento: Update assets

@@
 ymajorgrids,
-legend style={legend cell align=left, align=left, draw=white!15!black},
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
+title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]
@@
 ymajorgrids,
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]

### 2021-08-12 assets/convergence_bcd.tex
:bento: Update assets

@@
 ylabel style={font=\color{white!15!black}},
-ylabel={DC current [$\mu$A]},
+ylabel={DC [$\mu$A]},
 axis background/.style={fill=white},

### 2021-08-12 assets/waveform_subband.tex
:bento: Update assets

@@
 width=4.036in,
-height=0.438in,
-at={(0.677in,3.233in)},
+height=0.462in,
+at={(0.677in,3.21in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
-1	4.47213593413934\\
+1	4.47213593809508\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
-1	0.000411418946938571\\
+1	0.000358590327058133\\
 };
@@
 width=4.036in,
-height=0.438in,
-at={(0.677in,2.54in)},
+height=0.462in,
+at={(0.677in,2.522in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.434593216761001\\
-2	4.3899297145933\\
+1	0.550823184768846\\
+2	4.36837845097092\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.15579196934664e-05\\
-2	1.1748417131072e-05\\
+1	1.48597207854411e-05\\
+2	1.53805823004565e-05\\
 };
@@
 width=4.036in,
-height=0.438in,
-at={(0.677in,1.846in)},
+height=0.462in,
+at={(0.677in,1.834in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.0143736245770149\\
-2	0.0303952314208929\\
-3	0.115397989725443\\
-4	1.83286171599636\\
+1	0.0326721056203988\\
+2	0.0697944085211443\\
+3	0.193520763120912\\
+4	1.91750698481035\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	1.03274778152889\\
-2	1.26444789136652\\
-3	1.50497289223671\\
-4	2.05482037288244\\
+1	0.972503011468572\\
+2	1.22779327868874\\
+3	1.48063097057209\\
+4	2.13162879975205\\
 };
@@
 width=4.036in,
-height=0.438in,
-at={(0.677in,1.152in)},
+height=0.462in,
+at={(0.677in,1.146in)},
 scale only axis,
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.00193817595567525\\
-2	0.00257713054060487\\
-3	0.00348488793501541\\
-4	0.00488691757665795\\
-5	0.00708186101407546\\
-6	0.0115819776031387\\
-7	0.0297619841444503\\
-8	0.248823174288891\\
+1	0.00676327571402152\\
+2	0.00930781551713654\\
+3	0.0129863266085796\\
+4	0.0182780278377859\\
+5	0.0264785684252956\\
+6	0.0417816477229242\\
+7	0.0921547943904462\\
+8	0.387871897134795\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.958056681914786\\
-2	1.1753523246861\\
-3	1.34398156020033\\
-4	1.48468938243277\\
-5	1.59662285127524\\
-6	1.68382811164256\\
-7	1.75299266281476\\
-8	1.84970533450897\\
+1	0.897080828535262\\
+2	1.11267484124012\\
+3	1.2760937466216\\
+4	1.42973823824102\\
+5	1.54367522426452\\
+6	1.64897920494507\\
+7	1.73956386270218\\
+8	1.89059947472085\\
 };
@@
 width=4.036in,
-height=0.438in,
+height=0.462in,
 at={(0.677in,0.458in)},
@@
 \addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
-1	0.000699803366708424\\
-2	0.000800867722584431\\
-3	0.000917767493119273\\
-4	0.00105546869283256\\
-5	0.0012213408897823\\
-6	0.00141507752657299\\
-7	0.00165144517333923\\
-8	0.00193060125433753\\
-9	0.00227670870277157\\
-10	0.0027030187224025\\
-11	0.00324897530466221\\
-12	0.00397867693137808\\
-13	0.00501781698344776\\
-14	0.00655613193903264\\
-15	0.009024934371904\\
-16	0.0130872335381684\\
+1	0.00205132551819701\\
+2	0.00235447373497551\\
+3	0.00272196136127332\\
+4	0.00316588966668174\\
+5	0.00369517036368117\\
+6	0.00432537450541609\\
+7	0.00508695652011363\\
+8	0.00600094215308655\\
+9	0.00710012267822671\\
+10	0.00851262778314969\\
+11	0.0103510448032954\\
+12	0.0128569172775466\\
+13	0.0164283761517276\\
+14	0.0229541038226562\\
+15	0.0402894292810385\\
+16	0.0926842285796484\\
 };
@@
 \addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
-1	0.658945444448673\\
-2	0.748750326986652\\
-3	0.825803524447847\\
-4	0.897209109075901\\
-5	0.959520330551997\\
-6	1.01644204271237\\
-7	1.07098120306596\\
-8	1.11834785156968\\
-9	1.16491430867279\\
-10	1.20444111502631\\
-11	1.24260696441405\\
-12	1.27263946826968\\
-13	1.29990806955352\\
-14	1.31826230888077\\
-15	1.33150577776743\\
-16	1.33694997002172\\
+1	0.628841069483884\\
+2	0.717675502523908\\
+3	0.795496148359302\\
+4	0.864626670343281\\
+5	0.930591126638763\\
+6	0.989724762400551\\
+7	1.04508455096183\\
+8	1.09678731061405\\
+9	1.14380160245268\\
+10	1.18636001210616\\
+11	1.2248217690153\\
+12	1.2585853066132\\
+13	1.28750705323146\\
+14	1.31224542931104\\
+15	1.33460858167442\\
+16	1.35822969320702\\
 };

### 2021-08-12 assets/waveform_wit_modulated.tex
:bento: Update assets

@@
 legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
 ]
@@
 ymajorgrids,
-title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
+title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
 ]

### 2021-08-12 review/response_2.tex
:package: Add review-related files

@@
 				}
-				\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+				\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 				\label{fi:channel_amplitude}
@@
 			In the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference.
-Moreover, all plots are re-simulated over \num{100} channel realizations.
+Moreover, all plots are re-simulated over \num{200} channel realizations.
 Please refer to the following specification for details.
@@
 We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
-Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 			\end{framed}

### 2021-08-12 review/letter_2.tex
:package: Add review-related files

--- 2021-01-28 letter.tex
@@
 	\begin{letter}{Prof.
-Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design)}
+Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-21-0553 (IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model)}
 		\opening{Dear Prof. Liang Xiao and Reviewers,}
@@
 The manuscript has been revised carefully based on your valuable comments and suggestions.
-In particular, we attempted to clarify the motivations and contributions of this work.
-To answer the questions and concerns, we include a point-to-point response below, which also describes all modifications made to the manuscript.
+In particular, we added computational complexity analysis for all proposed algorithms, addressed the optimality issue regarding Algorithm 4, discussed the convergence conditions in Algorithm 5, emphasized the design challenge introduced by passive beamforming and nonlinear EH model, and updated the simulation parameters and reference list.
+To answer the questions and concerns, we also include a point-to-point response below to discuss all modifications made to the manuscript.
 We hope that the revisions are to the satisfaction of the editor and reviewers.

### 2021-08-12 review/submit_1.tex
:package: Add review-related files

\documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usetikzlibrary{plotmarks}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\usetikzlibrary{arrows,matrix,positioning}

\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicif}{\textbf{If}}
\algrenewcommand{\algorithmicthen}{\textbf{Then}}
\algrenewcommand{\algorithmicelse}{\textbf{Else}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}

\makeatletter
\newcommand\setalgorithmcaptionfont[1]{%
	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
	\def\floatc@ruled{%
		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
		#1\floatc@ruled}}
\algrenewcommand\ALG@beginalgorithmic{\footnotesize}
\makeatother

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE,}\\
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes. Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique. To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes. Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states. Results also emphasize the importance of modeling harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
	\end{abstract}

	\begin{IEEEkeywords}
		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, beamforming design, energy harvester nonlinearity.
	\end{IEEEkeywords}

	\begin{section}{Introduction}
		\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via Radio-Frequency (RF) waves. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}. The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage is then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.

		Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming). Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection. Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.

		The major issue of WPT and SWIPT is the low harvested DC power. To increase it, we introduce an IRS that enhances the end-to-end energy efficiency and boosts the harvester input power level. The smart channel control and low power consumption of IRS can bring more opportunities to SWIPT. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams. However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model. Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

		\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, a beamforming gain, and the channel selectivity across spatial and frequency domains to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.

		\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

		\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time and power domains to facilitate practical SWIPT implementation. To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode. The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.

		\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

		\emph{Organization:} Section~\ref{se:system_model} introduces the system model. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design. Section~\ref{se:performance_evaluation} provides simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

		\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
	\end{section}

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.5\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided multi-carrier SWIPT system.}
			\label{fi:system}
		\end{figure}

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands. We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels are known. The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.

		\begin{subsection}{Transmitted Signal}
			Denote $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ as the information symbol transmitted over subband $n \in \{1, \dots, N\}$. The superposed signal transmitted on antenna $m \in \{1, \dots, M\}$ at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\mathrm{I},n,m}\tilde{x}_{\mathrm{I},n}(t)}+w_{\mathrm{P},n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{\mathrm{I/P},n,m}$ denotes the complex weight of the modulated/multisine waveform transmitted at subband $n$ on antenna $m$, and $f_n$ is the frequency of subband $n$. On top of this, we stack up $\boldsymbol{w}_{\mathrm{I/P},n} \triangleq [w_{\mathrm{I/P},n,1},\dots,w_{\mathrm{I/P},n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq [x_1(t),\dots,x_M(t)]^T \triangleq \boldsymbol{x}_{\mathrm{I}}(t)+\boldsymbol{x}_{\mathrm{P}}(t) \in \mathbb{C}^{M \times 1}$, where
			\begin{equation}
				\boldsymbol{x}_{\mathrm{I}}(t) = \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\quad \boldsymbol{x}_{\mathrm{P}}(t) = \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}
			\end{equation}
			are the modulated and multisine components, respectively.
		\end{subsection}

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define respectively $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.

			\begin{remark}\label{re:reflection_coefficient}
				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely. Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands. In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
			\end{remark}

			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$. The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel. Hence, the composite equivalent channel reduces to
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define the cascaded channel without IRS reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.

			\begin{remark}\label{re:subband_tradeoff}
				The cascaded channel varies at different frequencies. Since we regard the reflection as frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain. Moreover, each IRS element simultaneously assists all transmit antennas such that the reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Received Signal}
			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
			\begin{equation}
				y_{\mathrm{I}}(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}, \quad y_{\mathrm{P}}(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			capture respectively the modulated and multisine components. Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
		\end{subsection}

		\begin{subsection}{Receiving Modes}
			\begin{figure}[!t]
				\centering
				\subfloat[TS receiver\label{fi:ts_receiver}]{
					\resizebox{0.45\columnwidth}{!}{
						\centering
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
								to[short,-o] ++(0,-1) node[below]{Time Switcher}
								to[short] node[spdt,anchor=in](s){} ++(0.5,0);

							\draw (s.out 1) node[above right]{$1-\eta$}
								to ++(1.25,0)
								to ++(0,0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);

							\draw (s.out 2) node[below right]{$\eta$}
								to ++(1.25,0)
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\subfloat[PS receiver\label{fi:ps_receiver}]{
					\resizebox{0.45\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
								to[short,-o] ++(0,-1)
								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
							\draw (c.right up)
								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
								to ++(0,0.5)
								to ++(1.25,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
							\draw (c.right down)
								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
								to ++(0,-0.5)
								to ++(1.25,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\caption{Practical co-located receiving modes.}
				\label{fi:receiver}
			\end{figure}

			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes for the co-located information decoder and energy harvester \cite{Zhou2013} to utilize the superposed signal. The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively. During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly. Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point. On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively. The data stream is fed into the information decoder while the energy stream is fed into the energy harvester. During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff. In the following context, we consider the analysis based on the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at RF-band and during RF-to-baseband conversion on tone $n$. Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

		\begin{subsection}{Energy Harvester}
			\begin{figure}[!t]
				\centering
				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
					\resizebox{0.3\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
					\resizebox{0.3\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
					}
				}
				\caption{Receive antenna and energy harvester circuits.}
			\end{figure}

			Importantly the rectenna model used in this section, taken from \cite{Clerckx2016a}, captures the dependency of the output DC current on both the power and shape of the received signal. This is critical for efficient signal designs in WPT and SWIPT \cite{Clerckx2021}. Fig.~\ref{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has an resistance $R_{\mathrm{A}}$ and the incoming signal creates an voltage source $v_{\mathrm{S}}(t)$. Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible. When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by
			\begin{align}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)
				& = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr) +\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}&&\nonumber\\
				& \quad +6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
			\end{align}

			Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms. Moreover, we define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$. Hence, the components of $z$ reduce to
			\begin{align}
				\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
				\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
				\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
				\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
					& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
			\end{align}

			\begin{figure*}[!t]
				\begin{equation*}
					\boldsymbol{W}_{\mathrm{I/P}}=
					\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
						\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
						{
							\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
							\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
							\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
							\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
						};
						\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
						\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
						\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
						\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
						\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
						\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
						\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
						\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
					\end{tikzpicture}
				\end{equation*}
				\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$. $\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks. Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively. For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
				\label{fi:block_diagonal}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{equation}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{equation}
			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of sine waves to the average value.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

		\begin{subsection}{Passive Beamforming}
			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
			\begin{align}
				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}
				= \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}
				= \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})
				= \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
			\end{align}
			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{\mathrm{I/P},k}$ as
			\begin{align}
				t_{\mathrm{I/P},k}
				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}
				= \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})
				= \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})
				= \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})
				= \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
			\end{align}
			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
			\begin{align}
				R(\boldsymbol{\Phi})
				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
				z(\boldsymbol{\Phi})
				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}\label{eq:z_irs}
			\end{align}

			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
			\begin{align}
				(t_{\mathrm{I},0}^{(i)})^2
				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
				& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2.\label{eq:taylor_3}
			\end{align}

			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices. Due to symmetry \cite{Huang2017}, we have
			\begin{equation}\label{eq:coupled_terms}
				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
			\end{equation}

			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation
			\begin{align}
				\tilde{z}(\boldsymbol{\Phi}^{(i)})
				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right)\label{eq:z_irs_approx}
			\end{align}
			and transform problem~\eqref{op:original} to
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
			\end{maxi!}
			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}. The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it to formulate a convex problem \cite{Luo2010}. The tightness of rank relaxation is verified below.

			\begin{proposition}\label{pr:relaxation}
				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
			\end{proposition}

			\begin{proof}\label{pf:relaxation}
				See Appendix~\ref{ap:relaxation}.
			\end{proof}

			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}. We update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}.
			\setalgorithmcaptionfont{\scriptsize}
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\bar{R},\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

			\begin{proposition}\label{pr:sca}
				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
			\end{proposition}

			\begin{proof}\label{pf:sca}
				See Appendix~\ref{ap:sca}.
			\end{proof}
		\end{subsection}

		\begin{subsection}{Active Beamforming}
			We decouple the waveform in the spatial and frequency domains by
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder. Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}^{N \times 1}$. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b_n}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
			\end{equation}

			\begin{proposition}\label{pr:mrt}
				For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
			\end{proposition}

			\begin{proof}\label{pf:mrt}
				See Appendix~\ref{ap:mrt}.
			\end{proof}
		\end{subsection}

		\begin{subsection}{Waveform and Splitting Ratio}
			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$. On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$, and \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
			\begin{align}
				R(\boldsymbol{s}_{\mathrm{I}},\rho)
				& = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),\label{eq:R_waveform}\\
				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \Biggl( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 \nonumber\\
				& \quad + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \Biggr) + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).&&\label{eq:z_waveform}
			\end{align}so that problem~\eqref{op:original} boils down to

			\begin{maxi!}
				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
			\end{maxi!}

			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
			\begin{mini!}
				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
				\addConstraint{\rho + \bar{\rho} \le 1.}
			\end{mini!}

			The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
			\begin{align}
				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}
			\end{align}
			where $m_{\mathrm{I},n}=2$ and $m_\mathrm{P}=(2N^3+6N^2+7N)/3$. We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
			\begin{mini!}
				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
				\addConstraint{\rho + \bar{\rho} \le 1}
			\end{mini!}
			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$, $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$. The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
			\begin{align}
				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
			\end{align}

			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}. We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence. The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}.
			\setalgorithmcaptionfont{\scriptsize}
			\begin{algorithm}[!t]
				\caption{GP: Waveform Amplitude and Splitting Ratio.}
				\label{al:gp}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_n,P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
					\State Compute $R^{(0)},z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Repeat
						\State $i \gets i + 1$
						\State Update $\{\gamma_{m_{\mathrm{I},n}}^{(i)},\gamma_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star},\boldsymbol{s}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

			\begin{proposition}\label{pr:gp}
				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
			\end{proposition}

			\begin{proof}\label{pf:gp}
				See \cite{Clerckx2016a,Clerckx2018b}.
			\end{proof}
		\end{subsection}

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality with exponential computational complexity \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design. Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session. When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}

			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.

			\setalgorithmcaptionfont{\scriptsize}
			\begin{algorithm}[!t]
				\caption{M-SCA: IRS Phase Shift.}
				\label{al:m_sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\If{$\rho=0$}
						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
					\Else
						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
						\Repeat
							\State $i \gets i + 1$
								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\EndIf
					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

		\begin{subsection}{Block Coordinate Descent}
			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence. The steps are summarized in the BCD Algorithm~\ref{al:bcd}. For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
			\setalgorithmcaptionfont{\scriptsize}
			\begin{algorithm}[!t]
				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
				\label{al:bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

			\setalgorithmcaptionfont{\scriptsize}
			\begin{algorithm}[!t]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $R^{(i)},z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}

			\begin{proposition}\label{pr:bcd}
				For any feasible initial point, the BCD Algorithm~\ref{al:bcd} is guaranteed to converge to local optimal points of the original waveform and beamforming problem~\eqref{op:original}.
			\end{proposition}

			\begin{proof}\label{pf:bcd}
				See Appendix~\ref{ap:bcd}
			\end{proof}
		\end{subsection}
	\end{section}

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is \SI{2}{\dBi}. Moreover, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \emph{First,} it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. It is because less power is allocated to each subband but more balanced DC terms are introduced to boost the harvested energy. On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order. It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. This observation origins from the rectifier nonlinearity. Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials. Hence, the benefit of multisine outstands for a sufficiently large $N$. \emph{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefers PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depend on the number of subbands.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_noise}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_noise.tex}
				}
			}
			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/splitting_ratio_noise.tex}
				}
			}
			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		The average noise power influences the R-E region as in Fig.~\ref{fi:re_noise}. \emph{First,} we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly. At low SNR, the power is allocated to the modulated waveform on few strongest subbands to achieve a high rate. As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power due to frequency coupling and harvester nonlinearity. \emph{Second,} there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose. As $\bar{R}$ further decreases, due to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$. The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss product\label{fi:path_loss}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$. Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}. Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ thus maximize the R-E tradeoff. It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems. Considering the passive characteristic of the IRS, chances are that it can be directly supported by the SWIPT network.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
		\end{figure}

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \emph{First,} adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy. \emph{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT. As a reference, the Adaptive Single Sinewave (ASS) allocates all power to the multisine at the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}. For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR, which corresponds to a transmit array gain of $M$ and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, which suggests an active scaling law in the order of $M^2$. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB}, which implies a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. Moreover, the ASS strategy does not exploit the harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap compared to SMF and GP. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the passive beamforming design.

		\begin{figure}[!t]
			\centering
			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_irs_1mhz.tex}
				}
			}
			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_irs_10mhz.tex}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT. The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}. The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region. The random IRS models the phase shift of all elements as i.i.d. uniform random variables over $[0, 2\pi)$. \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited. Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations. \emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS when the bandwidth is large. In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands. It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region. Hence, the achievable R-E region is obtained by varying the waveform amplitude and splitting ratio. On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoff points for broadband SWIPT. By adaptive passive beamforming, the equivalent channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power. It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.35\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance. Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis. Consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
		\begin{equation}
			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
		\end{equation}
		where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$. Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$. Note that the estimations at different subbands are independent, but the subchannel responses are indeed correlated. Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$. On the other hand, since the practical reflection coefficient depends on the available element impedances, we quantize each reflection coefficient by $b$ bits and introduce a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead. Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible. These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
	\end{section}

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in a novel IRS-aided multi-carrier MISO SWIPT system. Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region. A three-stage local optimal BCD algorithm is proposed to solve the problem. In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition. In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method. We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance in different scenarios. Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design. Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order. However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.

        One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system. Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
	\end{section}

	\begin{appendix}
		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds due to the modulus constraint~\eqref{co:irs_modulus}. Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and recast problem~\eqref{op:irs} as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
			\end{maxi!}

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian at iteration $i$ is given by
			\begin{align}\label{eq:lagrangian}
				\mathcal{L}
				&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
						(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
					\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
						4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
						\Bigr)
						\nonumber\\
				&\quad+ \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
					\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
					\Bigr) + 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
						\Bigr)\nonumber\\
				&\quad- \mathrm{tr}^2 \Bigl(
					(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
					\Bigr)
					\Biggr) + \mu \Biggl(
					2^{\bar{R}} - \prod_{n=1}^N \biggl(
						1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
							\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
						\Bigr)}{\sigma_n^2}
					\biggr)
				\Biggr)\nonumber\\
				&\quad+ \mathrm{tr}\biggl(
					\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
						\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
					\Bigr)
				\biggr) - \mathrm{tr} \Bigl(
					\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
				\Bigr) + \zeta,
			\end{align}
			where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$. The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
			\begin{subequations}
				\begin{equation}\label{eq:lagrange_multiplier}
					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:complementary_slackness}
					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:gradient}
					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}

			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is given by
			\begin{align}\label{eq:delta}
				\boldsymbol{\Delta}^\star
				&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
					\Biggl(
						2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k}\nonumber\\
				&\quad+ (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) - (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
						\Bigr)
					\Biggr)\nonumber\\
				&\quad+ \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
					1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
						\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
					\Bigr)}{\sigma_{n'}^2}
				\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).
			\end{align}

			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
		\end{subsection}

		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$. Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \eqref{co:irs_modulus}. Thus, Algorithm~\ref{al:sca} is guaranteed to converge. Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}. Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem. According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
		\end{subsection}

		\begin{subsection}{Proof of Proposition~\ref{pr:mrt}}\label{ap:mrt}
			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ thus maximizes the rate \eqref{eq:R}. From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ thus maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}. Therefore, MRT is the global optimal information and power precoder.
		\end{subsection}

		\begin{subsection}{Proof of Proposition~\ref{pr:bcd}}\label{ap:bcd}
			The objective function \eqref{ob:original} is non-decreasing over the iterations of Algorithm~\ref{al:bcd}, which is also upper-bounded due to the unit-modulus constraint \eqref{co:original_modulus} and the transmit power constraint \eqref{co:original_power}. Therefore, Algorithm~\ref{al:bcd} is guaranteed to converge. Since the IRS phase shift by Algorithm~\ref{al:sca} is local optimal, the active precoder by \eqref{eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{al:gp} are local optimal, according to \cite{Grippo2000}, the limit point obtained by iteratively updating $\boldsymbol{\phi}$, $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$, $\boldsymbol{s}_{\mathrm{I/P}}$ and $\rho$ via Algorithm~\ref{al:bcd} is also local optimal to problem~\eqref{op:original}.
		\end{subsection}
	\end{appendix}

	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

### 2021-08-12 review/submit_2.tex
:package: Add review-related files

--- 2021-08-11 main.tex
@@
-\documentclass[journal]{IEEEtran}
+\documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}
 
@@
 \usepackage{siunitx}
+\usepackage{soul}
 \usepackage{stfloats}
@@
 
+\makeatletter
+\newcommand\setalgorithmcaptionfont[1]{%
+	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
+	\def\floatc@ruled{%
+		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
+		#1\floatc@ruled}}
+\algrenewcommand\ALG@beginalgorithmic{\footnotesize}
+\makeatother
+
+\setalgorithmcaptionfont{\scriptsize}
+
+\soulregister\cite7
+\soulregister\ref7
+\soulregister\eqref7
+\soulregister\num7
+
 \begin{document}
@@
 			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
-
-			This paper has been submitted for publication.
 		}
@@
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
+The answers shed new light on the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
 It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
@@
 To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
+\hl{The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.} In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
 		\end{subsection}
@@
 		\begin{subsection}{IRS-Aided SWIPT}
-			By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
-In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+			\hl{By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.} In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
 It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
 However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+\hl{Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
 The proposed framework provides a flexible tradeoff between performance and complexity.
-To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
+To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.} In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, \hl{to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.} We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
 
 			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
+\hl{Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.} To exploit the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
 The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
@@
 The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
-The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
+\hl{The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.}
 
 			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that \hl{1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT;} 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 			\centering
-			\def\svgwidth{0.9\columnwidth}
+			\def\svgwidth{0.5\columnwidth}
 			\import{assets/}{system.pdf_tex}
@@
 
-		\begin{subsection}{Transmitted Signal}
+		\begin{subsection}{\hl{Transmitted Signal}}
 			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
@@
 			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
+				\hl{The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
 Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
@@
 In the MISO case, a similar effect also exists in the spatial domain.
-Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
+Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.}
 			\end{remark}
@@
 
-		\begin{subsection}{Received Signal}
+		\begin{subsection}{\hl{Received Signal}}
 			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
@@
 				\subfloat[TS receiver\label{fi:ts_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
+					\resizebox{0.45\columnwidth}{!}{
 						\centering
@@
 				}
-				\\
 				\subfloat[PS receiver\label{fi:ps_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
+					\resizebox{0.45\columnwidth}{!}{
 						\begin{circuitikz}[transform shape]
@@
 In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by
+			\begin{align}
+				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}\nonumber\\
+				&\quad+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
+			\end{align}
 			Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
@@
 As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
+Hence, the components of $z$ reduce to
+			\begin{align}
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
+				&\qquad\qquad=\frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+			\end{align}
 
@@
 			\end{figure*}
-
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
-				\end{align}
-			\end{figure*}
 		\end{subsection}
@@
 			The achievable R-E region is defined as
-			\begin{align}
-				\mathcal{C}_{\mathrm{R-E}}
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
-			\end{align}
+			\begin{equation}
+				\mathcal{C}_{\mathrm{R-E}} \triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
+			\end{equation}
 			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of the sine waves to the average value.
@@
 				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
+				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}
+				= \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}
+				= \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})
+				= \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
 			\end{align}
@@
 				t_{\mathrm{I/P},k}
-				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
+				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}
+				= \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})
+				= \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
+				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})
+				= \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})
+				= \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k}
 			\end{align}
@@
 				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
 			\end{align}
@@
 			\end{equation}
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
-			\begin{figure*}[!b]
-				\hrule
+			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as
 			\begin{align}
@@
 			\end{align}
-			\end{figure*}
+			Hence, problem~\eqref{op:original} is transformed to
 			\begin{maxi!}
@@
 			\end{maxi!}
-			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.
-In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+			\hl{We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.} In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
 This conclusion is summarized below.
@@
 
-			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
-The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.
+			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by \hl{$\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$}.
+The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, \hl{where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.}
 
@@
 					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+					\State Set \hl{$\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$}
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 		\begin{subsection}{Active Beamforming}
-			To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.
-The weight on subband $n$ is essentially
+			\hl{To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.} The weight on subband $n$ is essentially
 			\begin{equation}\label{eq:w}
@@
 			\end{equation}
-			and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
-			\begin{figure*}[!b]
-				\hrule
+			and the DC \eqref{eq:z_expand} rewrites as
 			\begin{align}
 				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
-				\end{align}
-			\end{figure*}
+				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \Biggl( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2\nonumber\\
+				& \quad + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \Biggr) + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
+			\end{align}
+			On top of this, problem~\eqref{op:original} boils down to
 			\begin{maxi!}
@@
 			\end{mini!}
-			It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
-The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
+			\hl{It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.} The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
 			\begin{align}
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
-			\end{align}
-			We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} \triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho}), \quad z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) \triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_IP}.
+			\end{align}
+			We upper bound \eqref{eq:g_IP} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 			\begin{mini!}
@@
 			\begin{align}
-				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
-			\end{align}
-			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+				\gamma_{m_{\mathrm{I},n}}^{(i)} = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}, \quad \gamma_{m_\mathrm{P}}^{(i)} = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_IP}.
+			\end{align}
+			With \eqref{eq:gamma_IP}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
 We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
-The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, \hl{which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.}
 
@@
 					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_IP}
 					\Repeat
 						\State $i \gets i + 1$
-						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
+						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_IP}
 						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
 						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_IP}
 					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
@@
 			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
-			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
+				s_{\mathrm{I}, n} = \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \quad s_{\mathrm{P}, n} = \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_ip}
+			\end{align}
+			\hl{where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{\hl{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}}}
 
 			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+\hl{Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
 To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
@@
 Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
+Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.}
 
@@
 					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+					\State \hl{Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$}
 					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
@@
 			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
-It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
+The steps are summarized in the BCD Algorithm~\ref{al:bcd}, \hl{whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
+It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.}
 
@@
 
-			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
+			\hl{For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_ip}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{\hl{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.}} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.}
 
@@
 						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_ip}
 						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
@@
 						\If{$\rho=0$}
-							\State $\Delta \gets R^{(i)} - R^{(i-1)}$
+							\State \hl{$\Delta \gets R^{(i)} - R^{(i-1)}$}
 						\Else
-							\State $\Delta \gets z^{(i)} - z^{(i-1)}$
+							\State \hl{$\Delta \gets z^{(i)} - z^{(i-1)}$}
 						\EndIf
-					\Until $\lvert \Delta \rvert \le \epsilon$
+					\Until \hl{$\lvert \Delta \rvert \le \epsilon$}
 					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
@@
 			\centering
-			\def\svgwidth{0.9\columnwidth}
+			\def\svgwidth{0.5\columnwidth}
 			\import{assets/}{layout.pdf_tex}
@@
 The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
-All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
+We consider a large open space Wi-Fi-like environment at center frequency \hl{\mbox{\SI{2.4}{\GHz}}} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
+\hl{Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \mbox{\SI{10}{\meter}}, and \num{3.5} onwards to further penalize the channels with large distance.} All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
 CSCG variables.
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
-Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.8\columnwidth}{!}{
+We also choose the average Effective Isotropic Radiated Power (EIRP) as \hl{$P=\mbox{\SI{40}{\dBm}}$}, the receive antenna gain as \hl{\mbox{\SI{3}{\dBi}}}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity \hl{(and one-dimensional search to obtain the R-E region)}.
+Each R-E point is averaged over \hl{\num{200}} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.5\columnwidth}{!}{
 				\input{assets/channel_amplitude.tex}
 			}
-			\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			% \subfloat[Channel amplitude\label{fi:channel_amplitude}]{
+			% 	\resizebox{0.5\columnwidth}{!}{
+			% 		\input{assets/channel_amplitude.tex}
+			% 	}
+			% }
+			\caption{\hl{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\mbox{\SI{-40}{\dBm}}$, $B=\mbox{\SI{10}{\MHz}}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\mbox{\SI{2}{\meter}}$.}}
 			\label{fi:channel_amplitude}
@@
 
-		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
+		\hl{Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
 Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
@@
 Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
-In other words, IRS has a subtle impact on the waveform design.
+In other words, IRS has a subtle impact on the waveform design.}
 
@@
 			\subfloat[R-E region\label{fi:re_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_subband.tex}
@@
 			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/waveform_subband.tex}
@@
 When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
+\hl{When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
 It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
-Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.} Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
 
@@
 			\subfloat[R-E region\label{fi:re_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_noise.tex}
@@
 			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/splitting_ratio_noise.tex}
@@
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
-Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
+\hl{Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.}
 
@@
 			\subfloat[R-E region\label{fi:re_distance}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_distance.tex}
@@
 			\subfloat[Path loss product\label{fi:path_loss}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/path_loss.tex}
@@
 			\subfloat[R-E region\label{fi:re_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_tx.tex}
@@
 			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/scaling_tx.tex}
@@
 			}
-			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
+			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
 		\end{figure}
@@
 			\subfloat[R-E region\label{fi:re_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_reflector.tex}
@@
 			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/scaling_reflector.tex}
@@
 		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
+\hl{First, it is observed that adding either active or passive elements can improve the equivalent SNR and produce a nearly concave R-E region, which suggests that the receiver should operate in the PS mode in such cases.
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
+To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.} As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \mbox{\SI{20}{\dBA}} gap compared to the nonlinear model-based SMF and GP designs.
 Third, passive beamforming has a larger array gain and power scaling order than active beamforming.
@@
 			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_irs_1mhz.tex}
@@
 			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_irs_10mhz.tex}
@@
 			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_csi.tex}
@@
 			\subfloat[Quantized IRS\label{fi:re_quantization}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.375\columnwidth}{!}{
 					\input{assets/re_quantization.tex}
@@
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-We assume the cascaded channel at subband $n$ is
-		\begin{equation}
-			\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
-		\end{equation}
-		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+We assume the cascaded channel at subband $n$ is $\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n}$, where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{\hl{Note that the subchannel responses are correlated but the estimations can be independent.}} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and \hl{uniformly quantize} the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{\hl{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.}} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
@@
         One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
+\hl{Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.}
 	\end{section}
@@
 $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, and strong duality holds.
-The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
-			\begin{figure*}[!b]
-				\hrule
+The corresponding Lagrangian function at iteration $i$ is given by
 			\begin{align}\label{eq:lagrangian}
@@
 							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-							\Bigr) + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
+						\Bigr)\nonumber\\
+				& \quad + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
 							\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
-							\Bigr)\nonumber\\
-					& \quad + 2 t_{\mathrm{P},0}^{(i-1)} \mathrm{tr}\Bigl(
+						\Bigr) + 2 t_{\mathrm{P},0}^{(i-1)} \mathrm{tr}\Bigl(
 						\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
@@
 					\Bigr)
-						\Biggr) + \mu \Biggl(
+					\Biggr)\nonumber\\
+				& \quad + \mu \Biggl(
 					2^{\bar{R}} - \prod_{n=1}^N \biggl(
@@
 					\biggr)
-					\Biggr)\nonumber\\
-					& \quad + \mathrm{tr}\biggl(
+				\Biggr) + \mathrm{tr}\biggl(
 					\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
@@
 					\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta.
-				\end{align}
-			\end{figure*}
+				\Bigr) + \zeta,
+			\end{align}
+			where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
 The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
@@
 			\end{subequations}
-			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
-			\begin{equation}
-				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star,
-			\end{equation}
-			where $\boldsymbol{\Delta}^\star$ is given by \eqref{eq:delta}.
-			\begin{figure*}[!b]
-				\hrule
+			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as $\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star$, where $\boldsymbol{\Delta}^\star$ is given by
 			\begin{align}\label{eq:delta}
@@
 			\end{align}
-			\end{figure*}
 			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.

### 2021-08-12 main.tex
:triangular_flag_on_post: arXiv and TCOM 120821

@@
 We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
-Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 			}
-			\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 			\label{fi:channel_amplitude}
@@
 		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy.
+First, it is observed that adding either active or passive elements can improve the equivalent SNR and produce a nearly concave R-E region, which suggests that the receiver should operate in the PS mode in such cases.
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.

### 2021-09-15 main.tex
:pencil: Update manuscript

@@
 			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS not only provides constructive reflection but also enables flexible subchannel design in the frequency domain, which is essential for SWIPT; 2) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 3) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 4) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 5) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 6) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 7) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 8) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 9) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, it is observed that adding either active or passive elements can improve the equivalent SNR and produce a nearly concave R-E region, which suggests that the receiver should operate in the PS mode in such cases.
+First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
@@
 As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, passive beamforming has a larger array gain and power scaling order than active beamforming.
-This behavior is more obvious in the case of WIT and WPT.
-For active beamforming, doubling $M$ brings a \SI{3}{\dBA} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power.
-Thanks to the rectenna nonlinearity, the output DC ends up with a nearly four-time (\SI{12}{\dBA}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}.
-On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dBA}, which implies a reflect array gain of $L^2$ \cite{Wu2019}.
+Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC.
+From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC by \num{16} times (\SI{24}{\dBA}), corresponding to a passive scaling law in the order of $L^4$.
+From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
+This novel observation is then verified in a simplified case where we assume the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct link is negligible.
+The DC in such case reduces to
+		\begin{equation}
+			z = \beta_2 \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^4 L^4 P^2,
+		\end{equation}
+		which scales quartically with $L$.
 Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
@@
 Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
-Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order.
-However, a large number of reflecting elements may be required to compensate the double fading effect in the auxiliary link.
+Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
+Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.
 
@@
 			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
-By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
+By reusing the proof in \cite[Appendix~A]{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
 On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.

### 2021-09-16 main.tex
:pencil: Update manuscript

@@
 During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
-Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point.
+The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
 On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
@@
 		\begin{subsection}{Active Beamforming}
-			To avoid straightforward optimization over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$, we decouple the waveform in the spatial and frequency domains to reduce the size of variables.
+			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
 The weight on subband $n$ is essentially
@@
 			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
@@
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region).
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
+To further reduce the complexity of the LC-BCD algorithm, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound.
 Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
-This novel observation is then verified in a simplified case where we assume the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct link is negligible.
+We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel is negligible.
+Let $X$ be the cascaded small-scale fading coefficient.
 The DC in such case reduces to
 		\begin{equation}
-			z = \beta_2 \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \lvert h_{\mathrm{R}} h_{\mathrm{I}} \rvert^4 L^4 P^2,
+			z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
 		\end{equation}

### 2021-09-16 review/response_3.tex
:package: Add review 3

\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[short]{optidef}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage[normalem]{ulem}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xr-hyper}
\usepackage{hyperref}

\externaldocument[M-]{../submit_3}

\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\DeclareSIUnit{\belA}{BA}
\DeclareSIUnit{\dBA}{\deci\belA}

\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}
\newcounter{response}[reviewer]
\setcounter{response}{0}

\let\svbibcite\bibcite
\def\bibcite#1#2{\svbibcite{#1}{R#2}}
\makeatletter
\let\svbiblabel\@biblabel
\def\@biblabel#1{\svbiblabel{R#1}}
\makeatother

\renewcommand{\theequation}
	{E\arabic{equation}}

\renewcommand{\thefigure}
	{F\arabic{figure}}

\renewcommand{\thetable}
	{T\arabic{table}}

\renewcommand{\thealgorithm}
	{A\arabic{algorithm}}

\newcommand{\editor}
	{\bigskip \hrule \section*{Editor}}

\newcommand{\reviewer}
	{\stepcounter{reviewer} \bigskip \hrule \section*{Reviewer \thereviewer}}

\renewcommand{\thepoint}
	{\thereviewer.\arabic{point}}

\renewcommand{\theresponse}
	{\thereviewer.\arabic{response}}

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter_3.pdf}

	\begin{editor}
		\begin{point}
			Provide more in-depth theoretical analysis on the performance of IRS-Aided SWIPT and discuss its implementation issues in practical systems such as how to obtain the information required by the system.
		\end{point}

		\begin{response}
			Thank you for the comments. Please refer to Response~\ref{re:2.1} and \ref{re:4.1}.
		\end{response}
	\end{editor}

	\begin{reviewer}
		We would like to express our appreciation for the time and effort dedicated to the reviewing of our paper.
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			It is strongly suggested to add more theoretical verification in the manuscript, e.g., the one shown in Response 2.1, in addition to the numerical verification. To avoid exceeding the page counts, the authors may want to adjust the layout/contents of their manuscript.
		\end{point}

		\begin{response}
			We appreciate this suggestion and believe adding a theoretical verification would make the discussion more convincing. The analysis in previous Response 2.1 has been incorporated into the updated manuscript as follows.
			\begin{framed}
				Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{M-Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{M-Clerckx2016a,M-Clerckx2018b}. Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC. From the perspective of WIT, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{M-Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. From the perspective of WPT, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model. We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible. Let $X$ be the cascaded small-scale fading coefficient. The DC in such case reduces to
				\begin{equation}
					z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
				\end{equation}
				which scales quartically with $L$.
			\end{framed}
			\label{re:2.1}
		\end{response}

		\begin{point}
			As shown in Response 2.2, as Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design. This observation is crucial and may be highlighted in the conclusions.
		\end{point}

		\begin{response}
			We agree with the reviewer that this is indeed an important conclusion, and have emphasized it in both the contribution and conclusion. The manuscript has been updated as follows.
			\begin{framed}
				1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design;

				\textellipsis

				Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design. Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design.
			\end{framed}
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		We would like to express our appreciation for the time and effort dedicated to the reviewing of our paper.
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			If $\delta$ and $\rho$ are unequal at each point, how to obtain the R-E region in the simulation? What is the difference of R-E region between the situation of $\delta$ and $\rho$ are unequal or equal?
		\end{point}

		\begin{response}
			We sincerely appreciate your opinions and would like to clarify this point in more details. First, recall that the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver. Each $(\delta, \rho)$ pair input to Algorithm~\ref{M-al:lc_bcd} corresponds to a unique R-E boundary point, and the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search from $(0, 0)$ to $(1, 1)$. Hence, the case of equal $\delta$ and $\rho$ is strictly no better than the case where $\delta$ and $\rho$ are not necessarily equal.

			On the other hand, we notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each R-E point. Therefore, we assume in the simulation that $\delta=\rho$ at all points to further reduce the algorithm complexity (by performing one-dimensional search instead of two-dimensional search). Simulation results showed that even the case of equal $\delta$ and $\rho$ can achieve a good R-E performance. Accordingly, we have updated the manuscript as follows.
			\begin{framed}
				Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.

				\textellipsis

				To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound for the LC-BCD algorithm.
			\end{framed}
			\label{re:4.1}
		\end{response}

		\begin{point}
			How does the decoupling process of the waveform in the spatial and frequency domains reduce the size of variables in the Response of Comment 2.4?
		\end{point}

		\begin{response}
			The original waveform and active beamforming problem~\eqref{M-op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$. By decoupling the design in spatial and frequency domains, we enable independent optimizations respectively from spatial and frequency domains and reduces the size of variables from $2MN$ to $2(M+N)$. This point has been clarified in the manuscript as follows.

			\begin{framed}
				The original waveform and active beamforming problem~\eqref{M-op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$. Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
			\end{framed}
		\end{response}

		\begin{point}
			Clarify the system model with more details in Section II. For example, what is the meaning of WIT point and WPT point? What is the positional relationship among AP, IRS and UE?
		\end{point}

		\begin{response}
			We agree with the reviewer that the description on WIT/WPT points in Section II can be ambiguous for readers. We have instead change the wording as follows.
			\begin{framed}
				\sout{Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point.} The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
			\end{framed}
			Besides, there is no constraint on the positional relationship among AP, IRS and UE. The authors believe the system model fits general ideal point-to-point IRS-aided SWIPT systems. An example is given in Fig.\ref{M-fi:layout}, and we would like to keep the model as is.
		\end{response}
	\end{reviewer}

\end{document}

### 2021-09-16 review/letter_3.tex
:package: Add review 3

--- 2021-04-13 letter.tex
@@
 	\begin{letter}{Prof.
-Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-20-1501 (Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design)}
+Liang Xiao \\ Editor \\ IEEE Transactions on Communications \\ ~ \\ Re: Decision on TCOM-TPS-21-0553.R1 (IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model)}
 		\opening{Dear Prof. Liang Xiao and Reviewers,}
@@
 The manuscript has been revised carefully based on your valuable comments and suggestions.
-In particular, we clarified the motivations and contributions of this work, added two low-complexity designs with near-optimal rate-energy performance, and considered the cases of imperfect cascaded CSIT and finite IRS reflection states.
-To answer the questions and concerns, we include a point-to-point response below, which also describes all modifications made to the manuscript.
 We hope that the revisions are to the satisfaction of the editor and reviewers.

### 2021-09-16 review/submit_3.tex
:package: Add review 3

--- 2021-09-16 main.tex
@@
 Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
+To exploit the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
 The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
@@
 			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that \hl{1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design;} 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
-The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
-On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
+\hl{The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.} On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
 The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
@@
 		\begin{subsection}{Active Beamforming}
-			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
-The weight on subband $n$ is essentially
+			\hl{The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.} The weight on subband $n$ is essentially
 			\begin{equation}\label{eq:w}
@@
 			\begin{align}
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
-			\end{align}
-			We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} \triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho}), \quad z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) \triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_IP}.
+			\end{align}
+			We upper bound \eqref{eq:g_IP} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 			\begin{mini!}
@@
 			\begin{align}
-				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
-			\end{align}
-			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+				\gamma_{m_{\mathrm{I},n}}^{(i)} = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}, \quad \gamma_{m_\mathrm{P}}^{(i)} = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_IP}.
+			\end{align}
+			With \eqref{eq:gamma_IP}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
 We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
@@
 			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
+				s_{\mathrm{I}, n} = \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \quad s_{\mathrm{P}, n} = \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_ip}
 			\end{align}
@@
 
-			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
-The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_ip}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, \hl{while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.} The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
 The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
@@
 We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity of the LC-BCD algorithm, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound.
-Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+\hl{To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound for the LC-BCD algorithm.} Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 			\centering
-			\resizebox{0.8\columnwidth}{!}{
+			\resizebox{0.5\columnwidth}{!}{
 				\input{assets/channel_amplitude.tex}
@@
 			\label{fi:channel_amplitude}
+			% \subfloat[Channel amplitude\label{fi:channel_amplitude}]{
+			% 	\resizebox{0.5\columnwidth}{!}{
+			% 		\input{assets/channel_amplitude.tex}
+			% 	}
+			% }
+			% \caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
 
-		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
+		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the sorted equivalent subchannel amplitude for one channel realization.
 Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
@@
 			\subfloat[R-E region\label{fi:re_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_subband.tex}
@@
 			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/waveform_subband.tex}
@@
 			\subfloat[R-E region\label{fi:re_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_noise.tex}
@@
 			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/splitting_ratio_noise.tex}
@@
 			\subfloat[R-E region\label{fi:re_distance}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_distance.tex}
@@
 			\subfloat[Path loss product\label{fi:path_loss}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/path_loss.tex}
@@
 			\subfloat[R-E region\label{fi:re_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_tx.tex}
@@
 			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/scaling_tx.tex}
@@
 			\subfloat[R-E region\label{fi:re_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_reflector.tex}
@@
 			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/scaling_reflector.tex}
@@
 		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
-Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
+First, it is observed that adding either active or passive elements can improve the equivalent SNR, \hl{which produces a nearly concave R-E region and favors the PS receiver.} Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
 To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
 As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
-Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC.
-From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
+\hl{Third, doubling $M$ brings a \mbox{\SI{3}{\dB}} gain at the output SNR and a \mbox{\SI{12}{\dBA}} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \mbox{\SI{6}{\dB}} gain at the output SNR and a \mbox{\SI{24}{\dBA}} increase at the harvested DC.
+From the perspective of WIT, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
-We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel is negligible.
+From the perspective of WPT, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
+We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
 Let $X$ be the cascaded small-scale fading coefficient.
-The DC in such case reduces to
+The DC in such case reduces to}
 		\begin{equation}
@@
 		\end{equation}
-		which scales quartically with $L$.
-Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+		\hl{which scales quartically with $L$.} Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
 These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
@@
 			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_irs_1mhz.tex}
@@
 			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_irs_10mhz.tex}
@@
 			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_csi.tex}
@@
 			\subfloat[Quantized IRS\label{fi:re_quantization}]{
-				\resizebox{0.45\columnwidth}{!}{
+				\resizebox{0.3\columnwidth}{!}{
 					\input{assets/re_quantization.tex}
@@
 Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-We assume the cascaded channel at subband $n$ is
-		\begin{equation}
-			\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
-		\end{equation}
-		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+We assume the cascaded channel at subband $n$ is $\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n}$, where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
 CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
@@
 Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
-Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
-Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.
+\hl{Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
+Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design.}
 

### 2021-09-16 main.tex
:pencil: Update manuscript

@@
 We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity of the LC-BCD algorithm, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound.
+To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound for the LC-BCD algorithm.
 Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
@@
 
-		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
+		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the sorted equivalent subchannel amplitude for one channel realization.
 Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
@@
 As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
 Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC.
-From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
+From the perspective of WIT, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
 An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
-We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel is negligible.
+From the perspective of WPT, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
+We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
 Let $X$ be the cascaded small-scale fading coefficient.
@@
 Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
-Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.
+Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design.
 

### 2021-09-16 review/response_3.tex
:package: Update review 3

@@
 			We sincerely appreciate your opinions and would like to clarify this point in more details.
-First, recall that the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.
+First, recall that the combining ratio $\delta$ determines the power ratio of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the power ratio of the energy harvester at the receiver.
 Each $(\delta, \rho)$ pair input to Algorithm~\ref{M-al:lc_bcd} corresponds to a unique R-E boundary point, and the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search from $(0, 0)$ to $(1, 1)$.
@@
 			On the other hand, we notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each R-E point.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.
 Therefore, we assume in the simulation that $\delta=\rho$ at all points to further reduce the algorithm complexity (by performing one-dimensional search instead of two-dimensional search).
@@
 			\begin{framed}
+				Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.
+
+				\textellipsis
+
 				Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
@@
 			The original waveform and active beamforming problem~\eqref{M-op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-By decoupling the design in spatial and frequency domains, we enable independent optimizations respectively from spatial and frequency domains and reduces the size of variables from $2MN$ to $2(M+N)$.
+By decoupling the design in spatial and frequency domains, we enable independent optimizations respectively from spatial and frequency domains and reduce the size of variables from $2MN$ to $2(M+N)$.
 This point has been clarified in the manuscript as follows.
@@
 				The original waveform and active beamforming problem~\eqref{M-op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
 			\end{framed}

### 2021-09-16 review/submit_3.tex
:package: Update review 3

@@
 			\hl{The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.} The weight on subband $n$ is essentially
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.} The weight on subband $n$ is essentially
 			\begin{equation}\label{eq:w}
@@
 			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
+			where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+\hl{Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.}}
 

### 2021-09-16 main.tex
:triangular_flag_on_post: arXiv and TCOM 210916

@@
 			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
 The weight on subband $n$ is essentially
@@
 			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
+			where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.}
 

### 2021-11-13 main.tex
:books: Update reference

@@
 			\end{maxi!}
-			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.
+			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
 In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
@@
 The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010b}.
 
@@
 The proofs are omitted here.
-Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
+Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010b}.
 Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
@@
 The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010b}.
 
@@
 Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
+Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978a}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
 Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.

### 2021-11-16 assets/ps_receiver.tex
:bento: Update assets

--- 2021-09-16 main.tex
@@
-\documentclass[journal]{IEEEtran}
-
-\usepackage{adjustbox}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{array}
-\usepackage{cite}
-\usepackage{colortbl}
-\usepackage{environ}
-\usepackage{grffile}
-\usepackage{hyperref}
-\usepackage{import}
-\usepackage{mathtools}
-\usepackage{microtype}
-\usepackage{multirow}
-\usepackage{pgfplots}
-\usepackage{siunitx}
-\usepackage{stfloats}
-\usepackage{tikz}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage[RPvoltages]{circuitikz}
-\usepackage[T1]{fontenc}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage[short]{optidef}
-\usepackage[subtle]{savetrees}
-
-\interdisplaylinepenalty=2500
-\pgfplotsset{compat=newest}
-\usetikzlibrary{plotmarks}
-\usetikzlibrary{arrows.meta}
-\usepgfplotslibrary{patchplots}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
-\DeclareSIUnit{\belA}{BA}
-\DeclareSIUnit{\dBA}{\deci\belA}
-\usetikzlibrary{arrows,matrix,positioning}
-
-\algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicthen}{\textbf{Then}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
-\algrenewcommand{\algorithmicend}{\textbf{End}}
-\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
-\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-
-\begin{document}
-	\title{IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
-	\author{
-		\IEEEauthorblockN{
-			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE,}
-			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
-		}
-		\thanks{
-			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
-
-			This paper has been submitted for publication.
-		}
-	}
-	\maketitle
-
-	\begin{abstract}
-		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength.
-To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency.
-This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes.
-Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique.
-To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes.
-Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states, and emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
-	\end{abstract}
-
-	\begin{IEEEkeywords}
-		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, beamforming design, energy harvester nonlinearity.
-	\end{IEEEkeywords}
-
-	\begin{section}{Introduction}
-		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via Radio-Frequency (RF) waves.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
-
-            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
-It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT.
-Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
-A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
-		\end{subsection}
-
-		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
-
-			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
-\cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
-The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
-		\end{subsection}
-
-		\begin{subsection}{IRS-Aided SWIPT}
-			By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
-In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
-However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
-The proposed framework provides a flexible tradeoff between performance and complexity.
-To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
-
-			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
-This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-
-			\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
-The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
-Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
-This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
-
-			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
-The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
-The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
-
-			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
-
-			\emph{Organization:} Section~\ref{se:system_model} introduces the system model.
-Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design.
-Section~\ref{se:performance_evaluation} provides simulation results.
-Section~\ref{se:conclusion_and_future_works} concludes the paper.
-
-			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
-$j$ denotes the imaginary unit.
-$\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
-$\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
-$\Re\{\cdot\}$ retrieves the real part of a complex entity.
-$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
-$\odot$ denotes the Hadamard product.
-$\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
-$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-$\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t.
-random variable $X$ ($X$ is omitted for simplicity).
-The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-$\sim$ means ``distributed as''.
-$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{System Model}\label{se:system_model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{system.pdf_tex}
-			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
-			\label{fi:system}
-		\end{figure}
-
-		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
-The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
-
-		\begin{subsection}{Transmitted Signal}
-			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
-The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
-			\end{equation}
-			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
-On the other hand, the power signal transmitted over subband $n$ at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
-			\end{equation}
-			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
-			\end{equation}
-			We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-		\end{subsection}
-
-		\begin{subsection}{Reflection Pattern and Composite Channel}
-			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
-			\begin{equation}
-				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
-			\end{equation}
-			where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.
-
-			\begin{remark}\label{re:reflection_coefficient}
-				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
-Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
-			\end{remark}
-
-			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflected channel.
-Hence, the composite equivalent channel reduces to
-			\begin{equation}\label{eq:h_n}
-				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
-			\end{equation}
-			where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
-We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
-
-			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-That is to say, IRS essentially enables a flexible subchannel design.
-In the MISO case, a similar effect also exists in the spatial domain.
-Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
-			\end{remark}
-		\end{subsection}
-
-		\begin{subsection}{Received Signal}
-			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
-			\begin{equation}
-				y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
-			\end{equation}
-			where $\tilde{n}_n(t)$ is the noise at RF band $n$.
-Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
-		\end{subsection}
-
-		\begin{subsection}{Receiving Modes}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[TS receiver\label{fi:ts_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
-						\centering
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
-								to[short,-o] ++(0,-1) node[below]{Time Switcher}
-								to[short] node[spdt,anchor=in](s){} ++(0.5,0);
-
-							\draw (s.out 1) node[above right]{$1-\eta$}
-								to ++(1.25,0)
-								to ++(0,0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
-
-							\draw (s.out 2) node[below right]{$\eta$}
-								to ++(1.25,0)
-								to ++(0,-0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
-						\end{circuitikz}
-					}
-				}
-				\\
-				\subfloat[PS receiver\label{fi:ps_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
 \begin{circuitikz}[transform shape]
@@
 \end{circuitikz}
-					}
-				}
-				\caption{Diagrams of practical co-located receivers.}
-				\label{fi:receiver}
-			\end{figure}
-
-			As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
-The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
-During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
-The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
-On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
-The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
-During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoffs.
-In the following context, we consider the optimization with the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
-		\end{subsection}
-
-		\begin{subsection}{Information Decoder}
-			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
-			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
-			\end{equation}
-			where $\sigma_n^2$ is the noise variance at the RF-band and during the RF-to-baseband conversion on tone $n$.
-		\end{subsection}
-
-		\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
-					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
-							\draw (0,2) to [short] (1,2);
-							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
-							\draw (3,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
-					}
-				}
-				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
-					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
-							\draw (0,2) to [short] (0.25,2);
-							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
-							\draw (2.25,2) to [short, -*] (2.5,2);
-							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
-							\draw (2.5,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
-					}
-				}
-				\caption{Equivalent circuits of receive antenna and energy harvester.}
-			\end{figure}
-
-			Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC on both the power and shape of the received signal.
-Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
-Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
-When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
-Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
-			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
-			\end{equation}
-			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC in this paper.
-It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling effect among different frequencies, some high-order AC components compensate each other in frequency and further contribute to the output DC power.
-In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
-Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
-
-			\begin{figure*}[!t]
-				\begin{equation*}
-					\boldsymbol{W}_{\mathrm{I/P}}=
-					\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
-						\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
-						{
-							\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-							\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
-							\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-							\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-						};
-						\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
-						\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
-						\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
-						\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
-						\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
-						\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
-						\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
-						\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
-					\end{tikzpicture}
-				\end{equation*}
-				\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
-$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
-Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
-For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
-				\label{fi:block_diagonal}
-			\end{figure*}
-
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
-				\end{align}
-			\end{figure*}
-		\end{subsection}
-
-		\begin{subsection}{Rate-Energy Region}
-			The achievable R-E region is defined as
-			\begin{align}
-				\mathcal{C}_{\mathrm{R-E}}
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
-			\end{align}
-			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of the sine waves to the average value.
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
-			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
-			\addConstraint{0 \le \rho \le 1.}
-		\end{maxi!}
-		Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift; 2) the active precoder; 3) the waveform amplitude and splitting ratio, until convergence.
-
-		\begin{subsection}{Passive Beamforming}
-			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
-			\begin{align}
-				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
-			\end{align}
-			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On the other hand, we define $t_{\mathrm{I/P},k}$ as
-			\begin{align}
-				t_{\mathrm{I/P},k}
-				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
-			\end{align}
-			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
-			\begin{align}
-				R(\boldsymbol{\Phi})
-				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
-			\end{align}
-			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
-Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
-			\begin{align}
-				(t_{\mathrm{I},0}^{(i)})^2
-				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
-				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
-				& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
-				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
-				& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
-			\end{align}
-			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
-Due to symmetry \cite{Golub2013}, we have
-			\begin{equation}\label{eq:coupled_terms}
-				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
-			\end{equation}
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
-				\end{align}
-			\end{figure*}
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
-				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
-			\end{maxi!}
-			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.
-In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
-This conclusion is summarized below.
-
-			\begin{proposition}\label{pr:relaxation}
-				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
-			\end{proposition}
-
-			\begin{proof}\label{pf:relaxation}
-				Please refer to Appendix~\ref{ap:relaxation}.
-			\end{proof}
-
-			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
-The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.
-
-			\begin{algorithm}[!t]
-				\caption{SCA: IRS Phase Shift.}
-				\label{al:sca}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
-					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
-						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{proposition}\label{pr:sca}
-				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:sca}
-				Please refer to Appendix~\ref{ap:sca}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Active Beamforming}
-			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
-The weight on subband $n$ is essentially
-			\begin{equation}\label{eq:w}
-				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
-			\end{equation}
-			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
-The MRT precoder at subband $n$ is given by
-			\begin{equation}\label{eq:b_n}
-				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
-			\end{equation}
-
-			\begin{proposition}\label{pr:mrt}
-				For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
-			\end{proposition}
-
-			\begin{proof}\label{pf:mrt}
-				Please refer to Appendix~\ref{ap:mrt}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
-Hence, the rate \eqref{eq:R} reduces to
-			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
-			\end{equation}
-			and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
-				\end{align}
-			\end{figure*}
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
-				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
-			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
-			\begin{mini!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
-			\end{mini!}
-			It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
-The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
-			\begin{align}
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
-			\end{align}
-			We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
-			\begin{mini!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
-				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
-				\addConstraint{\rho + \bar{\rho} \le 1,}
-			\end{mini!}
-			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
-			\begin{align}
-				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
-			\end{align}
-			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
-We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
-The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
-
-			\begin{algorithm}[!t]
-				\caption{GP: Waveform Amplitude and Splitting Ratio.}
-				\label{al:gp}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
-					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{proposition}\label{pr:gp}
-				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:gp}
-				Please refer to \cite{Clerckx2016a,Clerckx2018b}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Low-Complexity Adaptive Design}
-			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively.
-For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
-			\begin{equation}\label{eq:wf}
-				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
-			\end{equation}
-			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
-On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
-			\begin{equation}\label{eq:smf}
-				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
-			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
-When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
-When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
-			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
-			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
-
-			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
-The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-Similarly, no loss is introduced by SDR and local optimality is guaranteed.
-The proofs are omitted here.
-Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
-
-			\begin{algorithm}[!t]
-				\caption{M-SCA: IRS Phase Shift.}
-				\label{al:m_sca}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-					\If{$\rho=0$}
-						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
-					\Else
-						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
-						\Repeat
-							\State $i \gets i + 1$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
-								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-						\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-					\EndIf
-					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-		\end{subsection}
-
-		\begin{subsection}{Block Coordinate Descent}
-			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
-It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
-
-			\begin{algorithm}[!t]
-				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
-				\label{al:bcd}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
-					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
-The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
-
-			\begin{algorithm}[!t]
-				\caption{LC-BCD: Waveform and Beamforming.}
-				\label{al:lc_bcd}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
-					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\If{$\rho=0$}
-							\State $\Delta \gets R^{(i)} - R^{(i-1)}$
-						\Else
-							\State $\Delta \gets z^{(i)} - z^{(i-1)}$
-						\EndIf
-					\Until $\lvert \Delta \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{layout.pdf_tex}
-			\caption{System layout in simulation.}
-			\label{fi:layout}
-		\end{figure}
-
-		To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
-$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
-The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
-All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
-CSCG variables.
-Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity of the LC-BCD algorithm, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound.
-Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/channel_amplitude.tex}
-			}
-			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-			\label{fi:channel_amplitude}
-		\end{figure}
-
-		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
-Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
-Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
-On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
-Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
-In other words, IRS has a subtle impact on the waveform design.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_subband.tex}
-				}
-			}
-			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_subband.tex}
-				}
-			}
-			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-This is because less power is allocated to each subband but more balanced DC terms are introduced by frequency coupling to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
-It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-This observation origins from the rectifier nonlinearity.
-Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
-Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
-It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
-Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_noise.tex}
-				}
-			}
-			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/splitting_ratio_noise.tex}
-				}
-			}
-			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		The average noise power influences the R-E region as shown in Fig.~\subref*{fi:re_noise}.
-First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
-At low SNR, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
-As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power because of frequency coupling and harvester nonlinearity.
-Second, there exists a turning point in the R-E region, especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
-As $\bar{R}$ further decreases, thanks to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
-The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
-Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_distance}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_distance.tex}
-				}
-			}
-			\subfloat[Path loss product\label{fi:path_loss}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/path_loss.tex}
-				}
-			}
-			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		In Fig.~\subref*{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
-Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
-It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_tx.tex}
-				}
-			}
-			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_tx.tex}
-				}
-			}
-			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_reflector.tex}
-				}
-			}
-			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_reflector.tex}
-				}
-			}
-			\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
-		\end{figure}
-
-		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
-Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
-Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC.
-From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
-An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
-We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel is negligible.
-Let $X$ be the cascaded small-scale fading coefficient.
-The DC in such case reduces to
-		\begin{equation}
-			z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
-		\end{equation}
-		which scales quartically with $L$.
-Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_1mhz.tex}
-				}
-			}
-			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_10mhz.tex}
-				}
-			}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
-The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
-The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region.
-The random IRS models the phase shift of all elements as i.i.d.
-uniform random variables over $[0, 2\pi)$.
-First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after averaging.
-Second, when the bandwidth is small, the performance of ideal, adaptive, and WIT/WPT-optimized IRS are similar; when the bandwidth is large, the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
-On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoffs points for broadband SWIPT.
-As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high SNR, or focused on a few strongest subbands to boost the output DC, thanks to adaptive passive beamforming.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_csi.tex}
-				}
-			}
-			\subfloat[Quantized IRS\label{fi:re_quantization}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_quantization.tex}
-				}
-			}
-			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.
-$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
-		\end{figure}
-
-		We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance.
-Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-We assume the cascaded channel at subband $n$ is
-		\begin{equation}
-			\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
-		\end{equation}
-		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
-These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
-	\end{section}
-
-	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage BCD algorithm was proposed to solve the problem.
-In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition.
-In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method.
-We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity.
-Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
-Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
-Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.
-
-        One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
-	\end{section}
-
-	\begin{appendix}
-		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
-			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds because of the modulus constraint~\eqref{co:irs_modulus}.
-Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and recast problem~\eqref{op:irs} as
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
-				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
-				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
-			\end{maxi!}
-			By applying SDR, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
-$\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, and strong duality holds.
-The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}\label{eq:lagrangian}
-					\mathcal{L}
-					& = \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
-							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
-						\Bigr) - \frac{3}{4} \beta_4 \rho^2 \Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
-								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-							\Bigr) + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
-								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
-							\Bigr)\nonumber\\
-					& \quad + 2 t_{\mathrm{P},0}^{(i-1)} \mathrm{tr}\Bigl(
-							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-						\Bigr) + 2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
-							\boldsymbol{C}_{\mathrm{P},0} \boldsymbol{\Phi}^{(i)}
-						\Bigr)
-						\Biggr) + \mu \Biggl(
-						2^{\bar{R}} - \prod_{n=1}^N \biggl(
-							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
-								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
-							\Bigr)}{\sigma_n^2}
-						\biggr)
-					\Biggr)\nonumber\\
-					& \quad + \mathrm{tr}\biggl(
-						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
-							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
-						\Bigr)
-					\biggr) - \mathrm{tr} \Bigl(
-						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta.
-				\end{align}
-			\end{figure*}
-			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
-			\begin{subequations}
-				\begin{equation}\label{eq:lagrange_multiplier}
-					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
-				\end{equation}
-				\begin{equation}\label{eq:complementary_slackness}
-					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
-				\end{equation}
-				\begin{equation}\label{eq:gradient}
-					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
-				\end{equation}
-			\end{subequations}
-			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
-			\begin{equation}
-				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star,
-			\end{equation}
-			where $\boldsymbol{\Delta}^\star$ is given by \eqref{eq:delta}.
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}\label{eq:delta}
-					\boldsymbol{\Delta}^\star
-					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
-						\Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + 2 t_{\mathrm{P},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + 2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{P},0}
-						\Biggr)\nonumber\\
-					& \quad + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
-						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
-							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
-						\Bigr)}{\sigma_{n'}^2}
-					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).
-				\end{align}
-			\end{figure*}
-			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
-By reusing the proof in \cite[Appendix~A]{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
-On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.
-Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}.
-Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
-		\end{subsection}
-
-		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
-			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above because of the unit-modulus constraint \eqref{co:irs_modulus}.
-Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
-According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
-		\end{subsection}
-
-		\begin{subsection}{Proof of Proposition~\ref{pr:mrt}}\label{ap:mrt}
-			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ and maximizes the rate \eqref{eq:R}.
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ and maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}.
-Therefore, MRT is the global optimal information and power precoder.
-		\end{subsection}
-	\end{appendix}
-
-	\bibliographystyle{IEEEtran}
-	\bibliography{IEEEabrv,library.bib}
-\end{document}

### 2021-11-16 assets/ts_receiver.tex
:bento: Update assets

--- 2021-09-16 main.tex
@@
-\documentclass[journal]{IEEEtran}
-
-\usepackage{adjustbox}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{array}
-\usepackage{cite}
-\usepackage{colortbl}
-\usepackage{environ}
-\usepackage{grffile}
-\usepackage{hyperref}
-\usepackage{import}
-\usepackage{mathtools}
-\usepackage{microtype}
-\usepackage{multirow}
-\usepackage{pgfplots}
-\usepackage{siunitx}
-\usepackage{stfloats}
-\usepackage{tikz}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage[RPvoltages]{circuitikz}
-\usepackage[T1]{fontenc}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage[short]{optidef}
-\usepackage[subtle]{savetrees}
-
-\interdisplaylinepenalty=2500
-\pgfplotsset{compat=newest}
-\usetikzlibrary{plotmarks}
-\usetikzlibrary{arrows.meta}
-\usepgfplotslibrary{patchplots}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\DeclareSIUnit{\belm}{Bm}
-\DeclareSIUnit{\dBm}{\deci\belm}
-\DeclareSIUnit{\beli}{Bi}
-\DeclareSIUnit{\dBi}{\deci\beli}
-\DeclareSIUnit{\belA}{BA}
-\DeclareSIUnit{\dBA}{\deci\belA}
-\usetikzlibrary{arrows,matrix,positioning}
-
-\algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicthen}{\textbf{Then}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
-\algrenewcommand{\algorithmicend}{\textbf{End}}
-\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
-\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-
-\begin{document}
-	\title{IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
-	\author{
-		\IEEEauthorblockN{
-			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE,}
-			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
-		}
-		\thanks{
-			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
-
-			This paper has been submitted for publication.
-		}
-	}
-	\maketitle
-
-	\begin{abstract}
-		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength.
-To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency.
-This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) employing practical receiving schemes.
-Considering harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint optimization of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT).
-This problem is solved by the Block Coordinate Descent (BCD) method, where we obtain the active precoder in closed form, the passive beamforming by the Successive Convex Approximation (SCA) approach, and the waveform amplitude by the Geometric Programming (GP) technique.
-To facilitate practical implementation, we also propose a low-complexity design based on closed-form adaptive waveform schemes.
-Simulation results demonstrate the proposed algorithms bring considerable R-E gains with robustness to CSIT inaccuracy and finite IRS states, and emphasize the importance of modeling harvester nonlinearity in the IRS-aided SWIPT design.
-	\end{abstract}
-
-	\begin{IEEEkeywords}
-		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, beamforming design, energy harvester nonlinearity.
-	\end{IEEEkeywords}
-
-	\begin{section}{Introduction}
-		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via Radio-Frequency (RF) waves.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks.
-The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
-
-            The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
-It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT.
-Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
-A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
-		\end{subsection}
-
-		\begin{subsection}{Intelligent Reflecting Surface}
-			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
-
-			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
-\cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
-The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
-		\end{subsection}
-
-		\begin{subsection}{IRS-Aided SWIPT}
-			By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
-In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
-However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
-The proposed framework provides a flexible tradeoff between performance and complexity.
-To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
-
-			\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
-This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-
-			\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
-The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
-Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
-This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
-
-			\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
-The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
-The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
-
-			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
-
-			\emph{Organization:} Section~\ref{se:system_model} introduces the system model.
-Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design.
-Section~\ref{se:performance_evaluation} provides simulation results.
-Section~\ref{se:conclusion_and_future_works} concludes the paper.
-
-			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
-$j$ denotes the imaginary unit.
-$\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
-$\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
-$\Re\{\cdot\}$ retrieves the real part of a complex entity.
-$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
-$\odot$ denotes the Hadamard product.
-$\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
-$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-$\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t.
-random variable $X$ ($X$ is omitted for simplicity).
-The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-$\sim$ means ``distributed as''.
-$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{System Model}\label{se:system_model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{system.pdf_tex}
-			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
-			\label{fi:system}
-		\end{figure}
-
-		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
-The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
-
-		\begin{subsection}{Transmitted Signal}
-			Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
-The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
-			\end{equation}
-			where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
-On the other hand, the power signal transmitted over subband $n$ at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
-			\end{equation}
-			where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
-			\begin{equation}
-				\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
-			\end{equation}
-			We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
-		\end{subsection}
-
-		\begin{subsection}{Reflection Pattern and Composite Channel}
-			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
-The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
-			\begin{equation}
-				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
-			\end{equation}
-			where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.
-
-			\begin{remark}\label{re:reflection_coefficient}
-				The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
-Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
-			\end{remark}
-
-			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflected channel.
-Hence, the composite equivalent channel reduces to
-			\begin{equation}\label{eq:h_n}
-				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
-			\end{equation}
-			where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
-We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
-
-			\begin{remark}\label{re:subband_tradeoff}
-				The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-That is to say, IRS essentially enables a flexible subchannel design.
-In the MISO case, a similar effect also exists in the spatial domain.
-Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
-			\end{remark}
-		\end{subsection}
-
-		\begin{subsection}{Received Signal}
-			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
-			\begin{equation}
-				y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
-			\end{equation}
-			where $\tilde{n}_n(t)$ is the noise at RF band $n$.
-Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
-		\end{subsection}
-
-		\begin{subsection}{Receiving Modes}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[TS receiver\label{fi:ts_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
-						\centering
 \begin{circuitikz}[transform shape]
@@
 \end{circuitikz}
-					}
-				}
-				\\
-				\subfloat[PS receiver\label{fi:ps_receiver}]{
-					\resizebox{0.9\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
-								to[short,-o] ++(0,-1)
-								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
-							\draw (c.right up)
-								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
-								to ++(0,0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
-							\draw (c.right down)
-								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
-								to ++(0,-0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
-						\end{circuitikz}
-					}
-				}
-				\caption{Diagrams of practical co-located receivers.}
-				\label{fi:receiver}
-			\end{figure}
-
-			As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
-The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
-During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
-The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
-On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
-The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
-During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoffs.
-In the following context, we consider the optimization with the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
-		\end{subsection}
-
-		\begin{subsection}{Information Decoder}
-			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
-			\begin{equation}\label{eq:R}
-				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
-			\end{equation}
-			where $\sigma_n^2$ is the noise variance at the RF-band and during the RF-to-baseband conversion on tone $n$.
-		\end{subsection}
-
-		\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
-					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
-							\draw (0,2) to [short] (1,2);
-							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
-							\draw (3,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
-					}
-				}
-				\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
-					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
-							\draw (0,2) to [short] (0.25,2);
-							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
-							\draw (2.25,2) to [short, -*] (2.5,2);
-							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
-							\draw (2.5,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
-					}
-				}
-				\caption{Equivalent circuits of receive antenna and energy harvester.}
-			\end{figure}
-
-			Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC on both the power and shape of the received signal.
-Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
-Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
-When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
-Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
-			\begin{equation}\label{eq:z}
-				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
-			\end{equation}
-			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC in this paper.
-It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling effect among different frequencies, some high-order AC components compensate each other in frequency and further contribute to the output DC power.
-In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
-Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
-
-			\begin{figure*}[!t]
-				\begin{equation*}
-					\boldsymbol{W}_{\mathrm{I/P}}=
-					\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
-						\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
-						{
-							\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-							\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
-							\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-							\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-						};
-						\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
-						\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
-						\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
-						\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
-						\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
-						\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
-						\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
-						\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
-					\end{tikzpicture}
-				\end{equation*}
-				\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
-$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
-Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
-For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
-				\label{fi:block_diagonal}
-			\end{figure*}
-
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
-					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
-					&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
-				\end{align}
-			\end{figure*}
-		\end{subsection}
-
-		\begin{subsection}{Rate-Energy Region}
-			The achievable R-E region is defined as
-			\begin{align}
-				\mathcal{C}_{\mathrm{R-E}}
-				&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
-			\end{align}
-			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of the sine waves to the average value.
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{Problem Formulation}\label{se:problem_formulation}
-		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
-			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
-			\addConstraint{0 \le \rho \le 1.}
-		\end{maxi!}
-		Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift; 2) the active precoder; 3) the waveform amplitude and splitting ratio, until convergence.
-
-		\begin{subsection}{Passive Beamforming}
-			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
-			\begin{align}
-				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
-			\end{align}
-			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On the other hand, we define $t_{\mathrm{I/P},k}$ as
-			\begin{align}
-				t_{\mathrm{I/P},k}
-				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-				& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
-			\end{align}
-			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
-On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
-			\begin{align}
-				R(\boldsymbol{\Phi})
-				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-				z(\boldsymbol{\Phi})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
-			\end{align}
-			To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
-Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
-			\begin{align}
-				(t_{\mathrm{I},0}^{(i)})^2
-				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
-				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
-				& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
-				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
-				& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
-			\end{align}
-			Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
-Due to symmetry \cite{Golub2013}, we have
-			\begin{equation}\label{eq:coupled_terms}
-				\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
-			\end{equation}
-			Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					\tilde{z}(\boldsymbol{\Phi}^{(i)})
-					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
-				\end{align}
-			\end{figure*}
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
-				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
-			\end{maxi!}
-			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}.
-In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
-This conclusion is summarized below.
-
-			\begin{proposition}\label{pr:relaxation}
-				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
-			\end{proposition}
-
-			\begin{proof}\label{pf:relaxation}
-				Please refer to Appendix~\ref{ap:relaxation}.
-			\end{proof}
-
-			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
-The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.
-
-			\begin{algorithm}[!t]
-				\caption{SCA: IRS Phase Shift.}
-				\label{al:sca}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
-					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
-						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{proposition}\label{pr:sca}
-				For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:sca}
-				Please refer to Appendix~\ref{ap:sca}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Active Beamforming}
-			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$.
-The weight on subband $n$ is essentially
-			\begin{equation}\label{eq:w}
-				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
-			\end{equation}
-			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
-The MRT precoder at subband $n$ is given by
-			\begin{equation}\label{eq:b_n}
-				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
-			\end{equation}
-
-			\begin{proposition}\label{pr:mrt}
-				For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
-			\end{proposition}
-
-			\begin{proof}\label{pf:mrt}
-				Please refer to Appendix~\ref{ap:mrt}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Waveform and Splitting Ratio}
-			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
-Hence, the rate \eqref{eq:R} reduces to
-			\begin{equation}\label{eq:R_waveform}
-				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
-			\end{equation}
-			and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}
-					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
-					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
-				\end{align}
-			\end{figure*}
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
-				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
-			\end{maxi!}
-			Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
-			\begin{mini!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-				\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
-				\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
-				\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
-			\end{mini!}
-			It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
-The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
-			\begin{align}
-				1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
-			\end{align}
-			We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
-			\begin{mini!}
-				{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
-				\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
-				\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
-				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
-				\addConstraint{\rho + \bar{\rho} \le 1,}
-			\end{mini!}
-			where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
-			\begin{align}
-				\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-				\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
-			\end{align}
-			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
-We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
-The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
-
-			\begin{algorithm}[!t]
-				\caption{GP: Waveform Amplitude and Splitting Ratio.}
-				\label{al:gp}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
-					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			\begin{proposition}\label{pr:gp}
-				For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
-			\end{proposition}
-
-			\begin{proof}\label{pf:gp}
-				Please refer to \cite{Clerckx2016a,Clerckx2018b}.
-			\end{proof}
-		\end{subsection}
-
-		\begin{subsection}{Low-Complexity Adaptive Design}
-			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively.
-For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
-			\begin{equation}\label{eq:wf}
-				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
-			\end{equation}
-			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
-On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
-			\begin{equation}\label{eq:smf}
-				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
-			\end{equation}
-			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
-When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
-When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
-			\begin{align}
-				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
-			\end{align}
-			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}
-
-			Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
-The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-Similarly, no loss is introduced by SDR and local optimality is guaranteed.
-The proofs are omitted here.
-Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.
-Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
-
-			\begin{algorithm}[!t]
-				\caption{M-SCA: IRS Phase Shift.}
-				\label{al:m_sca}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
-					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
-					\If{$\rho=0$}
-						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
-					\Else
-						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
-						\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
-						\Repeat
-							\State $i \gets i + 1$
-								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
-								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-						\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-					\EndIf
-					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-		\end{subsection}
-
-		\begin{subsection}{Block Coordinate Descent}
-			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
-It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
-
-			\begin{algorithm}[!t]
-				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
-				\label{al:bcd}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
-					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-
-			For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
-The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.
-
-			\begin{algorithm}[!t]
-				\caption{LC-BCD: Waveform and Beamforming.}
-				\label{al:lc_bcd}
-				\begin{algorithmic}[1]
-					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
-					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
-					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\Repeat
-						\State $i \gets i + 1$
-						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
-						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
-						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-						\If{$\rho=0$}
-							\State $\Delta \gets R^{(i)} - R^{(i-1)}$
-						\Else
-							\State $\Delta \gets z^{(i)} - z^{(i-1)}$
-						\EndIf
-					\Until $\lvert \Delta \rvert \le \epsilon$
-					\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
-					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
-				\end{algorithmic}
-			\end{algorithm}
-		\end{subsection}
-	\end{section}
-
-	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{layout.pdf_tex}
-			\caption{System layout in simulation.}
-			\label{fi:layout}
-		\end{figure}
-
-		To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
-$d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference.
-The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
-We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
-All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
-CSCG variables.
-Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity of the LC-BCD algorithm, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound.
-Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/channel_amplitude.tex}
-			}
-			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-			\label{fi:channel_amplitude}
-		\end{figure}
-
-		Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization.
-Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
-Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
-On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
-Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
-In other words, IRS has a subtle impact on the waveform design.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_subband.tex}
-				}
-			}
-			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_subband.tex}
-				}
-			}
-			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
-First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-This is because less power is allocated to each subband but more balanced DC terms are introduced by frequency coupling to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
-It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
-This observation origins from the rectifier nonlinearity.
-Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
-Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
-It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
-Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_noise.tex}
-				}
-			}
-			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/splitting_ratio_noise.tex}
-				}
-			}
-			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		The average noise power influences the R-E region as shown in Fig.~\subref*{fi:re_noise}.
-First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
-At low SNR, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
-As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power because of frequency coupling and harvester nonlinearity.
-Second, there exists a turning point in the R-E region, especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$).
-The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
-As $\bar{R}$ further decreases, thanks to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
-The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
-Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_distance}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_distance.tex}
-				}
-			}
-			\subfloat[Path loss product\label{fi:path_loss}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/path_loss.tex}
-				}
-			}
-			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		In Fig.~\subref*{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
-Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
-It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_tx.tex}
-				}
-			}
-			\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_tx.tex}
-				}
-			}
-			\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[R-E region\label{fi:re_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_reflector.tex}
-				}
-			}
-			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_reflector.tex}
-				}
-			}
-			\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.2}{\meter}$.}
-		\end{figure}
-
-		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
-Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR and a \SI{12}{\dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the diode nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
-Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \SI{6}{\dB} gain at the output SNR and a \SI{24}{\dBA} increase at the harvested DC.
-From the perspective of WIT, passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
-An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-From the perspective of WPT, passive beamforming comes with a power scaling order $L^4$ under the diode nonlinear harvester model.
-We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel is negligible.
-Let $X$ be the cascaded small-scale fading coefficient.
-The DC in such case reduces to
-		\begin{equation}
-			z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
-		\end{equation}
-		which scales quartically with $L$.
-Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$B=\SI{1}{\MHz}$\label{fi:re_irs_1mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_1mhz.tex}
-				}
-			}
-			\subfloat[$B=\SI{10}{\MHz}$\label{fi:re_irs_10mhz}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_10mhz.tex}
-				}
-			}
-			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
-		\end{figure}
-
-		Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
-The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
-The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region.
-The random IRS models the phase shift of all elements as i.i.d.
-uniform random variables over $[0, 2\pi)$.
-First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after averaging.
-Second, when the bandwidth is small, the performance of ideal, adaptive, and WIT/WPT-optimized IRS are similar; when the bandwidth is large, the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
-On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoffs points for broadband SWIPT.
-As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high SNR, or focused on a few strongest subbands to boost the output DC, thanks to adaptive passive beamforming.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_csi.tex}
-				}
-			}
-			\subfloat[Quantized IRS\label{fi:re_quantization}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_quantization.tex}
-				}
-			}
-			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.
-$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
-		\end{figure}
-
-		We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance.
-Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
-We assume the cascaded channel at subband $n$ is
-		\begin{equation}
-			\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
-		\end{equation}
-		where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
-These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
-	\end{section}
-
-	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage BCD algorithm was proposed to solve the problem.
-In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition.
-In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method.
-We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity.
-Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
-Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
-Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of waveform design.
-
-        One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
-	\end{section}
-
-	\begin{appendix}
-		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
-			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always holds because of the modulus constraint~\eqref{co:irs_modulus}.
-Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and recast problem~\eqref{op:irs} as
-			\begin{maxi!}
-				{\scriptstyle{\boldsymbol{\Phi}}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
-				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
-				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
-				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
-				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_equivalent_rank}}
-			\end{maxi!}
-			By applying SDR, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t.
-$\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, and strong duality holds.
-The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}\label{eq:lagrangian}
-					\mathcal{L}
-					& = \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
-							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
-						\Bigr) - \frac{3}{4} \beta_4 \rho^2 \Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
-								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-							\Bigr) + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
-								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
-							\Bigr)\nonumber\\
-					& \quad + 2 t_{\mathrm{P},0}^{(i-1)} \mathrm{tr}\Bigl(
-							\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
-						\Bigr) + 2 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
-							\boldsymbol{C}_{\mathrm{P},0} \boldsymbol{\Phi}^{(i)}
-						\Bigr)
-						\Biggr) + \mu \Biggl(
-						2^{\bar{R}} - \prod_{n=1}^N \biggl(
-							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
-								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
-							\Bigr)}{\sigma_n^2}
-						\biggr)
-					\Biggr)\nonumber\\
-					& \quad + \mathrm{tr}\biggl(
-						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
-							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
-						\Bigr)
-					\biggr) - \mathrm{tr} \Bigl(
-						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
-					\Bigr) + \zeta.
-				\end{align}
-			\end{figure*}
-			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
-			\begin{subequations}
-				\begin{equation}\label{eq:lagrange_multiplier}
-					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
-				\end{equation}
-				\begin{equation}\label{eq:complementary_slackness}
-					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
-				\end{equation}
-				\begin{equation}\label{eq:gradient}
-					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
-				\end{equation}
-			\end{subequations}
-			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
-			\begin{equation}
-				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star,
-			\end{equation}
-			where $\boldsymbol{\Delta}^\star$ is given by \eqref{eq:delta}.
-			\begin{figure*}[!b]
-				\hrule
-				\begin{align}\label{eq:delta}
-					\boldsymbol{\Delta}^\star
-					& = \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
-						\Biggl(
-							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + 2 t_{\mathrm{P},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + 2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{P},0}
-						\Biggr)\nonumber\\
-					& \quad + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
-						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
-							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
-						\Bigr)}{\sigma_{n'}^2}
-					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).
-				\end{align}
-			\end{figure*}
-			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$.
-By reusing the proof in \cite[Appendix~A]{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$.
-On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$.
-Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}.
-Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
-		\end{subsection}
-
-		\begin{subsection}{Proof of Proposition~\ref{pr:sca}}\label{ap:sca}
-			The objective function \eqref{ob:irs} is non-decreasing over iterations because the solution to \eqref{ob:irs}--\eqref{co:irs_sd} at iteration $i-1$ is still feasible at iteration $i$.
-Also, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above because of the unit-modulus constraint \eqref{co:irs_modulus}.
-Thus, Algorithm~\ref{al:sca} is guaranteed to converge.
-Besides, we notice that Algorithm~\ref{al:sca} is an inner approximation algorithm \cite{Marks1978}, because $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$ and the approximation \eqref{eq:taylor_1}--\eqref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Li2013}.
-Therefore, it is guaranteed to provide a local optimal $\boldsymbol{\Phi}^{\star}$ to the relaxed passive beamforming problem.
-According to Proposition~\ref{pr:relaxation}, $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} such that $\boldsymbol{\phi}^{\star}$ can be extracted without performance loss and the local optimality inherits to the original problem~\eqref{op:original}.
-		\end{subsection}
-
-		\begin{subsection}{Proof of Proposition~\ref{pr:mrt}}\label{ap:mrt}
-			From the perspective of WIT, the MRT precoder maximizes $\lvert{\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I}, n}}\rvert = \lVert{\boldsymbol{h}_{n}}\rVert s_{\mathrm{I}, n}$ and maximizes the rate \eqref{eq:R}.
-From the perspective of WPT, the MRT precoder maximizes $(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})(\boldsymbol{h}_{n}^H \boldsymbol{w}_{\mathrm{I/P}, n})^* = \lVert{\boldsymbol{h}_{n}}\rVert^2 s_{\mathrm{I/P}, n}^2$ and maximizes the second and fourth order DC terms \eqref{eq:y_I2}--\eqref{eq:y_P4}.
-Therefore, MRT is the global optimal information and power precoder.
-		\end{subsection}
-	\end{appendix}
-
-	\bibliographystyle{IEEEtran}
-	\bibliography{IEEEabrv,library.bib}
-\end{document}

### 2021-11-17 main.tex
:triangular_flag_on_post: TCOM 211117

@@
 \usepackage{environ}
+\usepackage{graphicx}
 \usepackage{grffile}
@@
 			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{system.pdf_tex}
+			\import{assets/}{system.eps_tex}
 			\caption{An IRS-aided multi-carrier MISO SWIPT system.}
@@
 					\resizebox{0.9\columnwidth}{!}{
-						\centering
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
-								to[short,-o] ++(0,-1) node[below]{Time Switcher}
-								to[short] node[spdt,anchor=in](s){} ++(0.5,0);
-
-							\draw (s.out 1) node[above right]{$1-\eta$}
-								to ++(1.25,0)
-								to ++(0,0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
-
-							\draw (s.out 2) node[below right]{$\eta$}
-								to ++(1.25,0)
-								to ++(0,-0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
-						\end{circuitikz}
+						\includegraphics{assets/ts_receiver.eps}
 					}
@@
 					\resizebox{0.9\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
-								to[short,-o] ++(0,-1)
-								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
-							\draw (c.right up)
-								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
-								to ++(0,0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
-							\draw (c.right down)
-								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
-								to ++(0,-0.5)
-								to ++(1,0)
-								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
-						\end{circuitikz}
+						\includegraphics{assets/ps_receiver.eps}
 					}
@@
 					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{S}}$] (0,2);
-							\draw (0,2) to [short] (1,2);
-							\draw (1,2) to [R=$R_{\mathrm{A}}$] (3,2);
-							\draw (3,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{in}}$, v<=$v_{\mathrm{in}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
+						\includegraphics{assets/antenna_equivalent_circuit.eps}
 					}
@@
 					\resizebox{0.45\columnwidth}{!}{
-						\begin{circuitikz}[transform shape]
-							\draw (0,0) to [sV=$v_{\mathrm{in}}$] (0,2);
-							\draw (0,2) to [short] (0.25,2);
-							\draw (0.25,2) to [D, v<=$v_{\mathrm{D}}$, i=$i_{\mathrm{D}}$] (2.25,2);
-							\draw (2.25,2) to [short, -*] (2.5,2);
-							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
-							\draw (2.5,2) to [short] (4,2);
-							\draw (4,2) to [R=$R_{\mathrm{L}}$, v<=$v_{\mathrm{out}}$, i=$i_{\mathrm{out}}$] (4,0);
-							\draw (4,0) to [short] (2,0) node[ground](GND){};
-							\draw (2,0) to [short] (0,0);
-						\end{circuitikz}
+						\includegraphics{assets/a_single_diode_rectifier.eps}
 					}
@@
 			\def\svgwidth{0.9\columnwidth}
-			\import{assets/}{layout.pdf_tex}
+			\import{assets/}{layout.eps_tex}
 			\caption{System layout in simulation.}
@@
 			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/channel_amplitude.tex}
+				\includegraphics{assets/channel_amplitude.eps}
 			}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_subband.tex}
+					\includegraphics{assets/re_subband.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/waveform_subband.tex}
+					\includegraphics{assets/waveform_subband.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_noise.tex}
+					\includegraphics{assets/re_noise.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/splitting_ratio_noise.tex}
-				}
-			}
-			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
+					\includegraphics{assets/splitting_ratio_noise.eps}
+				}
+			}
+			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
 		\end{figure}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_distance.tex}
+					\includegraphics{assets/re_distance.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/path_loss.tex}
+					\includegraphics{assets/path_loss.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_tx.tex}
+					\includegraphics{assets/re_tx.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_tx.tex}
+					\includegraphics{assets/scaling_tx.eps}
 				}
@@
 			\subfloat[R-E region\label{fi:re_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_reflector.tex}
+				\resizebox{0.425\columnwidth}{!}{
+					\includegraphics{assets/re_reflector.eps}
 				}
@@
 			\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/scaling_reflector.tex}
+				\resizebox{0.475\columnwidth}{!}{
+					\includegraphics{assets/scaling_reflector.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_1mhz.tex}
+					\includegraphics{assets/re_irs_1mhz.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_irs_10mhz.tex}
+					\includegraphics{assets/re_irs_10mhz.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_csi.tex}
+					\includegraphics{assets/re_csi.eps}
 				}
@@
 				\resizebox{0.45\columnwidth}{!}{
-					\input{assets/re_quantization.tex}
+					\includegraphics{assets/re_quantization.eps}
 				}

### 2021-11-24 main.tex
:pencil: Update indexes

@@
 A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; 3) a combination of PS and TS is generally the best strategy; 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); 5) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
+Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
 Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
@@
 			\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that 1) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; 2) IRS mainly affects the effective channel instead of the waveform design; 3) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; 4) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; 5) there exist two optimal IRS development locations, one close to the AP and one close to the UE; 6) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; 7) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; 8) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; 9) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; 10) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that (i) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; (ii) IRS mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; (v) there exist two optimal IRS development locations, one close to the AP and one close to the UE; (vi) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; (vii) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; (viii) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; (ix) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
 
@@
 		Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates 1) the IRS phase shift; 2) the active precoder; 3) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose a BCD algorithm that iteratively updates (i) the IRS phase shift; (ii) the active precoder; (iii) the waveform amplitude and splitting ratio, until convergence.
 
@@
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; (ii) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
 As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs.

### 2021-12-03 main.tex
:triangular_flag_on_post: arXiv 211203

@@
 \begin{document}
+	\bstctlcite{IEEEexample:BSTcontrol}
 	\title{IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model}
@@
 
-			This paper has been submitted for publication.
+			Digital Object Identifier 10.1109/TCOMM.2021.3129931.
 		}
@@
 			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
-In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+In this specific case, we found the solution provided by CVX toolbox \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
 This conclusion is summarized below.
@@
 			\end{align}
-			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}.
+			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2016}.
 We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
